### 2022-11-24 abstract.tex
commit local files

% % Aus der Promotionsverordnung MNF §11 (4):
% % "Dem wissenschaftlichen Teil der Dissertation ist eine allgemein
% % verständliche kurze Zusammenfassung voranzustellen."

% \cleardoublepage
% \pdfbookmark{Zusammenfassung}{abstract_DE}

% { % need this extra grouping to avoid carry-over effects
% \begin{otherlanguage}{ngerman}
% \enlargethispage{4\baselineskip}
% \begin{center}\abstractnamefont
%   Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
%   incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis
%   nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
%   Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore
%   eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt
%   in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor
%   sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut
%   labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud
%   exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis
%   aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu
%   fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
%   culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit
%   amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore
%   et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
%   ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
%   in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
%   pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui
%   officia deserunt mollit anim id est laborum.

% \end{center}
% \end{otherlanguage}
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cleardoublepage
\pdfbookmark{Abstract}{abstract_EN}

\enlargethispage{4\baselineskip}
\begin{center}\abstractnamefont
  \textbf{Abstract}
\end{center}

The fact that a scientific finding can be replicated in an independent
replication study is central for its credibility. However, various large-scale
replication failures have shown that the replicability of scientific findings is
often lower than expected. This ``replication crisis'' has led to several
methodological reforms in the past decade, an increased conduct of replication
studies being one of them. Yet despite this rise of replication research, there
is no consensus on which statistical methods should be used for the design and
analysis of replication studies; Various methods already exist and various new
ones have been proposed in response to the crisis. This thesis centres around
the proposal from \citet{Held2020}, which is based on a reverse-Bayes approach.
The key idea is to reverse the traditional ``forward'' use of Bayes' theorem
(``prior + likelihood $\rightarrow$ posterior''), starting instead with a
pre-specified posterior and deducing the corresponding prior (``posterior +
likelihood $\rightarrow$
prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% setting as it enables the mathematical formalization of scepticism regarding the
% finding from the original study.
This allows to challenge the original finding by determining a sceptical prior
for the underlying effect size such that the resulting posterior is no longer
convincing. This prior then represents the position of a sceptic who remains
unconvinced by the original study. Whether or not the sceptics' position is
justified can then be assessed in light of the new data from the replication
study. The larger the conflict between the replication data and the sceptic, the
larger the degree of replication success. This procedure can be summarized in a
single quantitative measure of replication success, termed the sceptical
$p$-value.

The first and largest part of the thesis consists of extending this procedure. A
first extension replaces tail probabilities by Bayes factors as measures of
evidence. The sceptical prior is now determined such that the original finding
is no longer convincing in terms of a Bayes factor. In contrast to tail
probabilities, Bayes factors have a more natural interpretation and allow for
direct quantification of evidence for one hypothesis versus another. Similarly
as with the sceptical $p$-value, the procedure leads to a single measure
quantifying the degree of replication success called the sceptical Bayes factor.
A second extensions recalibrates the original procedure to produce more
appropriate inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The third extension provides a
framework for Bayesian design of replication studies. The framework allows
combining the data from the original study with external knowledge, which leads
to potentially more efficient designs compared to classical approaches.

The second part of the thesis is concerned with reverse-Bayes approaches in
general. The reverse-Bayes idea was first proposed in the 1950s, but it has
mostly been forgotten. To increase awareness and show potential use cases,
reverse-Bayes history and methods are summarized in a comprehensive review.
Furthermore, a short commentary on a recently proposed reverse-Bayes method
draws connections to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for the low replicability in
applied research. These practices can similarly harm methodological research,
but this is often not recognized. To raise awareness, an illustrative simulation
study is conducted in which it is shown how a novel method can easily be
presented as superior over established competitor methods if questionable
research practices are employed.

\textbf{Key words}: Bayesian inference, meta-science, replication studies

\newpage ~

\newpage

\begin{center}
  \vspace*{5cm}

  \textit{Dedicated to my mother Christa. \\
    You are deeply missed.}
\end{center}

### 2022-11-24 intro.Rnw
commit local files

<< "main-setup", include = FALSE >>=
## knitr options
library(knitr)
opts_chunk$set(fig.height = 4,
               echo = FALSE,
               warning = FALSE,
               message = FALSE,
               cache = FALSE,
               eval = TRUE)

## should sessionInfo be printed at the end?
Reproducibility <- FALSE

## Packages
library(ggplot2) # plotting
library(xtable) # table
library(ReplicationSuccess) # replication study stuff
library(dplyr) # data manipulation
library(UpSetR) # upset plot
@

% Aus der Promotionsordnung MNF §13 (2):
% "Eine kumulative Dissertation besteht aus einer inhaltlich zusammenhängenden
% und durch eine übergeordnete Fragestellung verbundenen Sammlung von
% Manuskripten und/oder Publikationen, denen ein einführendes Kapitel
% vorangestellt wird, das die Beiträge in eine übergeordnete Fragestellung
% einbettet, deren wissenschaftlichen Zusammenhang sowie den Mehrwert der
% Zusammenstellung gegenüber den einzelnen Teilen darlegt."

\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

% \hfill
% \begin{tabular}{p{0.7\textwidth}}
%   We can make judgments of initial probabilities and infer
%   final ones, or we can equally make judgments of final ones and infer
%   initial ones by \emph{Bayes's theorem in reverse}. \\
%   \hfill I.J. \citet[p. 29]{Good1983}
% \end{tabular}

\begin{wrapfigure}{r}{0.34\textwidth}
  \centering
  \includegraphics[height = 8.9cm]{images/xkcd.png}
  \caption*{Replication studies as illustrated by Randall Munroe
    (\url{https://xkcd.com/242/}).}
\end{wrapfigure}

\section{Replication studies}

How can we know if a finding from a study is really true? For example, how can
we know if the protective effect of a vaccine found in a study is real? The
answer to this question is of highest importance to scientists and decision
makers, but typically we can never know for sure as any study result comes with
uncertainty.

% the sad truth is that we can never know for sure.

One way to come a little closer to the truth, however, is to repeat that
original study with new subjects. Such a \emph{replication study} may then yield
similar results which would make us more confident about the original finding,
or it may yield conflicting results which would lower our confidence.
Replication studies are thus an essential part of the scientific process as they
provide a means for substantiating genuine research findings and refuting
research findings which occurred merely by chance. For this reason,
``successful'' replication is often a requirement, for example, for acceptance
of newly proposed scientific theories (\eg{} a new physical model) or the
implementation of policies based on scientific knowledge (\eg{} market approval
of a drug). The results from replication studies may thus have real world
consequences, such as deciding whether we should get vaccinated (a consequence
that anyone who experienced the COVID-19 pandemic is very aware of).

Despite their tremendous importance, the traditional academic system has made it
unattractive for researchers to conduct replication studies; the currencies of
science --publications, citations, and grant money-- are typically easier to
acquire by conducting novel research. This is because until relatively recently,
top journals in many fields refused to publish replication studies as they were
considered not ``innovative'' enough. To build a successful career, researchers
thus often had no other choice than to concentrate their efforts on producing
novel and eye-catching research results.

The perceived value of replication studies, however, has changed over the past
decade. Earlier criticisms of low research standards \citep{Altman1994,
  Ioannidis2005} were backed up by empirical evidence. For instance,
pharmaceutical companies reported surprisingly low replication rates from
pre-clinical research \citep{Begley2012} followed by later studies estimating
that %\$28 billion
billions are wasted each year on flawed and non-replicable research in medicine
and the life sciences \citep{Chalmers2014, Freedman2015, Glasziou2018}.
Similarly, reports of fraud \citep{Wicherts2011} and questionable research
practices \citep{Wagenmakers2011, Simmons2011, John2012} sparked intense
discussion about the need for higher research standards in psychology and the
social sciences. These discussions eventually culminated in large-scale
replication projects conducted by huge researcher consortia in fields such as
psychology \citep{Opensc2015, Klein2014, Klein2018, Protzko2020}, economics
\citep{Camerer2016}, the social sciences \citep{Camerer2018}, experimental
philosophy \citep{Cova2018}, or cancer biology \citep{Errington2021}.

Most of these large-scale replication projects confirmed what many researchers
had feared; carefully conducted replication studies often show less impressive
results than their original counterparts, and the replicability of research
findings is surprisingly low on average. This realization led many to declare
science as being in a ``replication crisis''. Debates arose about whether or not
the crisis really existed, and who or what was to blame \citep{Gilbert2016,
  Amrhein2019}. Even the popular press became interested
\citep[\eg{}][]{Carey2015, Kovic2016, Achenbach2017, Devlin2018}, so that also
in the eyes of the public the credibility of science became seriously
threatened.

\begin{figure}[!htb]
<< "google-scholar-graph", fig.height = 2.5 >>=
## Data gathered on October 18 2022
searchTerm <- "Replication Study"
searchDate <- as.Date(x = "2022-10-18", format = "%Y-%m-%d", tz = "GMT")
searchDateFormat <- format(searchDate, format = "%B %d %Y")
resultsAnytime <- 114000
scholarDF <- data.frame(year = seq(2022, 1990, -1),
                        results = c(4530, 11400, 13600, 12200, 11300, 10700,
                                    9880, 9220, 8660, 8200, 7500, 6700, 6040,
                                    5370, 4680, 3890, 3380, 3070, 2790, 2520,
                                    2310, 2190, 2120, 2020, 1920, 1840, 1730,
                                    1490, 1270, 1230, 1140, 1070, 970))

## plot data
ggplot(data = filter(scholarDF, year < 2022),
       aes(x = year, y = results)) +
    geom_segment(aes(xend = year, yend = 0), alpha = 0.2, size = 0.4) +
    geom_point() +
    scale_y_continuous(breaks = seq(0, 15000, 2500)) +
    scale_x_continuous(breaks = seq(1990, 2020, 5)) +
    ## scale_y_log10() +
    labs(x = "Year", y = paste0('Results for "', searchTerm, '"')) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank()## ,
          ## panel.grid.major.y = element_line(colour = "grey", linetype = "dashed")
          )
@
\caption{Number of results per year for search term ``\Sexpr{searchTerm}'' on
  Google Scholar. The search was conducted on 18 October 2022.}
\label{fig:scholar}
\end{figure}

In the midst of this doomsday, % , particularly from the hard-hit
% field of psychology,
various reforms were implemented to safe the reputation of science and to
prevent a second crisis from happening \citep[for an overview see
\eg{}][]{Munafo2017}. For instance, many journals adopted the ``registered
report'' format \citep{Chambers2021} in which a study proposal is peer reviewed
\emph{before} the study is conducted, and which, if accepted, gives provisional
publication acceptance regardless of the study outcome. Similarly, digital
infrastructure platforms, such as zenodo (\url{https://zenodo.org/}) or the open
science framework (\url{https://osf.io/}), were created to facilitate
preregistration, preprints, code, and data sharing, all of which have
substantially increased over the last decade \citep{Kidwell2016, Nosek2018,
  Rawlinson2019}. The practice of conducting replication studies has also gained
popularity, and several journals and funders are now explicitly promoting and
funding replication research \citep{NWO2016, NSL2018, Nature2022}.
Figure~\ref{fig:scholar} illustrates this trend via the yearly number of results
for ``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
that the numbers have been rapidly growing, especially after the mid 2000s (with
a minor drop in 2021, perhaps because of research slowing down due to the
COVID-19 pandemic).

\subsection{The statistics of replication studies}
Despite the increased interest in replication studies, the research community
has not yet agreed on one important question: When is a replication study
successful? For this reason, replication researchers typically report the
results from different methods for assessing replication success. For example,
\citet{Opensc2015} state ``[t]here is no single standard for evaluating
replication success. We evaluated [replicability] using significance and P
values, effect sizes, subjective assessments of replication teams, and
meta-analyses of effect sizes'' (p. 11). In the following, I will give an
overview about these and other methods which have been used in practice.

\begin{table}[!htb]
  \centering
  \caption{Study level summary statistics for original and replication study.
    The cumulative distribution function of the standard normal distribution is
    denoted by $\Phi(\cdot)$, and the $1 - \alpha$ quantile of the standard
    normal distribution is denoted by $\Phi^{-1}(1 - \alpha) = \z{\alpha}$.
    Confidence intervals and $p$-values are based on a normal approximation.}
  \label{tab:meta}
  \begin{tabular}{lcc}
    \toprule
    & Original study & Replication study \\
    \midrule
    effect estimate & $\that_o$ & $\that_{r}$ \\
    standard error & $\sigma_{o}$ & $\sigma_{r}$ \\
    $(1 - \alpha)$ confidence interval &
    $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
    $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
    % $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
    % $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
    $z$-value & $z_{o} = \that_{o}/\sigma_{o}$ & $z_{r} = \that_{r}/\sigma_{r}$ \\
    $p$-value (two-sided) & $p_{o} = 2\{1 - \Phi(|z_{o}|)\}$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    % One-sided $p$-value & $p_{o} = 1 - \Phi(|z_{o}|)$ & $p_{r} = 2\{1 - \Phi(|z_{r}|)\}$ \\
    \bottomrule
  \end{tabular}
\end{table}

Most methods for analyzing replication studies can be formulated in terms of
study level summary statistics as shown in Table~\ref{tab:meta}. % Effect
% estimates, standard error, confidence intervals, and $p$-values
All of these are routinely reported in researcher articles, and if one of them
is missing they typically can, under some assumptions, be back-calculated from
the others. Using summary statistics is also often the only possible way for
conducting the analysis as the raw data from the original study may not be
available to the replicators. The most important statistic is the effect
estimate $\that$. It provides an estimate of the underlying effect size $\theta$
which quantifies the effect or association of an intervention/exposure with an
outcome variable. Typical effect sizes are mean differences and correlations
(for continuous outcomes), odds ratios (for binary outcomes), or hazard ratios
(for time to event outcomes). Depending on the effect size type, a
transformation might be required so that the assumption of approximately
normally distributed effect estimates around the unknown effect size $\theta$
(for large enough sample sizes) is justifiable. This could be, for instance, the
Fisher $z$-transformation for correlations, or the log-transformation for
odds/hazard ratios \citep[chapter 11]{Cooper2019}. The associated standard error
$\sigma$ represents the statistical uncertainty of the estimate. Under the
assumption of (asymptotic) normality, confidence intervals for $\theta$ and
$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
computed as shown in Table~\ref{tab:meta}.

\begin{table}[!htb]
  \centering
  \caption{Statistical criteria for assessing replication success which have
    been used in practice \citep{Opensc2015, Camerer2016, Camerer2018, Cova2018,
      Errington2021}.}
  \label{tab:rsdef}
  \begin{tabular}{p{0.21\textwidth}p{0.7\textwidth}}
    \toprule
    Criterion type & Description \\
    \midrule
    Significance & The original and replication $p$-values are smaller than
                   a threshold $\alpha$ and their effect estimates show
                   the same direction
                   ($p_{o} < \alpha$, $p_{r} < \alpha$, and
                   $\sign(\that_{o}) = \sign(\that_{r})$). Usually $\alpha = 5\%$.
    \\
                   & \\
    Meta-analytic significance & The meta-analytic $p$-value is smaller than a threshold
                                 $\alpha$ ($p_{m} = 2(1 - \Phi(|\that_{m}|/\sigma_{m})) < \alpha$)
                                 where $\that_{m} =
                                 (\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r})\sigma^{2}_{m}$
                                 is the  pooled effect estimate with standard error
                                 $\sigma_{m} = (1/\sigma^{2}_{o} + 1/\sigma^{2}_{r})^{-1/2}$.
                                 Usually $\alpha = 5\%$. \\
                   & \\
    Relative effect size & The effect estimate of the replication study goes in the same
                           direction and is at least as large as $d_{\text{min}}$ times
                           the original one ($d = \that_{r}/\that_{o} \geq d_{\text{min}}$).
                           Usually $d_{\text{min}} = 1$. \\
                   & \\
    Confidence interval & The replication effect estimate is contained in the
                          $(1 - \alpha)$ original confidence interval
                          ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\sigma_{o}]$).
                          Sometimes, also defined as the original effect estimate is
                          contained in the $(1 - \alpha)$ replication confidence interval
                          ($\that_{o} \in [\that_{r} \pm z_{\alpha/2}\sigma_{r}]$).
                          Usually $\alpha = 5\%$. \\
                   & \\
    Prediction interval ($Q$-test) & The replication effect estimate is contained with its
                                     $(1 - \alpha)$ prediction interval
                                     ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\sqrt{\sigma_{o}^{2}
                                     + \sigma_{r}^{2}}]$). Usually $\alpha = 5\%$.
                                     This criterion is equivalent to $p_{Q} \geq \alpha$ where
                                     $p_{Q}$ is the $p$-value from the meta-analytic $Q$-test\footnotemark.\\
    \bottomrule
  \end{tabular}
\end{table}
\footnotetext{The $p$-value from the $Q$-test is
  $p_{Q} = 2\{1 - \Phi(\surd Q)\}$ where
  $Q = \sum_{i \in \{o, r\}} (\that_{i} - \that_{m})^{2}\sigma_{i}^{-2} = (\that_{o}- \that_{r})^{2}(\sigma^{2}_{o} + \sigma^{2}_{r})^{-1}$
  is the $Q$-statistic and $\that_{m}$ is the fixed-effects pooled estimate as
  defined in Table~\ref{tab:rsdef}.}

Table~\ref{tab:rsdef} lists commonly used criteria for replication success in
terms of the summary statistics from Table~\ref{tab:meta}. The most popular
criterion defines replication success by simultaneous statistical significance
of original and replication study along with their effect estimates showing the
same direction. This approach is also called the ``two-trials rule''
\citep{Senn2008} in drug regulation or ``vote-counting'' in meta-analysis
\citep{Cooper2019}. The criterion can similarly be defined through one-sided
$p$-values, so that the original and replication effect estimate are not
required to show the same direction as this is taken into account by the
$p$-values. Some replication projects \citep{Opensc2015, Errington2021} also
defined replication success via simultaneous non-significance of original and
replication study ($p_{o} > \alpha$ and $p_{r} > \alpha$). However, with this
definition ``replication success'' can almost always be achieved by conducting
original and replication study with just very few samples so that the $p$-values
are large. The approach is also logically questionable as it could be seen as an
instance of the ``absence of evidence fallacy'' \citep{Altman1995} meaning that
the failure to find evidence against the null hypothesis is erroneously
interpreted as evidence for the null hypothesis. Meta-analytic extensions of the
significance approach define replication success by significance of a combined
effect estimate\footnote{The meta-analytic approach can also be given a Bayesian
  interpretation: A flat prior distribution for the underlying effect size
  $\theta$ is updated by the data from original and replication study.
  Replication success defined by a meta-analytic $p$-value being smaller than
  $\alpha$ is then equivalent to replication success via a Bayesian posterior
  probability $\Pr(\theta > 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$,
  respectively, $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$
  depending on the direction of combined estimate.}. Typically, the assumption
of a common underlying effect size is seen as reasonable so that fixed-effects
meta-analysis is used for pooling. Random-effects meta-analysis has mostly been
used if more than one replication study of the same original study are conducted
since in this case replicators are often interested in also understanding
between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.

The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
compatibility in effect size between original and replication study. For
example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
much the replication effect estimate changed compared to the original one, and
the smaller $d$ the smaller the degree of replication success. Some projects
also report a confidence interval for $d$ \citep{Camerer2016, Camerer2018},
while others ignore its uncertainty and make a binary cut at one to define
replication success \citep{Errington2021}.

In contrast, the criteria based on confidence and prediction intervals define
effect size compatibility on an absolute scale. However, the criterion based on
the original confidence interval ignores the uncertainty from the replication,
whereas the criterion based on the replication confidence interval ignores the
uncertainty from the original study. The prediction interval criterion, on the
other hand, takes into account both sources of uncertainty \citep{Patil2016}.
Yet, also declaring ``replication success'' based on the prediction interval may
be logically questionable due to its connection to the meta-analytic $Q$-test.
% as it may also be seen as an instance of the ``absence of evidence fallacy''
% \citep{Altman1995};
That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is equivalent
to the replication effect estimate $\that_{r}$ being contained in its
$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
that the underlying effect sizes of original and replication study are the same
($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
corresponds to demonstrating replication failure and not replication success.
Interpreting a failure to reject the null hypothesis as evidence for it is again
an instance of the absence of evidence fallacy
\citep{Hedges2019}. % To establish replication success a
% test based on the null hypothesis $H_{0} \colon \theta_{o} \neq \theta_{r}$
% would be required \citep{Hedges2019}.
As in the case of defining replication success by simultaneous non-significance
of original and replication study, the mismatch of the null hypothesis of the
prediction interval criterion results in the undesirable property that
``replication success'' can almost always be achieved if the sample size of the
studies is small enough as the prediction interval becomes wider with larger
standard errors.

% The rapidly increasing conduct of replication studies has
% outpaced the development of methodology for their analysis which is perhaps the
% reason why many of these criteria have some logical flaws. For instance, the
% confidence interval criterion does only take into account the statistical
% variability of one of the two studies. As a result,

\subsubsection{Example: Reproducibility Project Cancer Biology}
I will now illustrate the assessment of replicability on data from the
Reproducibility Project: Cancer Biology \citep{Errington2021}. This large-scale
project attempted to replicate 53 landmark studies from the field of cancer
biology. However, due to various difficulties (\eg{} missing information from
the original studies or problems in conducting the experiments) only 23 of the
53 studies could be repeated. \citet{Errington2021} report that these
experiments led to data on 158 quantitative effects. However, from the data
which they provide only 132 quantitative effects come with original and
replication standardized mean difference effect estimates along with standard
errors, and only these data will be used in the subsequent analyses.

\begin{figure}[!htb]
<< "RPCB-graph", fig.height = 3.25 >>=
ciFormat. <- function(lower, upper) {
    paste0("[", format(round(lower, 2), nsmall = 2),
           ", ", format(round(upper, 2), nsmall = 2), "]")
}
ciFormat <- Vectorize(FUN = ciFormat.)
pFormat. <- function(p) {
    if (is.na(p)) {
        return(NA)
    } else if (p > 0.0001) {
        return(as.character(signif(p, 2)))
    } else {
        return("< 0.0001")
    }
}
pFormat <- Vectorize(FUN = pFormat.)
za <- qnorm(p = 0.975)
rpcb <- read.csv("data/rpcb.csv") |>
    mutate(zo = smdo/so,
           zr = smdr/sr,
           c = so^2/sr^2,
           d = smdr/smdo,
           po2 = 2*(1 - pnorm(q = abs(zo))),
           pr2 = 2*(1 - pnorm(q = abs(zr))),
           sm = 1/sqrt(1/so^2 + 1/sr^2),
           smdm = (smdo/so^2 + smdr/sr^2)*sm^2,
           pm2 = 2*(1 - pnorm(q = abs(smdm/sm))),
           Q = (smdo - smdr)^2/(so^2 + sr^2),
           pQ = pchisq(q = Q, df = 1, lower.tail = FALSE),
           dFormat = ifelse(d > 1,
                            paste0("\\textcolor{nicegreen}{", round(d, 2),
                                   "}"),
                            paste0("\\textcolor{red}{", round(d, 2), "}")),
           cioL = smdo - za*so,
           cioU = smdo + za*so,
           cirL = smdr - za*sr,
           cirU = smdr + za*sr,
           cimL = smdm - za*sm,
           cimU = smdm + za*sm,
           id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
           po2Format = ifelse(po2 < 0.05,
                              paste0("\\textcolor{nicegreen}{", pFormat(po2),
                                     "}"),
                              paste0("\\textcolor{red}{", pFormat(po2), "}")),
           pr2Format = ifelse(pr2 < 0.05,
                              paste0("\\textcolor{nicegreen}{", pFormat(pr2),
                                     "}"),
                              paste0("\\textcolor{red}{", pFormat(pr2), "}")),
           pm2Format = ifelse(pm2 < 0.05,
                              paste0("\\textcolor{nicegreen}{", pFormat(pm2),
                                     "}"),
                              paste0("\\textcolor{red}{", pFormat(pm2), "}")),
           pQFormat = ifelse(pQ > 0.05, paste0("\\textcolor{nicegreen}{", pFormat(pQ),
                                               "}"),
                             paste0("\\textcolor{red}{", pFormat(pQ), "}")),
           smdoFormat = paste(format(round(smdo, 2), nsmall = 2),
                              ciFormat(lower = cioL, upper = cioU)),
           smdrFormat = paste(format(round(smdr, 2), nsmall = 2),
                              ciFormat(lower = cirL, upper = cirU)),
           smdmFormat = paste(format(round(smdm, 2), nsmall = 2),
                              ciFormat(lower = cimL, upper = cimU)),
           rsig = factor(pr2 <= 0.05, levels = c(FALSE, TRUE),
                         labels = c("italic(p[r]) > 0.05",
                                    "italic(p[r]) <= 0.05")))
## compute sceptical p-value (TODO fix problems with NA)
ind <- !is.na(rpcb$zo) & !is.na(rpcb$zr) & !is.na(rpcb$c)
rpcb$ps2 <- NA
rpcb$ps2[ind] <- pSceptical(zo = rpcb$zo[ind], zr = rpcb$zr[ind], c = rpcb$c[ind],
                            alternative = "two.sided", type = "nominal")
rpcb$ps2Format <- NA
rpcb$ps2Format[ind] <- ifelse(rpcb$ps2[ind] < 0.05, paste0("\\textcolor{nicegreen}{",
                                                           pFormat(rpcb$ps2[ind]),
                                                           "}"),
                              paste0("\\textcolor{red}{", pFormat(rpcb$ps2[ind]), "}"))

zoom <- c(-2, 12)
alphazoom <- 0.6
ltyzoom <- 3
rpcbWithoutNA <- na.omit(rpcb)
plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[1], yend = zoom[1], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[2],
             y = zoom[2], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[1], xend = zoom[1],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    annotate(geom = "segment", x = zoom[2], xend = zoom[2],
             y = zoom[1], yend = zoom[2], alpha = alphazoom,
             lty = ltyzoom) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, alpha = 0.8) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "Replication effect estimate (SMD)",
         fill = "") +
    coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
    scale_fill_discrete(labels = scales::parse_format()) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          legend.position = c(0.5, 0.835))

plotB <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
    geom_abline(intercept = 0, slope = 1, alpha = 0.3) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
    geom_point(aes(fill = rsig), shape = 21, alpha = 0.8,
               show.legend = FALSE) +
    geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
    labs(x = "Original effect estimate (SMD)",
         y = "",
         fill = "") +
    coord_fixed(xlim = zoom, ylim = zoom) +
    theme_bw() +
    theme(panel.grid = element_blank())
ggpubr::ggarrange(plotA, plotB, ncol = 2, align = "v")
@
\caption{Results for 132 effects from the Reproducibility Project: Cancer
  Biology \citep{Errington2021} for which effect estimates and standard errors
  are available on standardized mean difference scale. The right plot shows a
  zoomed-in view of the dotted area in the left plot. The \textit{p}-values are
  recomputed using a normal approximation. Two study pairs with original effect
  estimate larger than 80 are not shown.}
\label{fig:rpcb}
\end{figure}

Figure~\ref{fig:rpcb} shows the original versus the replication effect estimate
(on standardized mean difference scale) with the color indicating whether the
replication study was statistically significant at the 5\% level (two-sided). As
in most other replication projects, the majority of the replications show
smaller effect estimates compared to their original counterparts (mean relative
effect estimate $\bar{d} = \Sexpr{round(mean(rpcbWithoutNA[,"d"]), 2)}$). Many
of the replications also fail to achieve statistical significance at the 5\%
level. Specifically, from the
\Sexpr{sum(rpcbWithoutNA$po2 < 0.05)} effects which were significant in the original study only \Sexpr{ sum(rpcbWithoutNA$po2 < 0.05
  & rpcbWithoutNA$pr2 < 0.05 & rpcbWithoutNA$d > 0)} were also significant in
the replication study (in the same direction).

\begin{figure}[!htb]
<< "RPCB-table1", results = "asis", fig.height = 4.8 >>=
## show number of successes
alpha <- 0.05
dmin <- 1
rpcbUpset<- rpcb |>
    filter(!is.na(po2), !is.na(pr2), !is.na(smdo), !is.na(smdr),
           !is.na(so), !is.na(sr)) |>
    mutate("Significance" = as.numeric(po2 < alpha & pr2 < alpha & sign(smdo) == sign(smdr)),
           "Meta analytic \nsignificance" = as.numeric(pm2 < alpha),
           "Relative \neffect size" = as.numeric(d >= dmin),
           "Prediction \ninterval" = as.numeric(pQ > alpha))
nsig <- sum(rpcbUpset[,"Significance"], na.rm = TRUE)
nma <- sum(rpcbUpset[,"Meta analytic \nsignificance"], na.rm = TRUE)
nres <- sum(rpcbUpset[,"Relative \neffect size"], na.rm = TRUE)
npi <- sum(rpcbUpset[,"Prediction \ninterval"], na.rm = TRUE)

upset(rpcbUpset, sets = c("Significance", "Meta analytic \nsignificance",
                          "Relative \neffect size", "Prediction \ninterval"),
      order.by = "freq", mainbar.y.label = "Successful replications (combined criteria)",
      sets.x.label = "Successful replications \n(single criterion)") #, empty.intersections = "on")
@
\caption{Upset plot for data on 132 effects from the Reproducibility Project:
  Cancer Biology \citep{Errington2021} for which effect estimates and standard
  errors are available on standardized mean difference scale. Shown are the
  number of replication successes according to the different criteria from
  Table~\ref{tab:rsdef} and their combinations. A level
  $\alpha = \Sexpr{round(100*alpha, 2)}\%$ and a relative effect size threshold
  $d_{\text{min}} = \Sexpr{dmin}$ are used.}
\label{fig:upset}
\end{figure}

Figure~\ref{fig:upset} shows how many of the replications are successful
according to the criteria from Table~\ref{tab:rsdef}, and their combinations.
For the total 132 replications, most successes occur for the meta-analytic
significance (\Sexpr{nma}) and the prediction interval criteria (\Sexpr{npi}),
followed by significance (\Sexpr{nsig}), and relative effect size (\Sexpr{nres}).
Looking at the combinations of the criteria, only in two replications are all of
them satisfied simultaneously.

A detailed view for a subset of the data from the project is given in
Table~\ref{tab:RPCB}. For no single study pair in the table are all commonly
used criteria satisfied simultaneously. For instance, the two pairs (48, 2, 1)
and (16, 3, 3) at the top of the table satisfy the significance criterion
($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic significance ($p_{m} < 0.05$)
and the $Q$-test/prediction interval criterion ($p_{Q} > 0.05$), yet the
replication effect estimate is smaller than the original one ($d < 1$).
Similarly, there is no single study pair for which all criteria indicate
replication failure. For example, the pair (5, 1, 3) at the bottom of the table
is a clear failure with respect to the relative effect estimate ($d < 1$) and
the significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test
does not indicate evidence for inconsistency of the two effect estimates
($p_{Q} > 0.05$).

Taken together, this analysis demonstrates that conclusions based on commonly
used replication success criteria often differ. It is not always clear cut
whether or not a replication is successful. Reducing replicability to a single
criterion without mentioning these difficulties, as often done by the popular
press \citep[\eg{} ``more than half of the findings did not hold up when
retested'' in][]{Carey2015}, is a clear simplification of the matter.
% that may harm the credibility of science.

\begin{landscape}
\begin{table}
  \centering
  \caption{Subset of results from the Reproducibility Project: Cancer Biology
    \citep{Errington2021}. (P, X, E) denotes effect E from experiment X, from
    original paper P. Shown are original $\that_{o}$, replication $\that_{r}$,
    and pooled effect estimate $\that_{m}$ with 95\% confidence intervals,
    variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimate
    $d = \that_{r}/\that_{o}$, original $p$-value $p_{o}$, replication $p$-value
    $p_{r}$, meta-analytic $p$-value $p_{m}$, $Q$-test $p$-value $p_{Q}$, and
    sceptical $p$-value $p_{\mathrm{S}}$. A level $\alpha = 5\%$ is used as
    threshold for replication success via $p$-values, and a threshold
    $d_{\text{min}} = 1$ for the relative effect estimate.}
  \label{tab:RPCB}
% \resizebox{1\textwidth}{!}{%
<< "RPCB-table2", results = "asis" >>=
## select a subset with one effect per paper
set.seed(7)
rpcbTable <- rpcb |>
    na.omit() |>
    filter(smdo < 80, smdr < 80) |>
    group_by(paper) |>
    sample_n(size = 1) |>
    ungroup() |>
    arrange(pr2) |>
    select(id, smdoFormat, ## so,
           smdrFormat, smdmFormat,
           c, dFormat, ## sr,
           po2Format, pr2Format, pm2Format, pQFormat, ps2Format
           )

rpcbXtable <- xtable(rpcbTable)
colnames(rpcbXtable) <- c("(P, X, E)",
                          "$\\that_o$ [95\\% CI]",
                          ## "$\\sigma_o$",
                          "$\\that_r$ [95\\% CI]",
                          "$\\that_m$ [95\\% CI]",
                          "$c$", #"$\\sigma^2_o/\\sigma^2_r$",
                          "$d$", #"$\\that_r/\\that_o$",
                          ## "$\\sigma_r$",
                          "$p_o$",
                          "$p_r$",
                          "$p_m$",
                          "$p_Q$",
                          "$p_{\\text{S}}$"
                          )
print(rpcbXtable, booktabs = TRUE, floating = FALSE, include.rownames = FALSE,
      sanitize.text.function = function(x) {x},
      size = "small")
@
% %
% }
\end{table}

\end{landscape}

\subsection{Reverse-Bayes assessment of replication studies}
In response to the lack of a standard criterion for replication success, various
methods have been proposed \citep[among others]{Verhagen2014, Simonsohn2015,
  Anderson2016, Patil2016, Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019,
  Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
thesis is to refine and extended the proposal from \citet{Held2020} which
combines \emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a
method for assessing replication success. In the following, I will summarize its
main ideas and technical underpinnings.

\subsubsection{Reverse-Bayes inference}

Bayesian inference is an approach to statistical inference where Bayes' theorem
is used to make probability statements about unknown parameters based on the
observed data. The central quantity for doing so is the distribution of the
parameters conditional on the data, called the \emph{posterior distribution}. It
can be obtained from Bayes' theorem
\begin{align*}
  f(\theta \given \text{data})
  = f(\theta) \times \frac{f(\text{data} \given \theta)}{f(\text{data})}
\end{align*}
meaning that the \emph{prior distribution} for the parameter $\theta$ with
density/probability mass function $f(\theta)$ is multiplied by the (normalized)
likelihood of the data, also know as \emph{Bayesian updating}. Parameter values
which increase the likelihood of the data become more likely \emph{a
  posteriori}, however, they are also weighted by their plausibility \emph{a
  priori} through the prior. As such, Bayesian inference provides a formal way
for combining information from the data at hand with external knowledge encoded
in the prior.

However, many also consider the prior to be the weak point of Bayesian
inference, as it is unclear how it should be specified in the absence of
external knowledge. The \emph{reverse-Bayes} approach, first proposed by
\citet{Good1950}, is one way of dealing with this issue. The idea is to flip
Bayes' theorem around
\begin{align*}
  f(\theta) = f(\theta \given \text{data}) \times
  \frac{f(\text{data})}{f(\text{data} \given \theta)}
\end{align*}
and instead ``downdate'' a posterior with the observed data. So, in contrast to
the conventional ``forward-Bayes'' approach where we start with a prior, update
it with the data, and end up with a posterior, the reverse-Bayes approach starts
with the posterior and ends up with the prior. Reverse-Bayes inference then
revolves around the question whether the resulting prior is plausible in light
of external knowledge, and if so, this could be seen as support for the
specified posterior.

To illustrate reverse-Bayes inference, let us return to the replication setting.
Assume we want to conduct inference about the unknown effect size $\theta$ based
on the effect estimate from the original study $\that_{o}$ and its standard
error $\sigma_{o}$. We will assume that $\that_{o}$ is normally distributed
around the unknown effect size $\theta$ with (known) variance equal to its
squared standard error $\sigma^{2}_{o}$, here and henceforth denoted by
$\that_{o} \given \theta \sim \Nor(\theta, \sigma^{2}_{o})$. Furthermore, we
specify a zero-mean normal prior with variance $\tau^{2}$ for the effect size
$\theta$, representing the position of a sceptic who does not believe in the
presence of a non-zero effect. The ``stubbornness'' of the sceptic is determined
by how large the variance $\tau^{2}$ is chosen. Combining the sceptical prior
with the likelihood produces then a posterior which is again normal
$\theta \given \that_{o}, \sigma_{o} \sim \Nor(\mu_{\text{post}}, \sigma^{2}_{\text{post}})$
with mean and variance
\begin{align*}
  &\mu_{\text{post}} = \frac{\that_{o}}{1 + \sigma^{2}_{o}/\tau^{2}}&
  &\text{and}&
  &\sigma^{2}_{\text{post}} = \frac{1}{1/\sigma^{2}_{o} + 1/\tau^{2}}.&
\end{align*}
The associated $(1- \alpha)$ highest posterior density credible interval is
given by
\begin{align}
  \left[\mu_{\text{post}} \pm z_{\alpha/2} \, \sigma_{\text{post}}\right]
  \label{eq:postCI}
\end{align}
and if this credible interval excludes parameter values smaller/larger than zero
(depending on the orientation of the effect size) this may be interpreted as
evidence\footnote{For readers who do not agree with this notion of evidence, do
  not panic. In this thesis we will extend this reverse-Bayes procedure to use
  alternative measures of evidence, such as Bayes factors.} for a genuine effect
found in the original study.

Depending on how large the prior variance $\tau^{2}$ is chosen, the posterior
credible interval~\eqref{eq:postCI} will either include or exclude zero.
Different data analysts may have different degrees of scepticism and may thus
choose different prior variances $\tau^{2}$. As a default choice,
\citet{Held2020} proposed to use the reverse-Bayes approach from
\citet{Matthews2001b}, that is, to determine the \emph{sufficiently sceptical
  prior variance} $\tau^{2}_{\alpha}$ so that the appropriate limit of the
$(1 - \alpha)$ credible interval is just fixed to zero. The resulting prior then
represent the beliefs of a sceptic who is just stubborn enough to not find the
original study convincing at level $\alpha$.

\begin{figure}[!htb]
<< "RBexample", fig.height = 3 >>=
## show reverse-Bayes for replications for a study and its three replications
exDat <- rpcb |>
    filter(id == "(9, 2, 5)")
to <- unique(exDat$smdo)
so <- unique(exDat$so)
zo <- to/so
tr <- exDat$smdr
sr <- exDat$sr

## do reverse-Bayes calculations
alpha <- 0.05
za <- qnorm(p = 1 - alpha/2)
sprior <- sqrt(so^2/(zo^2/za^2 - 1))
sposterior <- sqrt(1/(1/sprior^2 + 1/so^2))
mposterior <- sposterior^2*to/so^2
plotDF <- data.frame(t = c(to, tr, 0, mposterior),
                     s = c(so, sr, sprior, sposterior),
                     type = c("Original", rep("Replication", 3), "Prior",
                              "Posterior"))
plotDF$type <- factor(plotDF$type, levels = c("Original", "Posterior", "Prior",
                                              "Replication"))

## compute prior density
xprior <- seq(-3*sprior, 3*sprior, length.out = 200)
dprior <- dnorm(x = xprior, mean = 0, sd = sprior)
dpriorScaled <- 0.75*dprior#*max(dprior)

## compute posterior density
xpost <- seq(mposterior - 3*sposterior, mposterior + 3*sposterior,
             length.out = 200)
dpost <- dnorm(x = xpost, mean = mposterior, sd = sposterior)
dpostScaled <- 0.75*dpost#*max(dpost)

## prior data conflict assessment
pbox <- pchisq(q = tr^2/(sr^2 + sprior^2), df = 1, lower.tail = FALSE)
pboxFormat <- pFormat(p = pbox)
pboxLabel <- paste("italic(p)['Box'] == ", pboxFormat)
plotDF$Label <- c(NA, pboxLabel, NA, NA)
dodgewidth <- 0.5

ggplot(data = plotDF, aes(x = type, y = t)) +
    geom_hline(yintercept = 0, lty = 2, alpha = 0.3) +
    geom_pointrange(aes(ymin = t - za*s, ymax = t + za*s, col = type),
                    fatten = 3,
                    position = position_dodge2(width = dodgewidth),
                    show.legend = FALSE) +
    annotate("segment", x = 1.85, y = -0.5, xend = 1.98, yend = -0.05,
             alpha = 0.6,
             arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
    annotate("text", x = 1.85, y = -0.6, size = 3, alpha = 0.6,
             label = paste0(round(100*alpha/2, 2), "% quantile fixed at zero")) +
    annotate("segment", x = 1.6, y = 2.25, xend = 2.7, yend = 2.25,
             alpha = 0.6,
             arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
    annotate("text", x = 2.1, y = 2.45, size = 3, alpha = 0.6,
             label = "reverse-Bayes analysis") +
    annotate("segment", x = 3, y = 2.25, xend = 4, yend = 2.25,
             alpha = 0.6,
             arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
    annotate("text", x = 3.45, y = 2.45, size = 3, alpha = 0.6,
             label = "assess prior-data conflict") +
    annotate("path", x = 3 + dpriorScaled, y = xprior, color = 2, alpha = 0.5) +
    annotate("path", x = 2 + dpostScaled, y = xpost, color = 4, alpha = 0.5) +
    geom_text(aes(label = Label, y = t - za*s*0.9),
              position = position_dodge2(width = dodgewidth),
              parse = TRUE, size = 2.75, alpha = 0.8, hjust = -0.08) +
    labs(x = NULL, y = "Effect size") +
    scale_color_manual(values = c("Original" = 1, "Replication" = 1,
                                  "Posterior" = 4, "Prior" = 2)) +
    theme_bw() +
    theme(panel.grid.minor = element_blank(),
          panel.grid.major.x = element_blank(),
          axis.text.x = element_text(size = 11))
@
\caption{Illustration of reverse-Bayes assessment of replication success using
  data from the original study (Paper 9, Experiment 2, Effect 5) and its three
  replication studies from the Reproducibility Project: Cancer Biology
  \citep{Errington2021}. Shown are effect estimates and prior/posterior means
  with \Sexpr{100*(1-alpha)}\% confidence/credible interval. The original finding is
  challenged with a ``sceptical'' prior, sufficiently concentrated around zero so
  that the resulting posterior is no longer convincing at level
  $\alpha = \Sexpr{100*(alpha)}\%$.}
\label{fig:RBillustration}
\end{figure}

Figure~\ref{fig:RBillustration} illustrates the derivation of the sufficiently
sceptical prior variance for an original study included in the Reproducibility
Project: Cancer Biology with standardized mean difference effect estimate
$\that_{o} = \Sexpr{round(to, 2)}$ and standard error
$\sigma_{o} = \Sexpr{round(so, 2)}$. We see that a sufficiently sceptical prior
with variance $\tau_{\alpha}^{2} = \Sexpr{round(sprior, 2)}^{2}$ is required to
render the resulting posterior no longer convincing at level
$\alpha = \Sexpr{round(100*alpha, 2)}$\%.

\citet{Held2019a} showed that the sufficiently sceptical prior variance
$\tau^{2}_{\alpha}$ for a level $\alpha$ is available in closed-form
\begin{align}
  \tau^{2}_{\alpha} =
  \begin{cases}
    \dfrac{\sigma^{2}_{o}}{\left(z_{o}^{2}/z_{\alpha/2}^{2}\right) - 1}
    & \text{if} ~ z_{o}^{2} > z_{\alpha/2}^{2} \\
    \text{undefined} & \text{else.}
  \end{cases}
  \label{eq:tau2alpha}
\end{align}
From~\eqref{eq:tau2alpha} we see that convincing original studies (those with
large absolute $z$-values $|z_{o}|$) require smaller sufficiently sceptical
prior variances to render the posterior no longer convincing for the same level
$\alpha$. Conversely, if the original study is not convincing enough (if
$|z_{o}| \leq z_{\alpha/2}$) the sufficiently sceptical prior variance is
undefined meaning that the data provide so little evidence on their own that no
scepticism is required to make them unconvincing.

This shows that the reverse-Bayes approach based on sceptical priors can be used
to formally ``challenge'' the finding of an original study. However, once this
sceptical prior is determined, the question becomes whether it is plausible in
light of external data. A natural candidate for answering the question are data
from a replication study. In the following, I will show how Bayesian model
criticism can be used for doing so.

% \begin{figure}[!htb]
%   \centering
%   \begin{tikzpicture}[node distance = 5em, thick]
%     % nodes %
%     \node[text width=5em, text centered] (data) {Likelihood $f(\text{data} \,|\, \theta)$};
%     \node[text width=3em, text centered] (prior) [left=6.5em of data] {Prior $f(\theta)$};
%     \node[text width=5em, text centered] (post) [right=5em of data] {Posterior $f(\theta \,|\, \text{data})$};
%     \node[text width=10em, text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
%     \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};

%     % edges %
%     \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
%     \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
%     \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
%     \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
%   \end{tikzpicture}
%   \caption{Schematic illustration of forward-Bayes and reverse-Bayes inference
%     for an unknown parameter $\theta$.}
%   \label{fig:illustrationRB}
% \end{figure}

\subsubsection{Bayesian model criticism}
Model criticism describes the assessment of compatibility between observed data
and their assumed statistical model. If incompatibility is diagnosed, this
alarms the data analyst that inferences based on the model may be invalid and
modifications may be required. A formal framework for Bayesian model criticism
was first introduced by \citet{Box1980}. To understand whether a Bayesian model
M consisting of a joint distribution for parameter $\theta$ and data is
adequate, Box gave the following fundamental decomposition of the joint
distribution
\begin{align*}
  f(\theta, \text{data} \given \text{M})
  % &= f(\theta \given \text{M}) \times f(\text{data} \given \theta, \text{M})
  % \label{eq:decomp1} \\
  &= f(\theta \given \text{data}, \text{M}) \times f(\text{data} \given \text{M}).
    % \label{eq:decomp2}.
\end{align*}
% He noted from the first decomposition~\eqref{eq:decomp1} that the model M may
% only be regarded as adequate if current belief about
He reasoned that inferences based on the left factor, the posterior distribution
$f(\theta \given \text{data}, \text{M})$, should only be trusted if the right
factor, the prior predictive distribution
\begin{align*}
  f(\text{data} \given \text{M})
  = \int f(\text{data} \given \theta, \text{M}) \,
  f(\theta \given \text{M}) \, \text{d}\theta
\end{align*}
is compatible with the observed data. If the model M was indeed adequate, the
empirical distribution of the observed data should be close to their predictive
distribution under the model M. On the other hand, if the empirical distribution
differed from the predictive distribution, this would imply that model M is
inadequate due to misspecification of the likelihood
$f(\text{data} \given \theta, \text{M})$ and/or misspecification of the prior
$f(\theta \given \text{M})$.

Based on these observations, Box proposed two general approaches for conducting
Bayesian model criticism. First, the predictive density of the observed data (or
the value of a ``checking function'' applied to the observed data) can be
compared to its reference distribution via a \emph{prior predictive $p$-value}
\begin{align}
  p_{\text{Box}}
  = \Pr\left\{f(\text{data} \given \text{M}) <
  f(\text{observed data} \given \text{M})\right\},
  \label{eq:pppval}
\end{align}
that is, the probability of obtaining data with lower predictive density (``more
surprising'' data) than the observed data. The lower the $p$-value
$p_{\text{Box}}$, the more incompatibility between the observed data and the
assumed model M. This approach was used by \citet{Held2020}, and it will soon
be explained in more detail.
% The literature on Bayesian model criticism following \citet{Box1980} also
% mostly focused on prior predictive $p$-values. However, what has been mostly
% ignored is that Box also mentioned an alternative approach.
However, Box also mentioned a second approach which has mostly been forgotten.
If a second ``benchmarking'' model $\text{M}_{2}$ alternative to the model under
investigation $\text{M}_{1}$ is available, Box proposed that the \emph{prior
  predictive ratio}
\begin{align*}
  \text{PR}_{\text{Box}}
  = \frac{f(\text{observed data} \given \text{M}_{1})}{f(\text{observed data} \given \text{M}_{2})},
\end{align*}
the ratio of predictive densities from the observed data under both models,
could be used to judge the relative adequacy of model $\text{M}_{1}$. Again, the
lower the predictive ratio $\text{PR}_{\text{Box}}$, the less compatible the
observed data with the model $\text{M}_{1}$. Bayesian model criticism approaches
based on predictive ratios will be used in later parts of this
thesis\footnote{Some readers may have noted that the predictive ratio is also
  the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
  $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
  approach is therefore particularly useful in combination with reverse-Bayes
  procedures based on Bayes factors, as will be demonstrated in this thesis.}.

% In general,
% a distinction can be made between checking for \emph{likelihood-data conflict}
% and checking for \emph{prior-data conflict}. In the following, we will assume
% that the likelihood is adequate and focus on the

We now return to the replication setting. Having obtained a sceptical prior
$\theta \sim \Nor(0, \tau^{2}_{\alpha})$ with sufficiently sceptical prior
variance $\tau^{2}_{\alpha}$ from~\eqref{eq:tau2alpha}, the aim is now to assess
its adequacy in light of the data from a replication study. If we are able to
show that the prior is inadequate, this would demonstrate that scepticim
regarding the original finding is unjustified and that the original study
therefore provided evidence for a genuine effect. Under the assumption of a
normal likelihood for the replication effect estimate, \ie{}
$\that_{r} \given \theta \sim \Nor(\theta, \sigma^{2}_{r})$, the prior
predictive distribution is given by
$\that_{r} \given \theta \sim \Nor(0, \sigma^{2}_{r} + \tau^{2}_{\alpha})$. As
the prior predictive distribution is symmetric around zero, the prior predictive
$p$-value~\eqref{eq:pppval} is
% the probability of observing replication effects larger in absolute value than
% the observed one $\that_{r}$ under
\begin{align}
  p_{\text{Box}}
  = 2\left\{1 - \Phi\left(\frac{|\that_{r}|}{\sqrt{\sigma^{2}_{r} +
  \tau^{2}_{\alpha}}}\right)\right\}.
  \label{eq:pboxNorm}
\end{align}

<< "example2" >>=
## do reverse-Bayes calculations
alpha2 <- 0.1
za2 <- qnorm(p = 1 - alpha2/2)
sprior2 <- sqrt(so^2/(zo^2/za2^2 - 1))

## prior data conflict assessment
pbox2 <- pchisq(q = tr^2/(sr^2 + sprior2^2), df = 1, lower.tail = FALSE)
pboxFormat2 <- pFormat(p = pbox2)
@

Figure~\ref{fig:RBillustration} shows the prior predictive $p$-values
from~\eqref{eq:pboxNorm} computed for three example replication studies from the
Replication Project: Cancer Biology. We see that larger effect estimates show
prior predictive $p$-values $p_{\text{Box}}$, indicating more prior-data
conflict. This is because the standard errors from all three replications are
roughly the same size, so that mostly the distance between zero and the
replication effect estimate matters. The $p$-values suggest that there is hardly
any conflict between the sceptical prior and the first two replications (those
with $p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
$p_{\text{Box}} = \Sexpr{pboxFormat[2]}$), while the conflict seems larger for
the third one (the one with $p_{\text{Box}} = \Sexpr{pboxFormat[3]}$).

% However, it is not clear how numerical values of $p_{\text{Box}}$ should be
% interpreted and below which value a replication should be declared
% ``successful''.
\citet{Held2020} then defined replication success at level $\alpha$ by
\begin{align*}
  p_{\text{Box}} \leq \alpha,
\end{align*}
that is, replication success is established if there is more conflict between
the sceptical prior and the replication data than there was evidence against the
null hypothesis in the original study. For the examples in
Figure~\ref{fig:RBillustration}, all prior predictive $p$-values are larger than
the level $\alpha = 5\%$ used for computing the sufficiently sceptical prior
variance ($\tau^{2}_{\alpha} = \Sexpr{round(sprior, 2)}^{2}$), so neither of
them achieves replication success at level $\alpha = 5\%$. However, at a larger
level, \eg{} $\alpha = \Sexpr{round(alpha2*100, 2)}\%$, the corresponding
sufficiently sceptical prior variance would be smaller
($\tau^{2}_{\alpha} = \Sexpr{round(sprior2, 2)}^{2}$). Consequently, there would
be more conflict between the prior and the replication data,
% (in the same order as in Figure~\ref{fig:RBillustration}:
% $p_{\text{Box}} = \Sexpr{pboxFormat2[1]}$,
% $p_{\text{Box}} = \Sexpr{pboxFormat2[2]}$, and
% $p_{\text{Box}} = \Sexpr{pboxFormat2[3]}$),
so that the third replication would be successful (since the prior predictive
$p$-value would be
$p_{\text{Box}} = \Sexpr{pboxFormat2[3]} < \Sexpr{round(alpha2*100, 2)}\%$).

<< "example3" >>=
## do reverse-Bayes calculations
alpha2 <- 0.1
za2 <- qnorm(p = 1 - alpha2/2)
sprior2 <- sqrt(so^2/(zo^2/za2^2 - 1))

## prior data conflict assessment
pbox2 <- pchisq(q = tr^2/(sr^2 + sprior2^2), df = 1, lower.tail = FALSE)
pboxFormat2 <- pFormat(p = pbox2)

zr <- tr/sr
c <- so^2/sr^2
ps <- pSceptical(zo = zo, zr = zr, c = c, alternative = "two.sided", type = "nominal")
psFormat <- pFormat(p = ps)
@
\subsubsection{The sceptical \textit{p}-value}
To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
determine the smallest level at which replication success can be established. He
called this level the \emph{sceptical $p$-value} $p_{\text{S}}$, and showed that
it is available in closed-form
\begin{align*}
  p_{\text{S}}
  % = \inf_{\alpha \in (0, 1)} \left\{\alpha : p_{\text{Box}} \leq \alpha \right\}.
  = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
\end{align*}
where
\begin{align*}
  z_{\text{S}}^{2}
  = \begin{cases}
    z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
    \left\{\surd\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
          z_{\text{H}}^{2}(c - 1)\right\}\right]
      - z_{\text{A}}^{2}\right\}/(c - 1)
    & \text{for} ~ c \neq 1
  \end{cases}
\end{align*}
with arithmetic mean $z_{\text{A}}^{2} = (z^{2}_{o} + z^{2}_{r})/2$ and harmonic
mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$.
Replication success at level $\alpha$ is then equivalent to
$p_{\text{S}} \leq \alpha$. For instance, the sceptical $p$-values of the three
replication studies in Figure~\ref{fig:RBillustration} are
$p_{\text{S}} = \Sexpr{psFormat[1]}$, $p_{\text{S}} = \Sexpr{psFormat[2]}$, and
$p_{\text{S}} = \Sexpr{psFormat[3]}$ (from left to right), so we can see that
the third replication is unsuccessful at level $\alpha = 5\%$ but successful at
level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
have to be dichotomized but can also be interpreted as a quantitative measure of
replication success, the smaller $p_{\text{S}}$ the higher the degree of
replication success.

The sceptical $p$-value has several interesting properties \citep[section
3]{Held2020}: First, it is always larger than the maximum of the original and
replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
both $p$-values have to be smaller than $\alpha$ so that replication success
based on $p_{\text{S}} \leq \alpha$ is possible. Second, if the $p$-values
$p_{o}$ and $p_{r}$ remain fixed but the relative effect estimate
$d = \that_{r}/\that_{o}$ decreases, the sceptical $p$-value increases, meaning
that shrinkage of the replication effect estimate is penalized. The sceptical
$p$-value hence requires \emph{both} studies to be sufficiently convincing on
their own (in terms of their $p$-values), similarly to the significance
criterion for replication success. Unlike the significance criterion, however,
if the $p$-values remain fixed but the replication effect estimate $\that_{r}$
becomes smaller than the original estimate $\that_{o}$, the sceptical $p$-value
indicates less replication success. This property seems desirable in the
replication setting as a smaller replication effect estimate $\that_{r}$ may not
be practically relevant anymore, despite its statistical significance.

The results from the Reproducibility Project: Cancer Biology in
Table~\ref{tab:RPCB} illustrate these two properties. The third study from above
(19, 1, 2) fails to achieve replication success at level $\alpha = 5\%$ with the
sceptical $p$-value, even though the replication study was highly convincing
--the effect estimate was almost five times as large as in the original study.
Yet, as the approach requires both studies to be convincing on their own --and
the original study was not significant at the 5\% level-- replication success at
this level is impossible with the sceptical $p$-value. The second property is
illustrated by the fifth study from above (1, 3, 5). Here the original study was
convincing and also the replication study achieved significance. However, the
effect estimate from the replication was roughly 60\% smaller than the one from
the original study, and significance is merely achieved because the standard
error was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times). The
sceptical $p$-value is therefore only $p_{\text{S}} = 0.25$, indicating hardly
any replication success.

This concludes the introduction to replication studies and the summary of the
reverse-Bayes assessment of replication success. The interested reader is
referred to the original article by \citet{Held2020} for additional properties
(\eg{} the null distribution of the sceptical $p$-value) and extensions of the
procedure (\eg{} a one-sided version of the sceptical $p$-value, power and
sample size calculations). However, this introduction should have prepared the
reader well enough to understand the remaining parts of this thesis.

\subsubsection{Software and data}
Code and data to reproduce the analyses and recompile the thesis are available
at \url{https://doi.org/10.5281/zenodo.XXXXXXX}. All analyses were conducted in
the R programming language version \Sexpr{paste(version$major, version$minor,
  sep = ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. The
CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
\citep{Errington2021} were downloaded from
\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
  data.csv}''.

<< "sessionInfo1", eval = Reproducibility, results = "asis" >>=
## print R sessionInfo to see system information and package versions
## used to compile the manuscript (set Reproducibility = FALSE, to not do that)
cat("\\newpage \\section*{Computational details}")
@
<< "sessionInfo2", echo = Reproducibility, results = Reproducibility >>=
sessionInfo()
@

### 2022-11-24 paper1.tex
commit local files

\section*{Abstract}

Replication studies are increasingly conducted but there is no established
statistical criterion for replication success. We propose a novel approach
combining reverse-Bayes analysis with Bayesian hypothesis testing: a sceptical
prior is determined for the effect size such that the original finding is no
longer convincing in terms of a Bayes factor. This prior is then contrasted to
an advocacy prior (the reference posterior of the effect size based on the
original study), and replication success is declared if the replication data
favour the advocacy over the sceptical prior at a higher level than the original
data favoured the sceptical prior over the null hypothesis. The sceptical Bayes
factor is the highest level where replication success can be declared. A
comparison to existing methods reveals that the sceptical Bayes factor combines
several notions of replicability: it ensures that both studies show sufficient
evidence against the null and penalises incompatibility of their effect
estimates. Analysis of asymptotic properties and error rates, as well as case
studies from the Social Sciences Replication Project show the advantages of the
method for the assessment of replicability.

\textbf{Key words}:
Bayes factor, Bayesian hypothesis testing, replication studies, reverse-Bayes,
sceptical $p$-value

\section{Introduction}
As a consequence of the so-called replication crisis, the scientific community
increasingly recognises the value of replication studies, and several attempts
have been made to assess replicability on a large scale \citep{Errington2014,
Klein2014, Opensc2015, Camerer2016, Camerer2018, Cova2018}. Despite most
researchers agreeing on the importance of replication, there is currently no
agreement on a statistical criterion for replication success. Instead, a variety
of statistical methods, frequentist \citep{Simonsohn2015, Patil2016, Hedges2019,
Mathur2020}, Bayesian \citep{Bayarri2002b, Bayarri2002, Verhagen2014,
Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019}, and combinations thereof
\citep{Held2020, Pawel2020, Held2021} have been proposed to quantify replication
success.

Due to this lack of an established method, replication projects typically report
the results of several methods and it is not uncommon for these to contradict
each other. For example, both studies may find evidence against a null effect,
but the individual effect estimates may still be incompatible (often the
replication estimate is much smaller). Conversely, both estimates may be
compatible, but there may not be enough evidence against a null effect in one of
the studies.

The objective of this paper is to present a novel Bayesian method for
quantifying replication success, which builds upon a previously proposed method
\citep[the \emph{sceptical $p$-value} from][]{Held2020} and unifies several
notions of replicability. The method combines the natural fit of the
reverse-Bayes approach to the replication setting with the use of Bayes factors
for hypothesis testing \citep{Jeffreys1961, Kass1995} and model criticism
\citep{Box1980}. In a nutshell, replication success is declared if the
replication data favour an advocacy prior for the effect size, which emerges
from taking the original result at face value, over a sceptical prior, which
renders the original result unconvincing.

\citet{Held2020} proposed a reverse-Bayes approach for the assessment of
replication success: The main idea is to challenge the result from an original
study by determining a \emph{sceptical prior} for the effect size, sufficiently
concentrated around the null value such that the resulting posterior is rendered
unconvincing \citep{Matthews2001b}. An unconvincing posterior at level $\alpha$
is defined by its $(1 - \alpha)$ credible interval just including the null
value. Subsequently, the replication data are used in a prior-data conflict
assessment \citep{Box1980, Evans2006} and replication success is concluded if
there is sufficient conflict between the sceptical prior and the replication
data. Specifically, replication success at level $\alpha$ is established if the
prior predictive tail probability of the replication estimate is smaller than
$\alpha$. The smallest level $\alpha$ at which replication success can be
declared corresponds to the sceptical $p$-value.

The method comes with appealing properties: The sceptical $p$-value is never
smaller than the ordinary $p$-values from both studies, thus ensuring that they
both provide evidence against the null. At the same time, it also takes into
account the size of their effect estimates, penalising the case when the
replication estimate is smaller than the original estimate. \citet{Held2021}
further refined the method with a recalibration that allows the sceptical
$p$-value to be interpreted on the same scale as an ordinary $p$-value, as well
as ensuring appropriate frequentist properties, such as type I error rate
control if the replication sample size is not smaller than in the original
study.

Despite the methods' Bayesian nature, it relies on tail probabilities as primary
inference tool. An alternative is the Bayes factor, the principled Bayesian
solution to hypothesis testing and model selection \citep{Jeffreys1961,
Kass1995}. In contrast to tail probabilities, Bayes factors have a more natural
interpretation and allow for direct quantification of evidence for one
hypothesis versus another. In this paper we therefore extend the reverse-Bayes
procedure from \citet{Held2020} to use Bayes factors for the purpose of
quantifying evidence. This extension was suggested by \citet{Consonni2019} and
\citet{Pericchi2020} independently. Interestingly, a similar extension of the
reverse-Bayes method from \citet{Matthews2001b} was already hinted at by
\citet{Berger2001}, but to date no one has attempted to realise the idea.

The inclusion of Bayes factors leads to a new quantity which we call the
\emph{sceptical Bayes factor}. Unlike standard forward-Bayes methods, but
similar to the sceptical $p$-value, the proposed method combines two notions of
replication success: It requires from both studies to show sufficient evidence
against the null, while also penalising incompatibility of their effect
estimates. However, while the sceptical $p$-value quantifies compatibility only
indirectly through conflict with the sceptical prior, the sceptical Bayes factor
evaluates directly how likely the replication data are to occur under an
advocacy prior (the reference posterior of the effect conditional on the
original study). This direct assessment of compatibility allows for stronger
statements about the degree of replication success, and it may also lead to
different conclusions in certain situations.

This paper is structured as follows: Section \ref{sec:methods} presents the
derivation of the sceptical Bayes factor. Its asymptotic and finite sample
properties are then compared with other measures of replication success in
Section \ref{sec:comparison}. An extension to non-normal models is presented in
Section \ref{sec:tdist}. Section \ref{sec:applications} illustrates how the
method works in practice using case studies from the \emph{Social Sciences
  Replication Project} \citep{Camerer2018}. Section \ref{sec:discussion}
provides concluding remarks about strengths, limitations and extensions of the
method.

\subsection*{Notation and assumptions}
Denote the Bayes factor comparing the plausibility of hypotheses $H_1$ and $H_2$
with respect to the observed data $x$ by
\begin{align*}
  \BFcol{1}{2}(x) = \frac{f(x \given H_1)}{f(x \given H_2)}
  = \frac{\int_{\Theta_1} f(x \given \theta_1)f(\theta_1) \, \text{d}\theta_1}{
  \int_{\Theta_2} f(x \given \theta_2)f(\theta_2) \, \text{d}\theta_2},
\end{align*}
where $f(x \given H_i)$ is the marginal likelihood of the data under $H_i$
obtained by integrating the likelihood $f(x \given \theta_{i})$ with respect to
the prior distribution $f(\theta_{i})$ of the model parameters
$\theta_i \in \Theta_i$ with $i = 1, 2$. Sometimes we will also write
$\BFcol{1}{2}(x ; \phi^\prime)$ to indicate that the Bayes factor is evaluated
for a specific value $\phi^\prime$ of a hyperparameter $\phi$ of one of the
model priors. To simplify comparison with $p$-values we will orient Bayes
factors such that lower values indicate more evidence against a null hypothesis.

Let $\theta$ denote the effect of a treatment on an outcome of interest. Let
$\that_o$ and $\that_r$ denote its maximum likelihood estimates obtained from an
original (subscript $o$) and from a replication study (subscript $r$),
respectively. Let the corresponding standard errors be denoted by $\sigma_o$ and
$\sigma_r$, the $z$-values by $z_o = \that_o/\sigma_o$ and
$z_r = \that_r/\sigma_r$, and define the variance ratio as
$c = \sigma_o^2/\sigma_r^2$ and the relative effect estimate as
$d = \that_r/\that_o = z_r/(z_o\sqrt{c})$. For many effect size types the
variances are inversely proportional to the sample size, \ie
$\sigma^2_{o} = \kappa/n_{o}$ and $\sigma^2_{r} = \kappa/n_{r}$ for some unit
variance $\kappa$. The variance ratio is then the ratio of the replication to
the original sample size $c = n_{r}/n_{o}$.

We adopt a meta-analytic framework and consider the effect estimates as the
data, rather than their underlying samples, and assume that
$\that_k \given \theta \sim \Nor(\theta, \sigma^2_k)$ for $k \in \{o, r\},$ \ie
normality of the effect estimates around $\theta$, with known variances equal to
their squared standard errors. For studies with reasonable sample size, this
framework usually provides a good approximation for a wide range of (suitably
transformed) effect size types \citep[Chapter 2.4]{Spiegelhalter2004}. For
example, means and mean differences (no transformation), odds ratios, hazard
ratios, risk ratios (logarithmic transformation), or correlation coefficients
(``Fisher-$z$'' transformation). We refer to the literature of meta-analysis for
details about transformations of effect sizes \citep[\eg][Chapter
11.6]{Cooper2019}. The normal model in combination with conjugate priors enables
derivation of closed-form expressions in many cases, which allows us to easily
study limiting behaviour and facilitates interpretability. In Section
\ref{sec:tdist}, we will present relaxations of the normality assumption, which
can lead to more accurate inferences when studies have small sample sizes and/or
show extreme results.

\section{Reverse-Bayes assessment of replication success with Bayes factors}
\label{sec:methods}
% ``judgements are made concerning the values that the final
% probabilities would have after some imaginary results are obtained; then Bayes'
% theorem is used backwards to estimate what the consistent initial probabilities
% must be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain
% estimates of the final probabilities in the light of the actual observations.
% This device takes \emph{seriously} the view that a theory of probability or of
% rationality is no more than a theory of consistency'' (p. 126).
The idea of reversing Bayes' theorem was first proposed by \citet{Good1950}. He
acknowledged that in many situations there is no obvious choice for the prior
distributions involved in Bayesian analyses. On the other hand, we are often
more certain which posterior inferences would convince us regarding the
credibility of a hypothesis. For this reason, Good inverted Bayes' theorem and
derived priors, which combined with the observed data, would lead to posterior
inferences that were specified beforehand (\eg the data favour one hypothesis
over another). His reverse-Bayes inference then centred around the question
whether the resulting prior is plausible, and if so, this would legitimise the
posterior inference. See Figure~\ref{fig:RBschmema} for a graphical illustration
of this process.

\begin{figure}[!htb]
  \centering
%% first attempt
\begin{tikzpicture}[node distance = 5em, thick]
  % nodes %
  \node[font = \large] (data) {$f(\mathrm{data} \,|\, \theta)$};
  \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \mathrm{data})$};
  \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
  \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};

  % edges %
  \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
  %% other names could be:
  %% - reverse Bayesian updating vs forward Bayesian updating
  %% - Bayesian reverting
  \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
  \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
  \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
\end{tikzpicture}
\caption{Schematic illustration of reverse-Bayes and forward-Bayes inference
  for an unknown parameter $\theta$.}
\label{fig:RBschmema}
\end{figure}

Good argued that philosophically there is nothing wrong with inferences
resulting from backwards use of Bayes' theorem, since the theorem merely
constrains prior and posterior to be consistent with the laws of probability
(regardless of their conventional names suggesting a particular temporal
ordering). Despite his advocacy, the reverse-Bayes idea remained largely
unexplored until \citet{Matthews2001b} introduced the \emph{Analysis of
Credibility}, which in turn led to new developments in reverse-Bayes methodology
(see \citet{Held2021b} for a recent review). Most of these approaches use the
reversal of Bayes' theorem in order to challenge or substantiate the credibility
of scientific claims. Usually, a posterior inference corresponding to
(non-)credibility of a claim is specified, and the associated prior is then
derived from the data. Inference is subsequently carried out based on this
reverse-Bayes prior, \eg the interest is often to check whether the prior is
plausible in light of external evidence, an obvious candidate being data from a
replication study. This can be done, for example, using methods to assess
prior-data conflict \citep{Box1980, Evans2006}.

% Good, Good Thinking, P. 126:
%``In some cases it should be possible to make some progress in the estimation of
% relative initial probabilities by assuming that the current judgements are correct and
% by using Bayes's theorem backwards. This idea is closely related to the ``device
% of imaginary results'' in which judgements are made concerning the values that the
% final probabilities would have after some imaginary results are obtained; then Bayes'
% theorem is used backwards to estimate what the consistent initial probabilities must
% be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain estimates
% of the final probabilities in the light of the actual observations. This device takes
% \emph{seriously} the view that a theory of probability or of rationality is no more
% than a theory of consistency.''

In this paper, we consider a reverse-Bayes procedure consisting of two stages
that naturally fit the replication setting: We first determine a
\emph{sufficiently sceptical prior} for the effect $\theta$ such that the
original result is no longer convincing in terms of a suitable Bayes factor.
Using another Bayes factor, we then quantify replication success by comparing
how likely the replication data are predicted by the sufficiently sceptical
prior relative to an \emph{advocacy prior}, which is the posterior of the effect
$\theta$ conditional on the original data and an uninformative/reference prior.
Box \hyperref[box:nutshell]{1} provides a summary of the procedure, the
following sections will explain it in more detail.

% summarize procedure in box
\begin{table}[!hbt]
\begin{center}
\fbox{
\begin{minipage}{.95\linewidth}
  \begin{enumerate}[leftmargin=*]

    \item \textbf{Original study}:
    For the original effect estimate
$\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$ consider the point null
hypothesis $H_0 \colon \theta = 0$ vs. $\HS \colon \theta \neq 0$. Fix a level
$\gamma \in (0, 1)$ and determine the sufficiently sceptical prior under the
alternative $\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ such that the
Bayes factor contrasting $H_0$ to $\HS$
is $$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma.$$ The prior
$\theta \given \HS$ represents a \emph{sceptic} who remains unconvinced about
the presence of an effect at level $\gamma$.

    \item \textbf{Replication study}:
          For the replication effect estimate
$\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ compute the Bayes factor
contrasting the sceptic $\HS \colon \theta \sim \Nor(0, \gy \cdot \sigma^2_o)$
to an advocate $\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$. Declare
\emph{replication success} at level $\gamma$ if
          $$\BFcol{\mathrm{S}}{\mathrm{A}}(\that_r; \gy) \leq \gamma,$$
          \ie the data favour the advocate over the sceptic at a higher level
than the sceptic's initial objection.

    \item[$\rightarrow$] The \emph{sceptical Bayes factor} $\BFs$ is the
smallest level $\gamma$ at which replication success can be declared.
 \end{enumerate}
\end{minipage}
}
\end{center}
\caption*{\textbf{\textrm{Box 1}}: Summary of reverse-Bayes assessment of replication success with
Bayes factors.}
\label{box:nutshell}
\end{table}

\subsection{Data from the original study}
For the effect estimate $\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$
from the original study consider a hypothesis test comparing the null hypothesis
$H_0\colon$ $\theta = 0$ to the alternative $\HS \colon$ $\theta \neq 0$.
Specification of a prior distribution for $\theta$ under $\HS$ is now required
for Bayesian hypothesis testing. A typical choice \citep{Jeffreys1961} is a
local alternative, a unimodal symmetric prior distribution centred around the
null value. We consider the sceptical prior
$\theta \given \HS \sim \Nor(0, \sigma^2_s = g \cdot \sigma^2_o)$ with relative
sceptical prior variance $g$ for this purpose (relative to the variance from the
original estimate $g = \sigma^2_s/\sigma^2_o$), resembling the $g$-prior known
from the regression literature \citep{Zellner1986, Liang2008}. The explicit form
of the Bayes factor is then given by
\begin{align}
  \label{eq:BFo}
  \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)
  = \sqrt{1 + g} \cdot
  \exp\left\{-\frac{1}{2} \cdot \frac{g}{1 + g} \cdot z^2_o\right\}.
\end{align}

The Bayes factor from equation ~\eqref{eq:BFo} is shown in Figure ~\ref{fig:bfo}
as a function of $g$ and for different original $z$-values $z_o$. For fixed
$z_o$, it is well known that this Bayes factor is bounded from below by
\begin{align}
  \label{eq:minBFo}
  \minBF_{o} =
  \begin{cases}
    |z_o| \cdot  \exp(-z_o^2/2) \cdot \sqrt{e} & \text{for} ~ |z_o| > 1 \\
    1 & \text{for} ~ |z_o| \leq 1
  \end{cases}
\end{align}
which is reached at $\gminBFo = \max\{0, z^2_o - 1\}$ \citep{Edwards1963}.
Further increasing the relative sceptical prior variance increases
\eqref{eq:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \to \infty$ for $g \to \infty$
\citep[][Section 6.1.4]{Bernardo2000}. Hence, for a relative sceptical prior
variance $g \in [0, \gminBFo]$, the resulting Bayes factor will be
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \in [\minBF_o, 1]$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/plot-BFo-1.pdf}
\end{knitrout}
\caption{Bayes factor $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of
relative sceptical prior variance $g$ for different values of
$|z_o| = |\that_o|/\sigma_o$. Minimum Bayes factors $\minBF_{o}$ are indicated
by dots. Dashed vertical lines indicate sufficiently sceptical relative prior
variance $g_{\scriptscriptstyle \gamma}$ at level $\gamma = 1/10$, if they
exist.}
\label{fig:bfo}
\end{figure}

We now apply the reverse-Bayes idea and challenge the original finding. To do
so, we fix a level $\gamma$ above which the original finding is no longer
convincing to us. For example, this could be $\gamma = 1/10$; the threshold for
strong evidence against $H_0$ according to the classification from
\citet{Jeffreys1961}. Suppose now there exists a $\gy \leq \gminBFo$ such that
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma$. It can be shown (Appendix
\ref{appendix:ssrv}) that $\gy$ can be explicitly computed by
\begin{align}
\label{ggamma}
  \gy &=
  \begin{cases}
    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &= \lw{-1} \left(-\frac{z_o^2}{\gamma^2} \cdot
  \exp\left\{-z_o^2\right\}\right)
  \nonumber
\end{align}
with $\lw{-1}(\cdot)$ the branch of the Lambert $W$ function \citep{Corless1996}
that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, see Appendix
\ref{appendix:lambertW} for details about the Lambert $W$ function. The
sufficiently sceptical prior is then given by
$\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ and it can be interpreted
as the view of a sceptic who argues that given their prior belief about the
effect $\theta$, the observed effect estimate $\hat{\theta}_o$ cannot convince
them about the presence of a non-null effect at level $\gamma$. An alternative
data-based interpretation of sufficiently sceptical priors is to see them as the
priors obtained by updating an initial uniform prior with the data from an
imaginary study, which was $1/\gy$ times the size of the original study, and
which resulted in an effect estimate of exactly zero \citep{Held2021b}.

From Figure \ref{fig:bfo} we can see that the more compelling the original data
(\ie the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
variance $\gy$ needs to be in order to make the result no longer convincing at
level $\gamma$. In the most extreme case, when $|z_{o}| \to \infty$ and $\gamma$
remains fixed, the sufficiently sceptical prior variance will converge to
zero (Appendix \ref{appendix:lambertW}). On the other hand, if $|z_o|$ is not
sufficiently large, $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ will either be
always increasing in $g$ (if $|z_o| \leq 1$) or it will reach a minimum above
the chosen level $\gamma$. In both cases the sufficiently sceptical relative
prior variance $\gy$ is not defined since there is no need to challenge an
already unconvincing result.

A side note on the Jeffreys-Lindley paradox is worth being mentioned: If a
$\gy < \gminBFo$ exists, there exists also a $\gy^\prime > \gminBFo$ as the
Bayes factor monotonically increases in $g > \gminBFo$ and therefore must
intersect a second time with $\gamma$, due to the paradox. This means that the
more compelling the original result, the larger $\gy^\prime$ needs to be chosen,
such that the result becomes no longer convincing at level $\gamma$. However,
priors which become increasingly diffuse do not represent increasing scepticism
but rather increasing ignorance. Using \eqref{ggamma} therefore avoids this
manifestation of the Jeffreys-Lindley paradox, since it determines sceptical
priors only from the class of priors that become increasingly concentrated for
increasing evidence (\ie priors with $\gy \leq \gminBFo$). In principle, the
solution $\gy^\prime > \gminBFo $ could also be computed by replacing the
$\lw{-1}$ branch of the Lambert $W$ function in \eqref{ggamma} with the $\lw{0}$
branch, but this will not be of interest to us.

\subsection{Data from the replication study}
\label{sec:bfr}
In order to assess whether the original finding can be replicated in an
independent study, a replication study is conducted, leading to a new effect
estimate $\hat{\theta}_r$. In light of the new data, the sceptic is now
challenged by an advocate of the original finding. This is formalised with
another Bayes factor, which compares the plausibility of the replication effect
estimate $\hat{\theta}_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
sceptical prior $\HS \colon$ $\theta \sim \Nor(0, g \cdot \sigma^2_o)$ relative
to the advocacy prior $\HA \colon$ $\theta \sim \Nor(\that_o, \sigma^2_o)$. The
the view of an advocate is represented by $\HA$ since this is the posterior of
$\theta$ given the original estimate and a uniform prior (also the reference
prior for this model). The Bayes factor is given by
\begin{align}
  \label{eq:BFr}
  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
%%   &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
%%   \exp\left\{-\frac{1}{2}\left(\frac{z_r^2}{1/c + g} -
%%   \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}
  &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
  \exp\left\{-\frac{z_o^2}{2}\left(\frac{d^2}{1/c + g} -
  \frac{\left(d - 1\right)^2}{1/c + 1} \right)\right\}
\end{align}
so it depends on the original $z$-statistic $z_o$, the relative sceptical prior
variance $g$, the relative effect estimate $d = \that_r/\that_o$, and the
relative variance $c = \sigma^2_o/\sigma^2_r$.

Our goal is now to define a condition for \emph{replication success} in terms of
\eqref{eq:BFr}. It is natural to consider a replication successful if the
replication data favour the advocate over the sceptic to a higher degree than
the sceptic's initial objection to the original study. More formally, we say
that if the Bayes factor from \eqref{eq:BFr} evaluated at the sufficiently
sceptical relative prior variance $\gy$ is not larger than the corresponding
level $\gamma$ used to define the sufficiently sceptical prior:
\begin{align}
  \label{eq:success}
  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
  \leq \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) =\gamma,
\end{align}
we have established \emph{replication success at level $\gamma$}.

For example, if we observe $z_o = 3$ (equivalent to minimum Bayes factor
$\minBF_{o} = 1/18$) and choose a level $\gamma = 1/10$
the sufficiently sceptical relative prior variance \eqref{ggamma} is
$\gy = 1.6$. If a replication is conducted with the
same precision ($c = 1$) and we observe $z_r = 2.5$ (equivalent to
minimum Bayes factor $\minBF_{r} = 1/5.5$ and relative effect
estimate $d = z_{r}/(z_{o}\sqrt{c}) = 0.83$), using equation
\eqref{eq:BFr} this would lead to $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r;
1.6) = 1/3.5$, which means
that the replication was not successful at level $\gamma = 1/10$.
However, if we had chosen a less stringent level, \eg$\gamma =
1/3$, the replication would have been considered successful
since then $\gy = 0.4$ and
$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; 0.4)
= 1/7.4$.

\subsection{The sceptical Bayes factor}
Apart from specifying a level $\gamma$, the described procedure offers an
automated way to assess replication success. One way to remove this dependence
is to find the smallest level $\gamma$ where replication success can be
established. We thus call this level the \emph{the sceptical Bayes factor}
\begin{align}
  \label{eq:bfs}
  \BFs
  =
  %% \inf_{\gy \in [0, \gminBFo]}
  \inf
  \Big\{\gamma :
  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
  \leq \gamma\Big\},
\end{align}
and replication success at level $\gamma$ is equivalent with $\BFs \leq \gamma$.

Figure \ref{fig:bfs} shows $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ as a function of $\gy$ for several
values of $z_o$ and $d$ along with the corresponding $\BFs$. Typically, $\BFs$
is given by the height of the intersection between
$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ in $\gy$. It may also happen that
$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ remains below
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ for all values of $\gy$, in such
situations $\BFs$ is equal to the original minimum Bayes factor $\minBF_o$.
Finally, in some pathological cases it may happen that either $z_o$, $d$, or
both are so small that replication success cannot be established for any level
$\gamma$ and hence $\BFs$ does not exist. This means that the replication study
was unsuccessful since it is impossible for the advocate to convince the sceptic
at any level of evidence.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/plot-BFs-1}
\end{knitrout}
\caption{Bayes factors $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of the sufficiently
sceptical relative prior variance $\gy$. In all examples
$c = \sigma^2_o/\sigma^2_r = 1$. Minimum Bayes factors $\minBF_o$ are indicated
by dots, sceptical Bayes factors $\BFs$ are indicated by crosses where existent.}
\label{fig:bfs}
\end{figure}

In terms of computing the sceptical Bayes factor, it is worth noting that for
the special case when the replication is conducted with the same precision as
the original study ($c = 1$) and $\BFs$ is located at the intersection of
$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ in $g$, there is an explicit expression
for $\BFs$
\begin{align}
  \label{eq:BFsc1}
  \BFs =
  \sqrt{-\frac{z^2_{o}}{k} \cdot \frac{1 + d^{2}}{2}} \cdot
  \exp\left\{-\left(\frac{z_o^2}{2} + \frac{k}{1 + d^2}\right)\right\}
\end{align}
with
$$k = \lw{}\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{d^{2} + 1}{2} \cdot \exp\left\{-\frac{z_o^2}{2}
  \left[1 + \frac{(1 -
d)^2}{2}\right]\right\}\right),$$ see Appendix \ref{appendix:bfs} for details.

\section{Properties}
\label{sec:comparison}
To study properties of the sceptical Bayes factor and facilitate comparison with
other methods we will look at the requirements for replication success based on
the relative effect estimate $d = \that_{r}/\that_{o}$, the variance ratio
$c = \sigma^{2}_{o}/\sigma^{2}_{r}$ and the original minimum Bayes factor
$\minBF_{o}$ (respectively the original $z$-value $z_{o}$). This perspective is
helpful because it disentangles how the method reacts to changes in
compatibility of the effect estimates ($d$), evidence from the original study
($\minBF_{o}$), and the change in sample size of the replication compared to the
original study ($c$).

The condition for replication success at level $\gamma$ from \eqref{eq:success}
is equivalent to
\begin{align}
  \label{eq:RSCond-d}
  \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
  \frac{z_o^2}{1 + 1/\gy} &\leq z_o^2 \left(\frac{d^2}{1/c +
    \gy} - \frac{\left(d - 1\right)^2}{1/c + 1} \right).
\end{align}
On the right-hand side of~\eqref{eq:RSCond-d} the $Q$-statistic
\begin{align}
  \label{eq:Qstat}
  Q
  = \frac{(\hat{\theta}_o - \hat{\theta}_r)^2}{\sigma^2_o + \sigma^2_r}
  %% = \frac{(z_r - z_o\sqrt{c})^2}{1 + c}
  = \frac{z_o^2(d - 1)^2}{1/c + 1}
\end{align}
appears. The $Q$-statistic was proposed as a measure of incompatibility among
original and replication effect estimates since its distribution is known for
standard meta-analytic models of effect sizes \citep{Hedges2019}. The connection
to the sceptical Bayes factor is such that $Q$ acts as a penalty term
in~\eqref{eq:RSCond-d} and a larger value will lower the degree of replication
success possible. However, as we will see, the sceptical Bayes factor goes
beyond assessing effect estimate compatibility as there is also a trade-off with
the amount of evidence that the replication study provides against the null.

Applying some algebraic manipulations to \eqref{eq:RSCond-d}, one can show that
replication success at level $\gamma$ is achieved if and only if the relative
effect estimate $d$ falls within a success region given by
\begin{align}
  \label{eq:dsuccess}
  \begin{cases}
    d \not\in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy < 1 \\
    d \geq [1 + (1 + 1/c)\{1/2 - \log(2)/z_o^2\}]/2
    & \text{if} ~ \gy = 1 \\
   d \in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy > 1\\
  \end{cases}
\end{align}
where
\begin{align*}
  M &= \frac{1/c + \gy}{\gy - 1} \\
  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\}\Bigm/ z_o^2 +
  \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \\
  B &= \frac{1 - \gy}{(1/c + \gy)(1/c + 1)}.
\end{align*}

The top-left plot in Figure~\ref{fig:dcomparison} shows the conditions on $d$
from~\eqref{eq:dsuccess} to achieve replication success at level $\gamma = 1/3$
as a function of the original minimum Bayes factor $\minBF_{o}$ and for
different values of the relative variance $c$. It is important to note that
$\gamma = 1/3$ is an arbitrary choice and in practice one should interpret the
sceptical Bayes factor as a quantitative measure of replication success. Only
the success regions for positive $d$ are shown as replication success in the
opposite direction is usually not of interest (see
Section~\ref{sec:replicationParadox} for a discussion of this issue). We see
that with increased precision of the replication study (larger $c$), the success
regions shift closer to zero. This means that the method allows for more
shrinkage of the replication effect estimate when the replication provides more
evidence against the null (because $\abs{z_{r}} = d \abs{z_{o}} \sqrt{c}$
increases with increasing $c$). However, the success regions cannot be pushed
arbitrarily close to zero but are bounded away. So when $c \to \infty$ the
methods still requires the replication estimate to be sufficiently large,
despite that the evidence against the null becomes overwhelming (since
$\abs{z_{r}} \to \infty$ as $c \to \infty$).

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/plot-success-region-comparison-1}
\end{knitrout}
\caption{Required relative effect estimate $d = \that_{r}/\that_{o}$ to achieve
  replication success based on the sceptical Bayes factor
  ($\BFs \leq 1/3$), the two-trials rule (2TR:
  $\minBF_{o} \leq 1/3$ and $\minBF_{r} \leq 1/3$),
  the replication Bayes factor ($\BFr \leq 1/3$), and the
  recalibrated sceptical $p$-value
  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$ with
  $\gamma = 1/3$) as a function of the original minimum
  Bayes factor $\minBF_{o}$ (respectively the corresponding $z$-value $z_{o}$)
  for different values of the relative variance
  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. Shading indicates regions where
  replication success is possible. Only positive relative effect estimates $d$
  are shown.}
\label{fig:dcomparison}
\end{figure}

By definition the sceptical Bayes factor can never be smaller than $\minBF_{o}$,
so replication success at level $\gamma$ is impossible for original studies with
$\minBF_{o} > \gamma$. This property is visible in the top-left plot in
Figure~\ref{fig:dcomparison} by the cut-off at $\minBF_{o} = \gamma = 1/3$. In
contrast, for more convincing original studies with $\minBF_{o} < 1/3$
replication success is possible and two cases can be distinguished in terms of
the success region: When $1/4.5 < \minBF_{o} \leq 1/3$ the
sufficiently sceptical relative prior variance is $\gy > 1$ and thus by
condition~\eqref{eq:dsuccess} the success region consists of an interval
$(\dmin, \dmax)$. Hence, in this case the method also penalises too large
replication effect estimates. For original studies with
$\minBF_{o} < 1/4.5$, the sufficiently sceptical relative prior
variance is $\gy \leq 1$, so due to~\eqref{eq:dsuccess} the success region for
positive $d$ is given by $(\dmin, \dmax = \infty)$. This means that for more
convincing original studies there are no upper restrictions for the relative
effect estimate, whereas shrinkage of the replication estimate is still
penalised.

\subsection{Comparison with other methods}
Of interest is the relationship between the sceptical Bayes factor and other
measures of replication success. Here, we review and compare a classical (the
two-trials rule), a forward-Bayes \citep[the replication Bayes factor
from][]{Verhagen2014} and a reverse-Bayes method \citep[the sceptical $p$-value
from][]{Held2020}. These methods provide a useful benchmark as they all are
based on hypothesis testing, have unique properties, and can be directly
compared in terms of their replication success regions as shown in
Figure~\ref{fig:dcomparison}.

\subsubsection{The two-trials rule}
Replication success is most commonly declared when both original and replication
study provide compelling evidence against a null effect. This approach is also
known as the \emph{two-trials rule} in drug development and usually a
requirement for drug approval \citep[Section 9.4]{Kay2015}. Most replication
projects report $p$-values associated with the effect estimates as measures of
evidence against the null, but also default Bayes factors have been used
\citep[see \eg the Bayesian supplement of][]{Camerer2018}. To compare the
two-trials rule with methods based on Bayes factors we will study the two-trials
rule based on the minimum Bayes factor from~\eqref{eq:minBFo}, \ie replication
success at level $\gamma$ is established when both
$\minBF_{k} % = \abs{z_{k}}\exp(-z_{k}^{2}/2)\sqrt{e}
\leq \gamma$ for $k \in \{o, r\}$, as well as
$\sign(\hat{\theta}_o) = \sign(\hat{\theta}_r)$. This approach has a one-to-one
correspondence to the usual version of two-trials rule as minimum Bayes factors
and $p$-values both only depend on the $z$-values of original and replication
study.

The two-trials rule guarantees that both studies provide compelling evidence
against the null. Similarly, the sceptical Bayes factor requires the original
study to be compelling on its own since it can never be smaller than
$\minBF_{o}$. However, one can easily construct examples where the sceptical
Bayes factor is smaller than the minimum Bayes factor from the replication study
(\eg when $\minBF_{o} = 1/2$,
$\minBF_{r} = 1/1.5$, and $c = 1$
we obtain $\BFs = 1/1.9$). So for the same level of
replication success $\gamma$ the two-trials may not flag replication success
whereas the sceptical Bayes factor would.

By definition the two-trials rule can never be fulfilled when the original study
was uncompelling. Assuming now that $\minBF_{o} < \gamma$, replication success
with the two-trials rule at level $\gamma$ is achieved if and only if the
relative effect estimate is
\begin{align}
  \label{eq:2TR}
  d \geq \frac{z_{\gamma}}{z_{o} \sqrt{c}}
\end{align}
with $z_{\gamma} > 1$ corresponding to
$\minBF = z_{\gamma}\exp(-z_{\gamma}^{2}/2)\sqrt{e} = \gamma$. The success
region from~\eqref{eq:2TR} is displayed in the top-right plot of
Figure~\ref{fig:dcomparison}. We see that the success regions shift closer to
zero as the relative variance $c$ increases. Also there is a cut-off at
$\minBF_{o} = \gamma = 1/3$ similarly as with the sceptical Bayes factor. In
contrast to the sceptical Bayes factor, however, the two-trials can be fulfilled
for any arbitrary small (but positive) relative effect estimate $d$, provided
the relative variance $c$ is large enough. Hence, the two-trials rule may flag
success even when the replication effect estimate is much smaller than the
original one.

\subsubsection{The replication Bayes factor}
\citet{Verhagen2014} proposed the \emph{replication Bayes factor} as a measure
of replication success. It is defined as the Bayes factor comparing the point
null hypothesis $H_0 \colon \theta = 0$, to the alternative that the effect is
distributed according to the posterior distribution of $\theta$ after observing
the original data. For the normal model considered so far and if an initial
reference prior was chosen, this alternative is also the advocacy prior
$\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$ and therefore the replication
Bayes factor is given by
\begin{align}
  \label{eq:BFrep}
  \BFr
  = \BFcol{\mathrm{0}}{\mathrm{A}}(\hat{\theta}_r)
  %% = \sqrt{1 + c} \cdot
  %% \exp\left\{-\frac{1}{2} \left(z_r^2 -
  %% \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}.
  = \sqrt{1 + c} \cdot
  \exp\left\{-\frac{z_o^2}{2} \left(d^2 \cdot c -
  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}.
\end{align}

Similarly, as with the sceptical Bayes factor, the $Q$-statistic
from~\eqref{eq:Qstat} appears in~\eqref{eq:BFrep} and acts as a penalty term,
\ie larger values of $Q$ lower the degree of replication success. However, in
contrast to the sceptical Bayes factor, the replication Bayes factor is not
limited by the evidence from the original study because $\BFr \downarrow 0$ as
$c \to \infty$ provided $z_{o} \neq 0$ and $d \neq 0$. Moreover, we have that
\begin{align*}
  1 \geq \BFs \geq \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs})
  = \BFcol{\mathrm{S}}{0}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs}) \cdot \underbrace{\BFcol{0}{\mathrm{A}}(\hat{\theta}_r)}_{= \BFr}.
\end{align*}
So the sceptical Bayes factor is larger than the replication Bayes factor if the
replication data favour the sceptical prior
$\HS \colon \theta \sim \Nor(0, g_{\scriptscriptstyle \BFs} \cdot \sigma^{2}_{o})$
over the null hypothesis. They can only coincide when $\BFs = 1$ since then
$g_{\scriptscriptstyle \BFs} = 0$.

We can also determine conditions on the relative effect estimate in terms of
replication success based on $\BFr \leq \gamma$. The replication success region
is given by
\begin{align}
  \label{eq:BFRsuccess}
  d \not\in [-\sqrt{J} - H, \sqrt{J} - H]
\end{align}
with
\begin{align*}
  J &= \left\{1 + \frac{\log(1 + c) - 2 \log \gamma}{z_o^2}\right\} \cdot
  \frac{1/c + 1}{c} \\
  H &= \frac{1/c + 1}{1 + c}.
\end{align*}
The condition \eqref{eq:BFRsuccess} implies that replication success can also be
achieved for negative relative effect estimates $d$ (see
Section~\ref{sec:replicationParadox} for a discussion of this issue). The
bottom-left plot in Figure~\ref{fig:dcomparison} shows the conditions
from~\eqref{eq:BFRsuccess} for positive relative effect estimates. As with the
two-trials rule, the success region of the replication Bayes factor can be
pushed arbitrarily close to zero by increasing the relative variance $c$. In
contrast to the two-trials rule, however, replication success can also be
achieved for original studies with $\minBF_{o} > 1/3$.

\subsubsection{The sceptical \textit{p}-value}
Of particular interest is the relationship between the sceptical Bayes factor
and the sceptical $p$-value \citep{Held2020}, as it is the outcome of a similar
reverse-Bayes procedure. One also considers a sceptical prior for the effect
size $\theta \sim \Nor(0, \tau^2)$, the sufficiently sceptical prior variance at
level $\alpha$ is then defined as $\tau^2 = \tau^2_\alpha$ such that the
$(1 - \alpha)$ credible interval for $\theta$ based on the posterior
$\theta \given \that_o, \tau^2_\alpha$ does not include zero. Replication
success is declared if the tail probability of the replication effect estimate
under its prior predictive distribution
$\that_r \given \tau^2_\alpha \sim \Nor(0, \tau^2_\alpha + \sigma^2_r)$ is
smaller than $\alpha$. The smallest level $\alpha$ where replication success can
be established defines the sceptical $p$-value. In contrast to the sceptical
Bayes factor, the sceptical $p$-value always exists and there are closed form
expressions to compute it for all values of $c$, \ie
$\ps = 1 - \Phi(z_{\mathrm{S}})$ with
\begin{equation*}
  z^2_{\mathrm{S}} =
  \begin{cases}
    z^2_H/2 & \text{for}~c=1 \\ \frac{1}{c - 1}\left\{\sqrt{z^2_A\left[z^2_A +
          (c - 1)z^2_H\right]} - z^2_A\right\} & \text{for}~c \neq 1
  \end{cases}
  \label{eq:z2s}
\end{equation*}
where $z^2_H = 2/(1/z_o^2 + 1/z_r^2)$ the harmonic mean,
$z^2_A = (z_o^2 + z_r^2)/2$ the arithmetic mean of the squared $z$-statistics,
and provided that $\sign(\that_o) = \sign(\that_r)$ (otherwise
$\ps = \Phi(z_{\mathrm{S}})$).

Similar to the two-trials rule, the sceptical $p$-value requires both studies to
provide compelling evidence due to the property that
$\ps \geq \max\{p_o, p_r\}$. The sceptical $p$-value also penalises the case
when the replication effect estimate shrinks as compared to the original one
since it monotonically increases with decreasing relative effect estimate $d$
\citep[Section 3.1]{Held2020}.

\citet{Held2021} showed that replication success based on
$\ps \leq \alpha_{\mathrm{S}}$ is achieved when
\begin{align}
  \label{eq:psSuccessd}
  d \geq \sqrt{\frac{1/c + 1/(K - 1)}{K}}
\end{align}
with $K = z_{o}^{2}/z_{\alpha_{\mathrm{S}}}^{2}$ where
$z_{\alpha_{\mathrm{S}}} = \Phi^{-1}(1 - \alpha_{\mathrm{S}})$. Thresholding the
sceptical $p$-value with the ordinary significance level $\alpha$ for
traditional $p$-values leads to a very stringent criterion for replication
success. For example, when $z_{o} = 2$, $\alpha = 0.025$, and
$c = 2$, the replication effect estimate needs to be
$d = 4.87$ times larger than the original one. Therefore,
\citet{Held2021} used~\eqref{eq:psSuccessd} to determine the \emph{golden level}
$\alpha_{\mathrm{S}} = 1 - \Phi(z_\alpha/\sqrt{\varphi})$ with
$\varphi = (1 + \sqrt{5})/2$ the golden ratio. The golden level ensures that
borderline significant original studies ($\abs{z_{o}} = z_{\alpha}$) can still
achieve replication success provided the replication effect estimate does not
shrink compared to the original one ($d \geq 1$). Instead of comparing the
sceptical $p$-value to the golden level ($\ps < \alpha_{\mathrm{S}}$), one can
compute a recalibrated sceptical $p$-value
$\tilde{p}_{\mathrm{S}} = 1 - \Phi(z_{\mathrm{S}} \sqrt{\varphi})$ and compare it to
the ordinary significance level ($\tilde{p}_{\mathrm{S}} < \alpha$).

The bottom-right plot in Figure~\ref{fig:dcomparison} shows the success region
for the recalibrated sceptical $p$-value. We see that increasing the precision
of the replication study lowers the required minimum relative effect estimate
$\dmin$ as for all other methods. Similarly, as with the sceptical Bayes factor,
$\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily close to zero.
However, its limiting minimum relative effect estimate in $c$
($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
factor when $\minBF_{o} < 1/5.6$, while for
$\minBF_{o} > 1/5.6$ it is the other way around. So for more
convincing original studies the sceptical $p$-value is less stringent than the
sceptical Bayes factor. Due to the recalibration, the sceptical $p$-value also
allows replication success when the $\minBF_{o} > \gamma$. This is visible in
the bottom-right plot of Figure~\ref{fig:dcomparison} where the success region
has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
the sceptical Bayes factor.

\subsection{Paradoxes in the assessment of replication success}
The replication setting is different from the classical setting where data from
only one study are analysed. As a result, several unique paradoxes may occur.

\subsubsection{The replication paradox}
\label{sec:replicationParadox}
The \emph{replication-paradox} \citep{Ly2018} occurs when original and
replication effect estimates go in opposite directions
($\sign(\that_{o}) \neq \sign(\that_{r})$) but a method flags replication
success. This is undesired since effect direction is crucial to most
scientific theories and research questions.

The two-trials rule and the sceptical $p$-value both avoid the replication
paradox by using one-sided test-statistics. In contrast, the sceptical Bayes
factor and the replication Bayes factor may suffer from the paradox as their
success regions from~\eqref{eq:dsuccess} and~\eqref{eq:BFRsuccess},
respectively, include negative relative effect estimates $d < 0$. This is
related to the fact that Bayes factors are quantifying relative evidence: When
the replication estimate goes in the opposite direction, it will be poorly
predicted by the sceptical prior $\HS$ and the advocacy prior $\HA$, yet when
$\HS$ is mostly concentrated around zero (or a point-null in case of the
replication Bayes factor), replication estimates going in the opposite direction
may still be better predicted by $\HA$.

In practice, the replication paradox is hardly an issue, since replications
rarely show such contradictory results, \eg to achieve replication success at
level $\gamma = 1/3$ with
$\minBF_{o} = 1/10$ and $c = 1$, the
relative effect estimate needs to be $d < -7.09$ for the
paradox to appear with the sceptical Bayes factor. The replication Bayes factor
is more prone to the paradox because its point-null hypothesis fails more
strongly to predict estimates in opposite direction, \eg for the same numbers as
before it requires $d < -2.66$.

In both cases the paradox can be overcome by truncating the advocacy prior $\HA$
such that only effects in the same direction as the original estimate $\that_o$
have non-zero probability, \ie for positive $\that_{o}$ consider
$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \, \mathbb{1}_{(0, \infty)}(\theta)$,
where $\mathbb{1}_{B}(x)$ is the indicator function of the set $B$. The Bayes
factor contrasting $\HS$ to $\HAp$ turns out to be
\begin{align}
  \BFcol{\mathrm{S}}{\mathrm{A}^\prime}(\hat{\theta}_r; g)
  &= \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
  \frac{\Phi(\abs{z_o})}{\Phi\left\{\mathrm{sign}(z_o)
    %     \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}} \right\}}
    \frac{z_o(1 + dc)}{\sqrt{1 + c}} \right\}}
   \label{eq:BFrtrunc}
\end{align}
where $\Phi(\cdot)$ is the cumulative distribution function of the standard
normal distribution (see Appendix \ref{app:BFtrunc}). Hence, \eqref{eq:BFrtrunc}
is the Bayes factor under the standard advocacy prior multiplied by a correction
term. Determining the smallest level of replication success
with~\eqref{eq:BFrtrunc} leads to a corrected sceptical Bayes factor, while
setting $g = 0$ in~\eqref{eq:BFrtrunc} leads to a corrected replication Bayes
factor. The correction term goes to one when the replication estimate goes in
the same direction as the original one and the replication sample size increases
($d > 0$ and $c \to \infty$), but it penalises when the replication estimate
goes in the opposite direction ($d < 0$ and $c \to \infty$).

This modification guarantees that the replication paradox is avoided and we
recommend to compute the sceptical Bayes factor using~\eqref{eq:BFrtrunc} in
cases where the replication paradox is likely to appear. However, truncated
priors are unnatural and hard to interpret. Also the non-truncated advocacy
prior penalises effect estimate incompatibility and the
modification~\eqref{eq:BFrtrunc} will only make a difference in extreme
situations. Due to its easier mathematical treatment we will focus on the
standard version of the procedure in the remaining part of the paper.

\subsubsection{The shrinkage paradox}
The comparison showed that for certain methods replication success is still
achievable even when the replication estimate is substantially smaller than the
original one. However, a substantially smaller effect estimate in the
replication does not reflect an effect size of the same practical importance as
the original one and a method should thus not flag replication success. The {\em
shrinkage paradox} occurs if a particular method may flag replication success
for any arbitrarily small (but positive) relative effect estimate.

Two forms of the shrinkage paradox can formally be distinguished: the
\emph{shrinkage paradox at replication} appears when, for fixed evidence from
the original study $\minBF_{o}$ (respectively $z_{o}$), the minimum relative
effect estimate $\dmin > 0$ required for replication success at a fixed level
$\gamma$ becomes arbitrarily small as the relative variance $c$ increases:
\begin{align*}
  \dmin \downarrow 0 ~\text{as}~ c \to \infty.
\end{align*}
\citet{Held2021} found that this form of the paradox occurs for the two-trials
rule but not for the sceptical $p$-value. Similarly, the minimum relative effect
estimate $\dmin$ of the sceptical Bayes factor is bounded away from zero, while
it converges to zero for the replication Bayes factor
(Appendix~\ref{app:shrinkage}). Hence, among the Bayes factor methods, the
sceptical Bayes factor avoids the paradox, whereas the replication Bayes factor
suffers from it.

The shrinkage paradox at replication is a serious issue since it depends on the
relative variance $c$ which can usually be directly influenced by changing the
replication sample size. However, there is also a second form of the paradox
which is affected only by evidence from the original study. The \emph{shrinkage
paradox at original} appears when, for fixed relative variance $c$, the minimum
relative effect estimate $\dmin > 0$ required for replication success at a fixed
level $\gamma$ becomes arbitrarily small as the evidence in the original study
increases:
\begin{align*}
  \dmin \downarrow 0 ~\text{as}~ z_{o}^{2} \to \infty.
\end{align*}

The replication Bayes factor and the sceptical Bayes factor do not suffer from
this form of the paradox, while the two-trials rule and the sceptical $p$-value
do (Appendix~\ref{app:shrinkage}). Hence, with the latter two methods, shrinkage
of the replication effect estimate is hardly penalised when the original study
was already very convincing.

\subsection{Frequentist properties}
Despite the fact that Bayesian methods do not rely on repeated testing, it is
still often of interest to study their frequentist operating characteristics
\citep{Dawid1982, Grieve2016}. This is especially important in the replication
setting where regulators and funders usually require from statistical methods to
have appropriate error control. We will therefore study and compare type I error
rate as well as power of the sceptical Bayes factor and other methods.

\subsubsection{Global type I error rate}
The probability for replication success at level $\gamma$ conditional on the
original result $z_{o}$ and the relative variance $c$ can be easily computed as
shown in Appendix~\ref{app:powerBFs}. Under the null hypothesis
($H_{0}: \theta = 0$) the distribution of the $z$-values is
$z_{o}, z_{r} \given H_{0} \sim \Nor(0, 1)$ and hence the global type I error
rate (T1E) based on $\BFs \leq \gamma$ is
\begin{align*}
  \text{T1E} = 2 \int_{z_{\gamma}}^{\infty} \P(\BFs \leq \gamma \given z_{o}, c) \phi(z_{o}) \,
  \text{d}z_{o}
\end{align*}
with $\phi(\cdot)$ the standard normal density function. In a similar fashion
one can compute the type I error rate of the sceptical $p$-value \citep[see
Section 3 in][]{Held2021}, as well as the replication Bayes factor
(Appendix~\ref{app:powerBFr}). The type I error rate of the two trials rule is
simply $\text{T1E} = 2\{1 - \Phi(z_{\gamma})\}^{2}$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/T1E-comparison-1}
\end{knitrout}
\caption{Type I error rate of the two-trials rule (2TR: $\minBF_{o} \leq \gamma$
  and $\minBF_{r} \leq \gamma$), the replication Bayes factor
  ($\BFr \leq \gamma$), the sceptical Bayes factor ($\BFs \leq \gamma$), and the
  recalibrated sceptical $p$-value
  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$) as a function of the
  relative variance $c = \sigma^{2}_{o}/\sigma^{2}_{r}$ for different levels of
  replication success $\gamma$.}
\label{fig:t1ec}
\end{figure}

Figure~\ref{fig:t1ec} compares the type I error rates of the four methods for
different levels $\gamma$. The conventional nominal
$\text{T1E} = 0.05 \times 0.025$ (two independent experiments with two-sided
testing in the first and one-sided testing in the second) along with the
corresponding level ($z_{\gamma} = 1.96$ corresponding to $\gamma = 1/2.1$ and
$\alpha = 0.025$) is also indicated. In contrast to the other methods, the type
I error rate of the two trials rule does not depend on the relative variance $c$
and therefore does not change for the same level $\gamma$. Type I error rates of
sceptical $p$-value and sceptical Bayes factor are decreasing with increasing
$c$, the former usually being slightly smaller than the latter. The point at
which both become smaller than the type I error rate from the two-trials rule
becomes smaller with more stringent level $\gamma$. Roughly speaking the type I
error rate of the sceptical Bayes factor is controlled at the conventional level
when $c$ is slightly larger than one, while for the sceptical $p$-value it is
controlled when $c$ is slightly below one. Surprisingly, the type I error rate
of the replication Bayes factor is non-monotone in $c$ and far higher compared
to the other methods. This suggests that a more stringent level $\gamma$ should
be used for the replication Bayes factor compared to the other methods to ensure
appropriate type I error control.

\subsubsection{Power conditional on the original study}
Another frequentist operating characteristic is the probability to establish
replication success assuming there is an underlying effect (power). While in
principle original and replication study could be powered simultaneously, we
will assume the original study has already been conducted since this is the
usual situation. The power to establish replication success $\BFs \leq \gamma$
can be computed using the result from Appendix~\ref{app:powerBFs} and either
assuming that the underlying true effect corresponds to its estimate from the
original study (\emph{conditional power}) or using the predictive distribution
of the replication effect estimate based on the advocacy prior (\emph{predictive
  power}) \citep{Spiegelhalter1986b, Micheloud2020}. In practice, both forms may
be too optimistic as original results are often inflated due to publication bias
and questionable research practices. One solution is to shrink the original
effect estimate for power calculations \citep{Pawel2020, Held2021}, but we will
not focus on this aspect here as this would not provide much more insight but
simply lower the power curves of all methods.

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/power-plots-1}
\end{knitrout}
\caption{Power of the two-trials rule (2TR: $\minBF_{o} \leq
1/3$ and $\minBF_{r} \leq
1/3$), the replication Bayes factor ($\BFr
\leq 1/3$), the sceptical Bayes factor ($\BFs
\leq
1/3$), and the recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}
\leq 1 - \Phi\{z_{\gamma}\}$ with $\gamma =
1/3$) as a function of the relative variance $c
= \sigma^2_o/\sigma^2_r$ for different original $z$-values $z_o =
\that_o/\sigma_o$ (respectively corresponding minimum Bayes factor $\minBF_o$).}
\label{fig:condpower}
\end{figure}

Figure~\ref{fig:condpower} shows conditional and predictive power as a function
of the relative variance $c$ and for several values of of the original $z$-value
$z_o$ (respectively original minimum Bayes factor $\minBF_{o}$). In general,
uncertainty about replication success is higher for predictive power, leading it
to be closer to 50\% in all cases. As can also be seen, if the original result
was not convincing on its own (\eg if $z_o = 1.5$ or $z_{o} = 2$), it is
impossible to achieve replication success with the two-trials rule, the
sceptical Bayes factor, and the sceptical $p$-value. This is not the case for
the replication Bayes factor, for which high power can also be obtained for
small $z_o$ if $c$ is sufficiently large. However, as shown in the previous
section, the higher power of the replication Bayes factor comes at the cost of a
massive type I error inflation. For $z_o = 2.5$, the sceptical Bayes factor
shows higher power than the two-trials rule when $c = 1$, but the power of the
two-trials rule increases faster in $c$ and approaches the power curve of the
replication Bayes factor. The power of the sceptical $p$-value is still a bit
lower, likely due to the more stringent requirement on the minimum relative
effect estimate. For $z_{o} = 3$, the power differences between the methods
mostly disappear.

\subsection{Information consistency}
\label{sec:informationcons}
Bayesian hypothesis testing procedures are desired to fulfil certain asymptotic
properties \citep{Bayarri2012}. Most notably, they should be \emph{information
consistent} in the sense that if data provide overwhelming support for a
particular hypothesis, the procedure should indefinitely favour this hypotheses
over alternative hypotheses.

There are concerns whether the sceptical Bayes factor is information consistent
when we look at the asymptotics only in terms of the replication data
\citep{Consonni2021, Ly2021}. The sceptical Bayes factor can never be smaller
than the original minimum Bayes factor $\minBF_{o}$. This means that it will be
bounded away from zero as the replication sample size grows ($c \to \infty$),
even when the data are generated from the same model in both studies. Similarly,
the sceptical Bayes factor will be bounded away from zero when the replication
effect estimate increases indefinitely. If these two cases constitute
overwhelming evidence for replication success, they could be considered
instances of the \emph{information paradox} \citep{Liang2008}
% Similarly, with increasing replication effect estimate
% ($\that_{r} \to \infty$ implying that also the relative effect estimate
% $d \to \infty$ when $\that > 0$), replication success can at most be established for a
% sufficiently sceptical relative prior variance $\gy \leq 1$ due to the
% success conditions~\eqref{eq:dsuccess}. This implies that the sceptical Bayes factor
% $\BFs \to \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g = 1)$, provided $\abs{z_o} \geq
% \sqrt{2}$ so that $g_{\minBF_{o}} \geq 1$. Hence, the sceptical Bayes factor is
% also bounded away from zero and this could be considered an
% instance of the \emph{information paradox} \citep{Liang2008}.

The key to resolving the paradox is to realise that overwhelming evidence for
replication success needs to be defined through both studies, not only through
the replication. Assume there is a ``true'' effect size $\theta_{*} \neq 0$
underlying both effect estimates
$\that_{i} \sim \Nor(\theta_{*}, \sigma_{i}^{2})$, $i \in \{o, r\}$. Also assume
the variances $\sigma_{i}^{2} = \kappa/n$ are inversely proportional to the
sample size $n = n_{o} = n_{r}$ for the same unit variance $\kappa$ in both
studies. Letting the sample size $n$ go to infinity is then equivalent to
$\sigma_{o}^{2} \downarrow 0$ and $c = \sigma^{2}_{r}/\sigma^{2}_{o} = 1$. With
decreasing variances the estimates will
converge to the true effect size ($\that_{i} \to \theta_{*}$), the relative
effect estimate will converge to one ($d \to 1$), and the $z$-values will go to
infinity ($\abs{z_{i}} \to \infty$). Since $c = 1$, the sceptical Bayes factor
is given by equation~\eqref{eq:BFsc1}. Moreover, we are allowed to use of the
approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ as the argument of
the Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
350]{Corless1996}. Taken together, we have
\begin{align}
  \label{eq:BFsc1lim2}
  \BFs =
  \sqrt{\frac{1 + d^{2}}{1 + (1 - d)^{2}/2 -
\mathcal{O}\left\{\log(z_{o}^{2})/z_{o}^{2}\right\}}} \cdot
  \exp\left\{-\frac{z_o^2\left(d^{2} + 2d - 1 \right)}{4(1 + d^{2})}
- \mathcal{O}\left(\log z_{o}^{2}\right)\right\}
\end{align}
Plugging $d = 1$ into~\eqref{eq:BFsc1lim2}, we see that $\BFs \downarrow 0$ as
$\abs{z_{o}} \to \infty$, so the sceptical Bayes factor is information
consistent.

The expression for the sceptical Bayes factor~\eqref{eq:BFsc1lim2} is also valid
for other relative effect sizes $d$. Solving for $d$ such that the
multiplicative term of $z_{o}^{2}$ in the exponent changes the sign, we see that
the sceptical Bayes factor goes to zero when the underlying true effect size of
the replication study is at least
$d > \sqrt{2} - 1 \approx 0.41$ times the size of the
true effect size from the original study (or
$d < -\sqrt{2} - 1 \approx -2.41$ due to the
replication paradox if the advocacy prior is not truncated). This means that
under the more realistic scenario where the underlying effect sizes from
original and replication are not exactly the same, the sceptical Bayes factor is
still consistent when there is not more than 60\% shrinkage of the replication
effect size.

\section{Extension to non-normal models} \label{sec:tdist}
So far, we have always assumed approximate normality of the effect estimates
$\that_o$ and $\that_r$, as well as known variances $\sigma^2_o$ and
$\sigma^2_r$. This may be a problem for studies with small sample size and/or
extreme results (\eg when a study examines a rare disease with death rates close
to 0\%). One way of dealing with this issue is to consider the exact likelihood
of the data underlying the effect estimates, and then marginalise over possible
nuisance parameters \citep[Chapter 8.2.2]{Spiegelhalter2004}. This leads to
marginal likelihoods which are again only conditional on the effect size
$\theta$, allowing the procedures to be used analogously as described in the
proceeding sections. The choice of the likelihood depends on the type of effect
size $\theta$. We will illustrate the approach for \emph{standardised mean
differences} (SMD) and \emph{log odds ratios} (logOR), two of the most widely
used types of effect sizes.

\subsection{Standardised mean difference}
The SMD quantifies how many standard deviation units $\sigma$, the means $\mu_1$
and $\mu_2$ of measurements from two groups differ, \ie
$$\theta = \frac{\mu_1 - \mu_2}{\sigma}.$$
Assume now that the measurements come from a normal distribution with common
variance $\sigma^2$. Knowing the test-statistic $t_i$ from the usual two-sample
$t$-test, as well as the sample sizes in both groups $n_{1i}$ and $n_{2i}$ from
study $i \in \{o, r\}$ is sufficient to compute the exact likelihood of the
data. It is given by a non-central $t$-distribution with degrees of freedom
$\nu_i = n_{1i} + n_{2i} - 2$ and non-centrality parameter $\theta \sqrt{n^*_i}$
with $n^*_i = (n_{1i}n_{2i})/(n_{1i} + n_{2i})$ \citep{Bayarri2002}
\begin{align}
  \label{eq:nct}
  T_i \given \theta \sim \text{NCT}_{\nu_i} \left(\theta \sqrt{n^*_i}\right).
\end{align}
The same framework is also applicable to test-statistics $t_{i}$ from paired
$t$-tests based on $n_{i}$ paired measurements. The SMD $\theta$ represents then
the standardised mean difference score and $\nu_{i} = n_{i} - 1$ and
$n_{i}^{*} = n_{i}$ need to be used in~\eqref{eq:nct}.

There is no conjugate prior for the SMD $\theta$ under model~\eqref{eq:nct}, so
it is not obvious which prior should be chosen to represent scepticism about it.
We will use a zero-mean normal prior $\theta \given \HS \sim \Nor(0, \tau^{2})$
so that the exact procedure is equivalent with the normal approximation as the
sample size increases. For the advocacy prior we need to know the posterior
distribution of the SMD $\theta$ conditional on the original study and a flat
prior on $\theta$. Exploiting the fact that the non-central $t$-distribution can
be expressed as a location-scale mixture of a normal with an inverse-gamma
distribution
%% \ie $\text{NCT}_\nu(t; \theta \sqrt{n^*}) = \int
%% \Nor(t; \theta \sqrt{n^*\tau^2}, \tau^2) \text{IG}(\tau^2; \nu/2, \nu/2) d\tau^2$
\citep[Chapter 31]{Johnson1995}, the density of the SMD under the advocacy prior
is given by
\begin{align*}
  f(\theta \given t_o)
  = \int_0^\infty \Nor\left(\theta; \frac{t_o}{\sqrt{n_o^* \tau^2}},
  \frac{1}{n_o^*}\right)  \text{IG}\left(\tau^2; \frac{\nu_o + 1}{2},
  \frac{\nu_o}{2}\right) \, \text{d}\tau^2,
\end{align*}
where $\Nor(x; \mu, \phi)$ denotes the density function of the normal
distribution with mean $\mu$ and variance $\phi$ evaluated at $x$, and similarly
$\text{IG}(y; a, b)$ denotes the density function of the inverse-gamma
distribution with shape and rate parameters $a$ and $b$ evaluated at $y$.

Taken together, the SMD version of the method proceeds analogously as in
Box~\hyperref[box:nutshell]{1} with the two Bayes factors replaced by
\begin{align*}
  \BFcol{0}{\mathrm{S}}(t_{o};\tau^{2})
  &= \frac{\text{NCT}_{\nu_{o}}(t_{o}; 0)}{\int
  \text{NCT}_{\nu_{o}}(t_{o}; \theta \sqrt{n_{o}^{*}})
  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
  \BFcol{\text{S}}{\text{A}}(t_{r};\tau^{2})
  &= \frac{\int\text{NCT}_{\nu_{r}}(t_{r};\theta
  \sqrt{n_{r}^{*}})\Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
  \int\text{NCT}_{\nu_{r}}(t_{r};\theta
  \sqrt{n_{r}^{*}}) f(\theta \given t_{o}) \, \text{d} \theta}
\end{align*}
and using numerical integration as the integrals cannot be evaluated
analytically.

\subsection{Log odds ratio}
In the case of binary data, we have two independent binomial samples
\begin{align*}
  &X_{1i} \given \pi_1 \sim \Bin(n_{1i}, \pi_1)&
  &X_{2i} \given \pi_2 \sim \Bin(n_{2i}, \pi_2)&
\end{align*}
for each study $i \in \{o, r\}$, and the effect of the treatment in group 1
relative to the treatment in group 2 is quantified with the logOR
$$\theta = \log \frac{\pi_1/(1 - \pi_1)}{\pi_2/(1 - \pi_2)}.$$
To obtain a marginal likelihood that only depends on $\theta$, we need to
specify a prior for either $\pi_2$ or $\pi_1$ and marginalise over it. A
principled choice is the translation invariant Jeffreys prior,
$\pi_1, \pi_2 \sim \Be(1/2, 1/2)$. The exact marginal likelihood for the data
from study $i$ is then given by
\begin{align}
  \label{eq:binexact}
  f(x_{1i}, x_{2i} \given \theta)
  &= \int_0^1 \Bin\left(x_{1i}; n_{1i}, \left\{1 + \exp\left[-\theta - \log
    \frac{\pi_2}{1 - \pi_2}\right]\right\}^{-1}\right) \Bin(x_{2i}; n_{2i}, \pi_2)
  \nonumber
  \\ &\phantom{= \int_0^1}  \times \Be(\pi_2; 1/2, 1/2) \, \text{d} \pi_2
\end{align}
where $\Bin(x; n, \pi)$ denotes the probability mass function of the binomial
distribution with $n$ trials and probability $\pi$ evaluated at $x$, and
likewise $\Be(y; a, b)$ denotes the density function of the beta distribution
with parameters $a$ and $b$ evaluated at $y$.

There is no conjugate prior for the logOR under model~\eqref{eq:binexact}, but a
pragmatic choice is to specify a zero-mean normal prior
$\theta \given \HS \sim \Nor(0, \tau^{2})$ for the sceptic, to match with the
normal approximation as the sample size increases. For the advocacy prior, we
need to know the posterior distribution of the logOR $\theta$ based on the
original study.
Using a result from \citet{Marshall1988} combined with a change-of-variables,
the exact posterior density of the logOR $\theta$ given the original data and
Jeffreys priors on $\pi_1$ and $\pi_2$ is
\begin{align*}
  f(\theta \given x_{1o}, x_{2o}) &=
  \begin{cases}
    % C \, \exp\{(x_{1o} + 1/2) \theta\} \,
    % F(n_{1o} + 1, x_{1o} + x_{2o} + 1, n_{1o} + n_{2o} + 2, 1 - \exp(\theta))
    % & \text{for} ~ \theta < 0 \\
    % C \, \exp\{-(n_{1o} - x_{1o} + 1/2) \theta\} \,
    % F(n_{1o} + 1, n_{10} - x_{1o} + n_{2o} - x_{2o} + 1, n_{1o} + n_{2o} + 2,
    % 1 - \exp(-\theta)) & \text{for} ~ \theta > 0 \\
    C \, \exp\{e \theta\} \,
    F\left(e + f, e + g, e + f + g + h, 1 - \exp\{\theta\}\right)
    & \text{for} ~ \theta < 0 \\
    C \, \exp\{-f \theta\} \,
    F\left(e + f, f + h, e + f + g + h, 1 - \exp\{-\theta\}\right)
    & \text{for} ~ \theta > 0 \\
  \end{cases}
\end{align*}
where $F(\cdot)$ is the hypergeometric function, $e = x_{1o} + 1/2$,
$f = n_{1o} - x_{1o} + 1/2$, $g = x_{2o} + 1/2$, $h = n_{2o} - x_{2o} + 1/2$,
$C = \text{B}(e + g, f + h)/\{\text{B}(e, f) \text{B}(g, h)\}$, and
$\text{B}(\cdot, \cdot)$ is the Beta function.

Combining the previous results, we obtain
\begin{align*}
  \BFcol{0}{\text{S}}(x_{1o}, x_{2o};\tau^{2})
  &= \frac{ f(x_{1o}, x_{2o} \given 0)}{\int
   f(x_{1o}, x_{2o} \given \theta)
  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
  \BFcol{\text{S}}{\text{A}}(x_{1r}, x_{2r};\tau^{2})
  &= \frac{\int f(x_{1r}, x_{2r} \given \theta)
    \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
    \int f(x_{1r}, x_{2r} \given \theta)
    f(\theta \given x_{1o}, x_{2o}) \, \text{d} \theta}
\end{align*}
as an exact replacement for the Bayes factors in Box~\hyperref[box:nutshell]{1}.
Again, there are no closed form expressions for the integrals, but numerical
integration needs to be used.

\section{Application}
\label{sec:applications}
The following section will illustrate application of the sceptical Bayes factor
using data from the \emph{Social Sciences Replication Project}
\citep{Camerer2018}, provided in Table \ref{tab:ssrp}. Effect estimates were
reported on the correlation scale ($r$), which is why we applied the Fisher
$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$. This leads to the
transformed estimates having approximate variance
$\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}, so the relative variance
$c$ is roughly the ratio of the replication to the original study sample size
$c \approx n_{r}/n_{o}$.

For all studies except \citet{Janssen2010} and \citet{Derex2013}, the exact
approach for either SMD or logOR effect sizes from Section~\ref{sec:tdist} is
applicable. In the studies with binary data
% \citep{Balafoutas2012, Gneezy2014, Hauser2014},
computing the exact posterior using the hypergeometric function led to numerical
issues in some cases and numerical integration was used then.
% Balafoutas and Sutter - integration and hypergeo work
% Gneezy et al. - only integration works
% Hauser et al. - only hypergeo works
In most cases, the normal approximation of the likelihood seems to lead to
similar numerical results for both $\BFs$ and $\BFr$ as compared to their
counterparts based on exact likelihoods. Qualitative conclusions are the same
under both approaches and we will therefore focus on the normal approximation
due to better comparability with the remaining measures of replication success
as all of them were computed based on approximate normal likelihoods.

For the study pairs where the sceptical Bayes factor suggests a large degree of
replication success, all other methods suggest the same in every case. However,
there are also cases where there appear to be discrepancies among the methods.
For instance, the two-trials rule and the replication Bayes factor may indicate
a larger degree of replication success compared to the sceptical $p$-value and
sceptical Bayes factor. This happens for replications that show a substantial
increase in sample size but also a much smaller effect estimate compared to the
original study. For example, in \citet{Balafoutas2012} the sample size was about
$c = 3.48$ times larger in the replication, whereas the effect estimate was only
$d = 0.52$ the size of the original one. The replication is successful at
$\gamma = 1/3$ with the two-trials rule ($\minBF_{o} = 1/4.2$ and
$\minBF_{r} = 1/3.6$) and the replication Bayes factor ($\BFr = 1/3.9$), but not
with the sceptical Bayes factor ($\BFr = 1/1.6$) or the sceptical $p$-value
($\tilde{p}_{\mathrm{S}} = 0.04 > 1 - \Phi(z_\gamma = 2.18) = 0.01$).

\begin{landscape}
\begin{table}[!htb]
\centering
\caption{Results for data from \emph{Social Sciences Replication Project}
  \citep{Camerer2018}. Shown are relative variances
  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimates
  $d = \that_{r}/\that_{o}$ (computed on Fisher $z$-scale), $Q$-statistic
  $Q = (\that_{o} - \that_{r})^{2}/(\sigma^{2}_{o} + \sigma^{2}_{r})$, minimum
  Bayes factors of original and replication effect estimate ($\minBF$),
  recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}$), sceptical Bayes
  factors ($\BFs$) and replication Bayes factors ($\BFr$), the latter two
  computed using either a normal approximation or the exact likelihood of the
  data. }
% \resizebox{1\textwidth}{!}{%

% latex table generated in R 4.2.2 by xtable 1.8-4 package
% Thu Nov 24 10:46:19 2022
{\small
\begin{tabular}{lrrrlllllll}
  \toprule
Original study & $c$ & $d$ & $Q$ & $\minBF_o$ & $\minBF_r$ & $\tilde{p}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ (exact) & $\mathrm{BF}_{\mathrm{R}}$ & $\mathrm{BF}_{\mathrm{R}}$ (exact) \\
  \midrule
Hauser et al. (2014) & 0.51 & 1.04 & 0.03 & < 1/1000 & < 1/1000 & < 0.0001 & < 1/1000 & < 1/1000 & < 1/1000 & < 1/1000 \\
  Aviezer et al. (2012) & 0.92 & 0.60 & 3.49 & < 1/1000 & 1/347 & < 0.0001 & 1/78 & 1/10 & 1/284 & 1/41 \\
  Wilson et al. (2014) & 1.33 & 0.83 & 0.28 & < 1/1000 & 1/659 & 0.0001 & 1/45 & 1/35 & < 1/1000 & < 1/1000 \\
  Derex et al. (2013) & 1.29 & 0.65 & 1.14 & 1/520 & 1/17 & 0.002 & 1/8.5 &  & 1/31 &  \\
  Gneezy et al. (2014) & 2.31 & 0.81 & 0.22 & 1/18 & 1/157 & 0.004 & 1/6.9 & 1/7.5 & 1/474 & 1/551 \\
  Karpicke and Blunt (2011) & 1.24 & 0.58 & 1.75 & < 1/1000 & 1/9.6 & 0.002 & 1/5.6 & 1/5 & 1/12 & 1/12 \\
  Morewedge et al. (2010) & 2.97 & 0.76 & 0.30 & 1/7.3 & 1/65 & 0.011 & 1/3.9 & 1/4 & 1/160 & 1/156 \\
  Kovacs et al. (2010) & 4.38 & 1.38 & 0.59 & 1/3.2 & < 1/1000 & 0.009 & 1/3.2 & 1/3.8 & < 1/1000 & < 1/1000 \\
  Duncan et al. (2012) & 7.42 & 0.57 & 1.29 & 1/12 & < 1/1000 & 0.011 & 1/3.1 & 1/3.1 & < 1/1000 & < 1/1000 \\
  Nishi et al. (2015) & 2.42 & 0.57 & 1.05 & 1/12 & 1/6.1 & 0.016 & 1/2.5 & 1/2.2 & 1/8.2 & 1/7.6 \\
  Janssen et al. (2010) & 0.65 & 0.48 & 3.51 & < 1/1000 & 1/3.3 & 0.003 & 1/1.6 &  & 1/1.6 &  \\
  Balafoutas and Sutter (2012) & 3.48 & 0.52 & 1.02 & 1/4.2 & 1/3.6 & 0.04 & 1/1.6 & 1/1.6 & 1/3.9 & 1/3.9 \\
  Pyc and Rawson (2010) & 9.18 & 0.38 & 1.79 & 1/3.5 & 1/7.3 & 0.061 & 1/1.2 & 1/1.2 & 1/4 & 1/4 \\
  Rand et al. (2012) & 6.27 & 0.18 & 3.96 & 1/7.1 & 1 & 0.13 &  &  & 9.6 & 9.7 \\
  Ackerman et al. (2010) & 11.69 & 0.23 & 2.15 & 1/2.2 & 1/1.3 & 0.15 &  &  & 3.2 & 3.2 \\
  Sparrow et al. (2011) & 3.50 & 0.13 & 5.80 & 1/26 & 1 & 0.19 &  &  & 29 & 32 \\
  Shah et al. (2012) & 11.62 & -0.05 & 4.08 & 1/2.2 & 1 & 0.66 &  &  & 25 & 26 \\
  Kidd and Castano (2013) & 8.57 & -0.10 & 6.83 & 1/5.7 & 1 & 0.77 &  &  & 72 & 69 \\
  Gervais and Norenzayan (2012) & 9.78 & -0.12 & 5.44 & 1/3 & 1 & 0.78 &  &  & 36 & 37 \\
  Lee and Schwarz (2010) & 7.65 & -0.11 & 6.80 & 1/5.4 & 1 & 0.79 &  &  & 65 & 69 \\
  Ramirez and Beilock (2011) & 4.47 & -0.09 & 19.29 & < 1/1000 & 1 & 0.85 &  &  & > 1000 & > 1000 \\
   \bottomrule
\end{tabular}
}
% %
% }
\label{tab:ssrp}
\end{table}

\end{landscape}

% % EJ Wagenmakers' analysis
% % - Ackerman et al. (2010): BFR 3.23  -- our BFR 3.2
% % -* Aviezer et al. (2012): BFR 1/57 -- our BFR 1/284
% % - Balafoutas and Sutter (2012): 1/4.27 -- our BFR 1/3.9
% % -** Derex et al. (2013): 1/3'701 -- our BFR 1/31
% % - Duncan et al. (2012): 1/2513 -- our BFR 1/3079.4
% % - Gervais & Norenzayan (2012): 36.5 -- our BFR 36
% % - Gneezy et al. (2014): 1/485.27 -- our BFR 1/474
% % -* Hauser et al. (2014): 1/10'211 -- our BFR 1/620'059
% % -** Janssen et al. (2010): 2'134'835 -- our BFR 1/1.6
% % - Karpicke & Blunt (2011): 1/11.82 -- our BFR 12
% % - Kidd & Castano (2013): 71.43 -- our BFR 72
% % - Kovacs et al. (2010): 1/132'389'305 -- our BFR 1/333'616'129
% % - Lee & Schwarz (2010): 68 -- our BFR 65
% % - Morewedge et al. (2010): 1/158 -- our BFR 1/160
% % - Nishi et al. (2015): 1/7.77 -- our BFR 1/8.2
% % - Pyc and Rawson (2010): 1/4.04 -- our BFR 1/4
% % -* Ramirez & Beilock (2011): 12'240 -- our BFR 24'996
% % - Rand et al. (2012): 9.71 -- our BFR 9.6
% % - Shah et al. (2012): 26.05 -- our BFR 25
% % - Sparrow et al. (2011): 31.65 -- our BFR 29
% % -* Wilson et al. (2014): 1/1871 -- our BFR 1/2533

%% ps does but BFs doesn't flag RS
Discrepancies between the sceptical $p$-value and the sceptical Bayes factor
happen in situations where the replication shows an effect estimate that,
although incompatible with the sceptical prior, is also incompatible with the
advocacy prior. For example in the \citet{Janssen2010} replication, both effect
estimates are substantially larger than zero ($\that_o = 0.74$ with
$\minBF_{o} < 1/1000$ and $\that_r = 0.36$ with $\minBF_{r} = 1/3.3$), yet the
$Q$-statistic indicates some incompatibility ($Q = 3.51$), which explains why
$\tilde{p}_{\mathrm{S}} = 0.003$, but $\BFs = 1/1.6$ only.

Discrepancies between the replication Bayes factor and the sceptical Bayes
factor arise when the replication finding provides overwhelming evidence against
the null, whereas the original finding was less compelling. The replication of
\citet{Kovacs2010} illustrates this situation. The original study provided only
moderate evidence against the null ($\that_o = 0.49$ and $\minBF_o = 1/3.2$),
whereas the replication finding was more compelling ($\that_r = 0.67$ and
$\minBF_r < 1/1000$). By construction the sceptical Bayes factor can only be as
small as the minimum Bayes factor from the original study $\minBF_o$, which is
actually attained in this case ($\BFs = 1/3.2$). The replication Bayes factor,
on the other hand, is not limited by the moderate level of evidence from the
original study and indicates decisive evidence for the advocate
($\BFr < 1/1000$). This illustrates that in order to achieve a reasonable degree
of replication success, the sceptical Bayes factor requires the original study
to be convincing, whereas the replication Bayes factor only requires a
compelling replication result.

\section{Discussion}
\label{sec:discussion}
We proposed a novel method for the statistical assessment of replicability
combining reverse-Bayes analysis with Bayesian hypothesis testing. Compared to
other methods, the sceptical Bayes factor poses more stringent requirements but
also allows for stronger statements about replication success. It ensures that
both studies provide sufficient evidence against a null effect, while also
penalising incompatibility of their effect estimates. If the replication sample
size is not too small, the sceptical Bayes factor comes with appropriate
frequentist error rates, which is often a requirement from research funders and
regulators. Asymptotic analysis of the method showed that it is information
consistent in the sense that if the sample size in both studies increases, the
sceptical Bayes factor will indicate overwhelming replication success when the
underlying effect size of the replication is not much smaller than the
underlying effect size of the original study. Finally, the sceptical Bayes
factor is the only method in our comparison which does not suffer from any form
of the shrinkage paradox, \ie replication success can never be achieved with
arbitrarily small replication effect estimates, not even when the replication
sample size becomes very large or the evidence from the original study
overwhelming.

In extreme scenarios the sceptical Bayes factor can suffer from the replication
paradox, which means that it may flag success when the replication estimate goes
in opposite direction of the original one. However, the paradox can be avoided
by truncating the advocacy prior to the direction of the original estimate. It
may also happen that the result of the replication is so inconclusive that
replication success cannot be established at any level, so the sceptical Bayes
factor does not exist. Other methods, such as the sceptical $p$-value or the
replication Bayes factor, can be used in this situation.

%% extensions and limitations
The proposed method could be extended in many ways. First, in many cases not
just one but several replication studies are conducted for one original study
\citep[\eg as in][]{Klein2014}. The Bayesian framework allows to easily extend
the sceptical Bayes factor to the ``many-to-one'' replication setting as the
likelihoods are also straightforward to compute for a sample of replication
effect estimates. Second, a multivariate generalisation would allow for effects
in the form of a vector with approximate multivariate normal likelihood which is
then combined with a sceptical $g$-prior \citep{Liang2008}. The normal prior
could also be replaced with other distributions, for example the (multivariate)
Cauchy distribution which is often the preferred prior choice for default Bayes
factor hypothesis tests \citep{Jeffreys1961}. The $g$ parameter of the $g$-prior
or the scale parameter of the Cauchy prior would then take over the role of the
relative sceptical prior variance. Third, based on the replication result one
could also compute a posterior distribution for the effect size based on a
model-average of the advocacy prior and the sceptical prior (using the variance
at the sceptical Bayes factor). This distribution would provide a formal
compromise between scepticism and advocacy of the original finding. Fourth,
while Bayes factors are an important part in Bayesian hypothesis testing, they
do not take into account the prior probabilities of the hypotheses under
consideration. It would be interesting to investigate whether the reverse-Bayes
approach could be used in a framework where priors are assigned jointly to the
hypothesis and parameter space \citep{Dellaportas2012}. Finally, an important
aspect is the design of new replication studies. An appropriate sample size is
of particular importance for a replication to be informative. We will report in
the future on sample size planning based on the sceptical Bayes factor.

% conclusion
For a thorough assessment of replication attempts, no single metric seems to be
able to answer all important questions completely. Instead, we recommend that
researchers conduct a comprehensive statistical evaluation of replication
success. Reverse-Bayes methods naturally fit to the replication setting, they
avoid various paradoxes from which other methods suffers, and they combine
different notions of replicability. The reverse-Bayes approach therefore leads
to sensible inferences and decisions, which is why we advocate it as a key part
in the assessment of replication success.

\section*{Software and data}
All analyses were performed in the R programming language version
4.2.2 \citep{R}. The code to
reproduce this manuscript is available at
\url{https://gitlab.uzh.ch/samuel.pawel/BFScode}. We used the implementation of
the Lambert $W$ function from the package \texttt{lamW} \citep{Adler2015},
graphics were created with the \texttt{ggplot2} package \citep{Wickham2016}, the
sceptical $p$-value and related calculations were conducted using the package
\texttt{ReplicationSuccess} available on the Comprehensive R Archive Network
% \url{https://cran.r-project.org/web/packages/ReplicationSuccess/index.html}
\citep{Held2020}. All methods are implemented in the R package \texttt{BayesRep}
which is available at \url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}.

Data on effect estimates from the \emph{Social Sciences Replication Project}
\citep{Camerer2018} were downloaded from \url{https://osf.io/abu7k/},
respectively, taken from \url{https://osf.io/nsxgj/} for exact calculations.

\section*{Acknowledgements}
We thank the anonymous referees for the helpful comments and suggestions that
have considerably improved the paper. We also thank Guido Consonni, Luca La
Rocca, Malgorzata Roos, Georgia Salanti, Charlotte Micheloud, and Maria
Bekker-Nielsen Dunbar for helpful discussion and comments on drafts of the
manuscript.

\section*{Funding}
This work was supported by the Swiss National Science Foundation (project number
189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
design, data collection and analysis, decision to publish, or preparation of the
manuscript.

% Bibliography
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

\begin{subappendices}
  \label{sec:appendices}
  \renewcommand{\thesection}{\Alph{section}}

\section{Sufficiently sceptical relative prior variance}
\label{appendix:ssrv}
The sufficiently sceptical relative prior variance at level $\gamma$ is the
value $\gy \in [0, \gminBFo]$ that fulfils the condition
\begin{align}
  \label{sspv}
  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gy)
  &= \gamma.
\end{align}
Substituting~\eqref{sspv} and rearranging terms, we obtain
\begin{align}
  \label{sspv2}
  \sqrt{1 + \gy} \cdot
  \exp\left\{-\frac{1}{2} \cdot
  \frac{\gy}{1 + \gy} \cdot z^2_o\right\}
  &= \gamma \nonumber \\
  \iff \frac{1}{\gamma} \cdot \exp\left\{-\frac{z_o^2}{2}\right\}
  &= \frac{1}{\sqrt{1 + \gy}} \exp\left\{-\frac{1}{2} \cdot
  \frac{z_o^2}{1 + \gy}\right\}. \nonumber
  \\
  \intertext{Squaring both sides and multiplying by $-z_o^2$, this becomes}
  \iff -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
  &= -\frac{z_o^2}{1 + \gy}
  \exp\left\{-\frac{z_o^2}{1 + \gy}\right\}.
\end{align}
This is a transcendental equation that cannot be explicitly solved in terms of
elementary functions. However, if we set $q = -z_o^2/(1 + \gy)$
then~\eqref{sspv2} becomes
\begin{align*}
  -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
  &= q \cdot \exp\left\{q\right\}.
\end{align*}
The solution for $q$ (and consequently for $\gy$) can be explicitly computed
with
\begin{align}
\label{eq:solutionvss}
  q &= \lw{-1}\left(-\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}\right)
  \nonumber \\
  \gy &=
  \begin{cases}
    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases}
\end{align}
where $\lw{-1}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
$W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, ensuring that $\gy \leq \gminBFo$. See
Appendix~\ref{appendix:lambertW} for details about the Lambert $W$ function. For
some $z_o$, equation \eqref{sspv2} can also be satisfied for negative $\gy$,
which is why we need to add the condition $-z_o^2/q \geq 1$ in equation
\eqref{eq:solutionvss}, such that $\gy$ is a valid relative variance.

As $z_{o}^{2}$ becomes larger, the argument to the Lambert function
$x = -z_{o}^{2}\exp(-z_{o}^{2})/\gamma^{2}$ will approach zero, so the
approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ can be applied
\citep[p. 350]{Corless1996}. This leads to
\begin{align*}
  \gy \approx \frac{z_{o}^{2}}{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2} +
  \log\{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2}\}} - 1.
\end{align*}
We can see that $\gy \downarrow 0$ when $\gamma$ remains fixed and
$z_{o}^{2} \to \infty$, which means that the sufficiently sceptical relative
prior variance converges to zero for increasingly compelling evidence from the
original study.

\section{The Lambert $W$ function}
\label{appendix:lambertW}
The Lambert $W$ function \citep{Corless1996} is defined as the function
$W(\cdot)$ satisfying
$$W(y) \cdot \exp\{W(y)\} = y$$
and it is also known as ``product logarithm`` since it returns the number which
plugged in the exponential function and then multiplied by itself produces $y$.
For real $y$, $W(y)$ is only defined for $y \geq - e^{-1}$ and for
$y \in [-e^{-1}, 0)$ the function has two branches that are commonly denoted by
$\lw{0}(\cdot)$, the branch with $W(y) \geq -1$, and $\lw{-1}(\cdot)$, the
branch with $W(y) \leq -1$ (see Figure \ref{fig:lambertW} for an illustration).
\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper1/plot-Lambert-1}
\end{knitrout}
\caption{Lambert $W$ function for real argument $y$.}
\label{fig:lambertW}
\end{figure}

\section{Computation of the sceptical Bayes factor}
\label{appendix:bfs}
From the definition of the sceptical Bayes factor it is apparent that $\BFs$ is
either
\begin{enumerate}
  \item \label{undef} undefined,
  if
  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g) >
  \BFcol{\text{0}}{\text{S}}(\hat{\theta}_o; g)$ for all $g \in [0,
    \gminBFo]$

  \item \label{lowbound} $\BFs = \minBF_{o}$, if
  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq
  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gminBFo)$

  \item \label{intersection}
  $\BFs = \inf_{\gy}
  \left\{\gamma : \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)
  = \gamma\right\}$,
  the height of the lowest intersection of
  $\BFcol{0}{\text{S}}(\hat{\theta}_o; \gy) = \gamma$ and
  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)$
  in $\gy$ otherwise
\end{enumerate}
Whether $\BFs$ attains the lower bound $\minBF_{o}$ (condition \ref{lowbound})
can be checked by evaluating if
$\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq \minBF_{o}$ and setting
$\BFs = \minBF_{o}$ if it is the case. For condition \ref{intersection}, we know
that the intersections satisfy
\begin{align*}
  \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g_*) &=
  \BFcol{0}{\text{S}}(\hat{\theta}_o; g_*) \\
  \sqrt{\frac{1/c + 1}{1/c + g_*}} \cdot
  \exp\left\{-\frac{z_{o}^{2}}{2}\left(\frac{d^2}{1/c + g_*} -
  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}
  &= \sqrt{1 + g_*} \cdot
  \exp\left\{-\frac{1}{2} \cdot \frac{g_*}{1 + g_*} \cdot z^2_o\right\}
\end{align*}
which is equivalent to
\begin{align}
  \sqrt{\frac{1}{(1 + g_*)(1/c + g_*)}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
  \frac{1}{1 + g_*} + \frac{d^{2}}{1/c + g_*}\right)\right\} \nonumber \\
  = \sqrt{\frac{1}{1/c + 1}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
  1 + \frac{(1 - d)^{2}}{1/c + 1}\right)\right\}.
  \label{eq:bfsroot}
\end{align}
This is a transcendental equation that has no closed-form solution for $g_*$ in
terms of elementary functions, but root-finding algorithms can be used to
compute it. However, when $c = 1$, equation~\eqref{eq:bfsroot} simplifies
\begin{align}
  \label{eq:bfsroot2}
  \frac{1}{1 + g_*}\cdot\exp\left\{-\frac{z_{o}^{2}}{2} \cdot
  \frac{1 + d^{2}}{1 + g_*}\right\}
  &= \frac{1}{\sqrt{2}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
  1 + \frac{(1 - d)^{2}}{2}\right)\right\}.
\end{align}
Multiplying~\eqref{eq:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
Lambert $W$ function leads to
\begin{align}
  \label{eq:gintersect}
  % q &= W\left(-\frac{z_A^2}{\sqrt{2}} \cdot
  % \exp\left\{-\frac{z_o^2}{2} \left(1 + \frac{(1 - d)^2}{2}\right)\right\}\right) \\
  % g_* &=
  % \begin{cases}
  %   \dfrac{-z_A^2}{q} - 1 & ~~ \text{if} ~ \dfrac{-z_A^2}{q} \geq 1 \\
  %   \text{undefined} & ~~ \text{else},
  % \end{cases}
  k &= W\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{1 + d^{2}}{2} \cdot
      \exp\left\{-\frac{z_o^2}{2} \left[1 + \frac{(1 - d)^2}{2}\right]\right\}\right)
  \nonumber \\
  g_* &=
  \begin{cases}
    -\dfrac{z_o^2}{k}\cdot \dfrac{1 + d^{2}}{2} - 1 & ~~ \text{if} ~
    -\dfrac{z_o^2}{k}\cdot\dfrac{1 + d^{2}}{2} \geq 1 \\
    \text{undefined} & ~~ \text{else},
  \end{cases}
\end{align}
with the condition that $-z_o^2(1 + d^{2})/(2k) \geq 1$ such that $g_*$ is a
valid relative variance, as the equation may otherwise be satisfied for negative
$g_*$. Since the argument to $W(\cdot)$ is real and negative (if $z_{o}\neq 0$),
the branches $\lw{-1}(\cdot)$ and $\lw{0}(\cdot)$ both provide solutions that
can fulfil the equation (assuming the argument is not smaller than $-e^{-1}$
which would mean that there are no intersections). It must also hold that
$g_{*} \leq g_{\minBF_{o}} = \max\{z_{o}^{2} - 1, 0\}$ for $g_{*}$ to be a valid
sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the $g_{*}$
from~\eqref{eq:gintersect} can only be computed with the $\lw{-1}(\cdot)$
branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$ the solution
$g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the relative prior
variance $g_{*}$ from~\eqref{eq:gintersect} into the Bayes factor
from~\eqref{eq:BFo}, we obtain the expression for the sceptical Bayes factor
in~\eqref{eq:BFsc1}.

\section{Bayes factor with truncated advocacy prior}
\label{app:BFtrunc}
For now assume $\that_o > 0$. The marginal likelihood of the replication effect
estimate $\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
truncated advocacy prior
$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \mathbb{1}_{(0, \infty)}(\theta)$
is
\begin{align}
  f(\that_r \given \HAp)
  &= \int_{-\infty}^{+\infty} f(\that_r \given \theta) f(\theta \given
  \HAp) \, \text{d}\theta \nonumber \\
  &= \int_{-\infty}^{+\infty}
  \frac{\mathbb{1}_{(0, \infty)}(\theta)}{2\pi\sigma_r\sigma_o\Phi(z_o)}
  \exp\left\{-\frac{1}{2}\left[\frac{(\that_o - \theta)^2}{\sigma^2_r}
  + \frac{(\theta - \that_o)^2}{\sigma^2_o}\right]\right\}
  \, \text{d}\theta \nonumber \\
  &=
  \frac{1}{2\pi\sigma_r\sigma_o\Phi(z_o)}
  \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}\right\}
   \underbrace{\int_{0}^{+\infty}
   \exp\left\{-\frac{1}{2}\frac{(\theta - \frac{\that_o/\sigma^2_o +
       \that_r/\sigma^2_r}{1/\sigma^2_o + 1/\sigma^2_r})^2}{\left(
     1/\sigma^2_o + 1/\sigma^2_r\right)^{-1}}\right\}
   \, \text{d}\theta}_{=\sqrt{\frac{2\pi}{1/\sigma^2_o + 1/\sigma^2_r}}
   % \Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)} \nonumber \\
  \Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)} \nonumber \\
   &= \frac{1}{\sqrt{2\pi(\sigma_r^2 + \sigma_o^2)}}
   \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}
     % \right\}  \frac{\Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)}{
     \right\}  \frac{\Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)}{
     \Phi(z_o)}.
   \label{eq:truncmarg}
\end{align}
With a similar argument one can show that this result holds for any $\that_o$ if
the last factor in \eqref{eq:truncmarg} is changed to
\begin{align*}
  % \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}
  \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o(1 + dc)}{\sqrt{1 + c}}
  \right\}}{\Phi\left\{\abs{z_o}\right\}}.
\end{align*}
By dividing the marginal likelihood of the replication data under the
sceptical prior by the marginal likelihood under the truncated advocacy prior,
the Bayes factor in \eqref{eq:BFrtrunc} is obtained.

\section{The shrinkage paradox}
\label{app:shrinkage}
We want to investigate what happens to the replication success regions as the
relative variance $c$ and the squared original $z$-value $z_{o}^{2}$ (a monotone
transformation of the original minimum Bayes factor $\minBF_{o}$) become larger.
Ignoring the success regions on the wrong side of zero (due to the replication
paradox), the minimum relative effect estimates $\dmin$ as shown in
Section~\ref{sec:comparison} are given by

\begin{align*}
    &\dmin^{\scriptscriptstyle \BFs} =
      \frac{1/c + \gy}{\gy - 1} +
      \sqrt{\frac{\log\left[\frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right]/z_{o}^{2}
      + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\left[(1/c + \gy)(1/c + 1)\right]}}&
  &\text{(sceptical Bayes factor)} \\
    &\dmin^{\scriptscriptstyle \text{2TR}} =
      \frac{z_{\gamma}}{z_{o}\sqrt{c}}&
  &\text{(two-trials rule)} \\
    &\dmin^{\scriptscriptstyle \BFr} =
      \sqrt{\left[1 + \frac{\log(1 + c) - 2\log \gamma}{z_{o}^{2}}\right] \frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c} &
  &\text{(replication Bayes factor)} \\
    &\dmin^{\scriptscriptstyle \ps} =
      \sqrt{\frac{1/c + 1/(z_{o}^{2}/z_{\gamma}^{2} - 1)}{z_{o}^{2}/z_{\gamma}^{2}}}&
  &\text{(sceptical $p$-value)} \\
\end{align*}
where for the sceptical Bayes factor it was assumed that $\gy > 1$ (otherwise
the plus before the square root term needs to be replaced by a minus).

For the sceptical Bayes factor, we obtain
\begin{align*}
  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFs} =
  \frac{\gy}{\gy - 1} +
    \sqrt{\frac{\log\left[\frac{1}{\gy(1 + \gy)}\right]/z_{o}^{2}
    + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\gy}}&
  &\text{and}&
  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFs} =
    \sqrt{\frac{1/c + 1}{c}} - \frac{1}{c}&
\end{align*}
where for the second limit we used that $\lim_{z_{o}^{2} \to \infty} \gy = 0$
for a fixed level $\gamma$ (Appendix~\ref{appendix:ssrv}). So the sceptical
Bayes factor does not suffer from any form of the shrinkage paradox. The limits
for the two-trials rule are given by
\begin{align*}
  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
  &\text{and}&
  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
\end{align*}
so the two-trials rule suffers from both forms of the shrinkage paradox. For the
sceptical $p$-value, we obtain
\begin{align*}
  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \ps} =
    \sqrt{\frac{z_{\gamma}^{2}}{z_{o}^{2}(z_{o}^{2}/z_{\gamma}^{2} - 1)}}&
  &\text{and}&
  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \ps} = 0&
\end{align*}
thus, the sceptical $p$-value suffers from the shrinkage paradox at original.
Finally, the limits for the replication Bayes factor are
\begin{align*}
  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFr} = 0 &
  &\text{and}&
  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFr} =
    \sqrt{\frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c}&
\end{align*}
which means that the replication Bayes factor suffers from the shrinkage paradox
at replication.

\section{Probability of replication success with the sceptical Bayes factor}
\label{app:powerBFs}
Conditional on the original study, the probability for replication success at
level $\gamma$ is given by the probability of \eqref{eq:RSCond-d}. This event
involves $z_r = dz_o \sqrt{c}$ as the only random quantity if the original study
has been completed. Assuming a normal distribution
\begin{align*}
  z_r \given z_o, c \sim \Nor(\mu_{z_r}, \sigma^2_{z_r})
\end{align*}
which may depend on $z_o$ and $c$ encompasses the typical scenarios under which
one would want to compute the probability for replication success. For example,
under the null hypothesis ($H_{0} \colon \theta = 0$), we have $\mu_{z_r} = 0$
and $\sigma^2_{z_r} = 1$. For conditional power we assume the underlying effect
size equals the original effect estimate ($\theta = \that_o$) and therefore
$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1$. Finally, predictive power
is obtained by using the predictive distribution based on the advocacy prior
($\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$) and thus
$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1 + c$.

Applying some algebraic manipulations to \eqref{eq:RSCond-d}, the
probability for replication success at level $\gamma$ can be computed by
\begin{align}
  \label{eq:powerBFs}
  \Pr\left(\BFs \leq \gamma \given z_o, c\right) =
  \begin{cases}
    \Pr(\chi^2_{1,\lambda} \geq  A/[B \sigma^2_{z_r}])
    & \text{for} ~ \gy < 1 \\
    \Phi(\text{sign}(z_o) \left\{\mu_{z_r} - D\right\}/\sigma_{z_r})
    & \text{for} ~ \gy = 1 \\
    \Pr(\chi^2_{1,\lambda} \leq A/[B \sigma^2_{z_r}])
    & \text{for} ~ \gy > 1
  \end{cases}
\end{align}
with non-centrality parameter $\lambda = (\mu_{z_r} - M)^2/\sigma^2_{z_r}$
and
\begin{align*}
  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
  z_o^2 \left\{\frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \right\}, \\
  B &= \frac{1 - \gy}{(1 + c\gy)(1/c + 1)}, \\
  D &= \frac{z_o^2 \{1/2 + 1/(1/c + 1)\} - \log 2}{2 z_o \sqrt{c}} (1 + c) \\
  M &= \frac{z_o(1 + c\gy)}{\sqrt{c}(\gy - 1)}.
\end{align*}
The probability is zero, if the original $z$-value $|z_o|$ is not large enough
such that the sufficiently sceptical relative prior variance $\gy$ can be
computed for level $\gamma$ with \eqref{ggamma}.

\section{Probability of replication success with the replication Bayes factor}
\label{app:powerBFr}
The probability of $\BFr \leq \gamma$ is equivalent to the probability of
\begin{align}
  \label{eq:BFrsuccess}
  \log(1 + c) - z_{r}^{2} + \frac{(z_{r} - z_{o}\sqrt{c})^{2}}{1 + c}
  \leq  2 \log \gamma
\end{align}
Applying some algebraic manipulations to \eqref{eq:BFrsuccess} and assuming a
normal distribution for $z_{r}$ as in Appendix~\ref{app:powerBFs} leads to
\begin{align*}
  \Pr\left(\BFr \leq \gamma \given z_o, c\right) =
  \Pr\left(\chi^2_{1,\lambda} \geq \left\{z_{o}^{2} + \log(1 + c) - \log \gamma^{2}
  \right\} [1 + 1/c] / \sigma^2_{z_r}\right)
\end{align*}
with non-centrality parameter $\lambda = (\mu_{z_r} + z_{o}/\sqrt{c})^2/\sigma^2_{z_r}$.

\end{subappendices}

% %% R sessionInfo for reproducibility
% %% -----------------------------------------------------------------------------
% \newpage \section*{Computational details}
% \begin{knitrout}\footnotesize
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
% \begin{alltt}
% \hlkwd{sessionInfo}\hlstd{()}
% \end{alltt}
% \begin{verbatim}
% ## R version 4.2.2 Patched (2022-11-10 r83330)
% ## Platform: x86_64-pc-linux-gnu (64-bit)
% ## Running under: Ubuntu 20.04.5 LTS
% ##
% ## Matrix products: default
% ## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
% ## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
% ##
% ## locale:
% ##  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
% ##  [3] LC_TIME=de_CH.UTF-8        LC_COLLATE=en_US.UTF-8
% ##  [5] LC_MONETARY=de_CH.UTF-8    LC_MESSAGES=en_US.UTF-8
% ##  [7] LC_PAPER=de_CH.UTF-8       LC_NAME=C
% ##  [9] LC_ADDRESS=C               LC_TELEPHONE=C
% ## [11] LC_MEASUREMENT=de_CH.UTF-8 LC_IDENTIFICATION=C
% ##
% ## attached base packages:
% ## [1] stats     graphics  grDevices utils     datasets  methods   base
% ##
% ## other attached packages:
% ##  [1] lamW_2.1.1             xtable_1.8-4           scales_1.2.1
% ##  [4] ggplot2_3.4.0          tidyr_1.2.1            dplyr_1.0.10
% ##  [7] ReplicationSuccess_1.2 biostatUZH_1.8.0       survival_3.4-0
% ## [10] BayesRep_0.1           knitr_1.40
% ##
% ## loaded via a namespace (and not attached):
% ##  [1] Rcpp_1.0.9         RColorBrewer_1.1-3 pillar_1.8.1       compiler_4.2.2
% ##  [5] highr_0.9          tools_4.2.2        digest_0.6.30      boot_1.3-28
% ##  [9] viridisLite_0.4.1  evaluate_0.18      lifecycle_1.0.3    tibble_3.1.8
% ## [13] gtable_0.3.1       lattice_0.20-45    pkgconfig_2.0.3    rlang_1.0.6
% ## [17] Matrix_1.5-1       cli_3.4.1          DBI_1.1.3          xfun_0.34
% ## [21] withr_2.5.0        stringr_1.4.1      contfrac_1.1-12    elliptic_1.4-0
% ## [25] generics_0.1.3     vctrs_0.5.0        grid_4.2.2         tidyselect_1.2.0
% ## [29] deSolve_1.34       glue_1.6.2         R6_2.5.1           fansi_1.0.3
% ## [33] farver_2.1.1       purrr_0.3.5        magrittr_2.0.3     MASS_7.3-58.1
% ## [37] codetools_0.2-18   ellipsis_0.3.2     splines_4.2.2      assertthat_0.2.1
% ## [41] colorspace_2.0-3   labeling_0.4.2     utf8_1.2.2         stringi_1.7.8
% ## [45] RcppParallel_5.1.5 munsell_0.5.0      hypergeo_1.2-13
% \end{verbatim}
% \end{kframe}
% \end{knitrout}

### 2022-11-24 preface.tex
commit local files

\section*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This thesis is submitted under the PhD program ``Epidemiology and
Biostatistics'' at the University of Zurich for the degree of Doctor of
Philosophy.
%(\url{http://www.epibiostat-phd.uzh.ch})
The research contained in this thesis was conducted between October 2019 and
December 2022. Financial support was provided by the Swiss National Science
Foundation through the project ``Reverse-Bayes design and analysis of
replication studies'' (project
\href{https://data.snf.ch/grants/grant/189295}{\#189295}) awarded to Leonard
Held.

First and foremost I want to thank my supervisor Leo for giving me the
opportunity to do this PhD, for showing me an open-minded and pragmatic approach
to statistics, and for giving me the freedom to explore and develop into an
independent researcher. I also want to thank the other two members of my PhD
committee, Guido and Reinhard, for always providing excellent advice and being
great collaborators. Another thank you goes to Robert Matthews who also is a
great collaborator and without whom this PhD project would never exist as it was
him who resurrected the reverse-Bayes approach from the dead almost twenty years
ago. Furthermore, I want to thank Eric-Jan Wagenmakers for reviewing this thesis
and for giving me the opportunity to do a very interesting and productive six
months research stay in Amsterdam.

I also want to thank my friends and colleagues from the Epidemiology,
Biostatistics, and Prevention Institute from the University of Zurich (in
alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
Dafne, Dominik, Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas,
Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Martin,
Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala, Torsten, Ulrike. Another
``thanks'' goes to my friends from the Department of Psychological Methods from
the University of Amsterdam (in alphabetical order): Adam, Alexander, Alexandra,
Alessandra, Alejandro, Angelika, Bruno, Don, František, Frederik, Jason, Johnny,
Joris, Jill, Julia, Lukas, Maarten, Michelle, Nora, Omid, Quentin, René, Serjan,
Suzanne, Ting. I also want to thank my good friends from outside academia (in
alphabetical order): Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela,
Peter. A special thanks goes to Ada. Finally, I thank my family Beni, Christa,
Elisabeth, Fabian, Harry, Markus, Maja, Noemi for their support.

\begin{flushright}
  \hfill Zürich, December 2022

  \hfill Samuel Pawel
\end{flushright}

### 2022-11-24 summary.tex
commit local files

\newpage
\section{Thesis summary}
\label{sec:summary}
\raggedbottom

This thesis consists of six papers. Paper I and II (and to a lesser extent III)
focus on extending the reverse-Bayes assessment of replication success from
\citet{Held2020}. Paper III presents a general Bayesian framework for
replication study design. Paper IV is a review paper about reverse-Bayes
methodology. Paper V is a short comment on another article which proposed a
reverse-Bayes method. Paper VI lists and illustrates questionable research
practices in simulation studies.

\startPaperSummary{PaperI}{%
  The sceptical Bayes factor for the assessment of replication success}{%
  Samuel Pawel, Leonhard Held \\
  \textit{Journal of the Royal Statistical Society: Series B (Statistical
    Methodology)}, 2022, 84(3), 879--911.
  \url{https://doi.org/10.1111/rssb.12491}.}

The reverse-Bayes approach from \citet{Held2020} is based on challenging the
original study with a sceptical prior so that there is no longer evidence for an
effect. Evidence is quantified in terms of credible intervals, respectively,
tail-probabilities. However, there exist also other measures of evidence, and it
has been a matter of long debates which is the most appropriate \citep[see
\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
  Lakens2018, Amrhein2019b}. In this paper, we therefore extend the
reverse-Bayes assessment of replication studies to use Bayes factors
\citep{Good1958, Jeffreys1961} for quantifying evidence and prior-data
conflict. % Bayes factors are also
% used for prior-data conflict assessment as suggested by \citep{Box1980}.
Similarly to the sceptical $p$-value, the procedure leads to a single measure
for quantifying the degree of replication success, \emph{the sceptical Bayes
  factor}. Systematic comparisons show that the sceptical Bayes factor shares
most properties with the sceptical $p$-value due to the reverse-Bayes approach
underlying both methods, yet in some situations conclusions may also differ
because of their different ways of quantifying evidence. Specifically, it is
shown that the sceptical $p$-values suffers from a certain type of ``shrinkage
paradox'', which is avoided by the sceptical Bayes factor; when the $p$-value
from the original study goes to zero, replication success based on the sceptical
$p$-value can be achieved with any arbitrarily small replication effect
estimate, whereas replication success based on the sceptical Bayes factor poses
a finite limit on how much shrinkage is allowed. Technically, the procedure is
more involved and closed-form solutions for the sceptical Bayes factor are only
available in special situations. % and in terms of the
% ``Lambert W function'' \citep{Corless1996}.
The method is illustrated on data from the Social Sciences Replication Project
\citep{Camerer2018}, and implemented in an R package.

The idea to use Bayes factors instead of tail probabilities was suggested by
\citet{Consonni2019} and \citet{Pericchi2020} independently in response to
original article by \citet{Held2020}. L. Held then implemented a first version
of the procedure for the grant application of this research project
\citep{Heldproposal2019}. I then worked out the technical and implementation
details, including closed-form solution for the sceptical Bayes factors,
asymptotic properties, type-I and type-II error rates, and non-normal extensions
of the procedure. I wrote the initial draft of the manuscript and the R package.
Throughout, L. Held gave high-level feedback. I presented initial results at the
GMDS and CEN-IBS conference in 2020 (online), L. Held presented the final
results at the ISBA world meeting 2021 (online).

\startPaperSummary{PaperII}{%
  The assessment of replication success based on relative effect size}{%
  Leonhard Held, Charlotte Micheloud, Samuel Pawel \\
  \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
  \url{https://doi.org/10.1214/21-AOAS1502}.}

It is not clear how to numerically interpret the sceptical $p$-value, as it is
not an ordinary $p$-value (which has a uniform distribution under the
corresponding null hypothesis). Similarly, it is unclear which threshold should
be used in case the sceptical $p$-value needs to be dichotomized into
replication success/failure. In this article, we therefore look closer at the
``success region'' of the sceptical $p$-value in terms of the relative effect
estimate $d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a
new default level for thresholding the sceptical $p$-value called the
\emph{golden level} $\alpha_{G}$ (because the golden ration appears in its
derivation). The golden level is defined through the property that for an
original study which was just borderline significant ($p_{o} = \alpha$),
replication success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if
the replication effect estimate is at least as large as the original one
($d \geq 1$). The behavior of the golden level seems to align with common sense;
For original studies which were already convincing (in terms of their $p$-value)
the effect estimate in the replication study is allowed to shrink, to some
extent, whereas for less convincing original studies (those with $p$-values
around the significance level) shrinkage is more strongly penalized. We find
that in typical situations, replication success based on the golden level also
has similar or improved frequentist properties (type-I error rate and project
power) compared to the standard significance criterion. Case studies from four
large-scale replication projects illustrate the properties of the method.

L. Held had the idea to apply the sceptical $p$-value method to the data from
the four replication projects, which I collected for my master thesis. C.
Micheloud and L. Held came up with the golden level. L. Held wrote an initial
draft of the manuscript. C. Micheloud, L. Held, and I then iteratively worked on
the manuscript.

\startPaperSummary{PaperIII}{%
  Bayesian approaches to designing replication studies}{%
  Samuel Pawel, Guido Consonni, Leonhard Held \\
  2022. arXiv preprint.
  \url{https://doi.org/10.48550/arXiv.2211.02552}.}

An important aspect in the design of replication studies is determining their
sample size. How exactly the sample size should be determined depends on the
method which will be used for analyzing the replication data. Various approaches
have been proposed for doing so which are specifically tailored to certain
analysis methods. In this article, we provide a general Bayesian framework which
applies to any analysis method (including the sceptical $p$-value and the
sceptical Bayes factor). We show how the data from the original study and
external knowledge can be combined in a \emph{design prior} for the underlying
model parameters. Based on a design prior, predictions about the replication
data can then be computed, and the replication sample size can be chosen such
the probability of replication success becomes as high as desired. We illustrate
Bayesian design of replication studies in the normal-normal hierarchical model
which provides sufficient flexibility for specification of design priors. Data
from a cross-laboratory replication project are used for illustrating our
methods, which are also available in an R package.

L. Held specified in the grant application of this research project
\citep{Heldproposal2019} that we will investigate power and sample size
calculations for the sceptical $p$-value and the sceptical Bayes factor. For the
first paper I already derived the power function of the sceptical Bayes factor
in closed-form for two types of design priors. After its completion, I
generalized the result to any design prior in the normal-normal hierarchical
model, and started working on this manuscript. I presented a first draft to L.
Held and G. Consonni in the beginning of 2021. G. Consonni then helped
developing the methodology for multisite replication study design. I continued
working on the manuscript in 2022 and also wrote the accompanying R package.
Throughout, L. Held and G. Consonni gave high-level feedback.

\startPaperSummary{PaperIV}{%
  Reverse-Bayes methods for evidence assessment and research synthesis}{%
  Leonhard Held, Robert Matthews, Manuela Ott, Samuel Pawel \\
  \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
  \url{https://doi.org/10.1002/jrsm.1538}.}

While the popularity of Bayesian methods has been rapidly increasing since the
advent of modern computational methods in the 1990s, reverse-Bayes methods % , such
% as the reverse-Bayes assessment of replication studies,
have remained largely unknown to statisticians and users of statistics alike. In
this article, we review reverse-Bayes history and methods to increase awareness
about the approach. Specifically, we summarize the work on reverse-Bayes by I.
J. Good \citep{Good1950}, who first proposed the idea. We then review methods
such as the \emph{Analysis of Credibility} from \citet{Matthews2001b,
  Matthews2018}, its extension to Bayes factors, and the \emph{False Positive
  Risk} from \citet{Colquhoun2017}. To illustrate these method, we use data from
a meta-analysis on the effect of corticosteroids on COVID-19 mortality.

L. Held and M. Ott started working on this article several years ago when M. Ott
was still a PhD student (around 2017). When I discovered the connection between
the Analysis of Credibility and the fail-safe N method, L. Held suggested that
it would fit nicely into this manuscript, and that I should start to overhaul
it. I rewrote and expanded his initial draft, adding also a new section on
reverse-Bayes approaches with Bayes factors, largely based on the work from
paper I. We then managed to recruit R. Matthews to also contribute. From that
point on the three of us iteratively worked on the manuscript and M. Ott gave
high-level feedback.

\startPaperSummary{PaperV}{%
  Comment on ``Bayesian additional evidence for decision making under small
sample uncertainty''}{%
   Samuel Pawel, Leonhard Held, Robert Matthews \\
  \textit{BMC Medical Research Methodology}, 2022, 22(149).
  \url{https://doi.org/10.1186/s12874-022-01635-4}.}

Shortly after the acceptance of paper III, the article by \citet{Sondhi2021}
appeared. It proposed a novel reverse-Bayes method called \emph{Bayesian
  Additional Evidence}, and we noted some flaws in the article. This prompted us
to write a commentary. We show that --contrary to the statement by
\citet{Sondhi2021}-- there is a closed form solution for the key quantity in
their approach termed ``Bayesian Additional Evidence tipping point''.
% The Bayesian Additional Evidence method provides an answer to the question
% ``What prior do I have to choose so that that my unconvincing data become
% convincing?''.
The method is also closely related the Analysis of Credibility by
\citet{Matthews2018}. We investigate differences and similarities of the two
methods, showing that the priors determined through the Bayesian Additional
Evidence method are not always helpful.

R. Matthews attended us about the article from \citet{Sondhi2021}. After reading
it, I realized that their statement about closed-form solutions was incorrect
and derived a solution. L. Held suggested to write a commentary. I wrote an
initial draft of the manuscript, which R. Matthews substantially improved. The
two of us iteratively worked on the manuscript, while L. Held gave mostly
high-level feedback.

\startPaperSummary{PaperVI}{%
  Pitfalls and Potentials in Simulation Studies}{%
  Samuel Pawel, Lucas Kook, Kelly Reeve \\
  2022. arXiv preprint.
  \url{https://doi.org/10.48550/arXiv.2203.13076}.}

Simulation studies are frequently used for evaluating statistical methods.
However, several studies showed that the reporting standards in simulation
studies have remained low over the years \citep{Hoaglin1975, Burton2006,
  Morris2019}. Moreover, some authors have recently argued that also
methodological research is suffering from reproducibility issues, publication
bias, and a ``replication crisis'' due to researchers engaging in questionable
research practices, such as selective reporting \citep{Boulesteix2020}. In this
article, we raise awareness about these issues. We summarize possible
questionable research practices in simulation studies, and show how easy it is
make a method seem superior if various questionable research practices are
employed. We also give recommendations which could help to alleviate these
issues, most importantly we recommend researchers to write and pre-register
simulation protocols.

The manuscript is co-first authored by myself and L. Kook. I had the idea to
invent a ``mock-method'' and use questionable research practices that make it
seem superior, to draw attention to the low standards in methodological
research. I then wrote a first draft of the manuscript and proposed the idea to
L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
and started writing the simulation protocol. L. Kook took lead in developing the
R package and simulation study code. K. Reeve provided feedback on the
simulation protocol and helped polishing the manuscript. Recently, I was invited
to present the results from this project at the CEN conference 2023 in Basel.

### 2022-11-24 thesis.Rnw
commit local files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% LaTeX master document for a cumulative PhD thesis
%%%
%%% Copyright (C) 2015-2016  Sebastian Meyer
%%%
%%% This template can be redistributed and/or modified under the terms
%%% of the GNU General Public License, version 2 or later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, pagesize, twoside, open=right, cleardoublepage=empty,
headinclude=false, footinclude=false, headsepline, footsepline, parskip=half,
numbers=noendperiod, BCOR=10mm, DIV=18 ]{scrreprt}

%% input header with specifications and custom definitions
\input{header}
\input{defs}

%% load the hyperref package
\usepackage{hyperref}
\hypersetup{
  bookmarksdepth = 2,  % otherwise same depth as TOC (only chapters)
  colorlinks = {true},
  linkcolor = {black},
  citecolor = {Blue},
  urlcolor = {Blue},
  pdftitle = {Reverse-Bayes Methods for Replication Studies and Beyond},
  pdfauthor = {Samuel Pawel},
  pdfsubject = {},
  pdfpagemode = {UseOutlines}
}

\addto{\extrasUKenglish}{%
  \renewcommand{\chapterautorefname}{\chaptername} % "Paper"
  \renewcommand{\sectionautorefname}{Section}      % uppercase
}

%% start with roman numbers
\pagenumbering{roman}

\begin{document}

% ==============================================================================
% COVER
% ==============================================================================
\pdfbookmark{Title}{titlepage}
\includepdf{cover.pdf}

% ==============================================================================
% FRONT MATTER
% ==============================================================================
\pagestyle{empty}
\input{abstract}
\input{outline}

\cleardoublepage
\input{preface}
\pagestyle{scrheadings}

% ==============================================================================
% INTRODUCTION
% ==============================================================================
\cleardoublepage
\pagenumbering{arabic}
% \begin{bibunit}
<< "introduction", child = "intro.Rnw" >>=
@

\input{summary}
% \clearpage
% \putbib
% \end{bibunit}
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

\addtocontents{toc}{\bigskip}

% ==============================================================================
% PAPERS
% ==============================================================================
\cleardoublepage
\cfoot[]{\chapapp $\:$ \thechapter}

% Paper I
% ------------------------------------------------------------------------------
\paperchapter{%
 The sceptical Bayes factor for the assessment of replication success
}{%
  Samuel Pawel, Leonhard Held
}{%
   \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
   \url{https://doi.org/10.1111/rssb.12491}.
 }
\include{paper1}

% \includepdf[pagecommand={}, pages=-, width=1.15\textwidth, offset=0cm 0cm
% ]{pdf/2022-Pawel_Held.pdf}

% Paper II
% ------------------------------------------------------------------------------
\paperchapter{%
 The assessment of replication success based on relative effect size
}{%
  Leonhard Held, Charlotte Micheloud, Samuel Pawel
}{%
   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
  \url{https://doi.org/10.1214/21-AOAS1502}.}
% \includepdf[pagecommand={}, pages=-, width=1.05\textwidth, offset=0cm 0cm
% ]{pdf/2022-Held_etal.pdf}

% Paper III
% ------------------------------------------------------------------------------
\paperchapter{%
  Bayesian approaches to designing replication studies}{%
  Samuel Pawel, Guido Consonni, Leonhard Held}{%
  2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2211.02552}.}
% \includepdf[pagecommand={}, pages=-, width=1.1\textwidth, offset=-0.5cm 0.4cm
% ]{pdf/2022-Pawel_etal.pdf}

% Paper IV
% ------------------------------------------------------------------------------
\paperchapter{%
 Reverse-Bayes methods for evidence assessment and research synthesis
}{%
  Leonhard Held, Robert Matthews, Manuela Ott, Samuel Pawel
}{%
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
  \url{https://doi.org/10.1186/s12874-022-01635-4}.}
% \includepdf[pagecommand={}, pages=-, width=1.15\textwidth, offset=0cm 0cm
% ]{pdf/2021-Held_etal.pdf}

% Paper V
% ------------------------------------------------------------------------------
\paperchapter{%
 Comment on ``Bayesian additional evidence for decision making under small
sample uncertainty''
}{%
  Samuel Pawel, Leonhard Held, Robert Matthews
}{%
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
  \url{https://doi.org/10.1002/jrsm.1538}.}
% \includepdf[pagecommand={}, pages=-, width=1.2\textwidth, offset=0cm 0cm
% ]{pdf/2022-Pawel_etal.pdf}

% Paper VI
% ------------------------------------------------------------------------------
\paperchapter{%
 Pitfalls and Potentials in Simulation Studies
}{%
  Samuel Pawel, Lucas Kook, Kelly Reeve
}{%
  2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2203.13076}.}
% \includepdf[pagecommand={}, pages=-, width=1.1\textwidth, offset=0cm 0cm
% ]{pdf/2022-Pawel_etalb.pdf}

% ==============================================================================
% APPENDIX
% ==============================================================================

% \appendix
% \renewcommand{\chaptername}{Appendix}
% \paperchapter{%
% Multivariate reverse-Bayes analysis
% \label{app:multiRB}
% }{%
%  Samuel Pawel
% }{}

% \paperchapter{%
% Reverse-Bayes asssessment of multiple replications
% \label{app:multipleRB}
% }{%
%  Samuel Pawel
% }{}

\end{document}

### 2022-11-24 intro.Rnw
third paper

@@
                message = FALSE,
-               cache = FALSE,
+               cache = TRUE,
                eval = TRUE)

### 2022-11-24 paper3.tex
third paper

\section*{Abstract}

Replication studies are essential for assessing the credibility of claims from
original studies. A critical aspect of designing replication studies is
determining their sample size; a too small sample size may lead to inconclusive
studies whereas a too large sample size may waste resources that could be
allocated better in other studies. Here we show how Bayesian approaches can be
used for tackling this problem. The Bayesian framework allows researchers to
combine the original data and external knowledge in a design prior distribution
for the underlying parameters. Based on a design prior, predictions about the
replication data can be made, and the replication sample size can be chosen to
ensure a sufficiently high probability of replication success. Replication
success may be defined through Bayesian or non-Bayesian criteria, and different
criteria may also be combined to meet distinct stakeholders and allow conclusive
inferences based on multiple analysis approaches. We investigate sample size
determination in the normal-normal hierarchical model where analytical results
are available and traditional sample size determination is a special case where
the uncertainty on parameter values is not accounted for. An application to data
from a multisite replication project of social-behavioral experiments
illustrates how Bayesian approaches help to design informative and
cost-effective replication studies. Our methods can be used through the R
package BayesRepDesign.

\textbf{Key words}: Bayesian design, design prior, multisite replication, sample
size determination

\section{Introduction}

The replicability of research findings is a cornerstone for the credibility of
science. However, there is growing evidence that the replicability of many
scientific findings is lower than expected \citep{Ioannidis2005,Opensc2015,
  Camerer2018, Errington2021}. This ``replication crisis'' has led to
methodological reforms in various fields of science, one of which is an
increased conduct of replication studies \citep{Munafo2017}. Statistical
methodology plays a key role in the evaluation of replication studies, and
various methods have been proposed for quantifying how ``successful'' a
replication study was in replicating the original finding \citep[among
others]{Bayarri2002, Verhagen2014, Simonsohn2015, Anderson2016, Patil2016,
  Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019, Hedges2019, Mathur2020,
  Held2020, Pawel2020, Bonett2020, Held2021, Pawel2022b}. Yet, as with ordinary
studies, statistical methodology is not only important for analyzing replication
studies but also for designing them, in particular for their \emph{sample size
  determination} (SSD). Optimal SSD is important since too small sample sizes
may lead to inconclusive studies, whereas too large sample sizes may waste
resources which could have been allocated better in other research projects.

SSD for replication studies comes with unique opportunities and challenges; the
data from the original study can be used to inform SSD, at the same time the
analysis of replication success based on original and replication study is
typically different from an analysis of a single study for which traditional SSD
methodology was developed. Since analysis and design of replication studies
should be in accordance, a relatively small literature has emerged which
specifically deals with replication study power calculations and SSD
\citep{Bayarri2002, Goodman1992, Senn2002, Anderson2017, Micheloud2020,
  vanZwet2022, Held2020, Pawel2022b, Hedges2021, Anderson2022}. However, most of
these articles only deal with selected analysis methods and data models. % For
% instance, SSD for standardized mean difference effect sizes analyzed with Bayes
% factors \citep{Bayarri2002}, SSD for statistical significance assessment of the
% replication \citep{Goodman1992, Senn2002, Micheloud2020, vanZwet2022}, SSD for
% reverse-Bayes assessment of replication studies \citep{Held2020, Pawel2022b}, or
% SSD for meta-analysis of replication studies \citep{Hedges2021}.
An exception is the excellent article by \citet{Anderson2022} which discusses
more general principles of replication SSD in the context of psychological
research, mostly from a frequentist perspective. As they state ``the literature
on Bayesian sample size planning is still nascent, particularly with respect to
Bayes Factors \citep{Schoenbrodt2017}, and has not yet been clearly optimized
for the context of most replication goals'' \citep[p. 18]{Anderson2022}. Our
goal is therefore to complement their article by developing a unified framework
of replication SSD (schematically illustrated in Figure~\ref{fig:SSDschema})
based on principles from Bayesian design approaches \citep{Spiegelhalter1986b,
  Spiegelhalter1986c, Weiss1997, OHagan2001b, Gelfand2002, DeSantis2004,
  Spiegelhalter2004, Schoenbrodt2017, Pek2019, Kunzmann2021, Park2022,
  Grieve2022}. We aim to provide both a theoretical basis for methodologists
developing new methods for design and analysis methods of replication studies,
and also to illustrate how Bayesian design approaches can practically be used by
researchers planning a replication study.

\begin{figure}[!ht]
  \centering
  \begin{tikzpicture}[thick, node distance = 11em and 1em,
  font=\fontsize{10pt}{12pt}\selectfont]

   % nodes
    \node[rectangle, draw, rounded corners = 0.2em] (oData)
    {\begin{tabular}{c} \textbf{Original data} \\
        {\scriptsize $f(x_{o} \given \theta)$} \\
     \end{tabular}};

   \node (designPrior) [below right = 3.5em and 2em of oData]
   {\begin{tabular}{c} \textbf{Design prior for model parameter} \\
      {\scriptsize $f(\theta \given x_{o}, \text{external
      knowledge})$}\\
    \end{tabular}};

  \node[rectangle, draw, rounded corners = 0.2em] (external) [right = 17em of oData]
  {\begin{tabular}{c} \textbf{Initial prior for model parameter} \\
     {\scriptsize $f(\theta \given \text{external knowledge})$} \\
   \end{tabular}};

   \node[rectangle, draw, rounded corners = 0.2em] (externalknowl) [below = 2em of external]
   {\begin{tabular}{l}
      \multicolumn{1}{c}{\textbf{External knowledge}} \\
     {\scriptsize -- between-study heterogeneity} \\
     {\scriptsize -- skepticism regarding original study} \\
     {\scriptsize -- data from other studies} \\
     {\scriptsize $\phantom{\rightarrow} \hdots$} \\
   \end{tabular}};

 \node (rData) [below = 4.5em of designPrior]
 {\begin{tabular}{c} \textbf{Predictive distribution of replication data} \\
    {\scriptsize $f(x_{r} \given n_{r}, x_{o}, \text{external
    knowledge})$}
  \end{tabular}};

\node[rectangle, draw, fill = lightlightgray] (nr) [below = 2em of externalknowl]
{\begin{tabular}{c} \textbf{Replication sample size} \\
   {\scriptsize $n_{r}$}
 \end{tabular}};

\node (PRS) [below = 4.5em of rData]
{\begin{tabular}{c} \textbf{Probability of replication success} \\
   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \text{external
    knowledge})$}
 \end{tabular}};

\node[rectangle, draw, rounded corners = 0.2em] (measureRS) [below = 15em of oData]
{\begin{tabular}{c} \textbf{Analysis method}  \\
    {\scriptsize success region $S$} \\
 \end{tabular}};

\node[rectangle, draw, rounded corners = 0.2em] (sideCond) [below = 2.5em of nr]
{\begin{tabular}{l}
   \multicolumn{1}{c}{\textbf{Constraints}} \\
   {\scriptsize -- type-I error rate requirements} \\
   {\scriptsize -- cost/availability constraints} \\
   {\scriptsize $\phantom{\rightarrow} \hdots$} \\
 \end{tabular}};

% edges
\draw [->] [bend left] (oData.east) to ([xshift=-1em]designPrior.north);
\draw [->] [bend right] (external.west) to ([xshift=1em]designPrior.north);
\draw [->] (designPrior) to (rData);
\draw [->] (rData) to (PRS.north);
\draw [->] [bend right] (nr.west) to ([xshift=1em]rData.north);
\draw [->] [bend left] (measureRS.east) to ([xshift=-1em]PRS.north);
\draw [->] [dashed] (oData) to (measureRS);
\draw [->] [dashed] (sideCond) to (nr.south);
\draw [->] [dashed] (externalknowl.north) to (external.south);

\end{tikzpicture}

  \caption{Schematic illustration of Bayesian sample size determination for
    replication studies. The original and replication data are denoted by
    $x_{o}$ and $x_{r}$, respectively. Both are assumed to come from a
    distribution with density/probability mass function denoted by
    $f(x_{i} \given \theta)$ for $i \in \{o, r\}$. An initial prior with density
    function $f(\theta \given \text{external knowledge})$ is assigned to the
    model parameter $\theta$.}
\label{fig:SSDschema}
\end{figure}

The design of replication studies is a natural candidate for Bayesian knowledge
updating as it allows to combine uncertain information from different sources
--for instance, the data from the original study and/or expert knowledge-- in a
so-called \emph{design prior} distribution for the underlying model parameters.
If the analysis of the replication data is also Bayesian, the design prior may
be different from the so-called \emph{analysis prior} which, unlike the design
prior, is usually desired to be objective or ``uninformative''
\citep{OHagan2001b}. Based on the design prior, predictions about the
replication data can then be made, and the sample size can be chosen such that
the probability of replication success becomes sufficiently high. Importantly,
Bayesian design approaches can also be used if the planned analysis of the
replication study is non-Bayesian, which is the more common situation in
practice. Bayesian design based on a frequentist analysis is known under various
names, such as ``hybrid classical-Bayesian design'' \citep{Spiegelhalter2004} or
``Bayesian assurance'' \citep{OHagan2005}, and has also been used before for
psychological applications \citep{Pek2019, Park2022} and replication studies
\citep{Anderson2017, Micheloud2020}.

This paper is structured as follows: We start with presenting a general
framework for Bayesian SSD of replication studies which applies to any kind of
data model and analysis method. We then investigate design priors and SSD in the
normal-normal hierarchical model framework which provides sufficient flexibility
for incorporating the original data and external knowledge in replication
design. No advanced computational methods, such as (Markov Chain) Monte Carlo
sampling, are required for conducting Bayesian SSD in this framework, and in
many cases there are even simple formulae which generalize classical power and
sample size calculations. We illustrate the methodology for several Bayesian and
non-Bayesian analysis methods, and for both singlesite and multisite replication
studies. Since multisite replication studies are becoming increasingly popular
in psychology \citep[\eg{}][]{Klein2018}, we also discuss how to choose the
optimum allocation of samples within and between sites from a Bayesian design
point of view. As a running example we use data from a multisite replication
project of social-behavioral experiments \citep{Protzko2020}. Finally, we close
with concluding remarks, limitations, and open questions.

\section{General framework} \label{sec:GFW}

% Figure~\ref{fig:SSDschema} schematically illustrates the process of Bayesian SSD
% for replication studies, which we will explain in more detail in the following.
Suppose an original study has been conducted and resulted in a data set $x_{o}$.
These data are assumed to come from a distribution characterized by an unknown
parameter $\theta$ and with density function $f(x_{o} \given \theta)$. To assess
the replicability of a claim from the original study, an independent and
identically designed (apart from the sample size) replication study is
conducted, and the goal of the design stage is to determine its sample size
$n_{r}$.

As the observed original data $x_{o}$, the yet unobserved replication data
$X_{r}$ are assumed to come from a distribution depending on the parameter
$\theta$. The parameter $\theta$ thus provides a link between the two studies,
and the knowledge obtained from the original study can be used to make
predictions about the replication. The central quantity for doing so is the
so-called \emph{design prior} of the parameter $\theta$, which we write as the
posterior distribution of $\theta$ based on the original data and an
\emph{initial prior} for $\theta$
\begin{align}
  \label{eq:dp}
  f(\theta \given x_o, \text{external knowledge}) =
  \frac{f(x_o \given \theta) \, f(\theta \given \text{external knowledge})}{f(x_o \given
  \text{external knowledge})}.
\end{align}
The initial prior of $\theta$ may depend on external knowledge (\eg{} data from
other studies) and it represents the uncertainty about $\theta$ before observing
the original data. We will discuss common types of external knowledge in the
replication setting in the next Section. %~\ref{sec:SS}.
The design prior~\eqref{eq:dp} hence represents the state of knowledge and
uncertainty about the parameter $\theta$ before the replication is conducted,
and, along with an assumed replication sample size $n_{r}$, it can be used to
compute a predictive distribution for the replication data
\begin{align}
  \label{eq:ftr}
  f(x_r \given n_r, x_o, \text{external knowledge})
  &= \int%_\Theta
  % \underbrace{f(x_r \given n_{r}, \theta)}_{\text{likelihood}}
    f(x_r \given n_{r}, \theta)
    % \, \underbrace{f(\theta \given x_o, \text{external knowledge})}_{\text{design prior}}
    \, f(\theta \given x_o, \text{external knowledge})
    \, \text{d}\theta.
\end{align}

After completion of the replication, the observed data $x_r$ will be analyzed in
some way to quantify to what extent the original result could be replicated. The
analysis may involve the original data (for example, a meta-analysis of the two
data sets) or it may only use the replication data. Typically, there is a
\emph{success region} $S$ which implies that if the replication data fall within
it ($x_r \in S$), the replication is successful. The \emph{probability of
  replication success} can thus be computed by integrating the predictive
density~\eqref{eq:ftr} over $S$. To ensure a sufficiently conclusive replication
design, the sample size $n_{r}$ is determined such that the probability of
replication success is at least as large as a desired target probability of
success, here and henceforth denoted by $1 - \beta$. The required sample size
$n_r^*$ is then the smallest sample size which leads to a probability of
replication success of at least $1 - \beta$, \ie{}
\begin{align}
  \label{eq:nr}
  n_r^* = \inf \left\{n_r : \Pr(X_{r} \in S \given
  n_r, x_{o}, \text{external knowledge}) \geq 1 - \beta \right\}.
\end{align}

Often, replication studies are analyzed using several methods which quantify
different aspects of replicability, and which have different success regions
(\eg{} one method for quantifying parameter compatibility and another for
quantifying evidence against a null hypothesis). In this case, the sample size
may be chosen such that the probability of replication success is as large as
desired for all planned analysis methods.

There may sometimes be certain constraints which the replication sample size
needs to satisfy. For instance, in most cases there is an upper limit on the
possible sample size due to limited resources and/or availability of samples.
Moreover, funders and regulators may also require methods to be
\emph{calibrated} \citep{Grieve2016}, that is, to have appropriate type I error
rate control. The sample size $n_r^*$ may thus also need to satisfy a type I
error rate not larger than some required level.
% Similarly, it may be reasonable to have \emph{precision} constraints, \eg{} to
% require that a confidence interval for the replication effect estimate has to be
% at least as tight as the confidence interval estimated in the original study.

\section{Sample size determination in the normal-normal hierarchical model}
\label{sec:SS}
We will now illustrate the general methodology from the previous section in the
\emph{normal-normal hierarchical model} where predictive distributions and the
probability of replication success can often be expressed in closed-form,
permitting further insight. % To conduct SSD for replication studies
It is pragmatic to adopt a meta-analytic perspective and use only study level
summary statistics instead of the raw study data since the raw data from the
original study are not always available to the replicators. Typically, the
underlying parameter $\theta$ is a univariate effect size quantifying the effect
on the outcome variable (\eg{} a mean difference, a log odds ratio, or a log
hazard ratio). The original and replication study can then be summarized through
an effect estimate $\that$, possibly the maximum likelihood estimate, and a
corresponding standard error $\sigma$, \ie{} $x_{o} = \{\that_{o}, \sigma_{o}\}$
and $x_{r} = \{\that_{r}, \sigma_{r}\}$. Effect estimates and standard errors
are routinely reported in research articles or can, under some assumptions, be
computed from $p$-values and confidence intervals. As in the conventional
meta-analytic framework \citep{Sutton2001}, we further assume that for study
$k \in \{o, r\}$ the (suitably transformed) effect estimate $\hat{\theta}_k$ is
approximately normally distributed around a study specific effect size
$\theta_k$ and with (known) variance equal to its squared standard error
$\sigma_k^2$, here and henceforth denoted by
$\hat{\theta}_k \given \theta_k \sim \Nor(\theta_k, \sigma_k^2)$. The standard
error $\sigma_k$ is typically of the form $\sigma_k = \lambda/\sqrt{n_k}$ with
$\lambda^{2}$ some unit variance and $n_{k}$ the sample size. The ratio of the
original to the replication variance is thus the ratio of the replication to the
original sample size
\begin{align*}
  c = \sigma^2_o/\sigma^2_r = n_r/n_o,
\end{align*}
which is often the main focus of SSD as it quantifies how much the replication
sample $n_{r}$ size needs to be changed compared to the original sample size
$n_{o}$. Depending on the effect size type, this framework might require slight
modifications \citep[see \eg{}][ch. 2.4]{Spiegelhalter2004}.

Assuming a normal sampling model for the effect
estimates~\eqref{eq:hat_theta_k}, as described previously, and specifying an
initial hierarchical normal prior for the study specific effect
sizes~\eqref{eq:theta_k} and the effect size~\eqref{eq:theta}, leads then to the
normal-normal hierarchical model
\begin{subequations}
\label{eq:hierarch-model}
\begin{align}
  \hat{\theta}_k \given \mspace{-1mu} \theta_k &\sim \Nor(\theta_k, \sigma_k^2)
  \label{eq:hat_theta_k} \\
  \theta_k \given \theta \,\,  &\sim \Nor(\theta, \tau^2) \label{eq:theta_k} \\
  \theta \,\, &\sim \Nor(\mutheta,
  \sigmatheta^2). \label{eq:theta}
\end{align}
\end{subequations}
By marginalizing over the study specific effects sizes, the
model~\eqref{eq:hierarch-model} can alternatively be expressed as
\begin{subequations}
\label{eq:hierarch-model2}
\begin{align}
  \hat{\theta}_k \given \mspace{-1mu} \theta &\sim \Nor(\theta, \sigma_k^2 + \tau^{2})
  \label{eq:hat_theta_k2} \\
  \theta  &\sim \Nor(\mutheta,
  \sigmatheta^2) \label{eq:theta2}
\end{align}
\end{subequations}
which is often more useful for derivations and computations. In the following we
will explain how the normal-normal hierarchical model can be used
% is similar to the random effects model typically used in meta-analysis, and
% to incorporate the original data and external knowledge into
for SSD of the replication study.

\subsection{Design prior and predictive distribution}
\label{sec:designpredictive}
The observed original data $x_{o} = \{\that_{o}, \sigma_{o}\}$ can be combined
with the initial prior~\eqref{eq:theta2} %by Bayes' theorem~\eqref{eq:dp}
by standard Bayesian theory for normal prior and likelihood \citep[ch.
3.7]{Spiegelhalter2004} to obtain a posterior distribution for the effect size
$\theta$
\begin{align}
  \label{eq:dpnormal}
  \theta \given \hat{\theta}_o, \sigma^2_o
  \sim
  \Nor\left(
  \frac{\hat{\theta}_o}{1 + 1/g} + \frac{\mutheta}{1 + g},
  \frac{\sigma^2_o + \tau^2}{1 + 1/g} \right)
\end{align}
where $g = \sigmatheta^2/(\sigma^2_o + \tau^2)$ is the \emph{relative prior
  variance}. This posterior serves then as the design prior for predicting the
replication data.

It is interesting to contrast the design prior \eqref{eq:dpnormal} to the
``conditional'' design prior \citep{Micheloud2020}, that is, to assume that the
unknown effect size $\theta$ corresponds to the original effect estimate
$\that_{o}$. This is a standard approach in practice, for instance,
\citet{Opensc2015} determined the sample sizes of its 100 replications under
this assumption. In our framework it implies that the normal design
prior~\eqref{eq:dpnormal} becomes a point mass at the original effect estimate
$\that_{o}$, which can either be achieved through overwhelmingly informative
original data ($\sigma^{2}_{o} \downarrow 0$) along with no heterogeneity
($\tau^{2} = 0$), or through an overwhelmingly informative initial prior
($g \downarrow 0$) centered around the original effect estimate
($\mutheta = \that_{o}$). Both cases show that from a Bayesian perspective the
standard approach is unnatural as it either corresponds to making the standard
error $\sigma_{o}$ smaller than it actually was, or to cherry-picking the prior
based on the data.

Based on the design prior~\eqref{eq:dpnormal}, the predictive distribution of
the replication effect estimate $\that_{r}$ can then be computed by assuming a
replication standard error $\sigma_{r}$ and integrating the marginal density of
the replication effect estimate~\eqref{eq:hat_theta_k2} with respect to the
prior density, leading to
\begin{align}
  \label{eq:fthetar}
  \hat{\theta}_r \given \hat{\theta}_o, \sigma^2_o, \sigma^2_r
  \sim
  \Nor\left(\muthatr =
  \frac{\hat{\theta}_o}{1 + 1/g} + \frac{\mutheta}{1 + g}, \sigmathatr^{2} =
  \, \sigma^2_r + \tau^2 + \frac{\sigma^2_o + \tau^2}{1 + 1/g}\right)
\end{align}
which can again be shown using standard Bayesian theory \citep[ch.
3.13.3]{Spiegelhalter2004}.
% For some analysis methods, replication success is more naturally defined via the
% replication $z$-value $z_{r} = \that_{r}/\sigma_{r}$. In these cases, it can be
% more convenient to use the associated predictive distribution of $z_{r}$
% \begin{align}
%   \label{eq:zr}
%   z_r \given z_o, c%,  z_{\scriptscriptstyle{\theta}},h, g
%   \sim
%   \Nor\left\{\muzr =
%   \sqrt{c} \left(\frac{z_o}{1 + 1/g} +
%   \frac{z_{\scriptscriptstyle{\theta}} \sqrt{g  (1 + h)}}{1 + g}\right),
%   \sigmazr^{2} =
%   \, 1 + c \left( h + \frac{1 + h}{1 + 1/g}  \right) \right\}
% \end{align}
% which only depends on relative parameters, \ie{} the variance ratio
% $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, the original $z$-value
% $z_{o} = \that_{o}/\sigma_{o}$, the prior $z$-value
% $z_{\scriptscriptstyle{\theta}} = \mutheta/\sigma_{\scriptscriptstyle{\theta}}$,
% and the relative heterogeneity $h = \tau^{2}/\sigma^{2}_{o}$.
The design prior~\eqref{eq:dpnormal} and the resulting predictive
distribution~\eqref{eq:fthetar}
% and~\eqref{eq:zr}
depend on the parameters of the initial prior ($\tau^ {2}$, $\mutheta$,
$\sigmatheta^{2}$). We will now explain how these parameters can be specified
based on external knowledge.

\subsection{Incorporating external knowledge in the initial prior}
\label{sec:initialPrior}

At least three common types of external knowledge can be distinguished in the
replication setting: (i) expected heterogeneity between original and replication
study due to differences in study design, execution, and population, (ii) prior
knowledge about the effect size either from theory or from related studies,
(iii) skepticism regarding the original study due to the possibility of
exaggerated results.

\subsubsection{Between-study heterogeneity}
\label{sec:heterogeneity}
The expected degree of between-study heterogeneity can be incorporated via the
variance $\tau^2$ in~\eqref{eq:theta_k}. As $\tau^{2}$ decreases, the study
specific effect sizes become more similar, whereas for increasing $\tau^{2}$
they become more unrelated. If the replicators do not expect any heterogeneity
they can thus set $\tau^{2} = 0$ which will lead to the model collapsing to a
fixed effects model.

If heterogeneity is expected, there are different approaches for specifying
$\tau^{2}$. A domain expert may subjectively assess how much heterogeneity is to
be expected due to the change in laboratory, study population, and other
factors. An alternative is to take an estimate from the literature, \eg{} from
multisite replication projects or from systematic reviews. Finally, one can also
specify an upper limit of ``tolerable heterogeneity''. This approach is similar
to specifying a minimal clinically relevant difference in classical power
analysis in the sense that a true replication effect size which is intolerably
heterogeneous from the original effect size is not relevant to be detected. An
absolute \citep[ch. 5.7.3]{Spiegelhalter2004} and a relative approach
\citep{Held2020c} can be considered. In the absolute approach, a value of
$\tau^{2}$ is chosen such that a suitable range of study-specific effect sizes
is not larger than an effect size difference considered negligible. For example,
when 95\% of the study specific effect sizes should not vary more than a small
effect size \eg{} $d = 0.2$ on standardized mean difference
scale based on the \citet{Cohen1992} effect size classification, this would lead
to $\tau = d/(2 \cdot 1.96) \approx 0.05$. % Similarly, one
% could consider the distribution of the difference of two effect sizes
% $\theta_{1} - \theta_{2} \given \theta \sim \Nor(0, 2\tau^{2})$ and choose
% $\tau$ such that the, \eg{} the 95\% range is not larger than some desired
% value.
In the relative approach, $\tau^{2}$ is specified relative to the variance of
the original estimate $\sigma^{2}_{o}$ using field conventions for tolerable
relative heterogeneity. For example, in the Cochrane guidelines for systematic
reviews \citep{Deeks2019} a value of
$I^{2} = \tau^{2}/(\tau^{2} + \sigma^{2}_{o}) = 40\%$ is classified as
``negligible'', which translates to
$\tau^{2} = \sigma^{2}_{o}/(1/I^{2} - 1) = (2\sigma^{2}_{o})/3$.

We note that one can also assign a prior distribution to $\tau^2$ \citep[for an
overview of prior distributions for heterogeneity variances in the normal-normal
hierarchical model see][]{Rover2021}. In this case there is no closed-form
expression for the predictive distribution of the replication effect estimate
but numerical or Monte Carlo integration need to be used. % To
% gain more insight, we will thus only consider fixed $\tau^{2}$ in the remaining
% part of the paper.
We illustrate in the supplement how the probability of replication success can
in this case be computed. The derived closed-form expressions conditional on
$\tau^{2}$ are still useful as they enable computation of the predictive
distribution up to a single one-dimensional integral which can be computed
numerically.
% However, a relatively straightforward solution is to first simulate from the
% marginal posterior distribution of $\tau^{2}$ based on an the original data
% $x_{o} = \{\that_{o}, \sigma_{o}\}$ and initial prior for $\theta$ and
% $\tau^{2}$, and then compute the relevant quantity based on the closed-form
% expression conditional on $\tau^{2}$.

\subsubsection{Knowledge about the effect size}
Prior knowledge about the effect size $\theta$ can be incorporated via the prior
mean $\mutheta$ and the prior variance $\sigmatheta^2$ in~\eqref{eq:theta}. For
instance, the parameters may be specified based on a meta-analysis of related
studies \citep{McKinney2021} or based on expert elicitation \citep{OHagan2019}.
The resulting design prior will then contain more information than what was
provided by the original data alone, leading to potentially more efficient
designs. If there is no prior knowledge available, a standard approach is to
specify an (improper) flat prior by letting the variance go to infinity
($\sigmatheta^2 \to \infty$). The resulting design prior will then only contain
the information from the original study.

\subsubsection{Exaggerated original results}
\label{sec:shrinkage}
Potentially exaggerated original results can be counteracted by setting
$\mutheta = 0$ which shrinks the design prior towards smaller effect sizes (in
absolute value) than the observed effect estimate $\that_{o}$. For instance,
replicators could believe that the results from the original study are
exaggerated because there is no pre-registered study protocol available. Even
without such beliefs, weakly informative shrinkage priors may also be motivated
from a ``regularization'' point of view as they can correct for statistical
biases \citep{Copas1983, Firth1993} or prevent unreasonable parameter values
from taking over the posterior in settings with uninformative data
\citep{Gelman2009}.

The amount of shrinkage is determined via the prior variance $\sigmatheta^2$. A
diffuse prior ($\sigmatheta^2 \to \infty$) will lead to no shrinkage, while a
highly concentrated prior ($\sigmatheta^2 \downarrow 0$) will completely shrink
the design prior to a point mass on zero. One option for specifying
$\sigmatheta^2$ is to use an estimate from a corpus of related studies. For
instance, \citet{vanZwet2021} used the Cochrane library of systematic reviews to
specify design priors for hypothetical replication studies of RCTs. If no corpus
is available, a pragmatic alternative is to use the empirical Bayes estimate
based on the original data
\begin{align}
  \label{eq:EBestimate}
  \hat{\sigma}^2_{\scriptscriptstyle{\theta}} = \max\{(\that_{o} - \mutheta)^{2} - \tau^{2} - \sigma^{2}_{o}, 0\}.
\end{align}
The estimate~\eqref{eq:EBestimate} will lead to adaptive shrinkage
\citep{Pawel2020} in the sense that shrinkage is large for unconvincing original
studies (those with small effect estimates in absolute value $|\that_{o}|$
and/or large standard errors $\sigma_{o}$), but disappears as the data become
more convincing (through larger effect estimates in absolute value $|\that_{o}|$
and/or smaller standard errors $\sigma_{o}$).

\subsection{Example: Cross-laboratory replication project}
\label{sec:example}
We will now illustrate the construction of design priors based on data from a
recently conducted replication project \citep{Protzko2020}, see
Figure~\ref{fig:data} for a summary of the data. The data were collected in four
laboratories which, over the course of five years, conducted their typical
social-behavioral experiments on topics such as psychology, communication, or
political science. From the experiments conducted in this period, each lab
submitted four original findings to be replicated. For instance, the original
finding from the ``Labels'' experiment was: ``When a researcher uses a label to
describe people who hold a certain opinion, he or she is interpreted as
disagreeing with those attributes when a negative label is used and agreeing
with those attributes when a positive label is used'' \citep[p.
17]{Protzko2020}, which was based on an effect estimate
$\that_{o} = 0.205$ with 95\% confidence interval from
$0.11$ to $0.3$. For each submitted
original finding, four replication studies were then carried out, one by the
same lab (a \emph{self-replication}) and three by the other three labs (three
\emph{external-replications}).

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=0.97\textwidth]{images/paper3/analysis-protzko-1}
\end{knitrout}
\caption{Data from cross-laboratory replication project by \citet{Protzko2020}.
  Shown are standardized mean difference (SMD) effect estimates with 95\%
  confidence intervals stratified by experiment and laboratory. For each
  replication study, the relative sample size $c = n_{r}/n_{o}$, the one-sided
  replication $p$-value $p_{r}$, the one-sided meta-analytic $p$-value $p_{m}$,
  and the replication Bayes factor $\BFr$ are shown. Experiments are ordered
  (left to right, top to bottom) by their original one-sided $p$-value
  $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$)}
\label{fig:data}
\end{figure}

Most studies used simple between-subject designs with two groups and a
continuous outcome so that for a study $i \in \{o, r\}$ the standardized mean
difference (SMD) effect estimate $\that_{i}$ can be computed from the group
means $\bar{y}_{i1}, \bar{y}_{i2}$, group standard deviations $s_{i1}, s_{i2}$,
and group sample sizes $n_{i1}, n_{i2}$ by
\begin{align*}
  \that_{i} = \frac{\bar{y}_{i1} - \bar{y}_{i2}}{s_{i}}
\end{align*}
with
$s^{2}_{i} = \{(n_{i1} - 1)s_{i1}^{2} + (n_{i2} - 1)s_{i2}^{2}\}/(n_{i1} + n_{i2} - 2)$
the pooled sample variance. Under a normal sampling model and assuming equal
variances in both groups, the approximate variance of $\that_{i}$ is
\begin{align}
  \sigma^{2}_{i} = \frac{n_{i1} + n_{i2}}{n_{i1}n_{i2}} + \frac{\that_{i}^{2}}{2(n_{i1} + n_{i2})}
  \label{eq:varSMD}
\end{align}
\citep{Hedges1981}. A cruder, but for SSD more useful, approximation
$\sigma^{2}_{i} \approx 4/n_{i}$ is obtained by assuming the same sample size in
both groups $n_{i1} = n_{i2} = n_{i}/2$, with $n_{i}$ the total sample size, and
neglecting the second term in~\eqref{eq:varSMD} which will be close to zero for
small effect estimates and/or large sample sizes \citep{Hedges2021}. We thus
have the approximate unit variance $\lambda^{2} = 4$ and the relative variance
$c = \sigma^{2}_{o}/\sigma^{2}_{r} = n_{r}/n_{o}$,
which can be interpreted as the ratio of the replication to the original sample
size.

Suppose now the original studies have been finished, and we want to conduct SSD
for the not yet conducted replication studies. We start by specifying the design
priors (one for each replication). Since the original studies have been
preregistered, we do not expect an exaggeration of their effect estimates due to
selective reporting or other questionable research practices. Therefore, we
choose an uninformative initial prior ($\sigmatheta^{2} \to \infty$), which
leads to design prior and predictive distribution both centered around the
original effect estimate $\that_{o}$.

For specifying the between-study heterogeneity variance $\tau^{2}$, a
distinction needs to be made between self-replications and
external-replications. For self-replications it is reasonable to set
$\tau^{2} = 0$ because we would expect no between-study heterogeneity as the
experimental conditions will be nearly identical in both studies. In contrast,
one would expect some between-study heterogeneity for external-replications as
the experimental conditions may slightly differ between the labs. In the
following, we will use $\tau^{2} = 0.05^{2}$ elicited via
the ``absolute'' approach as discussed previously,
% in Section~\ref{sec:heterogeneity},
so that the range between the 2.5\% and the 97.5\% quantile of the study
specific effect size distribution is equal to a small effect size $d = 0.2$.
% since it is independent of the sample size of the original study.

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/example-design-prior-1}
\end{knitrout}

\caption{Design priors for the effect size $\theta$ (SMD) in the experiment
  ``Labels'' based on the original effect estimate
  $\hat{\theta}_{o} = 0.205$ with standard error
  $\sigma_{o} = 0.051$. Shown are different
  choices for the between-study heterogeneity $\tau$ and the initial prior for
  the effect size $\theta$, ``uninformative'' corresponds to a flat prior,
  ``shrinkage'' corresponds to a zero-mean normal prior with empirical Bayes
  variance estimate~\eqref{eq:EBestimate}, and ``optimistic'' corresponds to a
  flat prior updated by the data from a pilot study with effect estimate
  $\hat{\theta}_{p} = 0.195$ and standard error
  $\sigma_{p} = 0.052$.}
\label{fig:dpexample}
\end{figure}

Taken together, we obtain the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o})$
for self-replications and the design prior
$\theta \given \hat{\theta}_{o}, \sigma^{2}_{o} \sim \Nor(\hat{\theta}_{o}, \sigma^{2}_{o} + \tau^{2})$
with $\tau^{2} = 0.05^{2}$ for external-replications. For
example, for the experiment ``Labels'', the design prior would be
centered around the original effect estimate
$\hat{\theta}_{o} = 0.205$ with variance
$\sigma^{2}_{o} = 0.05^{2}$ for a
self-replication, and with variance
$\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$
for an external-replication. Figure~\ref{fig:dpexample} (dark-gray solid lines)
shows the densities of the two priors.
% Note that power
% calculations under the former prior have been termed ``predictive power''
% \citep{Micheloud2020}, while the latter prior has not appeared in the SSD for
% replication studies literature.

While these two priors seem sensible for the \citet{Protzko2020} data, it is
interesting to think about alternative scenarios. If there had been reasons to
believe that the original result might be exaggerated, we could have specified
an initial shrinkage prior ($\mutheta = 0$ and $\sigmatheta^{2} < \infty$). For
instance, the empirical Bayes estimate for the prior variance $\sigmatheta^{2}$
from~\eqref{eq:EBestimate} leads to a prior whose mean and variance are shrunken
towards zero by $12$\% (medium-gray
dashed lines in Figure~\ref{fig:dpexample}). In contrast, if we had prior
knowledge about the effect size $\theta$ from another study, we could have
specified an initial ``optimistic'' prior. For example, if the self-replication
of the ``Labels'' experiment had been a pilot study and we used its
effect estimate $\hat{\theta}_{p} = 0.195$ and
standard error $\sigma_{p} = 0.05$ to specify
the initial prior, this would lead to a design prior centered around the
weighted mean of original and pilot study, and a prior precision equal to the
sum of the precision of both estimates (light-gray dot-dashed lines in
Figure~\ref{fig:dpexample}). Due to the inclusion of the external data, this
design prior is much more concentrated than the other two.

\subsection{Probability of replication success and required sample size}
To compute the probability of replication success one needs to select an
analysis method and integrate the predictive distribution~\eqref{eq:fthetar}
% , respectively, \eqref{eq:zr}
over the associated success region $S$. There is no universally accepted method
for quantifying replicability and here we do not intend to contribute to the
debate about the most appropriate method. We will simply show the success
regions of different methods, and how the replication sample size can be
computed from them. Some methods depend on the direction of the original effect
estimate $\that_{o}$ and throughout we will assume that it was positive
($\that_{o} > 0$). Functions for computing the probability of replication
success and the required sample size are implemented in the R package
\textbf{BayesRepDesign} (see Appendix) %~\ref{app:package})
for all analysis methods discussed in the following.

\subsubsection{The two-trials rule}
The most common approach for the analysis of replication studies is to declare
replication success when both the original and replication study lead to a
$p$-value for testing the null hypothesis $H_{0} \colon \theta = 0$ smaller than
a pre-specified threshold $\alpha$, usually $\alpha = 5\%$ for two-sided tests
and $\alpha = 2.5\%$ for one-sided tests. This procedure is known as the
\emph{two-trials rule} in drug regulation \citep{Senn2008}.

We now assume that the one-sided original $p$-value was significant at some
level $\alpha$, \ie{} $p_{o} = 1 - \Phi(\that_{o}/\sigma_{o}) \leq \alpha$.
Replication success at level $\alpha$ % with the two-trials
is then achieved if the replication $p$-value is also significant, \ie{}
$p_{r} = 1 - \Phi(\that_{r}/\sigma_{r}) \leq \alpha$, which implies a success
region
\begin{align*}
  S_{\scriptscriptstyle \text{2TR}}
  = \left[\zalpha\, \sigma_{r}, \infty \right),
\end{align*}
where $\zalpha$ is the $1 - \alpha$ quantile of the standard
normal distribution. The probability of replication success is thus given by
\begin{align}
  \label{eq:2TRpros}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
  = % \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sqrt{\sigma^{2}_{r} +
  % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right)
  \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sigmathatr}\right)
\end{align}
with $\Phi(\cdot)$ the standard normal cumulative distribution function and
$\muthatr$ and $\sigmathatr$ the mean and standard deviation of the predictive
distribution~\eqref{eq:fthetar}. %, the latter also depending on $\sigma_{r}$.
Importantly, by decreasing the standard error $\sigma_{r}$ (through increasing
the sample size $n_{r}$), the probability of replication
success~\eqref{eq:2TRpros} cannot become arbitrarily large but is bounded from
above by
\begin{align}
  \label{eq:limP2TR}
  \text{limPr}_{\scriptscriptstyle \text{2TR}} =
  \Phi\left(\frac{ \muthatr}{\sqrt{
\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
\end{align}
The required replication standard error $\sigma_{r}^{*}$ to achieve a target
probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{2TR}}$ can now be obtained
by equating~\eqref{eq:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
leads to
\begin{align}
  \label{eq:ssd2tr}
  \sigma_{r}^{*} =
  \frac{\muthatr \zalpha - \zbeta\sqrt{
  (\zalpha^{2} - \zbeta^{2})\left\{\tau^{2} + (\sigma^{2}_{o} +
  \tau^{2})/(1 + 1/g)\right\} + \muthatr^{2}}}{\zalpha^{2} - \zbeta^{2}}
\end{align}
for $\alpha < \beta$. The standard error $\sigma_{r}^{*}$ can subsequently be
translated in a sample size. The translation depends on the type of effect size,
for instance, for SMD effect sizes we can use the approximation
$n_{r}^{*} \approx 4/(\sigma^*_{r})^{2}$ from
earlier. %Section~\ref{sec:example}.
Moreover, by assuming a standard error of the form
$\sigma_{r} = \lambda/\sqrt{n_{r}}$ and plugging in the parameters of the
``conditional'' design prior %from Section~\ref{sec:designpredictive}
($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$), we obtain the
well-known sample size formula \citep[ch. 3.3]{Matthews2006}
\begin{align*}
  n_{r}^{*} = \frac{(\zalpha + \zbeta)^{2}}{(\that_{o}/\lambda)^{2}}
\end{align*}
for a one-sided significance test at level $\alpha$ with power $1 - \beta$ to
detect the original effect estimate $\that_{o}$. The formula~\eqref{eq:ssd2tr}
thus generalizes standard sample size calculation to take into account the
uncertainty of the original estimate, between-study heterogeneity and other
types of external knowledge.

\subsubsection{Fixed effects meta-analysis}
The data from the original and replication studies are sometimes pooled via
fixed-effects meta-analysis. The pooled effect estimate $\that_{m}$ and standard
error $\sigma_{m}$ are then given by
\begin{align*}
  &\that_{m} =
    \left(\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r}\right)\sigma^{2}_{m}&
&\text{and}&                                                                                       &\sigma_{m} = \left(1/\sigma^{2}_{o} + 1/\sigma^{2}_{r}\right)^{-1/2},&
\end{align*}
and they are also equivalent to the mean and standard deviation of a posterior
distribution for the effect size $\theta$ based on the data from both studies
and an initial flat prior for $\theta$. The success
region %for the replication effect estimate $\that_{r}$
\begin{align}
  \label{eq:SMA}
  S_{\scriptscriptstyle \text{MA}}
  = \left[\sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}} -
  (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o},
  \infty \right)
\end{align}
then corresponds to both replication success defined via a one-sided
meta-analytic $p$-value being smaller than level $\alpha$, \ie{}
$p_{m} = 1 - \Phi(\that_{m}/\sigma_{m}) \leq \alpha$, or to replication success
defined via a Bayesian posterior probability
$\Pr(\theta > 0 \given \that_{o}, \that_{r}, \sigma_{o}, \sigma_{r}) \geq 1 - \alpha$.
Based on the success region~\eqref{eq:SMA} and an assumed standard error
$\sigma_{r}$, the probability of replication success can be computed by
\begin{align}
  \label{eq:MApros}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{MA}} \given \that_{o}, \sigma_{o}, \sigma_{r})
  = % \Phi\left(\frac{\muthatr - \sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}}
%   + (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o}}{\sqrt{\sigma^{2}_{r} +
%   \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
  \Phi\left(\frac{\muthatr - \sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}}
  + (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o}}{\sigmathatr}\right).
\end{align}
As for the two-trials rule, the probability~\eqref{eq:MApros} cannot be made
arbitrarily large by decreasing the standard error $\sigma_{r}$ but is bounded
from above by $\text{limPr}_{\text{2TR}}$ defined in~\eqref{eq:limP2TR}.
% However, as the original data already provide some information, the
% probability of replication success is also bounded from below.
The required standard error $\sigma_{r}^{*}$ to achieve a target probability of
replication success $1 - \beta < \text{limPr}_{\text{2TR}}$ can be computed
numerically using root finding algorithms.

\subsubsection{Effect size equivalence test}
% Both the two-trials rule and the fixed effects meta-analysis approach define
% replication success via measures of evidence against the null hypothesis
% $H_{0} \colon \theta = 0$. Other approaches define replication success via
% compatibility of the effect estimates from original and replication study. For
% instance,
\citet{Anderson2016} proposed a method for quantifying replicability based on
effect size equivalence. Under normality, replication success at level $\alpha$
is achieved if the $(1 - \alpha)$ confidence interval for the effect size
difference $\theta_{r} - \theta_{o}$
\begin{align*}
  \that_{r} - \that_{o} \pm \zalphatwo \sqrt{\sigma^{2}_{r} + \sigma^{2}_{o}}
\end{align*}
is fully inside an equivalence region $[-\Delta, \Delta]$ defined via the
pre-specified margin $\Delta > 0$. This procedure corresponds to rejecting the
null hypothesis $H_{0} \colon |\theta_{r} - \theta_{o}| > \Delta$ in an
equivalence test, and it implies a success region for the replication effect
estimate $\that_{r}$ given by
\begin{align}
  \label{eq:equivalence}
  S_{\scriptscriptstyle \text{E}}
  = \left[\that_{o} - \Delta + \zalphatwo \sqrt{\sigma^{2}_{o} +
  \sigma^{2}_{r}}, \that_{o} + \Delta - \zalphatwo
  \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}}\right]
\end{align}
for $\Delta \geq \zalphatwo \sqrt{\sigma_{o}^{2} + \sigma^{2}_{r}}$. For too
small margins ($\Delta < \zalphatwo \sqrt{\sigma_{o}^{2} + \sigma^{2}_{r}}$),
the success region~\eqref{eq:equivalence} becomes the empty set meaning that
replication success is impossible.
% Typically the original study is already conducted but the standard error of the
% replication study can still be changed
% Whether or
% not replication success is achievable depends on the standard error of the
% original estimate $\sigma_{o}$, and in particular when the margin is chosen too
% small ($\Delta \leq \zalphatwo \sigma_{o}$), replication success is impossible
% regardless of how small the replication standard error $\sigma_{r}$ will be.
Assuming now that the margin is large enough,
% ($\Delta \geq \zalphatwo \sqrt{\sigma_{o}^{2} + \sigma^{2}_{r}}$),
the probability
of replication success can be computed by
\begin{align}
  \label{eq:porsEqu}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{E}} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &= % \Phi\left(\frac{\that_{o} + \Delta - \zalphatwo
%   \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}} -\muthatr}{\sqrt{\sigma^{2}_{r} +
%   \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right) \nonumber \\
% &\phantom{=} -
%   \Phi\left(\frac{\that_{o} - \Delta + \zalphatwo
%   \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}} -\muthatr}{\sqrt{\sigma^{2}_{r} +
%   \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
    \Phi\left(\frac{\that_{o} + \Delta - \zalphatwo
  \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}} -\muthatr}{\sigmathatr}\right) \nonumber \\
&\phantom{=} -
  \Phi\left(\frac{\that_{o} - \Delta + \zalphatwo
  \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}} -\muthatr}{\sigmathatr}\right).
\end{align}
As with the previous methods, the probability~\eqref{eq:porsEqu} cannot be made
arbitrarily large by decreasing the replication standard error $\sigma_{r}$, but
is bounded by
\begin{align*}
  \text{limPr}_{\scriptscriptstyle \text{E}} =
  \Phi\left(\frac{\that_{o} + \Delta - \zalphatwo\sigma_{o}
  -\muthatr}{\sqrt{\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right)
  -\Phi\left(\frac{\that_{o} - \Delta + \zalphatwo\sigma_{o}
  -\muthatr}{\sqrt{\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
\end{align*}
The required replication standard error $\sigma_{r}^{*}$ to achieve a target
probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{E}}$ can again be computed
numerically.

\subsubsection{The replication Bayes factor}
A Bayesian hypothesis testing approach for assessing replication success was
proposed by \citet{Verhagen2014} and further developed by \citet{Ly2018}. They
define a ``replication Bayes factor''
\begin{align*}
  \BFr = \frac{f(x_{r} \given H_{0})}{f(x_{r} \given H_{1})}
\end{align*}
which is the ratio of the marginal likelihoods of the replication data $x_{r}$
under the null hypothesis $H_{0} \colon \theta = 0$ to the marginal likelihood
of $x_{r}$ under the alternative hypothesis
$H_{1} \colon \theta \sim f(\theta \given x_{o})$, that is the posterior of the
effect size $\theta$ based on the original data $x_{o}$. If the original study
provides evidence against the null hypothesis, replication Bayes factor values
$\BFr < 1$ indicate replication success, and the smaller the value the higher
the degree of success.

Under normality and assuming no heterogeneity, the success region for achieving
$\BFr \leq \gamma$ is given by
\begin{align}
  \label{eq:BFrsuccess}
  S_{\scriptscriptstyle \BFr}
  = \left(-\infty, -\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}\right] \bigcup
   \left[\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}, \infty\right)
\end{align}
with
$A = \sigma^{2}_{r}(1 + \sigma^{2}_{r}/\sigma^{2}_{o}) \{\that_{o}^{2}/\sigma^{2}_{o} - 2 \log \gamma + \log(1 + \sigma^{2}_{o}/\sigma^{2}_{r})\}$.
Details of this calculation are given in the supplement. The fact that the
success region~\eqref{eq:BFrsuccess} is defined on both sides around zero shows
that replication success is also possible if the replication effect estimate
goes in opposite direction of the original one, which is known as the
``replication paradox'' \citep{Ly2018}. The paradox can be avoided using a
modified version of the replication Bayes factor but the success region is no
longer available in closed-form \citep[Appendix D]{Pawel2022b}. Based on the
success region~\eqref{eq:BFrsuccess}, the probability of replication success can
be computed by
\begin{align}
  \label{eq:BFrpros}
  \Pr(\that_{r} \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &=%  \Phi\left(\frac{\muthatr - \sqrt{A} + (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}}{\sqrt{\sigma^{2}_{r} +
%     \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right) \nonumber \\
%   &\phantom{=}
%     + \Phi\left(\frac{-\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}
% - \muthatr}{\sqrt{\sigma^{2}_{r} +
% \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right).
      \Phi\left(\frac{\muthatr - \sqrt{A} + (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}}{
      \sigmathatr}\right)
    + \Phi\left(\frac{-\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}
- \muthatr}{\sigmathatr}\right).
\end{align}
One may want to compute the probability of replication success only for the part
of the success region with the same sign as the original effect estimate to
avoid the replication paradox. As for the other methods, the
probability~\eqref{eq:BFrpros} is bounded from above by a constant
$\text{limPr}_{\scriptscriptstyle \BFr} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})$,
and root finding algorithms can be used to numerically determine the required
standard error $\sigma^{*}_{r}$ for achieving a target probability of
replication success $1 - \beta < \text{limPr}_{\scriptscriptstyle \BFr}$.

\subsubsection{The skeptical \textit{p}-value}
\citet{Held2020} proposed a reverse-Bayes approach for quantifying replication
success. The main idea is to determine the variance of a ``skeptical'' zero-mean
normal prior for the effect size $\theta$ such that its posterior distribution
based on the original study is no longer credible. Replication success is then
achieved if the replication data are in conflict with the skeptical prior. The
procedure can be summarized by a ``skeptical $p$-value'' $\ps$, and the lower
the $p$-value the higher the degree of replication success. \citet[sec.
2.1]{Held2021} showed that the success region for replication success defined by
$\ps \leq \alpha$ is given by
\begin{align}
  \label{eq:Pssuccess}
  S_{\scriptscriptstyle \ps}
  = \left[\zalpha \sqrt{\sigma^{2}_{r} +
  \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}}, \infty\right).
\end{align}
From the success region~\eqref{eq:Pssuccess} the probability of replication
success at level $\alpha$ is
\begin{align*}
  \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})
  &=%  \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    % \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sqrt{\sigma^{2}_{r} +
    % \tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g)}}\right),
     \Phi\left(\frac{\muthatr - \zalpha \sqrt{\sigma^{2}_{r} +
    \sigma^{2}_{o}/\{(z_{o}^{2}/\zalpha^{2}) - 1}\}}{\sigmathatr}\right),
\end{align*}
and also bounded from above by a constant
$\text{limPr}_{\scriptscriptstyle \ps} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})$.
As for the two-trials rule, the required standard error $\sigma_{r}^{*}$ to
achieve a probability of replication success
$1 - \beta < \text{limPr}_{\scriptscriptstyle \ps}$ can be computed analytically
for $\alpha < \beta$:
\begin{align*}
  \sigma_{r}^{*} = \sqrt{x^{2} - \frac{\sigma^{2}_{o}}{(z_{o}/\zalpha)^{2} - 1}}
\end{align*}
with
\begin{align*}
  x = \frac{\zalpha \muthatr - \zbeta \sqrt{\muthatr^{2} - (\zalpha^{2} - \zbeta^{2})
  [\tau^{2} + (\sigma^{2}_{o} + \tau^{2})/(1 + 1/g) - \sigma^{2}_{o}/\{(z_{o}/\zalpha)^{2}
  - 1\}]}}{\zalpha^{2} - \zbeta^{2}}.
\end{align*}

\subsubsection{The skeptical Bayes factor}
\citet{Pawel2022b} modified the previously described reverse-Bayes assessment of
replication success from \citet{Held2020} to work with Bayes factors instead of
tail probabilities as measures of evidence and prior data conflict. Again, the
procedure can be summarized in a single measure termed the ``skeptical Bayes
factor'' $\BFs$, with lower values of $\BFs$ pointing to higher degrees of
replication success. Also for this method, the success region and the
probability of replication success can be expressed in closed-form but the
derivations are more involved than for the other methods. For this reason, they
are only given in the supplement.

\subsection{Example: Cross-laboratory replication project (continued)}

%

We will now revisit the experiment ``Labels'' % from
% Section~\ref{sec:example}
and compute the probability of replication success.
% and
% the replication sample size
% based on the previously discussed analysis methods.
The parameters of the analysis methods are specified as follows: For the
two-trials rule we use the conventional one-sided significance level
$\alpha = 0.025$, while for meta-analysis we use the more
stringent level $\alpha = 0.025^{2}$ as the
method is based on two data sets rather than one. We use a
$1 - \alpha = 90\%$ confidence interval which is
conventionally used in equivalence testing, along with a margin
$\Delta = 0.2$ corresponding to a small SMD effect size according to
the classification from \citet{Cohen1992}. For the skeptical $p$-value we use
the recommended ``golden'' level $\alpha = 0.062$ as it
guarantees that for original studies which where just significant at
$\alpha = 0.025$ replication success is only possible if the replication effect
estimate is larger than the original one \citep{Held2021}. Finally, for the
replication Bayes factor and the skeptical Bayes factor we use the ``strong
evidence'' level $\gamma = 1/10$ from \citet{Jeffreys1961}.

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/example-applied-1}
\end{knitrout}
\caption{Probability of replication success as a function of relative sample
  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original
  effect estimate $\hat{\theta}_{o} = 0.205$ and
  standard error $\sigma_{o} = 0.051$ for
  different initial prior parameters ($\tau, \mutheta, \sigmatheta^{2}$). The
  probability of replication success with the design prior
  $\tau = 0, \mutheta = 0$, and $\sigmatheta^{2} = 0$ (right plot) corresponds
  to the type I error rate under the fixed effects null hypothesis
  ($H_{0}\colon \theta = 0, \tau^{2} = 0$). Replication success is defined by
  the two-trials rule at level $\alpha = 0.025$, the replication
  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
  analysis at level $\alpha = 0.025^{2}$, effect size
  equivalence based on $90\%$ confidence interval and with
  margin $\Delta = 0.2$, skeptical $p$-value at level
  $\alpha = 0.062$, and skeptical Bayes factor at level
  $\gamma = 1/10$.}
\label{fig:example}
\end{figure}
Figure~\ref{fig:example} shows the probability of replication success as a
function of the relative sample size $c = n_{r}/n_{o}$ and for different initial
priors. The left and middle plot are based on an uninformative prior for the
effect size ($\sigmatheta^{2} \to \infty$) without heterogeneity ($\tau^{2} = 0$)
and with heterogeneity ($\tau^{2} = 0.05^{2}$),
respectively. The right plot shows the prior corresponding to the ``fixed
effects null hypothesis'' $H_{0} \colon \theta = 0, \tau^{2} =
0$, %, \ie{} the effect size
% $\theta$ is a point mass at zero and there is no heterogeneity,
so that the probability of replication success is the type I error rate which
some stakeholders might require to be ``controlled'' at some adequate level.

We see from the left and middle plots that increasing the relative sample size
monotonically increases the probability of replication success for all methods
but meta-analysis (light blue). Meta-analysis shows a non-monotone behavior
because the original study was already highly significant so that the pooled
effect estimate is significant even for replication studies with very small
sample size \citep{Micheloud2020}. The uncertainty regarding the replication
effect estimate $\that_{r}$ may therefore even reduce the probability of
replication success for meta-analysis if the sample size is increased. If
heterogeneity is taken into account (middle plot) the probability of replication
success becomes closer to 50\% for all methods but the equivalence test,
reflecting the larger uncertainty about the effect size $\theta$. To achieve
$80\%$ probability of replication success the fewest
samples are required with meta-analysis, followed by the skeptical $p$-value,
the two-trials rule, the replication Bayes factor, the skeptical Bayes factor,
and lastly the equivalence test. If the chosen sample size should guarantee a
sufficiently conclusive replication study with all these methods, the
replication sample size has to be slightly larger than the original one in the
situation of no heterogeneity ($\tau^{2} = 0$), while it has to be increased
more than ten-fold if there is heterogeneity
($\tau^{2} = 0.05^{2}$). However, this is mostly due to the
equivalence test which requires by far the most samples. If the equivalence test
sample size is ignored, the relative sample size
$c = 2.5$ ensures at least
$80\%$ probability of replication success with the
remaining methods.

The right plot in Figure~\ref{fig:example} shows that the type I error rate of
the two-trials rule (black) stays constant at
$\alpha = 0.025$, as expected by definition of the method.
In contrast, the type I error rates of the other methods vary with the relative
sample size $c$ but most of them stay below
$\alpha = 0.025$ for all $c$ with the exception of
meta-analysis and the skeptical $p$-value. Meta-analysis (light blue) has an
extremely high type I error rate as the pooling with the highly significant
original data leads to replication success if the replication sample size is not
drastically increased. The type I error rate of the skeptical $p$-value (yellow)
is only slightly larger than $\alpha = 0.025$ which is
expected since the level $\alpha = 0.062$ is used for
declaring replication success with the skeptical $p$-value, and its type I error
rate is always smaller than the level for thresholding it \citep{Held2020}. The
type I error rate of the skeptical $p$-value decreases to values smaller than
$\alpha = 0.025$ of the two-trials rule at approximately
$c = 3$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/ssd-protzko-1}
\end{knitrout}
\caption{The left plot shows the required relative sample size $c = n_r/n_o$ to
  achieve a target probability of replication success of
  $1 - \beta = 80$\% (if possible). Replication success
  is defined through the two-trials rule at level $\alpha = 0.025$,
  replication Bayes factor at level $\gamma = 1/10$, fixed
  effects-meta analysis at level $\alpha = 0.025^{2}$,
  effect size equivalence at level $\alpha = 0.1$ with margin
  $\Delta = 0.2$, skeptical $p$-value at level
  $\alpha = 0.062$, and skeptical Bayes factor at level
  $\gamma = 1/10$ for data from the replication project by
  \citet{Protzko2020}. A flat initial prior
  ($\mutheta = 0, \sigmatheta^{2} \to \infty$) is used for the effect size
  $\theta$ is used either without ($\tau = 0$) or with heterogeneity
  ($\tau = 0.05$). The right plot shows the type I error
  rate associated with the required sample size. Experiments are ordered (top to
  bottom) by their original one-sided $p$-value
  $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
\label{fig:ssd-all}
\end{figure}

We now conduct SSD for all studies from the replication project of
\citet{Protzko2020}. Figure~\ref{fig:ssd-all} shows the required relative sample
size and the associated type I error rates if a sample size can be computed for
a probability of replication success of
$1 - \beta = 80$\%. If there is no sample size for
which a probability of $80$\% can be achieved the space
is left blank. This is, for instance, the case for the meta-analysis method for
all studies below the ``Labels'' experiment as the probability stays above
$80$\% for any relative sample size. % for the
% studies which were significant at level $\alpha = levelSig$ (so that
% they can fulfill the two-trials rule).

We see that for all methods but the equivalence test the required relative
sample size $c$ decreases with decreasing original $p$-value $p_{o}$, and
original studies with very small $p$-values require much fewer samples in the
replication study. For the equivalence test, the required sample size depends
instead on the size of the original standard error $\sigma_{o}$, and smaller
standard errors leads to smaller required sample sizes in the
replication. % For instance, the
% experiment ``Orientation'' with the original standard error $\sigma_{o} = 0.045$
% requires much less samples than the experiment ``Self-Control'' with original
% standard error $\sigma_{o} = 0.052$.
We also see that taking into account heterogeneity (triangle) increases the
required sample size for all methods compared to not taking it into account
(dot). At the same time, a larger required sample size reduces the type I error
rate for most methods. We see again the pattern that the type I error rate of
the equivalence test and the skeptical $p$-value is larger than the type I error
rate 2.5\% of the two-trials rule. However, while the type I error rate of the
skeptical $p$-value decreases when replication studies require larger sample
sizes, the type I error rate of the equivalence test may also be large if the
replication requires very large sample sizes (\eg{} for the experiment ``FSD'')
since it depends on whether the original effect estimate $\that_{o}$ is
sufficiently different from zero. If the original effect estimate $\that_{o}$ is
close to zero, the type I error rate of the equivalence test is drastically
increased as equivalence can also be established if the effect estimates from
original and replication studies are close to zero (as under the null
hypothesis).

Taken together, for most of the experiments all methods but the equivalence test
require fewer samples in the replication than in the original study to achieve a
target probability of replication success
$1 - \beta = 80$\%. This is still the case if
heterogeneity is taken into account in the design prior (triangles), which
generally increases the required sample size compared to when heterogeneity is
not taken into account (dots), especially for studies with large original
$p$-value. Larger replication sample sizes are required for some original
studies. In some cases these are unrealistically large (\eg{} in the experiment
``Prediction'' an almost 30 times increase in sample size for the replication
Bayes factor), but in other cases they seem more realistic and could be
reallocated from the other studies which require fewer samples (\eg{} in the
experiment ``Referrals'' an almost three times increase for the skeptical Bayes
factor). On the other hand, the equivalence test typically requires larger
sample sizes in the replication because the original standard errors are large
relative to the specified margin. If one anticipates to analyze the original and
replication pair with an equivalence test, this should therefore be taken into
account already at the design stage of the original study.

\subsection{Sample size determination for multisite replication projects}
So far we considered the situation where a pair of a single original and a
single replication study are analyzed in isolation. However, if multiple
replications per single original study are conducted (so-called \emph{multisite}
replication studies) the ensemble of replications can also be analyzed jointly.
In this case, some adaptations of the SSD methodology are required.

The replication effect estimate and its standard error are now vectors
$\bthat_{r} = (\that_{r1}, \dots, \that_{rm})^{\top}$ and
$\bsigma^{2}_{r} = (\sigma^{2}_{r1}, \dots, \sigma^{2}_{rm})^{\top}$ consisting
of $m$ replication effect estimates, respectively, their standard errors. The
normal hierarchical model for the replication estimates $\bthat_{r}$ then
becomes
\begin{subequations}
\label{eq:hierarch-model2}
\begin{align}
  \bthat_r \given \mspace{-1mu} \btheta_r &\sim \Nor_{m}\left\{\btheta_r, \text{diag}\left(\bsigma_r^2\right)\right\}
  \label{eq:hat_theta_k22} \\
  \btheta_r \given \theta \,\,  &\sim \Nor_{m}\left\{\theta \, \bone_{m},
  \tau^2 \text{diag}(\bone_{m})\right\}, \label{eq:theta_k2}
\end{align}
\end{subequations}
where $\btheta_{r}$ is a vector of $m$ study specific effect sizes, $\bone_{m}$
is a vector of $m$ ones, and $\Nor_{m}(\boldsymbol{\mu}, \boldsymbol{\Sigma})$
denotes the $m$-variate normal distribution with mean vector $\boldsymbol{\mu}$
and covariance matrix $\boldsymbol{\Sigma}$. By marginalizing over the study
specific effect size $\btheta_{k}$, the model can alternatively be expressed by
\begin{align}
  \bthat_r \given \theta \sim \Nor_{m}\left\{\theta \, \bone_{m},
\text{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right)\right\},
  \label{eq:margimulti}
\end{align}
so the predictive distribution of $\bthat_r$ based on the design
prior~\eqref{eq:dpnormal} is given by
\begin{align}
  \bthat_r \given \hat{\theta}_o, \sigma^{2}_{o}, \bsigma^{2}_{r}
  \sim \Nor_{m}\left\{\muthatr \bone_{m},
  \text{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right) +
  \left(\frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g}\right)
  \bone_{m} \bone_{m}^{\top} \right\}
  \label{eq:ftrmulti}
\end{align}
with $ \muthatr$ the mean of the predictive distribution of a single replication
effect estimate from~\eqref{eq:fthetar}. Importantly, the replication effect
estimates are correlated as the covariance matrix in~\eqref{eq:ftrmulti} has
$(\tau^2+\sigma^{2}_{o})/(1 + 1/g)$ in the off-diagonal entries.

Often the assessment of replication success can be formulated in terms of a
weighted average of the replication effect estimates
$\hat{\theta}_{r*} = (\sum_{i = 1}^{m} w_{i} \hat{\theta}_{ri})/(\sum_{i = 1}^{m} w_{i})$
with $w_{i}$ the weight of replication $i$. For instance, several multisite
replication projects \citep[\eg][]{Klein2018} have defined replication success
by the fixed or random effects meta-analytic effect estimate of the replication
effect estimates achieving statistical significance. Based on the predictive
distribution of the replication effect estimate vector~\eqref{eq:ftrmulti}, the
predictive distribution of the weighted average $\hat{\theta}_{r*}$ is given by
\begin{align}
  \hat{\theta}_{r*} \given \hat{\theta}_o, \sigma^{2}_{o}, \bsigma^{2}_{r}
  \sim \Nor\Biggl\{
  \mu_{\scriptscriptstyle \that_{r}},
  \sigma^{2}_{\scriptscriptstyle \that_{r*}} =
  \biggl(\sum_{i=1}^{m} w_{i}^{2} \sigma^{2}_{\scriptscriptstyle \that_{ri}} +
  \sum_{i=1}^{m}\sum_{\substack{j =1 \\ j\neq i}}^{m} w_{i}w_{j}
\frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g} \biggr)\big/\biggl(\sum_{i=1}^{m} w_{i}\biggr)^{2} \Biggr\}
  \label{eq:ftwm}
\end{align}
with $\sigma^{2}_{\scriptscriptstyle \that_{ri}}$ the predictive variance of a
single replication effect estimate with standard error $\sigma_{ri}$ as
in~\eqref{eq:fthetar}. In particular when the studies receive equal weights
($w_{i} = w$ for $i = 1, \dots, m$) and the standard errors of the replication
effect estimates are equal ($\sigma_{ri} = \sigma_{r}$ for $i = 1, \dots, m$),
the predictive variance becomes
\begin{align}
  \sigma^{2}_{\scriptscriptstyle \that_{r*}} =
  % \left(\sigma^{2}_{\scriptscriptstyle \that_{r}} + (n - 1) \frac{g}{g + 1} [\tau^{2} + \sigma^{2}_{o}]\right) \big/ n.
  \frac{\sigma^{2}_{r} + \tau^{2}}{m} + \frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g}.
  \label{eq:predvarequal}
\end{align}
The probability of replication success can now be obtained by
integrating~\eqref{eq:ftrmulti}, respectively~\eqref{eq:ftwm}, over the
corresponding success region $S$. This may be more involved if the success
region is defined in terms of the replication effect estimate vector
$\bthat_{r}$, whereas it is as simple as in the singlesite replication case if
the success region is formulated in terms of the weighted average $\that_{r*}$.

\subsubsection{Optimal allocation within and between sites}
A key challenge in SSD for multisite replication studies is the optimal
allocation of samples within and between sites, that is, how many sites $m$ and
how many samples $n_{ri}$ per site $i$ should be used. A similar problem exists
in SSD for cluster randomized trials and we can adapt the common solution based
on cost functions \citep{Raudenbush1997}. %\citep[ch. 9.6]{Cochran1977}.
That is, the optimal configuration is determined so that the probability of
replication success is maximized subject to a constrained cost function which
accounts for the (typically different) costs of additional samples and sites.

For example, assume a balanced design ($n_{ri} = n_{r}$ for $i = 1, \dots, m$)
and that the standard errors of the replication effect estimates are inversely
proportional to the square-root of the sample size
$\sigma_{ri} = \lambda/\sqrt{n_{r}}$ for some unit variance $\lambda^{2}$.
Further assume that maximizing the probability of replication success
corresponds to minimizing the variance of the weighted average
$\sigma^{2}_{\scriptscriptstyle \that_{r*}}$ in~\eqref{eq:predvarequal}. % This
% is, for instance, the case if the analysis consists of computing a $p$-value for
% the weighted average.
Let $K_{s}$ denote the cost of an additional site, and $K_{c}$ the cost of an
additional sample/case. The total cost of the project is then
$K = m(K_{c} \, n_{r} + K_{s})$, and constrained minimization of the predictive
variance~\eqref{eq:predvarequal} leads to the optimal sample size per site
\begin{align*}
  n_{r}^{*} =  \frac{\lambda}{\tau} \, \sqrt{\frac{K_{s}}{K_{c}}}
\end{align*}
which is equivalent to the optimal cluster sample size known from cluster
randomized trials \citep{Raudenbush2000}. Note that the optimal sample size per
site may be different for other analysis approaches where maximizing the
probability of replication success does not correspond to minimizing the
variance of the weighted average. % \citep[for optimal
% % sample sizes for estimation of between replication variances see
% % \eg][]{Hedges2021}.
% % For example, \citet{Hedges2021}
% % found that the optimal sample size for between study variance estimation is
% % given by
% % \begin{align*}
% %   n_{r}^{*} =  \frac{1 + \sqrt{1 + 8\tau^{2} K_{s}/K_{i}}}{2 \tau^{2}/\lambda^{2}}.
% % \end{align*}
Moreover, there are also practical considerations which affect the choice of how
many sites should be included in a project. For instance, there may simply not
be enough labs available with the required expertise to perform the replication
experiments.

\subsection{Example: Cross-laboratory replication project (continued)}
Figure~\ref{fig:multisite} illustrates multisite SSD for the experiment
``Labels'' from \citet{Protzko2020} for planned analyses based on the
two-trials rule and the replication Bayes factor (see the supplement for details
on the multisite extension of these two methods). As for singlesite SSD, we use
the design prior based on an initial flat prior for the effect size and taking
into account heterogeneity ($\tau = 0.05$). The top
plots show the probability of replication success as a function of the total
sample size $m \times n_{r}$ for different number of sites $m$. We see that for
the same total sample size a larger number of sites increases the probability of
replication success. For instance, a total sample size of roughly 3000 is
required to achieve an 80\% target probability with one site %(yellow)
for the two-trials rule, whereas only approximately half as many samples are
required for two sites. %(green).

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{images/paper3/multisite-protzko-1}
\end{knitrout}
\caption{Top plots show the probability of replication success based on the
  replication Bayes factor at level $\gamma = 1/10$ (left) and the
  two-trials rule at level $\alpha = 0.025$ (right) as a function of
  the total sample size and for different number of sites $m$ for data from the
  experiment ``Labels''. A design prior with heterogeneity
  $\tau = 0.05$ and flat initial prior for the effect size
  $\theta$ is used. The same heterogeneity value is assumed in the analysis of the
  replications. %($\tau_{r} = \tau$). Bottom plot shows the total cost $K$ of the
  design (relative to the cost of a single sample $K_{c}$) as a function of the
  number of sites $m$ and for different site costs $K_{s}$. The sample size of
  each design corresponds to a target probability of replication success
  $1 - \beta = 80$\%.}
\label{fig:multisite}
\end{figure}

However, focusing only on the total sample size ignores the fact that the cost
of an additional site is usually larger than the cost of an additional
observation. The bottom plot shows the total cost $K$ of a design (relative to
the cost of one sample $K_{c}$) whose sample size is determined for a target
probability of replication success $1 - \beta = 80$\%.
We see that if the cost of an additional site $K_{s}$ is not much larger than
the cost of an additional sample $K_{c}$, \eg{} $K_{S}/K_{c} = 30$ %(yellow)
the optimal number of sites is $m = 5$ for the two-trials rule and $m = 8$ for
the replication Bayes factor. If an additional site is more costly the optimal
number of sites is lower, \eg{} if the cost ratio is $K_{S}/K_{c} = 300$,
% (purple),
the optimal number of sites is $m = 2$ for the two trials rule and $m = 3$ for
the replication Bayes factor. This is similar to the actually used number of
sites $m = 3$ (counting only external-replications), respectively, $m = 4$
(counting also the internal-replication) from \citet{Protzko2020}.

\section{Discussion}
\label{sec:discussion}

We showed how Bayesian approaches can be used to determine the sample size of
replication studies based on all the available information and the associated
uncertainty. % The Bayesian framework allows to make use of all the available
% information, and to take into account the associated uncertainty.
A key strength of the approach is that it can be applied to any kind of
replication analysis method, Bayes or non-Bayes, as long as there is a
well-defined success region for the replication effect estimate. Methods for
assessing replication success which have not yet been adapted to Bayesian design
approaches in the normal-normal hierarchical model (or which have not even been
proposed) can thus benefit from our methodology. For instance, our methods could
be straightforwardly applied to the ``dual-criterion'' from
\citet{Rosenkranz2021} which defines replication success via simultaneous
statistical significance and practical relevance of the effect estimates from
original and replication study.

There are some limitations and possible extensions: we have developed the
methodology for ``direct'' replication studies \citep{Simons2014} which attempt
to replicate the conditions from the original study as closely as possible; yet
SSD methodology is also needed for ``conceptual'' replication and for
``generalization'' studies which may show systematic deviations from the
original study. While the heterogeneity variance in the design prior allows to
take effect size heterogeneity into account for SSD, to some extent, further
research is needed for investigating how systematic study deviations and
external knowledge can be incorporated. Furthermore, as is standard in
meta-analysis we assumed that the variances of the effect estimates are known,
which can sometimes be inadequate \citep{Jackson2018}. Specifying priors also
for the variances could better reflect the available uncertainty but would come
at the price of lower interpretability and higher computational complexity. We
did also not consider designs where the replication data are analyzed in a
sequential manner. Ideas from the Bayesian sequential design
\citep{Schoenbrodt2017, Stefan2022} or from the adaptive trials literature
\citep{Bretz2009} could be adapted to the replication setting as in
\citet{Micheloud2020}. A sequential analysis of the replication data could
possibly increase the efficiency of the replication. An additional point is that
we assumed that the original study has been completed when planning the
replication study. One could also consider a scenario where both the original
and replication study are planned simultaneously and adopt a ``project''
perspective \citep{Maca2002, Held2021}. However, in this case no information from
the original study is available and the design prior needs to be specified
entirely based on external knowledge. Finally, researchers have only limited
resources and it may happen that they cannot afford a large enough sample size
to obtain their desired probability of replication success. In this situation a
reverse-Bayes approach \citep{Held2021b} could be applied in order to determine
the prior for the effect size which is required to achieve the desired
probability of replication success based on the maximally possible sample size.
Researchers can then judge whether or not such prior beliefs are scientifically
sensible, and decide whether they should conduct the replication study with
their limited resources.

\section*{Software and data}
All our analyses were conducted in the R programming language version 4.2.2
\citep{R}. Code to reproduce this manuscript is available at
\url{https://github.com/SamCH93/BAtDRS}. A snapshot of the Git repository at the
time of writing is archived at \url{https://doi.org/10.5281/zenodo.7291076}.
Methods for Bayesian design of replication studies are implemented in the R
package BayesRepDesign which is available at
\url{https://github.com/SamCH93/BayesRepDesign}. The CC-By 4.0 licensed data
were downloaded from \url{https://osf.io/42ef9/}. The R markdown script
``Decline effects main analysis.Rmd'' was executed and the relevant variables
from the objects ``ES\_experiments'' and ``decline\_effects'' were saved.

\section*{Acknowledgments}
This work was supported by the Swiss National Science Foundation (\#189295). The
funder had no role in study design, data collection, data analysis, data
interpretation, decision to publish, or preparation of the manuscript. We thank
\citet{Protzko2020} for publicly sharing their data. We thank Charlotte
Micheloud and Angelika Stefan for helpful comments on drafts of the manuscript.
Our acknowledgment of these individuals does not imply their endorsement of this
article.

%% Bibliography
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}
\section{The BayesRepDesign R package}
\label{app:package}

\begin{knitrout}\footnotesize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(}\hlstr{"BayesRepDesign"}\hlstd{)}

\hlcom{## design prior (flat initial prior for effect size + heterogeneity)}
\hlstd{dp} \hlkwb{<-} \hlkwd{designPrior}\hlstd{(}\hlkwc{to} \hlstd{=} \hlnum{0.2}\hlstd{,} \hlkwc{so} \hlstd{=} \hlnum{0.05}\hlstd{,} \hlkwc{tau} \hlstd{=} \hlnum{0.08}\hlstd{)}
\hlkwd{plot}\hlstd{(dp)}
\end{alltt}
\end{kframe}
\includegraphics[width=0.9\textwidth]{images/paper3/package-illustration-1}
\begin{kframe}\begin{alltt}
\hlcom{## compute replication standard error for achieving significance at 2.5%}
\hlkwd{ssdSig}\hlstd{(}\hlkwc{level} \hlstd{=} \hlnum{0.025}\hlstd{,} \hlkwc{dprior} \hlstd{= dp,} \hlkwc{power} \hlstd{=} \hlnum{0.8}\hlstd{)}
\end{alltt}
\begin{verbatim}
##        Bayesian sample size calculation for replication studies
##        ========================================================
##
## success criterion and computation
## ------------------------------------------------------------------------
##   replication p-value <= 0.025 (exact computation)
##
## original data and initial prior for effect size
## ------------------------------------------------------------------------
##   to = 0.2 : original effect estimate
##   so = 0.05 : standard error of original effect estimate
##   tau = 0.08 : assumed heterogeneity standard deviation
##   N(mean = 0, sd = Inf) : initial normal prior
##
## design prior for effect size
## ------------------------------------------------------------------------
##   N(mean = 0.2, sd = 0.094) : normal design prior
##
## probability of replication success
## ------------------------------------------------------------------------
##   PoRS = 0.8 : specified
##   PoRS = 0.8 : recomputed with sr
##
## required sample size
## ------------------------------------------------------------------------
##   sr = 0.045 : required standard error of replication effect estimate
##   c = so^2/sr^2 ~= nr/no = 1.2 : required relative variance / sample size
\end{verbatim}
\begin{alltt}
\hlcom{## compute numerically via success region and method agnostic function}
\hlstd{sregFun} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{sr}\hlstd{) \{}
    \hlcom{## success region is [1.96*sr, Inf)}
    \hlkwd{successRegion}\hlstd{(}\hlkwc{intervals} \hlstd{=} \hlkwd{cbind}\hlstd{(}\hlkwd{qnorm}\hlstd{(}\hlkwc{p} \hlstd{=} \hlnum{0.975}\hlstd{)}\hlopt{*}\hlstd{sr,} \hlnum{Inf}\hlstd{))}
\hlstd{\}}
\hlkwd{ssd}\hlstd{(}\hlkwc{sregionfun} \hlstd{= sregFun,} \hlkwc{dprior} \hlstd{= dp,} \hlkwc{power} \hlstd{=} \hlnum{0.8}\hlstd{)}
\end{alltt}
\begin{verbatim}
##        Bayesian sample size calculation for replication studies
##        ========================================================
##
## success criterion and computation
## ------------------------------------------------------------------------
##   method agnostic success region (numerical computation)
##
## original data and initial prior for effect size
## ------------------------------------------------------------------------
##   to = 0.2 : original effect estimate
##   so = 0.05 : standard error of original effect estimate
##   tau = 0.08 : assumed heterogeneity standard deviation
##   N(mean = 0, sd = Inf) : initial normal prior
##
## design prior for effect size
## ------------------------------------------------------------------------
##   N(mean = 0.2, sd = 0.094) : normal design prior
##
## probability of replication success
## ------------------------------------------------------------------------
##   PoRS = 0.8 : specified
##   PoRS = 0.8 : recomputed with sr
##
## required sample size
## ------------------------------------------------------------------------
##   sr = 0.045 : required standard error of replication effect estimate
##   c = so^2/sr^2 ~= nr/no = 1.2 : required relative variance / sample size
\end{verbatim}
\end{kframe}
\end{knitrout}

\end{subappendices}

### 2022-11-24 paper3.tex
paper 3 supplement

@@
      {\scriptsize -- between-study heterogeneity} \\
-     {\scriptsize -- skepticism regarding original study} \\
+     {\scriptsize -- scepticism regarding original study} \\
      {\scriptsize -- data from other studies} \\
@@
 knowledge about the effect size either from theory or from related studies,
-(iii) skepticism regarding the original study due to the possibility of
+(iii) scepticism regarding the original study due to the possibility of
 exaggerated results.
@@
 
-\subsubsection{The skeptical \textit{p}-value}
+\subsubsection{The sceptical \textit{p}-value}
 \citet{Held2020} proposed a reverse-Bayes approach for quantifying replication
-success. The main idea is to determine the variance of a ``skeptical'' zero-mean
+success. The main idea is to determine the variance of a ``sceptical'' zero-mean
 normal prior for the effect size $\theta$ such that its posterior distribution
 based on the original study is no longer credible. Replication success is then
-achieved if the replication data are in conflict with the skeptical prior. The
-procedure can be summarized by a ``skeptical $p$-value'' $\ps$, and the lower
+achieved if the replication data are in conflict with the sceptical prior. The
+procedure can be summarized by a ``sceptical $p$-value'' $\ps$, and the lower
 the $p$-value the higher the degree of replication success. \citet[sec.
@@
 
-\subsubsection{The skeptical Bayes factor}
+\subsubsection{The sceptical Bayes factor}
 \citet{Pawel2022b} modified the previously described reverse-Bayes assessment of
@@
 tail probabilities as measures of evidence and prior data conflict. Again, the
-procedure can be summarized in a single measure termed the ``skeptical Bayes
+procedure can be summarized in a single measure termed the ``sceptical Bayes
 factor'' $\BFs$, with lower values of $\BFs$ pointing to higher degrees of
@@
 $\Delta = 0.2$ corresponding to a small SMD effect size according to
-the classification from \citet{Cohen1992}. For the skeptical $p$-value we use
+the classification from \citet{Cohen1992}. For the sceptical $p$-value we use
 the recommended ``golden'' level $\alpha = 0.062$ as it
@@
 estimate is larger than the original one \citep{Held2021}. Finally, for the
-replication Bayes factor and the skeptical Bayes factor we use the ``strong
+replication Bayes factor and the sceptical Bayes factor we use the ``strong
 evidence'' level $\gamma = 1/10$ from \citet{Jeffreys1961}.
@@
   equivalence based on $90\%$ confidence interval and with
-  margin $\Delta = 0.2$, skeptical $p$-value at level
-  $\alpha = 0.062$, and skeptical Bayes factor at level
+  margin $\Delta = 0.2$, sceptical $p$-value at level
+  $\alpha = 0.062$, and sceptical Bayes factor at level
   $\gamma = 1/10$.}
@@
 $80\%$ probability of replication success the fewest
-samples are required with meta-analysis, followed by the skeptical $p$-value,
-the two-trials rule, the replication Bayes factor, the skeptical Bayes factor,
+samples are required with meta-analysis, followed by the sceptical $p$-value,
+the two-trials rule, the replication Bayes factor, the sceptical Bayes factor,
 and lastly the equivalence test. If the chosen sample size should guarantee a
@@
 $\alpha = 0.025$ for all $c$ with the exception of
-meta-analysis and the skeptical $p$-value. Meta-analysis (light blue) has an
+meta-analysis and the sceptical $p$-value. Meta-analysis (light blue) has an
 extremely high type I error rate as the pooling with the highly significant
 original data leads to replication success if the replication sample size is not
-drastically increased. The type I error rate of the skeptical $p$-value (yellow)
+drastically increased. The type I error rate of the sceptical $p$-value (yellow)
 is only slightly larger than $\alpha = 0.025$ which is
 expected since the level $\alpha = 0.062$ is used for
-declaring replication success with the skeptical $p$-value, and its type I error
+declaring replication success with the sceptical $p$-value, and its type I error
 rate is always smaller than the level for thresholding it \citep{Held2020}. The
-type I error rate of the skeptical $p$-value decreases to values smaller than
+type I error rate of the sceptical $p$-value decreases to values smaller than
 $\alpha = 0.025$ of the two-trials rule at approximately
@@
   effect size equivalence at level $\alpha = 0.1$ with margin
-  $\Delta = 0.2$, skeptical $p$-value at level
-  $\alpha = 0.062$, and skeptical Bayes factor at level
+  $\Delta = 0.2$, sceptical $p$-value at level
+  $\alpha = 0.062$, and sceptical Bayes factor at level
   $\gamma = 1/10$ for data from the replication project by
@@
 rate for most methods. We see again the pattern that the type I error rate of
-the equivalence test and the skeptical $p$-value is larger than the type I error
+the equivalence test and the sceptical $p$-value is larger than the type I error
 rate 2.5\% of the two-trials rule. However, while the type I error rate of the
-skeptical $p$-value decreases when replication studies require larger sample
+sceptical $p$-value decreases when replication studies require larger sample
 sizes, the type I error rate of the equivalence test may also be large if the
@@
 reallocated from the other studies which require fewer samples (\eg{} in the
-experiment ``Referrals'' an almost three times increase for the skeptical Bayes
+experiment ``Referrals'' an almost three times increase for the sceptical Bayes
 factor). On the other hand, the equivalence test typically requires larger
@@
 article.
-
-%% Bibliography
-\bibliographystyle{apalikedoiurl}
-\bibliography{bibliography}
 
@@
 
+\section{Supplementary material}
+
+Here, we provide additional information on computing the predictive distribution
+of the replication effect estimate when a prior is assigned to the heterogeneity
+variance $\tau^{2}$ (Section~\ref{sec:priortau}). We also provide additional
+information on methods for analyzing replication data. For each method we derive
+the \emph{success region} in terms of the effect estimate of the replication
+study $\that_{r}$, which is required for sample size determination as
+illustrated in the main manuscript (Section~\ref{sec:2TR} to~\ref{sec:BFs}). For
+the two-trials rule and the replication Bayes factor methods we additionally
+provide derivations on how these methods can be generalized to the multisite
+replication setting. We show then how the optimal number of samples per site can
+be derived for multisite SSD (Section~\ref{sec:multi}). Finally, we show SSD for
+the \citet{Protzko2020} project but using an adaptive shrinkage prior instead of
+the flat prior as in the main manuscript (Section~\ref{sec:ssdprotzko}).
+
+\subsection{Prior on the heterogeneity variance}
+\label{sec:priortau}
+When also a prior is assigned to the heterogeneity variance $\tau^{2}$, the
+predictive distribution of the replication effect estimate $\that_{r}$ is given
+by
+\begin{align*}
+  f(\that_{r} \given \that_{o}, \sigma_{o}, \sigma_{r})
+  &= \int_{0}^{+\infty} f(\that_{r} \given \sigma_{r}, \that_{o}, \sigma_{o},
+    \tau^{2}) \,
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}.
+\end{align*}
+That is, it is the predictive distribution of the replication effect estimate
+$\that_{r}$ integrated with respect to the marginal posterior of $\tau^{2}$
+based on the original data $x_{o} = \{\that_{o}, \sigma^{2}_{o}\}$. If the
+initial prior for $\theta$ is normal
+$\theta \sim \Nor(\mutheta, \sigmatheta^{2})$, and the initial prior for
+$\tau^{2}$ has density $f(\tau^{2})$, we have
+\begin{align*}
+  f(\tau^{2} \given \that_{o}, \sigma_{o})
+  &= \int_{-\infty}^{+\infty} f(\theta, \tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\theta \\
+  &= \frac{\int_{-\infty}^{+\infty} f(\that_{o} \given \theta, \tau^{2}, \sigma^{2}_{o}) \,
+    f(\theta \given \tau^{2}) \, f(\tau^{2}) \, \text{d}\theta}{\int_{0}^{+\infty}
+    \int_{-\infty}^{+\infty} f(\that_{o} \given \theta_{*}, \tau^{2}_{*}, \sigma^{2}_{o}) \,
+    f(\theta_{*} \given \tau^{2}_{*}) \, f(\tau^{2}_{*}) \, \text{d}\theta_{*} \,
+    \text{d}\tau^{2}_{*}} \\
+  &= \frac{f(\tau^{2}) \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta, \tau^{2}
+    + \sigma^{2}_{o}) \, \Nor(\theta \given \mutheta, \sigmatheta^{2}) \,\text{d}\theta
+    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
+    \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta_{*}, \tau^{2}_{*} + \sigma^{2}_{o}) \,
+    \Nor(\theta_{*} \given \mutheta, \sigmatheta^{2}) \, \text{d}\theta_{*} \,
+    \text{d}\tau^{2}_{*}} \\
+  &= \frac{f(\tau^{2}) \, \Nor(\that_{o} \given \mutheta, \tau^{2}
+    + \sigma^{2}_{o} + \sigmatheta^{2})
+    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
+    \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
+    \text{d}\tau^{2}_{*}}.
+\end{align*}
+To compute the marginal posterior density of $\tau^{2}$ one numerical
+integration is hence required. The updating of the prior depends on the distance
+between prior mean $\mutheta$ and the original effect estimate $\that_{o}$
+relative to the prior variance $\sigmatheta^{2}$ and the squared standard error
+$\sigma_{o}^{2}$. If an improper uniform prior is assigned to $\theta$
+($\sigmatheta^{2} \to \infty$), the posterior reduces to the prior
+\begin{align*}
+  \lim_{\sigmatheta^{2} \to \infty} f(\tau^{2} \given \that_{o}, \sigma_{o})
+  &= \lim_{\sigmatheta^{2} \to \infty} \frac{f(\tau^{2}) \, \Nor(\that_{o} \given \mutheta, \tau^{2}
+    + \sigma^{2}_{o} + \sigmatheta^{2})
+    }{\int_{0}^{+\infty} f(\tau^{2}_{*})
+    \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
+    \text{d}\tau^{2}_{*}} \\
+  &= \lim_{\sigmatheta^{2} \to \infty}  \int_{0}^{+\infty} \frac{f(\tau^{2})}{f(\tau^{2}_{*})} \,
+    \underbrace{\sqrt{\frac{\tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}}{\tau^{2} + \sigma^{2}_{o} +
+    \sigmatheta^{2}}}}_{\to 1} \, \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{
+    \frac{(\that_{o} - \mutheta)^{2}}{\tau^{2} + \sigma^{2}_{o} + \sigmatheta^{2}}}_{\downarrow 0} -
+    \underbrace{\frac{(\that_{o} - \mutheta)^{2}}{\tau^{2}_{*} + \sigma^{2}_{o} +
+    \sigmatheta^{2}}}_{\downarrow 0} \bigg\}\bigg] \, \text{d}\tau^{2}_{*} \\
+  &= f(\tau^{2}),
+\end{align*}
+the limit can be interchanged with the integral because of the monotone
+convergence theorem. This means that with a uniform prior nothing can be learned
+about the variance $\tau^{2}$ which intuitively makes sense as estimation of a
+variance requires at least two observations. The phenomenon is illustrated in
+Figure~\ref{fig:margposttau2} for the data from the experiment ``Labels''
+\citep{Protzko2020} as also used in the main manuscript. We see that as the
+prior standard deviation increases (making the prior more uniform), the marginal
+posterior density becomes closer to the prior density.
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper3/sup-tau-random-example-1}
+\end{knitrout}
+\caption{Marginal posterior distribution of heterogeneity variance $\tau^{2}$
+  based on data from experiment ``Labels'' from \citet{Protzko2020} with
+  original effect estimate $\hat{\theta}_{o} = 0.205$ and
+  standard error $\sigma_{o} = 0.051$. A
+  $\theta \sim \Nor(0, \sigmatheta^{2})$ prior is assigned to the
+  effect size $\theta$ and a half normal prior with standard deviation
+  $0.04$ is assigned to $\tau$.}
+\label{fig:margposttau2}
+\end{figure}
+
+Combining all the previous results, we obtain the probability of replication
+success as
+\begin{align*}
+  \Pr(\that_{r} \in S \given \that_{o}, \sigma_{o}, \sigma_{r})
+  &= \int_{S}\int_{0}^{+\infty} f(\that_{r} \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\that_{r} \,\text{d}\tau^{2} \\
+  &= \int_{0}^{+\infty} \Pr(\that_{r} \in S \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}. \\
+\end{align*}
+This mean computing the probability of replication success with a prior on
+$\tau^{2}$ requires two-dimensional numerical integration. However, in the
+common case when a uniform prior is assigned to $\theta$, the marginal posterior
+distribution of $\tau^{2}$ reduces to the prior, and only one numerical
+integration is required.
+
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper3/sup-example-applied-1}
+\end{knitrout}
+\caption{Probability of replication success as a function of relative sample
+  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original effect estimate
+  $\hat{\theta}_{o} = 0.205$ and standard error
+  $\sigma_{o} = 0.051$ for uniform initial prior for effect size
+  $\theta$ and either fixed $\tau = 0.05$ (as in main
+  manuscript) or half normal prior with standard deviation
+  $0.04$ assigned to $\tau$. Replication success is defined
+  by the two-trials rule at level $\alpha = 0.025$, the replication
+  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
+  analysis at level $\alpha = 0.025^{2}$, effect size
+  equivalence based on $90\%$ confidence interval and with
+  margin $\Delta = 0.2$, sceptical $p$-value at level
+  $\alpha = 0.062$, and sceptical Bayes factor at level
+  $\gamma = 1/10$.}
+\label{fig:exampletaurandom}
+\end{figure}
+
+Figure~\ref{fig:exampletaurandom} shows the probability of replication success
+based on data from the ``Labels'' experiment, as in the main manuscript. A half
+normal prior with is assigned to the heterogeneity $\tau$ which is a typical
+prior distribution used for heterogeneity modeling in meta-analysis
+\citep{Rover2021}. The standard deviation of the prior is set to
+$0.04$ so that the mean of the prior equals the value of
+the fixed heterogeneity $\tau = 0.05$ elicited in the main manuscript. We see
+that the probability of replication success is only slightly higher compared to
+the fixed $\tau = 0.05$ from the main manuscript.
+
+\subsection{The two-trials rule}
+\label{sec:2TR}
+The two-trials rule is the most common analysis approach for replication
+studies. Replication success is declared if both original and replication study
+achieve statistical significance at some level $\alpha$ (and both estimates go
+in the same direction which can be taken into account by using one-sided
+$p$-values). We will study the two-trial under normality using the data model
+$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with $\that_{i}$ the
+estimate of the unknown effect size $\theta$ from study $i$ and $\sigma_{i}$ is
+the corresponding standard error (assumed to be know). The $p$-values for
+testing $H_{0} \colon \theta = 0$ versus $H_{1} \colon \theta > 0$ are then
+$p_{i} = 1 - \Phi(\that_{i}/\sigma_{i})$ whereas for the alternative
+$H_{1} \colon \theta < 0$ they are $p_{i} = \Phi(\that_{i}/\sigma_{i})$. Suppose
+the original effect estimate was statistically significant at level $\alpha$,
+\ie{} $p_{o} \leq \alpha$. Replication success at level $\alpha$ is then
+established if the replication effect estimate $\that_{r}$ is also statistically
+significant at level $\alpha$, \ie{} $p_{r} \leq \alpha$. By applying some
+algebraic manipulations to the success condition, one can show that this implies
+that replication success is achieved if the replication effect estimate
+$\that_{r}$ is contained in the success region
+\begin{align*}
+  S_{\text{2TR}} =
+  \begin{cases}
+    \left[\zalpha \, \sigma_{r}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
+    \left[-\infty, -\zalpha \, \sigma_{r} \right) & \text{for} ~ \that_{o} < 0.
+  \end{cases}
+\end{align*}
+
+\subsubsection{The multisite two-trials rule}
+If multiple replication studies are conducted for one original study (a
+\emph{multisite} replication), the two-trials rule is typically modified by
+meta-analyzing the effect estimates from all replications and then using the
+combined estimate as usual in the two-trials rule \citep[see \eg{} the ``Many
+labs'' projects from][]{Klein2014, Klein2018}. Suppose $m$ replication studies
+are conducted and produce $m$ effect estimates $\that_{r1}, \dots, \that_{m}$
+with standard errors $\sigma_{r1}, \dots, \sigma_{rm}$. Subsequently, a weighted
+average
+$\hat{\theta}_{r*} = \{\sum_{i = 1}^{m} \hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\}\,\sigma_{r*}^{2}$
+with standard error
+$\sigma_{r*} = 1/\surd\{\sum_{i}^{m}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\}$ can be
+computed. If the between-replication heterogeneity variance $\tau^{2}_{r}$ is
+set to zero this corresponds to the fixed effects estimate of $\theta$, while
+estimating $\tau^{2}_{r}$ from the data corresponds to the random effects
+estimate. Replication success at level $\alpha$ is then established if the
+replication $p$-value is smaller than $\alpha$, \ie{}
+$p_{r*} = 1 - \Phi(\that_{r*}/\sigma_{r*}) \leq \alpha$. With some algebra one
+can show that this implies a success region for the weighted average replication
+effect estimate $\that_{r*}$ given by
+\begin{align*}
+  S_{\text{2TR}} =
+  \begin{cases}
+    \left[\zalpha \, \sigma_{r*}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
+    \left[-\infty, -\zalpha \, \sigma_{r*} \right) & \text{for} ~ \that_{o} < 0.
+  \end{cases}
+\end{align*}
+
+\subsection{Fixed effects meta-analysis}
+Assume again the data model
+$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ where $\that_{i}$ is
+an estimate of the effect size $\theta$ from study $i \in \{o, r\}$ and
+$\sigma_{i}$ is the corresponding standard error (assumed to be know). In the
+fixed effects meta-analysis approach replicability is assessed in terms of the
+pooled effect estimate $\that_{m}$ and standard error $\sigma_{m}$ which are
+\begin{align*}
+  &\that_{m} =
+    \left(\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r}\right)\sigma^{2}_{m}&
+&\text{and}&                                                                                       &\sigma_{m} = \left(1/\sigma^{2}_{o} + 1/\sigma^{2}_{r}\right)^{-1/2},&
+\end{align*}
+which are also equivalent to the mean and standard deviation of a posterior
+distribution for the effect size $\theta$ based on the data from original and
+replication study and an initial flat prior for $\theta$. Fixed effects
+meta-analysis is typically used because estimating a heterogeneity variance from
+two studies is highly unstable. Replication success at level $\alpha$ is
+established if the one-sided meta-analytic $p$-value (in the direction of the
+original effect estimate $\that$) is significant at level $\alpha$, \ie{}
+$p_{m} = 1 - \Phi(\that_{m}/\sigma_{m}) \leq \alpha$ for $\that_{o} > 0$ and
+$p_{m} = \Phi(\that_{m}/\sigma_{m}) \leq \alpha$ for $\that_{o} < 0$.
+With some algebraic manipulations one can show that this criterion implies a
+success region $S_{\text{MA}}$ for the replication effect estimate $\that_{r}$
+given by
+\begin{align*}
+  \SMA
+  =
+  \begin{cases}
+    [\sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}} -
+      (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o},   \infty )
+    & \text{for} ~ \that_{o} > 0 \\
+    (-\infty, -\sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}} -
+      (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o}]
+    & \text{for} ~ \that_{o} < 0.
+\end{cases}
+\end{align*}
+
+\subsection{Effect size equivalence}
+The effect size equivalence approach \citep{Anderson2016} defines replication
+success via compatibility of the effect estimates from both studies. Under
+normality we may assume the data model
+$\that_{i} \given \theta_{i} \sim \Nor(\theta_{i}, \sigma^{2}_{i})$ for study
+$i \in \{o, r\}$, and we are interested in the true effect size difference
+$\delta = \theta_{r} - \theta_{o}$. A $(1 - \alpha)$ confidence interval for
+$\delta$ is then given by
+\begin{align*}
+  C_{\alpha} = \left[\that_{r} - \that_{o} - \zalphatwo \sqrt{\sigma^{2}_{r} + \sigma^{2}_{r}},
+  \that_{r} - \that_{o} + \zalphatwo \sqrt{\sigma^{2}_{r} + \sigma^{2}_{r}}\right]
+\end{align*}
+Effect size equivalence is established if the confidence interval is fully
+included in an equivalence region $C_{\alpha} \subseteq [-\Delta, \Delta]$ with
+$\Delta > 0$ a pre-specified margin. Applying some algebraic manipulations to
+the success conditions one can show that the equivalence test replication success
+criterion implies a success region $\SEqu$ for the replication estimate
+$\that_{r}$ given by
+\begin{align*}
+  \SEqu
+  = \left[\that_{o} - \Delta + \zalphatwo \sqrt{\sigma^{2}_{o} +
+  \sigma^{2}_{r}}, \that_{o} + \Delta - \zalphatwo
+  \sqrt{\sigma^{2}_{o} + \sigma^{2}_{r}}\right].
+\end{align*}
+
+\subsection{The replication Bayes factor}
+The replication Bayes factor approach uses the replication data $x_{r}$ to
+quantify the evidence for the null hypothesis $H_{0}\colon \theta = 0$ relative
+to the alternative hypothesis $H_{1} \colon \theta \sim f(\theta \given x_{o})$,
+which postulates that the effect size $\theta$ is distributed according to its
+posterior distribution based on the original data $x_{o}$. Assume again a normal
+model $\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with
+$\that_{i}$ an estimate of the effect size $\theta$ from study $i \in \{o, r\}$
+and $\sigma_{i}$ the corresponding standard error (assumed to be know), and that
+we use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which
+arises from updating an initial flat prior for $\theta$ the original data
+$x_{o} = \{\that_{o}, \sigma_{o}\}$. The replication Bayes factor is then
+\begin{align}
+  \label{eq:bfr}
+  \BFr &= \frac{f(\that_{r} \given H_{0})}{f(\that_{r} \given H_{1})}
+       = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r}} \, \exp\left[
+         -\frac{1}{2}\left\{ \frac{\that^{2}_{r}}{\sigma^{2}_{r}} -
+         \frac{(\that_{r} - \that_{o})^{2}}{\sigma^{2}_{o} + \sigma^{2}_{r}}
+         \right\}\right].
+\end{align}
+Replication success at level $\gamma \in (0, 1)$ is achieved if
+$\BFr \leq \gamma$. By applying some algebra to $\BFr \leq \gamma$, one can show
+that it is equivalent to the replication effect estimate $\that_{r}$ falling in
+the success region
+\begin{align*}
+  \SBFr
+  = \left(-\infty, -\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}\right] \bigcup
+   \left[\sqrt{A} - (\that_{o}\sigma^{2}_{r})/\sigma^{2}_{o}, \infty\right)
+\end{align*}
+where
+$A = \sigma^{2}_{r}(1 + \sigma^{2}_{r}/\sigma^{2}_{o}) \{\that_{o}^{2}/\sigma^{2}_{o} - 2 \log \gamma + \log(1 + \sigma^{2}_{o}/\sigma^{2}_{r})\}$.
+
+\subsection{The multisite replication Bayes factor}
+The generalization of the replication Bayes factor to the multisite setting is
+straightforward. The data are represented by vector of replication effect
+estimates $\bthat_{r} = (\that_{r1}, \dots, \that_{rm})^{\top}$ with
+corresponding standard error vector
+$\bsigma_{r} = (\sigma_{r1}, \dots, \sigma_{rm})^{\top}$, and we assume the data
+model
+$\bthat_{r} \given \theta \sim \Nor_{m}\{\theta \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$
+where $\bone_{m}$ is a vector of $m$ ones and $\tau^{2}_{r}$ is a heterogeneity
+variance for the replication effect sizes (not to be confused with the
+heterogeneity variance $\tau^{2}$ used in the design prior).
+
+As in the singlesite case, the replication Bayes factor quantifies the evidence
+that the data provide for the null hypothesis $H_{0}\colon \theta = 0$ relative
+to the alternative hypothesis
+$H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$. The marginal density
+of the replication data under the null hypothesis is simply
+$\bthat_{r} \given H_{0} \sim \Nor_{m}\{0 \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$,
+whereas the marginal likelihood under the alternative $H_{1}$ is obtained from
+integrating the likelihood
+% $\bthat_{r} \given \theta \sim \Nor_{m}\{\theta \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$
+with respect to the prior distribution of $\theta$ under the alternative
+$H_{1}$. % $H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma_{o})$.
+Let $\Nor(x;m,v)$ denote the normal density function mean $m$ and variance $v$
+evaluated at $x$. Define also
+$\hat{\theta}_{r*} = \left\{\sum_{i=1}^{n}\hat{\theta}_{ri}/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\} \sigma^{2}_{r*}$
+and
+$\sigma^{2}_{r*} = 1/\left\{\sum_{i=1}^{n}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\right\}$,
+\ie{} the weighted average of the replication effect estimates based on the
+heterogeneity $\tau^{2}_{r}$ and its variance. The marginal density is then
+
+\begin{align*}
+        f(\hat{\theta}_{r} \given H_{1})
+        &= \int f(\hat{\theta}_{r} \given \theta) f(\theta \given H_{1})
+                        \, \text{d}\theta \\
+              &= \int \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \theta)^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +
+                  \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
+                                    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
+    \, \text{d}\theta \\
+  &= \int \frac{
+    \exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +  \frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
+    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right]}{
+    \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
+    \, \text{d}\theta \\
+  &= \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}}\right\} \right]}{\left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
+    \underbrace{\int \exp\left[-\frac{1}{2} \left\{\frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
+    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right] \text{d}\theta}_{= \Nor(\hat{\theta}_{r*}; m, \sigma^{2}_{o} + \sigma^{2}_{r*}) 2\pi \sigma_{o} \sigma_{r*}} \\
+  &= \left\{(1 + \sigma^{2}_{o}/\sigma^{2}_{r*}) \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{-1/2} \exp\left[-\frac{1}{2}\left\{
+    \sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} + \frac{(\hat{\theta}_{r*} - \that_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
+\end{align*}
+Dividing the marginal density of $\bthat_{r}$ under $H_{0}$ by the marginal
+density of $\bthat_{r}$ under $H_{1}$ leads to cancellation of several terms, and
+produces the replication Bayes factor
+\begin{align*}
+  \BF_{01}(\hat{\theta}_{r})
+  &= \frac{f(\hat{\theta}_{r} \given H_{0})}{f(\hat{\theta}_{r} \given H_{1})}
+    = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r*}}  \exp\left[-\frac{1}{2}\left\{
+    \frac{\hat{\theta}_{r*}^{2}}{\sigma^{2}_{r*}} -
+    \frac{(\hat{\theta}_{r*} - \hat{\theta}_{o})^{2}}{\sigma^{2}_{r*} + \sigma^{2}_{o}}\right\}\right].
+\end{align*}
+The multisite replication Bayes factor is therefore equivalent to the singlesite
+replication Bayes factor from~\eqref{eq:bfr} but using the weighted average
+$\that_{r*}$ and its standard error $\sigma_{r*}$ as the replication effect
+estimate $\that_{r}$ and standard error $\sigma_{r}$.
+
+\subsection{The sceptical \textit{p}-value}
+\citet{Held2020} proposed a reverse-Bayes approach for assessing replicability.
+One assumes again the data model
+$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with
+$i \in \{o, r\}$, along with a zero-mean ``sceptical'' prior
+$\theta \sim \Nor(0, \sigma^{2}_{s})$ for the effect size. In a first step, a
+level $\alpha \geq p_{o} = 1 - \Phi(|\that_{o}|/\sigma_{o})$ is fixed and the
+``sufficiently sceptical'' prior variance $\sigma^{2}_{s}$ is computed
+\begin{align*}
+  \sigma^{2}_{s} = \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}
+\end{align*}
+where $z_{o} = \that_{o}/\sigma_{o}$. The sufficiently sceptical prior variance
+$\sigma^{2}_{s}$ has the property that it renders the resulting posterior of
+$\theta$ no longer ``credible'' at level $\alpha$, that is, the posterior tail
+probability is fixed to
+$\Pr(\theta \geq 0 \given \that_{o}, \sigma_{o}, \sigma_{s}) = 1 - \alpha$ for
+positive estimates and
+$\Pr(\theta \leq 0 \given \that_{o}, \sigma_{o}, \sigma_{s}) = 1 - \alpha$ for
+negative estimates. In a second step, the conflict between the sceptical prior
+and the observed replication data is quantified, larger conflict indicating a
+higher degree of replication success. For doing so, a prior predictive tail
+probability
+\begin{align*}
+  p_{\text{Box}} =
+  \begin{cases}
+    1 - \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^{2}_{s})\right\}
+    & \text{if} ~ \that_{o} > 0 \\
+   \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^{2}_{s})\right\}
+    & \text{if} ~ \that_{o} < 0 \\
+    \end{cases}
+\end{align*}
+is computed and replication success at level $\alpha$ is declared if
+$p_{\text{Box}} \leq \alpha$. The smallest level $\alpha$ at which replication
+success is achieved is called the \emph{the sceptical $p$-value} $\ps$ and
+replication success at level $\alpha$ is equivalent with $\ps \leq \alpha$
+\citep[see][for more details on $\ps$]{Held2020, Held2021}. By applying some
+algebraic manipulations to the condition $p_{\text{Box}} \leq \alpha$, one can
+show that it is equivalent to the replication effect estimate $\that_{r}$
+falling in the success region
+\begin{align*}
+  \SPs =
+  \begin{cases}
+    [\zalpha \surd\{\sigma^{2}_{r} +
+  \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}\}, \infty)
+    & \text{if} ~ \that_{o} > 0 \\
+   (-\infty, -\zalpha \surd\{\sigma^{2}_{r} +
+  \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}\}]
+    & \text{if} ~ \that_{o} < 0. \\
+    \end{cases}
+\end{align*}
+
+\subsection{The sceptical Bayes factor}
+\label{sec:BFs}
+\citet{Pawel2022b} modified the reverse-Bayes assessment of replication success
+from \citet{Held2020} to use Bayes factors \citep{Jeffreys1961, Kass1995}
+instead of tail probabilities as measures of evidence and prior data conflict.
+The procedure assumes again the data model
+$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ for study
+$i \in \{o, r\}$. In the first step the original data are used to contrast the
+evidence for the point null hypothesis $H_{0} \colon \theta = 0$ relative to the
+``sceptical'' alternative $H_{S} \colon \theta \sim \Nor(0, \sigma^{2}_{s})$
+with the Bayes factor
+\begin{align*}
+  \BF_{0S}
+  = \frac{f(\that_{o} \given H_{0})}{f(\that_{o} \given H_{S})}
+  = \sqrt{1 + \sigma^{2}_{s}/\sigma^{2}_{o}} \, \exp\left\{-
+  \, \frac{z_{o}^{2}}{2(1 + \sigma^{2}_{o}/\sigma^{2}_{s})}\right\}.
+\end{align*}
+where $z_{o} = \that/\sigma^{2}_{o}$. One then determines the sufficiently
+sceptical prior variance $\sigma^{2}_{s}$ so that the Bayes factor is fixed to a
+level $\gamma \in (0, 1)$ meaning that there is no longer evidence against the
+null hypothesis at level $\gamma$. The sufficiently sceptical prior variance can
+be computed by
+\begin{align}
+  \label{eq:ssv}
+  \sigma^{2}_{s} &=
+  \begin{cases}
+    -\dfrac{\that_{o}^2}{q} - \sigma^{2}_{o} & ~~ \text{if} ~ -\dfrac{\that_o^2}{q} \geq \sigma^{2}_{o} \\
+    \text{undefined} & ~~ \text{else}
+  \end{cases} \\
+  \text{where} ~ q &= \lw{-1} \left\{-\frac{z_o^2}{\gamma^2} \,
+  \exp\left(-z_o^2\right)\right\}
+\end{align}
+with $\lw{-1}(\cdot)$ the branch of the
+Lambert W function with $\text{W}(y) \leq -1$ for $y \in [-1/e, 0)$.
+
+In a second step the conflict between the sceptical prior and the replication
+data is quantified. To do so, the sceptic is contrasted to the ``advocacy''
+alternative $H_{A} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$ which
+represents the position of an advocate as the prior corresponds to the posterior
+distribution based on the original data $\{\that_{o}, \sigma_{o}\}$ and a flat
+prior for the effect size $\theta$. This is done by computing the Bayes factor
+\begin{align*}
+  \BF_{SA}
+  = \frac{f(\that_{r} \given H_{S})}{f(\that_{r} \given H_{A})}
+  = \sqrt{\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^{2}_{s} + \sigma^{2}_{r}}}
+  \, \exp\left[-\frac{1}{2}\left\{\frac{\that_{r}^{2}}{\sigma^{2}_{s} +
+  \sigma^{2}_{r}} - \frac{(\that_{r} - \that_{o}^{2})}{\sigma^{2}_{o} +
+  \sigma^{2}_{r}}\right\}\right]
+\end{align*}
+and replication success at level $\gamma$ is defined by $\BF_{SA} \leq \gamma$
+as the data favor the advocate over the sceptic at a higher level than the
+sceptic's initial objection to the null hypothesis. The smallest level $\gamma$
+at which replication success is achievable is then called \emph{the sceptical
+  Bayes factor} $\BFs$, and replication success at level $\gamma$ is equivalent
+to $\BFs \leq \gamma$ \citep[see][for details on how to compute
+$\BFs$]{Pawel2022b}. To derive the success region of the sceptical Bayes factor
+one can apply algebraic manipulations to $\BF_{SA} \leq \gamma$, the condition
+for replication success at level $\gamma$, which leads to
+\begin{align}
+  \label{eq:BFssuccess}
+  S_{\scriptscriptstyle \BFs}
+  = \begin{cases}
+    (-\infty, -\sqrt{B} - M] \bigcup [\sqrt{B} - M, \infty) & \text{for} ~ \sigma^{2}_{s} < \sigma^{2}_{o} \\
+    [\that_{o} -\{(\sigma^{2}_{o} + \sigma^{2}_{r})\log\gamma\}/\that_{o}, \infty)
+    & \text{for} ~ \sigma^{2}_{s} = \sigma^{2}_{o}  \\
+    [-\sqrt{B} - M, \sqrt{B} - M] & \text{for} ~ \sigma^{2}_{s} > \sigma^{2}_{o}
+    \end{cases}
+\end{align}
+with
+\begin{align*}
+  B &= \left\{\frac{\that_{o}^{2}}{\sigma^{2}_{o} - \sigma^{2}_{s}} +
+      2\log\left(\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^{2}_{s} + \sigma^{2}_{r}}\right)
+      - 2\log \gamma \right\}
+      \frac{(\sigma^{2}_{s} + \sigma^{2}_{r})(\sigma^{2}_{o} + \sigma^{2}_{r})}{\sigma^{2}_{o}
+       - \sigma^{2}_{s}} \\
+  M &= \frac{\that_{o} (\sigma^{2}_{s} + \sigma^{2}_{r})}{\sigma^{2}_{o} - \sigma^{2}_{s}}
+\end{align*}
+and the sufficiently sceptical prior variance $\sigma^{2}_{s}$ computed
+by~\eqref{eq:ssv}.
+
+\subsection{Optimal number of sites}
+\label{sec:multi}
+The total cost of the design are $K = m(K_{c}n_{r} + K_{s})$ so that we can
+write the number of sites $m$ for a given total cost as
+\begin{align}
+  \label{eq:msites}
+  m = K (K_{c}n_{r} + K_{s})^{-1}.
+\end{align}
+We now want to minimize the predictive variance of the weighted average
+$\that_{r*}$ which, for a balanced design, is given by
+\begin{align}
+  \label{eq:predvar}
+  \sigma^{2}_{\scriptscriptstyle \that_{r*}}
+  = \frac{\sigma^{2}_{r} + \tau^{2}}{m} + \frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g}.
+\end{align}
+Plugging in~\eqref{eq:msites} into~\eqref{eq:predvar} and minimizing it with
+respect to $n_{r}$, leads to the optimal sample size
+\begin{align*}
+  n_{r}^{*}
+  = \frac{\lambda}{\tau} \, \sqrt{\frac{K_{s}}{K_{c}}}
+\end{align*}
+for a given cost ratio $K_{s}/K_{c}$.
+
+\begin{figure}[!htb]
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper3/sup-ssd-protzko-1}
+\end{knitrout}
+\caption{The left plot shows the required relative sample size $c = n_r/n_o$ to
+  achieve a target probability of replication success of
+  $1 - \beta = 80$\% (if possible). Replication success
+  is defined through the two-trials rule at level $\alpha = 0.025$,
+  replication Bayes factor at level $\gamma = 1/10$, fixed
+  effects-meta analysis at level $\alpha = 0.025^{2}$,
+  effect size equivalence at level $\alpha = 0.1$ with margin
+  $\Delta = 0.2$, sceptical $p$-value at level
+  $\alpha = 0.062$, and sceptical Bayes factor at level
+  $\gamma = 1/10$ for data from the replication project by
+  \citet{Protzko2020}. An adaptive shrinkage prior is used for the effect size
+  $\theta$ either without ($\tau = 0$) or with between-study heterogeneity
+  ($\tau = 0.05$). The right plot shows the type I error
+  rate associated with the required sample size. Experiments are ordered (top to
+  bottom) by their original one-sided $p$-value
+  $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
+\label{fig:ssd-all-shrink}
+\end{figure}
+
+\subsection{Sample size determination with adaptive shrinkage prior}
+\label{sec:ssdprotzko}
+Figure~\ref{fig:ssd-all-shrink} shows sample size determination for all studies
+from the \citet{Protzko2020} project as in the main manuscript but using an
+``adaptive shrinkage prior'' for the effect size $\theta$ where the variance of
+the shrinkage prior is estimated by empirical Bayes. We see that the required
+sample size increases for studies with large $p$-values compared to the analysis
+based on a flat prior for $\theta$ as in the main manuscript, whereas it stays
+about the same for studies with small $p$-values. This is because studies with
+large $p$-values receive more shrinkage.
 \end{subappendices}
+
+%% Bibliography
+\bibliographystyle{apalikedoiurl}
+\bibliography{bibliography}

### 2022-11-24 paper5.tex
paper 5 added

\section*{Abstract}
We examine the concept of Bayesian Additional Evidence (BAE) recently proposed
by Sondhi et al. We derive simple closed-form expressions for BAE and compare
its properties with other methods for assessing findings in the light of new
evidence. We find that while BAE is easy to apply, it lacks both a compelling
rationale and clarity of use needed for reliable decision-making.

\textbf{Key words}: Advocacy prior, Analysis of Credibility, Bayesian Additional
Evidence, Reverse-Bayes

\section{Introduction}

We read with great interest the article by \citet{Sondhi2021}, which introduces
the concept of \emph{Bayesian Additional Evidence} (BAE). The authors use a
reverse-Bayes argument to define BAE, and apply it to the important issue of how
new evidence affects the overall credibility of an existing finding. As they
state, BAE is thus closely related to another reverse-Bayes approach known as
\emph{Analysis of Credibility} (AnCred) proposed by \citet{Matthews2018}; see
also the recent review of Reverse-Bayes methods \citep{Held2021b}. In what
follows, we comment on the similarities and differences of the two approaches
and their inferential consequences. We find that decision making based on the
BAE approach is limited by the restrictive assumption that the additional
evidence must have equal or smaller variance than the variance of the observed
data.

\section{Bayesian additional evidence}
We begin by showing that fortunately -- and contrary to the statement by Sondhi
et al. on page 4 of their article -- there is a closed-form solution for what
they term the BAE ``tipping point'', which is key to their approach.

Assume, as per Sondhi et al., that both the likelihood of an effect estimate
$\hat{\theta}$ (the ``data'') and the prior of the underlying effect size
$\theta$ are represented by normal distributions
$\hat{\theta}\given \theta \sim \Nor(\theta, \sigma^{2})$ and
$\theta \sim \Nor(\mu, \tau^{2})$, with the latter evidence coming either from
pre-existing insight/studies or from a subsequent replication. Bayes's Theorem
then implies a posterior distribution
$\theta \given \hat{\theta} \sim \Nor(\mu_{p}, \tau^{2}_{p})$ whose mean and
variance satisfy
\begin{align*}
  &\frac{\mu_{p}}{\tau^{2}_{p}} = \frac{\hat{\theta}}{\sigma^{2}} + \frac{\mu}{\tau^{2}}&
  &\text{and}&
  &\frac{1}{\tau^{2}_{p}} = \frac{1}{\sigma^{2}} + \frac{1}{\tau^{2}}&
\end{align*}
Sondhi et al. further assume that $\tau^{2} = \sigma^{2}$, that is, the prior
variance $\tau^{2}$ is equal to the data variance $\sigma^{2}$ which itself is
equal to the squared (known) standard error $\sigma$ of the effect estimate
$\hat{\theta}$. It then follows that the posterior mean is the mean of the data
and the prior mean, and that the posterior variance is half the data variance
\begin{align}
  &\mu_{p} = \frac{\hat{\theta} + \mu}{2}&
  &\text{and}&
  &\tau^{2}_{p} = \frac{\sigma^{2}}{2}&
  \label{eq:varconstraints}
\end{align}

The BAE ``tipping point'' is then defined as the least extreme prior mean that
results in a posterior credible interval which excludes the null value. If the
substantive hypothesis is for positive effect estimates (\eg
$\log(\mbox{HR}) > 0$) the BAE is the prior mean which leads to the lower limit
$L_{p}$ of the $100(1 - \alpha)$\% posterior credible interval being zero
\begin{align}
  L_{p} = \mu_{p} - z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq:postcredL}
\end{align}
while for negative effect estimates the upper limit $U_{p}$ is fixed to zero
\begin{align}
  U_{p} = \mu_{p} + z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq:postcredU}
\end{align}
with $z_{\scriptscriptstyle \alpha/2}$ the $1 - \alpha/2$ quantile of the
standard normal distribution. Combining Eq.~\eqref{eq:varconstraints} with
Eq.~\eqref{eq:postcredL}, respectively Eq.~\eqref{eq:postcredU}, leads to
\begin{align}
  \text{BAE}
  & =  \sign(\hat{\theta}) \sqrt{2} \, z_{\scriptscriptstyle \alpha/2} \, \sigma - \hat{\theta}
    \label{eq:bae}
\end{align}
where $\sign(\hat{\theta}) = 1$ when $\hat{\theta} > 0$ and
$\sign(\hat{\theta}) = -1$ otherwise. Re-written in terms of the upper and lower
$100(1 - \alpha)$\% confidence interval (CI) limits $U$ and $L$ of the effect
estimate $\hat{\theta}$ we obtain
\begin{align}
  \text{BAE} = \frac{\text{sign}(\hat{\theta}) \sqrt{2} (U - L) - (U + L)}{2}
  \label{eq:baeneg}
\end{align}
We see from Eq.~\eqref{eq:bae} that Sondhi et al.'s proposal has the intuitive
property that as the study becomes more convincing (through larger effect sizes
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the BAE will decrease
(increase) for positive (negative) $\hat{\theta}$, indicating that less
additional evidence is needed to push a non-significant study towards
credibility. Eq.~\eqref{eq:bae} and Eq.~\eqref{eq:baeneg} also hold for
significant studies but the BAE then represents the mean of a ``sceptical''
prior which renders the study non-significant.

These closed-form solutions greatly simplify the use of the BAE methodology. For
example, Sondhi et al. use a comparison of monoclonals to show how it identifies
additional evidence which, when combined with a non-significant finding, leads
to overall credibility. The trial estimated the hazard ratio of the
bevacizumab+chemo patients compared to the cetuximab+chemo patients as
$\mbox{HR} = 0.42$ (95\% CI: 0.14 to 1.23), a non-significant finding with $p = 0.11$. Expressed as log(HR), we
have $L = -1.97$ and
$U = 0.21$. We use Eq.~\eqref{eq:baeneg} and find that
on log hazard ratio scale $\mbox{BAE} = -0.66$ equivalent to an
HR of $0.52$. Figure~\ref{fig:illustration} shows the
corresponding prior mean with 95\% prior
credible interval.

Thus additional evidence in the form of prior insight or a subsequent
replication supporting an HR at least as impressive as this (\ie an
$\mbox{HR} < 0.52$ in this case), and a CI at least as tight as that of the
original study will render this non-significant result credible at the 95\%
level. Sondhi et al. cite prior evidence from \citet{Innocenti2019} who found an
$\mbox{HR} = 0.13$ (95\% CI: 0.06 to 0.30) which meets both criteria set by the
BAE, and renders the original study credible.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper5/bae-comparison-fig-1}
\end{knitrout}
\caption{Comparison of BAE, AnCred, and fixed mean 95\% prior and posterior
  credible intervals for the data from \citet{Sondhi2021}. Additional data from
  \citet{Innocenti2019} are also shown.}
\label{fig:illustration}
\end{figure}

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{images/paper5/plot-2d-1}
\end{knitrout}
\caption{Relative prior mean vs. relative prior variance for the data from
  Sondhi et al. The dashed region represents parameter values, which do not lead
  to posterior credibility, whereas values in the dotted region lead to
  posterior credibility (at $\alpha = 5\%$). The
  colored lines indicate the parameters which fulfil the side-constraints of the
  respective method.}
\label{fig:priospace}
\end{figure}

\section{Alternatives approaches}
In order to get a unique solution for the BAE, Sondhi et al. make the assumption
that the prior variance equals the data variance, but also other possibilities
exist. An alternative rationale would be to set the mean of the additional
evidence, rather than variance, to that of the original finding (\ie
$\mu = \hat{\theta}$), and determining the prior variance $\tau^{2}$ such that
the posterior credible interval includes the null value. Under this approach,
the prior variance is given by
\begin{align*}
  \tau^{2} = \frac{\sigma^{2}}{z_{\scriptscriptstyle \alpha/2}^2/z^2 - 1}
\end{align*}
with $z = \hat{\theta}/\sigma$. The resulting prior represents a study with
identical effect estimate but different precision compared to the observed one.
As the observed study becomes more convincing (with larger effect estimates
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the prior will become
more diffuse, so less additional evidence is needed to render the finding
credible. We see in Figure~\ref{fig:illustration} that prior and posterior are
similar to BAE for the clinical trial data from Sondhi et al.

Figure~\ref{fig:illustration} also illustrates that the BAE and the fixed mean
approach can lead to priors which support effect sizes opposing that of the
original finding. This is not possible with the AnCred advocacy prior whose
prior credible interval is fixed to the null value so that the prior adheres to
the Principle of Fairminded Advocacy \citep{Matthews2018}. \citet{Held2021b}
showed that this constraint is equivalent to fixing the coefficient of variation
from the prior to $\tau/\mu = z_{\scriptscriptstyle \alpha/2}^{-1}$. Hence, its
mean and variance are given by
\begin{align*}
  &\mu = \frac{2 \, \hat{\theta}}{1 - z^{2}/z_{\scriptscriptstyle \alpha/2}^{2}}&
  &\text{and}&
  &\tau^{2} = \frac{\mu^{2}}{z_{\scriptscriptstyle \alpha/2}^{2}}.&
\end{align*}
We see that -- as with the fixed mean approach -- the AnCred prior becomes more
diffuse for increasingly convincing studies. However, at the same time the prior
mean also increases (decreases) for positive (negative) effect estimates, so
that only effect sizes in the correct direction are supported.

Figure~\ref{fig:illustration} shows that the AnCred advocacy prior credible
interval is far wider compared to the other approaches. Perhaps this observation
led Sondhi et al. to state that AnCred is harder to interpret than BAE, and that
it can lead to prior intervals ``wide enough to effectively contain any effect
size, which is unhelpful for decision making''. We would argue that broad priors
are a valuable diagnostic of when little additional evidence is needed to
achieve posterior credibility, as it is the case with the example Sondhi et al.
consider. Moreover, we would argue that AnCred priors are very helpful in
decision making since any additional evidence whose confidence interval is
contained in the AnCred prior credible interval will \emph{necessarily} lead to
posterior credibility when combined with the observed data \citep{Held2021b}. In
contrast, the BAE approach requires decision makers to keep in mind the variance
of the additional evidence, since only additional evidence with a point estimate
that is more extreme as the BAE and with confidence interval at least as tight
as the observed confidence interval from the study is guaranteed to lead to
posterior credibility. Assume, for example, the additional data from Innocenti
et al. had been more impressive, say, $\mbox{HR} = 0.05$, with a 95\% CI from
0.015 to 0.16. Intuition suggests, and direct calculation confirms, that this
would be even more capable of making the original finding credible. However,
this would not be clear to a decision maker using the BAE approach as currently
formulated, as the confidence interval is wider than the one of the observed
study (on the log scale).

While Sondhi et al. acknowledge the dependence of the BAE on the choice of the
prior variance, they do not give clear guidance on when it should be set to a
value different from the observed data variance. Fortunately, when the prior and
data variances differ, there is again a closed form solution for the BAE
``tipping point''
\begin{align}
  \text{BAE}(g)
  & =  \sign(\hat{\theta}) \sqrt{g \, (1 + g)} \, z_{\scriptscriptstyle \alpha/2} \, \sigma
    - g \, \hat{\theta}
    \label{eq:bae2}
\end{align}
with relative prior variance $g = \tau^{2}/\sigma^{2}$. We see from
Figure~\ref{fig:priospace} that Eq.~\eqref{eq:bae2} substantially depends on the
chosen prior variance and that the BAE based on $g = 1$ only captures a limited
range of priors which lead to posterior credibility. Unfortunately, Sondhi et
al. do not give a clear rationale for the default choice of $g = 1$. It may
therefore be more helpful for decision makers to base their decision on the more
principled AnCred advocacy prior or on a visualisation of the prior parameter
space as in Figure~\ref{fig:priospace}.

\section{Conclusion}
In summary, we welcome BAE as an interesting application of reverse-Bayes
methods, and we hope our derivation of closed-form solutions will encourage
further research. However, as currently formulated BAE lacks both a clear
rationale for the constraints on which it is based, and a sufficiently detailed
explanation allowing reliable decision-making.

\section*{Software and data}
Summary statistics on the case study were taken from \citet{Sondhi2021}. The
code to reproduce our analyses is available at
\url{https://github.com/SamCH93/BAEcomment}. A snapshot of the Git repository at
the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.

\section*{Acknowledgments}
We thank two anonymous referees and the third referee Riko Kelter for their
helpful suggestions. Financial support from the Swiss National Science
Foundation (Project \#189295) is gratefully acknowledged. The funder had no role
in study design, data collection, data analysis, data interpretation, decision
to publish, or preparation of the manuscript.

\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

### 2022-11-24 intro.Rnw
fix chapter wise references

@@
-<< "main-setup", include = FALSE >>=
-## knitr options
-library(knitr)
-opts_chunk$set(fig.height = 4,
-               echo = FALSE,
-               warning = FALSE,
-               message = FALSE,
-               cache = TRUE,
-               eval = TRUE)
-
-## should sessionInfo be printed at the end?
-Reproducibility <- FALSE
-
-## Packages
-library(ggplot2) # plotting
-library(xtable) # table
-library(ReplicationSuccess) # replication study stuff
-library(dplyr) # data manipulation
-library(UpSetR) # upset plot
-@
-
-% Aus der Promotionsordnung MNF §13 (2):
-% "Eine kumulative Dissertation besteht aus einer inhaltlich zusammenhängenden
-% und durch eine übergeordnete Fragestellung verbundenen Sammlung von
-% Manuskripten und/oder Publikationen, denen ein einführendes Kapitel
-% vorangestellt wird, das die Beiträge in eine übergeordnete Fragestellung
-% einbettet, deren wissenschaftlichen Zusammenhang sowie den Mehrwert der
-% Zusammenstellung gegenüber den einzelnen Teilen darlegt."
-
 \chapter*{Introduction}
@@
 @
+
+\newpage
+\section{Thesis summary}
+\label{sec:summary}
+\raggedbottom
+
+This thesis consists of six papers. Paper I and II (and to a lesser extent III)
+focus on extending the reverse-Bayes assessment of replication success from
+\citet{Held2020}. Paper III presents a general Bayesian framework for
+replication study design. Paper IV is a review paper about reverse-Bayes
+methodology. Paper V is a short comment on another article which proposed a
+reverse-Bayes method. Paper VI lists and illustrates questionable research
+practices in simulation studies.
+
+\startPaperSummary{PaperI}{%
+  The sceptical Bayes factor for the assessment of replication success}{%
+  Samuel Pawel, Leonhard Held \\
+  \textit{Journal of the Royal Statistical Society: Series B (Statistical
+    Methodology)}, 2022, 84(3), 879--911.
+  \url{https://doi.org/10.1111/rssb.12491}.}
+
+The reverse-Bayes approach from \citet{Held2020} is based on challenging the
+original study with a sceptical prior so that there is no longer evidence for an
+effect. Evidence is quantified in terms of credible intervals, respectively,
+tail-probabilities. However, there exist also other measures of evidence, and it
+has been a matter of long debates which is the most appropriate \citep[see
+\eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
+  Lakens2018, Amrhein2019b}. In this paper, we therefore extend the
+reverse-Bayes assessment of replication studies to use Bayes factors
+\citep{Good1958, Jeffreys1961} for quantifying evidence and prior-data
+conflict. % Bayes factors are also
+% used for prior-data conflict assessment as suggested by \citep{Box1980}.
+Similarly to the sceptical $p$-value, the procedure leads to a single measure
+for quantifying the degree of replication success, \emph{the sceptical Bayes
+  factor}. Systematic comparisons show that the sceptical Bayes factor shares
+most properties with the sceptical $p$-value due to the reverse-Bayes approach
+underlying both methods, yet in some situations conclusions may also differ
+because of their different ways of quantifying evidence. Specifically, it is
+shown that the sceptical $p$-values suffers from a certain type of ``shrinkage
+paradox'', which is avoided by the sceptical Bayes factor; when the $p$-value
+from the original study goes to zero, replication success based on the sceptical
+$p$-value can be achieved with any arbitrarily small replication effect
+estimate, whereas replication success based on the sceptical Bayes factor poses
+a finite limit on how much shrinkage is allowed. Technically, the procedure is
+more involved and closed-form solutions for the sceptical Bayes factor are only
+available in special situations. % and in terms of the
+% ``Lambert W function'' \citep{Corless1996}.
+The method is illustrated on data from the Social Sciences Replication Project
+\citep{Camerer2018}, and implemented in an R package.
+
+The idea to use Bayes factors instead of tail probabilities was suggested by
+\citet{Consonni2019} and \citet{Pericchi2020} independently in response to
+original article by \citet{Held2020}. L. Held then implemented a first version
+of the procedure for the grant application of this research project
+\citep{Heldproposal2019}. I then worked out the technical and implementation
+details, including closed-form solution for the sceptical Bayes factors,
+asymptotic properties, type-I and type-II error rates, and non-normal extensions
+of the procedure. I wrote the initial draft of the manuscript and the R package.
+Throughout, L. Held gave high-level feedback. I presented initial results at the
+GMDS and CEN-IBS conference in 2020 (online), L. Held presented the final
+results at the ISBA world meeting 2021 (online).
+
+\startPaperSummary{PaperII}{%
+  The assessment of replication success based on relative effect size}{%
+  Leonhard Held, Charlotte Micheloud, Samuel Pawel \\
+  \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
+  \url{https://doi.org/10.1214/21-AOAS1502}.}
+
+It is not clear how to numerically interpret the sceptical $p$-value, as it is
+not an ordinary $p$-value (which has a uniform distribution under the
+corresponding null hypothesis). Similarly, it is unclear which threshold should
+be used in case the sceptical $p$-value needs to be dichotomized into
+replication success/failure. In this article, we therefore look closer at the
+``success region'' of the sceptical $p$-value in terms of the relative effect
+estimate $d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a
+new default level for thresholding the sceptical $p$-value called the
+\emph{golden level} $\alpha_{G}$ (because the golden ration appears in its
+derivation). The golden level is defined through the property that for an
+original study which was just borderline significant ($p_{o} = \alpha$),
+replication success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if
+the replication effect estimate is at least as large as the original one
+($d \geq 1$). The behavior of the golden level seems to align with common sense;
+For original studies which were already convincing (in terms of their $p$-value)
+the effect estimate in the replication study is allowed to shrink, to some
+extent, whereas for less convincing original studies (those with $p$-values
+around the significance level) shrinkage is more strongly penalized. We find
+that in typical situations, replication success based on the golden level also
+has similar or improved frequentist properties (type-I error rate and project
+power) compared to the standard significance criterion. Case studies from four
+large-scale replication projects illustrate the properties of the method.
+
+L. Held had the idea to apply the sceptical $p$-value method to the data from
+the four replication projects, which I collected for my master thesis. C.
+Micheloud and L. Held came up with the golden level. L. Held wrote an initial
+draft of the manuscript. C. Micheloud, L. Held, and I then iteratively worked on
+the manuscript.
+
+\startPaperSummary{PaperIII}{%
+  Bayesian approaches to designing replication studies}{%
+  Samuel Pawel, Guido Consonni, Leonhard Held \\
+  2022. arXiv preprint.
+  \url{https://doi.org/10.48550/arXiv.2211.02552}.}
+
+An important aspect in the design of replication studies is determining their
+sample size. How exactly the sample size should be determined depends on the
+method which will be used for analyzing the replication data. Various approaches
+have been proposed for doing so which are specifically tailored to certain
+analysis methods. In this article, we provide a general Bayesian framework which
+applies to any analysis method (including the sceptical $p$-value and the
+sceptical Bayes factor). We show how the data from the original study and
+external knowledge can be combined in a \emph{design prior} for the underlying
+model parameters. Based on a design prior, predictions about the replication
+data can then be computed, and the replication sample size can be chosen such
+the probability of replication success becomes as high as desired. We illustrate
+Bayesian design of replication studies in the normal-normal hierarchical model
+which provides sufficient flexibility for specification of design priors. Data
+from a cross-laboratory replication project are used for illustrating our
+methods, which are also available in an R package.
+
+L. Held specified in the grant application of this research project
+\citep{Heldproposal2019} that we will investigate power and sample size
+calculations for the sceptical $p$-value and the sceptical Bayes factor. For the
+first paper I already derived the power function of the sceptical Bayes factor
+in closed-form for two types of design priors. After its completion, I
+generalized the result to any design prior in the normal-normal hierarchical
+model, and started working on this manuscript. I presented a first draft to L.
+Held and G. Consonni in the beginning of 2021. G. Consonni then helped
+developing the methodology for multisite replication study design. I continued
+working on the manuscript in 2022 and also wrote the accompanying R package.
+Throughout, L. Held and G. Consonni gave high-level feedback.
+
+\startPaperSummary{PaperIV}{%
+  Reverse-Bayes methods for evidence assessment and research synthesis}{%
+  Leonhard Held, Robert Matthews, Manuela Ott, Samuel Pawel \\
+  \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
+  \url{https://doi.org/10.1002/jrsm.1538}.}
+
+While the popularity of Bayesian methods has been rapidly increasing since the
+advent of modern computational methods in the 1990s, reverse-Bayes methods % , such
+% as the reverse-Bayes assessment of replication studies,
+have remained largely unknown to statisticians and users of statistics alike. In
+this article, we review reverse-Bayes history and methods to increase awareness
+about the approach. Specifically, we summarize the work on reverse-Bayes by I.
+J. Good \citep{Good1950}, who first proposed the idea. We then review methods
+such as the \emph{Analysis of Credibility} from \citet{Matthews2001b,
+  Matthews2018}, its extension to Bayes factors, and the \emph{False Positive
+  Risk} from \citet{Colquhoun2017}. To illustrate these method, we use data from
+a meta-analysis on the effect of corticosteroids on COVID-19 mortality.
+
+L. Held and M. Ott started working on this article several years ago when M. Ott
+was still a PhD student (around 2017). When I discovered the connection between
+the Analysis of Credibility and the fail-safe N method, L. Held suggested that
+it would fit nicely into this manuscript, and that I should start to overhaul
+it. I rewrote and expanded his initial draft, adding also a new section on
+reverse-Bayes approaches with Bayes factors, largely based on the work from
+paper I. We then managed to recruit R. Matthews to also contribute. From that
+point on the three of us iteratively worked on the manuscript and M. Ott gave
+high-level feedback.
+
+\startPaperSummary{PaperV}{%
+  Comment on ``Bayesian additional evidence for decision making under small
+sample uncertainty''}{%
+   Samuel Pawel, Leonhard Held, Robert Matthews \\
+  \textit{BMC Medical Research Methodology}, 2022, 22(149).
+  \url{https://doi.org/10.1186/s12874-022-01635-4}.}
+
+Shortly after the acceptance of paper III, the article by \citet{Sondhi2021}
+appeared. It proposed a novel reverse-Bayes method called \emph{Bayesian
+  Additional Evidence}, and we noted some flaws in the article. This prompted us
+to write a commentary. We show that --contrary to the statement by
+\citet{Sondhi2021}-- there is a closed form solution for the key quantity in
+their approach termed ``Bayesian Additional Evidence tipping point''.
+% The Bayesian Additional Evidence method provides an answer to the question
+% ``What prior do I have to choose so that that my unconvincing data become
+% convincing?''.
+The method is also closely related the Analysis of Credibility by
+\citet{Matthews2018}. We investigate differences and similarities of the two
+methods, showing that the priors determined through the Bayesian Additional
+Evidence method are not always helpful.
+
+R. Matthews attended us about the article from \citet{Sondhi2021}. After reading
+it, I realized that their statement about closed-form solutions was incorrect
+and derived a solution. L. Held suggested to write a commentary. I wrote an
+initial draft of the manuscript, which R. Matthews substantially improved. The
+two of us iteratively worked on the manuscript, while L. Held gave mostly
+high-level feedback.
+
+\startPaperSummary{PaperVI}{%
+  Pitfalls and Potentials in Simulation Studies}{%
+  Samuel Pawel, Lucas Kook, Kelly Reeve \\
+  2022. arXiv preprint.
+  \url{https://doi.org/10.48550/arXiv.2203.13076}.}
+
+Simulation studies are frequently used for evaluating statistical methods.
+However, several studies showed that the reporting standards in simulation
+studies have remained low over the years \citep{Hoaglin1975, Burton2006,
+  Morris2019}. Moreover, some authors have recently argued that also
+methodological research is suffering from reproducibility issues, publication
+bias, and a ``replication crisis'' due to researchers engaging in questionable
+research practices, such as selective reporting \citep{Boulesteix2020}. In this
+article, we raise awareness about these issues. We summarize possible
+questionable research practices in simulation studies, and show how easy it is
+make a method seem superior if various questionable research practices are
+employed. We also give recommendations which could help to alleviate these
+issues, most importantly we recommend researchers to write and pre-register
+simulation protocols.
+
+The manuscript is co-first authored by myself and L. Kook. I had the idea to
+invent a ``mock-method'' and use questionable research practices that make it
+seem superior, to draw attention to the low standards in methodological
+research. I then wrote a first draft of the manuscript and proposed the idea to
+L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
+and started writing the simulation protocol. L. Kook took lead in developing the
+R package and simulation study code. K. Reeve provided feedback on the
+simulation protocol and helped polishing the manuscript. Recently, I was invited
+to present the results from this project at the CEN conference 2023 in Basel.
+
+% Bibliography
+\bibliographystyle{apalikedoiurl}
+\bibliography{bibliography}

### 2022-11-24 thesis.Rnw
third paper
paper 5 added
fix chapter wise references

@@
 % ==============================================================================
-% INTRODUCTION
+% INTRODUCTION + SUMMARY
 % ==============================================================================
@@
 \pagenumbering{arabic}
-% \begin{bibunit}
-<< "introduction", child = "intro.Rnw" >>=
+
+<< "main-setup", include = FALSE, echo = FALSE, warning = FALSE, message = FALSE >>=
+## knitr options
+library(knitr)
+opts_chunk$set(fig.height = 4,
+               echo = FALSE,
+               warning = FALSE,
+               message = FALSE,
+               cache = TRUE,
+               eval = TRUE)
+
+## should sessionInfo be printed at the end?
+Reproducibility <- FALSE
+
+## Packages
+library(ggplot2) # plotting
+library(xtable) # table
+library(ReplicationSuccess) # replication study stuff
+library(dplyr) # data manipulation
+library(UpSetR) # upset plot
+
+## knit introduction first to tex so that by-chapter reference works (since chapter natbib requires "include" command)
+knitr::knit(input = "intro.Rnw")
 @
 
-\input{summary}
-% \clearpage
-% \putbib
-% \end{bibunit}
-\bibliographystyle{apalikedoiurl}
-\bibliography{bibliography}
+\include{intro}
 
@@
 
-% \includepdf[pagecommand={}, pages=-, width=1.15\textwidth, offset=0cm 0cm
-% ]{pdf/2022-Pawel_Held.pdf}
-
 % Paper II
@@
   \url{https://doi.org/10.1214/21-AOAS1502}.}
-% \includepdf[pagecommand={}, pages=-, width=1.05\textwidth, offset=0cm 0cm
-% ]{pdf/2022-Held_etal.pdf}
 
@@
   2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2211.02552}.}
-% \includepdf[pagecommand={}, pages=-, width=1.1\textwidth, offset=-0.5cm 0.4cm
-% ]{pdf/2022-Pawel_etal.pdf}
+\include{paper3}
 
@@
   \url{https://doi.org/10.1186/s12874-022-01635-4}.}
-% \includepdf[pagecommand={}, pages=-, width=1.15\textwidth, offset=0cm 0cm
-% ]{pdf/2021-Held_etal.pdf}
 
@@
   \url{https://doi.org/10.1002/jrsm.1538}.}
-% \includepdf[pagecommand={}, pages=-, width=1.2\textwidth, offset=0cm 0cm
-% ]{pdf/2022-Pawel_etal.pdf}
+\include{paper5}
 
@@
   2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2203.13076}.}
-% \includepdf[pagecommand={}, pages=-, width=1.1\textwidth, offset=0cm 0cm
-% ]{pdf/2022-Pawel_etalb.pdf}
 

### 2022-11-25 paper2.tex
paper 2 start

\section*{Abstract}
Replication studies are increasingly conducted in order to confirm original
findings. However, there is no established standard how to assess replication
success and in practice many different approaches are used. The purpose of this
paper is to refine and extend a recently proposed reverse-Bayes approach for the
analysis of replication studies. We show how this method is directly related to
the relative effect size, the ratio of the replication to the original effect
estimate. This perspective leads to a new proposal to recalibrate the assessment
of replication success, the golden level. The recalibration ensures that for
borderline significant original studies replication success can only be achieved
if the replication effect estimate is larger than the original one. Conditional
power for replication success can then take any desired value if the original
study is significant and the replication sample size is large enough. Compared
to the standard approach to require statistical significance of both the
original and replication study, replication success at the golden level offers
uniform gains in project power and controls the Type-I error rate if the
replication sample size is not smaller than the original one. An application to
data from four large replication projects shows that the new approach leads to
more appropriate inferences, as it penalizes shrinkage of the replication
estimate compared to the original one, while ensuring that both effect estimates
are sufficiently convincing on their own.

\textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
two-trials rule, type-I error rate

\section{Introduction}
Replication studies are conducted in order to investigate whether an original
finding can be confirmed in an independent study. Although replication has long
been a central part of the scientific method in many fields, the so-called
replication crisis \citep{Ioannidis2005, Begley2015} has led to increased
interest in replication over the last decade. These developments eventually
culminated in large-scale replication projects that were conducted in various
fields \citep{Errington2014, Klein2014, OSC2015, Ebersole2016, Camerer2016,
  Camerer2018, Cova2018, Klein2018}.

% Declaring a replication as successful is, however, not a
% straightforward task, and currently used approaches include
% \emph{statistical} significance of both the original and replication
% study,
%  compatibility of their effect estimates, and meta-analysis of
% the effect estimates. \emph{Many of the replication projects listed above also
%   report the relative effect size, the ratio of the
%   replication to the original effect estimate. For example, in \citet{Camerer2018}
%   the replication effect estimates were only half as large as the original ones
%   on average and even smaller in \citet{OSC2015}. This gives
%   clear evidence of a systematic bias of the original studies and
%   strongly suggests that the original and replication study should not
%   be treated as exchangeable. However, all the approaches mentioned
%   above will give the same results if the order of studies would be reversed. }

% In order to address \emph{this problem}, a new method has recently been
% proposed in \citet{held2020}. The approach combines the analysis of
% credibility \citep{matthews:2001,matthews:2001b} with a prior-data
% conflict assessment \citep{box:1980}. Replication success is declared if
% the replication study is in conflict with a sceptical prior that would
% make the original study non-significant. \emph{This approach penalizes
%   small relative effect sizes as we will see in more detail in the following.}

% To introduce some notation, let $z_o = \hat \theta_o/\sigma_o$ and
% $z_r = \hat \theta_r/\sigma_r$ denote the $z$-statistic of the
% original and replication study, respectively. Here $\hat \theta_o$ and
% $\hat \theta_r$ are the corresponding effect estimates (assumed to be
% normally distributed) of the unknown
% effect $\theta$ with standard errors $\sigma_o$ and $\sigma_r$, respectively.
% The corresponding one-sided
% $p$-values are denoted by $p_o=1-\Phi(z_o)$ and $p_r=1-\Phi(z_r)$,
% respectively, where $\Phi(\cdot)$ denotes the standard normal cumulative
% distribution function.
% Let $c = \sigma_o^2/\sigma_r^2$ denote the variance
% ratio of the squared standard errors of the original and replication
% effect estimates. The squared standard errors are usually inversely
% proportional to the sample size of each study, \ie
% $\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some
% unit variance $\kappa^2$.  The variance ratio $c$ can then be
% identified as the relative sample size $c=n_r/n_o$. The relative effect size
% \begin{equation}\label{eq:d}
%   d = \frac{\hat \theta_r}{\hat \theta_o} = \frac{1}{\sqrt{c}} \frac{z_r}{z_o}
% \end{equation}
% quantifies the size of the replication effect estimate $\hat \theta_r$ relative
% to the original effect estimate $\hat \theta_o$. The corresponding shrinkage
% of the replication effect estimate will be denoted as $s=1-d$.

% Suppose the original study achieved statistical significance at one-sided
% level $\alpha$, so $p_o \leq \alpha$.  The standard approach to assess
% replication success is based on significance of the replication effect
% estimate at the same level $\alpha$, \ie the replication is considered successful if also $p_r \leq \alpha$.
% This approach is known in drug development as the two-trials rule \citep{senn:2007}, usually
% conducted at $\alpha=0.025$.
% Let $z_\alpha = \Phi^{-1}(1-{\alpha})>0$ denote the $z$-value corresponding
% to the level $\alpha$, then significance of the replication
% \emph{study is achieved if $z_r \geq z_\alpha$, which}
% is equivalent to the \emph{condition}
% \begin{equation}\label{eq:dSig}
%    d \geq \frac{z_\alpha}{z_o  \, \sqrt{c}}
% \end{equation}
% on the relative effect size \eqref{eq:d}.
% The right hand-side goes to zero for increasing $c$, so if the
% relative sample size $c$ is large enough, significance of the
% replication study can be achieved with any arbitrarily small (but
% positive) relative effect size $d$. \emph{However, declaring replication
% success when there is substantial shrinkage is contrary to common
% sense, as the replication effect estimate may not reflect an effect
% size of the same practical relevance as the original one, despite its
% statistical significance.}

% \emph{In this paper we first review the \citet{held2020} approach for
%   the assessment of replication success, followed by showing how it
%   relates to the relative effect size (Section \ref{sec:res}). This perspective
%   is used in Section \ref{sec:goldenthresh} and \ref{sec:recalib}
%   to propose  a recalibration of the
%   method, the \textit{golden level}, which leads to a more appropriate
%   criterion for replication success compared to the two-trials rule
%   (Section \ref{sec:2TR}). In Section \ref{sec:ER} we study
%   power and Type-I error rates of the proposed method and compare it to the
%   two-trials rule. The recalibrated method ensures that conditional power can
%   take any desired value if the original study has been significant and the replication
%   sample size is large enough
% (Section \ref{sec:powerrep}), controls the overall Type-I error if the replication
% sample size is not smaller than the original one (Section \ref{sec:T1E}), and
% offers uniform
% gains in project power compared to the two-trials rule (Section \ref{sec:PP}). Section \ref{sec:application}
% describes an application to data from four replication projects and Section
% \ref{sec:discussion} closes with some discussion.}

% \clearpage
% \section{Replication success}\label{sec:RS}

% \begin{center}
% \begin{figure}[!h]
% \begin{center}
% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig1-1}

% }

% \end{knitrout}
% \caption{Example of the assessment of replication success. The original study from \citet{Pyc2010} has effect estimate  $\hat \theta_o=
%   0.4$ on Fisher's $z$ scale
%   (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value
%   $p_o = 0.011$.
%   The left part of the figure illustrates the \emph{reverse-Bayes derivation of the sufficiently sceptical prior
%     based on}
%   the original study result and the posterior with lower credible limit fixed at zero. \emph{The comparison} of the sufficiently sceptical prior with the replication study result ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$)
%   in the right part of the figure \emph{is used to assess potential prior-data conflict.}
%   \label{fig:fig1}}
% \end{center}
% \end{figure}
% \end{center}

% Hereinafter we focus on the one-sided assessment of replication
% success to ensure that replication success can only occur if the
% original and replication effect estimates go in the same
% direction. Figure \ref{fig:fig1} illustrates the \citet{held2020} approach
% based on a replication study
% from the \textit{Social Sciences Replication Project} \citep{Camerer2018}:
% the significant original finding by \citet{Pyc2010} at
% one-sided level $\alpha=0.025$ is
% challenged with a sceptical prior, sufficiently concentrated around
% zero to make the original study result no longer convincing \citep{matthews:2001,matthews:2001b}.
% Replication success is then defined as conflict between the
% sceptical prior and the result from the replication study in order to
% \emph{disprove} the sceptic. Conflict is quantified by a prior-predictive
% tail probability $p_{\mbox{\scriptsize Box}}$ \citep{box:1980} where a small value
% $p_{\mbox{\scriptsize Box}} \leq \alpha$ defines replication success.
% In Figure \ref{fig:fig1}  the original finding is only borderline significant, so the
% sufficiently sceptical prior is fairly wide.  Furthermore, there is
% substantial shrinkage
% ($d = 0.15/0.4 =
% 0.38$)
% of the replication effect estimate
% and therefore hardly any conflict with the sufficiently
% sceptical prior (one-sided $p_{\mbox{\scriptsize Box}}=0.31$).
% We are thus not able to declare replication success at
% level $2.5$\%.

% \emph{The actual value of $p_{\mbox{\scriptsize
%       Box}}$ is difficult to interpret as it depends on the level $\alpha$ and does not even exist if
%   the original $p$-value $p_o$ exceeds $\alpha$. However, }
% \citet{held2020} showed
% that if both $\sign(z_o)=\sign(z_r)$ and
% \begin{equation}\label{eq:extrinsic.p}
% \left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
% - 1 \right) \geq c
% \end{equation}
% hold, replication success at level ${\alpha_S}$ is achieved, where $z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$.
% The requirement \eqref{eq:extrinsic.p} can be assessed for \emph{any} value of
% \emph{${{\alpha_S}} > \max\{p_o, p_r\}$} and of particular interest is the
% smallest possible value of $\alpha_S$ where \eqref{eq:extrinsic.p} holds,
% the so-called {\it sceptical $p$-value} $p_S$.
% We are thus interested in the value $z_S^2$ that fulfills
% \begin{equation}\label{eq:extrinsic.p2}
% \left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
% - 1 \right) = c.
% \end{equation}
% There is a unique solution of \eqref{eq:extrinsic.p2} which defines
% the one-sided {sceptical $p$-value} $p_S=
% 1-\Phi\left({z_S}\right)$ where $z_{S} \coloneqq +
% \sqrt{z_{S}^2}$, provided
% $\sign(z_o)=\sign(z_r)$ holds.  Replication success at level
% $\alpha_S$ is then achieved if $p_S \leq
% \alpha_S$.  In the introductory example based on the original study by
% \citet{Pyc2010}, the sceptical
% $p$-value turns out to be $p_S=0.11$.

% The sceptical
% $p$-value has a number of interesting properties, see \citet[Section
% 3.1]{held2020} for details. In particular, $p_S > \max\{p_o, p_r\}$
% always holds with $p_S \downarrow \max\{p_o, p_r\}$ for $c \downarrow
% 0$. Furthermore, if the $p$-values $p_o$ and
% $p_r$ are fixed, the sceptical $p$-value
% $p_S$ increases with \emph{decreasing} relative effect size
% $d$.  The first property ensures that both the original and the
% replication study have to be sufficiently convincing on their own to
% \emph{achieve} replication success.  The second property guarantees that
% shrinkage of the replication effect estimate is penalized.

% The level for replication success $\alpha_S$ has to be distinguished
% from the significance level $\alpha$ associated with the ordinary
% $p$-value.  \citet{held2020} has used the {\it nominal level} for
% replication success ($\alpha_S=\alpha$) for convenience, but in the
% following we will propose a recalibration of the procedure along with
% a new value for $\alpha_S$, the {\it golden level} (Section~\ref{sec:goldenthresh}).
% \emph{The derivation is based on a property of the required
% relative effect size for replication success, if the relative sample size is very large
% (Section~\ref{sec:res}).}
% In a nutshell, the golden level
% ensures that for original studies which were only borderline
% significant \emph{($p_o=\alpha$)}, replication success is only possible if the replication
% effect estimate is larger than the original one \emph{($d > 1$)}.\\

% \subsection{Relative effect size}\label{sec:res}
% Without loss of generality we \emph{now} assume that $\hat \theta_o > 0$ and that
% $p_o < {\alpha_S}$ has been observed in the original study, otherwise
% it would be impossible to achieve replication success at level
% $\alpha_S$ because $p_S$ is always larger than $p_o$.
% The condition \eqref{eq:extrinsic.p} for replication
% success can then be re-written as
% \begin{equation}\label{eq:eq.z}
%   z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
% \end{equation}
% where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of
% \eqref{eq:eq.z} is the minimum replication $z$-value $\zrmin$ required
% to achieve replication success.  Note that $\zrmin$ increases with increasing $c$, so increasing the replication
% sample size leads to a more stringent success requirement \emph{for $z_r$ and the corresponding} replication
% $p$-value $p_r$.

% Equation \eqref{eq:eq.z} can be further transformed to a
% condition on the relative effect size \eqref{eq:d}:
% \begin{equation}\label{eq:res}
%   d \geq  \frac{\sqrt{1+c/(K-1)}}{ \sqrt{c K}} \eqqcolon \dmin .
% \end{equation}
% To achieve replication success, the relative effect size
% must be
% at least as large as the right hand-side of \eqref{eq:res}, the
%   minimum relative effect size $\dmin$, a function of $K$ and the
% relative sample size $c$.
% If the relative sample
% size becomes very large, \ie $c \rightarrow \infty$, we have
% $\dmin \downarrow \dinfty$ where
% \begin{equation}\label{eq:smallestpossible}
%   \dinfty = 1/\sqrt{K (K-1)}
% \end{equation}
% \emph{is the {\it limiting relative effect size}.}
% This shows that the minimum relative effect size $\dmin$ in \eqref{eq:res}
% does not go to zero for increasing $c$, so replication success cannot
% be achieved if the relative effect size $d$ is smaller or equal to
% $\dinfty$, no matter how large the replication study is.
% \emph{In contrast}, the corresponding criterion \eqref{eq:dSig} \emph{of the
% two-trials rule}
% can be achieved for any positive relative effect size, regardless of
% how small, provided the replication sample size is sufficiently large.

% \subsection{The golden level}\label{sec:goldenthresh}
% Significance of both the original and the replication study at level
% $\alpha$ is a necessary but not sufficient requirement for replication
% success at the nominal level ($\alpha_S = \alpha$).  The nominal level
% may therefore be too stringent.  It is more reasonable to calibrate
% the procedure in such a way that to establish replication success,
% original and replication study do not both necessarily need to be
% significant at level $\alpha$, provided that the replication effect
% estimate does not shrink compared to the original one.  We therefore
% choose a level $\alpha_S$ such that a borderline
% significant original study ($p_o = \alpha$) cannot lead to replication
% success if there is shrinkage $s > 0$ of the replication effect
% estimate.  Mathematically, this translates to setting $\dinfty = 1$
% and $K = z_\alpha^2/z_{\alpha_S}^2$ in~\eqref{eq:smallestpossible} and
% leads to the quadratic equation $K(K-1) = 1$ with solution
% $K = \varphi$ where
% $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
% known as the golden ratio. Solving for $z_{\alpha_S}$ gives
% \emph{$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$
% and the corresponding  \textit{golden level}
% \begin{eqnarray}\label{eq:golden}
% \alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
% \end{eqnarray}
% for replication success. }
% This is our recommended default choice to assess replication success and we will study its properties in the following
%                    in more detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$),
% the golden level is $\alpha_S =0.062$.
% In the introductory example
% shown in Figure \ref{fig:fig1},
% the sceptical $p$-value is $p_S=0.11 > 0.062$, so
% the replication  of the \citet{Pyc2010} study was not successful.

% \emph{The golden level \eqref{eq:golden} is derived from~\eqref{eq:smallestpossible} with $\dinfty = 1$.
% However, we may also use a different value for the
% limiting relative effect size $\dinfty$, say $\dinfty=0.8$.
% Then replication success is only possible for a borderline significant result ($p_o = \alpha$)
% if there is less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication effect estimate.
% This approach is equivalent to a limiting relative effect size of 1 if the original $p$-value
% $p_o$ is equal to a different level $\alpha'$, which can be derived as follows:
% First, solving \eqref{eq:smallestpossible} for $\dinfty > 0$ gives
% $K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
% $\alpha'$ fulfills  $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so $z_\alpha^2/K=z_{\alpha'}^2/\varphi$
% and therefore
% \begin{equation}\label{eq:alphaPrime}
% \alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
% \end{equation}
% For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.
% }

% \subsection{Recalibration of the sceptical $p$-value}\label{sec:recalib}

% The condition $p_S \leq \alpha_S$ for replication success at the
% golden level is equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$,
% \ie $z_S \sqrt{\varphi} \geq z_\alpha$.  In practice it may be
% preferable to recalibrate the sceptical $p$-value
% $p_{S} = 1 - \Phi(z_S)$ to
% $ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be
% compared to $\alpha$ (rather than $\alpha_S$) to assess replication
% success and can thus be interpreted on the same scale as an ordinary
% $p$-value.  For example, the recalibrated sceptical $p$-value for the
% replication of \citet{Pyc2010} turns out to be
% $\tilde{p}_S=0.061$ and does not lead to replication
% success at \emph{any level $\alpha<0.061$, including} the
% standard $0.025$ level.

% \subsection{Comparison with the two-trials rule}\label{sec:2TR}
% A useful benchmark for comparison is the two-trials rule in drug
% development \citep[Section 9.4]{kay:2015}, which requires ``at least
% two adequate and well-controlled studies, each convincing on its own,
% to establish effectiveness'' \citep[p.~3]{FDA1998}.  This is usually
% achieved by independently replicating the result of a first study in a
% second study, both significant at one-sided level
% $\alpha=0.025$.  {It is worth noting that in practice the two trials are often run in parallel} {\citep{senn:2007}}{, so do not exactly resemble the replication setting.}

% The main difference between the replication success and the two-trials
% rule approach concerns how shrinkage of the replication effect
% estimate is handled. Figure~\ref{fig:fig2} illustrates that
% shrinkage is penalized in the assessment of replication success, \ie
% the original $p$-value needs to be quite small to achieve replication
% success for a relative effect size $d<1$. In contrast, significance of
% the replication study can be achieved even if there is substantial
% shrinkage, provided the replication sample size is large enough.

% \begin{figure}[!h]
% \centering
% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig2-1}

% }

% \end{knitrout}
% \caption{Comparison of replication success at the golden level ($p_S \leq \alpha_S =
% 0.062$) and the two-trials rule ($p_o \leq 0.025$ and $p_r \leq 0.025$).
% The \emph{dotted} areas indicate that success is
% impossible for original $p$-value $p_o$ and relative effect size $d$.
% In the white areas success is possible and
% depends on the relative sample size $c$ as indicated by the grey lines.
% \emph{The dashed black line in the left plot indicates the limiting relative
% effect size $\dinfty$.}
% }
% \label{fig:fig2}
% \end{figure}

% It is interesting to directly compare the two-trials rule and
% replication success at the golden level in terms of
% the required relative effect size $d$ to fulfill the criteria
% \eqref{eq:dSig} and \eqref{eq:res}, respectively, see Figure~\ref{fig:fig2}.  If the original
% $p$-value is not significant at level $\alpha$, only replication
% success can be achieved, but will require a replication effect
% estimate larger than the original one.
% \emph{
%   For example, four studies with one-sided
%   $p_o \in (0.025, 0.03)$ have been included in the
%   \textit{Reproducibility Project: Psychology} \citep{OSC2015} and one
%   of them achieves replication success (see Section \ref{sec:application} for
%   details).  By definition, such non-significant original findings can
%   never fulfill the two-trials rule.
% }

% If the original $p$-value is
% smaller than $\alpha$, then the situation depends on the relative
% sample size $c$.  For example, when the replication sample size is
% chosen to be the same as in the original study ($c=1$) and
% $\alpha=0.025$, original studies with a $p$-value larger than
% $0.006$ will require a smaller relative effect
% size $d$ with the two-trials rule, while $p$-values smaller than
% $0.006$ will require a smaller relative effect
% size $d$ with the replication success method.  This illustrates that
% the latter method is less stringent than the two-trials rule if the
% original study is already sufficiently convincing.

% \section{Power and Type-I Error Rate}\label{sec:ER}
% Although Bayesian methods do not rely on the frequentist paradigm of
% repeated testing, it is still useful to investigate their frequentist
% operating characteristics \citep{Dawid1982, Rubin1984, Grieve2016}
% and this also holds for the proposed reverse-Bayes assessment of
% replication success. We first condition on the results from the original
% study and compare the power to achieve replication success with the two-trials
% rule in Section \ref{sec:powerrep}.
% We then
% assume that none of the two studies have been conducted and
% investigate the \emph{overall} Type-I error rate (Section \ref{sec:T1E}) and the project power
% (Section \ref{sec:PP})
% \citep{Maca2002} \emph{over both studies in combination for fixed relative sample size $c$}.

% \subsection{Conditional power}\label{sec:powerrep}

% \begin{figure}[!ht]
% \begin{center}
% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig3-1}

% }

% \end{knitrout}
% \end{center}
% \caption{\emph{Conditional} power as a function of the {one-sided}
%   $p$-value of the original study with \emph{relative} sample size
%   $c=1$ (left) and $c=5$ (right). Shown is
%   conditional power \emph{assuming the unknown parameter is equal to
%   the original effect estimate (solid)} \emph{and conditional
%     power based on 20\% shrinkage of the original
%     effect estimate (dashed)} for the two-trials rule (2TR) at level
%   $\alpha = 0.025$ and for replication success
%   % (RS)
%   at the
%   corresponding golden and nominal level. Power values of exactly zero
%   are omitted.}
% \label{fig:fig3}
% \end{figure}

% Figure~\ref{fig:fig3} compares the power for replication success
% \emph{\citep[see][Section 4 for details]{held2020}} at the golden and at
% the nominal level with the power of the two-trials rule for relative
% sample size $c = 1$ (left) and $c = 5$ (right)
% as a function of the one-sided $p$-value \emph{$p_o$} from the original
% study.  \emph{Shown is the conditional power assuming the unknown parameter
%   $\theta$ is equal to the original effect estimate $\hat \theta_o$. Then
% $\hat \theta_r \given \hat \theta_o \sim \Nor(\hat \theta_o, \kappa^2/n_r)$
% and it follows that
% $d \given \hat \theta_o \sim \Nor(1, 1/(c z_o^2))$.
% The conditional power for replication
% success can therefore be calculated as
% \begin{equation}\label{eq:condPower}
% \P(d \geq \dmin \given \hat \theta_o) = \Phi\left[\sqrt{c} z_o (1-\dmin)\right],
% \end{equation}
% where $\dmin$ is
% given in \eqref{eq:res}.  Predictive power, which is conditional
% power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution
% for the effect size $\theta$, could also be calculated, then
% \mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}.
% Conditional and predictive power of the two-trials rule
% also depend on $z_o$, $c$ and $\alpha$ and are given in
% \citet{MicheloudHeld2021}.}

% The two-trials rule requires a significant original study and hence it is
% impossible to power a replication study when $p_o > 0.025$.
% \emph{The same applies for replication success at the nominal level,
% where the power is zero for any $p_o > 0.025$, regardless
% of the replication sample size.
% This is different for the golden level,
% where the conditional power of an original study with $0.025 < p_o
% < 0.062$ is low, but not zero.}
% \emph{However, if the original $p$-value $p_o$ is slightly smaller than
% $0.025$, the two-trials rule has a larger power, both for $c=1$ and $c=5$. }
% \emph{But if the original $p$-value is sufficiently
% small ($p_o < 0.006$ for $c=1$), the power for replication success at the golden level is larger
% than the power of the two-trials rule. }

% \emph{ Compared to
%   $c=1$, the conditional power for $c=5$
%   of both the two-trials rule
%   and the replication success approach at the golden level
%   increases if $p_o \leq \alpha$.     A remarkable feature of the
%   replication success approach at the golden level is that conditional
%   power can be pushed towards 100\% for large enough $c$ if
%   $p_o<\alpha$, but not otherwise. This can be seen from \eqref{eq:condPower} because
%   $\dmin < 1$ for $p_o<\alpha$ and large enough relative sample size $c$.
% On the other hand, for $p_o > \alpha$ conditional power for replication success
% will tend to 0\% for increasing $c$ because $\dmin>1$ for all $c$. Finally, for $p_o = \alpha$
% the limit is 50\%.
%   The same
%   property can be observed at the nominal level, however at the
%   smaller threshold $1-\Phi(z_\alpha \sqrt{\varphi})$ which is $0.006$ for  $\alpha=0.025$. Only if $p_o < 0.006$ will the conditional power
%   for replication success attain 100\% for $c \to \infty$. This further highlights the stringency
%   of the nominal level.  }

% \emph{The approach described so far takes the original study at
%   face-value since it assumes that $\hat \theta_o$ is equal to the unknown effect size $\theta$.
%   In practice, however,
%   there are often good reasons to believe that original effect estimates
%   have a tendency to be inflated (\eg due to publication bias). One
%   way to address this issue is to base power calculations on a
%   shrunken version of the original effect
%   estimate, where the amount of shrinkage is guided by domain knowledge and
%   a risk of bias assessment of the original study.
%   For illustration, Figure~\ref{fig:fig3} also shows conditional power based
%   on 20\% shrinkage of the original effect estimate
%   which reduces the conditional power for all methods, especially for
%   a relative sample size $c = 1$.  Conditional power for
%   replication success at the golden level can now be pushed towards 100\%
%   only for $p_o < 0.018$, which can be derived by
%   solving \eqref{eq:alphaPrime} for $\alpha$ with
%   $\alpha'=0.025$ and $\dinfty=0.8$.  To be able to
%   push conditional power based on 20\% shrinkage towards 100\% for all
%   $p_o < 0.025$,
%   equation \eqref{eq:alphaPrime} would have to be used directly to relax the level
%   from $\alpha=0.025$ to $\alpha'=0.033$.
%   }

% \subsection{Overall Type-I error rate}\label{sec:T1E}
% \emph{The two studies are assumed to be independent with Type-I error
% rate fixed at $\alpha$ for each of them,} so the Type-I error rate of the
% two-trials rule \emph{over the entire project} is simply $\alpha^2$ for
% any value of the relative effect size $c$.
% In contrast, the Type-I
% error rate of the proposed replication success assessment {depends on}
% \emph{the relative sample size} $c$.

% For $c=1$, \citet[Section 3]{held2020} showed that $z_S^2$ in \eqref{eq:extrinsic.p2}
% simplifies to half the harmonic mean of the squared test statistics
% $z_o^2$ and $z_r^2$.  The
% connection $z_S^2 = z_H^2/4$ to the harmonic mean $\chi^2$-test
% statistic $z_H^2$ \citep{held2020b}, which has a
% $\chi^2(1)$-distribution under the null hypothesis, makes it
% straightforward to compute the Type-I error rate  at level
% $\alpha_S$ for $c = 1$ as
% \begin{eqnarray}\label{eq:T1E}
% \mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
%  \right]\right\}/2.
% \end{eqnarray}
% For the golden level $\alpha_S =0.062$ at
% $\alpha = 0.025$, the Type-I error rate \eqref{eq:T1E}
% is $0.0515$\%, slightly less than the Type-I
% error rate $\alpha^2=0.0625$\% of the
% two-trials rule.  For comparison, the Type-I error rate at the nominal
% level $\alpha_S=0.025$ is
% $0.0022$\%, \emph{much} smaller than
% 0.0625\%.

% For $c \neq 1$,  the Type-I error rate can be calculated through numerical
% integration:
% \begin{equation}\label{eq:T1E0}
%   \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
% \P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
%   \phi(z_o) \, dz_o,
% \end{equation}
% where $\phi(\cdot)$ denotes the standard normal density function.
% The first term in the integral of \eqref{eq:T1E0} is the probability of
% replication success at level $\alpha_S$ conditional on a fixed original test
% statistic $z_o$ and a relative sample size $c$.
% Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
% this term simplifies to
%   $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$
% where $\zrmin$ in \eqref{eq:eq.z} depends on $z_o$, $c$, and $\alpha_S$.

% \begin{figure}[!h]
% \centering

% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig4-1}

% }

% \end{knitrout}

% \caption{\emph{Overall} Type-I error rate (left) and project power (right) for fixed relative sample size $c$.
%   Results are given for replication success
%   % (RS)
%   at the nominal and golden
%   level and compared with the two-trials rule (2TR) at $\alpha = 0.025$.
%   \emph{The dashed darkgrey line is the project power at the golden level based on significant original studies ($p_o \leq 0.025$).}
%   The power of the original study is 90\%.}
% \label{fig:fig4}
% \end{figure}

% The left plot in Figure \ref{fig:fig4} displays the Type-I error
% rate for $\alpha=0.025$ as a function of the relative sample
% size $c$.  It can be seen that the Type-I error \emph{of the replication success approach} decreases with
% increasing relative sample size $c$. \emph{This also follows from \eqref{eq:T1E0}
%   where
% $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$
% decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
% see equation \eqref{eq:eq.z}. }

% The Type-I error rate of the nominal level is always below the target
% $0.0625$\%.  Although the Type-I error will
% eventually attain $\alpha^2$ in the limit $c \downarrow 0$
% \citep[Section 3.4]{held2020}, the nominal level seems to be too
% stringent for realistic values of $c$.  The Type-I error rate of the
% golden level is smaller than $0.0625$\% for
% $c >0.85$.  Appropriate Type-I error control is
% thus ensured even for replication studies where the sample size is
% slightly smaller than in the original study.

% \begin{figure}[!ht]
% \begin{center}

% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig5-1}

% }

% \end{knitrout}

% \end{center}
% \caption{\emph{Overall Type-I error rate if the
%   replication sample size equal to the original study
%   ($c=1$).  The two-trials rule (2TR)
%   is compared to replication success
%   % (RS)
%   at the
%   golden and nominal level for different values of $\alpha$.}}
% \label{fig:fig5}
% \end{figure}

% \emph{Figure \ref{fig:fig5} compares for $c=1$ the Type-I error rate \eqref{eq:T1E}
%   of replication success at the golden and at the nominal level
%     with the
%   two-trials rule for different values of $\alpha$. The
%   Type-I error rate of the two-trials rule is $\alpha^2$ and the
%   replication success approach at the nominal level always has a much
%   smaller Type-I error rate than $\alpha^2$.  At the golden level
%   the Type-I error rate of the
%   replication success approach is much closer to $\alpha^2$, still slightly smaller
%   if $\alpha < 0.058$. For $\alpha = 0.058$ the
%   Type-I error rate is equal to the
%   Type-I error rate $0.058^2 = 0.34\%$ of the
%   two-trials rule and for $\alpha > 0.058$ the
%   Type-I error rate is slightly larger than $\alpha^2$.
%   The
%   Type-I error rate for replication success decreases with
%   increasing $c$, so as long as the replication sample size is not
%   smaller than the original sample size, Type-I error control at
%   $\alpha^2$ is guaranteed at the golden level for any one-sided level
%   $\alpha < 0.058$.}

% \subsection{Project power}\label{sec:PP}
% Under the alternative we have
% $z_o\sim \Nor(\mu, 1)$ with $\mu = z_\alpha + z_\beta$
% where $\alpha$ is
% the assumed significance level and
% \emph{
% $1-\beta = \Phi(\mu - z_\alpha)$
% is the power to detect the
% assumed effect $\theta = \mu \sigma_o$ in the original study \citep[Section 3.3]{mat2006}.
% In the following
% $\alpha=0.025$ and $\beta=0.1$ are
% used. The power of a significant
% replication study with sample size $n_r = c n_o$ is
% \begin{equation*}
% \Phi(\theta/\sigma_r - z_\alpha) =
% \Phi(\sqrt{c} \mu - z_\alpha),
% \end{equation*}
% }
% so
% depends on $\mu$ and the relative sample size $c$. The project power of the
% two-trials rule is therefore $(1-\beta) \, \Phi(\sqrt{c} \mu - z_\alpha)$ \emph{and increases with increasing $c$.}

% The project power for replication success is computed as
% \begin{equation*}
%   \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
% \P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
%   \phi(z_o - \mu) \, dz_o
% \end{equation*}
% and shown in the right plot of Figure \ref{fig:fig4} as a function
% of $c$.  For the golden level, the project power quickly increases to
% values above 90\%, whereas the nominal level only reaches around 80\%
% project power. The project power based on the two-trials rule is shown
% for comparison, which is always smaller than for the golden level
% and converges to 90\% for large $c$.

% \emph{The advantage in power stems partly from replication success still
%   being possible when the original $p$-value is larger than 0.025, but
%   smaller than 0.062. If we assume that a replication study is
%   only conducted if the original study is significant (with
%   $p_o \leq 0.025$), then the project power based on the
%   golden level (the dashed line in Figure \ref{fig:fig4}) is
%   slightly smaller and for $c>1$ barely different than for the
%   two-trials rule.  More substantial gains are still visible for
%   $c < 1$.
%   However, the restriction to original studies with
%   $p_o \leq 0.025$ may not reflect current practice in
%   large-scale replication projects. For example, 5 out of
%   143 replication studies considered in Section
%   \ref{sec:application} do have original $p$-values between
%   0.025 and 0.062.  }

% \section{Application}\label{sec:application}
% In this section, we illustrate the proposed methodology using
% data from four replication projects.
% All four projects reported effect estimates that were transformed to
% correlation coefficients ($r$). This scale allows for easy comparison of
% effect estimates from studies that investigate different phenomena
% \emph{and} is bounded to the interval between minus one and one.
% Moreover, the Fisher $z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$
% can be applied to the correlation coefficients, resulting in the transformed
% estimates being asymptotically normal with variance which is only a function
% of the study sample size $n$, \ie $\Var(\hat{\theta}) = 1/(n - 3)$
% \citep{Fisher1921}.

% The first data set comprises the results from the \textit{Reproducibility Project:
% Psychology} \citep{OSC2015}, whose aim was to replicate 100 studies, all of which
% were published in three major Psychology journals in 2008. For our purpose only
% the 73 study pairs from the ``meta-analytic'' subset are considered, since only
% for these studies the standard error of the Fisher $z$-transformed effect
% estimates can be computed \citep{Johnson2016}.
% The second data set comes from the \textit{Experimental Economics Replication
% Project} \citep{Camerer2016} which attempted to replicate 18 experimental
% economics studies published in two high impact economics journals between 2011
% and 2015.
% The third data stem from the \textit{Social Sciences Replication Project}
% \citep{Camerer2018} where 21 replications of studies on the social sciences
% were carried out, all of which were originally published in the journals
% \textit{Nature} and \textit{Science} between 2010 and 2015.
% The last data set originates from the \textit{Experimental Philosophy Replicability
% Project} \citep{Cova2018} which involved 40 replications of studies from the
% emerging field of experimental philosophy. Since only for 31 studies effective
% sample size for original and replication study were available simultaneously,
% only these pairs were included. For more information on the data sets see
% also \citet{Pawel2020}.

% Table~\ref{tab:marginalres} presents overall results for each of the
% replication projects. While the median relative effect size is below one for
% all of the four projects, there are still large differences. For
% example, the median relative effect size is only
% $0.29$
% in the Psychology project, whereas it is
% $0.86$ in the Philosophy project. The degree of shrinkage is also
% reflected in the success rates (according to the two-trials rule and the replication
% success approach \emph{at the golden level}), which are around 30\% for the former and more than 70\%
% for the latter. The proportion of successful replications is similar for the
% two-trials rule and the replication success approach. \emph{In the Experimental
% Economics project the methods perfectly agree, while in the other three projects
% the methods disagree for a few studies.}

% \begin{table}[!ht]
% \caption{Results for each replication project:
% Relative effect size $d$ (median with 25\% and 75\% quantiles on Fisher's $z$ scale), proportion of
% successful replications with the two-trials rule (2TR) and the replication success (RS)
% approach (at the golden level), and number of studies where the methods disagree.}
% % \resizebox{\textwidth}{!} {
% % latex table generated in R 4.0.5 by xtable 1.8-4 package
% % Fri Nov 25 10:07:05 2022
% \begin{tabular}{lcccc}
%   \toprule
% Project & relative effect size $d$ & 2TR (\%) & RS (\%) & discrepant \\
%   \midrule
% Psychology & 0.29 [0.03, 0.77] & 28.8 & 30.1 & 3/73 \\
%   Experimental Economics & 0.67 [0.35, 0.92] & 55.6 & 55.6 & 0/18 \\
%   Social Sciences & 0.52 [0.13, 0.65] & 61.9 & 52.4 & 2/21 \\
%   Experimental Philosophy & 0.86 [0.47, 1.12] & 74.2 & 71.0 & 1/31 \\
%    \bottomrule
% \end{tabular}

% % }
% \label{tab:marginalres}
% \end{table}

% \begin{figure}[!h]
% \centering
% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig6-1}

% }

% \end{knitrout}
% \caption{Relative effect size $d$ versus original $p$-value $p_o$.
% Black indicates that replication success was achieved at the golden level
% while grey indicates that it was not. The diamonds mark studies where
% the replication success approach (at the golden level) and the two-trials rule disagree. The dashed
% black line indicates the \emph{limiting relative effect size}
% at the golden level with $\alpha = 0.025$.
% }
% \label{fig:fig6}
% \end{figure}

% Figure~\ref{fig:fig6} displays the relative effect size $d$ versus the
% original $p$-value $p_o$ for each study pair and stratified by project.
% Note that one study pair from the Philosophy project is not shown due to
% extremely small original $p$-value and another study pair from the Psychology project
% is not shown due to a very large relative effect size.
% We can see that for most of the study pairs, the replication success approach
% and the two-trials rule lead to the same conclusion, only six replications
% show conflicting results.
% They are highlighted with diamonds in Figure~\ref{fig:fig6} and their
% characteristics are summarised in Table~\ref{tbl:discrep}.
% \begin{table}[!ht]
% \caption{Characteristics of studies for which the replication success approach
% (at the golden level)
% and the two-trials rule disagree (at one-sided $\alpha = 0.025$). Shown are relative
% sample size $c$, relative effect size $d$, original, replication and recalibrated sceptical
% $p$-value $p_o$, $p_r$ and $\tilde{p}_S$.}
% \label{tbl:discrep}
% % \resizebox{\textwidth}{!} {
% % latex table generated in R 4.0.5 by xtable 1.8-4 package
% % Fri Nov 25 10:07:05 2022
% \begin{tabular}{lllllll}
%   \toprule
% Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
%   \midrule
% \citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
%   \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
%   \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
%   \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
%   \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
%   \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
%    \bottomrule
% \end{tabular}

% % }
% \end{table}
% Two studies from the Psychology project show replication success
% but fail the two-trials rule.
% These studies show $p$-values that are slightly above the significance
% threshold in either original or replication study, but do not exhibit much
% shrinkage; in
% the replication of \citet{Oberauer2008}, the replication $p$-value was
% $p_r = 0.035$,
% a little too large to pass the two-trials rule. However, as the replication
% effect estimate shrunk only about
% $30$\%
% compared to the original one, replication success is still achieved. Conversely,
% the original $p$-value
% $p_o = 0.028$
% in \citet{Schmidt2008} was just above the significance level, yet the
% replication led to a highly significant result
% $p_r < 0.0001$
% with the effect estimate being even
% $30$\%
% larger than the original counterpart, which therefore also resulted in
% replication success.

% The remaining conflicting studies do not show replication
% success despite passing the two-trials rule.
% In all cases, there is substantial shrinkage of the replication effect estimate
% compared to the original one. For instance, in the replication study of
% \citet{Pyc2010}, the estimate shrunk by
% $62$\%
% and the replication $p$-value was only significant because the
% sample size was increased by a factor of
% $c = 9.2$.

% \emph{This analysis was based on the default choice $\dinfty=1$
%   at $\alpha=0.025$ for the golden level as described in Section
%   \ref{sec:goldenthresh}. We may also choose a different value for the
%   limiting relative effect size $\dinfty$ at $\alpha=0.025$ which then
%   corresponds to $\dinfty=1$ at a different level $\alpha'$ as given in \eqref{eq:alphaPrime}.  Figure
%   \ref{fig:fig7} compares the proportion of successful
%   replications with the replication success approach for
%   $\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
%   corresponding levels
%   $\alpha' \in (0.06,
%   0.022)$ for all four replication projects.
%   We can see that the two proportions agree fairly well for all values
%   of $\alpha'$ considered. The number of discrepant studies in each project varies
%   between 0 and 3.   Only in the Psychology project there are
%   some studies which are successful with the replication success approach but
%   not the two-trials rule
%   and some studies successful with the two-trials rule but not the replication
%   success approach.  The proportion of studies where both
%   methods are successful (also shown in Figure \ref{fig:fig7}) is then smaller than the proportion of
%   successful replications with either one of the two methods.  The
%   three discrepant studies  from the Psychology project listed in the top three rows of
%   Table~\ref{tbl:discrep} are an example of this particular feature.
% }

% \begin{figure}[!htb]
% \begin{knitrout}
% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

% {\centering \includegraphics[width=\maxwidth]{figure/fig7-1}

% }

% \end{knitrout}
% \caption{Proportion of successful replications as a function of the limiting
% relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
% equivalent level $\alpha'$ where the corresponding limiting relative effect size is 1.
% The replication success (RS) approach is compared with the two-trials rule (2TR).}
% \label{fig:fig7}
% \end{figure}

% \section{Discussion}\label{sec:discussion}
% In this paper, we have expanded on the replication success approach introduced
% in \citet{held2020} and demonstrated its advantages over alternative methods
% such as the two-trials rule. In particular, the method provides an attractive
% compromise between hypothesis testing and estimation,
% as it penalizes
% shrinkage of the replication effect estimate compared to the original one,
% while ensuring that both are statistically significant to some extent.
% %% For instance, the method will indicate only a low degree of replication success when
% %% the replication study shows a much smaller but statistically significant
% %% effect estimate, whereas it can still indicate some degree of
% %% success when either original or replication $p$-value are slightly above the
% %% significance level. %% , provided their effect estimates are compatible.
% %% %% \todo{SP: maybe ``provided the replication estimate does not shrink?''}

% We further refined the method by proposing the golden level, a
% new threshold for replication success. It guarantees that borderline
% significant original studies can only be replicated successfully if
% the replication effect estimate is larger than the original
% one. Compared to the two-trials rule, the golden level offers uniform
% gains in project power and controls the Type-I error rate \emph{at any
%   one-sided level $\alpha < 0.058$} if the
% replication sample size is not \emph{smaller than the original one}.
% Empirical evaluation of data from four replication projects highlights
% that in most cases the methods are in agreement, however, for the
% study pairs where the approaches disagree, the replication success
% approach seems to lead to more sensible conclusions.
% \emph{The good performance has been recently confirmed by a comparison of different
%   replication success metrics through a simulation study in the
%   presence of publication bias \citep{Muradchanian2021}.}

% Despite a lack of agreement as to which statistical method should be used to
% evaluate replication studies, conclusions based on different methods usually
% agree. Nevertheless, in some cases, classical methods such as the two-trials
% rule may produce anomalies. We argue that
% the replication success approach improves upon existing methods leading to
% more appropriate inferences and decisions that better
% reflect the available evidence.
% \emph{However, in extreme cases the performance of the sceptical $p$-value may be
%   considered as strange or even counterintuitive. Specifically, if the
%   original study was only borderline significant, a highly significant
%   replication study can only lead to success if the replication effect
%   estimate is larger than the original one. To understand this
%   behaviour it is important to realize that the proposed approach does
%   not synthesize the evidence from the two studies (like a standard
%   meta-analysis). The sceptical $p$-value is designed to confirm
%   claims of new discoveries through replication, but will remain
%   ``stubborn'' \citep{LyWagenmakers2020} if the original study was not
%   particularly convincing, even if the replication study
%   provides overwhelming evidence for an effect.  It will lead to a
%   different result if the order of studies was reversed, as long as
%   original and replication study do not have the same sample size
%   ($c \neq 1$).  The related harmonic mean $\chi^2$-test
%   \citep{held2020b} for evidence synthesis of two or more studies
%  also requires  each study to be convincing on its own to a certain degree, but
%   treats them as exchangeable. }

% With this paper we further advanced the reverse-Bayes methodology for
% the analysis and design of replication studies, yet certain
% limitations and opportunities for future research remain: First,
% assuming normality of the effect estimates may be questionable,
% especially for small sample sizes, and more robust distributional
% assumptions could be considered.  Second, in some types of analyses
% (\eg regression or ANOVA) the effect estimate is a vector and the
% approach would need suitable adaptations.
% Third, there is a recent trend to not only conduct one but
% several replications for one original study \citep[\eg][]{Klein2014, Ebersole2016, Klein2018}.
% Also for this situation,
% the method would need to be adapted, \eg the replication estimates
% could be first synthesized and an analysis of replication
% success could be performed subsequently.

% \emph{Throughout the paper we have assumed that the relative sample size is
% fixed in advance.  In practice the sample size of the replication
% study is often chosen based on the result of the original study
% \citep{Anderson2017}.  Power calculations as shown in Figure
% \ref{fig:fig3} can then be inverted to determine the appropriate
% sample size of the replication study. We can also invert
% equation \eqref{eq:res} to obtain the required replication sample size
% based on the specification of the minimum relative effect size $\dmin$
% to achieve replication success.
% This novel way of calculating the sample size requires the
% specification of the minimum relative effect size which can
% still be considered as acceptable.  Sample size calculations based on
% the two-trials rule can also be formulated in terms of the minimum
% relative effect size by inverting equation \eqref{eq:dSig}.
% We will report on a detailed comparison of the
% different approaches in future work. }

% \section*{Data and Software Availability}
% Data analyzed in this
% article and software are available in the R-package \texttt{ReplicationSuccess},
% which can be installed by running the following command in an R console:
% \texttt{install.packages("ReplicationSuccess", repos = \\"{http://R-Forge.R-project.org}"}).
% Further information on
% data preprocessing can be found on the corresponding help page
% (with the command \texttt{?RProjects}).

% \section*{Acknowledgments}
% Support by the Swiss
% National Science Foundation (Project \#~189295) is gratefully
% acknowledged. We acknowledge helpful and
% constructive comments by the Editor and a referee on an earlier version of this article.

\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

### 2022-11-25 thesis.Rnw
paper 2 start

@@
 \documentclass[a4paper, pagesize, twoside, open=right, cleardoublepage=empty,
-headinclude=false, footinclude=false, headsepline, footsepline, parskip=half,
+headinclude=false, footinclude=false, % headsepline, footsepline,
+parskip=half,
 numbers=noendperiod, BCOR=10mm, DIV=18 ]{scrreprt}
@@
   \url{https://doi.org/10.1214/21-AOAS1502}.}
+\include{paper2}
 

### 2022-11-25 intro.Rnw
paper 2 start
paper 2

@@
 \chapter*{Introduction}
+\phantomsection
 \addcontentsline{toc}{chapter}{Introduction}
@@
                                      This criterion is equivalent to $p_{Q} \geq \alpha$ where
-                                     $p_{Q}$ is the $p$-value from the meta-analytic $Q$-test\footnotemark.\\
+                                     $p_{Q}$ is the $p$-value from the meta-analytic $Q$-test.\footnotemark\\
     \bottomrule
@@
 significance approach define replication success by significance of a combined
-effect estimate\footnote{The meta-analytic approach can also be given a Bayesian
-  interpretation: A flat prior distribution for the underlying effect size
-  $\theta$ is updated by the data from original and replication study.
+effect estimate.\footnote{The meta-analytic approach can also be given a
+  Bayesian interpretation: A flat prior distribution for the underlying effect
+  size $\theta$ is updated by the data from original and replication study.
   Replication success defined by a meta-analytic $p$-value being smaller than
@@
   respectively, $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$
-  depending on the direction of combined estimate.}. Typically, the assumption
-of a common underlying effect size is seen as reasonable so that fixed-effects
+  depending on the direction of combined estimate.} Typically, the assumption of
+a common underlying effect size is seen as reasonable so that fixed-effects
 meta-analysis is used for pooling. Random-effects meta-analysis has mostly been
@@
 based on predictive ratios will be used in later parts of this
-thesis\footnote{Some readers may have noted that the predictive ratio is also
+thesis.\footnote{Some readers may have noted that the predictive ratio is also
   the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
@@
   approach is therefore particularly useful in combination with reverse-Bayes
-  procedures based on Bayes factors, as will be demonstrated in this thesis.}.
+  procedures based on Bayes factors, as will be demonstrated in this thesis.}
 

### 2022-11-25 paper2.tex
paper 2

@@
 culminated in large-scale replication projects that were conducted in various
-fields \citep{Errington2014, Klein2014, OSC2015, Ebersole2016, Camerer2016,
+fields \citep{Errington2014, Klein2014, Opensc2015, Ebersole2016, Camerer2016,
   Camerer2018, Cova2018, Klein2018}.
 
-% Declaring a replication as successful is, however, not a
-% straightforward task, and currently used approaches include
-% \emph{statistical} significance of both the original and replication
-% study,
-%  compatibility of their effect estimates, and meta-analysis of
-% the effect estimates. \emph{Many of the replication projects listed above also
-%   report the relative effect size, the ratio of the
-%   replication to the original effect estimate. For example, in \citet{Camerer2018}
-%   the replication effect estimates were only half as large as the original ones
-%   on average and even smaller in \citet{OSC2015}. This gives
-%   clear evidence of a systematic bias of the original studies and
-%   strongly suggests that the original and replication study should not
-%   be treated as exchangeable. However, all the approaches mentioned
-%   above will give the same results if the order of studies would be reversed. }
+Declaring a replication as successful is, however, not a straightforward task,
+and currently used approaches include statistical significance of both the
+original and replication study, compatibility of their effect estimates, and
+meta-analysis of the effect estimates. Many of the replication projects listed
+above also report the relative effect size, the ratio of the replication to the
+original effect estimate. For example, in \citet{Camerer2018} the replication
+effect estimates were only half as large as the original ones on average and
+even smaller in \citet{Opensc2015}. This gives clear evidence of a systematic
+bias of the original studies and strongly suggests that the original and
+replication study should not be treated as exchangeable. However, all the
+approaches mentioned above will give the same results if the order of studies
+would be reversed.
 
-% In order to address \emph{this problem}, a new method has recently been
-% proposed in \citet{held2020}. The approach combines the analysis of
-% credibility \citep{matthews:2001,matthews:2001b} with a prior-data
-% conflict assessment \citep{box:1980}. Replication success is declared if
-% the replication study is in conflict with a sceptical prior that would
-% make the original study non-significant. \emph{This approach penalizes
-%   small relative effect sizes as we will see in more detail in the following.}
+In order to address this problem, a new method has recently been proposed in
+\citet{Held2020}. The approach combines the analysis of credibility
+\citep{Matthews2001a,Matthews2001b} with a prior-data conflict assessment
+\citep{Box1980}. Replication success is declared if the replication study is in
+conflict with a sceptical prior that would make the original study
+non-significant. This approach penalizes small relative effect sizes as we will
+see in more detail in the following.
 
-% To introduce some notation, let $z_o = \hat \theta_o/\sigma_o$ and
-% $z_r = \hat \theta_r/\sigma_r$ denote the $z$-statistic of the
-% original and replication study, respectively. Here $\hat \theta_o$ and
-% $\hat \theta_r$ are the corresponding effect estimates (assumed to be
-% normally distributed) of the unknown
-% effect $\theta$ with standard errors $\sigma_o$ and $\sigma_r$, respectively.
-% The corresponding one-sided
-% $p$-values are denoted by $p_o=1-\Phi(z_o)$ and $p_r=1-\Phi(z_r)$,
-% respectively, where $\Phi(\cdot)$ denotes the standard normal cumulative
-% distribution function.
-% Let $c = \sigma_o^2/\sigma_r^2$ denote the variance
-% ratio of the squared standard errors of the original and replication
-% effect estimates. The squared standard errors are usually inversely
-% proportional to the sample size of each study, \ie
-% $\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some
-% unit variance $\kappa^2$.  The variance ratio $c$ can then be
-% identified as the relative sample size $c=n_r/n_o$. The relative effect size
-% \begin{equation}\label{eq:d}
-%   d = \frac{\hat \theta_r}{\hat \theta_o} = \frac{1}{\sqrt{c}} \frac{z_r}{z_o}
-% \end{equation}
-% quantifies the size of the replication effect estimate $\hat \theta_r$ relative
-% to the original effect estimate $\hat \theta_o$. The corresponding shrinkage
-% of the replication effect estimate will be denoted as $s=1-d$.
+To introduce some notation, let $z_o = \hat \theta_o/\sigma_o$ and
+$z_r = \hat \theta_r/\sigma_r$ denote the $z$-statistic of the original and
+replication study, respectively. Here $\hat \theta_o$ and $\hat \theta_r$ are
+the corresponding effect estimates (assumed to be normally distributed) of the
+unknown effect $\theta$ with standard errors $\sigma_o$ and $\sigma_r$,
+respectively. The corresponding one-sided $p$-values are denoted by
+$p_o=1-\Phi(z_o)$ and $p_r=1-\Phi(z_r)$, respectively, where $\Phi(\cdot)$
+denotes the standard normal cumulative distribution function. Let
+$c = \sigma_o^2/\sigma_r^2$ denote the variance ratio of the squared standard
+errors of the original and replication effect estimates. The squared standard
+errors are usually inversely proportional to the sample size of each study, \ie
+$\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
+variance $\kappa^2$. The variance ratio $c$ can then be identified as the
+relative sample size $c=n_r/n_o$. The relative effect size
+\begin{equation}\label{eq2:d}
+  d = \frac{\hat \theta_r}{\hat \theta_o} = \frac{1}{\sqrt{c}} \frac{z_r}{z_o}
+\end{equation}
+quantifies the size of the replication effect estimate $\hat \theta_r$ relative
+to the original effect estimate $\hat \theta_o$. The corresponding shrinkage of
+the replication effect estimate will be denoted as $s=1-d$.
 
-% Suppose the original study achieved statistical significance at one-sided
-% level $\alpha$, so $p_o \leq \alpha$.  The standard approach to assess
-% replication success is based on significance of the replication effect
-% estimate at the same level $\alpha$, \ie the replication is considered successful if also $p_r \leq \alpha$.
-% This approach is known in drug development as the two-trials rule \citep{senn:2007}, usually
-% conducted at $\alpha=0.025$.
-% Let $z_\alpha = \Phi^{-1}(1-{\alpha})>0$ denote the $z$-value corresponding
-% to the level $\alpha$, then significance of the replication
-% \emph{study is achieved if $z_r \geq z_\alpha$, which}
-% is equivalent to the \emph{condition}
-% \begin{equation}\label{eq:dSig}
-%    d \geq \frac{z_\alpha}{z_o  \, \sqrt{c}}
-% \end{equation}
-% on the relative effect size \eqref{eq:d}.
-% The right hand-side goes to zero for increasing $c$, so if the
-% relative sample size $c$ is large enough, significance of the
-% replication study can be achieved with any arbitrarily small (but
-% positive) relative effect size $d$. \emph{However, declaring replication
-% success when there is substantial shrinkage is contrary to common
-% sense, as the replication effect estimate may not reflect an effect
-% size of the same practical relevance as the original one, despite its
-% statistical significance.}
+Suppose the original study achieved statistical significance at one-sided level
+$\alpha$, so $p_o \leq \alpha$. The standard approach to assess replication
+success is based on significance of the replication effect estimate at the same
+level $\alpha$, \ie the replication is considered successful if also
+$p_r \leq \alpha$. This approach is known in drug development as the two-trials
+rule \citep{Senn2008}, usually conducted at $\alpha=0.025$. Let
+$z_\alpha = \Phi^{-1}(1-{\alpha})>0$ denote the $z$-value corresponding to the
+level $\alpha$, then significance of the replication study is achieved if
+$z_r \geq z_\alpha$, which is equivalent to the condition
+\begin{equation}\label{eq2:dSig}
+   d \geq \frac{z_\alpha}{z_o  \, \sqrt{c}}
+\end{equation}
+on the relative effect size \eqref{eq2:d}. The right hand-side goes to zero for
+increasing $c$, so if the relative sample size $c$ is large enough, significance
+of the replication study can be achieved with any arbitrarily small (but
+positive) relative effect size $d$. However, declaring replication success when
+there is substantial shrinkage is contrary to common sense, as the replication
+effect estimate may not reflect an effect size of the same practical relevance
+as the original one, despite its statistical significance.
 
-% \emph{In this paper we first review the \citet{held2020} approach for
-%   the assessment of replication success, followed by showing how it
-%   relates to the relative effect size (Section \ref{sec:res}). This perspective
-%   is used in Section \ref{sec:goldenthresh} and \ref{sec:recalib}
-%   to propose  a recalibration of the
-%   method, the \textit{golden level}, which leads to a more appropriate
-%   criterion for replication success compared to the two-trials rule
-%   (Section \ref{sec:2TR}). In Section \ref{sec:ER} we study
-%   power and Type-I error rates of the proposed method and compare it to the
-%   two-trials rule. The recalibrated method ensures that conditional power can
-%   take any desired value if the original study has been significant and the replication
-%   sample size is large enough
-% (Section \ref{sec:powerrep}), controls the overall Type-I error if the replication
-% sample size is not smaller than the original one (Section \ref{sec:T1E}), and
-% offers uniform
-% gains in project power compared to the two-trials rule (Section \ref{sec:PP}). Section \ref{sec:application}
-% describes an application to data from four replication projects and Section
-% \ref{sec:discussion} closes with some discussion.}
+In this paper we first review the \citet{Held2020} approach for the assessment
+of replication success, followed by showing how it relates to the relative
+effect size (Section \ref{sec2:res}). This perspective is used in Section
+\ref{sec2:goldenthresh} and \ref{sec2:recalib} to propose a recalibration of the
+method, the \textit{golden level}, which leads to a more appropriate criterion
+for replication success compared to the two-trials rule (Section \ref{sec2:2TR}).
+In Section \ref{sec2:ER} we study power and Type-I error rates of the proposed
+method and compare it to the two-trials rule. The recalibrated method ensures
+that conditional power can take any desired value if the original study has been
+significant and the replication sample size is large enough (Section
+\ref{sec2:powerrep}), controls the overall Type-I error if the replication sample
+size is not smaller than the original one (Section \ref{sec2:T1E}), and offers
+uniform gains in project power compared to the two-trials rule (Section
+\ref{sec2:PP}). Section \ref{sec2:application} describes an application to data
+from four replication projects and Section \ref{sec2:discussion} closes with some
+discussion.
 
-% \clearpage
-% \section{Replication success}\label{sec:RS}
+\section{Replication success}\label{sec2:RS}
 
-% \begin{center}
-% \begin{figure}[!h]
-% \begin{center}
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{center}
+\begin{figure}[!h]
+\begin{center}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-% {\centering \includegraphics[width=\maxwidth]{figure/fig1-1}
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig1-1}
+
+}
+
+\end{knitrout}
+\caption{Example of the assessment of replication success. The original study
+  from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
+  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value $p_o = 0.011$.
+  The left part of the figure illustrates the reverse-Bayes derivation of the
+  sufficiently sceptical prior based on the original study result and the
+  posterior with lower credible limit fixed at zero. The comparison of the
+  sufficiently sceptical prior with the replication study result
+  ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$) in the
+  right part of the figure is used to assess potential prior-data conflict.}
+  \label{fig2:fig1}
+\end{center}
+\end{figure}
+\end{center}
+
+Hereinafter we focus on the one-sided assessment of replication success to
+ensure that replication success can only occur if the original and replication
+effect estimates go in the same direction. Figure \ref{fig2:fig1} illustrates the
+\citet{Held2020} approach based on a replication study from the \textit{Social
+  Sciences Replication Project} \citep{Camerer2018}: the significant original
+finding by \citet{Pyc2010} at one-sided level $\alpha=0.025$ is challenged with
+a sceptical prior, sufficiently concentrated around zero to make the original
+study result no longer convincing \citep{Matthews2001a,Matthews2001b}.
+Replication success is then defined as conflict between the sceptical prior and
+the result from the replication study in order to disprove the sceptic. Conflict
+is quantified by a prior-predictive tail probability $p_{\mbox{\scriptsize
+    Box}}$ \citep{Box1980} where a small value $p_{\mbox{\scriptsize
+    Box}} \leq \alpha$ defines replication success. In Figure \ref{fig2:fig1} the
+original finding is only borderline significant, so the sufficiently sceptical
+prior is fairly wide. Furthermore, there is substantial shrinkage
+($d = 0.15/0.4 = 0.38$) of the replication effect estimate and therefore hardly
+any conflict with the sufficiently sceptical prior (one-sided
+$p_{\mbox{\scriptsize Box}}=0.31$). We are thus not able to declare replication
+success at level $2.5$\%.
+
+The actual value of $p_{\mbox{\scriptsize Box}}$ is difficult to interpret as it
+depends on the level $\alpha$ and does not even exist if the original $p$-value
+$p_o$ exceeds $\alpha$. However, \citet{Held2020} showed that if both
+$\sign(z_o)=\sign(z_r)$ and
+\begin{equation}\label{eq2:extrinsic.p}
+\left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
+- 1 \right) \geq c
+\end{equation}
+hold, replication success at level ${\alpha_S}$ is achieved, where
+$z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$. The requirement
+\eqref{eq2:extrinsic.p} can be assessed for any value of
+${{\alpha_S}} > \max\{p_o, p_r\}$ and of particular interest is the smallest
+possible value of $\alpha_S$ where \eqref{eq2:extrinsic.p} holds, the so-called
+\textit{sceptical $p$-value} $p_S$. We are thus interested in the value $z_S^2$
+that fulfills
+\begin{equation}\label{eq2:extrinsic.p2}
+\left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
+- 1 \right) = c.
+\end{equation}
+There is a unique solution of \eqref{eq2:extrinsic.p2} which defines the
+one-sided {sceptical $p$-value} $p_S= 1-\Phi\left({z_S}\right)$ where
+$z_{S} \coloneqq + \surd z_{S}^2$, provided $\sign(z_o)=\sign(z_r)$ holds.
+Replication success at level $\alpha_S$ is then achieved if $p_S \leq \alpha_S$.
+In the introductory example based on the original study by \citet{Pyc2010}, the
+sceptical $p$-value turns out to be $p_S=0.11$.
+
+The sceptical $p$-value has a number of interesting properties, see
+\citet[Section 3.1]{Held2020} for details. In particular,
+$p_S > \max\{p_o, p_r\}$ always holds with $p_S \downarrow \max\{p_o, p_r\}$ for
+$c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
+sceptical $p$-value $p_S$ increases with decreasing relative effect size $d$.
+The first property ensures that both the original and the replication study have
+to be sufficiently convincing on their own to achieve replication success. The
+second property guarantees that shrinkage of the replication effect estimate is
+penalized.
+
+The level for replication success $\alpha_S$ has to be distinguished from the
+significance level $\alpha$ associated with the ordinary $p$-value.
+\citet{Held2020} has used the \textit{nominal level} for replication success
+($\alpha_S=\alpha$) for convenience, but in the following we will propose a
+recalibration of the procedure along with a new value for $\alpha_S$, the
+\textit{golden level} (Section~\ref{sec2:goldenthresh}). The derivation is based
+on a property of the required relative effect size for replication success, if
+the relative sample size is very large (Section~\ref{sec2:res}). In a nutshell,
+the golden level ensures that for original studies which were only borderline
+significant ($p_o=\alpha$), replication success is only possible if the
+replication
+effect estimate is larger than the original one ($d > 1$).\\
+
+\subsection{Relative effect size}\label{sec2:res}
+Without loss of generality we now assume that $\hat \theta_o > 0$ and that
+$p_o < {\alpha_S}$ has been observed in the original study, otherwise it would
+be impossible to achieve replication success at level $\alpha_S$ because $p_S$
+is always larger than $p_o$. The condition \eqref{eq2:extrinsic.p} for
+replication success can then be re-written as
+\begin{equation}\label{eq2:eq.z}
+  z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
+\end{equation}
+where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of \eqref{eq2:eq.z} is
+the minimum replication $z$-value $\zrmin$ required to achieve replication
+success. Note that $\zrmin$ increases with increasing $c$, so increasing the
+replication sample size leads to a more stringent success requirement $z_r$ and
+the corresponding replication $p$-value $p_r$.
+
+Equation \eqref{eq2:eq.z} can be further transformed to a
+condition on the relative effect size \eqref{eq2:d}:
+\begin{equation}\label{eq2:res}
+  d \geq  \frac{\sqrt{1+c/(K-1)}}{ \sqrt{c K}} \eqqcolon \dmin .
+\end{equation}
+To achieve replication success, the relative effect size must be at least as
+large as the right hand-side of \eqref{eq2:res}, the minimum relative effect size
+$\dmin$, a function of $K$ and the relative sample size $c$. If the relative
+sample size becomes very large, \ie $c \rightarrow \infty$, we have
+$\dmin \downarrow \dinfty$ where
+\begin{equation}\label{eq2:smallestpossible}
+  \dinfty = 1/\sqrt{K (K-1)}
+\end{equation}
+is the \textit{limiting relative effect size}. This shows that the minimum
+relative effect size $\dmin$ in \eqref{eq2:res} does not go to zero for
+increasing $c$, so replication success cannot be achieved if the relative effect
+size $d$ is smaller or equal to $\dinfty$, no matter how large the replication
+study is. In contrast, the corresponding criterion \eqref{eq2:dSig} of the
+two-trials rule can be achieved for any positive relative effect size,
+regardless of how small, provided the replication sample size is sufficiently
+large.
+
+\subsection{The golden level}\label{sec2:goldenthresh}
+Significance of both the original and the replication study at level $\alpha$ is
+a necessary but not sufficient requirement for replication success at the
+nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
+stringent. It is more reasonable to calibrate the procedure in such a way that
+to establish replication success, original and replication study do not both
+necessarily need to be significant at level $\alpha$, provided that the
+replication effect estimate does not shrink compared to the original one. We
+therefore choose a level $\alpha_S$ such that a borderline significant original
+study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
+$s > 0$ of the replication effect estimate. Mathematically, this translates to
+setting $\dinfty = 1$ and $K = z_\alpha^2/z_{\alpha_S}^2$
+in~\eqref{eq2:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
+with solution $K = \varphi$ where $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
+known as the golden ratio. Solving for $z_{\alpha_S}$ gives
+$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
+  level}
+\begin{eqnarray}\label{eq2:golden}
+\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
+\end{eqnarray}
+for replication success. This is our recommended default choice to assess
+replication success and we will study its properties in the following in more
+detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
+$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig2:fig1},
+the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
+\citet{Pyc2010} study was not successful.
+
+The golden level \eqref{eq2:golden} is derived from~\eqref{eq2:smallestpossible}
+with $\dinfty = 1$. However, we may also use a different value for the limiting
+relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
+only possible for a borderline significant result ($p_o = \alpha$) if there is
+less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication
+effect estimate. This approach is equivalent to a limiting relative effect size
+of 1 if the original $p$-value $p_o$ is equal to a different level $\alpha'$,
+which can be derived as follows: First, solving \eqref{eq2:smallestpossible} for
+$\dinfty > 0$ gives
+$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
+$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
+$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
+\begin{equation}\label{eq2:alphaPrime}
+\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
+\end{equation}
+For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.
+
+\subsection{Recalibration of the sceptical \textit{p}-value}\label{sec2:recalib}
+
+The condition $p_S \leq \alpha_S$ for replication success at the golden level is
+equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie
+$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
+recalibrate the sceptical $p$-value $p_{S} = 1 - \Phi(z_S)$ to
+$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
+to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
+be interpreted on the same scale as an ordinary $p$-value. For example, the
+recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
+out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
+level $\alpha<0.061$, including the standard $0.025$ level.
+
+\subsection{Comparison with the two-trials rule}\label{sec2:2TR}
+A useful benchmark for comparison is the two-trials rule in drug development
+\citep[Section 9.4]{Kay2015}, which requires ``at least two adequate and
+well-controlled studies, each convincing on its own, to establish
+effectiveness'' \citep[p.~3]{FDA1998}. This is usually achieved by independently
+replicating the result of a first study in a second study, both significant at
+one-sided level $\alpha=0.025$. {It is worth noting that in practice the two
+  trials are often run in parallel} {\citep{Senn2008}}{, so do not exactly
+  resemble the replication setting.}
+
+The main difference between the replication success and the two-trials
+rule approach concerns how shrinkage of the replication effect
+estimate is handled. Figure~\ref{fig2:fig2} illustrates that
+shrinkage is penalized in the assessment of replication success, \ie
+the original $p$-value needs to be quite small to achieve replication
+success for a relative effect size $d<1$. In contrast, significance of
+the replication study can be achieved even if there is substantial
+shrinkage, provided the replication sample size is large enough.
+
+\begin{figure}[!h]
+\centering
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig2-1}
+
+}
+
+\end{knitrout}
+\caption{Comparison of replication success at the golden level
+  ($p_S \leq \alpha_S = 0.062$) and the two-trials rule ($p_o \leq 0.025$ and
+  $p_r \leq 0.025$). The dotted areas indicate that success is impossible for
+  original $p$-value $p_o$ and relative effect size $d$. In the white areas
+  success is possible and depends on the relative sample size $c$ as indicated
+  by the grey lines. The dashed black line in the left plot indicates the
+  limiting relative effect size $\dinfty$. }
+\label{fig2:fig2}
+\end{figure}
+
+It is interesting to directly compare the two-trials rule and replication
+success at the golden level in terms of the required relative effect size $d$ to
+fulfill the criteria \eqref{eq2:dSig} and \eqref{eq2:res}, respectively, see
+Figure~\ref{fig2:fig2}. If the original $p$-value is not significant at level
+$\alpha$, only replication success can be achieved, but will require a
+replication effect estimate larger than the original one.
+
+For example, four studies with one-sided $p_o \in (0.025, 0.03)$ have been
+included in the \textit{Reproducibility Project: Psychology} \citep{Opensc2015}
+and one of them achieves replication success (see Section \ref{sec2:application}
+for details). By definition, such non-significant original findings can never
+fulfill the two-trials rule.
+
+If the original $p$-value is smaller than $\alpha$, then the situation depends
+on the relative sample size $c$. For example, when the replication sample size
+is chosen to be the same as in the original study ($c=1$) and $\alpha=0.025$,
+original studies with a $p$-value larger than $0.006$ will require a smaller
+relative effect size $d$ with the two-trials rule, while $p$-values smaller than
+$0.006$ will require a smaller relative effect size $d$ with the replication
+success method. This illustrates that the latter method is less stringent than
+the two-trials rule if the original study is already sufficiently convincing.
+
+\section{Power and Type-I Error Rate}\label{sec2:ER}
+Although Bayesian methods do not rely on the frequentist paradigm of repeated
+testing, it is still useful to investigate their frequentist operating
+characteristics \citep{Dawid1982, Rubin1984, Grieve2016} and this also holds for
+the proposed reverse-Bayes assessment of replication success. We first condition
+on the results from the original study and compare the power to achieve
+replication success with the two-trials rule in Section \ref{sec2:powerrep}. We
+then assume that none of the two studies have been conducted and investigate the
+overall Type-I error rate (Section \ref{sec2:T1E}) and the project power (Section
+\ref{sec2:PP}) \citep{Maca2002} over both studies in combination for fixed
+relative sample size $c$.
+
+\subsection{Conditional power}\label{sec2:powerrep}
+
+\begin{figure}[!ht]
+\begin{center}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig3-1}
+
+}
+
+\end{knitrout}
+\end{center}
+\caption{Conditional power as a function of the {one-sided} $p$-value of the
+  original study with relative sample size $c=1$ (left) and $c=5$ (right). Shown
+  is conditional power assuming the unknown parameter is equal to the original
+  effect estimate (solid) and conditional power based on 20\% shrinkage of the
+  original effect estimate (dashed) for the two-trials rule (2TR) at level
+  $\alpha = 0.025$ and for replication success at the corresponding golden and
+  nominal level. Power values of exactly zero are omitted.}
+\label{fig2:fig3}
+\end{figure}
+
+Figure~\ref{fig2:fig3} compares the power for replication success
+\citep[see][Section 4 for details]{Held2020} at the golden and at the nominal
+level with the power of the two-trials rule for relative sample size $c = 1$
+(left) and $c = 5$ (right) as a function of the one-sided $p$-value $p_o$ from
+the original study. Shown is the conditional power assuming the unknown
+parameter $\theta$ is equal to the original effect estimate $\hat \theta_o$.
+Then $\hat \theta_r \given \hat \theta_o \sim \Nor(\hat \theta_o, \kappa^2/n_r)$
+and it follows that $d \given \hat \theta_o \sim \Nor(1, 1/(c z_o^2))$. The
+conditional power for replication success can therefore be calculated as
+\begin{equation}\label{eq2:condPower}
+\P(d \geq \dmin \given \hat \theta_o) = \Phi\left[\sqrt{c} z_o (1-\dmin)\right],
+\end{equation}
+where $\dmin$ is given in \eqref{eq2:res}. Predictive power, which is conditional
+power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution for the
+effect size $\theta$, could also be calculated, then
+\mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}. Conditional and
+predictive power of the two-trials rule also depend on $z_o$, $c$ and $\alpha$
+and are given in \citet{Micheloud2020}.
+
+The two-trials rule requires a significant original study and hence it is
+impossible to power a replication study when $p_o > 0.025$. The same applies for
+replication success at the nominal level, where the power is zero for any
+$p_o > 0.025$, regardless of the replication sample size. This is different for
+the golden level, where the conditional power of an original study with
+$0.025 < p_o < 0.062$ is low, but not zero. However, if the original $p$-value
+$p_o$ is slightly smaller than $0.025$, the two-trials rule has a larger power,
+both for $c=1$ and $c=5$. But if the original $p$-value is sufficiently small
+($p_o < 0.006$ for $c=1$), the power for replication success at the golden level
+is larger than the power of the two-trials rule.
+
+Compared to $c=1$, the conditional power for $c=5$ of both the two-trials rule
+and the replication success approach at the golden level increases if
+$p_o \leq \alpha$. A remarkable feature of the replication success approach at
+the golden level is that conditional power can be pushed towards 100\% for large
+enough $c$ if $p_o<\alpha$, but not otherwise. This can be seen from
+\eqref{eq2:condPower} because $\dmin < 1$ for $p_o<\alpha$ and large enough
+relative sample size $c$. On the other hand, for $p_o > \alpha$ conditional
+power for replication success will tend to 0\% for increasing $c$ because
+$\dmin>1$ for all $c$. Finally, for $p_o = \alpha$ the limit is 50\%. The same
+property can be observed at the nominal level, however at the smaller threshold
+$1-\Phi(z_\alpha \sqrt{\varphi})$ which is $0.006$ for $\alpha=0.025$. Only if
+$p_o < 0.006$ will the conditional power for replication success attain 100\%
+for $c \to \infty$. This further highlights the stringency of the nominal level.
+
+The approach described so far takes the original study at face-value since it
+assumes that $\hat \theta_o$ is equal to the unknown effect size $\theta$. In
+practice, however, there are often good reasons to believe that original effect
+estimates have a tendency to be inflated (\eg due to publication bias). One way
+to address this issue is to base power calculations on a shrunken version of the
+original effect estimate, where the amount of shrinkage is guided by domain
+knowledge and a risk of bias assessment of the original study. For illustration,
+Figure~\ref{fig2:fig3} also shows conditional power based on 20\% shrinkage of
+the original effect estimate which reduces the conditional power for all
+methods, especially for a relative sample size $c = 1$. Conditional power for
+replication success at the golden level can now be pushed towards 100\% only for
+$p_o < 0.018$, which can be derived by solving \eqref{eq2:alphaPrime} for
+$\alpha$ with $\alpha'=0.025$ and $\dinfty=0.8$. To be able to push conditional
+power based on 20\% shrinkage towards 100\% for all $p_o < 0.025$, equation
+\eqref{eq2:alphaPrime} would have to be used directly to relax the level from
+$\alpha=0.025$ to $\alpha'=0.033$.
+
+\subsection{Overall Type-I error rate}\label{sec2:T1E}
+The two studies are assumed to be independent with Type-I error rate fixed at
+$\alpha$ for each of them, so the Type-I error rate of the two-trials rule over
+the entire project is simply $\alpha^2$ for any value of the relative effect
+size $c$. In contrast, the Type-I error rate of the proposed replication success
+assessment {depends on} the relative sample size $c$.
+
+For $c=1$, \citet[Section 3]{Held2020} showed that $z_S^2$ in
+\eqref{eq2:extrinsic.p2} simplifies to half the harmonic mean of the squared test
+statistics $z_o^2$ and $z_r^2$. The connection $z_S^2 = z_H^2/4$ to the harmonic
+mean $\chi^2$-test statistic $z_H^2$ \citep{Held2020b}, which has a
+$\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
+compute the Type-I error rate at level $\alpha_S$ for $c = 1$ as
+\begin{eqnarray}\label{eq2:T1E}
+\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
+ \right]\right\}/2.
+\end{eqnarray}
+For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type-I error
+rate \eqref{eq2:T1E} is $0.0515$\%, slightly less than the Type-I error rate
+$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type-I error
+rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
+0.0625\%.
+
+For $c \neq 1$, the Type-I error rate can be calculated through numerical
+integration:
+\begin{equation}\label{eq2:T1E0}
+  \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \phi(z_o) \, dz_o,
+\end{equation}
+where $\phi(\cdot)$ denotes the standard normal density function. The first term
+in the integral of \eqref{eq2:T1E0} is the probability of replication success at
+level $\alpha_S$ conditional on a fixed original test statistic $z_o$ and a
+relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
+this term simplifies to
+$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ where $\zrmin$
+in \eqref{eq2:eq.z} depends on $z_o$, $c$, and $\alpha_S$.
+
+\begin{figure}[!h]
+\centering
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig4-1}
+
+}
+
+\end{knitrout}
+
+\caption{Overall Type-I error rate (left) and project power (right) for fixed
+  relative sample size $c$. Results are given for replication success at the
+  nominal and golden level and compared with the two-trials rule (2TR) at
+  $\alpha = 0.025$. The dashed darkgrey line is the project power at the golden
+  level based on significant original studies ($p_o \leq 0.025$). The power of
+  the original study is 90\%.}
+\label{fig2:fig4}
+\end{figure}
+
+The left plot in Figure \ref{fig2:fig4} displays the Type-I error rate for
+$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
+that the Type-I error of the replication success approach decreases with
+increasing relative sample size $c$. This also follows from \eqref{eq2:T1E0}
+where $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ decreases
+with increasing $c$, because $\zrmin$ increases with increasing $c$, see
+equation \eqref{eq2:eq.z}.
+
+The Type-I error rate of the nominal level is always below the target
+$0.0625$\%. Although the Type-I error will eventually attain $\alpha^2$ in the
+limit $c \downarrow 0$ \citep[Section 3.4]{Held2020}, the nominal level seems to
+be too stringent for realistic values of $c$. The Type-I error rate of the
+golden level is smaller than $0.0625$\% for $c >0.85$. Appropriate Type-I error
+control is thus ensured even for replication studies where the sample size is
+slightly smaller than in the original study.
+
+\begin{figure}[!ht]
+\begin{center}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig5-1}
+
+}
+
+\end{knitrout}
+
+\end{center}
+\caption{Overall Type-I error rate if the replication sample size equal to the
+  original study ($c=1$). The two-trials rule (2TR) is compared to replication
+  success at the golden and nominal level for different values of $\alpha$.}
+\label{fig2:fig5}
+\end{figure}
+
+Figure \ref{fig2:fig5} compares for $c=1$ the Type-I error rate \eqref{eq2:T1E} of
+replication success at the golden and at the nominal level with the two-trials
+rule for different values of $\alpha$. The Type-I error rate of the two-trials
+rule is $\alpha^2$ and the replication success approach at the nominal level
+always has a much smaller Type-I error rate than $\alpha^2$. At the golden level
+the Type-I error rate of the replication success approach is much closer to
+$\alpha^2$, still slightly smaller if $\alpha < 0.058$. For $\alpha = 0.058$ the
+Type-I error rate is equal to the Type-I error rate $0.058^2 = 0.34\%$ of the
+two-trials rule and for $\alpha > 0.058$ the Type-I error rate is slightly
+larger than $\alpha^2$. The Type-I error rate for replication success decreases
+with increasing $c$, so as long as the replication sample size is not smaller
+than the original sample size, Type-I error control at $\alpha^2$ is guaranteed
+at the golden level for any one-sided level $\alpha < 0.058$.
+
+\subsection{Project power}\label{sec2:PP}
+Under the alternative we have $z_o\sim \Nor(\mu, 1)$ with
+$\mu = z_\alpha + z_\beta$ where $\alpha$ is the assumed significance level and
+$1-\beta = \Phi(\mu - z_\alpha)$ is the power to detect the assumed effect
+$\theta = \mu \sigma_o$ in the original study \citep[Section 3.3]{Matthews2006}.
+In the following $\alpha=0.025$ and $\beta=0.1$ are used. The power of a
+significant replication study with sample size $n_r = c n_o$ is
+\begin{equation*}
+\Phi(\theta/\sigma_r - z_\alpha) =
+\Phi(\sqrt{c} \mu - z_\alpha),
+\end{equation*}
+
+so depends on $\mu$ and the relative sample size $c$. The project power of the
+two-trials rule is therefore $(1-\beta) \, \Phi(\sqrt{c} \mu - z_\alpha)$ and
+increases with increasing $c$.
+
+The project power for replication success is computed as
+\begin{equation*}
+  \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \phi(z_o - \mu) \, dz_o
+\end{equation*}
+and shown in the right plot of Figure \ref{fig2:fig4} as a function of $c$. For
+the golden level, the project power quickly increases to values above 90\%,
+whereas the nominal level only reaches around 80\% project power. The project
+power based on the two-trials rule is shown for comparison, which is always
+smaller than for the golden level and converges to 90\% for large $c$.
+
+The advantage in power stems partly from replication success still being
+possible when the original $p$-value is larger than 0.025, but smaller than
+0.062. If we assume that a replication study is only conducted if the original
+study is significant (with $p_o \leq 0.025$), then the project power based on
+the golden level (the dashed line in Figure \ref{fig2:fig4}) is slightly smaller
+and for $c>1$ barely different than for the two-trials rule. More substantial
+gains are still visible for $c < 1$. However, the restriction to original
+studies with $p_o \leq 0.025$ may not reflect current practice in large-scale
+replication projects. For example, 5 out of 143 replication studies considered
+in Section \ref{sec2:application} do have original $p$-values between 0.025 and
+0.062.
+
+\section{Application}\label{sec2:application}
+In this section, we illustrate the proposed methodology using data from four
+replication projects. All four projects reported effect estimates that were
+transformed to correlation coefficients ($r$). This scale allows for easy
+comparison of effect estimates from studies that investigate different phenomena
+and is bounded to the interval between minus one and one. Moreover, the Fisher
+$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$ can be applied to the
+correlation coefficients, resulting in the transformed estimates being
+asymptotically normal with variance which is only a function of the study sample
+size $n$, \ie $\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}.
+
+The first data set comprises the results from the \textit{Reproducibility
+  Project: Psychology} \citep{Opensc2015}, whose aim was to replicate 100
+studies, all of which were published in three major Psychology journals in 2008.
+For our purpose only the 73 study pairs from the ``meta-analytic'' subset are
+considered, since only for these studies the standard error of the Fisher
+$z$-transformed effect estimates can be computed \citep{Johnson2016}. The second
+data set comes from the \textit{Experimental Economics Replication Project}
+\citep{Camerer2016} which attempted to replicate 18 experimental economics
+studies published in two high impact economics journals between 2011 and 2015.
+The third data stem from the \textit{Social Sciences Replication Project}
+\citep{Camerer2018} where 21 replications of studies on the social sciences were
+carried out, all of which were originally published in the journals
+\textit{Nature} and \textit{Science} between 2010 and 2015. The last data set
+originates from the \textit{Experimental Philosophy Replicability Project}
+\citep{Cova2018} which involved 40 replications of studies from the emerging
+field of experimental philosophy. Since only for 31 studies effective sample
+size for original and replication study were available simultaneously, only
+these pairs were included. For more information on the data sets see also
+\citet{Pawel2020}.
+
+\begin{table}[!ht]
+    \centering
+\caption{Results for each replication project:
+Relative effect size $d$ (median with 25\% and 75\% quantiles on Fisher's $z$ scale), proportion of
+successful replications with the two-trials rule (2TR) and the replication success (RS)
+approach (at the golden level), and number of studies where the methods disagree.}
+% \resizebox{\textwidth}{!} {
+% latex table generated in R 4.0.5 by xtable 1.8-4 package
+% Fri Nov 25 12:12:30 2022
+\begin{tabular}{lcccc}
+  \toprule
+Project & relative effect size $d$ & 2TR (\%) & RS (\%) & discrepant \\
+  \midrule
+Psychology & 0.29 [0.03, 0.77] & 28.8 & 30.1 & 3/73 \\
+  Experimental Economics & 0.67 [0.35, 0.92] & 55.6 & 55.6 & 0/18 \\
+  Social Sciences & 0.52 [0.13, 0.65] & 61.9 & 52.4 & 2/21 \\
+  Experimental Philosophy & 0.86 [0.47, 1.12] & 74.2 & 71.0 & 1/31 \\
+   \bottomrule
+\end{tabular}
 
 % }
+\label{tab:marginalres}
+\end{table}
 
-% \end{knitrout}
-% \caption{Example of the assessment of replication success. The original study from \citet{Pyc2010} has effect estimate  $\hat \theta_o=
-%   0.4$ on Fisher's $z$ scale
-%   (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value
-%   $p_o = 0.011$.
-%   The left part of the figure illustrates the \emph{reverse-Bayes derivation of the sufficiently sceptical prior
-%     based on}
-%   the original study result and the posterior with lower credible limit fixed at zero.
-\emph{The comparison} of the sufficiently sceptical prior with the replication study result ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$)
-%   in the right part of the figure \emph{is used to assess potential prior-data conflict.}
-%   \label{fig:fig1}}
-% \end{center}
-% \end{figure}
-% \end{center}
+Table~\ref{tab:marginalres} presents overall results for each of the replication
+projects. While the median relative effect size is below one for all of the four
+projects, there are still large differences. For example, the median relative
+effect size is only $0.29$ in the Psychology project, whereas it is $0.86$ in
+the Philosophy project. The degree of shrinkage is also reflected in the success
+rates (according to the two-trials rule and the replication success approach at
+the golden level), which are around 30\% for the former and more than 70\% for
+the latter. The proportion of successful replications is similar for the
+two-trials rule and the replication success approach. In the Experimental
+Economics project the methods perfectly agree, while in the other three projects
+the methods disagree for a few studies.
 
-% Hereinafter we focus on the one-sided assessment of replication
-% success to ensure that replication success can only occur if the
-% original and replication effect estimates go in the same
-% direction. Figure \ref{fig:fig1} illustrates the \citet{held2020} approach
-% based on a replication study
-% from the \textit{Social Sciences Replication Project} \citep{Camerer2018}:
-% the significant original finding by \citet{Pyc2010} at
-% one-sided level $\alpha=0.025$ is
-% challenged with a sceptical prior, sufficiently concentrated around
-% zero to make the original study result no longer convincing \citep{matthews:2001,matthews:2001b}.
-% Replication success is then defined as conflict between the
-% sceptical prior and the result from the replication study in order to
-% \emph{disprove} the sceptic. Conflict is quantified by a prior-predictive
-% tail probability $p_{\mbox{\scriptsize Box}}$ \citep{box:1980} where a small value
-% $p_{\mbox{\scriptsize Box}} \leq \alpha$ defines replication success.
-% In Figure \ref{fig:fig1}  the original finding is only borderline significant, so the
-% sufficiently sceptical prior is fairly wide.  Furthermore, there is
-% substantial shrinkage
-% ($d = 0.15/0.4 =
-% 0.38$)
-% of the replication effect estimate
-% and therefore hardly any conflict with the sufficiently
-% sceptical prior (one-sided $p_{\mbox{\scriptsize Box}}=0.31$).
-% We are thus not able to declare replication success at
-% level $2.5$\%.
+\begin{figure}[!h]
+\centering
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-% \emph{The actual value of $p_{\mbox{\scriptsize
-%       Box}}$ is difficult to interpret as it depends on the level $\alpha$ and does not even exist if
-%   the original $p$-value $p_o$ exceeds $\alpha$. However, }
-% \citet{held2020} showed
-% that if both $\sign(z_o)=\sign(z_r)$ and
-% \begin{equation}\label{eq:extrinsic.p}
-% \left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
-% - 1 \right) \geq c
-% \end{equation}
-% hold, replication success at level ${\alpha_S}$ is achieved, where $z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$.
-% The requirement \eqref{eq:extrinsic.p} can be assessed for \emph{any} value of
-% \emph{${{\alpha_S}} > \max\{p_o, p_r\}$} and of particular interest is the
-% smallest possible value of $\alpha_S$ where \eqref{eq:extrinsic.p} holds,
-% the so-called {\it sceptical $p$-value} $p_S$.
-% We are thus interested in the value $z_S^2$ that fulfills
-% \begin{equation}\label{eq:extrinsic.p2}
-% \left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
-% - 1 \right) = c.
-% \end{equation}
-% There is a unique solution of \eqref{eq:extrinsic.p2} which defines
-% the one-sided {sceptical $p$-value} $p_S=
-% 1-\Phi\left({z_S}\right)$ where $z_{S} \coloneqq +
-% \sqrt{z_{S}^2}$, provided
-% $\sign(z_o)=\sign(z_r)$ holds.  Replication success at level
-% $\alpha_S$ is then achieved if $p_S \leq
-% \alpha_S$.  In the introductory example based on the original study by
-% \citet{Pyc2010}, the sceptical
-% $p$-value turns out to be $p_S=0.11$.
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig6-1}
 
-% The sceptical
-% $p$-value has a number of interesting properties, see \citet[Section
-% 3.1]{held2020} for details. In particular, $p_S > \max\{p_o, p_r\}$
-% always holds with $p_S \downarrow \max\{p_o, p_r\}$ for $c \downarrow
-% 0$. Furthermore, if the $p$-values $p_o$ and
-% $p_r$ are fixed, the sceptical $p$-value
-% $p_S$ increases with \emph{decreasing} relative effect size
-% $d$.  The first property ensures that both the original and the
-% replication study have to be sufficiently convincing on their own to
-% \emph{achieve} replication success.  The second property guarantees that
-% shrinkage of the replication effect estimate is penalized.
+}
 
-% The level for replication success $\alpha_S$ has to be distinguished
-% from the significance level $\alpha$ associated with the ordinary
-% $p$-value.  \citet{held2020} has used the {\it nominal level} for
-% replication success ($\alpha_S=\alpha$) for convenience, but in the
-% following we will propose a recalibration of the procedure along with
-% a new value for $\alpha_S$, the {\it golden level} (Section~\ref{sec:goldenthresh}).
-% \emph{The derivation is based on a property of the required
-% relative effect size for replication success, if the relative sample size is very large
-% (Section~\ref{sec:res}).}
-% In a nutshell, the golden level
-% ensures that for original studies which were only borderline
-% significant \emph{($p_o=\alpha$)}, replication success is only possible if the replication
-% effect estimate is larger than the original one \emph{($d > 1$)}.\\
+\end{knitrout}
+\caption{Relative effect size $d$ versus original $p$-value $p_o$. Black
+  indicates that replication success was achieved at the golden level while grey
+  indicates that it was not. The diamonds mark studies where the replication
+  success approach (at the golden level) and the two-trials rule disagree. The
+  dashed black line indicates the limiting relative effect size at the golden
+  level with $\alpha = 0.025$. }
+\label{fig2:fig6}
+\end{figure}
 
-% \subsection{Relative effect size}\label{sec:res}
-% Without loss of generality we \emph{now} assume that $\hat \theta_o > 0$ and that
-% $p_o < {\alpha_S}$ has been observed in the original study, otherwise
-% it would be impossible to achieve replication success at level
-% $\alpha_S$ because $p_S$ is always larger than $p_o$.
-% The condition \eqref{eq:extrinsic.p} for replication
-% success can then be re-written as
-% \begin{equation}\label{eq:eq.z}
-%   z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
-% \end{equation}
-% where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of
-% \eqref{eq:eq.z} is the minimum replication $z$-value $\zrmin$ required
-% to achieve replication success.  Note that $\zrmin$ increases with increasing $c$, so increasing the replication
-% sample size leads to a more stringent success requirement \emph{for $z_r$ and the corresponding} replication
-% $p$-value $p_r$.
-
-% Equation \eqref{eq:eq.z} can be further transformed to a
-% condition on the relative effect size \eqref{eq:d}:
-% \begin{equation}\label{eq:res}
-%   d \geq  \frac{\sqrt{1+c/(K-1)}}{ \sqrt{c K}} \eqqcolon \dmin .
-% \end{equation}
-% To achieve replication success, the relative effect size
-% must be
-% at least as large as the right hand-side of \eqref{eq:res}, the
-%   minimum relative effect size $\dmin$, a function of $K$ and the
-% relative sample size $c$.
-% If the relative sample
-% size becomes very large, \ie $c \rightarrow \infty$, we have
-% $\dmin \downarrow \dinfty$ where
-% \begin{equation}\label{eq:smallestpossible}
-%   \dinfty = 1/\sqrt{K (K-1)}
-% \end{equation}
-% \emph{is the {\it limiting relative effect size}.}
-% This shows that the minimum relative effect size $\dmin$ in \eqref{eq:res}
-% does not go to zero for increasing $c$, so replication success cannot
-% be achieved if the relative effect size $d$ is smaller or equal to
-% $\dinfty$, no matter how large the replication study is.
-% \emph{In contrast}, the corresponding criterion \eqref{eq:dSig} \emph{of the
-% two-trials rule}
-% can be achieved for any positive relative effect size, regardless of
-% how small, provided the replication sample size is sufficiently large.
-
-% \subsection{The golden level}\label{sec:goldenthresh}
-% Significance of both the original and the replication study at level
-% $\alpha$ is a necessary but not sufficient requirement for replication
-% success at the nominal level ($\alpha_S = \alpha$).  The nominal level
-% may therefore be too stringent.  It is more reasonable to calibrate
-% the procedure in such a way that to establish replication success,
-% original and replication study do not both necessarily need to be
-% significant at level $\alpha$, provided that the replication effect
-% estimate does not shrink compared to the original one.  We therefore
-% choose a level $\alpha_S$ such that a borderline
-% significant original study ($p_o = \alpha$) cannot lead to replication
-% success if there is shrinkage $s > 0$ of the replication effect
-% estimate.  Mathematically, this translates to setting $\dinfty = 1$
-% and $K = z_\alpha^2/z_{\alpha_S}^2$ in~\eqref{eq:smallestpossible} and
-% leads to the quadratic equation $K(K-1) = 1$ with solution
-% $K = \varphi$ where
-% $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
-% known as the golden ratio. Solving for $z_{\alpha_S}$ gives
-% \emph{$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$
-% and the corresponding  \textit{golden level}
-% \begin{eqnarray}\label{eq:golden}
-% \alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
-% \end{eqnarray}
-% for replication success. }
-% This is our recommended default choice to assess replication success and we will study its properties in the following
-%                    in more detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$),
-% the golden level is $\alpha_S =0.062$.
-% In the introductory example
-% shown in Figure \ref{fig:fig1},
-% the sceptical $p$-value is $p_S=0.11 > 0.062$, so
-% the replication  of the \citet{Pyc2010} study was not successful.
-
-% \emph{The golden level \eqref{eq:golden} is derived from~\eqref{eq:smallestpossible} with $\dinfty = 1$.
-% However, we may also use a different value for the
-% limiting relative effect size $\dinfty$, say $\dinfty=0.8$.
-% Then replication success is only possible for a borderline significant result ($p_o = \alpha$)
-% if there is less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication effect estimate.
-% This approach is equivalent to a limiting relative effect size of 1 if the original $p$-value
-% $p_o$ is equal to a different level $\alpha'$, which can be derived as follows:
-% First, solving \eqref{eq:smallestpossible} for $\dinfty > 0$ gives
-% $K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
-% $\alpha'$ fulfills  $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so $z_\alpha^2/K=z_{\alpha'}^2/\varphi$
-% and therefore
-% \begin{equation}\label{eq:alphaPrime}
-% \alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
-% \end{equation}
-% For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.
-% }
-
-% \subsection{Recalibration of the sceptical $p$-value}\label{sec:recalib}
-
-% The condition $p_S \leq \alpha_S$ for replication success at the
-% golden level is equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$,
-% \ie $z_S \sqrt{\varphi} \geq z_\alpha$.  In practice it may be
-% preferable to recalibrate the sceptical $p$-value
-% $p_{S} = 1 - \Phi(z_S)$ to
-% $ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be
-% compared to $\alpha$ (rather than $\alpha_S$) to assess replication
-% success and can thus be interpreted on the same scale as an ordinary
-% $p$-value.  For example, the recalibrated sceptical $p$-value for the
-% replication of \citet{Pyc2010} turns out to be
-% $\tilde{p}_S=0.061$ and does not lead to replication
-% success at \emph{any level $\alpha<0.061$, including} the
-% standard $0.025$ level.
-
-% \subsection{Comparison with the two-trials rule}\label{sec:2TR}
-% A useful benchmark for comparison is the two-trials rule in drug
-% development \citep[Section 9.4]{kay:2015}, which requires ``at least
-% two adequate and well-controlled studies, each convincing on its own,
-% to establish effectiveness'' \citep[p.~3]{FDA1998}.  This is usually
-% achieved by independently replicating the result of a first study in a
-% second study, both significant at one-sided level
-% $\alpha=0.025$.  {It is worth noting that in practice the two trials are often run in parallel} {\citep{senn:2007}}{, so do not exactly resemble the replication setting.}
-
-% The main difference between the replication success and the two-trials
-% rule approach concerns how shrinkage of the replication effect
-% estimate is handled. Figure~\ref{fig:fig2} illustrates that
-% shrinkage is penalized in the assessment of replication success, \ie
-% the original $p$-value needs to be quite small to achieve replication
-% success for a relative effect size $d<1$. In contrast, significance of
-% the replication study can be achieved even if there is substantial
-% shrinkage, provided the replication sample size is large enough.
-
-% \begin{figure}[!h]
-% \centering
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-% {\centering \includegraphics[width=\maxwidth]{figure/fig2-1}
+Figure~\ref{fig2:fig6} displays the relative effect size $d$ versus the original
+$p$-value $p_o$ for each study pair and stratified by project. Note that one
+study pair from the Philosophy project is not shown due to extremely small
+original $p$-value and another study pair from the Psychology project is not
+shown due to a very large relative effect size. We can see that for most of the
+study pairs, the replication success approach and the two-trials rule lead to
+the same conclusion, only six replications show conflicting results. They are
+highlighted with diamonds in Figure~\ref{fig2:fig6} and their characteristics are
+summarised in Table~\ref{tbl:discrep}.
+\begin{table}[!ht]
+    \centering
+  \caption{Characteristics of studies for which the replication success approach
+    (at the golden level) and the two-trials rule disagree (at one-sided
+    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
+    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
+    and $\tilde{p}_S$.}
+  \label{tbl:discrep}
+% \resizebox{\textwidth}{!} {
+% latex table generated in R 4.0.5 by xtable 1.8-4 package
+% Fri Nov 25 12:12:30 2022
+\begin{tabular}{lllllll}
+  \toprule
+Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
+  \midrule
+\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
+  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
+  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
+  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
+  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
+  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
+   \bottomrule
+\end{tabular}
 
 % }
+\end{table}
+Two studies from the Psychology project show replication success but fail the
+two-trials rule. These studies show $p$-values that are slightly above the
+significance threshold in either original or replication study, but do not
+exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
+replication $p$-value was $p_r = 0.035$, a little too large to pass the
+two-trials rule. However, as the replication effect estimate shrunk only about
+$30$\% compared to the original one, replication success is still achieved.
+Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
+above the significance level, yet the replication led to a highly significant
+result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
+original counterpart, which therefore also resulted in replication success.
 
-% \end{knitrout}
-% \caption{Comparison of replication success at the golden level ($p_S \leq \alpha_S =
-% 0.062$) and the two-trials rule ($p_o \leq 0.025$ and $p_r \leq 0.025$).
-% The \emph{dotted} areas indicate that success is
-% impossible for original $p$-value $p_o$ and relative effect size $d$.
-% In the white areas success is possible and
-% depends on the relative sample size $c$ as indicated by the grey lines.
-% \emph{The dashed black line in the left plot indicates the limiting relative
-% effect size $\dinfty$.}
-% }
-% \label{fig:fig2}
-% \end{figure}
+The remaining conflicting studies do not show replication success despite
+passing the two-trials rule. In all cases, there is substantial shrinkage of the
+replication effect estimate compared to the original one. For instance, in the
+replication study of \citet{Pyc2010}, the estimate shrunk by $62$\% and the
+replication $p$-value was only significant because the sample size was increased
+by a factor of $c = 9.2$.
 
-% It is interesting to directly compare the two-trials rule and
-% replication success at the golden level in terms of
-% the required relative effect size $d$ to fulfill the criteria
-% \eqref{eq:dSig} and \eqref{eq:res}, respectively, see Figure~\ref{fig:fig2}.  If the original
-% $p$-value is not significant at level $\alpha$, only replication
-% success can be achieved, but will require a replication effect
-% estimate larger than the original one.
-% \emph{
-%   For example, four studies with one-sided
-%   $p_o \in (0.025, 0.03)$ have been included in the
-%   \textit{Reproducibility Project: Psychology} \citep{OSC2015} and one
-%   of them achieves replication success (see Section \ref{sec:application} for
-%   details).  By definition, such non-significant original findings can
-%   never fulfill the two-trials rule.
-% }
+This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
+the golden level as described in Section \ref{sec2:goldenthresh}. We may also
+choose a different value for the limiting relative effect size $\dinfty$ at
+$\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
+$\alpha'$ as given in \eqref{eq2:alphaPrime}. Figure \ref{fig2:fig7} compares the
+proportion of successful replications with the replication success approach for
+$\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
+corresponding levels
+$\alpha' \in (0.06, 0.022)$ for
+all four replication projects. We can see that the two proportions agree fairly
+well for all values of $\alpha'$ considered. The number of discrepant studies in
+each project varies between 0 and 3. Only in the Psychology project there are
+some studies which are successful with the replication success approach but not
+the two-trials rule and some studies successful with the two-trials rule but not
+the replication success approach. The proportion of studies where both methods
+are successful (also shown in Figure \ref{fig2:fig7}) is then smaller than the
+proportion of successful replications with either one of the two methods. The
+three discrepant studies from the Psychology project listed in the top three
+rows of Table~\ref{tbl:discrep} are an example of this particular feature.
 
-% If the original $p$-value is
-% smaller than $\alpha$, then the situation depends on the relative
-% sample size $c$.  For example, when the replication sample size is
-% chosen to be the same as in the original study ($c=1$) and
-% $\alpha=0.025$, original studies with a $p$-value larger than
-% $0.006$ will require a smaller relative effect
-% size $d$ with the two-trials rule, while $p$-values smaller than
-% $0.006$ will require a smaller relative effect
-% size $d$ with the replication success method.  This illustrates that
-% the latter method is less stringent than the two-trials rule if the
-% original study is already sufficiently convincing.
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-% \section{Power and Type-I Error Rate}\label{sec:ER}
-% Although Bayesian methods do not rely on the frequentist paradigm of
-% repeated testing, it is still useful to investigate their frequentist
-% operating characteristics \citep{Dawid1982, Rubin1984, Grieve2016}
-% and this also holds for the proposed reverse-Bayes assessment of
-% replication success. We first condition on the results from the original
-% study and compare the power to achieve replication success with the two-trials
-% rule in Section \ref{sec:powerrep}.
-% We then
-% assume that none of the two studies have been conducted and
-% investigate the \emph{overall} Type-I error rate (Section \ref{sec:T1E}) and the project power
-% (Section \ref{sec:PP})
-% \citep{Maca2002} \emph{over both studies in combination for fixed relative sample size $c$}.
+{\centering \includegraphics[width=\maxwidth]{images/paper2/fig7-1}
 
-% \subsection{Conditional power}\label{sec:powerrep}
+}
 
-% \begin{figure}[!ht]
-% \begin{center}
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\end{knitrout}
+\caption{Proportion of successful replications as a function of the limiting
+  relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
+  equivalent level $\alpha'$ where the corresponding limiting relative effect
+  size is 1. The replication success (RS) approach is compared with the
+  two-trials rule (2TR).}
+\label{fig2:fig7}
+\end{figure}
 
-% {\centering \includegraphics[width=\maxwidth]{figure/fig3-1}
+\section{Discussion}\label{sec2:discussion}
+In this paper, we have expanded on the replication success approach introduced
+in \citet{Held2020} and demonstrated its advantages over alternative methods
+such as the two-trials rule. In particular, the method provides an attractive
+compromise between hypothesis testing and estimation,
+as it penalizes
+shrinkage of the replication effect estimate compared to the original one,
+while ensuring that both are statistically significant to some extent.
+%% For instance, the method will indicate only a low degree of replication success when
+%% the replication study shows a much smaller but statistically significant
+%% effect estimate, whereas it can still indicate some degree of
+%% success when either original or replication $p$-value are slightly above the
+%% significance level. %% , provided their effect estimates are compatible.
 
-% }
+We further refined the method by proposing the golden level, a new threshold for
+replication success. It guarantees that borderline significant original studies
+can only be replicated successfully if the replication effect estimate is larger
+than the original one. Compared to the two-trials rule, the golden level offers
+uniform gains in project power and controls the Type-I error rate at any
+one-sided level $\alpha < 0.058$ if the replication sample size
+is not smaller than the original one. Empirical evaluation of data from four
+replication projects highlights that in most cases the methods are in agreement,
+however, for the study pairs where the approaches disagree, the replication
+success approach seems to lead to more sensible conclusions. The good
+performance has been recently confirmed by a comparison of different replication
+success metrics through a simulation study in the presence of publication bias
+\citep{Muradchanian2021}.
 
-% \end{knitrout}
-% \end{center}
-% \caption{\emph{Conditional} power as a function of the {one-sided}
-%   $p$-value of the original study with \emph{relative} sample size
-%   $c=1$ (left) and $c=5$ (right). Shown is
-%   conditional power \emph{assuming the unknown parameter is equal to
-%   the original effect estimate (solid)} \emph{and conditional
-%     power based on 20\% shrinkage of the original
-%     effect estimate (dashed)} for the two-trials rule (2TR) at level
-%   $\alpha = 0.025$ and for replication success
-%   % (RS)
-%   at the
-%   corresponding golden and nominal level. Power values of exactly zero
-%   are omitted.}
-% \label{fig:fig3}
-% \end{figure}
+Despite a lack of agreement as to which statistical method should be used to
+evaluate replication studies, conclusions based on different methods usually
+agree. Nevertheless, in some cases, classical methods such as the two-trials
+rule may produce anomalies. We argue that the replication success approach
+improves upon existing methods leading to more appropriate inferences and
+decisions that better reflect the available evidence. However, in extreme cases
+the performance of the sceptical $p$-value may be considered as strange or even
+counterintuitive. Specifically, if the original study was only borderline
+significant, a highly significant replication study can only lead to success if
+the replication effect estimate is larger than the original one. To understand
+this behaviour it is important to realize that the proposed approach does not
+synthesize the evidence from the two studies (like a standard meta-analysis).
+The sceptical $p$-value is designed to confirm claims of new discoveries through
+replication, but will remain ``stubborn'' \citep{Ly2020} if the original study
+was not particularly convincing, even if the replication study provides
+overwhelming evidence for an effect. It will lead to a different result if the
+order of studies was reversed, as long as original and replication study do not
+have the same sample size ($c \neq 1$). The related harmonic mean $\chi^2$-test
+\citep{Held2020b} for evidence synthesis of two or more studies also requires
+each study to be convincing on its own to a certain degree, but treats them as
+exchangeable.
 
-% Figure~\ref{fig:fig3} compares the power for replication success
-% \emph{\citep[see][Section 4 for details]{held2020}} at the golden and at
-% the nominal level with the power of the two-trials rule for relative
-% sample size $c = 1$ (left) and $c = 5$ (right)
-% as a function of the one-sided $p$-value \emph{$p_o$} from the original
-% study.  \emph{Shown is the conditional power assuming the unknown parameter
-%   $\theta$ is equal to the original effect estimate $\hat \theta_o$. Then
-% $\hat \theta_r \given \hat \theta_o \sim \Nor(\hat \theta_o, \kappa^2/n_r)$
-% and it follows that
-% $d \given \hat \theta_o \sim \Nor(1, 1/(c z_o^2))$.
-% The conditional power for replication
-% success can therefore be calculated as
-% \begin{equation}\label{eq:condPower}
-% \P(d \geq \dmin \given \hat \theta_o) = \Phi\left[\sqrt{c} z_o (1-\dmin)\right],
-% \end{equation}
-% where $\dmin$ is
-% given in \eqref{eq:res}.  Predictive power, which is conditional
-% power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution
-% for the effect size $\theta$, could also be calculated, then
-% \mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}.
-% Conditional and predictive power of the two-trials rule
-% also depend on $z_o$, $c$ and $\alpha$ and are given in
-% \citet{MicheloudHeld2021}.}
+With this paper we further advanced the reverse-Bayes methodology for the
+analysis and design of replication studies, yet certain limitations and
+opportunities for future research remain: First, assuming normality of the
+effect estimates may be questionable, especially for small sample sizes, and
+more robust distributional assumptions could be considered. Second, in some
+types of analyses (\eg regression or ANOVA) the effect estimate is a vector and
+the approach would need suitable adaptations. Third, there is a recent trend to
+not only conduct one but several replications for one original study
+\citep[\eg][]{Klein2014, Ebersole2016, Klein2018}. Also for this situation, the
+method would need to be adapted, \eg the replication estimates could be first
+synthesized and an analysis of replication success could be performed
+subsequently.
 
-% The two-trials rule requires a significant original study and hence it is
-% impossible to power a replication study when $p_o > 0.025$.
-% \emph{The same applies for replication success at the nominal level,
-% where the power is zero for any $p_o > 0.025$, regardless
-% of the replication sample size.
-% This is different for the golden level,
-% where the conditional power of an original study with $0.025 < p_o
-% < 0.062$ is low, but not zero.}
-% \emph{However, if the original $p$-value $p_o$ is slightly smaller than
-% $0.025$, the two-trials rule has a larger power, both for $c=1$ and $c=5$. }
-% \emph{But if the original $p$-value is sufficiently
-% small ($p_o < 0.006$ for $c=1$), the power for replication success at the golden level is larger
-% than the power of the two-trials rule. }
+Throughout the paper we have assumed that the relative sample size is fixed in
+advance. In practice the sample size of the replication study is often chosen
+based on the result of the original study \citep{Anderson2017}. Power
+calculations as shown in Figure \ref{fig2:fig3} can then be inverted to determine
+the appropriate sample size of the replication study. We can also invert
+equation \eqref{eq2:res} to obtain the required replication sample size based on
+the specification of the minimum relative effect size $\dmin$ to achieve
+replication success. This novel way of calculating the sample size requires the
+specification of the minimum relative effect size which can still be considered
+as acceptable. Sample size calculations based on the two-trials rule can also be
+formulated in terms of the minimum relative effect size by inverting equation
+\eqref{eq2:dSig}. We will report on a detailed comparison of the different
+approaches in future work.
 
-% \emph{ Compared to
-%   $c=1$, the conditional power for $c=5$
-%   of both the two-trials rule
-%   and the replication success approach at the golden level
-%   increases if $p_o \leq \alpha$.     A remarkable feature of the
-%   replication success approach at the golden level is that conditional
-%   power can be pushed towards 100\% for large enough $c$ if
-%   $p_o<\alpha$, but not otherwise. This can be seen from \eqref{eq:condPower} because
-%   $\dmin < 1$ for $p_o<\alpha$ and large enough relative sample size $c$.
-% On the other hand, for $p_o > \alpha$ conditional power for replication success
-% will tend to 0\% for increasing $c$ because $\dmin>1$ for all $c$. Finally, for $p_o = \alpha$
-% the limit is 50\%.
-%   The same
-%   property can be observed at the nominal level, however at the
-%   smaller threshold $1-\Phi(z_\alpha \sqrt{\varphi})$ which is $0.006$ for  $\alpha=0.025$. Only if $p_o < 0.006$ will the conditional power
-%   for replication success attain 100\% for $c \to \infty$. This further highlights the stringency
-%   of the nominal level.  }
+\section*{Data and Software}
+Code and data to reproduce our analyses are available at
+\url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
+the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
+The data which was used is available in the R package
+\texttt{ReplicationSuccess} (available on CRAN). Further information can be
+found on the corresponding help page (with the command \texttt{?RProjects}).
 
-% \emph{The approach described so far takes the original study at
-%   face-value since it assumes that $\hat \theta_o$ is equal to the unknown effect size $\theta$.
-%   In practice, however,
-%   there are often good reasons to believe that original effect estimates
-%   have a tendency to be inflated (\eg due to publication bias). One
-%   way to address this issue is to base power calculations on a
-%   shrunken version of the original effect
-%   estimate, where the amount of shrinkage is guided by domain knowledge and
-%   a risk of bias assessment of the original study.
-%   For illustration, Figure~\ref{fig:fig3} also shows conditional power based
-%   on 20\% shrinkage of the original effect estimate
-%   which reduces the conditional power for all methods, especially for
-%   a relative sample size $c = 1$.  Conditional power for
-%   replication success at the golden level can now be pushed towards 100\%
-%   only for $p_o < 0.018$, which can be derived by
-%   solving \eqref{eq:alphaPrime} for $\alpha$ with
-%   $\alpha'=0.025$ and $\dinfty=0.8$.  To be able to
-%   push conditional power based on 20\% shrinkage towards 100\% for all
-%   $p_o < 0.025$,
-%   equation \eqref{eq:alphaPrime} would have to be used directly to relax the level
-%   from $\alpha=0.025$ to $\alpha'=0.033$.
-%   }
-
-% \subsection{Overall Type-I error rate}\label{sec:T1E}
-% \emph{The two studies are assumed to be independent with Type-I error
-% rate fixed at $\alpha$ for each of them,} so the Type-I error rate of the
-% two-trials rule \emph{over the entire project} is simply $\alpha^2$ for
-% any value of the relative effect size $c$.
-% In contrast, the Type-I
-% error rate of the proposed replication success assessment {depends on}
-% \emph{the relative sample size} $c$.
-
-% For $c=1$, \citet[Section 3]{held2020} showed that $z_S^2$ in \eqref{eq:extrinsic.p2}
-% simplifies to half the harmonic mean of the squared test statistics
-% $z_o^2$ and $z_r^2$.  The
-% connection $z_S^2 = z_H^2/4$ to the harmonic mean $\chi^2$-test
-% statistic $z_H^2$ \citep{held2020b}, which has a
-% $\chi^2(1)$-distribution under the null hypothesis, makes it
-% straightforward to compute the Type-I error rate  at level
-% $\alpha_S$ for $c = 1$ as
-% \begin{eqnarray}\label{eq:T1E}
-% \mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
-%  \right]\right\}/2.
-% \end{eqnarray}
-% For the golden level $\alpha_S =0.062$ at
-% $\alpha = 0.025$, the Type-I error rate \eqref{eq:T1E}
-% is $0.0515$\%, slightly less than the Type-I
-% error rate $\alpha^2=0.0625$\% of the
-% two-trials rule.  For comparison, the Type-I error rate at the nominal
-% level $\alpha_S=0.025$ is
-% $0.0022$\%, \emph{much} smaller than
-% 0.0625\%.
-
-% For $c \neq 1$,  the Type-I error rate can be calculated through numerical
-% integration:
-% \begin{equation}\label{eq:T1E0}
-%   \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
-% \P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
-%   \phi(z_o) \, dz_o,
-% \end{equation}
-% where $\phi(\cdot)$ denotes the standard normal density function.
-% The first term in the integral of \eqref{eq:T1E0} is the probability of
-% replication success at level $\alpha_S$ conditional on a fixed original test
-% statistic $z_o$ and a relative sample size $c$.
-% Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
-% this term simplifies to
-%   $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$
-% where $\zrmin$ in \eqref{eq:eq.z} depends on $z_o$, $c$, and $\alpha_S$.
-
-% \begin{figure}[!h]
-% \centering
-
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-% {\centering \includegraphics[width=\maxwidth]{figure/fig4-1}
-
-% }
-
-% \end{knitrout}
-
-% \caption{\emph{Overall} Type-I error rate (left) and project power (right) for fixed relative sample size $c$.
-%   Results are given for replication success
-%   % (RS)
-%   at the nominal and golden
-%   level and compared with the two-trials rule (2TR) at $\alpha = 0.025$.
-%   \emph{The dashed darkgrey line is the project power at the golden level based on significant original studies ($p_o \leq 0.025$).}
-%   The power of the original study is 90\%.}
-% \label{fig:fig4}
-% \end{figure}
-
-% The left plot in Figure \ref{fig:fig4} displays the Type-I error
-% rate for $\alpha=0.025$ as a function of the relative sample
-% size $c$.  It can be seen that the Type-I error \emph{of the replication success approach} decreases with
-% increasing relative sample size $c$. \emph{This also follows from \eqref{eq:T1E0}
-%   where
-% $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$
-% decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
-% see equation \eqref{eq:eq.z}. }
-
-% The Type-I error rate of the nominal level is always below the target
-% $0.0625$\%.  Although the Type-I error will
-% eventually attain $\alpha^2$ in the limit $c \downarrow 0$
-% \citep[Section 3.4]{held2020}, the nominal level seems to be too
-% stringent for realistic values of $c$.  The Type-I error rate of the
-% golden level is smaller than $0.0625$\% for
-% $c >0.85$.  Appropriate Type-I error control is
-% thus ensured even for replication studies where the sample size is
-% slightly smaller than in the original study.
-
-% \begin{figure}[!ht]
-% \begin{center}
-
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-% {\centering \includegraphics[width=\maxwidth]{figure/fig5-1}
-
-% }
-
-% \end{knitrout}
-
-% \end{center}
-% \caption{\emph{Overall Type-I error rate if the
-%   replication sample size equal to the original study
-%   ($c=1$).  The two-trials rule (2TR)
-%   is compared to replication success
-%   % (RS)
-%   at the
-%   golden and nominal level for different values of $\alpha$.}}
-% \label{fig:fig5}
-% \end{figure}
-
-% \emph{Figure \ref{fig:fig5} compares for $c=1$ the Type-I error rate \eqref{eq:T1E}
-%   of replication success at the golden and at the nominal level
-%     with the
-%   two-trials rule for different values of $\alpha$. The
-%   Type-I error rate of the two-trials rule is $\alpha^2$ and the
-%   replication success approach at the nominal level always has a much
-%   smaller Type-I error rate than $\alpha^2$.  At the golden level
-%   the Type-I error rate of the
-%   replication success approach is much closer to $\alpha^2$, still slightly smaller
-%   if $\alpha < 0.058$. For $\alpha = 0.058$ the
-%   Type-I error rate is equal to the
-%   Type-I error rate $0.058^2 = 0.34\%$ of the
-%   two-trials rule and for $\alpha > 0.058$ the
-%   Type-I error rate is slightly larger than $\alpha^2$.
-%   The
-%   Type-I error rate for replication success decreases with
-%   increasing $c$, so as long as the replication sample size is not
-%   smaller than the original sample size, Type-I error control at
-%   $\alpha^2$ is guaranteed at the golden level for any one-sided level
-%   $\alpha < 0.058$.}
-
-% \subsection{Project power}\label{sec:PP}
-% Under the alternative we have
-% $z_o\sim \Nor(\mu, 1)$ with $\mu = z_\alpha + z_\beta$
-% where $\alpha$ is
-% the assumed significance level and
-% \emph{
-% $1-\beta = \Phi(\mu - z_\alpha)$
-% is the power to detect the
-% assumed effect $\theta = \mu \sigma_o$ in the original study \citep[Section 3.3]{mat2006}.
-% In the following
-% $\alpha=0.025$ and $\beta=0.1$ are
-% used. The power of a significant
-% replication study with sample size $n_r = c n_o$ is
-% \begin{equation*}
-% \Phi(\theta/\sigma_r - z_\alpha) =
-% \Phi(\sqrt{c} \mu - z_\alpha),
-% \end{equation*}
-% }
-% so
-% depends on $\mu$ and the relative sample size $c$. The project power of the
-% two-trials rule is therefore $(1-\beta) \, \Phi(\sqrt{c} \mu - z_\alpha)$ \emph{and increases with increasing $c$.}
-
-% The project power for replication success is computed as
-% \begin{equation*}
-%   \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
-% \P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
-%   \phi(z_o - \mu) \, dz_o
-% \end{equation*}
-% and shown in the right plot of Figure \ref{fig:fig4} as a function
-% of $c$.  For the golden level, the project power quickly increases to
-% values above 90\%, whereas the nominal level only reaches around 80\%
-% project power. The project power based on the two-trials rule is shown
-% for comparison, which is always smaller than for the golden level
-% and converges to 90\% for large $c$.
-
-% \emph{The advantage in power stems partly from replication success still
-%   being possible when the original $p$-value is larger than 0.025, but
-%   smaller than 0.062. If we assume that a replication study is
-%   only conducted if the original study is significant (with
-%   $p_o \leq 0.025$), then the project power based on the
-%   golden level (the dashed line in Figure \ref{fig:fig4}) is
-%   slightly smaller and for $c>1$ barely different than for the
-%   two-trials rule.  More substantial gains are still visible for
-%   $c < 1$.
-%   However, the restriction to original studies with
-%   $p_o \leq 0.025$ may not reflect current practice in
-%   large-scale replication projects. For example, 5 out of
-%   143 replication studies considered in Section
-%   \ref{sec:application} do have original $p$-values between
-%   0.025 and 0.062.  }
-
-% \section{Application}\label{sec:application}
-% In this section, we illustrate the proposed methodology using
-% data from four replication projects.
-% All four projects reported effect estimates that were transformed to
-% correlation coefficients ($r$). This scale allows for easy comparison of
-% effect estimates from studies that investigate different phenomena
-% \emph{and} is bounded to the interval between minus one and one.
-% Moreover, the Fisher $z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$
-% can be applied to the correlation coefficients, resulting in the transformed
-% estimates being asymptotically normal with variance which is only a function
-% of the study sample size $n$, \ie $\Var(\hat{\theta}) = 1/(n - 3)$
-% \citep{Fisher1921}.
-
-% The first data set comprises the results from the \textit{Reproducibility Project:
-% Psychology} \citep{OSC2015}, whose aim was to replicate 100 studies, all of which
-% were published in three major Psychology journals in 2008. For our purpose only
-% the 73 study pairs from the ``meta-analytic'' subset are considered, since only
-% for these studies the standard error of the Fisher $z$-transformed effect
-% estimates can be computed \citep{Johnson2016}.
-% The second data set comes from the \textit{Experimental Economics Replication
-% Project} \citep{Camerer2016} which attempted to replicate 18 experimental
-% economics studies published in two high impact economics journals between 2011
-% and 2015.
-% The third data stem from the \textit{Social Sciences Replication Project}
-% \citep{Camerer2018} where 21 replications of studies on the social sciences
-% were carried out, all of which were originally published in the journals
-% \textit{Nature} and \textit{Science} between 2010 and 2015.
-% The last data set originates from the \textit{Experimental Philosophy Replicability
-% Project} \citep{Cova2018} which involved 40 replications of studies from the
-% emerging field of experimental philosophy. Since only for 31 studies effective
-% sample size for original and replication study were available simultaneously,
-% only these pairs were included. For more information on the data sets see
-% also \citet{Pawel2020}.
-
-% Table~\ref{tab:marginalres} presents overall results for each of the
-% replication projects. While the median relative effect size is below one for
-% all of the four projects, there are still large differences. For
-% example, the median relative effect size is only
-% $0.29$
-% in the Psychology project, whereas it is
-% $0.86$ in the Philosophy project. The degree of shrinkage is also
-% reflected in the success rates (according to the two-trials rule and the replication
-% success approach \emph{at the golden level}), which are around 30\% for the former and more than 70\%
-% for the latter. The proportion of successful replications is similar for the
-% two-trials rule and the replication success approach. \emph{In the Experimental
-% Economics project the methods perfectly agree, while in the other three projects
-% the methods disagree for a few studies.}
-
-% \begin{table}[!ht]
-% \caption{Results for each replication project:
-% Relative effect size $d$ (median with 25\% and 75\% quantiles on Fisher's $z$ scale), proportion of
-% successful replications with the two-trials rule (2TR) and the replication success (RS)
-% approach (at the golden level), and number of studies where the methods disagree.}
-% % \resizebox{\textwidth}{!} {
-% % latex table generated in R 4.0.5 by xtable 1.8-4 package
-% % Fri Nov 25 10:07:05 2022
-% \begin{tabular}{lcccc}
-%   \toprule
-% Project & relative effect size $d$ & 2TR (\%) & RS (\%) & discrepant \\
-%   \midrule
-% Psychology & 0.29 [0.03, 0.77] & 28.8 & 30.1 & 3/73 \\
-%   Experimental Economics & 0.67 [0.35, 0.92] & 55.6 & 55.6 & 0/18 \\
-%   Social Sciences & 0.52 [0.13, 0.65] & 61.9 & 52.4 & 2/21 \\
-%   Experimental Philosophy & 0.86 [0.47, 1.12] & 74.2 & 71.0 & 1/31 \\
-%    \bottomrule
-% \end{tabular}
-
-% % }
-% \label{tab:marginalres}
-% \end{table}
-
-% \begin{figure}[!h]
-% \centering
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-% {\centering \includegraphics[width=\maxwidth]{figure/fig6-1}
-
-% }
-
-% \end{knitrout}
-% \caption{Relative effect size $d$ versus original $p$-value $p_o$.
-% Black indicates that replication success was achieved at the golden level
-% while grey indicates that it was not. The diamonds mark studies where
-% the replication success approach (at the golden level) and the two-trials rule disagree. The dashed
-% black line indicates the \emph{limiting relative effect size}
-% at the golden level with $\alpha = 0.025$.
-% }
-% \label{fig:fig6}
-% \end{figure}
-
-% Figure~\ref{fig:fig6} displays the relative effect size $d$ versus the
-% original $p$-value $p_o$ for each study pair and stratified by project.
-% Note that one study pair from the Philosophy project is not shown due to
-% extremely small original $p$-value and another study pair from the Psychology project
-% is not shown due to a very large relative effect size.
-% We can see that for most of the study pairs, the replication success approach
-% and the two-trials rule lead to the same conclusion, only six replications
-% show conflicting results.
-% They are highlighted with diamonds in Figure~\ref{fig:fig6} and their
-% characteristics are summarised in Table~\ref{tbl:discrep}.
-% \begin{table}[!ht]
-% \caption{Characteristics of studies for which the replication success approach
-% (at the golden level)
-% and the two-trials rule disagree (at one-sided $\alpha = 0.025$). Shown are relative
-% sample size $c$, relative effect size $d$, original, replication and recalibrated sceptical
-% $p$-value $p_o$, $p_r$ and $\tilde{p}_S$.}
-% \label{tbl:discrep}
-% % \resizebox{\textwidth}{!} {
-% % latex table generated in R 4.0.5 by xtable 1.8-4 package
-% % Fri Nov 25 10:07:05 2022
-% \begin{tabular}{lllllll}
-%   \toprule
-% Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
-%   \midrule
-% \citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
-%   \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
-%   \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
-%   \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
-%   \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
-%   \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
-%    \bottomrule
-% \end{tabular}
-
-% % }
-% \end{table}
-% Two studies from the Psychology project show replication success
-% but fail the two-trials rule.
-% These studies show $p$-values that are slightly above the significance
-% threshold in either original or replication study, but do not exhibit much
-% shrinkage; in
-% the replication of \citet{Oberauer2008}, the replication $p$-value was
-% $p_r = 0.035$,
-% a little too large to pass the two-trials rule. However, as the replication
-% effect estimate shrunk only about
-% $30$\%
-% compared to the original one, replication success is still achieved. Conversely,
-% the original $p$-value
-% $p_o = 0.028$
-% in \citet{Schmidt2008} was just above the significance level, yet the
-% replication led to a highly significant result
-% $p_r < 0.0001$
-% with the effect estimate being even
-% $30$\%
-% larger than the original counterpart, which therefore also resulted in
-% replication success.
-
-% The remaining conflicting studies do not show replication
-% success despite passing the two-trials rule.
-% In all cases, there is substantial shrinkage of the replication effect estimate
-% compared to the original one. For instance, in the replication study of
-% \citet{Pyc2010}, the estimate shrunk by
-% $62$\%
-% and the replication $p$-value was only significant because the
-% sample size was increased by a factor of
-% $c = 9.2$.
-
-% \emph{This analysis was based on the default choice $\dinfty=1$
-%   at $\alpha=0.025$ for the golden level as described in Section
-%   \ref{sec:goldenthresh}. We may also choose a different value for the
-%   limiting relative effect size $\dinfty$ at $\alpha=0.025$ which then
-%   corresponds to $\dinfty=1$ at a different level $\alpha'$ as given in \eqref{eq:alphaPrime}.  Figure
-%   \ref{fig:fig7} compares the proportion of successful
-%   replications with the replication success approach for
-%   $\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
-%   corresponding levels
-%   $\alpha' \in (0.06,
-%   0.022)$ for all four replication projects.
-%   We can see that the two proportions agree fairly well for all values
-%   of $\alpha'$ considered. The number of discrepant studies in each project varies
-%   between 0 and 3.   Only in the Psychology project there are
-%   some studies which are successful with the replication success approach but
-%   not the two-trials rule
-%   and some studies successful with the two-trials rule but not the replication
-%   success approach.  The proportion of studies where both
-%   methods are successful (also shown in Figure \ref{fig:fig7}) is then smaller than the proportion of
-%   successful replications with either one of the two methods.  The
-%   three discrepant studies  from the Psychology project listed in the top three rows of
-%   Table~\ref{tbl:discrep} are an example of this particular feature.
-% }
-
-% \begin{figure}[!htb]
-% \begin{knitrout}
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-% {\centering \includegraphics[width=\maxwidth]{figure/fig7-1}
-
-% }
-
-% \end{knitrout}
-% \caption{Proportion of successful replications as a function of the limiting
-% relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
-% equivalent level $\alpha'$ where the corresponding limiting relative effect size is 1.
-% The replication success (RS) approach is compared with the two-trials rule (2TR).}
-% \label{fig:fig7}
-% \end{figure}
-
-% \section{Discussion}\label{sec:discussion}
-% In this paper, we have expanded on the replication success approach introduced
-% in \citet{held2020} and demonstrated its advantages over alternative methods
-% such as the two-trials rule. In particular, the method provides an attractive
-% compromise between hypothesis testing and estimation,
-% as it penalizes
-% shrinkage of the replication effect estimate compared to the original one,
-% while ensuring that both are statistically significant to some extent.
-% %% For instance, the method will indicate only a low degree of replication success when
-% %% the replication study shows a much smaller but statistically significant
-% %% effect estimate, whereas it can still indicate some degree of
-% %% success when either original or replication $p$-value are slightly above the
-% %% significance level. %% , provided their effect estimates are compatible.
-% %% %% \todo{SP: maybe ``provided the replication estimate does not shrink?''}
-
-% We further refined the method by proposing the golden level, a
-% new threshold for replication success. It guarantees that borderline
-% significant original studies can only be replicated successfully if
-% the replication effect estimate is larger than the original
-% one. Compared to the two-trials rule, the golden level offers uniform
-% gains in project power and controls the Type-I error rate \emph{at any
-%   one-sided level $\alpha < 0.058$} if the
-% replication sample size is not \emph{smaller than the original one}.
-% Empirical evaluation of data from four replication projects highlights
-% that in most cases the methods are in agreement, however, for the
-% study pairs where the approaches disagree, the replication success
-% approach seems to lead to more sensible conclusions.
-% \emph{The good performance has been recently confirmed by a comparison of different
-%   replication success metrics through a simulation study in the
-%   presence of publication bias \citep{Muradchanian2021}.}
-
-% Despite a lack of agreement as to which statistical method should be used to
-% evaluate replication studies, conclusions based on different methods usually
-% agree. Nevertheless, in some cases, classical methods such as the two-trials
-% rule may produce anomalies. We argue that
-% the replication success approach improves upon existing methods leading to
-% more appropriate inferences and decisions that better
-% reflect the available evidence.
-% \emph{However, in extreme cases the performance of the sceptical $p$-value may be
-%   considered as strange or even counterintuitive. Specifically, if the
-%   original study was only borderline significant, a highly significant
-%   replication study can only lead to success if the replication effect
-%   estimate is larger than the original one. To understand this
-%   behaviour it is important to realize that the proposed approach does
-%   not synthesize the evidence from the two studies (like a standard
-%   meta-analysis). The sceptical $p$-value is designed to confirm
-%   claims of new discoveries through replication, but will remain
-%   ``stubborn'' \citep{LyWagenmakers2020} if the original study was not
-%   particularly convincing, even if the replication study
-%   provides overwhelming evidence for an effect.  It will lead to a
-%   different result if the order of studies was reversed, as long as
-%   original and replication study do not have the same sample size
-%   ($c \neq 1$).  The related harmonic mean $\chi^2$-test
-%   \citep{held2020b} for evidence synthesis of two or more studies
-%  also requires  each study to be convincing on its own to a certain degree, but
-%   treats them as exchangeable. }
-
-% With this paper we further advanced the reverse-Bayes methodology for
-% the analysis and design of replication studies, yet certain
-% limitations and opportunities for future research remain: First,
-% assuming normality of the effect estimates may be questionable,
-% especially for small sample sizes, and more robust distributional
-% assumptions could be considered.  Second, in some types of analyses
-% (\eg regression or ANOVA) the effect estimate is a vector and the
-% approach would need suitable adaptations.
-% Third, there is a recent trend to not only conduct one but
-% several replications for one original study \citep[\eg][]{Klein2014, Ebersole2016, Klein2018}.
-% Also for this situation,
-% the method would need to be adapted, \eg the replication estimates
-% could be first synthesized and an analysis of replication
-% success could be performed subsequently.
-
-% \emph{Throughout the paper we have assumed that the relative sample size is
-% fixed in advance.  In practice the sample size of the replication
-% study is often chosen based on the result of the original study
-% \citep{Anderson2017}.  Power calculations as shown in Figure
-% \ref{fig:fig3} can then be inverted to determine the appropriate
-% sample size of the replication study. We can also invert
-% equation \eqref{eq:res} to obtain the required replication sample size
-% based on the specification of the minimum relative effect size $\dmin$
-% to achieve replication success.
-% This novel way of calculating the sample size requires the
-% specification of the minimum relative effect size which can
-% still be considered as acceptable.  Sample size calculations based on
-% the two-trials rule can also be formulated in terms of the minimum
-% relative effect size by inverting equation \eqref{eq:dSig}.
-% We will report on a detailed comparison of the
-% different approaches in future work. }
-
-% \section*{Data and Software Availability}
-% Data analyzed in this
-% article and software are available in the R-package \texttt{ReplicationSuccess},
-% which can be installed by running the following command in an R console:
-% \texttt{install.packages("ReplicationSuccess", repos = \\"{http://R-Forge.R-project.org}"}).
-% Further information on
-% data preprocessing can be found on the corresponding help page
-% (with the command \texttt{?RProjects}).
-
-% \section*{Acknowledgments}
-% Support by the Swiss
-% National Science Foundation (Project \#~189295) is gratefully
-% acknowledged. We acknowledge helpful and
-% constructive comments by the Editor and a referee on an earlier version of this article.
+\section*{Acknowledgments}
+Support by the Swiss National Science Foundation (Project \#~189295) is
+gratefully acknowledged. We acknowledge helpful and constructive comments by the
+editor and a referee on an earlier version of this article.
 

### 2022-11-25 paper1.tex
third paper
paper 3 supplement
paper 2 start
chapter specific referencing

@@
   Mathur2020}, Bayesian \citep{Bayarri2002b, Bayarri2002, Verhagen2014,
-Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019}, and combinations thereof
-\citep{Held2020, Pawel2020, Held2021} have been proposed to quantify replication
-success.
+  Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019}, and combinations
+thereof \citep{Held2020, Pawel2020, Held2021} have been proposed to quantify
+replication success.
 
@@
 
-This paper is structured as follows: Section \ref{sec:methods} presents the
+This paper is structured as follows: Section \ref{sec1:methods} presents the
 derivation of the sceptical Bayes factor. Its asymptotic and finite sample
 properties are then compared with other measures of replication success in
-Section \ref{sec:comparison}. An extension to non-normal models is presented in
-Section \ref{sec:tdist}. Section \ref{sec:applications} illustrates how the
+Section \ref{sec1:comparison}. An extension to non-normal models is presented in
+Section \ref{sec1:tdist}. Section \ref{sec1:applications} illustrates how the
 method works in practice using case studies from the \emph{Social Sciences
-  Replication Project} \citep{Camerer2018}. Section \ref{sec:discussion}
+  Replication Project} \citep{Camerer2018}. Section \ref{sec1:discussion}
 provides concluding remarks about strengths, limitations and extensions of the
@@
 study limiting behaviour and facilitates interpretability. In Section
-\ref{sec:tdist}, we will present relaxations of the normality assumption, which
+\ref{sec1:tdist}, we will present relaxations of the normality assumption, which
 can lead to more accurate inferences when studies have small sample sizes and/or
@@
 \section{Reverse-Bayes assessment of replication success with Bayes factors}
-\label{sec:methods}
+\label{sec1:methods}
 % ``judgements are made concerning the values that the final
@@
 whether the resulting prior is plausible, and if so, this would legitimise the
-posterior inference. See Figure~\ref{fig:RBschmema} for a graphical illustration
+posterior inference. See Figure~\ref{fig1:RBschmema} for a graphical illustration
 of this process.
@@
   % nodes %
-  \node[font = \large] (data) {$f(\mathrm{data} \,|\, \theta)$};
+  \node[font = \large] (data) {$f(\text{data} \,|\, \theta)$};
   \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
-  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \mathrm{data})$};
+  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \text{data})$};
   \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
@@
   for an unknown parameter $\theta$.}
-\label{fig:RBschmema}
+\label{fig1:RBschmema}
 \end{figure}
@@
 \begin{align}
-  \label{eq:BFo}
+  \label{eq1:BFo}
   \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)
@@
 
-The Bayes factor from equation ~\eqref{eq:BFo} is shown in Figure ~\ref{fig:bfo}
+The Bayes factor from equation ~\eqref{eq1:BFo} is shown in Figure ~\ref{fig1:bfo}
 as a function of $g$ and for different original $z$-values $z_o$. For fixed
@@
 \begin{align}
-  \label{eq:minBFo}
+  \label{eq1:minBFo}
   \minBF_{o} =
@@
 Further increasing the relative sceptical prior variance increases
-\eqref{eq:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie
+\eqref{eq1:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie
 $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \to \infty$ for $g \to \infty$
@@
 exist.}
-\label{fig:bfo}
+\label{fig1:bfo}
 \end{figure}
@@
 
-From Figure \ref{fig:bfo} we can see that the more compelling the original data
+From Figure \ref{fig1:bfo} we can see that the more compelling the original data
 (\ie the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
@@
 \subsection{Data from the replication study}
-\label{sec:bfr}
+\label{sec1:bfr}
 In order to assess whether the original finding can be replicated in an
@@
 \begin{align}
-  \label{eq:BFr}
+  \label{eq1:BFr}
   \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
@@
 Our goal is now to define a condition for \emph{replication success} in terms of
-\eqref{eq:BFr}. It is natural to consider a replication successful if the
+\eqref{eq1:BFr}. It is natural to consider a replication successful if the
 replication data favour the advocate over the sceptic to a higher degree than
 the sceptic's initial objection to the original study. More formally, we say
-that if the Bayes factor from \eqref{eq:BFr} evaluated at the sufficiently
+that if the Bayes factor from \eqref{eq1:BFr} evaluated at the sufficiently
 sceptical relative prior variance $\gy$ is not larger than the corresponding
@@
 \begin{align}
-  \label{eq:success}
+  \label{eq1:success}
   \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
@@
 estimate $d = z_{r}/(z_{o}\sqrt{c}) = 0.83$), using equation
-\eqref{eq:BFr} this would lead to $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r;
+\eqref{eq1:BFr} this would lead to $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r;
 1.6) = 1/3.5$, which means
@@
 \begin{align}
-  \label{eq:bfs}
+  \label{eq1:bfs}
   \BFs
@@
 
-Figure \ref{fig:bfs} shows $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
+Figure \ref{fig1:bfs} shows $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
 $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ as a function of $\gy$ for several
@@
 by dots, sceptical Bayes factors $\BFs$ are indicated by crosses where existent.}
-\label{fig:bfs}
+\label{fig1:bfs}
 \end{figure}
@@
 \begin{align}
-  \label{eq:BFsc1}
+  \label{eq1:BFsc1}
   \BFs =
@@
 \section{Properties}
-\label{sec:comparison}
+\label{sec1:comparison}
 To study properties of the sceptical Bayes factor and facilitate comparison with
@@
 
-The condition for replication success at level $\gamma$ from \eqref{eq:success}
+The condition for replication success at level $\gamma$ from \eqref{eq1:success}
 is equivalent to
 \begin{align}
-  \label{eq:RSCond-d}
+  \label{eq1:RSCond-d}
   \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
@@
 \end{align}
-On the right-hand side of~\eqref{eq:RSCond-d} the $Q$-statistic
-\begin{align}
-  \label{eq:Qstat}
+On the right-hand side of~\eqref{eq1:RSCond-d} the $Q$-statistic
+\begin{align}
+  \label{eq1:Qstat}
   Q
@@
 to the sceptical Bayes factor is such that $Q$ acts as a penalty term
-in~\eqref{eq:RSCond-d} and a larger value will lower the degree of replication
+in~\eqref{eq1:RSCond-d} and a larger value will lower the degree of replication
 success possible. However, as we will see, the sceptical Bayes factor goes
@@
 
-Applying some algebraic manipulations to \eqref{eq:RSCond-d}, one can show that
+Applying some algebraic manipulations to \eqref{eq1:RSCond-d}, one can show that
 replication success at level $\gamma$ is achieved if and only if the relative
@@
 \begin{align}
-  \label{eq:dsuccess}
+  \label{eq1:dsuccess}
   \begin{cases}
@@
 
-The top-left plot in Figure~\ref{fig:dcomparison} shows the conditions on $d$
-from~\eqref{eq:dsuccess} to achieve replication success at level $\gamma = 1/3$
+The top-left plot in Figure~\ref{fig1:dcomparison} shows the conditions on $d$
+from~\eqref{eq1:dsuccess} to achieve replication success at level $\gamma = 1/3$
 as a function of the original minimum Bayes factor $\minBF_{o}$ and for
@@
 opposite direction is usually not of interest (see
-Section~\ref{sec:replicationParadox} for a discussion of this issue). We see
+Section~\ref{sec1:replicationParadox} for a discussion of this issue). We see
 that with increased precision of the replication study (larger $c$), the success
@@
   are shown.}
-\label{fig:dcomparison}
+\label{fig1:dcomparison}
 \end{figure}
@@
 $\minBF_{o} > \gamma$. This property is visible in the top-left plot in
-Figure~\ref{fig:dcomparison} by the cut-off at $\minBF_{o} = \gamma = 1/3$. In
+Figure~\ref{fig1:dcomparison} by the cut-off at $\minBF_{o} = \gamma = 1/3$. In
 contrast, for more convincing original studies with $\minBF_{o} < 1/3$
@@
 sufficiently sceptical relative prior variance is $\gy > 1$ and thus by
-condition~\eqref{eq:dsuccess} the success region consists of an interval
+condition~\eqref{eq1:dsuccess} the success region consists of an interval
 $(\dmin, \dmax)$. Hence, in this case the method also penalises too large
@@
 $\minBF_{o} < 1/4.5$, the sufficiently sceptical relative prior
-variance is $\gy \leq 1$, so due to~\eqref{eq:dsuccess} the success region for
+variance is $\gy \leq 1$, so due to~\eqref{eq1:dsuccess} the success region for
 positive $d$ is given by $(\dmin, \dmax = \infty)$. This means that for more
@@
 compared in terms of their replication success regions as shown in
-Figure~\ref{fig:dcomparison}.
+Figure~\ref{fig1:dcomparison}.
 
@@
 two-trials rule with methods based on Bayes factors we will study the two-trials
-rule based on the minimum Bayes factor from~\eqref{eq:minBFo}, \ie replication
+rule based on the minimum Bayes factor from~\eqref{eq1:minBFo}, \ie replication
 success at level $\gamma$ is established when both
@@
 \begin{align}
-  \label{eq:2TR}
+  \label{eq1:2TR}
   d \geq \frac{z_{\gamma}}{z_{o} \sqrt{c}}
@@
 $\minBF = z_{\gamma}\exp(-z_{\gamma}^{2}/2)\sqrt{e} = \gamma$. The success
-region from~\eqref{eq:2TR} is displayed in the top-right plot of
-Figure~\ref{fig:dcomparison}. We see that the success regions shift closer to
+region from~\eqref{eq1:2TR} is displayed in the top-right plot of
+Figure~\ref{fig1:dcomparison}. We see that the success regions shift closer to
 zero as the relative variance $c$ increases. Also there is a cut-off at
@@
 \begin{align}
-  \label{eq:BFrep}
+  \label{eq1:BFrep}
   \BFr
@@
 Similarly, as with the sceptical Bayes factor, the $Q$-statistic
-from~\eqref{eq:Qstat} appears in~\eqref{eq:BFrep} and acts as a penalty term,
+from~\eqref{eq1:Qstat} appears in~\eqref{eq1:BFrep} and acts as a penalty term,
 \ie larger values of $Q$ lower the degree of replication success. However, in
@@
 \begin{align}
-  \label{eq:BFRsuccess}
+  \label{eq1:BFRsuccess}
   d \not\in [-\sqrt{J} - H, \sqrt{J} - H]
@@
 \end{align*}
-The condition \eqref{eq:BFRsuccess} implies that replication success can also be
+The condition \eqref{eq1:BFRsuccess} implies that replication success can also be
 achieved for negative relative effect estimates $d$ (see
-Section~\ref{sec:replicationParadox} for a discussion of this issue). The
-bottom-left plot in Figure~\ref{fig:dcomparison} shows the conditions
-from~\eqref{eq:BFRsuccess} for positive relative effect estimates. As with the
+Section~\ref{sec1:replicationParadox} for a discussion of this issue). The
+bottom-left plot in Figure~\ref{fig1:dcomparison} shows the conditions
+from~\eqref{eq1:BFRsuccess} for positive relative effect estimates. As with the
 two-trials rule, the success region of the replication Bayes factor can be
@@
   \end{cases}
-  \label{eq:z2s}
+  \label{eq1:z2s}
 \end{equation*}
@@
 \begin{align}
-  \label{eq:psSuccessd}
+  \label{eq1:psSuccessd}
   d \geq \sqrt{\frac{1/c + 1/(K - 1)}{K}}
@@
 $d = 4.87$ times larger than the original one. Therefore,
-\citet{Held2021} used~\eqref{eq:psSuccessd} to determine the \emph{golden level}
+\citet{Held2021} used~\eqref{eq1:psSuccessd} to determine the \emph{golden level}
 $\alpha_{\mathrm{S}} = 1 - \Phi(z_\alpha/\sqrt{\varphi})$ with
@@
 
-The bottom-right plot in Figure~\ref{fig:dcomparison} shows the success region
+The bottom-right plot in Figure~\ref{fig1:dcomparison} shows the success region
 for the recalibrated sceptical $p$-value. We see that increasing the precision
@@
 allows replication success when the $\minBF_{o} > \gamma$. This is visible in
-the bottom-right plot of Figure~\ref{fig:dcomparison} where the success region
+the bottom-right plot of Figure~\ref{fig1:dcomparison} where the success region
 has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
@@
 \subsubsection{The replication paradox}
-\label{sec:replicationParadox}
+\label{sec1:replicationParadox}
 The \emph{replication-paradox} \citep{Ly2018} occurs when original and
@@
 factor and the replication Bayes factor may suffer from the paradox as their
-success regions from~\eqref{eq:dsuccess} and~\eqref{eq:BFRsuccess},
+success regions from~\eqref{eq1:dsuccess} and~\eqref{eq1:BFRsuccess},
 respectively, include negative relative effect estimates $d < 0$. This is
@@
     \frac{z_o(1 + dc)}{\sqrt{1 + c}} \right\}}
-   \label{eq:BFrtrunc}
+   \label{eq1:BFrtrunc}
 \end{align}
 where $\Phi(\cdot)$ is the cumulative distribution function of the standard
-normal distribution (see Appendix \ref{app:BFtrunc}). Hence, \eqref{eq:BFrtrunc}
+normal distribution (see Appendix \ref{app:BFtrunc}). Hence, \eqref{eq1:BFrtrunc}
 is the Bayes factor under the standard advocacy prior multiplied by a correction
 term. Determining the smallest level of replication success
-with~\eqref{eq:BFrtrunc} leads to a corrected sceptical Bayes factor, while
-setting $g = 0$ in~\eqref{eq:BFrtrunc} leads to a corrected replication Bayes
+with~\eqref{eq1:BFrtrunc} leads to a corrected sceptical Bayes factor, while
+setting $g = 0$ in~\eqref{eq1:BFrtrunc} leads to a corrected replication Bayes
 factor. The correction term goes to one when the replication estimate goes in
@@
 This modification guarantees that the replication paradox is avoided and we
-recommend to compute the sceptical Bayes factor using~\eqref{eq:BFrtrunc} in
+recommend to compute the sceptical Bayes factor using~\eqref{eq1:BFrtrunc} in
 cases where the replication paradox is likely to appear. However, truncated
@@
 prior penalises effect estimate incompatibility and the
-modification~\eqref{eq:BFrtrunc} will only make a difference in extreme
+modification~\eqref{eq1:BFrtrunc} will only make a difference in extreme
 situations. Due to its easier mathematical treatment we will focus on the
@@
   replication success $\gamma$.}
-\label{fig:t1ec}
+\label{fig1:t1ec}
 \end{figure}
 
-Figure~\ref{fig:t1ec} compares the type I error rates of the four methods for
+Figure~\ref{fig1:t1ec} compares the type I error rates of the four methods for
 different levels $\gamma$. The conventional nominal
@@
 \that_o/\sigma_o$ (respectively corresponding minimum Bayes factor $\minBF_o$).}
-\label{fig:condpower}
+\label{fig1:condpower}
 \end{figure}
 
-Figure~\ref{fig:condpower} shows conditional and predictive power as a function
+Figure~\ref{fig1:condpower} shows conditional and predictive power as a function
 of the relative variance $c$ and for several values of of the original $z$-value
@@
 \subsection{Information consistency}
-\label{sec:informationcons}
+\label{sec1:informationcons}
 Bayesian hypothesis testing procedures are desired to fulfil certain asymptotic
@@
 % sufficiently sceptical relative prior variance $\gy \leq 1$ due to the
-% success conditions~\eqref{eq:dsuccess}. This implies that the sceptical Bayes factor
+% success conditions~\eqref{eq1:dsuccess}. This implies that the sceptical Bayes factor
 % $\BFs \to \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g = 1)$, provided $\abs{z_o} \geq
@@
 infinity ($\abs{z_{i}} \to \infty$). Since $c = 1$, the sceptical Bayes factor
-is given by equation~\eqref{eq:BFsc1}. Moreover, we are allowed to use of the
+is given by equation~\eqref{eq1:BFsc1}. Moreover, we are allowed to use of the
 approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ as the argument of
@@
 \begin{align}
-  \label{eq:BFsc1lim2}
+  \label{eq1:BFsc1lim2}
   \BFs =
@@
 \end{align}
-Plugging $d = 1$ into~\eqref{eq:BFsc1lim2}, we see that $\BFs \downarrow 0$ as
+Plugging $d = 1$ into~\eqref{eq1:BFsc1lim2}, we see that $\BFs \downarrow 0$ as
 $\abs{z_{o}} \to \infty$, so the sceptical Bayes factor is information
@@
 
-The expression for the sceptical Bayes factor~\eqref{eq:BFsc1lim2} is also valid
+The expression for the sceptical Bayes factor~\eqref{eq1:BFsc1lim2} is also valid
 for other relative effect sizes $d$. Solving for $d$ such that the
@@
 
-\section{Extension to non-normal models} \label{sec:tdist}
+\section{Extension to non-normal models} \label{sec1:tdist}
 So far, we have always assumed approximate normality of the effect estimates
@@
 \begin{align}
-  \label{eq:nct}
+  \label{eq1:nct}
   T_i \given \theta \sim \text{NCT}_{\nu_i} \left(\theta \sqrt{n^*_i}\right).
@@
 the standardised mean difference score and $\nu_{i} = n_{i} - 1$ and
-$n_{i}^{*} = n_{i}$ need to be used in~\eqref{eq:nct}.
-
-There is no conjugate prior for the SMD $\theta$ under model~\eqref{eq:nct}, so
+$n_{i}^{*} = n_{i}$ need to be used in~\eqref{eq1:nct}.
+
+There is no conjugate prior for the SMD $\theta$ under model~\eqref{eq1:nct}, so
 it is not obvious which prior should be chosen to represent scepticism about it.
@@
 \begin{align}
-  \label{eq:binexact}
+  \label{eq1:binexact}
   f(x_{1i}, x_{2i} \given \theta)
@@
 
-There is no conjugate prior for the logOR under model~\eqref{eq:binexact}, but a
+There is no conjugate prior for the logOR under model~\eqref{eq1:binexact}, but a
 pragmatic choice is to specify a zero-mean normal prior
@@
 \section{Application}
-\label{sec:applications}
+\label{sec1:applications}
 The following section will illustrate application of the sceptical Bayes factor
@@
 For all studies except \citet{Janssen2010} and \citet{Derex2013}, the exact
-approach for either SMD or logOR effect sizes from Section~\ref{sec:tdist} is
+approach for either SMD or logOR effect sizes from Section~\ref{sec1:tdist} is
 applicable. In the studies with binary data
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{sec1:discussion}
 We proposed a novel method for the statistical assessment of replicability
@@
 
-% Bibliography
-\bibliographystyle{apalikedoiurl}
-\bibliography{bibliography}
-
 \begin{subappendices}
-  \label{sec:appendices}
   \renewcommand{\thesection}{\Alph{section}}
@@
 \begin{align}
-\label{eq:solutionvss}
+\label{eq1:solutionvss}
   q &= \lw{-1}\left(-\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}\right)
@@
 which is why we need to add the condition $-z_o^2/q \geq 1$ in equation
-\eqref{eq:solutionvss}, such that $\gy$ is a valid relative variance.
+\eqref{eq1:solutionvss}, such that $\gy$ is a valid relative variance.
 
@@
 $\lw{0}(\cdot)$, the branch with $W(y) \geq -1$, and $\lw{-1}(\cdot)$, the
-branch with $W(y) \leq -1$ (see Figure \ref{fig:lambertW} for an illustration).
+branch with $W(y) \leq -1$ (see Figure \ref{fig1:lambertW} for an illustration).
 \begin{figure}[!htb]
@@
 \caption{Lambert $W$ function for real argument $y$.}
-\label{fig:lambertW}
+\label{fig1:lambertW}
 \end{figure}
@@
   1 + \frac{(1 - d)^{2}}{1/c + 1}\right)\right\}.
-  \label{eq:bfsroot}
+  \label{eq1:bfsroot}
 \end{align}
@@
 terms of elementary functions, but root-finding algorithms can be used to
-compute it. However, when $c = 1$, equation~\eqref{eq:bfsroot} simplifies
-\begin{align}
-  \label{eq:bfsroot2}
+compute it. However, when $c = 1$, equation~\eqref{eq1:bfsroot} simplifies
+\begin{align}
+  \label{eq1:bfsroot2}
   \frac{1}{1 + g_*}\cdot\exp\left\{-\frac{z_{o}^{2}}{2} \cdot
@@
 \end{align}
-Multiplying~\eqref{eq:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
+Multiplying~\eqref{eq1:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
 Lambert $W$ function leads to
 \begin{align}
-  \label{eq:gintersect}
+  \label{eq1:gintersect}
   % q &= W\left(-\frac{z_A^2}{\sqrt{2}} \cdot
@@
 sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the $g_{*}$
-from~\eqref{eq:gintersect} can only be computed with the $\lw{-1}(\cdot)$
+from~\eqref{eq1:gintersect} can only be computed with the $\lw{-1}(\cdot)$
 branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$ the solution
 $g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the relative prior
-variance $g_{*}$ from~\eqref{eq:gintersect} into the Bayes factor
-from~\eqref{eq:BFo}, we obtain the expression for the sceptical Bayes factor
-in~\eqref{eq:BFsc1}.
+variance $g_{*}$ from~\eqref{eq1:gintersect} into the Bayes factor
+from~\eqref{eq1:BFo}, we obtain the expression for the sceptical Bayes factor
+in~\eqref{eq1:BFsc1}.
 
@@
      \Phi(z_o)}.
-   \label{eq:truncmarg}
+   \label{eq1:truncmarg}
 \end{align}
 With a similar argument one can show that this result holds for any $\that_o$ if
-the last factor in \eqref{eq:truncmarg} is changed to
+the last factor in \eqref{eq1:truncmarg} is changed to
 \begin{align*}
@@
 sceptical prior by the marginal likelihood under the truncated advocacy prior,
-the Bayes factor in \eqref{eq:BFrtrunc} is obtained.
+the Bayes factor in \eqref{eq1:BFrtrunc} is obtained.
 
@@
 paradox), the minimum relative effect estimates $\dmin$ as shown in
-Section~\ref{sec:comparison} are given by
+Section~\ref{sec1:comparison} are given by
 
@@
 Conditional on the original study, the probability for replication success at
-level $\gamma$ is given by the probability of \eqref{eq:RSCond-d}. This event
+level $\gamma$ is given by the probability of \eqref{eq1:RSCond-d}. This event
 involves $z_r = dz_o \sqrt{c}$ as the only random quantity if the original study
@@
 
-Applying some algebraic manipulations to \eqref{eq:RSCond-d}, the
+Applying some algebraic manipulations to \eqref{eq1:RSCond-d}, the
 probability for replication success at level $\gamma$ can be computed by
 \begin{align}
-  \label{eq:powerBFs}
+  \label{eq1:powerBFs}
   \Pr\left(\BFs \leq \gamma \given z_o, c\right) =
@@
 \begin{align}
-  \label{eq:BFrsuccess}
+  \label{eq1:BFrsuccess}
   \log(1 + c) - z_{r}^{2} + \frac{(z_{r} - z_{o}\sqrt{c})^{2}}{1 + c}
@@
 \end{align}
-Applying some algebraic manipulations to \eqref{eq:BFrsuccess} and assuming a
+Applying some algebraic manipulations to \eqref{eq1:BFrsuccess} and assuming a
 normal distribution for $z_{r}$ as in Appendix~\ref{app:powerBFs} leads to
@@
 
-% %% R sessionInfo for reproducibility
-% %% -----------------------------------------------------------------------------
-% \newpage \section*{Computational details}
-% \begin{knitrout}\footnotesize
-% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-% \begin{alltt}
-% \hlkwd{sessionInfo}\hlstd{()}
-% \end{alltt}
-% \begin{verbatim}
-% ## R version 4.2.2 Patched (2022-11-10 r83330)
-% ## Platform: x86_64-pc-linux-gnu (64-bit)
-% ## Running under: Ubuntu 20.04.5 LTS
-% ##
-% ## Matrix products: default
-% ## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
-% ## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
-% ##
-% ## locale:
-% ##  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C
-% ##  [3] LC_TIME=de_CH.UTF-8        LC_COLLATE=en_US.UTF-8
-% ##  [5] LC_MONETARY=de_CH.UTF-8    LC_MESSAGES=en_US.UTF-8
-% ##  [7] LC_PAPER=de_CH.UTF-8       LC_NAME=C
-% ##  [9] LC_ADDRESS=C               LC_TELEPHONE=C
-% ## [11] LC_MEASUREMENT=de_CH.UTF-8 LC_IDENTIFICATION=C
-% ##
-% ## attached base packages:
-% ## [1] stats     graphics  grDevices utils     datasets  methods   base
-% ##
-% ## other attached packages:
-% ##  [1] lamW_2.1.1             xtable_1.8-4           scales_1.2.1
-% ##  [4] ggplot2_3.4.0          tidyr_1.2.1            dplyr_1.0.10
-% ##  [7] ReplicationSuccess_1.2 biostatUZH_1.8.0       survival_3.4-0
-% ## [10] BayesRep_0.1           knitr_1.40
-% ##
-% ## loaded via a namespace (and not attached):
-% ##  [1] Rcpp_1.0.9         RColorBrewer_1.1-3 pillar_1.8.1       compiler_4.2.2
-% ##  [5] highr_0.9          tools_4.2.2        digest_0.6.30      boot_1.3-28
-% ##  [9] viridisLite_0.4.1  evaluate_0.18      lifecycle_1.0.3    tibble_3.1.8
-% ## [13] gtable_0.3.1       lattice_0.20-45    pkgconfig_2.0.3    rlang_1.0.6
-% ## [17] Matrix_1.5-1       cli_3.4.1          DBI_1.1.3          xfun_0.34
-% ## [21] withr_2.5.0        stringr_1.4.1      contfrac_1.1-12    elliptic_1.4-0
-% ## [25] generics_0.1.3     vctrs_0.5.0        grid_4.2.2         tidyselect_1.2.0
-% ## [29] deSolve_1.34       glue_1.6.2         R6_2.5.1           fansi_1.0.3
-% ## [33] farver_2.1.1       purrr_0.3.5        magrittr_2.0.3     MASS_7.3-58.1
-% ## [37] codetools_0.2-18   ellipsis_0.3.2     splines_4.2.2      assertthat_0.2.1
-% ## [41] colorspace_2.0-3   labeling_0.4.2     utf8_1.2.2         stringi_1.7.8
-% ## [45] RcppParallel_5.1.5 munsell_0.5.0      hypergeo_1.2-13
-% \end{verbatim}
-% \end{kframe}
-% \end{knitrout}
+% Bibliography
+\bibliographystyle{apalikedoiurl}
+\bibliography{bibliography}

### 2022-11-25 paper3.tex
chapter specific referencing

@@
 goal is therefore to complement their article by developing a unified framework
-of replication SSD (schematically illustrated in Figure~\ref{fig:SSDschema})
+of replication SSD (schematically illustrated in Figure~\ref{fig3:SSDschema})
 based on principles from Bayesian design approaches \citep{Spiegelhalter1986b,
@@
     model parameter $\theta$.}
-\label{fig:SSDschema}
+\label{fig3:SSDschema}
 \end{figure}
@@
 
-\section{General framework} \label{sec:GFW}
-
-% Figure~\ref{fig:SSDschema} schematically illustrates the process of Bayesian SSD
+\section{General framework} \label{sec3:GFW}
+
+% Figure~\ref{fig3:SSDschema} schematically illustrates the process of Bayesian SSD
 % for replication studies, which we will explain in more detail in the following.
@@
 \begin{align}
-  \label{eq:dp}
+  \label{eq3:dp}
   f(\theta \given x_o, \text{external knowledge}) =
@@
 the original data. We will discuss common types of external knowledge in the
-replication setting in the next Section. %~\ref{sec:SS}.
-The design prior~\eqref{eq:dp} hence represents the state of knowledge and
+replication setting in the next Section. %~\ref{sec3:SS}.
+The design prior~\eqref{eq3:dp} hence represents the state of knowledge and
 uncertainty about the parameter $\theta$ before the replication is conducted,
@@
 \begin{align}
-  \label{eq:ftr}
+  \label{eq3:ftr}
   f(x_r \given n_r, x_o, \text{external knowledge})
@@
   replication success} can thus be computed by integrating the predictive
-density~\eqref{eq:ftr} over $S$. To ensure a sufficiently conclusive replication
+density~\eqref{eq3:ftr} over $S$. To ensure a sufficiently conclusive replication
 design, the sample size $n_{r}$ is determined such that the probability of
@@
 \begin{align}
-  \label{eq:nr}
+  \label{eq3:nr}
   n_r^* = \inf \left\{n_r : \Pr(X_{r} \in S \given
@@
 \section{Sample size determination in the normal-normal hierarchical model}
-\label{sec:SS}
+\label{sec3:SS}
 We will now illustrate the general methodology from the previous section in the
@@
 Assuming a normal sampling model for the effect
-estimates~\eqref{eq:hat_theta_k}, as described previously, and specifying an
+estimates~\eqref{eq3:hat_theta_k}, as described previously, and specifying an
 initial hierarchical normal prior for the study specific effect
-sizes~\eqref{eq:theta_k} and the effect size~\eqref{eq:theta}, leads then to the
+sizes~\eqref{eq3:theta_k} and the effect size~\eqref{eq3:theta}, leads then to the
 normal-normal hierarchical model
 \begin{subequations}
-\label{eq:hierarch-model}
+\label{eq3:hierarch-model}
 \begin{align}
   \hat{\theta}_k \given \mspace{-1mu} \theta_k &\sim \Nor(\theta_k, \sigma_k^2)
-  \label{eq:hat_theta_k} \\
-  \theta_k \given \theta \,\,  &\sim \Nor(\theta, \tau^2) \label{eq:theta_k} \\
+  \label{eq3:hat_theta_k} \\
+  \theta_k \given \theta \,\,  &\sim \Nor(\theta, \tau^2) \label{eq3:theta_k} \\
   \theta \,\, &\sim \Nor(\mutheta,
-  \sigmatheta^2). \label{eq:theta}
+  \sigmatheta^2). \label{eq3:theta}
 \end{align}
@@
 By marginalizing over the study specific effects sizes, the
-model~\eqref{eq:hierarch-model} can alternatively be expressed as
+model~\eqref{eq3:hierarch-model} can alternatively be expressed as
 \begin{subequations}
-\label{eq:hierarch-model2}
+\label{eq3:hierarch-model2}
 \begin{align}
   \hat{\theta}_k \given \mspace{-1mu} \theta &\sim \Nor(\theta, \sigma_k^2 + \tau^{2})
-  \label{eq:hat_theta_k2} \\
+  \label{eq3:hat_theta_k2} \\
   \theta  &\sim \Nor(\mutheta,
-  \sigmatheta^2) \label{eq:theta2}
+  \sigmatheta^2) \label{eq3:theta2}
 \end{align}
@@
 \subsection{Design prior and predictive distribution}
-\label{sec:designpredictive}
+\label{sec3:designpredictive}
 The observed original data $x_{o} = \{\that_{o}, \sigma_{o}\}$ can be combined
-with the initial prior~\eqref{eq:theta2} %by Bayes' theorem~\eqref{eq:dp}
+with the initial prior~\eqref{eq3:theta2} %by Bayes' theorem~\eqref{eq3:dp}
 by standard Bayesian theory for normal prior and likelihood \citep[ch.
@@
 \begin{align}
-  \label{eq:dpnormal}
+  \label{eq3:dpnormal}
   \theta \given \hat{\theta}_o, \sigma^2_o
@@
 
-It is interesting to contrast the design prior \eqref{eq:dpnormal} to the
+It is interesting to contrast the design prior \eqref{eq3:dpnormal} to the
 ``conditional'' design prior \citep{Micheloud2020}, that is, to assume that the
@@
 this assumption. In our framework it implies that the normal design
-prior~\eqref{eq:dpnormal} becomes a point mass at the original effect estimate
+prior~\eqref{eq3:dpnormal} becomes a point mass at the original effect estimate
 $\that_{o}$, which can either be achieved through overwhelmingly informative
@@
 
-Based on the design prior~\eqref{eq:dpnormal}, the predictive distribution of
+Based on the design prior~\eqref{eq3:dpnormal}, the predictive distribution of
 the replication effect estimate $\that_{r}$ can then be computed by assuming a
 replication standard error $\sigma_{r}$ and integrating the marginal density of
-the replication effect estimate~\eqref{eq:hat_theta_k2} with respect to the
+the replication effect estimate~\eqref{eq3:hat_theta_k2} with respect to the
 prior density, leading to
 \begin{align}
-  \label{eq:fthetar}
+  \label{eq3:fthetar}
   \hat{\theta}_r \given \hat{\theta}_o, \sigma^2_o, \sigma^2_r
@@
 % \begin{align}
-%   \label{eq:zr}
+%   \label{eq3:zr}
 %   z_r \given z_o, c%,  z_{\scriptscriptstyle{\theta}},h, g
@@
 % and the relative heterogeneity $h = \tau^{2}/\sigma^{2}_{o}$.
-The design prior~\eqref{eq:dpnormal} and the resulting predictive
-distribution~\eqref{eq:fthetar}
-% and~\eqref{eq:zr}
+The design prior~\eqref{eq3:dpnormal} and the resulting predictive
+distribution~\eqref{eq3:fthetar}
+% and~\eqref{eq3:zr}
 depend on the parameters of the initial prior ($\tau^ {2}$, $\mutheta$,
@@
 \subsection{Incorporating external knowledge in the initial prior}
-\label{sec:initialPrior}
+\label{sec3:initialPrior}
 
@@
 \subsubsection{Between-study heterogeneity}
-\label{sec:heterogeneity}
+\label{sec3:heterogeneity}
 The expected degree of between-study heterogeneity can be incorporated via the
-variance $\tau^2$ in~\eqref{eq:theta_k}. As $\tau^{2}$ decreases, the study
+variance $\tau^2$ in~\eqref{eq3:theta_k}. As $\tau^{2}$ decreases, the study
 specific effect sizes become more similar, whereas for increasing $\tau^{2}$
@@
 Prior knowledge about the effect size $\theta$ can be incorporated via the prior
-mean $\mutheta$ and the prior variance $\sigmatheta^2$ in~\eqref{eq:theta}. For
+mean $\mutheta$ and the prior variance $\sigmatheta^2$ in~\eqref{eq3:theta}. For
 instance, the parameters may be specified based on a meta-analysis of related
@@
 \subsubsection{Exaggerated original results}
-\label{sec:shrinkage}
+\label{sec3:shrinkage}
 Potentially exaggerated original results can be counteracted by setting
@@
 \begin{align}
-  \label{eq:EBestimate}
+  \label{eq3:EBestimate}
   \hat{\sigma}^2_{\scriptscriptstyle{\theta}} = \max\{(\that_{o} - \mutheta)^{2} - \tau^{2} - \sigma^{2}_{o}, 0\}.
 \end{align}
-The estimate~\eqref{eq:EBestimate} will lead to adaptive shrinkage
+The estimate~\eqref{eq3:EBestimate} will lead to adaptive shrinkage
 \citep{Pawel2020} in the sense that shrinkage is large for unconvincing original
@@
 \subsection{Example: Cross-laboratory replication project}
-\label{sec:example}
+\label{sec3:example}
 We will now illustrate the construction of design priors based on data from a
 recently conducted replication project \citep{Protzko2020}, see
-Figure~\ref{fig:data} for a summary of the data. The data were collected in four
+Figure~\ref{fig3:data} for a summary of the data. The data were collected in four
 laboratories which, over the course of five years, conducted their typical
@@
   $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$)}
-\label{fig:data}
+\label{fig3:data}
 \end{figure}
@@
   \sigma^{2}_{i} = \frac{n_{i1} + n_{i2}}{n_{i1}n_{i2}} + \frac{\that_{i}^{2}}{2(n_{i1} + n_{i2})}
-  \label{eq:varSMD}
+  \label{eq3:varSMD}
 \end{align}
@@
 both groups $n_{i1} = n_{i2} = n_{i}/2$, with $n_{i}$ the total sample size, and
-neglecting the second term in~\eqref{eq:varSMD} which will be close to zero for
+neglecting the second term in~\eqref{eq3:varSMD} which will be close to zero for
 small effect estimates and/or large sample sizes \citep{Hedges2021}. We thus
@@
 the ``absolute'' approach as discussed previously,
-% in Section~\ref{sec:heterogeneity},
+% in Section~\ref{sec3:heterogeneity},
 so that the range between the 2.5\% and the 97.5\% quantile of the study
@@
   ``shrinkage'' corresponds to a zero-mean normal prior with empirical Bayes
-  variance estimate~\eqref{eq:EBestimate}, and ``optimistic'' corresponds to a
+  variance estimate~\eqref{eq3:EBestimate}, and ``optimistic'' corresponds to a
   flat prior updated by the data from a pilot study with effect estimate
@@
   $\sigma_{p} = 0.052$.}
-\label{fig:dpexample}
+\label{fig3:dpexample}
 \end{figure}
@@
 $\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$
-for an external-replication. Figure~\ref{fig:dpexample} (dark-gray solid lines)
+for an external-replication. Figure~\ref{fig3:dpexample} (dark-gray solid lines)
 shows the densities of the two priors.
@@
 instance, the empirical Bayes estimate for the prior variance $\sigmatheta^{2}$
-from~\eqref{eq:EBestimate} leads to a prior whose mean and variance are shrunken
+from~\eqref{eq3:EBestimate} leads to a prior whose mean and variance are shrunken
 towards zero by $12$\% (medium-gray
-dashed lines in Figure~\ref{fig:dpexample}). In contrast, if we had prior
+dashed lines in Figure~\ref{fig3:dpexample}). In contrast, if we had prior
 knowledge about the effect size $\theta$ from another study, we could have
@@
 sum of the precision of both estimates (light-gray dot-dashed lines in
-Figure~\ref{fig:dpexample}). Due to the inclusion of the external data, this
+Figure~\ref{fig3:dpexample}). Due to the inclusion of the external data, this
 design prior is much more concentrated than the other two.
@@
 To compute the probability of replication success one needs to select an
-analysis method and integrate the predictive distribution~\eqref{eq:fthetar}
-% , respectively, \eqref{eq:zr}
+analysis method and integrate the predictive distribution~\eqref{eq3:fthetar}
+% , respectively, \eqref{eq3:zr}
 over the associated success region $S$. There is no universally accepted method
@@
 \begin{align}
-  \label{eq:2TRpros}
+  \label{eq3:2TRpros}
   \Pr(\that_{r} \in S_{\scriptscriptstyle \text{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
@@
 $\muthatr$ and $\sigmathatr$ the mean and standard deviation of the predictive
-distribution~\eqref{eq:fthetar}. %, the latter also depending on $\sigma_{r}$.
+distribution~\eqref{eq3:fthetar}. %, the latter also depending on $\sigma_{r}$.
 Importantly, by decreasing the standard error $\sigma_{r}$ (through increasing
 the sample size $n_{r}$), the probability of replication
-success~\eqref{eq:2TRpros} cannot become arbitrarily large but is bounded from
+success~\eqref{eq3:2TRpros} cannot become arbitrarily large but is bounded from
 above by
 \begin{align}
-  \label{eq:limP2TR}
+  \label{eq3:limP2TR}
   \text{limPr}_{\scriptscriptstyle \text{2TR}} =
@@
 $1 - \beta < \text{limPr}_{\scriptscriptstyle \text{2TR}}$ can now be obtained
-by equating~\eqref{eq:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
+by equating~\eqref{eq3:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
 leads to
 \begin{align}
-  \label{eq:ssd2tr}
+  \label{eq3:ssd2tr}
   \sigma_{r}^{*} =
@@
 $n_{r}^{*} \approx 4/(\sigma^*_{r})^{2}$ from
-earlier. %Section~\ref{sec:example}.
+earlier. %Section~\ref{sec3:example}.
 Moreover, by assuming a standard error of the form
 $\sigma_{r} = \lambda/\sqrt{n_{r}}$ and plugging in the parameters of the
-``conditional'' design prior %from Section~\ref{sec:designpredictive}
+``conditional'' design prior %from Section~\ref{sec3:designpredictive}
 ($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$), we obtain the
@@
 for a one-sided significance test at level $\alpha$ with power $1 - \beta$ to
-detect the original effect estimate $\that_{o}$. The formula~\eqref{eq:ssd2tr}
+detect the original effect estimate $\that_{o}$. The formula~\eqref{eq3:ssd2tr}
 thus generalizes standard sample size calculation to take into account the
@@
 \begin{align}
-  \label{eq:SMA}
+  \label{eq3:SMA}
   S_{\scriptscriptstyle \text{MA}}
@@
 $\Pr(\theta > 0 \given \that_{o}, \that_{r}, \sigma_{o}, \sigma_{r}) \geq 1 - \alpha$.
-Based on the success region~\eqref{eq:SMA} and an assumed standard error
+Based on the success region~\eqref{eq3:SMA} and an assumed standard error
 $\sigma_{r}$, the probability of replication success can be computed by
 \begin{align}
-  \label{eq:MApros}
+  \label{eq3:MApros}
   \Pr(\that_{r} \in S_{\scriptscriptstyle \text{MA}} \given \that_{o}, \sigma_{o}, \sigma_{r})
@@
 \end{align}
-As for the two-trials rule, the probability~\eqref{eq:MApros} cannot be made
+As for the two-trials rule, the probability~\eqref{eq3:MApros} cannot be made
 arbitrarily large by decreasing the standard error $\sigma_{r}$ but is bounded
-from above by $\text{limPr}_{\text{2TR}}$ defined in~\eqref{eq:limP2TR}.
+from above by $\text{limPr}_{\text{2TR}}$ defined in~\eqref{eq3:limP2TR}.
 % However, as the original data already provide some information, the
@@
 \begin{align}
-  \label{eq:equivalence}
+  \label{eq3:equivalence}
   S_{\scriptscriptstyle \text{E}}
@@
 small margins ($\Delta < \zalphatwo \sqrt{\sigma_{o}^{2} + \sigma^{2}_{r}}$),
-the success region~\eqref{eq:equivalence} becomes the empty set meaning that
+the success region~\eqref{eq3:equivalence} becomes the empty set meaning that
 replication success is impossible.
@@
 \begin{align}
-  \label{eq:porsEqu}
+  \label{eq3:porsEqu}
   \Pr(\that_{r} \in S_{\scriptscriptstyle \text{E}} \given \that_{o}, \sigma_{o}, \sigma_{r})
@@
 \end{align}
-As with the previous methods, the probability~\eqref{eq:porsEqu} cannot be made
+As with the previous methods, the probability~\eqref{eq3:porsEqu} cannot be made
 arbitrarily large by decreasing the replication standard error $\sigma_{r}$, but
@@
 \begin{align}
-  \label{eq:BFrsuccess}
+  \label{eq3:BFrsuccess}
   S_{\scriptscriptstyle \BFr}
@@
 Details of this calculation are given in the supplement. The fact that the
-success region~\eqref{eq:BFrsuccess} is defined on both sides around zero shows
+success region~\eqref{eq3:BFrsuccess} is defined on both sides around zero shows
 that replication success is also possible if the replication effect estimate
@@
 longer available in closed-form \citep[Appendix D]{Pawel2022b}. Based on the
-success region~\eqref{eq:BFrsuccess}, the probability of replication success can
+success region~\eqref{eq3:BFrsuccess}, the probability of replication success can
 be computed by
 \begin{align}
-  \label{eq:BFrpros}
+  \label{eq3:BFrpros}
   \Pr(\that_{r} \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})
@@
 avoid the replication paradox. As for the other methods, the
-probability~\eqref{eq:BFrpros} is bounded from above by a constant
+probability~\eqref{eq3:BFrpros} is bounded from above by a constant
 $\text{limPr}_{\scriptscriptstyle \BFr} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})$,
@@
 \begin{align}
-  \label{eq:Pssuccess}
+  \label{eq3:Pssuccess}
   S_{\scriptscriptstyle \ps}
@@
 \end{align}
-From the success region~\eqref{eq:Pssuccess} the probability of replication
+From the success region~\eqref{eq3:Pssuccess} the probability of replication
 success at level $\alpha$ is
@@
 We will now revisit the experiment ``Labels'' % from
-% Section~\ref{sec:example}
+% Section~\ref{sec3:example}
 and compute the probability of replication success.
@@
   $\gamma = 1/10$.}
-\label{fig:example}
+\label{fig3:example}
 \end{figure}
-Figure~\ref{fig:example} shows the probability of replication success as a
+Figure~\ref{fig3:example} shows the probability of replication success as a
 function of the relative sample size $c = n_{r}/n_{o}$ and for different initial
@@
 
-The right plot in Figure~\ref{fig:example} shows that the type I error rate of
+The right plot in Figure~\ref{fig3:example} shows that the type I error rate of
 the two-trials rule (black) stays constant at
@@
   $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
-\label{fig:ssd-all}
+\label{fig3:ssd-all}
 \end{figure}
@@
 We now conduct SSD for all studies from the replication project of
-\citet{Protzko2020}. Figure~\ref{fig:ssd-all} shows the required relative sample
+\citet{Protzko2020}. Figure~\ref{fig3:ssd-all} shows the required relative sample
 size and the associated type I error rates if a sample size can be computed for
@@
 \begin{subequations}
-\label{eq:hierarch-model2}
+\label{eq3:hierarch-model2}
 \begin{align}
   \bthat_r \given \mspace{-1mu} \btheta_r &\sim \Nor_{m}\left\{\btheta_r, \text{diag}\left(\bsigma_r^2\right)\right\}
-  \label{eq:hat_theta_k22} \\
+  \label{eq3:hat_theta_k22} \\
   \btheta_r \given \theta \,\,  &\sim \Nor_{m}\left\{\theta \, \bone_{m},
-  \tau^2 \text{diag}(\bone_{m})\right\}, \label{eq:theta_k2}
+  \tau^2 \text{diag}(\bone_{m})\right\}, \label{eq3:theta_k2}
 \end{align}
@@
 \text{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right)\right\},
-  \label{eq:margimulti}
+  \label{eq3:margimulti}
 \end{align}
 so the predictive distribution of $\bthat_r$ based on the design
-prior~\eqref{eq:dpnormal} is given by
+prior~\eqref{eq3:dpnormal} is given by
 \begin{align}
@@
   \bone_{m} \bone_{m}^{\top} \right\}
-  \label{eq:ftrmulti}
+  \label{eq3:ftrmulti}
 \end{align}
 with $ \muthatr$ the mean of the predictive distribution of a single replication
-effect estimate from~\eqref{eq:fthetar}. Importantly, the replication effect
-estimates are correlated as the covariance matrix in~\eqref{eq:ftrmulti} has
+effect estimate from~\eqref{eq3:fthetar}. Importantly, the replication effect
+estimates are correlated as the covariance matrix in~\eqref{eq3:ftrmulti} has
 $(\tau^2+\sigma^{2}_{o})/(1 + 1/g)$ in the off-diagonal entries.
@@
 effect estimates achieving statistical significance. Based on the predictive
-distribution of the replication effect estimate vector~\eqref{eq:ftrmulti}, the
+distribution of the replication effect estimate vector~\eqref{eq3:ftrmulti}, the
 predictive distribution of the weighted average $\hat{\theta}_{r*}$ is given by
@@
 \frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g} \biggr)\big/\biggl(\sum_{i=1}^{m} w_{i}\biggr)^{2} \Biggr\}
-  \label{eq:ftwm}
+  \label{eq3:ftwm}
 \end{align}
@@
 single replication effect estimate with standard error $\sigma_{ri}$ as
-in~\eqref{eq:fthetar}. In particular when the studies receive equal weights
+in~\eqref{eq3:fthetar}. In particular when the studies receive equal weights
 ($w_{i} = w$ for $i = 1, \dots, m$) and the standard errors of the replication
@@
   \frac{\sigma^{2}_{r} + \tau^{2}}{m} + \frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g}.
-  \label{eq:predvarequal}
+  \label{eq3:predvarequal}
 \end{align}
 The probability of replication success can now be obtained by
-integrating~\eqref{eq:ftrmulti}, respectively~\eqref{eq:ftwm}, over the
+integrating~\eqref{eq3:ftrmulti}, respectively~\eqref{eq3:ftwm}, over the
 corresponding success region $S$. This may be more involved if the success
@@
 corresponds to minimizing the variance of the weighted average
-$\sigma^{2}_{\scriptscriptstyle \that_{r*}}$ in~\eqref{eq:predvarequal}. % This
+$\sigma^{2}_{\scriptscriptstyle \that_{r*}}$ in~\eqref{eq3:predvarequal}. % This
 % is, for instance, the case if the analysis consists of computing a $p$-value for
@@
 $K = m(K_{c} \, n_{r} + K_{s})$, and constrained minimization of the predictive
-variance~\eqref{eq:predvarequal} leads to the optimal sample size per site
+variance~\eqref{eq3:predvarequal} leads to the optimal sample size per site
 \begin{align*}
@@
 \subsection{Example: Cross-laboratory replication project (continued)}
-Figure~\ref{fig:multisite} illustrates multisite SSD for the experiment
+Figure~\ref{fig3:multisite} illustrates multisite SSD for the experiment
 ``Labels'' from \citet{Protzko2020} for planned analyses based on the
@@
   $1 - \beta = 80$\%.}
-\label{fig:multisite}
+\label{fig3:multisite}
 \end{figure}
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{sec3:discussion}
 
@@
 of the replication effect estimate when a prior is assigned to the heterogeneity
-variance $\tau^{2}$ (Section~\ref{sec:priortau}). We also provide additional
+variance $\tau^{2}$ (Section~\ref{sec3sup:priortau}). We also provide additional
 information on methods for analyzing replication data. For each method we derive
@@
 study $\that_{r}$, which is required for sample size determination as
-illustrated in the main manuscript (Section~\ref{sec:2TR} to~\ref{sec:BFs}). For
+illustrated in the main manuscript (Section~\ref{sec3sup:2TR} to~\ref{sec3sup:BFs}). For
 the two-trials rule and the replication Bayes factor methods we additionally
@@
 replication setting. We show then how the optimal number of samples per site can
-be derived for multisite SSD (Section~\ref{sec:multi}). Finally, we show SSD for
+be derived for multisite SSD (Section~\ref{sec3sup:multi}). Finally, we show SSD for
 the \citet{Protzko2020} project but using an adaptive shrinkage prior instead of
-the flat prior as in the main manuscript (Section~\ref{sec:ssdprotzko}).
+the flat prior as in the main manuscript (Section~\ref{sec3sup:ssdprotzko}).
 
 \subsection{Prior on the heterogeneity variance}
-\label{sec:priortau}
+\label{sec3sup:priortau}
 When also a prior is assigned to the heterogeneity variance $\tau^{2}$, the
@@
 variance requires at least two observations. The phenomenon is illustrated in
-Figure~\ref{fig:margposttau2} for the data from the experiment ``Labels''
+Figure~\ref{fig3sup:margposttau2} for the data from the experiment ``Labels''
 \citep{Protzko2020} as also used in the main manuscript. We see that as the
@@
   $0.04$ is assigned to $\tau$.}
-\label{fig:margposttau2}
+\label{fig3sup:margposttau2}
 \end{figure}
@@
   $\gamma = 1/10$.}
-\label{fig:exampletaurandom}
+\label{fig3sup:exampletaurandom}
 \end{figure}
 
-Figure~\ref{fig:exampletaurandom} shows the probability of replication success
-based on data from the ``Labels'' experiment, as in the main manuscript. A half
-normal prior with is assigned to the heterogeneity $\tau$ which is a typical
-prior distribution used for heterogeneity modeling in meta-analysis
-\citep{Rover2021}. The standard deviation of the prior is set to
-$0.04$ so that the mean of the prior equals the value of
-the fixed heterogeneity $\tau = 0.05$ elicited in the main manuscript. We see
-that the probability of replication success is only slightly higher compared to
-the fixed $\tau = 0.05$ from the main manuscript.
+Figure~\ref{fig3sup:exampletaurandom} shows the probability of replication
+success based on data from the ``Labels'' experiment, as in the main manuscript.
+A half normal prior with is assigned to the heterogeneity $\tau$ which is a
+typical prior distribution used for heterogeneity modeling in meta-analysis
+\citep{Rover2021}. The standard deviation of the prior is set to $0.04$ so that
+the mean of the prior equals the value of the fixed heterogeneity $\tau = 0.05$
+elicited in the main manuscript. We see that the probability of replication
+success is only slightly higher compared to the fixed $\tau = 0.05$ from the
+main manuscript.
 
 \subsection{The two-trials rule}
-\label{sec:2TR}
+\label{sec3sup:2TR}
 The two-trials rule is the most common analysis approach for replication
@@
 \begin{align}
-  \label{eq:bfr}
+  \label{eq3sup:bfr}
   \BFr &= \frac{f(\that_{r} \given H_{0})}{f(\that_{r} \given H_{1})}
@@
 The multisite replication Bayes factor is therefore equivalent to the singlesite
-replication Bayes factor from~\eqref{eq:bfr} but using the weighted average
+replication Bayes factor from~\eqref{eq3sup:bfr} but using the weighted average
 $\that_{r*}$ and its standard error $\sigma_{r*}$ as the replication effect
@@
 \subsection{The sceptical Bayes factor}
-\label{sec:BFs}
+\label{sec3sup:BFs}
 \citet{Pawel2022b} modified the reverse-Bayes assessment of replication success
@@
 \begin{align}
-  \label{eq:ssv}
+  \label{eq3sup:ssv}
   \sigma^{2}_{s} &=
@@
 \begin{align}
-  \label{eq:BFssuccess}
+  \label{eq3sup:BFssuccess}
   S_{\scriptscriptstyle \BFs}
@@
 and the sufficiently sceptical prior variance $\sigma^{2}_{s}$ computed
-by~\eqref{eq:ssv}.
+by~\eqref{eq3sup:ssv}.
 
 \subsection{Optimal number of sites}
-\label{sec:multi}
+\label{sec3sup:multi}
 The total cost of the design are $K = m(K_{c}n_{r} + K_{s})$ so that we can
@@
 \begin{align}
-  \label{eq:msites}
+  \label{eq3sup:msites}
   m = K (K_{c}n_{r} + K_{s})^{-1}.
@@
 \begin{align}
-  \label{eq:predvar}
+  \label{eq3sup:predvar}
   \sigma^{2}_{\scriptscriptstyle \that_{r*}}
@@
 \end{align}
-Plugging in~\eqref{eq:msites} into~\eqref{eq:predvar} and minimizing it with
+Plugging in~\eqref{eq3sup:msites} into~\eqref{eq3sup:predvar} and minimizing it with
 respect to $n_{r}$, leads to the optimal sample size
@@
 \caption{The left plot shows the required relative sample size $c = n_r/n_o$ to
-  achieve a target probability of replication success of
-  $1 - \beta = 80$\% (if possible). Replication success
-  is defined through the two-trials rule at level $\alpha = 0.025$,
-  replication Bayes factor at level $\gamma = 1/10$, fixed
-  effects-meta analysis at level $\alpha = 0.025^{2}$,
-  effect size equivalence at level $\alpha = 0.1$ with margin
-  $\Delta = 0.2$, sceptical $p$-value at level
-  $\alpha = 0.062$, and sceptical Bayes factor at level
-  $\gamma = 1/10$ for data from the replication project by
-  \citet{Protzko2020}. An adaptive shrinkage prior is used for the effect size
-  $\theta$ either without ($\tau = 0$) or with between-study heterogeneity
-  ($\tau = 0.05$). The right plot shows the type I error
-  rate associated with the required sample size. Experiments are ordered (top to
-  bottom) by their original one-sided $p$-value
+  achieve a target probability of replication success of $1 - \beta = 80$\% (if
+  possible). Replication success is defined through the two-trials rule at level
+  $\alpha = 0.025$, replication Bayes factor at level $\gamma = 1/10$, fixed
+  effects-meta analysis at level $\alpha = 0.025^{2}$, effect size equivalence
+  at level $\alpha = 0.1$ with margin $\Delta = 0.2$, sceptical $p$-value at
+  level $\alpha = 0.062$, and sceptical Bayes factor at level $\gamma = 1/10$
+  for data from the replication project by \citet{Protzko2020}. An adaptive
+  shrinkage prior is used for the effect size $\theta$ either without
+  ($\tau = 0$) or with between-study heterogeneity ($\tau = 0.05$). The right
+  plot shows the type I error rate associated with the required sample size.
+  Experiments are ordered (top to bottom) by their original one-sided $p$-value
   $p_{o} = 1 - \Phi(|\hat{\theta}_{o}|/\sigma_{o}$).}
-\label{fig:ssd-all-shrink}
+\label{fig3sup:ssd-all-shrink}
 \end{figure}
@@
 \subsection{Sample size determination with adaptive shrinkage prior}
-\label{sec:ssdprotzko}
-Figure~\ref{fig:ssd-all-shrink} shows sample size determination for all studies
-from the \citet{Protzko2020} project as in the main manuscript but using an
-``adaptive shrinkage prior'' for the effect size $\theta$ where the variance of
-the shrinkage prior is estimated by empirical Bayes. We see that the required
+\label{sec3sup:ssdprotzko}
+Figure~\ref{fig3sup:ssd-all-shrink} shows sample size determination for all
+studies from the \citet{Protzko2020} project as in the main manuscript but using
+an ``adaptive shrinkage prior'' for the effect size $\theta$ where the variance
+of the shrinkage prior is estimated by empirical Bayes. We see that the required
 sample size increases for studies with large $p$-values compared to the analysis

### 2022-11-25 paper5.tex
chapter specific referencing

@@
   &\tau^{2}_{p} = \frac{\sigma^{2}}{2}&
-  \label{eq:varconstraints}
+  \label{eq5:varconstraints}
 \end{align}
@@
   L_{p} = \mu_{p} - z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
-  \label{eq:postcredL}
+  \label{eq5:postcredL}
 \end{align}
@@
   U_{p} = \mu_{p} + z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
-  \label{eq:postcredU}
+  \label{eq5:postcredU}
 \end{align}
 with $z_{\scriptscriptstyle \alpha/2}$ the $1 - \alpha/2$ quantile of the
-standard normal distribution. Combining Eq.~\eqref{eq:varconstraints} with
-Eq.~\eqref{eq:postcredL}, respectively Eq.~\eqref{eq:postcredU}, leads to
+standard normal distribution. Combining Eq.~\eqref{eq5:varconstraints} with
+Eq.~\eqref{eq5:postcredL}, respectively Eq.~\eqref{eq5:postcredU}, leads to
 \begin{align}
@@
   & =  \sign(\hat{\theta}) \sqrt{2} \, z_{\scriptscriptstyle \alpha/2} \, \sigma - \hat{\theta}
-    \label{eq:bae}
+    \label{eq5:bae}
 \end{align}
@@
   \text{BAE} = \frac{\text{sign}(\hat{\theta}) \sqrt{2} (U - L) - (U + L)}{2}
-  \label{eq:baeneg}
+  \label{eq5:baeneg}
 \end{align}
-We see from Eq.~\eqref{eq:bae} that Sondhi et al.'s proposal has the intuitive
+We see from Eq.~\eqref{eq5:bae} that Sondhi et al.'s proposal has the intuitive
 property that as the study becomes more convincing (through larger effect sizes
@@
 additional evidence is needed to push a non-significant study towards
-credibility. Eq.~\eqref{eq:bae} and Eq.~\eqref{eq:baeneg} also hold for
+credibility. Eq.~\eqref{eq5:bae} and Eq.~\eqref{eq5:baeneg} also hold for
 significant studies but the BAE then represents the mean of a ``sceptical''
@@
 have $L = -1.97$ and
-$U = 0.21$. We use Eq.~\eqref{eq:baeneg} and find that
+$U = 0.21$. We use Eq.~\eqref{eq5:baeneg} and find that
 on log hazard ratio scale $\mbox{BAE} = -0.66$ equivalent to an
-HR of $0.52$. Figure~\ref{fig:illustration} shows the
+HR of $0.52$. Figure~\ref{fig5:illustration} shows the
 corresponding prior mean with 95\% prior
@@
   \citet{Innocenti2019} are also shown.}
-\label{fig:illustration}
+\label{fig5:illustration}
 \end{figure}
@@
   respective method.}
-\label{fig:priospace}
+\label{fig5:priospace}
 \end{figure}
@@
 more diffuse, so less additional evidence is needed to render the finding
-credible. We see in Figure~\ref{fig:illustration} that prior and posterior are
+credible. We see in Figure~\ref{fig5:illustration} that prior and posterior are
 similar to BAE for the clinical trial data from Sondhi et al.
 
-Figure~\ref{fig:illustration} also illustrates that the BAE and the fixed mean
+Figure~\ref{fig5:illustration} also illustrates that the BAE and the fixed mean
 approach can lead to priors which support effect sizes opposing that of the
@@
 
-Figure~\ref{fig:illustration} shows that the AnCred advocacy prior credible
+Figure~\ref{fig5:illustration} shows that the AnCred advocacy prior credible
 interval is far wider compared to the other approaches. Perhaps this observation
@@
     - g \, \hat{\theta}
-    \label{eq:bae2}
+    \label{eq5:bae2}
 \end{align}
 with relative prior variance $g = \tau^{2}/\sigma^{2}$. We see from
-Figure~\ref{fig:priospace} that Eq.~\eqref{eq:bae2} substantially depends on the
+Figure~\ref{fig5:priospace} that Eq.~\eqref{eq5:bae2} substantially depends on the
 chosen prior variance and that the BAE based on $g = 1$ only captures a limited
@@
 principled AnCred advocacy prior or on a visualisation of the prior parameter
-space as in Figure~\ref{fig:priospace}.
+space as in Figure~\ref{fig5:priospace}.
 

### 2022-11-28 abstract.tex
paper 2
Maria feedback

@@
 The fact that a scientific finding can be replicated in an independent
-replication study is central for its credibility. However, various large-scale
+replication study is central to its credibility. However, various large-scale
 replication failures have shown that the replicability of scientific findings is
@@
 analysis of replication studies; Various methods already exist and various new
-ones have been proposed in response to the crisis. This thesis centres around
-the proposal from \citet{Held2020}, which is based on a reverse-Bayes approach.
-The key idea is to reverse the traditional ``forward'' use of Bayes' theorem
-(``prior + likelihood $\rightarrow$ posterior''), starting instead with a
-pre-specified posterior and deducing the corresponding prior (``posterior +
-likelihood $\rightarrow$
+ones have been proposed in response to the crisis. This thesis centres around a
+proposal based on the reverse-Bayes approach. The key idea is to reverse the
+traditional ``forward'' use of Bayes' theorem (``prior + likelihood
+$\rightarrow$ posterior''), starting instead with a pre-specified posterior and
+deducing the corresponding prior (``posterior + likelihood $\rightarrow$
 prior''). % As such, the reverse-Bayes approach naturally fits to the replication
@@
 % finding from the original study.
-This allows to challenge the original finding by determining a sceptical prior
-for the underlying effect size such that the resulting posterior is no longer
-convincing. This prior then represents the position of a sceptic who remains
-unconvinced by the original study. Whether or not the sceptics' position is
-justified can then be assessed in light of the new data from the replication
+This allows us to challenge the original finding by determining a sceptical
+prior for the underlying effect size such that the resulting posterior is no
+longer convincing. This prior then represents the position of a sceptic who
+remains unconvinced by the original study. Whether or not the sceptics' position
+is justified can then be assessed in light of the new data from the replication
 study. The larger the conflict between the replication data and the sceptic, the
@@
 probabilities, Bayes factors have a more natural interpretation and allow for
-direct quantification of evidence for one hypothesis versus another. Similarly
-as with the sceptical $p$-value, the procedure leads to a single measure
-quantifying the degree of replication success called the sceptical Bayes factor.
-A second extensions recalibrates the original procedure to produce more
-appropriate inferences in terms of effect size. % from the relative effect size
+direct quantification of evidence for one hypothesis versus another. As with the
+sceptical $p$-value, the procedure leads to a single measure quantifying the
+degree of replication success called the sceptical Bayes factor. A second
+extensions recalibrates the original procedure to produce more appropriate
+inferences in terms of effect size. % from the relative effect size
 % perspective
@@
 estimate is larger than the original one. The third extension provides a
-framework for Bayesian design of replication studies. The framework allows
+framework for Bayesian design of replication studies. This framework allows for
 combining the data from the original study with external knowledge, which leads

### 2022-11-28 intro.Rnw
Maria feedback

@@
 
-How can we know if a finding from a study is really true? For example, how can
-we know if the protective effect of a vaccine found in a study is real? The
-answer to this question is of highest importance to scientists and decision
-makers, but typically we can never know for sure as any study result comes with
-uncertainty.
+How can we know if a finding from a scientific study is really true? For
+example, how can we know if the protective effect of a vaccine found in a study
+is real? The answer to this question is of highest importance to scientists and
+decision makers, but typically we can never know for sure as any study result
+comes with uncertainty.
 
@@
 One way to come a little closer to the truth, however, is to repeat that
-original study with new subjects. Such a \emph{replication study} may then yield
+original study with new subjects. Such a \emph{replication study} may yield
 similar results which would make us more confident about the original finding,
@@
 of a drug). The results from replication studies may thus have real world
-consequences, such as deciding whether we should get vaccinated (a consequence
-that anyone who experienced the COVID-19 pandemic is very aware of).
+consequences, such as deciding whether we receive the recommendation to get
+vaccinated (a consequence that anyone who experienced the COVID-19 pandemic is
+very aware of).
 
@@
 unattractive for researchers to conduct replication studies; the currencies of
-science --publications, citations, and grant money-- are typically easier to
+science -- publications, citations, and grant money -- are typically easier to
 acquire by conducting novel research. This is because until relatively recently,
 top journals in many fields refused to publish replication studies as they were
-considered not ``innovative'' enough. To build a successful career, researchers
+not considered ``innovative'' enough. To build a successful career, researchers
 thus often had no other choice than to concentrate their efforts on producing
@@
 science as being in a ``replication crisis''. Debates arose about whether or not
-the crisis really existed, and who or what was to blame \citep{Gilbert2016,
+the crisis really existed and who or what was to blame \citep{Gilbert2016,
   Amrhein2019}. Even the popular press became interested
@@
                                     2310, 2190, 2120, 2020, 1920, 1840, 1730,
-                                    1490, 1270, 1230, 1140, 1070, 970))
+                                    1490, 1270, 1230, 1140, 1070, 970),
+                        study = c(156000, 487000, 1820000, 959000, 2360000,
+                                  675000, 3000000, 688000, 3150000, 512000,
+                                  3630000, 451000, 3650000, 396000, 3680000,
+                                  389000, 3890000, 375000, 3950000, 336000,
+                                  4160000, 364000, 4240000, 385000, 3470000,
+                                  377000, 3120000, 335000, 2620000, 376000,
+                                  2440000, 317000, 2220000))
 
@@
     geom_point() +
-    scale_y_continuous(breaks = seq(0, 15000, 2500)) +
+    ## scale_y_continuous(breaks = seq(0, 15000, 2500)) +
     scale_x_continuous(breaks = seq(1990, 2020, 5)) +
@@
 various reforms were implemented to safe the reputation of science and to
-prevent a second crisis from happening \citep[for an overview see
+prevent an escalation of the situation \citep[for an overview see
 \eg{}][]{Munafo2017}. For instance, many journals adopted the ``registered
@@
 science framework (\url{https://osf.io/}), were created to facilitate
-preregistration, preprints, code, and data sharing, all of which have
+preregistration, preprints, and code and data sharing, all of which have
 substantially increased over the last decade \citep{Kidwell2016, Nosek2018,
   Rawlinson2019}. The practice of conducting replication studies has also gained
-popularity, and several journals and funders are now explicitly promoting and
-funding replication research \citep{NWO2016, NSL2018, Nature2022}.
+popularity, and several academic journals and funders are now explicitly
+promoting and funding replication research \citep{NWO2016, NSL2018, Nature2022}.
 Figure~\ref{fig:scholar} illustrates this trend via the yearly number of results
@@
 has not yet agreed on one important question: When is a replication study
-successful? For this reason, replication researchers typically report the
-results from different methods for assessing replication success. For example,
-\citet{Opensc2015} state ``[t]here is no single standard for evaluating
-replication success. We evaluated [replicability] using significance and P
-values, effect sizes, subjective assessments of replication teams, and
+considered successful? For this reason, replication researchers typically report
+the results from different methods for assessing replication success. For
+example, the \citet{Opensc2015} states ``[t]here is no single standard for
+evaluating replication success. We evaluated [replicability] using significance
+and P values, effect sizes, subjective assessments of replication teams, and
 meta-analyses of effect sizes'' (p. 11). In the following, I will give an
@@
   \centering
-  \caption{Study level summary statistics for original and replication study.
-    The cumulative distribution function of the standard normal distribution is
-    denoted by $\Phi(\cdot)$, and the $1 - \alpha$ quantile of the standard
-    normal distribution is denoted by $\Phi^{-1}(1 - \alpha) = \z{\alpha}$.
-    Confidence intervals and $p$-values are based on a normal approximation.}
+  \caption{Study level summary statistics for an original and a replication
+    study. The cumulative distribution function of the standard normal
+    distribution is denoted by $\Phi(\cdot)$, and the $1 - \alpha$ quantile of
+    the standard normal distribution is denoted by
+    $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and $p$-values
+    are based on the normality assumption.}
   \label{tab:meta}
@@
 All of these are routinely reported in researcher articles, and if one of them
-is missing they typically can, under some assumptions, be back-calculated from
-the others. Using summary statistics is also often the only possible way for
+is missing they typically can, under some assumptions, be calculated from the
+others. Using summary statistics is also often the only possible way for
 conducting the analysis as the raw data from the original study may not be
@@
 (for continuous outcomes), odds ratios (for binary outcomes), or hazard ratios
-(for time to event outcomes). Depending on the effect size type, a
+(for time to event outcomes). Depending on the type of effect size, a
 transformation might be required so that the assumption of approximately
 normally distributed effect estimates around the unknown effect size $\theta$
-(for large enough sample sizes) is justifiable. This could be, for instance, the
+(for large enough sample sizes) is justified. This could be, for instance, the
 Fisher $z$-transformation for correlations, or the log-transformation for
@@
                    the same direction
-                   ($p_{o} < \alpha$, $p_{r} < \alpha$, and
-                   $\sign(\that_{o}) = \sign(\that_{r})$). Usually $\alpha = 5\%$.
+                   (\mbox{$p_{o} < \alpha$}, \mbox{$p_{r} < \alpha$}, and
+                   \mbox{$\sign(\that_{o}) = \sign(\that_{r})$}). Usually $\alpha = 5\%$.
     \\
@@
     Meta-analytic significance & The meta-analytic $p$-value is smaller than a threshold
-                                 $\alpha$ ($p_{m} = 2(1 - \Phi(|\that_{m}|/\sigma_{m})) < \alpha$)
-                                 where $\that_{m} =
-                                 (\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r})\sigma^{2}_{m}$
+                                 $\alpha$ (\mbox{$p_{m} = 2\{1 - \Phi(|\that_{m}|/\sigma_{m})\} < \alpha$})
+                                 where \mbox{$\that_{m} =
+                                 (\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r})\sigma^{2}_{m}$}
                                  is the  pooled effect estimate with standard error
-                                 $\sigma_{m} = (1/\sigma^{2}_{o} + 1/\sigma^{2}_{r})^{-1/2}$.
+                                 \mbox{$\sigma_{m} = (1/\sigma^{2}_{o} + 1/\sigma^{2}_{r})^{-1/2}$}.
                                  Usually $\alpha = 5\%$. \\
@@
     Relative effect size & The effect estimate of the replication study goes in the same
-                           direction and is at least as large as $d_{\text{min}}$ times
-                           the original one ($d = \that_{r}/\that_{o} \geq d_{\text{min}}$).
+                           direction as the original one and is at least $d_{\text{min}}$ times as large (\mbox{$d = \that_{r}/\that_{o} \geq d_{\text{min}}$}).
                            Usually $d_{\text{min}} = 1$. \\
@@
                                      $(1 - \alpha)$ prediction interval
-                                     ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\sqrt{\sigma_{o}^{2}
-                                     + \sigma_{r}^{2}}]$). Usually $\alpha = 5\%$.
+                                     ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\surd(\sigma_{o}^{2}
+                                     + \sigma_{r}^{2})]$). Usually $\alpha = 5\%$.
                                      This criterion is equivalent to $p_{Q} \geq \alpha$ where
-                                     $p_{Q}$ is the $p$-value from the meta-analytic $Q$-test.\footnotemark\\
+                                     $p_{Q}$ is the $p$-value from the meta-analytic $Q$-test
+                                     $p_{Q} = 2\{1 - \Phi(\surd Q)\}$ with $Q$-statistic
+                                     $Q = \sum_{i \in \{o, r\}} (\that_{i} - \that_{m})^{2}/\sigma_{i}^{2} = (\that_{o}- \that_{r})^{2}/(\sigma^{2}_{o} + \sigma^{2}_{r})$.\\
     \bottomrule
@@
 \end{table}
-\footnotetext{The $p$-value from the $Q$-test is
-  $p_{Q} = 2\{1 - \Phi(\surd Q)\}$ where
-  $Q = \sum_{i \in \{o, r\}} (\that_{i} - \that_{m})^{2}\sigma_{i}^{-2} = (\that_{o}- \that_{r})^{2}(\sigma^{2}_{o} + \sigma^{2}_{r})^{-1}$
-  is the $Q$-statistic and $\that_{m}$ is the fixed-effects pooled estimate as
-  defined in Table~\ref{tab:rsdef}.}
 
@@
 terms of the summary statistics from Table~\ref{tab:meta}. The most popular
-criterion defines replication success by simultaneous statistical significance
-of original and replication study along with their effect estimates showing the
-same direction. This approach is also called the ``two-trials rule''
-\citep{Senn2008} in drug regulation or ``vote-counting'' in meta-analysis
-\citep{Cooper2019}. The criterion can similarly be defined through one-sided
-$p$-values, so that the original and replication effect estimate are not
-required to show the same direction as this is taken into account by the
+criterion is listed first and defines replication success by simultaneous
+statistical significance of original and replication study along with their
+effect estimates showing the same direction. This approach is also called the
+``two-trials rule'' \citep{Senn2008} in drug regulation or ``vote-counting'' in
+meta-analysis \citep{Cooper2019}. The criterion can similarly be defined through
+one-sided $p$-values, so that the original and replication effect estimate are
+not required to show the same direction as this is taken into account by the
 $p$-values. Some replication projects \citep{Opensc2015, Errington2021} also
@@
 definition ``replication success'' can almost always be achieved by conducting
-original and replication study with just very few samples so that the $p$-values
-are large. The approach is also logically questionable as it could be seen as an
-instance of the ``absence of evidence fallacy'' \citep{Altman1995} meaning that
-the failure to find evidence against the null hypothesis is erroneously
-interpreted as evidence for the null hypothesis. Meta-analytic extensions of the
+original and replication study with very few samples so that the $p$-values are
+large. The approach is also logically questionable as it could be seen as an
+instance of the ``absence of evidence fallacy'' \citep{Altman1995} meaning the
+failure to find evidence against the null hypothesis is erroneously interpreted
+as evidence for the null hypothesis. Meta-analytic extensions of the
 significance approach define replication success by significance of a combined
@@
 a common underlying effect size is seen as reasonable so that fixed-effects
-meta-analysis is used for pooling. Random-effects meta-analysis has mostly been
-used if more than one replication study of the same original study are conducted
-since in this case replicators are often interested in also understanding
-between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
+meta-analysis is used for pooling. Random-effects meta-analysis has primarily
+been used if more than one replication study of the same original study are
+conducted since in this case replicators are often interested in also
+understanding between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
 
 The remaining criteria in Table~\ref{tab:rsdef} put more emphasis on
-compatibility in effect size between original and replication study. For
+compatibility in effect size between the original and the replication study. For
 example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
-much the replication effect estimate changed compared to the original one, and
-the smaller $d$ the smaller the degree of replication success. Some projects
-also report a confidence interval for $d$ \citep{Camerer2016, Camerer2018},
-while others ignore its uncertainty and make a binary cut at one to define
-replication success \citep{Errington2021}.
-
-In contrast, the criteria based on confidence and prediction intervals define
-effect size compatibility on an absolute scale. However, the criterion based on
-the original confidence interval ignores the uncertainty from the replication,
-whereas the criterion based on the replication confidence interval ignores the
-uncertainty from the original study. The prediction interval criterion, on the
-other hand, takes into account both sources of uncertainty \citep{Patil2016}.
-Yet, also declaring ``replication success'' based on the prediction interval may
-be logically questionable due to its connection to the meta-analytic $Q$-test.
+much the replication effect estimate changed compared to the original, and the
+smaller $d$ is the smaller the degree of replication success. Some projects also
+report a confidence interval for $d$ \citep{Camerer2016, Camerer2018}, while
+others ignore its uncertainty and make a binary cut at $d_{\text{min}} = 1$ to
+define replication success \citep{Errington2021}. In contrast, the criteria
+based on confidence and prediction intervals define effect size compatibility on
+an absolute scale. However, the criterion based on the original confidence
+interval ignores the uncertainty from the replication, whereas the criterion
+based on the replication confidence interval ignores the uncertainty from the
+original study. The prediction interval criterion, on the other hand, takes into
+account both sources of uncertainty \citep{Patil2016}. Yet, declaring
+``replication success'' based on the prediction interval may be logically
+questionable due to its connection to the meta-analytic $Q$-test.
 % as it may also be seen as an instance of the ``absence of evidence fallacy''
 % \citep{Altman1995};
-That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is equivalent
-to the replication effect estimate $\that_{r}$ being contained in its
+That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
+equivalent to the replication effect estimate $\that_{r}$ being contained in its
 $(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
@@
 Interpreting a failure to reject the null hypothesis as evidence for it is again
-an instance of the absence of evidence fallacy
+an instance of the ``absence of evidence fallacy''
 \citep{Hedges2019}. % To establish replication success a
@@
 experiments led to data on 158 quantitative effects. However, from the data
-which they provide only 132 quantitative effects come with original and
+which they provide only 132 quantitative effects are provided with original and
 replication standardized mean difference effect estimates along with standard
@@
     labs(x = "Original effect estimate (SMD)",
-         y = "",
+         y = "Replication effect estimate (SMD)",
          fill = "") +
@@
   Biology \citep{Errington2021} for which effect estimates and standard errors
-  are available on standardized mean difference scale. The right plot shows a
-  zoomed-in view of the dotted area in the left plot. The \textit{p}-values are
-  recomputed using a normal approximation. Two study pairs with original effect
-  estimate larger than 80 are not shown.}
+  are available on standardized mean difference (SMD) scale. The right plot
+  shows a zoomed-in view of the dotted area in the left plot. The
+  \textit{p}-values are recomputed using a normal approximation. Two study pairs
+  with original effect estimate larger than 80 are not shown.}
 \label{fig:rpcb}
@@
       order.by = "freq", mainbar.y.label = "Successful replications (combined criteria)",
-      sets.x.label = "Successful replications \n(single criterion)") #, empty.intersections = "on")
+      sets.x.label = "Successful replications \n(single criterion)", #, empty.intersections = "on")
+      queries = list(list(query = intersects,
+                          params = c("Significance",
+                                     "Meta analytic \nsignificance",
+                                     "Relative \neffect size",
+                                     "Prediction \ninterval"),
+                          color = "#1b9e77", active = TRUE)))
 @
-\caption{Upset plot for data on 132 effects from the Reproducibility Project:
+\caption{UpSet plot for data on 132 effects from the Reproducibility Project:
   Cancer Biology \citep{Errington2021} for which effect estimates and standard
@@
   number of replication successes according to the different criteria from
-  Table~\ref{tab:rsdef} and their combinations. A level
+  Table~\ref{tab:rsdef} and their combinations. A threshold of
   $\alpha = \Sexpr{round(100*alpha, 2)}\%$ and a relative effect size threshold
-  $d_{\text{min}} = \Sexpr{dmin}$ are used.}
+  of $d_{\text{min}} = \Sexpr{dmin}$ are used.}
 \label{fig:upset}
@@
 significance (\Sexpr{nma}) and the prediction interval criteria (\Sexpr{npi}),
-followed by significance (\Sexpr{nsig}), and relative effect size (\Sexpr{nres}).
-Looking at the combinations of the criteria, only in two replications are all of
-them satisfied simultaneously.
+followed by significance (\Sexpr{nsig}), and relative effect size
+(\Sexpr{nres}). However, looking at the combinations of the criteria, only in
+two replications are all of them satisfied simultaneously (green).
 
@@
 press \citep[\eg{} ``more than half of the findings did not hold up when
-retested'' in][]{Carey2015}, is a clear simplification of the matter.
+retested'' in][]{Carey2015}, is a simplification of the matter.
 % that may harm the credibility of science.
@@
 external knowledge. The \emph{reverse-Bayes} approach, first proposed by
-\citet{Good1950}, is one way of dealing with this issue. The idea is to flip
-Bayes' theorem around
+\citet{Good1950}, is one way of dealing with this issue. The idea is to reverse
+Bayes' theorem
 \begin{align*}
@@
 with the posterior and ends up with the prior. Reverse-Bayes inference then
-revolves around the question whether the resulting prior is plausible in light
-of external knowledge, and if so, this could be seen as support for the
+revolves around the question of whether the resulting prior is plausible in
+light of external knowledge, and if so, this could be seen as support for the
 specified posterior.
@@
 evidence\footnote{For readers who do not agree with this notion of evidence, do
-  not panic. In this thesis we will extend this reverse-Bayes procedure to use
-  alternative measures of evidence, such as Bayes factors.} for a genuine effect
-found in the original study.
+  not panic. In this thesis (Paper I and III) we extend this reverse-Bayes
+  procedure to use alternative measures of evidence, such as Bayes factors.} for
+a genuine effect found in the original study.
 
@@
 credible interval~\eqref{eq:postCI} will either include or exclude zero.
-Different data analysts may have different degrees of scepticism and may thus
+Different researchers may have different degrees of scepticism and may thus
 choose different prior variances $\tau^{2}$. As a default choice,
@@
   that the resulting posterior is no longer convincing at level
-  $\alpha = \Sexpr{100*(alpha)}\%$.}
+  $\alpha = \Sexpr{100*(alpha)}\%$. Prior predictive $p$-values $p_{\text{Box}}$ are
+  computed for quantifying prior-data conflict.}
 \label{fig:RBillustration}
@@
 This shows that the reverse-Bayes approach based on sceptical priors can be used
-to formally ``challenge'' the finding of an original study. However, once this
+to formally challenge the finding of an original study. However, once this
 sceptical prior is determined, the question becomes whether it is plausible in
-light of external data. A natural candidate for answering the question are data
+light of external data. A natural candidate for answering the question is data
 from a replication study. In the following, I will show how Bayesian model
@@
 is compatible with the observed data. If the model M was indeed adequate, the
-empirical distribution of the observed data should be close to their predictive
+empirical distribution of the observed data should be close to its predictive
 distribution under the model M. On the other hand, if the empirical distribution
@@
   approach is therefore particularly useful in combination with reverse-Bayes
-  procedures based on Bayes factors, as will be demonstrated in this thesis.}
+  procedures based on Bayes factors, as will be demonstrated in later parts of
+  this thesis (paper I and III).}
 
@@
 $\theta \sim \Nor(0, \tau^{2}_{\alpha})$ with sufficiently sceptical prior
-variance $\tau^{2}_{\alpha}$ from~\eqref{eq:tau2alpha}, the aim is now to assess
-its adequacy in light of the data from a replication study. If we are able to
-show that the prior is inadequate, this would demonstrate that scepticim
-regarding the original finding is unjustified and that the original study
-therefore provided evidence for a genuine effect. Under the assumption of a
-normal likelihood for the replication effect estimate, \ie{}
+variance $\tau^{2}_{\alpha}$ from~\eqref{eq:tau2alpha}, the aim is to assess its
+adequacy in light of the data from a replication study. If we are able to show
+that the prior is inadequate, this would demonstrate that scepticism regarding
+the original finding is unjustified and that the original study provided
+evidence for a genuine effect. Under the assumption of a normal likelihood for
+the replication effect estimate, \ie{}
 $\that_{r} \given \theta \sim \Nor(\theta, \sigma^{2}_{r})$, the prior
@@
 conflict. This is because the standard errors from all three replications are
-roughly the same size, so that mostly the distance between zero and the
-replication effect estimate matters. The $p$-values suggest that there is hardly
-any conflict between the sceptical prior and the first two replications (those
-with $p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
+roughly the same size, so that the distance between zero and the replication
+effect estimate matters most. The $p$-values suggest that there is hardly any
+conflict between the sceptical prior and the first two replications (those with
+$p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
 $p_{\text{Box}} = \Sexpr{pboxFormat[2]}$), while the conflict seems larger for
@@
 them achieves replication success at level $\alpha = 5\%$. However, at a larger
-level, \eg{} $\alpha = \Sexpr{round(alpha2*100, 2)}\%$, the corresponding
+level, \eg{} \mbox{$\alpha = \Sexpr{round(alpha2*100, 2)}\%$}, the corresponding
 sufficiently sceptical prior variance would be smaller
@@
 level $\alpha = 10\%$. However, the sceptical $p$-value does not necessarily
-have to be dichotomized but can also be interpreted as a quantitative measure of
-replication success, the smaller $p_{\text{S}}$ the higher the degree of
-replication success.
+have to be dichotomized in this manner, but can also be interpreted as a
+quantitative measure of replication success, the smaller $p_{\text{S}}$ the
+higher the degree of replication success.
 
@@
 replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
-both $p$-values have to be smaller than $\alpha$ so that replication success
+both $p$-values have to be smaller than $\alpha$ such that replication success
 based on $p_{\text{S}} \leq \alpha$ is possible. Second, if the $p$-values
@@
 becomes smaller than the original estimate $\that_{o}$, the sceptical $p$-value
-indicates less replication success. This property seems desirable in the
+indicates less replication success. This property is desirable in the
 replication setting as a smaller replication effect estimate $\that_{r}$ may not
@@
 --the effect estimate was almost five times as large as in the original study.
-Yet, as the approach requires both studies to be convincing on their own --and
-the original study was not significant at the 5\% level-- replication success at
-this level is impossible with the sceptical $p$-value. The second property is
+Yet, as the approach requires both studies to be convincing on their own -- and
+the original study was not significant at the 5\% level -- replication success
+at this level is impossible with the sceptical $p$-value. The second property is
 illustrated by the fifth study from above (1, 3, 5). Here the original study was
@@
 This concludes the introduction to replication studies and the summary of the
-reverse-Bayes assessment of replication success. The interested reader is
-referred to the original article by \citet{Held2020} for additional properties
-(\eg{} the null distribution of the sceptical $p$-value) and extensions of the
-procedure (\eg{} a one-sided version of the sceptical $p$-value, power and
-sample size calculations). However, this introduction should have prepared the
-reader well enough to understand the remaining parts of this thesis.
-
-\subsubsection{Software and data}
-Code and data to reproduce the analyses and recompile the thesis are available
-at \url{https://doi.org/10.5281/zenodo.XXXXXXX}. All analyses were conducted in
-the R programming language version \Sexpr{paste(version$major, version$minor,
-  sep = ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
-\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
-\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
-\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. The
-CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
+reverse-Bayes assessment of replication success. Some additional properties
+(\eg{} the null distribution of the sceptical $p$-value) and extensions (\eg{} a
+one-sided version of the sceptical $p$-value, power and sample size
+calculations) can be found in the original article by \citet{Held2020}. However,
+the parts of the procedure that are relevant for this thesis have been
+presented.
+
+\subsubsection{Data and software}
+The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
 \citep{Errington2021} were downloaded from
@@
 extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
-  data.csv}''.
+  data.csv}''. Code and data to reproduce the analyses and recompile the thesis
+are available at \url{https://doi.org/10.5281/zenodo.XXXXXXX}. All analyses were
+conducted in the R programming language version
+\Sexpr{paste(version$major, version$minor, sep = ".")} \citep{R}. The packages
+\texttt{dplyr} \citep{Wickham2022}, \texttt{ggplot2} \citep{Wickham2016},
+\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
+\texttt{UpSetR} \citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019}
+were used.
 
@@
 \newpage
-\section{Thesis summary}
+\section{Open questions and thesis contributions}
 \label{sec:summary}
@@
 The reverse-Bayes approach from \citet{Held2020} is based on challenging the
-original study with a sceptical prior so that there is no longer evidence for an
-effect. Evidence is quantified in terms of credible intervals, respectively,
-tail-probabilities. However, there exist also other measures of evidence, and it
-has been a matter of long debates which is the most appropriate \citep[see
+original study with a sceptical prior so there is no longer evidence for an
+effect. Evidence is quantified in terms of credible intervals and tail
+probabilities. However, there exist also other measures of evidence, and it has
+been a matter of long debates which is the most appropriate \citep[see
 \eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
@@
 most properties with the sceptical $p$-value due to the reverse-Bayes approach
-underlying both methods, yet in some situations conclusions may also differ
-because of their different ways of quantifying evidence. Specifically, it is
-shown that the sceptical $p$-values suffers from a certain type of ``shrinkage
-paradox'', which is avoided by the sceptical Bayes factor; when the $p$-value
-from the original study goes to zero, replication success based on the sceptical
+underlying both methods, yet in some situations conclusions may differ because
+of their different ways of quantifying evidence. Specifically, it is shown that
+the sceptical $p$-value suffers from a certain type of ``shrinkage paradox'',
+which is avoided by the sceptical Bayes factor; when the $p$-value from the
+original study goes to zero, replication success based on the sceptical
 $p$-value can be achieved with any arbitrarily small replication effect
@@
 The method is illustrated on data from the Social Sciences Replication Project
-\citep{Camerer2018}, and implemented in an R package.
+\citep{Camerer2018}, and implemented in the R package \texttt{BayesRep}
+(\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).
 
 The idea to use Bayes factors instead of tail probabilities was suggested by
-\citet{Consonni2019} and \citet{Pericchi2020} independently in response to
+\citet{Consonni2019} and \citet{Pericchi2020} independently in response to the
 original article by \citet{Held2020}. L. Held then implemented a first version
@@
 Throughout, L. Held gave high-level feedback. I presented initial results at the
-GMDS and CEN-IBS conference in 2020 (online), L. Held presented the final
-results at the ISBA world meeting 2021 (online).
+annual meeting of the GMDS and CEN-IBS (German Association for Medical
+Informatics, Biometry and Epidemiology and the Central European Network of the
+International Biometric Society) in 2020. L. Held presented the final results at
+the world meeting of the ISBA (International Society for Bayesian Analysis) in
+2021.
 
@@
 be used in case the sceptical $p$-value needs to be dichotomized into
-replication success/failure. In this article, we therefore look closer at the
+replication success or failure. In this article, we therefore look closer at the
 ``success region'' of the sceptical $p$-value in terms of the relative effect
@@
 new default level for thresholding the sceptical $p$-value called the
-\emph{golden level} $\alpha_{G}$ (because the golden ration appears in its
-derivation). The golden level is defined through the property that for an
-original study which was just borderline significant ($p_{o} = \alpha$),
+\emph{golden level} $\alpha_{G}$ (named ``golden'' because the golden ratio
+appears in its derivation). The golden level is defined through the property
+that for an original study which was borderline significant ($p_{o} = \alpha$),
 replication success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if
 the replication effect estimate is at least as large as the original one
-($d \geq 1$). The behavior of the golden level seems to align with common sense;
-For original studies which were already convincing (in terms of their $p$-value)
+($d \geq 1$). The behavior of the golden level seems to align with common sense:
+for original studies which were already convincing (in terms of their $p$-value)
 the effect estimate in the replication study is allowed to shrink, to some
@@
 around the significance level) shrinkage is more strongly penalized. We find
-that in typical situations, replication success based on the golden level also
-has similar or improved frequentist properties (type-I error rate and project
-power) compared to the standard significance criterion. Case studies from four
-large-scale replication projects illustrate the properties of the method.
+that for replication studies with equal or larger sample size than the original
+study, replication success based on the golden level also has similar or
+improved frequentist properties (type-I error rate and project power) compared
+to the standard significance criterion. Case studies from four large-scale
+replication projects \citep{Opensc2015, Camerer2016, Camerer2018, Cova2018}
+illustrate the properties of the method.
 
@@
 sample size. How exactly the sample size should be determined depends on the
-method which will be used for analyzing the replication data. Various approaches
-have been proposed for doing so which are specifically tailored to certain
-analysis methods. In this article, we provide a general Bayesian framework which
-applies to any analysis method (including the sceptical $p$-value and the
-sceptical Bayes factor). We show how the data from the original study and
-external knowledge can be combined in a \emph{design prior} for the underlying
-model parameters. Based on a design prior, predictions about the replication
-data can then be computed, and the replication sample size can be chosen such
-the probability of replication success becomes as high as desired. We illustrate
+method used for analyzing the replication data. Various approaches have been
+proposed for doing so which are specifically tailored to certain analysis
+methods. In this article, we provide a general Bayesian framework which applies
+to any analysis method (including the sceptical $p$-value and the sceptical
+Bayes factor). We show how the data from the original study and external
+knowledge can be combined in a \emph{design prior} for the underlying model
+parameters. Based on this design prior, predictions about the replication data
+can then be computed, and the replication sample size can be chosen such the
+probability of replication success becomes as high as desired. We illustrate
 Bayesian design of replication studies in the normal-normal hierarchical model
 which provides sufficient flexibility for specification of design priors. Data
-from a cross-laboratory replication project are used for illustrating our
-methods, which are also available in an R package.
+from a cross-laboratory replication project \citep{Protzko2020} are used for
+illustrating our methods, which are also available in the R package
+\texttt{BayesRepDesign} (\url{https://github.com/SamCH93/BayesRepDesign}).
 
@@
 \citep{Heldproposal2019} that we will investigate power and sample size
-calculations for the sceptical $p$-value and the sceptical Bayes factor. For the
-first paper I already derived the power function of the sceptical Bayes factor
-in closed-form for two types of design priors. After its completion, I
-generalized the result to any design prior in the normal-normal hierarchical
-model, and started working on this manuscript. I presented a first draft to L.
-Held and G. Consonni in the beginning of 2021. G. Consonni then helped
-developing the methodology for multisite replication study design. I continued
-working on the manuscript in 2022 and also wrote the accompanying R package.
-Throughout, L. Held and G. Consonni gave high-level feedback.
+calculations for the sceptical $p$-value and the sceptical Bayes factor. In
+paper I, I already derived the power function of the sceptical Bayes factor in
+closed-form for two types of design priors. After its completion, I generalized
+the result to any design prior in the normal-normal hierarchical model, and
+started working on this manuscript. I presented a first draft to L. Held and G.
+Consonni in the beginning of 2021. \mbox{G. Consonni} then helped developing the
+methodology for multisite replication study design. I continued working on the
+manuscript in 2022 and also wrote the accompanying R package. Throughout, L.
+Held and G. Consonni gave high-level feedback.
 
@@
 
-L. Held and M. Ott started working on this article several years ago when M. Ott
-was still a PhD student (around 2017). When I discovered the connection between
-the Analysis of Credibility and the fail-safe N method, L. Held suggested that
-it would fit nicely into this manuscript, and that I should start to overhaul
-it. I rewrote and expanded his initial draft, adding also a new section on
-reverse-Bayes approaches with Bayes factors, largely based on the work from
-paper I. We then managed to recruit R. Matthews to also contribute. From that
-point on the three of us iteratively worked on the manuscript and M. Ott gave
-high-level feedback.
+L. Held and M. Ott started working on this article several years ago. When I
+discovered the connection between the Analysis of Credibility and the fail-safe
+N method, L. Held suggested that it would fit nicely into this manuscript, and
+that I should start to overhaul it. I rewrote and expanded his initial draft,
+adding also a new section on reverse-Bayes approaches with Bayes factors,
+largely based on the work from paper I. We then managed to recruit R. Matthews
+to also contribute. From that point on the three of us iteratively worked on the
+manuscript and M. Ott gave high-level feedback.
 
@@
   Additional Evidence}, and we noted some flaws in the article. This prompted us
-to write a commentary. We show that --contrary to the statement by
-\citet{Sondhi2021}-- there is a closed form solution for the key quantity in
+to write a commentary. We show that -- contrary to the statement by
+\citet{Sondhi2021} -- there is a closed form solution for the key quantity in
 their approach termed ``Bayesian Additional Evidence tipping point''.
@@
 
-R. Matthews attended us about the article from \citet{Sondhi2021}. After reading
+R. Matthews alerted us about the article from \citet{Sondhi2021}. After reading
 it, I realized that their statement about closed-form solutions was incorrect
-and derived a solution. L. Held suggested to write a commentary. I wrote an
-initial draft of the manuscript, which R. Matthews substantially improved. The
-two of us iteratively worked on the manuscript, while L. Held gave mostly
-high-level feedback.
+and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
+an initial draft of the manuscript, which \mbox{R. Matthews} substantially
+improved by expanding it with some logical flaws of the method. The two of us
+iteratively worked on the manuscript, while L. Held gave mostly high-level
+feedback.
 
@@
 make a method seem superior if various questionable research practices are
-employed. We also give recommendations which could help to alleviate these
-issues, most importantly we recommend researchers to write and pre-register
-simulation protocols.
-
-The manuscript is co-first authored by myself and L. Kook. I had the idea to
-invent a ``mock-method'' and use questionable research practices that make it
+employed. We also give recommendations to alleviate these issues, most
+importantly we recommend researchers write and pre-register simulation
+protocols.
+
+The first authorship of this manuscript is shared with L. Kook. I had the idea
+to invent a ``mock-method'' and use questionable research practices that make it
 seem superior, to draw attention to the low standards in methodological
@@
 and started writing the simulation protocol. L. Kook took lead in developing the
-R package and simulation study code. K. Reeve provided feedback on the
-simulation protocol and helped polishing the manuscript. Recently, I was invited
-to present the results from this project at the CEN conference 2023 in Basel.
+R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
+simulation study code. K. Reeve provided feedback on the simulation protocol and
+helped polishing the manuscript. Recently, I was invited to present the results
+from this project at the CEN (Central European Network) conference 2023 in
+Basel.
 

### 2022-11-28 preface.tex
Maria feedback

@@
 committee, Guido and Reinhard, for always providing excellent advice and being
-great collaborators. Another thank you goes to Robert Matthews who also is a
-great collaborator and without whom this PhD project would never exist as it was
-him who resurrected the reverse-Bayes approach from the dead almost twenty years
+great collaborators. Another thanks goes to Robert Matthews who also is a great
+collaborator and without whom this PhD project would never exist as it was him
+who resurrected the reverse-Bayes approach from the dead almost twenty years
 ago. Furthermore, I want to thank Eric-Jan Wagenmakers for reviewing this thesis
@@
 I also want to thank my friends and colleagues from the Epidemiology,
-Biostatistics, and Prevention Institute from the University of Zurich (in
+Biostatistics and Prevention Institute from the University of Zurich (in
 alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
@@
 Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Martin,
-Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala, Torsten, Ulrike. Another
-``thanks'' goes to my friends from the Department of Psychological Methods from
-the University of Amsterdam (in alphabetical order): Adam, Alexander, Alexandra,
-Alessandra, Alejandro, Angelika, Bruno, Don, František, Frederik, Jason, Johnny,
-Joris, Jill, Julia, Lukas, Maarten, Michelle, Nora, Omid, Quentin, René, Serjan,
-Suzanne, Ting. I also want to thank my good friends from outside academia (in
-alphabetical order): Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela,
-Peter. A special thanks goes to Ada. Finally, I thank my family Beni, Christa,
-Elisabeth, Fabian, Harry, Markus, Maja, Noemi for their support.
+Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala, Torsten, and Ulrike.
+Another thanks goes to my friends from the Department of Psychological Methods
+from the University of Amsterdam (in alphabetical order): Adam, Alexander,
+Alexandra, Alessandra, Alejandro, Angelika, Bruno, Don, František, Frederik,
+Jason, Johnny, Joris, Jill, Julia, Lukas, Maarten, Michelle, Nora, Omid,
+Quentin, René, Serjan, Suzanne, and Ting. I also want to thank my good friends
+from outside of academia (in alphabetical order): Chronis, Dani, Eleftheria,
+Flo, Fabi, Giuachin, Mirela, and Peter. A special thanks goes to Ada. Finally, I
+thank my family: Beni, Christa, Elisabeth, Fabian, Harry, Markus, Maja, and
+Noemi for their support.
 

### 2022-11-29 abstract.tex
added paper 4

@@
 
-The fact that a scientific finding can be replicated in an independent
-replication study is central to its credibility. However, various large-scale
-replication failures have shown that the replicability of scientific findings is
-often lower than expected. This ``replication crisis'' has led to several
-methodological reforms in the past decade, an increased conduct of replication
-studies being one of them. Yet despite this rise of replication research, there
-is no consensus on which statistical methods should be used for the design and
-analysis of replication studies; Various methods already exist and various new
-ones have been proposed in response to the crisis. This thesis centres around a
-proposal based on the reverse-Bayes approach. The key idea is to reverse the
-traditional ``forward'' use of Bayes' theorem (``prior + likelihood
-$\rightarrow$ posterior''), starting instead with a pre-specified posterior and
-deducing the corresponding prior (``posterior + likelihood $\rightarrow$
-prior''). % As such, the reverse-Bayes approach naturally fits to the replication
-% setting as it enables the mathematical formalization of scepticism regarding the
-% finding from the original study.
-This allows us to challenge the original finding by determining a sceptical
-prior for the underlying effect size such that the resulting posterior is no
-longer convincing. This prior then represents the position of a sceptic who
-remains unconvinced by the original study. Whether or not the sceptics' position
-is justified can then be assessed in light of the new data from the replication
-study. The larger the conflict between the replication data and the sceptic, the
-larger the degree of replication success. This procedure can be summarized in a
-single quantitative measure of replication success, termed the sceptical
-$p$-value.
+The credibility of a scientific finding is based on the fact that it can be
+replicated when the same study is repeated with new subjects. However, various
+failures to replicate major scientific findings in the social and life sciences
+indicate that replicability is often lower than expected. This ``replication
+crisis'' has led to several methodological reforms in the past decade, an
+increased conduct of replication studies being one of them. Yet despite this
+increase in replication studies, there is no consensus on a fundamental
+question: How should replication success be defined statistically?
+% Various methods already exist and various new ones have
+% been proposed in response to the crisis. This thesis centres around a proposal
+% based on the reverse-Bayes approach. The key idea is to reverse the traditional
+% ``forward'' use of Bayes' theorem (``prior + likelihood $\rightarrow$
+% posterior''), starting instead with a pre-specified posterior and deducing the
+% corresponding prior (``posterior + likelihood $\rightarrow$
+% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
+% % setting as it enables the mathematical formalization of scepticism regarding the
+% % finding from the original study.
+% This allows us to challenge the original finding by determining a sceptical
+% prior for the underlying effect size such that the resulting posterior is no
+% longer convincing. This prior then represents the position of a sceptic who
+% remains unconvinced by the original study. Whether or not the sceptics' position
+% is justified can then be assessed in light of the new data from the replication
+% study. The larger the conflict between the replication data and the sceptic, the
+% larger the degree of replication success. This procedure can be summarized in a
+% single quantitative measure of replication success, termed the sceptical
+% $p$-value.
 
-The first and largest part of the thesis consists of extending this procedure. A
-first extension replaces tail probabilities by Bayes factors as measures of
-evidence. The sceptical prior is now determined such that the original finding
-is no longer convincing in terms of a Bayes factor. In contrast to tail
-probabilities, Bayes factors have a more natural interpretation and allow for
-direct quantification of evidence for one hypothesis versus another. As with the
-sceptical $p$-value, the procedure leads to a single measure quantifying the
-degree of replication success called the sceptical Bayes factor. A second
-extensions recalibrates the original procedure to produce more appropriate
-inferences in terms of effect size. % from the relative effect size
+The first and largest part of this thesis extends a recently proposed
+reverse-Bayes method for quantifying replication success. The key idea is to
+challenge the finding from the original study with a sceptical prior so that the
+resulting posterior provides no longer evidence for the finding from the study.
+While the original proposal defined evidence through tail probabilities, the
+extension developed here replaces them with Bayes
+factors. % The sceptical prior is now
+% determined such that the original finding is no longer convincing in terms of a
+% Bayes factor. In contrast to tail probabilities,
+We find that the extended method combines two notions of replicability: It
+ensures that original and replication study independently provide evidence for
+an effect while also ensuring that their effect estimates are compatible.
+Compared to the original method, the extension also avoids a statistical paradox
+which the original method suffered from.
+% Bayes factors have a more
+% natural interpretation and allow for direct quantification of evidence for one
+% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
+% to a single measure quantifying the degree of replication success called the
+% sceptical Bayes factor.
+The second extensions recalibrates the original procedure to produce more
+appropriate inferences in terms of effect size. % from the relative effect size
 % perspective
@@
 studies, replication success can only be achieved if the replication effect
-estimate is larger than the original one. The third extension provides a
-framework for Bayesian design of replication studies. This framework allows for
-combining the data from the original study with external knowledge, which leads
-to potentially more efficient designs compared to classical approaches.
+estimate is larger than the original one. The recalibrated procedure has good
+frequentist properties comparable to the standard method used in practice. The
+third extension provides a framework for Bayesian design of replication studies
+which allows for combining the data from the original study with external
+knowledge. External knowledge, such as data from other studies, is ubiquitous in
+the replication setting and it can potentially lead to more efficient designs
+compared to classical approaches that cannot take it into account.
 
@@
 mostly been forgotten. To increase awareness and show potential use cases,
-reverse-Bayes history and methods are summarized in a comprehensive review.
-Furthermore, a short commentary on a recently proposed reverse-Bayes method
-draws connections to other reverse-Bayes methods.
+reverse-Bayes history and methods are summarized in a comprehensive review. The
+review includes also some new results on connections between revere-Bayes
+methods and meta-analysis. Finally, a commentary paper on a recently proposed
+reverse-Bayes method draws connections to other reverse-Bayes methods.
 

### 2022-11-29 intro.Rnw
added paper 4

@@
 example, how can we know if the protective effect of a vaccine found in a study
-is real? The answer to this question is of highest importance to scientists and
+is real? The answer to such questions is of highest importance to scientists and
 decision makers, but typically we can never know for sure as any study result
@@
 publication acceptance regardless of the study outcome. Similarly, digital
-infrastructure platforms, such as zenodo (\url{https://zenodo.org/}) or the open
-science framework (\url{https://osf.io/}), were created to facilitate
+infrastructure platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open
+Science Framework (\url{https://osf.io/}), were created to facilitate
 preregistration, preprints, and code and data sharing, all of which have
@@
   \centering
-  \caption{Study level summary statistics for an original and a replication
+  \caption{Study-level summary statistics for an original and a replication
     study. The cumulative distribution function of the standard normal
@@
 Most methods for analyzing replication studies can be formulated in terms of
-study level summary statistics as shown in Table~\ref{tab:meta}. % Effect
+study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
 % estimates, standard error, confidence intervals, and $p$-values
@@
 others. Using summary statistics is also often the only possible way for
-conducting the analysis as the raw data from the original study may not be
-available to the replicators. The most important statistic is the effect
-estimate $\that$. It provides an estimate of the underlying effect size $\theta$
-which quantifies the effect or association of an intervention/exposure with an
-outcome variable. Typical effect sizes are mean differences and correlations
-(for continuous outcomes), odds ratios (for binary outcomes), or hazard ratios
-(for time to event outcomes). Depending on the type of effect size, a
-transformation might be required so that the assumption of approximately
-normally distributed effect estimates around the unknown effect size $\theta$
-(for large enough sample sizes) is justified. This could be, for instance, the
-Fisher $z$-transformation for correlations, or the log-transformation for
-odds/hazard ratios \citep[chapter 11]{Cooper2019}. The associated standard error
-$\sigma$ represents the statistical uncertainty of the estimate. Under the
-assumption of (asymptotic) normality, confidence intervals for $\theta$ and
-$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
-computed as shown in Table~\ref{tab:meta}.
+conducting the replication success analysis as the raw data from the original
+study may not be available to the replicators. The most important statistic is
+the effect estimate $\that$. It provides an estimate of the underlying effect
+size $\theta$ which quantifies the effect or association of an
+intervention/exposure with an outcome variable. Typical effect sizes are mean
+differences and correlations (for continuous outcomes), odds ratios (for binary
+outcomes), or hazard ratios (for time to event outcomes). Depending on the type
+of effect size, a transformation might be required so that the assumption of
+approximately normally distributed effect estimates around the unknown effect
+size $\theta$ (for large enough sample sizes) is justified. This could be, for
+instance, the Fisher $z$-transformation for correlations, or the
+log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
+associated standard error $\sigma$ represents the statistical uncertainty of the
+estimate. Under the assumption of (asymptotic) normality, confidence intervals
+for $\theta$ and $p$-values for testing the null hypothesis
+$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
 
@@
 others ignore its uncertainty and make a binary cut at $d_{\text{min}} = 1$ to
-define replication success \citep{Errington2021}. In contrast, the criteria
-based on confidence and prediction intervals define effect size compatibility on
-an absolute scale. However, the criterion based on the original confidence
-interval ignores the uncertainty from the replication, whereas the criterion
-based on the replication confidence interval ignores the uncertainty from the
-original study. The prediction interval criterion, on the other hand, takes into
-account both sources of uncertainty \citep{Patil2016}. Yet, declaring
-``replication success'' based on the prediction interval may be logically
-questionable due to its connection to the meta-analytic $Q$-test.
+define replication success \citep{Errington2021}. The criteria based on
+confidence and prediction intervals define effect size compatibility on an
+absolute scale. However, the criterion based on the original confidence interval
+ignores the uncertainty from the replication, whereas the criterion based on the
+replication confidence interval ignores the uncertainty from the original study.
+The prediction interval criterion takes into account both sources of uncertainty
+\citep{Patil2016}. Yet, declaring ``replication success'' based on the
+prediction interval may be logically questionable due to its connection to the
+meta-analytic $Q$-test.
 % as it may also be seen as an instance of the ``absence of evidence fallacy''
@@
   \caption{Subset of results from the Reproducibility Project: Cancer Biology
-    \citep{Errington2021}. (P, X, E) denotes effect E from experiment X, from
-    original paper P. Shown are original $\that_{o}$, replication $\that_{r}$,
-    and pooled effect estimate $\that_{m}$ with 95\% confidence intervals,
-    variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimate
-    $d = \that_{r}/\that_{o}$, original $p$-value $p_{o}$, replication $p$-value
-    $p_{r}$, meta-analytic $p$-value $p_{m}$, $Q$-test $p$-value $p_{Q}$, and
-    sceptical $p$-value $p_{\mathrm{S}}$. A level $\alpha = 5\%$ is used as
-    threshold for replication success via $p$-values, and a threshold
-    $d_{\text{min}} = 1$ for the relative effect estimate.}
+    \citep{Errington2021}. (P, X, E) denotes effect number E from experiment
+    number X, from original paper number P. Shown are original $\that_{o}$,
+    replication $\that_{r}$, and pooled effect estimate $\that_{m}$ with 95\%
+    confidence intervals, variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$,
+    relative effect estimate $d = \that_{r}/\that_{o}$, original $p$-value
+    $p_{o}$, replication $p$-value $p_{r}$, meta-analytic $p$-value $p_{m}$,
+    $Q$-test $p$-value $p_{Q}$, and sceptical $p$-value $p_{\mathrm{S}}$. A
+    level $\alpha = 5\%$ is used as threshold for replication success via
+    $p$-values, and a threshold $d_{\text{min}} = 1$ for the relative effect
+    estimate.}
   \label{tab:RPCB}
@@
   Hedges2019, Mathur2020, Held2020, Pawel2020, Bonett2020}. The focus of this
-thesis is to refine and extended the proposal from \citet{Held2020} which
-combines \emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a
-method for assessing replication success. In the following, I will summarize its
-main ideas and technical underpinnings.
+thesis is to refine and extend the proposal from \citet{Held2020} which combines
+\emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
+for assessing replication success. In the following, I will summarize its main
+ideas and technical underpinnings.
 
@@
 likelihood of the data, also know as \emph{Bayesian updating}. Parameter values
-which increase the likelihood of the data become more likely \emph{a
-  posteriori}, however, they are also weighted by their plausibility \emph{a
-  priori} through the prior. As such, Bayesian inference provides a formal way
-for combining information from the data at hand with external knowledge encoded
-in the prior.
-
-However, many also consider the prior to be the weak point of Bayesian
-inference, as it is unclear how it should be specified in the absence of
-external knowledge. The \emph{reverse-Bayes} approach, first proposed by
-\citet{Good1950}, is one way of dealing with this issue. The idea is to reverse
-Bayes' theorem
+which increase the likelihood of the data become more likely \emph{a posteriori}
+but they are also weighted by their \emph{a priori} plausibility through the
+prior. As such, Bayesian inference provides a formal way for combining
+information from the data at hand with external knowledge encoded in the prior.
+
+Many consider the prior to be also the weak point of Bayesian inference since it
+is unclear how it should be specified in the absence of external knowledge. The
+\emph{reverse-Bayes} approach, first proposed by \citet{Good1950}, is one way of
+dealing with this issue. The idea is to reverse Bayes' theorem
 \begin{align*}
@@
 \begin{align*}
-  \text{PR}_{\text{Box}}
+  \text{PPR}_{\text{Box}}
   = \frac{f(\text{observed data} \given \text{M}_{1})}{f(\text{observed data} \given \text{M}_{2})},
@@
 could be used to judge the relative adequacy of model $\text{M}_{1}$. Again, the
-lower the predictive ratio $\text{PR}_{\text{Box}}$, the less compatible the
-observed data with the model $\text{M}_{1}$. Bayesian model criticism approaches
-based on predictive ratios will be used in later parts of this
-thesis.\footnote{Some readers may have noted that the predictive ratio is also
-  the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
+lower the prior predictive ratio $\text{PPR}_{\text{Box}}$, the less compatible
+the observed data with the model $\text{M}_{1}$. Bayesian model criticism
+approaches based on prior predictive ratios will be used in later parts of this
+thesis.\footnote{Some readers may have noted that the prior predictive ratio is
+  also the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
   $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
@@
 calculations) can be found in the original article by \citet{Held2020}. However,
-the parts of the procedure that are relevant for this thesis have been
-presented.
-
-\subsubsection{Data and software}
-The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
-\citep{Errington2021} were downloaded from
-\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
-extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
-  data.csv}''. Code and data to reproduce the analyses and recompile the thesis
-are available at \url{https://doi.org/10.5281/zenodo.XXXXXXX}. All analyses were
-conducted in the R programming language version
-\Sexpr{paste(version$major, version$minor, sep = ".")} \citep{R}. The packages
-\texttt{dplyr} \citep{Wickham2022}, \texttt{ggplot2} \citep{Wickham2016},
-\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
-\texttt{UpSetR} \citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019}
-were used.
-
-<< "sessionInfo1", eval = Reproducibility, results = "asis" >>=
-## print R sessionInfo to see system information and package versions
-## used to compile the manuscript (set Reproducibility = FALSE, to not do that)
-cat("\\newpage \\section*{Computational details}")
-@
-<< "sessionInfo2", echo = Reproducibility, results = Reproducibility >>=
-sessionInfo()
-@
-
-\newpage
+the relevant parts of the procedure have been presented. In the following, I
+will discuss open questions and how they are addressed in this thesis.
+
 \section{Open questions and thesis contributions}
@@
 
-This thesis consists of six papers. Paper I and II (and to a lesser extent III)
-focus on extending the reverse-Bayes assessment of replication success from
-\citet{Held2020}. Paper III presents a general Bayesian framework for
-replication study design. Paper IV is a review paper about reverse-Bayes
-methodology. Paper V is a short comment on another article which proposed a
-reverse-Bayes method. Paper VI lists and illustrates questionable research
-practices in simulation studies.
+This thesis consists of six papers divided into three parts. The first part
+(Paper I, II, and III) focuses on methodology for design and analysis of
+replication studies. The second part (Paper IV and V) revolves around
+reverse-Bayes methodology in general. Paper IV is a review paper about
+reverse-Bayes methodology and Paper V is a short comment on another article
+which proposed a reverse-Bayes method. The last part (Paper VI) is about
+integrity issues methodological research with simulations
+studies. % The article lists and illustrates questionable
+% research practices in simulation studies, and gives recommendations how to avoid
+% them.
+
+\subsection{Design and analysis of replication studies}
 
@@
 
+\subsection{Reverse-Bayes methodology}
+
 \startPaperSummary{PaperIV}{%
@@
 
+\subsection{Integrity in methodological research}
+
 \startPaperSummary{PaperVI}{%
@@
 R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
-simulation study code. K. Reeve provided feedback on the simulation protocol and
-helped polishing the manuscript. Recently, I was invited to present the results
-from this project at the CEN (Central European Network) conference 2023 in
-Basel.
+simulation study code. Myself, L. Kook, and K. Reeve then designed the final
+simulation study and wrote the manuscript together. Recently, I was invited to
+present the results from this project at the CEN (Central European Network)
+conference 2023 in Basel.
+
+\phantomsection
+\addcontentsline{toc}{section}{Data and software}
+\section*{Data and software}
+The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
+\citep{Errington2021} were downloaded from
+\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
+extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
+  data.csv}''. All analyses from this chapter were conducted in the R
+programming language version \Sexpr{paste(version$major, version$minor, sep =
+  ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
+\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
+\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
+\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. Code and
+data to reproduce this thesis are available at
+\url{https://doi.org/10.5281/zenodo.XXXXXXX}.
+
+<< "sessionInfo1", eval = Reproducibility, results = "asis" >>=
+## print R sessionInfo to see system information and package versions
+## used to compile the manuscript (set Reproducibility = FALSE, to not do that)
+cat("\\newpage \\section*{Computational details}")
+@
+<< "sessionInfo2", echo = Reproducibility, results = Reproducibility >>=
+sessionInfo()
+@
 
 % Bibliography
+\nocite{Pawel2020b, Held2021, Pawel2022c,Held2021b, Pawel2022d, Pawel2022e}
 \bibliographystyle{apalikedoiurl}

### 2022-11-29 paper4.tex
added paper 4

\section*{Abstract}
It is now widely accepted that the standard inferential toolkit used by the
scientific research community -- null-hypothesis significance testing (NHST) --
is not fit for purpose. Yet despite the threat posed to the scientific
enterprise, there is no agreement concerning alternative approaches for evidence
assessment. This lack of consensus reflects long-standing issues concerning
Bayesian methods, the principal alternative to NHST. We report on recent work
that builds on an approach to inference put forward over 70 years ago to address
the well-known ``Problem of Priors'' in Bayesian analysis, by reversing the
conventional prior-likelihood-posterior (``forward'') use of Bayes's Theorem.
Such Reverse-Bayes analysis allows priors to be deduced from the likelihood by
requiring that the posterior achieve a specified level of credibility. We
summarise the technical underpinning of this approach, and show how it opens up
new approaches to common inferential challenges, such as assessing the
credibility of scientific findings, setting them in appropriate context,
estimating the probability of successful replications, and extracting more
insight from NHST while reducing the risk of misinterpretation. We argue that
Reverse-Bayes methods have a key role to play in making Bayesian methods more
accessible and attractive for evidence assessment and research synthesis. As a
running example we consider a recently published meta-analysis from several
randomized controlled trials (RCTs) investigating the association between
corticosteroids and mortality in hospitalized patients with COVID-19.

\textbf{Key words}: Analysis of Credibility, Bayes factor, false positive risk,
meta-analysis, prior-data conflict, reverse-Bayes

\section{Introduction: the origin of Reverse-Bayes methods}\label{sec4:intro}
\begin{center}
\begin{minipage}{12cm}
  { { { ``We can make judgments of initial probabilities and infer final ones,
        or we can equally make judgments of final ones and infer initial ones by
        \emph{Bayes's theorem in reverse}.'' }}}
\end{minipage}
\end{center}
\begin{flushright}
   \citet[p. 29]{Good1983}
\end{flushright}

There is now a common consensus that the most widely-used methods of statistical
inference have led to a crisis in both the interpretation of research findings
and their replication \citep{Gelman2014, Wasserstein2016}. At the same time,
there is a lack of consensus on how to address the challenge
\citep{Matthews2017}, as highlighted by the plethora of alternative techniques
to null-hypothesis significance testing now being put forward, see for example
\citet{Wasserstein2019} and the references therein.
Especially striking is the relative dearth of alternatives based on Bayesian
concepts. Given their intuitive inferential basis and output
\citep{Wagenmakers2008, McElreath2018}, these would seem obvious candidates to
supplant the prevailing frequentist methodology. However, it is well-known that
the adoption of Bayesian methods continues to be hampered by several factors,
such as the belief that advanced computational tools are required to make
Bayesian statistics practical \citep{Green2015}. The most persistent of these is
that the full benefit of Bayesian methods demands specification of a prior level
of belief, even in the absence of any appropriate insight. This ``Problem of
Priors'' has cast a shadow over Bayesian methods since their emergence over 250
years ago \citep{McGrayne2011}, and has led to a variety of approaches, such as
prior elicitation, prior sensitivity analysis, and objective Bayesian
methodology; all have their supporters and critics.

One of the least well-known was suggested over 70 years ago \citep{Good1950} by
one of the best-known proponents of Bayesian methods during the
20\textsuperscript{th} century, I.J.~Good. It involves reversing the
conventional direction of Bayes's Theorem and determining the level of prior
belief required to reach a specified level of posterior belief, given the
evidence observed. This reversal of Bayes's Theorem allows the assessment of new
findings on the basis of whether the resulting prior is reasonable in the light
of existing knowledge. Whether a prior is plausible in the light of existing
knowledge can be assessed informally or more formally using techniques for
comparing priors with existing data as suggested by \citet{Box1980} and further
refined by \citet{Evans2006}, see also \citet{Nott2020, Nott2021} for related
approaches. Good stressed that despite the routine use of the adjectives
``prior'' and ``posterior'' in applications of Bayes's Theorem, the validity of
any resulting inference does not require a specific temporal ordering, as the
theorem is simply a constraint ensuring consistency with the axioms of
probability. While reversing Bayes's Theorem is still regarded as unacceptable
by some on the grounds it allows ``cheating'' in the sense of choosing priors to
achieve a desired posterior inference \citep[p. 143]{OHagan2004}, others point
out this is not an ineluctable consequence of the reversal \citep[pp.
78--79]{Cox2006}. As we shall show, recent technical advances further weaken
this criticism.

Good's belief in the value of Reverse-Bayes methods won support from E.T.~Jaynes
in his well-known treatise on probability. Explaining a specific manifestation
of the approach (to be discussed shortly) Jaynes remarked: ``We shall find it
helpful in many cases where our prior information seems at first too vague to
lead to any definite prior probabilities; it stimulates our thinking and tells
us how to assign them after all'' \citep[p. 126]{Jaynes2003}. Yet despite the
advocacy of two leading figures in the foundations of Bayesian methodology, the
potential of Reverse-Bayes methods has remained largely unexplored. Most
published work has focused on their use in putting new research claims in
context, with Reverse-Bayes methods being used to assess whether the prior
evidence needed to make a claim credible is consistent with existing insight
\citep{Carlin1996,Matthews2001a,Matthews2001b,Spiegelhalter2004,Greenland2006,Greenland2011,Held2013,Colquhoun2017,Colquhoun2019,Held2019a,Held2020,Pawel2020b,
  Best2021}.

The purpose of this paper is to highlight recent technical developments of
Good's basic idea which lead to inferential tools of practical value in the
analysis of summary measures as reported in meta-analysis. As a running example
we consider a recently published meta-analysis investigating the association
between corticosteroids and mortality in hospitalized patients with COVID-19.
Specifically, we show how Reverse-Bayes methods address the current concerns
about the interpretation of new findings and their replication. We begin by
illustrating the basics of the Reverse-Bayes approach for both hypothesis
testing and parameter estimation. This is followed by a discussion of
Reverse-Bayes methods for assessing effect estimates in Section
\ref{sec4:effects}. These allow the credibility of both new and existing research
findings reported in terms of NHST to be evaluated in the context of existing
knowledge. This enables researchers to go beyond the standard dichotomy of
statistical significance/non-significance, extracting further insight from their
findings. We then discuss the use of the Reverse-Bayes approach in the most
recalcitrant form of the Problem of Priors, involving the assessment of research
findings which are unprecedented and thus lacking any clear source of prior
support. We show how the concept of intrinsic credibility resolves this
challenge, and puts recent calls to tighten $p$-value thresholds on a principled
basis \citep{Benjamin2017}. In Section \ref{sec4:bfs} we describe Reverse-Bayes
methods with Bayes factors, the principled solution for Bayesian hypothesis
testing. Finally, we describe in Section \ref{sec4:p.equals} Reverse-Bayes
approaches to interpretational issues that arise in conventional statistical
analysis based on $p$-values, and how they can be used to flag the risk of
inferential fallacies. We close with some extensions and final conclusions.

\subsection{Reverse-Bayes for hypothesis testing}
The subjectivity involved in the specification of prior distributions is often
seen as a weak point of Bayesian inference. The Reverse-Bayes approach can help
to resolve this issue both in hypothesis testing and parameter estimation, we
will start with the former.

Consider a null hypothesis $H_0$ with prior probability $\pi=\P(H_0)$, so
$\P(H_1) =1-\pi$ is the prior probability of the alternative hypothesis $H_1$.
Computation of the posterior probability of $H_1$ is routine with Bayes'
theorem:
\begin{equation*}
  \Pr(H_{1} \given \data) = \frac{\Pr(\data \given H_{1}) \Pr(H_{1})}{\Pr(\data \given H_{0}) \Pr(H_{0}) +
    \Pr(\data \given H_{1}) \Pr(H_{1})}.
\end{equation*}
Bayes' theorem can be written in more compact form as
\begin{equation}\label{eq4:eq0}
  \frac{\Pr(H_{1} \given \data)}{\Pr(H_{0} \given \data)} =
  \frac{\Pr(\data \given H_{1})}{\Pr(\data \given H_{0})} \,  \frac{\Pr(H_{1})}{\Pr(H_{0})},
\end{equation}
\ie the posterior odds are the likelihood ratio times the prior odds. The
standard 'forward-Bayes' approach thus fixes the prior odds (or one of the
underlying probabilities), determines the likelihood ratio for the available
data, and takes the product to compute the posterior odds. Of course, the latter
can be easily back-transformed to the posterior probability
$\Pr(H_{1} \given \data)$, if required. The Problem of Priors is now apparent:
in order for us to update the odds in favour of $H_1$, we must first specify the
prior odds. This can be problematic in situations where, for example, the
evidence on which to base the prior odds is controversial or even non-existent.

However, as Good emphasised it is entirely justifiable to ``flip'' Bayes's
theorem around, allowing us to ask the question: Which prior, when combined with
the data, leads to our specified posterior?
\begin{equation}\label{eq4:eq1}
  \frac{\Pr(H_{1})}{\Pr(H_{0})} = \left. \frac{\Pr(H_{1} \given \data)}{\Pr(H_{0} \given \data)} \, \Big/
\,   \frac{\Pr(\data \given H_{1})}{\Pr(\data \given H_{0})} \right. .
\end{equation}

For illustration we re-visit an example put forward by \citet[p. 35]{Good1950},
perhaps the first published Reverse-Bayes calculation. It centres on a question
for which the setting of an initial prior is especially problematic: does an
experiment provide convincing evidence for the existence of extra-sensory
perception (ESP)? The substantive hypothesis $H_{1}$ is that ESP exists, so that
$H_{0}$ asserts it does not exist. Imagine an experiment in which a person has
to make $n$ consecutive guesses of random digits (between 0 and 9) and all are
correct, as the ESP hypothesis $H_{1}$ would predict. The likelihood ratio is
therefore
\begin{equation}\label{eq4:ESPlik}
   \frac{\Pr(\data \given H_{1})}{\Pr(\data \given H_{0})} = \frac{1}{(1/10)^n} = 10^n .
\end{equation}
It is unlikely that sceptics and advocates of the existence of ESP would ever
agree on what constitutes reasonable priors from which to start a standard
Bayesian analysis of the evidence. However, Good argued that Reverse-Bayes
offers a way forward by using it to set bounds on the prior probabilities for
$H_{1}$ and $H_{0}$. This is achieved via the outcome of a thought (Gedanken)
experiment capable of demonstrating $H_{1}$ is more likely than $H_{0}$, that
is, of leading to posterior probabilities such that
$\Pr(H_1 \given \data) > \Pr(H_0 \given \data)$. Using this approach, which Good
termed the \emph{Device of Imaginary Results}, we see that if the ESP experiment
produced $n=20$ correct consecutive guesses, \eqref{eq4:eq1} combined with
\eqref{eq4:ESPlik} implies that ESP may be deemed more likely than not to exist
by anyone whose priors satisfy ${\Pr(H_{1})}/{\Pr(H_{0})} > 10^{-20}$. In
contrast, if only $n = 3$ correct guesses emerged, then the existence of ESP
could be rejected by anyone whose priors satisfy
${\Pr(H_{1})}/{\Pr(H_{0})} < 10^{-3}$. Using Bayes's Theorem in reverse has thus
led to a quantitative statement of the prior beliefs that either advocates or
sceptics of ESP must be able to justify in the face of results from a real
experiment. The practical value of Good's approach was noted by Jaynes in his
treatise: ``[I]n the present state of development of probability theory, the
device of imaginary results is usable and useful in a very wide variety of
situations, where we might not at first think it applicable''
\citep[p. 125--126]{Jaynes2003}.

It is straightforward to extend \eqref{eq4:eq0} and \eqref{eq4:eq1} to hypotheses
that involve unknown parameters $\theta$. The likelihood ratio
$\Pr(\data \given H_{1})/\Pr(\data \given H_{0})$ is then called a Bayes factor
\citep{Jeffreys1961, Kass1995} where
\begin{equation*}
  \Pr(\data \given H_{i}) = \int \Pr(\data \given \theta, H_{i}) \p(\theta \given H_{i}) d
  \theta
\end{equation*}
is the marginal likelihood under hypothesis $H_i$, $i=0,1$, obtained be
integration of the ordinary likelihood with respect to the prior distribution
$\p(\theta \given H_i)$. We will apply the Reverse-Bayes approach to Bayes
factors in Section \ref{sec4:bfs} and \ref{sec4:p.equals}.

\subsection{Reverse-Bayes for parameter estimation}
We can also apply the Reverse-Bayes idea to continuous prior and posterior
distributions of a parameter of interest $\theta$. Reversing Bayes' theorem
\begin{equation*}
  \p(\theta \given \data) = \frac{\p(\data \given \theta) \p(\theta)}{\p(\data)}
\end{equation*}
then leads to
\begin{equation}
  \p(\theta) = \p(\data) \, \frac{\p(\theta \given \data)}{\p(\data \given \theta)}.
\label{eq4:revBayesDensity}
\end{equation}
So the prior is proportional to the posterior divided by the likelihood with
proportionality constant $\p(\data)$.

Consider Bayesian inference for the mean $\theta$ of a univariate normal
distribution, assuming the variance $\sigma^2$ is known. Let $x$ denote the
observed value from that $\Nor(\theta, \sigma^2)$ distribution and suppose the
prior for $\theta$ (and hence also the posterior) is conjugate normal. Each of
them is determined by two parameters, usually the mean and the variance, but two
distinct quantiles would also work. If we fix both parameters of the posterior,
then the prior in \eqref{eq4:revBayesDensity} is -- under a certain regularity
condition -- uniquely determined. For ease of presentation we work with the
observational precision $\kappa=1/\sigma^2$ and denote the prior and posterior
precision by $\delta$ and $\delta'$, respectively. Finally let $\mu$ and $\mu'$
denote the prior and posterior mean, respectively.

Forward-Bayesian updating tells us how to compute the posterior precision and
mean:
\begin{align}
\label{eq4:posterior-precision}
\delta' &= \delta + \kappa, \\
\mu' &= \frac{\mu \delta + x \kappa}{\delta'}.\label{eq4:posterior-mean}
\end{align}
For example, fixed-effect (FE) meta-analysis is based on iteratively applying
\eqref{eq4:posterior-precision} and \eqref{eq4:posterior-mean} to the summary
effect estimate $x_i$ with standard error $\sigma_i$ from the $i$-th study,
$i=1,\ldots,n$, starting with an initial precision of zero. Reverse-Bayes simply
inverts these equations, which leads to the following:
\begin{align}
\label{eq4:prior-precision}
\delta &= \delta' - \kappa,  \\
\mu &= \frac{\mu'\delta' - x \kappa}{\delta}, \label{eq4:prior-mean}
\end{align}
provided $\delta' > \kappa$, \ie the posterior precision must be larger than the
observational precision.

We will illustrate the application of \eqref{eq4:prior-precision} and
\eqref{eq4:prior-mean} as well as the methodology in the rest of this paper
using a recent meta-analysis combining information from $n=7$ randomized
controlled trials investigating the association between corticosteroids and
mortality in hospitalized patients with COVID-19 \citep{REACT2020}; its results
are reproduced in Figure \ref{fig4:covid19-meta} (here and henceforth, odds
ratios (ORs) are expressed as log odds ratios to transform the range from
$(0, \infty)$ to $(-\infty, +\infty)$, consistent with the assumption of
normality). Let $x_i = \hat \theta_i$ denote the maximum likelihood estimate
(MLE) of the log odds ratio $\theta$ in the $i$-th study with standard error
$\sigma_i$. The meta-analytic odds ratio estimate under the fixed-effect model
(the pre-specified primary analysis) is $\widehat{\text{OR}} = 0.66$ [95\% CI
$0.53$ to $0.82$], respectively $\hat \theta = -0.42$ [95\% CI $-0.63$ to
$-0.20$] for the log odds ratio $\theta$, indicating evidence for lower
mortality of patients treated with corticosteroids compared to patients
receiving usual care or placebo. The pooled effect estimate $\hat \theta$
represents a posterior mean $\mu'$ with posterior precision $\delta'=83.8$.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/forest-plot-covid19-1}
}
\end{knitrout}
\caption{Forest plot of fixed-effect meta-analysis of $7$ randomized controlled
  trials investigating association between corticosteroids and mortality in
  hospitalized patients with COVID-19 \citep{REACT2020}. Shown are number of
  deaths among total number of patients for treatment/control group, log odds
  ratio effect estimates with 95\% confidence interval, two-sided $p$-values
  $p$, and prior-predictive tail probabilities $p_{\text{Box}}$ with a
  meta-analytic estimate based on the remaining studies serving as the prior.}
\label{fig4:covid19-meta}
\end{figure}

With a meta-analysis such as this, it is of interest to quantify potential
conflict among the effect estimates from the different studies. To do this, we
follow \citet{Presanis2013} and compute a prior-predictive tail probability
\citep{Box1980, Evans2006} for each study-specific estimate $\hat \theta_i$,
with a meta-analytic estimate based on the remaining studies serving as the
prior. As discussed above, fixed-effect meta-analysis is standard
forward-Bayesian updating for normally distributed effect estimates with an
initial flat prior. Hence, instead of fitting a reduced meta-analysis for each
study, we can simply use the the Reverse-Bayes equations
\eqref{eq4:prior-precision} and \eqref{eq4:prior-mean} together with the overall
estimate to compute the parameters of the prior in the absence of the $i$-th
study (denoted by the index $-i$):
\begin{eqnarray*}
\delta_{-i} & = & \delta' - 1/\sigma_i^2, \\
\mu_{-i} & = & \frac{ \mu' \delta' - \hat \theta_i / \sigma_i^2}{\delta_{-i}}.
\end{eqnarray*}
For example, through omitting the RECOVERY trial result $\hat{\theta}_i = -0.53$
with standard error ${\sigma}_i = 0.145$ we obtain $\delta_{-i} = 36.1$ and
$\mu_{-i} = -0.26$. A prior predictive tail probability using the approach from
\citet{Box1980} is then obtained by computing
$p_{\text{Box}} = \P(\chi^2_1 \geq t^2_{\text{Box}})$ with
$$
t_{\text{Box}} = \frac{\hat \theta_i - \mu_{-i}}{\sqrt{\sigma_i^2 + 1/\delta_{-i}}} =-1.24.$$
This leads to $p_{\text{Box}} = 0.22$ for the RECOVERY trial, indicating very
little prior-data conflict. The tail probabilities for the other studies are
even larger, with the exception of the COVID STEROID trial
($p_{\text{Box}}=0.05$), see Figure \ref{fig4:covid19-meta}. The lack of strong
conflict can be seen as an informal justification of the assumptions of the
underlying fixed-effect meta-analysis \citep{Presanis2013,Ferkingstad2017}. A
related method in network meta-analysis is to assess consistency via
``node-splitting'' \citep{Dias2010}. Reverse-Bayes methods may also be useful
for conflict assessment in more general evidence synthesis methods where
multiple distinct sources of data are combined \citep{Goodie2019,Cunen2021}, but
this may require more advanced numerical techniques.

Instead of determining the prior completely based on the posterior, one may also
want to fix one parameter of the posterior and one parameter of the prior. This
is of particular interest in order to challenge ``significant'' or
``non-significant'' findings through the Analysis of Credibility, as we will see
in the following section.

\section{Reverse-Bayes methods for the assessment of effect estimates}\label{sec4:effects}
A more general question amenable to Reverse-Bayes methods is the assessment of
effect estimates and their statistical significance or non-significance. This
issue has recently attracted intense interest following the public statement of
the American Statistical Association about the misuse and misinterpretation of
the NHST concepts of statistical significance and non-significance
\citep{Wasserstein2016}. First investigated 20 years ago by
\citet{Matthews2001a, Matthews2001b}, Reverse-Bayes methods for assessing both
statistically significant and non-significant findings have been termed the
Analysis of Credibility \citep{Matthews2018} (or AnCred), whose principles and
practice we now briefly review.

\subsection{The Analysis of Credibility}
\label{sec4:AnCred}
Suppose the study gives rise to a conventional confidence interval for the
unknown effect size $\theta$ at level $1 - \alpha$ with lower limit $L$ and
upper limit $U$. Assume that $L$ and $U$ are symmetric around the point estimate
$\hat \theta$ (assumed to be normally distributed with standard error $\sigma$).
AnCred then takes this likelihood and uses a Reverse-Bayes approach to deduce
the prior required in order to generate credible evidence for the existence of
an effect, in the form of a posterior that excludes no effect. As such, AnCred
allows evidence deemed \emph{statistically significant}/\emph{non-significant}
in the NHST framework to be assessed for its \emph{credibility} in the Bayesian
framework. As the latter conditions on the data rather than the null hypothesis,
it is inferentially directly relevant to researchers. After a suitable
transformation AnCred can be applied to a large number of commonly used effect
measures such as differences in means, odds ratios, relative risks and
correlations. We refer to the literature of meta-analysis for details about
conversion among effect size scales, \eg{} \citet[chapter 11.6]{Cooper2019}. The
inversion of Bayes's Theorem needed to assess credibility requires the form and
location of the prior distribution to be specified. This in turn depends on
whether the claim being assessed is statistically significant or
non-significant; we consider each below.

\subsubsection{Challenging statistically significant findings}
\label{sec4:significantFindings}

A statistically significant finding at level $\alpha$ is characterized by both
$L$ and $U$ being either positive or negative. Equivalently
$z^2 > z_{\alpha/2}^2$ is required where $z=\hat \theta/\sigma$ denotes the
corresponding test statistic and $z_{\alpha/2}$ the $(1-\alpha/2)$-quantile of
the standard normal distribution.

For significant findings, the idea is to ask how sceptical we would have to be
not to find the apparent effect estimate convincing. To this end, a
\emph{sceptical prior} is derived such that the corresponding posterior credible
interval just includes zero, the value of no effect. This critical prior
interval can then be compared with internal or external evidence to assess if
the finding is credible or not, despite being ``statistically significant''.

More specifically, a Reverse-Bayes approach is applied to significant confidence
intervals (at level $\alpha$) based on a normally distributed effect estimate.
The sceptical prior is a mean-zero normal distribution with variance
$\tau^2 = g \cdot \sigma^2$, so the only free parameter is the relative prior
variance $g = \tau^2/\sigma^2$. The posterior is hence also normal and either
its lower $\alpha/2$-quantile (for positive $\hat{\theta}$) or upper
$1 - \alpha/2$-quantile (for negative $\hat{\theta}$) is fixed to zero, so just
represents ``non-credible''. The sufficiently sceptical prior then has relative
variance
\begin{align}
  \label{eq4:sspv}
  g &=
      \begin{cases}
        \dfrac{1}{z^2/z_{\alpha/2}^2 - 1}
        & ~~ \text{if} ~
        {z^2} > {z_{\alpha/2}^2} \\
        \text{undefined} & ~~ \text{else}
      \end{cases}
\end{align}
see the Appendix in \citet{Held2019a} for a derivation. The corresponding
\emph{scepticism limit} \citep{Matthews2018}, the upper bound of the
equal-tailed sceptical prior credible interval at level $1-\alpha$, is
\begin{equation}
  \label{eq4:S}
  \SL = \frac{(U-L)^2}{4 \sqrt{UL}},
\end{equation}
which holds for any value of $\alpha$ provided the effect is significant at that
level.

The left plot in Figure \ref{fig4:anCredEx} illustrates the AnCred procedure for
the finding from the RECOVERY trial, the only statistically significant result
(at the conventional $\alpha=0.05$ level) shown in Figure
\ref{fig4:covid19-meta}. The trial found a decrease in COVID-19 mortality for
patients treated with corticosteroids compared to usual care or placebo
($\hat{\theta} = -0.53$ [95\% CI $-0.82$ to $-0.25$]. The sufficiently sceptical
prior has relative variance $g = 0.39$, so the sufficiently sceptical prior
variance needs to be roughly 2.5 times smaller than the variance of the estimate
to make the result non-credible. The scepticism limit on the log odds ratio
scale turns out to be $\SL=0.18$, which corresponds to a critical prior interval
with limits 0.84 and 1.19 on the odds ratio scale. Thus sceptics may still
reject the RECOVERY trial finding as lacking credibility despite its statistical
significance if external evidence suggests mortality reductions (in terms of
odds) are unlikely to exceed $1 - 0.84 \approx 16 \%$.

It is also possible to apply the approach to the meta-analytic log odds ratio
estimate $\hat \theta = -0.42$ [95\% CI $-0.63$ to $-0.20$] from all 7 studies
combined. Then $\SL= 0.13$, so the meta-analytic estimate can be considered as
non-credible if external evidence suggests that mortality reductions are
unlikely to exceed $1-\exp(-\SL)=1 - 0.88 \approx 12 \%$. This illustrates that
the meta-analytic estimate has gained credibility compared to the result from
the RECOVERY study alone, despite the reduction in the effect estimate
($\widehat{\text{OR}} = \exp(\hat \theta) = 0.66$ vs.~0.59 in the RECOVERY
study).

\subsubsection{Challenging statistically non-significant findings}
\label{sec4:nonSigAnCred}
It is also possible to challenge ``non-significant'' findings (\ie those for
which the CI now includes zero, so $z^2 < z_{\alpha/2}^2$) using a prior that
pushes the posterior towards being credible in the Bayesian sense, with
posterior credible interval no longer including zero, corresponding to no
effect.

\citet{Matthews2018} proposed the ``advocacy prior'' for this purpose, a normal
prior with positive mean $\mu$ and variance $\tau^2$ chosen such that the
$\alpha/2$-quantile is fixed to zero (for positive effect estimates
$\hat \theta > 0$). He showed that the ``advocacy limit'' AL, the
$(1-\alpha/2)$-quantile of the advocacy prior is
\begin{equation}\label{eq4:AL}
  \mbox{AL} = - \frac{U+L}{2 \, U L} (U-L)^2
\end{equation}
to reach credibility of the corresponding posterior at level $\alpha$. We show
in Appendix \ref{app:app1} that the corresponding relative prior mean
$f = \mu / \hat \theta$ is
\begin{align}
\label{eq4:mu}
  f &=
  \begin{cases}
    \dfrac{2}{1 - z^2/z_{\alpha/2}^2}
    & ~~ \text{if} ~
    {z^2} < {z_{\alpha/2}^2} \\
    \text{undefined} & ~~ \text{else. }
\end{cases}
\end{align}

There are two important properties of the advocacy prior. First, the coefficient
of variation CV is
$$\mbox{CV} = \tau/\mu = z_{\alpha/2}^{-1}.$$
The advocacy prior $\theta \sim \Nor(\mu, \tau^2=\mu^2 \, \mbox{CV}^2)$ is hence
characterized by a fixed coefficient of variation, so this prior has equal
evidential weight (quantified in terms of $\mu/\tau=z_{\alpha/2}$) as data which
are ``just significant'' at level $\alpha$. Second, the advocacy limit AL
defines the family of normal priors capable of rendering a ``non-significant''
finding credible at the same level. Such priors are summarized by the credible
interval ($L_o, U_o$) where $L_o \geq 0$, $U_o \leq \mbox{AL}$. Thus when
confronted with a ``non-significant'' result -- often, and wrongly, interpreted
as indicating no effect -- advocates of the existence of an effect may still
claim the existence of the effect is credible to the same level if there exists
prior evidence or insight compatible with the credible interval ($L_o, U_o$). If
the evidence for an effect is strong (weak), the resulting advocacy prior will
be broad (narrow), giving advocates of an effect more (less) latitude to make
their case under terms of AnCred. Note that \eqref{eq4:AL} and \eqref{eq4:mu}
also hold for negative effect estimates, where we fix the
$(1-\alpha/2)$-quantile of the advocacy prior to zero and define the advocacy
limit AL as the $\alpha/2$-quantile of the advocacy prior.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-examples-plot-1}
}
\end{knitrout}
\caption{Two examples of the Analysis of Credibility. Shown are point estimates
  within 95\% confidence/credible intervals. The left plot illustrates how a
  sceptical prior is used to challenge the significant finding from the RECOVERY
  trial \citep{RECOVERY2020}. The right plot illustrates how an advocacy prior
  is used to challenge a non-significant finding from the REMAP-CAP trial
  \citep{REMAPCAP2020}. In both scenarios the posterior is fixed to be just
  non-credible/credible.}
\label{fig4:anCredEx}
\end{figure}

For illustration we consider the data from the REMAP-CAP trial that supported
the RECOVERY trial finding of decreased COVID-19 mortality from corticosteroid
use. However, this trial involved far fewer patients, and despite the point
estimate showing efficacy, the relatively large uncertainty rendered the overall
finding non-significant at the 5\% level ($\hat{\theta} = -0.34$ [95\% CI
$-0.96$ to $0.29$]). Such an outcome is frequently (and wrongly) taken to imply
no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie $0.15$ on the
odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
advocates of the effectiveness of corticosteroids can regard the trial as
providing credible evidence of effectiveness despite its non-significance if
external evidence supports mortality reductions (in terms of odds) in the range
0\% to 85\%. So broad an advocacy range reflects the fact that this relatively
small trial provides only modest evidential weight, and thus little constraint
on prior beliefs about the effectiveness of corticosteroids.

Another way to push non-significant findings towards credibility is to use a
prior based on data from another study or a different subgroup. For example,
\citet{Best2021} consider results from the MENSA trial \citep{MENSA2014} on the
efficacy of Mepolizumab against placebo in 551 adult and 25 adolescent patients
with severe asthma. The treatment effect was estimated to be positive in both
subgroups but lacked significance among adolescents. Best et al. combine the
data in the adolescent subgroup with a mixture prior based on a weak and an
informative component. The weak component is a minimally informative normal
prior with mean zero and large variance. The variance is chosen such that the
information content of the prior is equivalent to that provided by a single
subject or event (\emph{unit-information prior}) \citep{Kass1995b}. The other
component is an informative prior based on the (significant) results from the
adolescent subgroup. A Reverse-Bayes approach is used to determine how much
prior weight one needs to assign to the informative component to obtain a
credible posterior result with a 95\% highest posterior credible interval no
longer including zero. In the MENSA trial the required prior weight on the
informative component was 0.7 (and thus 0.3 on the weak prior component) to
achieve a credible result \citep{Best2021}. This illustrates that a considerable
amount of ``Bayesian borrowing'' is required to extrapolate the results from
adults to adolescents.

\begin{figure}[!htb]
\begin{knitrout}
  \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/advocacy-borrowing-1}
}
\end{knitrout}
\caption{Illustration of the Reverse-Bayes borrowing method. The data from the
  (non-significant) REMAP-CAP trial are combined with a mixture prior consisting
  of the (significant) RECOVERY trial data and a unit-information prior (both
  estimates shown with 95\% confidence interval). The resulting posterior
  medians with equal-tailed 95\% credible intervals are shown for a range of
  mixing weights. The Reverse-Bayes mixing weight $w = 0.5$ leads to the
  highlighted posterior with upper credible interval limit fixed at one.}
\label{fig4:borrowing}
\end{figure}
In the meta-analytic setting we may ask a similar question: Suppose we want to
combine the REMAP-CAP study results with a fraction of the RECOVERY trial data,
how much weight do we need to assign to the RECOVERY trial to make the REMAP-CAP
study credible? The unit-information prior for a logOR has variance
$\tau^{2} = 4$ \citep[section 2.4.1]{Spiegelhalter2004}, so the mixture prior is
\begin{align*}
  \theta \sim w \cdot \Nor\left(0, \tau^{2} = 4\right) + (1 - w) \cdot
  \Nor\left( \hat{\theta}_{\scriptscriptstyle \text{REC}},
  \sigma^{2}_{\scriptscriptstyle \text{REC}}\right)
\end{align*}
with $w$ the mixing weight and point estimate
$\hat{\theta}_{\scriptscriptstyle \text{REC}}$ and squared standard error
$\sigma^{2}_{\scriptscriptstyle \text{REC}}$ of the RECOVERY trial,
respectively. The resulting posterior is again a mixture of two normals with the
posterior mean and variance of each component being the usual ones obtained from
conjugate Bayesian updating, while the weights are proportional to the marginal
likelihood of the data under each component \citep[section 3.5]{Best2021}.

Figure~\ref{fig4:borrowing} shows posterior medians with 95\% equal-tailed
credible intervals for a range of mixing weights. We see that a weight of at
least $w = 0.5$ is required to render the resulting posterior credible.
Advocates of corticosteroids thus need to be able to justify such levels of
prior beliefs, in order to conclude efficacy of corticosteroids also in the
REMAP-CAP trial.

\subsubsection{Assessing credibility via equivalent prior study sizes}
\label{sec4:prior-data-translation}
Reverse-Bayes credibility assessments can also be formulated in terms of the
size and content of a prior study capable of challenging a claim of statistical
significance/non-significance. This approach puts the weight of prior evidence
in the context of the observed data, expressed as participant numbers.
\citet{Greenland2006} demonstrated the value of this approach in assessing the
credibility of statistically significant findings from large observational
studies in epidemiology. The same concept can, however, be extended to the
assessment of both significant and non-significant outcomes more widely, such as
small randomized controlled trials. For any study generating binary data in the
form of event/non-event counts under two different conditions, the comparative
effect measure can be expressed as a log-odds ratio with variance (squared
standard error)
\begin{equation}
  \label{eq4:SElogOR}
%% \tau^{2} =
1/m_1 + 1/n_1 + 1/m_2 + 1/n_2.
\end{equation}
where $m_i$ and $n_i$ are the numbers of events and non-events, respectively, in
study arm $i=1,2$. This provides the link between the Reverse-Bayes prior
distribution and the corresponding numbers of prior study participants. Using
the simplifying assumptions of equal numbers of events $m = m_{1} = m_{2}$ and
large numbers of non-events $n_{1}$ and $n_2$ in each arm ($n_i > 100 \, m_i$,
say), the variance \eqref{eq4:SElogOR} reduces to $2/m$. The Reverse-Bayes
sceptical prior defined in Section \ref{sec4:significantFindings} has variance
$\tau^{2} = \SL^2/z_{\alpha/2}^{2}$, where $\SL$ is the sceptical limit.
Equating the two implies that such a prior is equivalent to a (large)
hypothetical study with $$m = 2/\tau^{2} = 2 \, z_{\alpha/2}^2/\SL^2$$ events in
both arms. The more compelling the data -- that is, the smaller the value of
$\SL$ -- the larger the number of events $m$ required in both arms of the
hypothetical large prior study to render the result non-credible at level
$\alpha$.

While the assumption of large studies can be appropriate with epidemiological
studies involving rare events, it can be harder to justify for RCTs.
Fortunately, the theory can be extended to encompass these and also the case of
non-significant findings with little additional complexity. In the case of the
sceptical prior, we simply require that the numbers of event $m$ and non-events
$n$ are the same in both arms to constrain the mean to zero; the variance
\eqref{eq4:SElogOR} then simplifies to $2/m + 2/n$. Adding the constraint that
the event rate of the sceptical prior $R= m /(m + n)$ matches that of the study
under assessment, we then find
\begin{eqnarray*}
  m = \frac{2}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}
For example, from Figure~\ref{fig4:covid19-meta} the RECOVERY trial has an
overall mortality rate $R=(95 + 283)/(324 + 683) = 37.54\%$ and $\SL = 0.178$ at
the $\alpha = 5\%$ level $(z_{\alpha/2} = 1.96)$ corresponds to
$\tau^2=0.091^2$, so $m = 389$ and $n = 648$ (these are integer approximations
of exact computations), and thus a prior study capable of challenging the
credibility of the RECOVERY trial requires $1037$ patients and $389$ deaths in
each arm. At more than twice the size of the RECOVERY trial ($2074$ vs. $1007$)
patients and considerably more deaths in both arms, this level of sceptical
prior evidence highlights the robustness of the trial finding.

A similar approach determines the characteristics of the hypothetical prior
study needed to turn a ``negative'' non-significant finding into one that is
credible to a specific $\alpha$ level. The Reverse-Bayes advocacy prior from
\citet{Matthews2018} described in Section~\ref{sec4:nonSigAnCred} has a mean
$\mu = \mbox{AL}/2$ and variance $\tau^{2} = \AL^2/(2z_{\alpha/2})^2$. Under the
large study assumption and equating the latter with \eqref{eq4:SElogOR} as
before, the corresponding number of events needed to be observed in both arms of
the hypothetical study is $m = 2/\tau^{2} = 8 \, z_{\alpha/2}^2/\mbox{AL}^2$. To
incorporate the non-zero mean by which this prior represents advocacy, these $m$
events are taken to have been observed among participants allocated to the two
study arms in the ratio $1 \colon K$ where $K = \exp(\mu) = \exp(\AL/2)$, the
allocation being such that it increases the relative evidential weight for the
hypothesis ``negated'' by the non-significance.

As before, while the large study approximation may be justified in
epidemiological examples, this is less likely to be true for RCTs. In such
cases, we can adapt the approach used for sceptical priors, the size and
composition of the advocacy prior being found by setting the numbers of events
$m$ in each arm the same, but this time allowing for different numbers of
non-events in each arm via the allocation ratio $K$. The resulting variance is
then
\begin{align*}
  \tau^{2} = \frac{2}{m} + \frac{K + 1}{n}
\end{align*}
where $n$ is the number of non-events in the arm used to support the null
hypothesis (\eg the control arm in an RCT). With the control arm event rate
$R = m/(m + n)$ constrained to match that of the actual study, we find
\begin{eqnarray*}
  m = \frac{2 - R(1 - K)}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}

As an example, we return to the REMAP-CAP trial, whose findings were consistent
with a reduction of mortality but failed to reach statistical significance. As
noted above, its advocacy limit ($\AL = -1.89)$ implies this trial has
relatively little evidential weight, and gives considerable scope for prior
studies to make its outcome credible at the 95\% level. With
$K = \exp(\mu) = \exp(\AL/2) = 0.39$, $R = 29/92$ and $z_{\alpha/2} = 1.96$ we
find $m = 11$ and $n = 25$. Thus the hypothetical prior study comprises $11$
deaths from $11$ + $25$ = $36$ patients in the control arm and the same number
of deaths from $11 + (25/0.4) = 75$ patients in the treatment arm. At barely
half the total size of REMAP-CAP but a considerably more impressive mortality
reduction from $R = 29/92 = 32\%$ in the control arm to $11/75=15$\% in the
treatment arm (rather than $26/105=25$\% in REMAP-CAP), the nature of this
hypothetical prior study confirms the paucity of evidence in the original trial.

\subsubsection{The fail-safe \textit{N} method}
Another data representation of a sceptical prior forms the basis of the
well-known ``fail-safe $N$'' method, sometimes also called ``file-drawer
analysis''. This method, first introduced by \citet{Rosenthal1979} and later
refined by \citet{Rosenberg2005}, is commonly applied to the results from a
meta-analysis and answers the question: ``How many unpublished negative studies
do we need to make the meta-analytic effect estimate non-significant?'' A
relatively large $N$ of such unpublished studies suggests that the estimate is
robust to potential null-findings, for example due to publication bias.
Calculations are made under the assumption that the unpublished studies have an
average effect of zero and a precision equal to the average precision of the
published ones.

While the method does not identify nor adjust for publication bias, it provides
a quick way to assess how robust the meta-analytic effect estimate is. The
method is available in common software packages such as \texttt{metafor}
\citep{Viechtbauer2010} and its simplicity and intuitive appeal have made it
very popular among researchers.

AnCred and the fail-safe $N$ are both based on the idea to challenge effect
estimates such that they become ``non-significant/not credible'', and it is easy
to show that the methods are under some circumstances also technically
equivalent. To illustrate this, we consider again the meta-analysis on the
association between corticosteroids and COVID-19 mortality \citep{REACT2020}
which gave the pooled log odds ratio estimate $\hat \theta = -0.42$ with
standard error $\sigma = 0.11$, posterior precision $\delta'=83.8$ and test
statistic $z=\hat \theta/\sigma= -3.81$.

Using the \citet{Rosenberg2005} approach (as implemented in the \texttt{fsn()}
function from the \texttt{metafor} package) we find that at least $N = 20$
additional but unpublished non-significant findings are needed to make the
published meta-analysis effect non-significant. If instead, we challenge the
overall estimate with AnCred, we obtain the relative prior variance $g = 0.36$
using equation \eqref{eq4:sspv}, so $\tau^2 = 0.0043$. Taking into account the
average precision $\delta' / n = 11.98$ of the different effect estimates
estimates in the meta-analysis leads to ${N} = n/(\delta' \cdot \tau^2) = 19.5$
which is equivalent to the fail-safe $N$ result after rounding to the next
larger integer.

\subsection{Intrinsic credibility}
\label{sec4:IC}

The Problem of Priors is at its most challenging in the context of entirely
novel ``out of the blue'' effects for which no obviously relevant external
evidence exist. By their nature, such findings often attract considerable
interest both within and beyond the research community, making their reliability
of particular importance. Given the absence of external sources of evidence,
\citet{Matthews2018} proposed the concept of \emph{intrinsic
  credibility}. This requires that the evidential weight of an unprecedented
finding is sufficient to put it in conflict with the sceptical prior rendering
it non-credible. In the AnCred framework, this implies a finding possesses
intrinsic credibility at level $\alpha$ if the estimate $\hat{\theta}$ is
outside the corresponding sceptical prior interval $[-\SL, \SL]$ extracted using
Reverse-Bayes from the finding itself, \ie $\hat{\theta}^2 > \SL^2$ with $\SL$
given in \eqref{eq4:S}. Matthews showed this implies an unprecedented finding is
intrinsically credible at level $\alpha=0.05$ if its $p$-value does not exceed
0.013.

\citet{Held2019a} refined the concept by suggesting the use of a
prior-predictive check \citep{Box1980, Evans2006} to assess potential prior-data
conflict. With this approach the uncertainty of the estimate $\hat{\theta}$ is
also taken into account since it is based on the prior-predictive distribution,
in this case $\hat\theta \sim \Nor(0, \sigma^2 + \tau^2=\sigma^2 \, (1+g))$ with
$g$ as given in \eqref{eq4:sspv}. Intrinsic credibility is declared if the
(two-sided) tail-probability
\begin{equation*}
  p_{\text{Box}} = \P\left(\chi^2_1 \geq \hat \theta^2/(\sigma^2+\tau^2)\right) = \P\left(\chi^2_1 \geq z^2/(1+g)\right)
\end{equation*}
of $\hat{\theta}$ under the prior-predictive distribution is smaller than
$\alpha$. It turns out that the $p$-value associated with $\theta$ needs to be
at least as small as 0.0056 to obtain intrinsic credibility at level
$\alpha=0.05$, providing another principled argument for the recent proposition
to lower the $p$-value threshold for the claims of new discoveries to 0.005
\citep{Benjamin2017}. A simple check for intrinsic credibility is based on the
\emph{credibility ratio}, the ratio of the upper to the lower limit (or vice
versa) of a confidence interval for a significant effect size estimate. If the
credibility ratio is smaller than 5.8 then the result is intrinsically credible
\citep{Held2019a}. This holds for confidence intervals at all possible values of
$\alpha$, not just for the 0.05 standard. For example, in the RECOVERY study the
95\% confidence interval for the log-odds ratio ranges from $-0.82$ to $-0.25$,
so the credibility ratio is $-0.82/-0.25 = 3.27 < 5.8$ and the result is
intrinsically credible at the standard 5\% level.

\subsubsection*{Replication of effect direction}

Whether intrinsic credibility is assessed based on the prior or the
prior-predictive distribution, it depends on the level $\alpha$ in both cases.
To remove this dependence, \citet{Held2019a} proposed to consider the
smallest level at which intrinsic credibility can be established, defining the
$p$-value for intrinsic credibility
\begin{align}
  \label{eq4:pic}
  \pIC
  &= 2\left\{1 - \Phi\left(\frac{\abs{z}}{\sqrt{2}}\right)\right\},
\end{align}
see section 4 in \citet{Held2019a} for the derivation. Now
$z=\hat \theta/\sigma$, so compared to the standard $p$-value
$p=2\left\{1 - \Phi\left(\abs{z}\right)\right\}$, the $p$-value for intrinsic
credibility is based on twice the variance $\sigma^2$ of the estimate
$\hat{\theta}$. Although motivated from a different perspective, inference based
on intrinsic credibility thus mimics the \emph{doubling the variance rule}
advocated by \citet{Copas2005} as a simple means of adjusting for model
uncertainty.

Moreover, \citet{Held2019a} showed that $\pIC$ is connected to $\prep$ of
\citet{Killeen2005}, the probability that a replication will result in an effect
estimate $\hat{\theta}_r$ in the same direction as the observed effect estimate
$\hat{\theta}$, by $\prep = 1 - \pIC/2$. Hence, an intrinsically credible
estimate at a small level $\alpha$ will have high chance of replicating since
$\prep \geq 1 - \alpha/2$. Note that $\prep$ lies between 0.5 and 1 with the
extreme case $\prep=0.5$ if $\hat \theta=0$.

As an example, the $p$-value for intrinsic credibility for the RECOVERY trial
finding (with $p$-value $p=0.0002$) cited earlier is $\pIC = 0.01$ and thus the
probability of the replication effect going in the same direction (\ie reduced
mortality in this case) is $0.995$. In contrast, the finding from the smaller
REMAP-CAP trial (with $p=0.29$) leads to $\pIC = 0.46$, and the probability of
effect direction replication is hence only $0.77$.

\section{Reverse-Bayes methods with Bayes factors}
\label{sec4:bfs}
The AnCred procedure as described above uses posterior credible intervals as a
means of quantifying evidence. However, quantification of evidence with Bayes
factors is a more principled solution for hypothesis testing in the Bayesian
framework \citep{Jeffreys1961, Kass1995}. Bayes factors enable direct
probability statements about null and alternative hypothesis and they can also
quantify evidence \emph{for} the null hypothesis, both are impossible with
indirect measures of evidence such as $p$-values \citep{Held2018}.
Reverse-Bayes approaches combined with Bayes factor methodology was pioneered by
\citet{Carlin1996} but then remained unexplored until \citet{Pawel2020b}
proposed an extension of AnCred where Bayes factors are used as a means of
quantifying evidence. Rather than determining a prior such that a finding
becomes ``non-credible'' in terms of a posterior credible interval, this
approach determines a prior such that the finding becomes ``non-compelling'' in
terms of a Bayes factor. In the second step of the procedure, the plausibility
of this prior is quantified using external data from a replication study. Here,
we will illustrate the methodology using only an original study; we mention
extensions for replications in Section \ref{sec4:extensions}.

\subsection{Sceptical priors}\label{sec4:sceptical}

As before, $\hat \theta$ denotes the estimate of the unknown mean $\theta$ of a
$\Nor(\theta, \sigma^2)$ distribution with known variance $\sigma^2$. A standard
hypothesis test compares the null hypothesis $H_0\colon$ $\theta = 0$ to the
alternative $H_1\colon$ $\theta \neq 0$. Bayesian hypothesis testing requires
specification of a prior distribution of $\theta$ under $H_1$. A typical choice
is a local alternative, a unimodal symmetric prior distribution centred around
the null value \citep{Johnson2010}. We consider again the conjugate sceptical
prior $\theta \given H_1 \sim \Nor(0, \tau^2 = g \cdot \sigma^2)$ with relative
prior variance $g$ for this purpose. This leads to the Bayes factor comparing
$H_0$ to $H_1$ being
\begin{align}
  \label{eq4:bf01}
  \BF_{01} =
  \sqrt{1 + g} \cdot
  \exp\left\{-\frac{g}{1 + g} \cdot \frac{z^2}{2} \right\},
\end{align}
where $z=\hat \theta/\sigma$. Yet again, the amount of evidence which the data
provide against the null hypothesis depends on the prior parameter $g$; As $g$
becomes smaller ($g \downarrow 0$), the null hypothesis and the alternative will
become indistinguishable, so the data are equally likely under both
($\BF_{01} \to 1$). On the other hand, for increasingly diffuse priors
($g \to \infty$), the null hypothesis will always prevail
($\BF_{01} \to \infty$) due to the Jeffreys-Lindley paradox \citep{Robert2014}.
In between, the $\BF_{01}$ reaches a minimum at
$g = \max\left\{z^2 - 1, 0\right\}$ leading to
\begin{align}
  \text{minBF}_{01} =
  \begin{cases}
    \abs{z} \cdot \exp\left\{-z^2/2\right\} \cdot \sqrt{e}
    & \text{if} ~ \abs{z} > 1 \\
    1 & \text{else}
  \end{cases}
  \label{eq4:minBFnorm}
\end{align}
which is an instance of a \emph{minimum Bayes factor}, the smallest possible
Bayes factor within a class of alternative hypotheses, in this case zero-mean
normal alternatives \citep{Edwards1963, Berger1987, Sellke2001, Held2018}.

Reporting of minimum Bayes factors is one attempt of solving the Problem of
Priors in Bayesian inference. However, this bound may be rather small and the
corresponding prior unrealistic. In contrast, the Reverse-Bayes approach makes
the choice of the prior explicit by determining the relative prior variance
parameter $g$ such that the finding is no longer compelling, followed by
assessing the plausibility of this prior. To do so, one first fixes
$\BF_{01} = \gamma$, where $\gamma$ is a cut-off above which the result is no
longer convincing, for example $\gamma = 1/10$, the level for strong evidence
according to the classification from \citet{Jeffreys1961}. The sufficiently
sceptical relative prior variance is then given by
\begin{align}
\label{ggamma}
  g &=
  \begin{cases}
    -\dfrac{z^2}{q} - 1
    & ~~ \text{if} ~
    -\dfrac{z^2}{q} \geq 1 \\
    \text{undefined} & ~~ \text{else}
  \end{cases} \\
  \text{where} ~ q &=
  \text{W} \left(-\frac{z^2}{\gamma^2} \cdot
  \exp\left\{-z^2\right\}\right)
  \nonumber
\end{align}
where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
$text{W}(y) \leq -1$ for $y \in [-e^{-1}, 0)$ \citep{Corless1996}, see the
Appendix in \citep{Pawel2020b} for a proof.

The sufficiently sceptical relative prior variance $g$ exists only for a cut-off
$\gamma$ if $\text{minBF}_{01} \leq \gamma$, similar to standard AnCred where it
exists only at level $\alpha$ if the original finding was significant at the
same level. In contrast to standard AnCred, however, if the sufficiently
sceptical relative prior variance $g$ exists, there are always two solutions, a
consequence of the Jeffreys-Lindley paradox: If $\BF_{01}$ decreases in $g$
below the chosen cut-off $\gamma$, after attaining its minimum it will
monotonically increase and intersect a second time with $\gamma$, admitting a
second solution for the sufficiently sceptical prior.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/AnCred-BF-examples-plot-1}
}
\end{knitrout}
\caption{Illustration of the AnCred with Bayes factors procedure using the
  findings from the meta-analysis on the association of COVID-19 mortality and
  corticosteroids. The left plot shows the Bayes factor $\BF_{01}$ as a function
  of the relative variance $g$ of the sceptical prior. The result from the
  RECOVERY trial is challenged with a sceptical prior such that
  $\BF_{01} = 1/10$, for the other trials such a prior does not exist. The right
  plot shows the Bayes factor $\BF_{01}$ as a function of the relative mean
  $f = \mu/\hat{\theta}$ of the advocacy prior where the coefficient of
  variation from the prior is fixed to
  $\text{CV} = \tau/\mu = 1/z(\gamma=1/3) = 0.67$, where $z(\gamma)$ is given in
  \eqref{eq4:zgamma}. The RECOVERY and the CAPE COVID findings are challenged
  such that $\BF_{01} = 1/3$, for the other trials such a prior does not exist.}
\label{fig4:bf}
\end{figure}

We now revisit the meta-analysis example considered earlier: The left plot in
Figure \ref{fig4:bf} shows the Bayes factor $\BF_{01}$ from~\eqref{eq4:bf01} as
a function of the relative prior variance $g$ for each finding included in the
meta-analysis. Most of them did not include a great number of participants and
thus provide little evidence against the null hypothesis for any value of the
relative prior variance $g$. In contrast, the finding from the RECOVERY trial
provides more compelling evidence and can be challenged up to
$\text{minBF}_{01} = 1/148.9$. For example, we see in Figure \ref{fig4:bf} that
the relative sceptical prior variance needs to be $g \leq 0.59$ such that the
finding is no longer compelling at level $\gamma = 1/10$. This translates to a
95\% prior credible interval from 0.8 to 1.24 for the OR (or any narrower
interval around 1). Hence, a sceptic might still consider the RECOVERY finding
to be unconvincing, despite its minimum BF being very compelling, if external
evidence supports ORs in that range. By applying the prior-to-data conversion
method described in Section~\ref{sec4:prior-data-translation} we can further see
that the evidential value of this prior is equivalent to a trial with 258 events
and 429 non-events in both arms (so that the overall mortality rate is
equivalent with the RECOVERY trial). For comparison, the sceptical prior from
standard AnCred at $\alpha = 0.05$ was equivalent to a trial with 389 events and
648 non-events, respectively.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/example5-RECOVERY-1}
}
\end{knitrout}
\caption{Comparison of the Bayes factor for intrinsic credibility $\BFIC$, the
  minimum Bayes factor $\mbox{minBF}_{01}$, and the $p$-value for intrinsic
  credibility $\pIC$ as a function of the absolute $z$-value $\abs{z}$. The
  value $\pIC = 0.15$ is at the breakpoint at $\abs{z} = 2.04$.}
\label{fig4:bfic}
\end{figure}

The plausibility of the sufficiently sceptical prior can be evaluated in light
of external evidence, but what should we do in the absence of such? We could
again use the \citet{Box1980} prior-predictive check as in
Section~\ref{sec4:IC}, however, the resulting tail probability is difficult to
compare to the Bayes-factor cut-off $\gamma$. When a specific alternative model
to the null is in mind, \citet[p. 391]{Box1980} also suggested to use a Bayes
factor for model criticism of the null model. Following this approach,
\citet{Pawel2020b} proposed to define a second Bayes factor contrasting the
sufficiently sceptical prior to an optimistic prior, which they defined as
$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$ the posterior of $\theta$
based on the data and the reference prior $f(\theta) \propto 1$. The optimistic
prior therefore represents the position of a proponent who takes the original
claim at face value. This leads to the second Bayes factor being
\begin{align}
  \label{eq4:bf12}
  \BF_{12} = \sqrt{\frac{2}{1 + g}} \cdot \exp\left\{-\frac{1}{2}\cdot \frac{z^{2}}{1 + g}\right\}.
\end{align}
Analogously to the tail probability approach from Section~\ref{sec4:IC},
intrinsic credibility is established if the data support the optimistic over the
sceptical prior at a higher level than they support the sceptical prior over the
null hypothesis, \ie if
\begin{align*}
  \BF_{12} \leq \BF_{01}
\end{align*}
with sufficiently sceptical relative prior variance $g$ from~\eqref{ggamma} used
in both Bayes factors. For example, if we challenge the RECOVERY trial finding
such that the resulting Bayes factor is only $\BF_{01} = 1/10$, we obtain
with~\eqref{eq4:sspv} the sufficiently sceptical relative prior variance
$g = 0.59$ and in turn with~\eqref{eq4:bf12} the Bayes factor $\BF_{12} = 1/64$,
so the finding is intrinsically credible at $\gamma = 1/10$.

To remove the dependence on the choice of the level $\gamma$, one can determine
the smallest level $\gamma$ where intrinsic credibility can be established. This
defines a Bayes factor for intrinsic credibility $\BFIC$ similar to the
definition of the $p$-value for intrinsic credibility $\pIC$
from~\eqref{eq4:pic}. Intrinsic credibility at level $\gamma$ is then equivalent
with $\BFIC \leq \gamma$. Details on the computation of $\BFIC$ are given in
Appendix~\ref{app:BFIC}. For the RECOVERY finding, the Bayes factor for
intrinsic credibility is $\BFIC = 1/25$. This means the data favour the
optimistic prior over any sceptical prior that is capable of rendering the
original result no longer convincing at $\gamma = 1/25$. For comparison the
$p$-value for intrinsic credibility~\eqref{eq4:pic} is $\pIC = 0.009$.

Figure~\ref{fig4:bfic} shows the Bayes factor for intrinsic credibility $\BFIC$
as a function of the $z$-value along with a comparison to the $p$-value for
intrinsic credibility $\pIC$ and the minimum Bayes factor $\mbox{minBF}_{01}$
from~\eqref{eq4:minBFnorm}. We see that the $\BFIC$ is undefined when
$\abs{z} < \sqrt{\log 2} \approx 0.83$. In this case the data are so
unconvincing that any sceptical prior is better supported by the data than the
optimistic prior. For $z$-values between $\sqrt{\log 2} \leq \abs{z} < 2.04$,
the $\BFIC$ equals the minimum Bayes factor $\mbox{minBF}_{01}$, whereas for
larger $z$-values $\abs{z} \geq 2.04$, the $\BFIC$ is always larger (more
conservative) than the $\mbox{minBF}_{01}$. In the absence of any prior
information, it may therefore be a useful evidential summary which formally
takes into account both scepticism and optimism about the observed data.

A $p$-value less than $0.05$ is usually regarded as sufficient evidence against
the null hypothesis, but how much evidence does $p = 0.05$ mean in terms of the
Bayes factor for intrinsic credibility? From Figure~\ref{fig4:bfic}, we see that
the $\BFIC = 1/2.1$ for $\abs{z} = 1.96$, so at most ``worth a bare mention''
according to the classification from \citet{Jeffreys1961}. Thus, also from this
perspective, the conventional $p$-value threshold of 0.05 for the claim of new
discoveries seems too lax in terms of the evidential value that a finding at
this threshold provides. We saw in Section~\ref{sec4:IC} that an ordinary
$p$-value needs to be at least as small as $p \leq 0.0056$ for a finding to be
intrinsically credible in terms of the $p$-value for intrinsic credibility
$\pIC \leq 0.05$. A $p$-value of 0.0056 corresponds to $\abs{z} = 2.77$ where
the Bayes factor for intrinsic credibility is $\BFIC = 1/5.7$, indicating at
least ``substantial'' evidence against the null hypothesis according to
Jeffreys. To achieve intrinsic credibility at the level for strong evidence
($\gamma = 1/10$) the requirements are even more stringent as the $z$-value
needs to be at least $\abs{z} \geq 3.15$ (equivalent to
$\mbox{minBF} \leq 1/27$, $p \leq 0.002$, or $\pIC \leq 0.026$).

\subsection{Advocacy priors}
A natural question is whether we can also define an advocacy prior, a prior
which renders an uncompelling finding compelling, in the AnCred framework with
Bayes factors. In traditional AnCred, advocacy priors always exist since one can
always find a prior that, when combined with the data, can overrule them. This
is fundamentally different to inference based on Bayes factors, where the prior
is not synthesized with the data, but rather used to predict them. A classical
result due to \citet{Edwards1963} states that if we consider the class of all
possible priors under $H_1$, the minimum Bayes factor is given by
\begin{equation}\label{eq4:ELSminBF}
  \text{minBF}_{01} = \exp\left\{-z^2/2\right\}
\end{equation}
which is obtained for $H_1$: $\theta = \hat{\theta}$. This implies that a
non-compelling finding can not be ``rescued'' further than to this bound. For
example, for the finding from the REMAP-CAP trial the bound is unsatisfactorily
$\text{minBF}_{01} = 1/1.7$, so at most ``worth a bare mention'' according to
the classification from \citet{Jeffreys1961}.

Putting these considerations aside, we may still consider the class of
$\Nor(\mu, \tau^2)$ priors under the alternative $H_1$. The Bayes factor
contrasting $H_0$ to $H_1$ is then given by
\begin{align*}
  \BF_{01}
  &= \sqrt{1 + \tau^2/\sigma^2} \cdot \exp\left\{-\frac{1}{2}\left[
  \frac{\hat{\theta}^2}{\sigma^2} - \frac{(\hat{\theta} - \mu)^2}{\sigma^2 +
  \tau^2}\right]\right\}.
\end{align*}
The Reverse-Bayes approach now determines the prior mean $\mu$ and variance
$\tau^2$ which lead to the Bayes factor $\BF_{01}$ being just at some cut-off
$\gamma$. However, if both parameters are free, there are infinitely many
solutions to $\BF_{01} = \gamma$, if any exist at all. The traditional AnCred
framework resolves this by restricting the class of possible priors to advocacy
priors with fixed coefficient of variation of
$\text{CV} = \tau/\mu = 1/z_{\alpha/2}$. We can translate this idea to the Bayes
factor AnCred framework and fix the prior's coefficient of variation to
$\text{CV} = 1/z(\gamma)$, where
\begin{align}
  z(\gamma) = \sqrt{- 2 \, \log \gamma}, \label{eq4:zgamma}
\end{align}
obtained by solving \eqref{eq4:ELSminBF} for $z$ with
$\text{minBF}_{01} = \gamma$. The advocacy prior thus carries the same
evidential weight as data with $\text{minBF}_{01} = \gamma$. Moreover, the
determination of the prior parameters becomes more feasible since there is only
one free parameter left (either $\mu$ or $\tau^2$).

The right plot in Figure \ref{fig4:bf} illustrates application of the procedure
on data from the meta-analysis on association between COVID-19 mortality and
corticosteroids. The coefficient of variation of the advocacy prior is fixed to
$\text{CV} = 1/z(\gamma=1/3) = 0.67$ (for comparison, the CV of the advocacy
prior in traditional AnCred at $\alpha = 0.05$ is
$\text{CV} = 1/z_{\alpha/2}= 0.51$) and thus the Bayes factor $\BF_{01}$ only
depends on the relative mean $f = \mu/\hat{\theta}$. Under the sceptical prior
only the RECOVERY finding could be challenged at $\gamma = 1/3$ (where
$z(\gamma)=1.5$ corresponds to $\alpha=13$\%). With the advocacy prior this is
now also possible for the CAPE COVID finding \citep{Dequin2020}, where a prior
with mean $\mu = f \cdot \hat{\theta} = 0.37 \cdot (-0.79) = -0.29$ and standard
deviation $\tau = \text{CV} \cdot \mu = 0.2$ is able to make the finding
compelling at $\gamma = 1/3$. The corresponding prior credible interval for the
OR at level $1-\alpha$ ranges from 0.55 to 1, so advocates may still consider
the ``non-compelling'' finding as providing moderate evidence in favour of a
benefit, if external evidence supports mortality reductions in that range. Using
the prior-to-data conversion described in
Section~\ref{sec4:prior-data-translation}, the prior can be translated to a
trial with 69 events in both arms, but 206 non-events in the treatment and 182
non-events in the control arm (such that the mortality rate in the control arm
is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
unique, \eg for the CAPE COVID finding the prior with relative mean
$f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
data as just compelling at $\gamma = 1/3$. We recommend to choose the prior with
$f$ closer to zero, as it is the more conservative choice.

\section{Reverse-Bayes analysis of the False Positive Risk}
\label{sec4:p.equals}

Application of the Analysis of Credibility with Bayes factors as described in
Section \ref{sec4:bfs} assumes some familiarity with Bayes factors as measures
of evidence. \citet{Colquhoun2019} argued that very few nonprofessional users of
statistics are familiar with the notion of Bayes factors or likelihood ratios.
He proposes to quantify evidence with the \emph{false positive risk}, ``if only
because that is what most users still think, mistakenly, that that is what the
$p$-value tells them''. More specifically, \citet{Colquhoun2019} defines the
\FPR{} as the posterior probability that the point null hypothesis $H_0$ of no
effect is true given the observed $p$-value $p$, \ie $\FPR = \Pr(H_0 \given p)$.
As before, $H_0$ corresponds to the point null hypothesis $H_0\colon$
$\theta = 0$. Note also that we take the exact (two-sided) $p$-value $p$ as the
observed ``data'', regardless of whether or not it is significant at some
pre-specified level, the so-called ``$p$-equals'' interpretation of NHST
\citep{Colquhoun2017}.

$\FPR$ can be calculated based on the Bayes factor associated with $p$. For ease
of presentation we invert Bayes' theorem \eqref{eq4:eq0} and obtain
\begin{equation}\label{eq4:bayes}
      \frac{\FPR}{1-\FPR} = \frac{\Pr(H_0 \given p)}{\Pr(H_1 \given p)}
      = {\mbox{BF}_{01}} \, \frac{\Pr(H_0)}{\Pr(H_1)},
\end{equation}
where $\mbox{BF}_{01}=1/\mbox{BF}_{10}$ is the Bayes factor for $H_0$ against
$H_1$, computed directly from the observed $p$-value $p$.

The common 'forward-Bayes' approach is to compute the $\FPR$ from the prior
probability $\Pr(H_0)$ and the Bayes factor with \eqref{eq4:bayes}. However, the
prior probability $\Pr(H_0)$ is usually unknown in practice and often hard to
assess. This can be resolved via the Reverse-Bayes approach
\citep{Colquhoun2017,Colquhoun2019}: Given a $p$-value and a false positive risk
value, calculate the corresponding prior probability $\Pr(H_0)$ that is needed
to achieve that false positive risk. Of specific interest is the value FPR =
5\%, because many scientists believe that a Type-I error of 5\% is equivalent to
a FPR of 5\% \citep{Greenland2016}. This is of course not true and we follow
Example 1 from \citet{Berger1987} and use the Reverse-Bayes approach to derive
the necessary prior assumptions on $\Pr(H_0)$ to achieve FPR = 5\% with Equation
\eqref{eq4:bayes}:
\begin{equation}
  \label{eq4:prior.prob}
     \Pr(H_0) = \left[ 1 + \frac{1-\FPR}{\FPR} \cdot \mbox{BF}_{01}  \right]^{-1}.
\end{equation}

\citet{Colquhoun2017} uses a Bayes factor based on the $t$-test, but for
compatibility with the previous sections we assume normality of the underlying
test statistic. We consider Bayes factors under all simple alternatives, but
also Bayes factors under local normal priors, see \citet{Held2018} for a
detailed comparison.

Instead of working with a Bayes factor for a specific prior distribution, we
prefer to work with the minimum Bayes factor $\mbox{minBF}_{01}$ as introduced
in Section \ref{sec4:sceptical}. In what follows we will use the minimum Bayes
factor based on the $z$-test, see Section 2.1 and 2.2 in \citet{Held2018}.

Let $\mbox{minBF}_{01}$ denote the minimum Bayes factor over a specific class of
alternatives. From equation \eqref{eq4:prior.prob} we obtain the inequality
\begin{equation}\label{eq4:prior.prob2}
    \Pr(H_0) \leq \left[ 1 + \frac{1-\FPR}{\FPR} \cdot \mbox{minBF}_{01}  \right]^{-1}.
\end{equation}
The right-hand side is thus an upper bound on the prior probability $\Pr(H_0)$
for a given $p$-value to achieve a pre-specified FPR value.

There are also minBFs not based on the $z$-test statistic
as~\eqref{eq4:minBFnorm}, but directly on the (two-sided) $p$-value $p$, the
so-called ``$- e \, p \log p$'' \citep{Sellke2001} calibration
\begin{equation}
\label{eq4:sbb}
{\mbox{minBF}} =  \left\{ \begin{array}{ll} - e \, p \log p & \mbox{ for } p < 1/e \\
  1 & \mbox{ otherwise, } \end{array}   \right.
\end{equation}
and the ``$- e \, q \log q$'' calibration, where $q = 1-p$, see Section 2.3 in
\citet{Held2018}:
\begin{equation}
\label{eq4:sbb2}
{\mbox{minBF}} =  \left\{ \begin{array}{ll} - e \, (1-p) \log (1-p) & \mbox{ for } p < 1-1/e \\
  1 & \mbox{ otherwise. } \end{array}   \right.
\end{equation}
For small $p$, equation \eqref{eq4:sbb2} can be simplified to
${\mbox{minBF}} \approx e \, p$, which mimics the \citet{Good1958}
transformation of $p$-values to Bayes factors \citep{Held2019b}.

The two $p$-based calibrations carry less assumptions than the minimum Bayes
factors based on the $z$-test under normality and can be used as alternative
expressions in~\eqref{eq4:prior.prob2}. The ``$- e \, p \log p$'' provides a
general bound under all unimodal and symmetrical local priors for $p$-values
from $z$-tests, see Section 3.2 in \citet{Sellke2001}. The ``$- e \, q \log q$''
calibration is more conservative and gives a smaller bound on the Bayes factor
than the ``$- e \, p \log p$'' calibration. It can be viewed as a general lower
bound under simple alternatives where the direction of the effect is taken into
account, see Section 2.1 and 2.3 in \citet{Held2018}.

\begin{figure}[!htb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
{\centering \includegraphics[width=\maxwidth]{images/paper4/FPR-plot-1}
}
\end{knitrout}
\caption{The left plot shows the upper bound on the prior probability $\Pr(H_0)$
  to achieve a false positive risk of 5\% as a function of the $p$-value
  calibrated with either a $z$-test calibration (simple or local alternatives)
  or with the ``$- e \, p \log p$'' or ``$- e \, q \log q$'' calibrations,
  respectively. The right plot shows the upper bound on $\Pr(H_0)$ as a function
  of the $p$-value using the same calibrations but assuming the $p$-value equals
  the $\FPR$.}
\label{fig4:fpr}
\end{figure}

The left plot in Figure \ref{fig4:fpr} shows the resulting upper bound on the
prior probability $\Pr(H_0)$ as a function of the two-sided $p$-value if the FPR
is fixed at 5\%. For $p=0.05$, the ``$- e \, p \log p$'' bound is around 11\%
and 28\% for the ``$- e \, q \log q$'' calibration. The corresponding values
based on the $z$-test are slightly smaller (10\% and 15\%, respectively). All
the probabilities are below the 50\% value of equipoise, illustrating that
borderline significant result with $p \approx 0.05$ do not provide sufficient
evidence to justify an FPR value of 5\%. For $p=0.005$, the upper bounds are
closer to 50\% (37\% for local and 57\% for simple alternatives).

Turning again to the example from the RECOVERY trial, the $p$-value associated
with the estimated treatment effect is $p = 0.0002$. The left plot in Figure
\ref{fig4:fpr} shows that the false positive risk can safely be assumed to be
around 5\% (or lower), since the upper bound on $\Pr(H_0)$ are all very large
for such a small $p$-value.

Fixing FPR at the 5\% level may be considered as arbitrary. Another widespread
misconception is the belief that the FPR is equal to the $p$-value.
\citet{Held2013} used a Reverse-Bayes approach to investigate which prior
assumptions are required such that $\FPR=p$ holds. Combining
\eqref{eq4:prior.prob} with the ``$- e \, p \log p$'' calibration
\eqref{eq4:sbb} gives the explicit condition
\begin{equation*}
  \Pr(H_0) \leq 1/\left\{ 1 - e \, (1-p) \, \log(p) \right\}
\end{equation*}
whereas the ``$- e \, q \log q$'' calibration \eqref{eq4:sbb2} leads to
\begin{equation*}
  \Pr(H_0) \leq 1/\left\{ 1 - e \, \frac{(1-p)^2}{p} \, \log(1-p) \right\} \approx 1/\left\{ 1 + e \, (1-p) \right\},
\end{equation*}
which is approximately $1/(1+e)=26.9$\% for small $p$.

The right plot in Figure \ref{fig4:fpr} compares the bounds based on these two
calibrations with the ones obtained from simple respectively local alternatives.
We can see that strong assumptions on $\Pr(H_0)$ are needed to justify the claim
$\FPR=p$: $\Pr(H_0)$ cannot be larger than 15.2\% if the $p$-value is
conventionally significant ($p<0.05$). For $p<0.005$, the bound drops further to
11.4\%. Even under the conservative ``$- e \, q \log q$'' calibration, the upper
bound on $\Pr(H_0)$ is $26.9$\% for small $p$ and increases only slightly for
larger values of $p$. This illustrates that the misinterpretation $\FPR=p$ only
holds if the prior probability of $H_0$ is substantially smaller than 50\%, an
assumption which is questionable in the absence of strong external knowledge.

\section{Discussion}

\subsection{Extensions, work in progress and outlook}
\label{sec4:extensions}
The Reverse-Bayes methods described above have focused on the comparison of the
prior needed for credibility with findings from other studies and/or more
general insights. However, replication studies make an obvious additional source
of external evidence, as these are typically conducted to confirm original
findings by repeating their experiments as closely as possible. The question is
then whether the original findings have been successfully ``replicated'',
currently of considerable concern to the research community. To date, there
remains no consensus on the precise meaning of replication in a statistical
sense. The proposal of \citet{Held2020} \citep[see also][]{Held2021} was to
challenge the original finding using AnCred, as described in Section
\ref{sec4:AnCred}, and then evaluate the plausibility of the resulting prior
using a prior-predictive check on the data from a replication study. A similar
procedure but using AnCred based on Bayes factors as in Section \ref{sec4:bfs}
was proposed in \citet{Pawel2020b}. Reverse-Bayes inference seems to fit
naturally into this setting as it provides a formal framework to challenge and
substantiate scientific findings.

Apart from using data from a replication study, there are also other possible
extensions of AnCred: We proposed to derive Reverse-Bayes priors using posterior
tail probabilities (or credible intervals) or Bayes factors as measures of
evidence, but also other measures such as relative belief ratios
\citep{Evans2015} could be used. When testing point null hypotheses, relative
belief ratios are equivalent to Bayes factors due to the Savage-Dickey density
ratio \citep[p. 98]{Evans2015}. Therefore, determining the sceptical prior
variance through fixing the resulting Bayes factor is equivalent to fixing the
resulting relative belief ratio. However, there is no connection to relative
belief in prior-data conflict assessment based on the Bayes factor contrasting
the sceptical to the optimistic prior since both are composite. Further research
is needed on Reverse-Bayes procedures in the relative belief framework,
candidate methods for prior-data conflict assessment are prior to posterior
divergence \citep{Nott2020} and prior expansions \citep{Nott2021} as these
methods have an interpretation in terms of relative beliefs. Moreover, we either
used prior-predictive checks \citep{Box1980, Evans2006} or Bayes-factors
\citep{Jeffreys1961, Kass1995} for the formal evaluation of the plausibility of
the priors derived through Reverse-Bayes. Other methods could be used for this
purpose, for example, Bayesian measures of surprise \citep{Bayarri2003}.
Furthermore, AnCred in its current state is derived assuming a normal likelihood
for the effect estimate $\hat{\theta}$. This is the same framework as in
standard meta-analysis and provides a good approximation for studies with
reasonable sample size \citep{Carlin1992}. For the comparison of binomial
outcomes with small counts, the normal approximation of the log odds ratio could
be improved with a Yates continuity correction \citep[section
2.4.1]{Spiegelhalter2004} or replaced with the exact profile likelihood of the
log odds ratio \citep[section 5.3]{Held2014}, see also Section 4 in
\citet{Pawel2020b} which shows AnCred with Bayes factors using either a
non-central $t$ or a Binomial likelihood. Likewise, the conjugate normal prior
could be replaced by a more robust prior distribution such as a mixture of
normals (as considered in Section~\ref{sec4:nonSigAnCred}), a
double-exponential, or a Student $t$-distribution \citep{Pericchi1992}. For
example, \citet{Fuquene2009} investigate the use of robust priors in an
application to binomial data from a randomized controlled trial. In general, any
distribution from the location-scale family can be used, whereby the scale
parameter takes over the role of the sceptical prior standard deviation, while
the location parameter is fixed to the null value.

\subsection{Conclusions}
The inferential advantages of Bayesian methods are increasingly recognised
within the statistical community. However, among the majority of working
researchers they have failed to make any serious headway, and retain a
reputation for complex and ``controversial''. We have outlined how an idea that
began with Jack Good's proposal for resolving the ``Problem of Priors'' over 70
years ago \citep{Good1950} has experienced a renaissance over recent years. The
basic idea is to invert Bayes' theorem: a specified posterior is combined with
the data to obtain the Reverse-Bayes prior, which is then used for further
inference. This approach is useful in situations where it is difficult to decide
what constitutes a reasonable prior, but easy to specify the posterior which
would lead to a particular decision. A subsequent prior-to-data conversion
\citep{Greenland2006} helps to assess the weight of the Reverse-Bayes prior in
relation to the actual data.

We have shown that the Reverse-Bayes methodology is useful to extract more
insights from the results typically reported in a meta-analysis. It facilitates
the computation of prior-predictive checks for conflict diagnostics
\citep{Presanis2013} and has been shown capable of addressing many common
inferential challenges, including assessing the credibility of scientific
findings \citep{Spiegelhalter2004,Greenland2011}, making sense of ``out of the
blue'' discoveries with no prior support \citep{Matthews2018, Held2019a},
estimating the probability of successful replications \citep{Held2019a,
  Held2020}, and extracting more insight from standard $p$-values while reducing
the risk of misinterpretation \citep{Held2013,Colquhoun2017,Colquhoun2019}. The
appeal of Reverse-Bayes techniques has recently been widened by the development
of inferential methods using both posterior probabilities and Bayes Factors
\citep{Carlin1996, Pawel2020b}.

These developments come at a crucial time for the role of statistical methods in
research. Despite the many serious -- and now well-publicised – inadequacies of
NHST \citep{Wasserstein2016}, the research community has shown itself to be
remarkably reluctant to abandon NHST. Techniques based on the Reverse-Bayes
methodology of the kind described in this review could encourage the wider use
of Bayesian inference by researchers. As such, we believe they can play a key
role in the scientific enterprise of the 21\textsuperscript{th} century.

\section*{Software and Data Availability}
All analyses were performed in the R programming language version 4.2.2
\citep{R}. Minimum Bayes factors were computed using the package
\texttt{pCalibrate} \citep{Held2018}. The package \texttt{metafor}
\citep{Viechtbauer2010} was used for meta-analysis and forest plots. Data and
code to reproduce all analyses are available at
\url{https://gitlab.uzh.ch/samuel.pawel/Reverse-Bayes-Code}.

\section*{Acknowledgments}
We are grateful to Sander Greenland for helpful comments on a previous version
of this article. We also acknowledge detailed comments by an Associate Editor
and two referees, that helped to improve the manuscript.

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}
\section{Mean of the advocacy prior}
\label{app:app1}
Suppose that the estimate $\hat \theta$ is not significant at level $\alpha$, so
$z^2/z_{\alpha/2}^2<1$. With $U,L = \hat \theta \pm z_{\alpha/2} \, \sigma$ we
have $U + L = 2 \, \hat \theta$,
$U L = \hat \theta^2 - z_{\alpha/2}^2 \, \sigma^2$ and $U-L =
2 \, z_{\alpha/2} \, \sigma$.

We therefore obtain with \eqref{eq4:AL}:
\begin{equation*}
\mu = \frac{\mbox{AL}}{2} =  - \frac{2 \, \hat \theta}{2 \, (\hat \theta^2 - z_{\alpha/2}^2 \, \sigma^2)} \frac{(2 \, z_{\alpha/2} \, \sigma)^2}{2}
 =  \frac{2 \, \hat \theta \, z_{\alpha/2}^2 \, \sigma^2}{z_{\alpha/2}^2 \, \sigma^2 - \hat \theta^2}
 =  \frac{2 \, \hat \theta}{1 - z^2/z_{\alpha/2}^2}.
\end{equation*}
Dividing by the effect estimate $\hat{\theta}$ leads to the relative mean
$f = \mu/\hat{\theta}$ as in~\eqref{eq4:mu}. The advocacy standard deviation is
$\tau = {\mbox{AL}}/{(2 \, z_{\alpha/2})} = {\mu}/{z_{\alpha/2}}$ and the
coefficient of variation is therefore
$\mbox{CV} = \tau/\mu = z_{\alpha/2}^{-1}$.

\section{Bayes factor for intrinsic credibility}
\label{app:BFIC}
Intrinsic credibility at level $\gamma$ is established when
\begin{align}
  \label{eq4:ic-condition}
  \BF_{12} \leq \BF_{01} = \gamma
\end{align}
and we are interested in the Bayes factor for intrinsic credibility $\BFIC$
which is the smallest level $\gamma \in (0, 1]$ where~\eqref{eq4:ic-condition}
holds. The $\BFIC$ is therefore a special case of the sceptical Bayes factor
from \citet{Pawel2020b} where the same data is used in both Bayes factors
(instead of the data from a replication study for $\BF_{12}$). It is hence given
by
\begin{align}
  \label{eq4:BFic}
  \BFIC =
  \begin{cases}
    \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
    & \text{if} \abs{z} \geq \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\}\\
    \mbox{minBF}_{01} \
    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\} \\
    \text{undefined}
    & \text{if} ~ \abs{z} < \sqrt{\log 2}
  \end{cases}
\end{align}
with $k = W(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $W(\cdot)$ the branch of the
Lambert $W$ function that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0).$ If
$\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at
the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative prior
variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
$\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$
for all $g$ and hence $\BFIC$ is given by $\mbox{minBF}_{01}$, the minimum of
$\BF_{01}$ from \eqref{eq4:minBFnorm}. Finally, when $\abs{z} < \sqrt{\log 2}$,
equation~\eqref{eq4:ic-condition} cannot be satisfied for any valid sufficiently
sceptical relative prior variance $g$, hence the $\BFIC$ is undefined.

\end{subappendices}

\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

### 2022-11-30 abstract.tex
some fixes

@@
 reverse-Bayes method for quantifying replication success. The key idea is to
-challenge the finding from the original study with a sceptical prior so that the
-resulting posterior provides no longer evidence for the finding from the study.
-While the original proposal defined evidence through tail probabilities, the
+challenge the data from the original study with a sceptical prior so that the
+resulting posterior no longer provides evidence for the finding from the study.
+While the proposed method defined evidence through tail probabilities, the
 extension developed here replaces them with Bayes
@@
 We find that the extended method combines two notions of replicability: It
-ensures that original and replication study independently provide evidence for
-an effect while also ensuring that their effect estimates are compatible.
-Compared to the original method, the extension also avoids a statistical paradox
-which the original method suffered from.
+requires that original and replication study independently provide evidence for
+an effect and ensures that their effect estimates are compatible. The extended
+method also avoids a statistical paradox which the proposed method suffered
+from.
 % Bayes factors have a more
@@
 % sceptical Bayes factor.
-The second extensions recalibrates the original procedure to produce more
-appropriate inferences in terms of effect size. % from the relative effect size
+Another extension proposed in this thesis recalibrates the proposed method to
+produce more appropriate inferences in terms of effect
+size. % from the relative effect size
 % perspective
-The recalibration is chosen such that for borderline significant original
-studies, replication success can only be achieved if the replication effect
-estimate is larger than the original one. The recalibrated procedure has good
-frequentist properties comparable to the standard method used in practice. The
-third extension provides a framework for Bayesian design of replication studies
-which allows for combining the data from the original study with external
+The recalibration is chosen such that for original studies which were borderline
+significant, replication success can only be achieved if the replication effect
+estimate is larger than the original one. The recalibrated method has good
+frequentist properties comparable to standard methods used in practice. The
+third and last extension provides a framework for Bayesian design of replication
+studies which allows for combining data from the original study with external
 knowledge. External knowledge, such as data from other studies, is ubiquitous in
-the replication setting and it can potentially lead to more efficient designs
-compared to classical approaches that cannot take it into account.
+the replication setting and taking it into account can potentially lead to more
+efficient designs compared to classical approaches.
 
-The second part of the thesis is concerned with reverse-Bayes approaches in
-general. The reverse-Bayes idea was first proposed in the 1950s, but it has
-mostly been forgotten. To increase awareness and show potential use cases,
-reverse-Bayes history and methods are summarized in a comprehensive review. The
-review includes also some new results on connections between revere-Bayes
-methods and meta-analysis. Finally, a commentary paper on a recently proposed
-reverse-Bayes method draws connections to other reverse-Bayes methods.
+The second part of the thesis is concerned with reverse-Bayes methodology. The
+reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
+forgotten. To increase awareness and show potential use cases, reverse-Bayes
+history and methods are summarized in a comprehensive review. The review
+includes also some new results on connections between revere-Bayes methods and
+meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
+method draws connections to other reverse-Bayes methods.
 
@@
 applied research. These practices can similarly harm methodological research,
-but this is often not recognized. To raise awareness, an illustrative simulation
+but are often not recognized. To raise awareness, an illustrative simulation
 study is conducted in which it is shown how a novel method can easily be

### 2022-11-30 intro.Rnw
some fixes

@@
 example, how can we know if the protective effect of a vaccine found in a study
-is real? The answer to such questions is of highest importance to scientists and
-decision makers, but typically we can never know for sure as any study result
-comes with uncertainty.
-
-% the sad truth is that we can never know for sure.
-
-One way to come a little closer to the truth, however, is to repeat that
-original study with new subjects. Such a \emph{replication study} may yield
-similar results which would make us more confident about the original finding,
-or it may yield conflicting results which would lower our confidence.
-Replication studies are thus an essential part of the scientific process as they
-provide a means for substantiating genuine research findings and refuting
-research findings which occurred merely by chance. For this reason,
-``successful'' replication is often a requirement, for example, for acceptance
-of newly proposed scientific theories (\eg{} a new physical model) or the
-implementation of policies based on scientific knowledge (\eg{} market approval
-of a drug). The results from replication studies may thus have real world
-consequences, such as deciding whether we receive the recommendation to get
-vaccinated (a consequence that anyone who experienced the COVID-19 pandemic is
-very aware of).
+is real? The answer to such questions is of high importance to scientists and
+decision makers. However, because any study result comes with uncertainty we can
+never know for sure.
+
+One way to come a little closer to the truth is to repeat the original study
+with new subjects. Such a \emph{replication study} may yield similar results
+which would make us more confident about the original finding, or may yield
+conflicting results which would lower our confidence. Replication studies are
+thus an essential part of the scientific process as they provide a means for
+substantiating genuine research findings and refuting research findings which
+occurred merely by chance. For this reason, ``successful'' replication is often
+a requirement, for example, for acceptance of newly proposed scientific theories
+(\eg{} a new physical model) or the implementation of policies based on
+scientific knowledge (\eg{} market approval of a drug). The results from
+replication studies may thus have real world consequences, such as deciding
+whether we receive the recommendation to get vaccinated (a consequence that
+anyone who experienced the COVID-19 pandemic is very aware of).
 
@@
 
-The perceived value of replication studies, however, has changed over the past
-decade. Earlier criticisms of low research standards \citep{Altman1994,
-  Ioannidis2005} were backed up by empirical evidence. For instance,
-pharmaceutical companies reported surprisingly low replication rates from
-pre-clinical research \citep{Begley2012} followed by later studies estimating
-that %\$28 billion
+The perceived value of replication studies has changed over the past decade.
+Earlier criticisms of low research standards \citep{Altman1994, Ioannidis2005}
+were backed up by empirical evidence. For instance, pharmaceutical companies
+reported surprisingly low replication rates from pre-clinical research
+\citep{Begley2012} followed by later studies estimating that %\$28 billion
 billions are wasted each year on flawed and non-replicable research in medicine
@@
 practices \citep{Wagenmakers2011, Simmons2011, John2012} sparked intense
-discussion about the need for higher research standards in psychology and the
+discussion about the need for better research standards in psychology and the
 social sciences. These discussions eventually culminated in large-scale
@@
 \citep{Camerer2016}, the social sciences \citep{Camerer2018}, experimental
-philosophy \citep{Cova2018}, or cancer biology \citep{Errington2021}.
+philosophy \citep{Cova2018}, and cancer biology \citep{Errington2021}.
 
@@
 % field of psychology,
-various reforms were implemented to safe the reputation of science and to
-prevent an escalation of the situation \citep[for an overview see
-\eg{}][]{Munafo2017}. For instance, many journals adopted the ``registered
-report'' format \citep{Chambers2021} in which a study proposal is peer reviewed
-\emph{before} the study is conducted, and which, if accepted, gives provisional
-publication acceptance regardless of the study outcome. Similarly, digital
-infrastructure platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open
-Science Framework (\url{https://osf.io/}), were created to facilitate
-preregistration, preprints, and code and data sharing, all of which have
-substantially increased over the last decade \citep{Kidwell2016, Nosek2018,
-  Rawlinson2019}. The practice of conducting replication studies has also gained
-popularity, and several academic journals and funders are now explicitly
-promoting and funding replication research \citep{NWO2016, NSL2018, Nature2022}.
-Figure~\ref{fig:scholar} illustrates this trend via the yearly number of results
-for ``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
-that the numbers have been rapidly growing, especially after the mid 2000s (with
-a minor drop in 2021, perhaps because of research slowing down due to the
+various reforms were implemented to prevent an escalation of the situation and
+save the reputation of science \citep[for an overview see \eg{}][]{Munafo2017}.
+For instance, many journals adopted the ``registered report'' format
+\citep{Chambers2021} in which a study proposal is peer reviewed \emph{before}
+the study is conducted, and which, if accepted, gives provisional publication
+acceptance regardless of the study outcome. Similarly, digital infrastructure
+platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open Science
+Framework (\url{https://osf.io/}), were created to facilitate preregistration,
+preprints, code and data sharing, all of which have substantially increased over
+the last decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of
+conducting replication studies has also gained popularity. Several academic
+journals and funders are now explicitly promoting replication research
+\citep{NWO2016, NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this
+trend via the yearly number of results for the search term
+``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
+that the numbers have been rapidly growing, especially after the mid 2000s, with
+a minor drop in 2021 (perhaps because of research slowing down due to the
 COVID-19 pandemic).
@@
     the standard normal distribution is denoted by
-    $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and $p$-values
-    are based on the normality assumption.}
+    $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and
+    \textit{p}-values are based on the normality assumption.}
   \label{tab:meta}
@@
 size $\theta$ (for large enough sample sizes) is justified. This could be, for
-instance, the Fisher $z$-transformation for correlations, or the
+instance, the Fisher $z$-transformation for correlations or the
 log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
@@
 been used if more than one replication study of the same original study are
-conducted since in this case replicators are often interested in also
-understanding between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
+conducted since replicators are often interested in understanding
+between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
 
@@
 replication standardized mean difference effect estimates along with standard
-errors, and only these data will be used in the subsequent analyses.
+errors, and only they will be used in the subsequent analyses.
 
@@
 Figure~\ref{fig:upset} shows how many of the replications are successful
-according to the criteria from Table~\ref{tab:rsdef}, and their combinations.
-For the total 132 replications, most successes occur for the meta-analytic
-significance (\Sexpr{nma}) and the prediction interval criteria (\Sexpr{npi}),
-followed by significance (\Sexpr{nsig}), and relative effect size
+according to the criteria from Table~\ref{tab:rsdef} (except the confidence
+interval criteria since they do not take into account the uncertainty from both
+studies). For the total 132 replications, most successes occur for the
+meta-analytic significance (\Sexpr{nma}) and the prediction interval criteria
+(\Sexpr{npi}), followed by significance (\Sexpr{nsig}), and relative effect size
 (\Sexpr{nres}). However, looking at the combinations of the criteria, only in
-two replications are all of them satisfied simultaneously (green).
+two replications are all criteria satisfied simultaneously (green).
 
@@
     confidence intervals, variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$,
-    relative effect estimate $d = \that_{r}/\that_{o}$, original $p$-value
-    $p_{o}$, replication $p$-value $p_{r}$, meta-analytic $p$-value $p_{m}$,
-    $Q$-test $p$-value $p_{Q}$, and sceptical $p$-value $p_{\mathrm{S}}$. A
-    level $\alpha = 5\%$ is used as threshold for replication success via
-    $p$-values, and a threshold $d_{\text{min}} = 1$ for the relative effect
-    estimate.}
+    relative effect estimate $d = \that_{r}/\that_{o}$, original
+    \textit{p}-value $p_{o}$, replication \textit{p}-value $p_{r}$,
+    meta-analytic \textit{p}-value $p_{m}$, $Q$-test \textit{p}-value $p_{Q}$,
+    and sceptical \textit{p}-value $p_{\mathrm{S}}$. A level $\alpha = 5\%$ is
+    used as threshold for replication success via \textit{p}-values, and a
+    threshold $d_{\text{min}} = 1$ for the relative effect estimate.}
   \label{tab:RPCB}
@@
 meaning that the \emph{prior distribution} for the parameter $\theta$ with
-density/probability mass function $f(\theta)$ is multiplied by the (normalized)
+probability density/mass function $f(\theta)$ is multiplied by the (normalized)
 likelihood of the data, also know as \emph{Bayesian updating}. Parameter values
@@
 it with the data, and end up with a posterior, the reverse-Bayes approach starts
-with the posterior and ends up with the prior. Reverse-Bayes inference then
-revolves around the question of whether the resulting prior is plausible in
-light of external knowledge, and if so, this could be seen as support for the
-specified posterior.
+with the posterior and ends up with the prior. For example, the posterior may be
+specified to indicate evidence for/against a particular hypothesis under
+investigation. Reverse-Bayes inference then revolves around the question of
+whether the resulting prior is plausible in light of external knowledge, and if
+so, this could be seen as support for the specified posterior.
 
@@
 $\theta$, representing the position of a sceptic who does not believe in the
-presence of a non-zero effect. The ``stubbornness'' of the sceptic is determined
+presence of a genuine effect. The ``stubbornness'' of the sceptic is determined
 by how large the variance $\tau^{2}$ is chosen. Combining the sceptical prior
-with the likelihood produces then a posterior which is again normal
+with the likelihood produces a posterior which is again normal
 $\theta \given \that_{o}, \sigma_{o} \sim \Nor(\mu_{\text{post}}, \sigma^{2}_{\text{post}})$
@@
 evidence\footnote{For readers who do not agree with this notion of evidence, do
-  not panic. In this thesis (Paper I and III) we extend this reverse-Bayes
+  not panic. In this thesis (Paper I and IV) we extend this reverse-Bayes
   procedure to use alternative measures of evidence, such as Bayes factors.} for
@@
   with \Sexpr{100*(1-alpha)}\% confidence/credible interval. The original finding is
-  challenged with a ``sceptical'' prior, sufficiently concentrated around zero so
+  challenged with a sceptical prior, sufficiently concentrated around zero so
   that the resulting posterior is no longer convincing at level
-  $\alpha = \Sexpr{100*(alpha)}\%$. Prior predictive $p$-values $p_{\text{Box}}$ are
+  $\alpha = \Sexpr{100*(alpha)}\%$. Prior predictive \textit{p}-values $p_{\text{Box}}$ are
   computed for quantifying prior-data conflict.}
@@
 $\that_{o} = \Sexpr{round(to, 2)}$ and standard error
-$\sigma_{o} = \Sexpr{round(so, 2)}$. We see that a sufficiently sceptical prior
-with variance $\tau_{\alpha}^{2} = \Sexpr{round(sprior, 2)}^{2}$ is required to
-render the resulting posterior no longer convincing at level
-$\alpha = \Sexpr{round(100*alpha, 2)}$\%.
+$\sigma_{o} = \Sexpr{round(so, 2)}$. We see that the sufficiently sceptical
+prior with variance $\tau_{\alpha}^{2} = \Sexpr{round(sprior, 2)}^{2}$ produces
+a posterior with $1 - \alpha = \Sexpr{round(100*(1 - alpha), 2)}\%$ credible
+interval fixed to zero, so that the original finding is rendered no longer
+convincing at level $\alpha = \Sexpr{round(100*alpha, 2)}$\%.
 
@@
 $|z_{o}| \leq z_{\alpha/2}$) the sufficiently sceptical prior variance is
-undefined meaning that the data provide so little evidence on their own that no
-scepticism is required to make them unconvincing.
+undefined meaning that the data provide so little evidence that no scepticism is
+required to make them unconvincing.
 
@@
   = \Pr\left\{f(\text{data} \given \text{M}) <
-  f(\text{observed data} \given \text{M})\right\},
+  f(\text{observed data} \given \text{M})\right\}.
   \label{eq:pppval}
 \end{align}
-that is, the probability of obtaining data with lower predictive density (``more
-surprising'' data) than the observed data. The lower the $p$-value
-$p_{\text{Box}}$, the more incompatibility between the observed data and the
-assumed model M. This approach was used by \citet{Held2020}, and it will soon
-be explained in more detail.
+The $p$-value $p_{\text{Box}}$ is the probability of obtaining data with lower
+predictive density (``more surprising'' data) than the observed data, and the
+lower $p_{\text{Box}}$, the more incompatibility between the observed data and
+the assumed model M. This approach was used by \citet{Held2020}.
 % The literature on Bayesian model criticism following \citet{Box1980} also
@@
 the observed data with the model $\text{M}_{1}$. Bayesian model criticism
-approaches based on prior predictive ratios will be used in later parts of this
+approaches based on prior predictive ratios will be used in latter parts of this
 thesis.\footnote{Some readers may have noted that the prior predictive ratio is
@@
   approach is therefore particularly useful in combination with reverse-Bayes
-  procedures based on Bayes factors, as will be demonstrated in later parts of
-  this thesis (paper I and III).}
+  procedures based on Bayes factors, as will be demonstrated later (Paper I and
+  III).}
 
@@
 Replication Project: Cancer Biology. We see that larger effect estimates show
-prior predictive $p$-values $p_{\text{Box}}$, indicating more prior-data
+smaller prior predictive $p$-values $p_{\text{Box}}$, indicating more prior-data
 conflict. This is because the standard errors from all three replications are
@@
 % ``successful''.
-\citet{Held2020} then defined replication success at level $\alpha$ by
+\citet{Held2020} defined replication success at level $\alpha$ by
 \begin{align*}
-  p_{\text{Box}} \leq \alpha,
+  p_{\text{Box}} \leq \alpha.
 \end{align*}
-that is, replication success is established if there is more conflict between
+In words, replication success is established if there is more conflict between
 the sceptical prior and the replication data than there was evidence against the
@@
 To remove the dependence on the level $\alpha$, \citet{Held2020} proposed to
-determine the smallest level at which replication success can be established. He
-called this level the \emph{sceptical $p$-value} $p_{\text{S}}$, and showed that
-it is available in closed-form
+determine the smallest level at which replication success can be established.
+This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and
+available in closed-form
 \begin{align*}
@@
 $d = \that_{r}/\that_{o}$ decreases, the sceptical $p$-value increases, meaning
-that shrinkage of the replication effect estimate is penalized. The sceptical
-$p$-value hence requires \emph{both} studies to be sufficiently convincing on
-their own (in terms of their $p$-values), similarly to the significance
-criterion for replication success. Unlike the significance criterion, however,
-if the $p$-values remain fixed but the replication effect estimate $\that_{r}$
-becomes smaller than the original estimate $\that_{o}$, the sceptical $p$-value
-indicates less replication success. This property is desirable in the
+that shrinkage of the replication effect estimate is penalized
+($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$ and $p_{r}$).
+Because of the first property, the sceptical $p$-value requires \emph{both}
+studies to be sufficiently convincing on their own (in terms of their
+$p$-values), similar to the significance criterion for replication success.
+However, unlike the significance criterion, if the $p$-values remain fixed but
+the replication effect estimate $\that_{r}$ becomes smaller than the original
+estimate $\that_{o}$, the sceptical $p$-value becomes larger so indicates less
+replication success due to the second property. This is desirable in the
 replication setting as a smaller replication effect estimate $\that_{r}$ may not
@@
 sceptical $p$-value, even though the replication study was highly convincing
---the effect estimate was almost five times as large as in the original study.
+(the effect estimate was almost five times as large as in the original study).
 Yet, as the approach requires both studies to be convincing on their own -- and
@@
 illustrated by the fifth study from above (1, 3, 5). Here the original study was
-convincing and also the replication study achieved significance. However, the
+convincing and the replication study also achieved significance. However, the
 effect estimate from the replication was roughly 60\% smaller than the one from
 the original study, and significance is merely achieved because the standard
-error was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times). The
-sceptical $p$-value is therefore only $p_{\text{S}} = 0.25$, indicating hardly
-any replication success.
+error was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller).
+The sceptical $p$-value is therefore only $p_{\text{S}} = 0.25$, indicating
+hardly any replication success.
 
@@
 replication studies. The second part (Paper IV and V) revolves around
-reverse-Bayes methodology in general. Paper IV is a review paper about
-reverse-Bayes methodology and Paper V is a short comment on another article
-which proposed a reverse-Bayes method. The last part (Paper VI) is about
-integrity issues methodological research with simulations
-studies. % The article lists and illustrates questionable
+reverse-Bayes methodology in general. % Paper IV is a review paper about
+% reverse-Bayes methodology and Paper V is a short comment on another article
+% which proposed a reverse-Bayes method.
+The last part (Paper VI) is about integrity issues in methodological research
+with simulations studies. % The article lists and illustrates questionable
 % research practices in simulation studies, and gives recommendations how to avoid
@@
 \subsection{Design and analysis of replication studies}
+% The research from this parts extends
 
@@
 \eg{}][]{Berger1987, Casella1987, Royall1997, Berger2003, Benjamin2017,
-  Lakens2018, Amrhein2019b}. In this paper, we therefore extend the
-reverse-Bayes assessment of replication studies to use Bayes factors
-\citep{Good1958, Jeffreys1961} for quantifying evidence and prior-data
+  Lakens2018, Amrhein2019b}. In this paper, we extend the reverse-Bayes
+assessment of replication studies to use Bayes factors \citep{Good1958,
+  Jeffreys1961} for quantifying evidence and prior-data
 conflict. % Bayes factors are also
 % used for prior-data conflict assessment as suggested by \citep{Box1980}.
-Similarly to the sceptical $p$-value, the procedure leads to a single measure
-for quantifying the degree of replication success, \emph{the sceptical Bayes
-  factor}. Systematic comparisons show that the sceptical Bayes factor shares
-most properties with the sceptical $p$-value due to the reverse-Bayes approach
-underlying both methods, yet in some situations conclusions may differ because
-of their different ways of quantifying evidence. Specifically, it is shown that
-the sceptical $p$-value suffers from a certain type of ``shrinkage paradox'',
-which is avoided by the sceptical Bayes factor; when the $p$-value from the
-original study goes to zero, replication success based on the sceptical
-$p$-value can be achieved with any arbitrarily small replication effect
-estimate, whereas replication success based on the sceptical Bayes factor poses
-a finite limit on how much shrinkage is allowed. Technically, the procedure is
-more involved and closed-form solutions for the sceptical Bayes factor are only
-available in special situations. % and in terms of the
+Similar to the sceptical $p$-value, the procedure leads to a single measure for
+quantifying the degree of replication success, \emph{the sceptical Bayes
+  factor}. Systematic comparisons show that the sceptical Bayes factor has
+similar properties as the sceptical $p$-value due to the reverse-Bayes approach
+underlying both methods (\eg{} it penalizes shrinkage of the replication effect
+estimate and requires compelling evidence from both studies). However, it is
+also shown that the sceptical $p$-value suffers from a certain type of
+``shrinkage paradox'', which is avoided by the sceptical Bayes factor; when the
+$p$-value from the original study goes to zero, replication success based on the
+sceptical $p$-value can be achieved with any arbitrarily small replication
+effect estimate, whereas replication success based on the sceptical Bayes factor
+poses a finite limit on how much shrinkage is allowed. Technically, the
+procedure is more involved and closed-form solutions for the sceptical Bayes
+factor are only available in special situations. % and in terms of the
 % ``Lambert W function'' \citep{Corless1996}.
@@
 details, including closed-form solution for the sceptical Bayes factors,
-asymptotic properties, type-I and type-II error rates, and non-normal extensions
-of the procedure. I wrote the initial draft of the manuscript and the R package.
+asymptotic properties, type-I and type-II error rates, and non-normal
+extensions. I wrote the initial draft of the manuscript and the R package.
 Throughout, L. Held gave high-level feedback. I presented initial results at the
@@
 International Biometric Society) in 2020. L. Held presented the final results at
-the world meeting of the ISBA (International Society for Bayesian Analysis) in
-2021.
+the ISBA (International Society for Bayesian Analysis) world meeting 2021.
 
@@
 replication projects \citep{Opensc2015, Camerer2016, Camerer2018, Cova2018}
-illustrate the properties of the method.
+illustrate the properties of the method. This extension is now implemented as
+the default option in the R package \texttt{ReplicationSuccess} available on
+CRAN (\url{https://cran.r-project.org/package=ReplicationSuccess}).
 
@@
 calculations for the sceptical $p$-value and the sceptical Bayes factor. In
-paper I, I already derived the power function of the sceptical Bayes factor in
+Paper I, I already derived the power function of the sceptical Bayes factor in
 closed-form for two types of design priors. After its completion, I generalized
@@
 discovered the connection between the Analysis of Credibility and the fail-safe
-N method, L. Held suggested that it would fit nicely into this manuscript, and
+$N$ method, L. Held suggested that it would fit nicely into this manuscript, and
 that I should start to overhaul it. I rewrote and expanded his initial draft,
 adding also a new section on reverse-Bayes approaches with Bayes factors,
-largely based on the work from paper I. We then managed to recruit R. Matthews
+largely based on the work from Paper I. We then managed to recruit R. Matthews
 to also contribute. From that point on the three of us iteratively worked on the
@@
 
-Shortly after the acceptance of paper III, the article by \citet{Sondhi2021}
+Shortly after the acceptance of Paper III, the article by \citet{Sondhi2021}
 appeared. It proposed a novel reverse-Bayes method called \emph{Bayesian
@@
 to write a commentary. We show that -- contrary to the statement by
-\citet{Sondhi2021} -- there is a closed form solution for the key quantity in
+Sondhi et al. -- there is a closed form solution for the key quantity in
 their approach termed ``Bayesian Additional Evidence tipping point''.
@@
 studies have remained low over the years \citep{Hoaglin1975, Burton2006,
-  Morris2019}. Moreover, some authors have recently argued that also
-methodological research is suffering from reproducibility issues, publication
-bias, and a ``replication crisis'' due to researchers engaging in questionable
-research practices, such as selective reporting \citep{Boulesteix2020}. In this
-article, we raise awareness about these issues. We summarize possible
-questionable research practices in simulation studies, and show how easy it is
-make a method seem superior if various questionable research practices are
-employed. We also give recommendations to alleviate these issues, most
-importantly we recommend researchers write and pre-register simulation
-protocols.
+  Morris2019}. Moreover, some authors have recently argued that methodological
+research is suffering from reproducibility issues, publication bias, and a
+``replication crisis'' due to researchers engaging in questionable research
+practices, such as selective reporting \citep{Boulesteix2020}. In this article,
+we raise awareness of these issues. We summarize possible questionable research
+practices in simulation studies, and show how easy it is make a method seem
+superior if various questionable research practices are employed. We also give
+recommendations to alleviate these issues. Most importantly we recommend
+researchers write and pre-register simulation protocols.
 

### 2022-11-30 paper1.tex
ie and eg

@@
 $d = \that_r/\that_o = z_r/(z_o\sqrt{c})$. For many effect size types the
-variances are inversely proportional to the sample size, \ie
+variances are inversely proportional to the sample size, \ie{}
 $\sigma^2_{o} = \kappa/n_{o}$ and $\sigma^2_{r} = \kappa/n_{r}$ for some unit
@@
 data, rather than their underlying samples, and assume that
-$\that_k \given \theta \sim \Nor(\theta, \sigma^2_k)$ for $k \in \{o, r\},$ \ie
+$\that_k \given \theta \sim \Nor(\theta, \sigma^2_k)$ for $k \in \{o, r\},$ \ie{}
 normality of the effect estimates around $\theta$, with known variances equal to
@@
 (``Fisher-$z$'' transformation). We refer to the literature of meta-analysis for
-details about transformations of effect sizes \citep[\eg][Chapter
+details about transformations of effect sizes \citep[\eg{}][Chapter
 11.6]{Cooper2019}. The normal model in combination with conjugate priors enables
@@
 derived priors, which combined with the observed data, would lead to posterior
-inferences that were specified beforehand (\eg the data favour one hypothesis
+inferences that were specified beforehand (\eg{} the data favour one hypothesis
 over another). His reverse-Bayes inference then centred around the question
@@
 derived from the data. Inference is subsequently carried out based on this
-reverse-Bayes prior, \eg the interest is often to check whether the prior is
+reverse-Bayes prior, \eg{} the interest is often to check whether the prior is
 plausible in light of external evidence, an obvious candidate being data from a
@@
           $$\BFcol{\mathrm{S}}{\mathrm{A}}(\that_r; \gy) \leq \gamma,$$
-          \ie the data favour the advocate over the sceptic at a higher level
+          \ie{} the data favour the advocate over the sceptic at a higher level
 than the sceptic's initial objection.
@@
 Further increasing the relative sceptical prior variance increases
-\eqref{eq1:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie
+\eqref{eq1:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie{}
 $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \to \infty$ for $g \to \infty$
@@
 From Figure \ref{fig1:bfo} we can see that the more compelling the original data
-(\ie the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
+(\ie{} the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
 variance $\gy$ needs to be in order to make the result no longer convincing at
@@
 priors only from the class of priors that become increasingly concentrated for
-increasing evidence (\ie priors with $\gy \leq \gminBFo$). In principle, the
+increasing evidence (\ie{} priors with $\gy \leq \gminBFo$). In principle, the
 solution $\gy^\prime > \gminBFo $ could also be computed by replacing the
@@
 that the replication was not successful at level $\gamma = 1/10$.
-However, if we had chosen a less stringent level, \eg$\gamma =
+However, if we had chosen a less stringent level, \eg{}$\gamma =
 1/3$, the replication would have been considered successful
@@
 evidence against the null, but also default Bayes factors have been used
-\citep[see \eg the Bayesian supplement of][]{Camerer2018}. To compare the
+\citep[see \eg{} the Bayesian supplement of][]{Camerer2018}. To compare the
 two-trials rule with methods based on Bayes factors we will study the two-trials
-rule based on the minimum Bayes factor from~\eqref{eq1:minBFo}, \ie replication
+rule based on the minimum Bayes factor from~\eqref{eq1:minBFo}, \ie{} replication
 success at level $\gamma$ is established when both
@@
 Bayes factor is smaller than the minimum Bayes factor from the replication study
-(\eg when $\minBF_{o} = 1/2$,
+(\eg{} when $\minBF_{o} = 1/2$,
 $\minBF_{r} = 1/1.5$, and $c = 1$
@@
 from~\eqref{eq1:Qstat} appears in~\eqref{eq1:BFrep} and acts as a penalty term,
-\ie larger values of $Q$ lower the degree of replication success. However, in
+\ie{} larger values of $Q$ lower the degree of replication success. However, in
 contrast to the sceptical Bayes factor, the replication Bayes factor is not
@@
 Bayes factor, the sceptical $p$-value always exists and there are closed form
-expressions to compute it for all values of $c$, \ie
+expressions to compute it for all values of $c$, \ie{}
 $\ps = 1 - \Phi(z_{\mathrm{S}})$ with
@@
 In practice, the replication paradox is hardly an issue, since replications
-rarely show such contradictory results, \eg to achieve replication success at
+rarely show such contradictory results, \eg{} to achieve replication success at
 level $\gamma = 1/3$ with
@@
 is more prone to the paradox because its point-null hypothesis fails more
-strongly to predict estimates in opposite direction, \eg for the same numbers as
+strongly to predict estimates in opposite direction, \eg{} for the same numbers as
 before it requires $d < -2.66$.
@@
 such that only effects in the same direction as the original estimate $\that_o$
-have non-zero probability, \ie for positive $\that_{o}$ consider
+have non-zero probability, \ie{} for positive $\that_{o}$ consider
 $\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \, \mathbb{1}_{(0, \infty)}(\theta)$,
@@
 to be closer to 50\% in all cases. As can also be seen, if the original result
-was not convincing on its own (\eg if $z_o = 1.5$ or $z_{o} = 2$), it is
+was not convincing on its own (\eg{} if $z_o = 1.5$ or $z_{o} = 2$), it is
 impossible to achieve replication success with the two-trials rule, the
@@
 $\sigma^2_r$. This may be a problem for studies with small sample size and/or
-extreme results (\eg when a study examines a rare disease with death rates close
+extreme results (\eg{} when a study examines a rare disease with death rates close
 to 0\%). One way of dealing with this issue is to consider the exact likelihood
@@
 The SMD quantifies how many standard deviation units $\sigma$, the means $\mu_1$
-and $\mu_2$ of measurements from two groups differ, \ie
+and $\mu_2$ of measurements from two groups differ, \ie{}
 $$\theta = \frac{\mu_1 - \mu_2}{\sigma}.$$
@@
 distribution
-%% \ie $\text{NCT}_\nu(t; \theta \sqrt{n^*}) = \int
+%% \ie{} $\text{NCT}_\nu(t; \theta \sqrt{n^*}) = \int
 %% \Nor(t; \theta \sqrt{n^*\tau^2}, \tau^2) \text{IG}(\tau^2; \nu/2, \nu/2) d\tau^2$
@@
 factor is the only method in our comparison which does not suffer from any form
-of the shrinkage paradox, \ie replication success can never be achieved with
+of the shrinkage paradox, \ie{} replication success can never be achieved with
 arbitrarily small replication effect estimates, not even when the replication
@@
 just one but several replication studies are conducted for one original study
-\citep[\eg as in][]{Klein2014}. The Bayesian framework allows to easily extend
+\citep[\eg{} as in][]{Klein2014}. The Bayesian framework allows to easily extend
 the sceptical Bayes factor to the ``many-to-one'' replication setting as the
@@
 
-\section{The Lambert $W$ function}
+\section{The Lambert \textit{W} function}
 \label{appendix:lambertW}

### 2022-11-30 paper2.tex
added paper 4
ie and eg

@@
 errors of the original and replication effect estimates. The squared standard
-errors are usually inversely proportional to the sample size of each study, \ie
+errors are usually inversely proportional to the sample size of each study, \ie{}
 $\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
@@
 success is based on significance of the replication effect estimate at the same
-level $\alpha$, \ie the replication is considered successful if also
+level $\alpha$, \ie{} the replication is considered successful if also
 $p_r \leq \alpha$. This approach is known in drug development as the two-trials
@@
 $\dmin$, a function of $K$ and the relative sample size $c$. If the relative
-sample size becomes very large, \ie $c \rightarrow \infty$, we have
+sample size becomes very large, \ie{} $c \rightarrow \infty$, we have
 $\dmin \downarrow \dinfty$ where
@@
 The condition $p_S \leq \alpha_S$ for replication success at the golden level is
-equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie
+equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
 $z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
@@
 estimate is handled. Figure~\ref{fig2:fig2} illustrates that
-shrinkage is penalized in the assessment of replication success, \ie
+shrinkage is penalized in the assessment of replication success, \ie{}
 the original $p$-value needs to be quite small to achieve replication
@@
 practice, however, there are often good reasons to believe that original effect
-estimates have a tendency to be inflated (\eg due to publication bias). One way
+estimates have a tendency to be inflated (\eg{} due to publication bias). One way
 to address this issue is to base power calculations on a shrunken version of the
@@
 asymptotically normal with variance which is only a function of the study sample
-size $n$, \ie $\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}.
+size $n$, \ie{} $\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}.
 
@@
   \label{tbl:discrep}
-% \resizebox{\textwidth}{!} {
+\resizebox{\textwidth}{!} {
 % latex table generated in R 4.0.5 by xtable 1.8-4 package
@@
    \bottomrule
-\end{tabular}
-
-% }
+\end{tabular}%
+}
 \end{table}
@@
 more robust distributional assumptions could be considered. Second, in some
-types of analyses (\eg regression or ANOVA) the effect estimate is a vector and
+types of analyses (\eg{} regression or ANOVA) the effect estimate is a vector and
 the approach would need suitable adaptations. Third, there is a recent trend to
 not only conduct one but several replications for one original study
-\citep[\eg][]{Klein2014, Ebersole2016, Klein2018}. Also for this situation, the
-method would need to be adapted, \eg the replication estimates could be first
+\citep[\eg{}][]{Klein2014, Ebersole2016, Klein2018}. Also for this situation, the
+method would need to be adapted, \eg{} the replication estimates could be first
 synthesized and an analysis of replication success could be performed

### 2022-11-30 paper4.tex
ie and eg

@@
 \end{equation}
-\ie the posterior odds are the likelihood ratio times the prior odds. The
+\ie{} the posterior odds are the likelihood ratio times the prior odds. The
 standard 'forward-Bayes' approach thus fixes the prior odds (or one of the
@@
 \end{align}
-provided $\delta' > \kappa$, \ie the posterior precision must be larger than the
+provided $\delta' > \kappa$, \ie{} the posterior precision must be larger than the
 observational precision.
@@
 \label{sec4:nonSigAnCred}
-It is also possible to challenge ``non-significant'' findings (\ie those for
+It is also possible to challenge ``non-significant'' findings (\ie{} those for
 which the CI now includes zero, so $z^2 < z_{\alpha/2}^2$) using a prior that
@@
 no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
-limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie $0.15$ on the
+limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{} $0.15$ on the
 odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
@@
 where $n$ is the number of non-events in the arm used to support the null
-hypothesis (\eg the control arm in an RCT). With the control arm event rate
+hypothesis (\eg{} the control arm in an RCT). With the control arm event rate
 $R = m/(m + n)$ constrained to match that of the actual study, we find
@@
 outside the corresponding sceptical prior interval $[-\SL, \SL]$ extracted using
-Reverse-Bayes from the finding itself, \ie $\hat{\theta}^2 > \SL^2$ with $\SL$
+Reverse-Bayes from the finding itself, \ie{} $\hat{\theta}^2 > \SL^2$ with $\SL$
 given in \eqref{eq4:S}. Matthews showed this implies an unprecedented finding is
@@
 finding (with $p$-value $p=0.0002$) cited earlier is $\pIC = 0.01$ and thus the
-probability of the replication effect going in the same direction (\ie reduced
+probability of the replication effect going in the same direction (\ie{} reduced
 mortality in this case) is $0.995$. In contrast, the finding from the smaller
@@
 sceptical prior at a higher level than they support the sceptical prior over the
-null hypothesis, \ie if
+null hypothesis, \ie{} if
 \begin{align*}
@@
 is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
-unique, \eg for the CAPE COVID finding the prior with relative mean
+unique, \eg{} for the CAPE COVID finding the prior with relative mean
 $f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
@@
 \FPR{} as the posterior probability that the point null hypothesis $H_0$ of no
-effect is true given the observed $p$-value $p$, \ie $\FPR = \Pr(H_0 \given p)$.
+effect is true given the observed $p$-value $p$, \ie{} $\FPR = \Pr(H_0 \given p)$.
 As before, $H_0$ corresponds to the point null hypothesis $H_0\colon$

### 2022-11-30 paper5.tex
ie and eg

@@
 results in a posterior credible interval which excludes the null value. If the
-substantive hypothesis is for positive effect estimates (\eg
+substantive hypothesis is for positive effect estimates (\eg{}
 $\log(\mbox{HR}) > 0$) the BAE is the prior mean which leads to the lower limit
@@
 Thus additional evidence in the form of prior insight or a subsequent
-replication supporting an HR at least as impressive as this (\ie an
+replication supporting an HR at least as impressive as this (\ie{} an
 $\mbox{HR} < 0.52$ in this case), and a CI at least as tight as that of the
@@
 exist. An alternative rationale would be to set the mean of the additional
-evidence, rather than variance, to that of the original finding (\ie
+evidence, rather than variance, to that of the original finding (\ie{}
 $\mu = \hat{\theta}$), and determining the prior variance $\tau^{2}$ such that

### 2022-12-01 abstract.tex
suggestions from Charlotte

@@
 
-The first and largest part of this thesis extends a recently proposed
-reverse-Bayes method for quantifying replication success. The key idea is to
-challenge the data from the original study with a sceptical prior so that the
-resulting posterior no longer provides evidence for the finding from the study.
-While the proposed method defined evidence through tail probabilities, the
-extension developed here replaces them with Bayes
-factors. % The sceptical prior is now
-% determined such that the original finding is no longer convincing in terms of a
-% Bayes factor. In contrast to tail probabilities,
+The first and largest part of this thesis consists of three extensions of a
+recently proposed reverse-Bayes method for quantifying replication success. The
+key idea of the method is to challenge the data from the original study with a
+sceptical prior so that the resulting posterior no longer provides evidence for
+the finding from the study. The first extension recalibrates the proposed method
+to produce more appropriate inferences in terms of effect size.
+% from the relative effect size perspective
+The recalibration is chosen such that for original studies which were borderline
+significant, replication success can only be achieved if the effect estimate
+from the replication study is larger than the estimate from the original study.
+The recalibrated method has good frequentist properties comparable to standard
+methods used in practice. The second extension replaces tail probabilities with
+Bayes factors as measures of evidence.
+% The sceptical prior is now determined such that the original finding is no
+% longer convincing in terms of a Bayes factor. In contrast to tail
+% probabilities,
 We find that the extended method combines two notions of replicability: It
@@
 an effect and ensures that their effect estimates are compatible. The extended
-method also avoids a statistical paradox which the proposed method suffered
-from.
+method also avoids a statistical paradox which the initial method suffered from.
 % Bayes factors have a more
@@
 % sceptical Bayes factor.
-Another extension proposed in this thesis recalibrates the proposed method to
-produce more appropriate inferences in terms of effect
-size. % from the relative effect size
-% perspective
-The recalibration is chosen such that for original studies which were borderline
-significant, replication success can only be achieved if the replication effect
-estimate is larger than the original one. The recalibrated method has good
-frequentist properties comparable to standard methods used in practice. The
-third and last extension provides a framework for Bayesian design of replication
-studies which allows for combining data from the original study with external
-knowledge. External knowledge, such as data from other studies, is ubiquitous in
-the replication setting and taking it into account can potentially lead to more
-efficient designs compared to classical approaches.
+The third and last extension provides a framework for Bayesian design of
+replication studies which allows for combining data from the original study with
+external knowledge. External knowledge, such as data from other studies, is
+ubiquitous in the replication setting and taking it into account can potentially
+lead to more efficient designs compared to classical approaches.
 
-The second part of the thesis is concerned with reverse-Bayes methodology. The
+The second part of the thesis is also concerned with reverse-Bayes methodology
+but with a wider ranger of applications than only replication studies. The
 reverse-Bayes idea was first proposed in the 1950s, but it has mostly been

### 2022-12-01 intro.Rnw
nicer toc
suggestions from Charlotte

@@
 \phantomsection
-\addcontentsline{toc}{chapter}{Introduction}
+\addcontentsline{toc}{chapter}{\texorpdfstring{\phantom{IV}Introduction}{Introduction}}
 
@@
 example, how can we know if the protective effect of a vaccine found in a study
-is real? The answer to such questions is of high importance to scientists and
-decision makers. However, because any study result comes with uncertainty we can
-never know for sure.
+is real? The answer to such questions is of high importance to scientists,
+decision makers, and the general population. However, because any study result
+comes with uncertainty we can never know for sure.
 
@@
 thus often had no other choice than to concentrate their efforts on producing
-novel and eye-catching research results.
+novel and eye-catching research results \citep{Martin2017}.
 
@@
 
-\subsection{The statistics of replication studies}
+\subsection{Statistical aspects of replication studies}
 Despite the increased interest in replication studies, the research community
@@
 the effect estimate $\that$. It provides an estimate of the underlying effect
-size $\theta$ which quantifies the effect or association of an
+size $\theta$ which quantifies the true effect or association of an
 intervention/exposure with an outcome variable. Typical effect sizes are mean
@@
   depending on the direction of combined estimate.} Typically, the assumption of
-a common underlying effect size is seen as reasonable so that fixed-effects
+a common underlying effect size is seen as reasonable so that fixed-effect
 meta-analysis is used for pooling. Random-effects meta-analysis has primarily
@@
 example, the relative effect estimate $d = \that_{r}/\that_{o}$ quantifies how
-much the replication effect estimate changed compared to the original, and the
-smaller $d$ is the smaller the degree of replication success. Some projects also
-report a confidence interval for $d$ \citep{Camerer2016, Camerer2018}, while
-others ignore its uncertainty and make a binary cut at $d_{\text{min}} = 1$ to
-define replication success \citep{Errington2021}. The criteria based on
-confidence and prediction intervals define effect size compatibility on an
-absolute scale. However, the criterion based on the original confidence interval
-ignores the uncertainty from the replication, whereas the criterion based on the
-replication confidence interval ignores the uncertainty from the original study.
-The prediction interval criterion takes into account both sources of uncertainty
-\citep{Patil2016}. Yet, declaring ``replication success'' based on the
-prediction interval may be logically questionable due to its connection to the
-meta-analytic $Q$-test.
+much the magnitude of the replication effect estimate changed compared to the
+original, and the smaller $d$ is the smaller the degree of replication success.
+Some projects also report a confidence interval for $d$ \citep{Camerer2016,
+  Camerer2018}, while others ignore its uncertainty and make a binary cut at
+$d_{\text{min}} = 1$ to define replication success \citep{Errington2021}. The
+criteria based on confidence and prediction intervals define effect size
+compatibility on an absolute scale. However, the criterion based on the original
+confidence interval ignores the uncertainty from the replication, whereas the
+criterion based on the replication confidence interval ignores the uncertainty
+from the original study. The prediction interval criterion takes into account
+both sources of uncertainty \citep{Patil2016}. Yet, declaring ``replication
+success'' based on the prediction interval may be logically questionable due to
+its connection to the meta-analytic $Q$-test.
 % as it may also be seen as an instance of the ``absence of evidence fallacy''
@@
 project attempted to replicate 53 landmark studies from the field of cancer
-biology. However, due to various difficulties (\eg{} missing information from
-the original studies or problems in conducting the experiments) only 23 of the
-53 studies could be repeated. \citet{Errington2021} report that these
-experiments led to data on 158 quantitative effects. However, from the data
-which they provide only 132 quantitative effects are provided with original and
-replication standardized mean difference effect estimates along with standard
-errors, and only they will be used in the subsequent analyses.
+biology but due to various difficulties (\eg{} missing information from the
+original studies or problems in conducting the experiments) only 23 of the 53
+studies could be repeated. \citet{Errington2021} report that these experiments
+led to data on 158 quantitative effects. However, from the data which they
+provide only 132 quantitative effects are provided with original and replication
+standardized mean difference effect estimates along with standard errors, and
+only they will be used in the subsequent analyses.
 
@@
            dFormat = ifelse(d > 1,
-                            paste0("\\textcolor{nicegreen}{", round(d, 2),
-                                   "}"),
-                            paste0("\\textcolor{red}{", round(d, 2), "}")),
+                            paste0("\\textcolor{nicegreen}{$", round(d, 2),
+                                   "$}"),
+                            paste0("\\textcolor{red}{$", round(d, 2), "$}")),
            cioL = smdo - za*so,
@@
                              paste0("\\textcolor{red}{", pFormat(pQ), "}")),
-           smdoFormat = paste(format(round(smdo, 2), nsmall = 2),
-                              ciFormat(lower = cioL, upper = cioU)),
-           smdrFormat = paste(format(round(smdr, 2), nsmall = 2),
-                              ciFormat(lower = cirL, upper = cirU)),
-           smdmFormat = paste(format(round(smdm, 2), nsmall = 2),
-                              ciFormat(lower = cimL, upper = cimU)),
+           smdoFormat = paste("$", format(round(smdo, 2), nsmall = 2),
+                              ciFormat(lower = cioL, upper = cioU), "$"),
+           smdrFormat = paste("$", format(round(smdr, 2), nsmall = 2),
+                              ciFormat(lower = cirL, upper = cirU), "$"),
+           smdmFormat = paste("$", format(round(smdm, 2), nsmall = 2),
+                              ciFormat(lower = cimL, upper = cimU), "$"),
            rsig = factor(pr2 <= 0.05, levels = c(FALSE, TRUE),
@@
 A detailed view for a subset of the data from the project is given in
-Table~\ref{tab:RPCB}. For no single study pair in the table are all commonly
-used criteria satisfied simultaneously. For instance, the two pairs (48, 2, 1)
-and (16, 3, 3) at the top of the table satisfy the significance criterion
+Table~\ref{tab:RPCB}. The subset is chosen such that from every original study
+one effect and one replication of that effect is included. For no single study
+pair in the table are all commonly used criteria satisfied simultaneously. For
+instance, the first two replications satisfy the significance criterion
 ($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic significance ($p_{m} < 0.05$)
@@
 Similarly, there is no single study pair for which all criteria indicate
-replication failure. For example, the pair (5, 1, 3) at the bottom of the table
-is a clear failure with respect to the relative effect estimate ($d < 1$) and
-the significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test
-does not indicate evidence for inconsistency of the two effect estimates
-($p_{Q} > 0.05$).
+replication failure. For example, the last replication (\#20) is a clear failure
+with respect to the relative effect estimate ($d < 1$) and the significance
+criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does not indicate
+evidence for inconsistency of the two effect estimates ($p_{Q} > 0.05$).
 
@@
     na.omit() |>
-    filter(smdo < 80, smdr < 80) |>
+    ## filter(smdo < 80, smdr < 80) |>
     group_by(paper) |>
@@
     arrange(pr2) |>
-    select(id, smdoFormat, ## so,
+    select(id,
+           smdoFormat, ## so,
            smdrFormat, smdmFormat,
@@
                           )
-print(rpcbXtable, booktabs = TRUE, floating = FALSE, include.rownames = FALSE,
+print(rpcbXtable, booktabs = TRUE, floating = FALSE, include.rownames = TRUE,
       sanitize.text.function = function(x) {x},
@@
 evidence\footnote{For readers who do not agree with this notion of evidence, do
-  not panic. In this thesis (Paper I and IV) we extend this reverse-Bayes
+  not panic. In this thesis (Paper II and IV) we extend this reverse-Bayes
   procedure to use alternative measures of evidence, such as Bayes factors.} for
@@
                     show.legend = FALSE) +
-    annotate("segment", x = 1.85, y = -0.5, xend = 1.98, yend = -0.05,
+    annotate("segment", x = 1.81, y = -0.5, xend = 1.97, yend = -0.05,
              alpha = 0.6,
@@
              label = paste0(round(100*alpha/2, 2), "% quantile fixed at zero")) +
+    annotate("segment", x = 2.8, y = -0.5, xend = 2.96, yend = -0.05,
+             alpha = 0.6,
+             arrow = arrow(type = "closed", length = unit(0.02, "npc"))) +
+    annotate("text", x = 2.75, y = -0.6, size = 3, alpha = 0.6,
+             label = "fixed at zero") +
     annotate("segment", x = 1.6, y = 2.25, xend = 2.7, yend = 2.25,
@@
   approach is therefore particularly useful in combination with reverse-Bayes
-  procedures based on Bayes factors, as will be demonstrated later (Paper I and
-  III).}
+  procedures based on Bayes factors, as will be demonstrated later (Paper II and
+  IV).}
 
@@
 both $p$-values have to be smaller than $\alpha$ such that replication success
-based on $p_{\text{S}} \leq \alpha$ is possible. Second, if the $p$-values
-$p_{o}$ and $p_{r}$ remain fixed but the relative effect estimate
-$d = \that_{r}/\that_{o}$ decreases, the sceptical $p$-value increases, meaning
-that shrinkage of the replication effect estimate is penalized
-($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$ and $p_{r}$).
-Because of the first property, the sceptical $p$-value requires \emph{both}
-studies to be sufficiently convincing on their own (in terms of their
-$p$-values), similar to the significance criterion for replication success.
-However, unlike the significance criterion, if the $p$-values remain fixed but
-the replication effect estimate $\that_{r}$ becomes smaller than the original
-estimate $\that_{o}$, the sceptical $p$-value becomes larger so indicates less
-replication success due to the second property. This is desirable in the
-replication setting as a smaller replication effect estimate $\that_{r}$ may not
-be practically relevant anymore, despite its statistical significance.
+at level $\alpha$ is possible. The sceptical $p$-value hence requires
+\emph{both} studies to be sufficiently convincing on their own (in terms of
+their $p$-values), similar to the significance criterion for replication
+success. Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the
+relative effect estimate $d = \that_{r}/\that_{o}$ decreases, the sceptical
+$p$-value increases, meaning that shrinkage of the replication effect estimate
+is penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$
+and $p_{r}$). The sceptical $p$-value thus takes effect shrinkage into account,
+unlike the significance criterion which can be achieved with any non-zero
+replication effect estimate $\that_{r}$ provided the standard error $\sigma_{r}$
+is small enough. This property is desirable in the replication setting as a
+smaller replication effect estimate $\that_{r}$ may not be practically relevant
+anymore, despite its statistical significance.
 
 The results from the Reproducibility Project: Cancer Biology in
-Table~\ref{tab:RPCB} illustrate these two properties. The third study from above
-(19, 1, 2) fails to achieve replication success at level $\alpha = 5\%$ with the
-sceptical $p$-value, even though the replication study was highly convincing
-(the effect estimate was almost five times as large as in the original study).
-Yet, as the approach requires both studies to be convincing on their own -- and
-the original study was not significant at the 5\% level -- replication success
-at this level is impossible with the sceptical $p$-value. The second property is
-illustrated by the fifth study from above (1, 3, 5). Here the original study was
-convincing and the replication study also achieved significance. However, the
-effect estimate from the replication was roughly 60\% smaller than the one from
-the original study, and significance is merely achieved because the standard
-error was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller).
-The sceptical $p$-value is therefore only $p_{\text{S}} = 0.25$, indicating
-hardly any replication success.
+Table~\ref{tab:RPCB} illustrate these two properties. The third study fails to
+achieve replication success at level $\alpha = 5\%$ with the sceptical
+$p$-value, even though the replication study was highly convincing (the effect
+estimate was almost five times as large as in the original study). Yet, as the
+approach requires both studies to be convincing on their own -- and the original
+study was not significant at the 5\% level -- replication success at this level
+is impossible with the sceptical $p$-value. The second property is illustrated
+by the fifth study. Here the original study was convincing and the replication
+study also achieved significance. However, the effect estimate from the
+replication was roughly 60\% smaller than the one from the original study, and
+significance is merely achieved because the standard error was much smaller
+(\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value
+is therefore only $p_{\text{S}} = 0.25$, indicating hardly any replication
+success.
 
@@
 one-sided version of the sceptical $p$-value, power and sample size
-calculations) can be found in the original article by \citet{Held2020}. However,
-the relevant parts of the procedure have been presented. In the following, I
-will discuss open questions and how they are addressed in this thesis.
-
-\section{Open questions and thesis contributions}
+calculations) can be found in the original article by \citet{Held2020}.
+Furthermore, the sceptical $p$-value and related methods are implemented in the
+R package \texttt{ReplicationSuccess} available on CRAN
+(\url{https://cran.r-project.org/package=ReplicationSuccess}). However, the
+relevant parts of the procedure have been presented. In the following, I will
+discuss open questions and how they are addressed in this thesis.
+
+\section{Thesis contributions}
 \label{sec:summary}
@@
 \startPaperSummary{PaperI}{%
+  The assessment of replication success based on relative effect size}{%
+  Leonhard Held, Charlotte Micheloud, Samuel Pawel \\
+  \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
+  \url{https://doi.org/10.1214/21-AOAS1502}.}
+
+It is not clear how to interpret the sceptical $p$-value as it is not an
+ordinary $p$-value (which has a uniform distribution under the corresponding
+null hypothesis). Moreover, when the same level $\alpha$ as for the significance
+criterion is used for dichotomizing the sceptical $p$-value, this leads to a
+much more stringent criterion for replication studies than the significance
+criterion, and many studies which intuitively seem successful will not satisfy
+it.
+
+In this article, we therefore look closer at the ``success region'' of the
+sceptical $p$-value in terms of the relative effect estimate
+$d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a new
+default level for thresholding the sceptical $p$-value called the \emph{golden
+  level} $\alpha_{G}$ (named ``golden'' because the golden ratio appears in its
+derivation). The golden level is defined through the property that for an
+original study which was borderline significant ($p_{o} = \alpha$), replication
+success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if the
+replication effect estimate is at least as large as the original one
+($d \geq 1$). For instance, for the significance level $\alpha = 5\%$, the
+corresponding golden level is $\alpha_{G} = 12.3\%$. The behavior of the golden
+level seems to align with common sense: for original studies which were already
+convincing (in terms of their $p$-value) the effect estimate in the replication
+study is allowed to shrink, to some extent, whereas for less convincing original
+studies (those with $p$-values around the significance level) shrinkage is more
+strongly penalized. We find that for replication studies with equal or larger
+sample size than the original study, replication success based on the golden
+level also has similar or improved frequentist properties (type-I error rate and
+project power) compared to the standard significance criterion. Case studies
+from four large-scale replication projects \citep{Opensc2015, Camerer2016,
+  Camerer2018, Cova2018} illustrate the properties of the method. This extension
+is now implemented as the default option in the R package
+\texttt{ReplicationSuccess}.
+
+L. Held had the idea to apply the sceptical $p$-value method to the data from
+the four replication projects, which I collected for my master thesis. C.
+Micheloud and L. Held came up with the golden level. L. Held wrote an initial
+draft of the manuscript. C. Micheloud, L. Held, and I then iteratively worked on
+the manuscript.
+
+\startPaperSummary{PaperII}{%
   The sceptical Bayes factor for the assessment of replication success}{%
@@
 
-\startPaperSummary{PaperII}{%
-  The assessment of replication success based on relative effect size}{%
-  Leonhard Held, Charlotte Micheloud, Samuel Pawel \\
-  \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \url{https://doi.org/10.1214/21-AOAS1502}.}
-
-It is not clear how to numerically interpret the sceptical $p$-value, as it is
-not an ordinary $p$-value (which has a uniform distribution under the
-corresponding null hypothesis). Similarly, it is unclear which threshold should
-be used in case the sceptical $p$-value needs to be dichotomized into
-replication success or failure. In this article, we therefore look closer at the
-``success region'' of the sceptical $p$-value in terms of the relative effect
-estimate $d = \that_{r}/\that_{o}$. This perspective leads to the proposal of a
-new default level for thresholding the sceptical $p$-value called the
-\emph{golden level} $\alpha_{G}$ (named ``golden'' because the golden ratio
-appears in its derivation). The golden level is defined through the property
-that for an original study which was borderline significant ($p_{o} = \alpha$),
-replication success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if
-the replication effect estimate is at least as large as the original one
-($d \geq 1$). The behavior of the golden level seems to align with common sense:
-for original studies which were already convincing (in terms of their $p$-value)
-the effect estimate in the replication study is allowed to shrink, to some
-extent, whereas for less convincing original studies (those with $p$-values
-around the significance level) shrinkage is more strongly penalized. We find
-that for replication studies with equal or larger sample size than the original
-study, replication success based on the golden level also has similar or
-improved frequentist properties (type-I error rate and project power) compared
-to the standard significance criterion. Case studies from four large-scale
-replication projects \citep{Opensc2015, Camerer2016, Camerer2018, Cova2018}
-illustrate the properties of the method. This extension is now implemented as
-the default option in the R package \texttt{ReplicationSuccess} available on
-CRAN (\url{https://cran.r-project.org/package=ReplicationSuccess}).
-
-L. Held had the idea to apply the sceptical $p$-value method to the data from
-the four replication projects, which I collected for my master thesis. C.
-Micheloud and L. Held came up with the golden level. L. Held wrote an initial
-draft of the manuscript. C. Micheloud, L. Held, and I then iteratively worked on
-the manuscript.
-
 \startPaperSummary{PaperIII}{%
@@
 calculations for the sceptical $p$-value and the sceptical Bayes factor. In
-Paper I, I already derived the power function of the sceptical Bayes factor in
+Paper II, I already derived the power function of the sceptical Bayes factor in
 closed-form for two types of design priors. After its completion, I generalized
@@
 discovered the connection between the Analysis of Credibility and the fail-safe
-$N$ method, L. Held suggested that it would fit nicely into this manuscript, and
-that I should start to overhaul it. I rewrote and expanded his initial draft,
-adding also a new section on reverse-Bayes approaches with Bayes factors,
-largely based on the work from Paper I. We then managed to recruit R. Matthews
-to also contribute. From that point on the three of us iteratively worked on the
-manuscript and M. Ott gave high-level feedback.
+$N$ method \citep{Rosenthal1979,Rosenberg2005}, L. Held suggested that it would
+fit nicely into this manuscript, and that I should start to overhaul it. I
+rewrote and expanded his initial draft, adding also a new section on
+reverse-Bayes approaches with Bayes factors, largely based on the work from
+Paper II. We then managed to recruit R. Matthews to also contribute. From that
+point on the three of us iteratively worked on the manuscript and M. Ott gave
+high-level feedback.
 

### 2022-12-01 abstract.tex
Lisa feedback

@@
 
-The first and largest part of this thesis consists of three extensions of a
+The first and largest part of this thesis consists of three extensions to a
 recently proposed reverse-Bayes method for quantifying replication success. The
@@
 sceptical prior so that the resulting posterior no longer provides evidence for
-the finding from the study. The first extension recalibrates the proposed method
-to produce more appropriate inferences in terms of effect size.
-% from the relative effect size perspective
-The recalibration is chosen such that for original studies which were borderline
-significant, replication success can only be achieved if the effect estimate
-from the replication study is larger than the estimate from the original study.
-The recalibrated method has good frequentist properties comparable to standard
-methods used in practice. The second extension replaces tail probabilities with
-Bayes factors as measures of evidence.
+the finding from the study. Replication success is then achieved if there is
+conflict between the sceptical prior and the replication data. The first
+extension recalibrates the method to produce more appropriate inferences in
+terms of effect size. The recalibration is chosen such that for original studies
+which were borderline significant, replication success can only be achieved if
+the effect estimate from the replication study is larger than the estimate from
+the original study. The recalibrated method has good frequentist properties
+comparable to standard methods used in practice. The second extension replaces
+tail probabilities with Bayes factors as measures of evidence.
 % The sceptical prior is now determined such that the original finding is no
@@
 % probabilities,
-We find that the extended method combines two notions of replicability: It
-requires that original and replication study independently provide evidence for
-an effect and ensures that their effect estimates are compatible. The extended
-method also avoids a statistical paradox which the initial method suffered from.
+% We find that the extended method combines two notions of replicability: It
+% requires that original and replication study independently provide evidence for
+% an effect and ensures that their effect estimates are compatible.
+The extended method has similar properties as the initial method but avoids a
+statistical paradox which the initial method suffers from -- in some situations
+it may flag success replication success even though the effect estimate from the
+replication is arbitrarily smaller than to the original one.
 % Bayes factors have a more
@@
 % sceptical Bayes factor.
-The third and last extension provides a framework for Bayesian design of
-replication studies which allows for combining data from the original study with
-external knowledge. External knowledge, such as data from other studies, is
-ubiquitous in the replication setting and taking it into account can potentially
-lead to more efficient designs compared to classical approaches.
+The third extension provides a framework for Bayesian design of replication
+studies which allows for combining data from the original study with external
+knowledge. External knowledge, such as data from other studies, is ubiquitous in
+the replication setting and taking it into account can lead to potentially more
+efficient designs compared to classical approaches.
 
-The second part of the thesis is also concerned with reverse-Bayes methodology
-but with a wider ranger of applications than only replication studies. The
-reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
-forgotten. To increase awareness and show potential use cases, reverse-Bayes
-history and methods are summarized in a comprehensive review. The review
-includes also some new results on connections between revere-Bayes methods and
-meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
-method draws connections to other reverse-Bayes methods.
+The second part of the thesis also deals with reverse-Bayes methods, but with a
+broader scope of applications than replication studies. The reverse-Bayes idea
+was first proposed in the 1950s, but it has mostly been forgotten. To increase
+awareness and show potential use cases, reverse-Bayes history and methods are
+summarized in a comprehensive review. The review includes also some new results
+on connections between revere-Bayes methods and meta-analysis. %  Finally, a
+% commentary paper on a recently proposed reverse-Bayes method draws connections
+% to other reverse-Bayes methods.
 
@@
 methodological research. Questionable research practices, such as selective
-reporting of results, are often seen as main cause for the low replicability in
-applied research. These practices can similarly harm methodological research,
-but are often not recognized. To raise awareness, an illustrative simulation
-study is conducted in which it is shown how a novel method can easily be
-presented as superior over established competitor methods if questionable
-research practices are employed.
+reporting of results, are often seen as main cause for replicability issues in
+the medical and social sciences. These practices can similarly harm
+methodological research, but are often not recognized. To raise awareness, an
+illustrative simulation study is conducted in which it is shown how a novel
+method can easily be presented as superior over established competitor methods
+if questionable research practices are employed.
 

### 2022-12-01 intro.Rnw
Lisa feedback

@@
   \centering
-  \includegraphics[height = 8.9cm]{images/xkcd.png}
+  \includegraphics[height = 9cm]{images/xkcd.png}
   \caption*{Replication studies as illustrated by Randall Munroe
@@
 % estimates, standard error, confidence intervals, and $p$-values
-All of these are routinely reported in researcher articles, and if one of them
-is missing they typically can, under some assumptions, be calculated from the
-others. Using summary statistics is also often the only possible way for
-conducting the replication success analysis as the raw data from the original
-study may not be available to the replicators. The most important statistic is
-the effect estimate $\that$. It provides an estimate of the underlying effect
-size $\theta$ which quantifies the true effect or association of an
-intervention/exposure with an outcome variable. Typical effect sizes are mean
-differences and correlations (for continuous outcomes), odds ratios (for binary
-outcomes), or hazard ratios (for time to event outcomes). Depending on the type
-of effect size, a transformation might be required so that the assumption of
-approximately normally distributed effect estimates around the unknown effect
-size $\theta$ (for large enough sample sizes) is justified. This could be, for
-instance, the Fisher $z$-transformation for correlations or the
-log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
-associated standard error $\sigma$ represents the statistical uncertainty of the
-estimate. Under the assumption of (asymptotic) normality, confidence intervals
-for $\theta$ and $p$-values for testing the null hypothesis
-$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
+All of these are routinely reported in research articles, and if one of them is
+missing they typically can be calculated from the others. Using summary
+statistics is also often the only possible way for conducting the replication
+success analysis as the raw data from the original study may not be available to
+the replicators. The most important statistic is the effect estimate $\that$. It
+provides an estimate of the underlying effect size $\theta$ which quantifies the
+true effect or association of an intervention/exposure with an outcome variable.
+Typical effect sizes are mean differences and correlations (for continuous
+outcomes), odds ratios (for binary outcomes), or hazard ratios (for time to
+event outcomes). Depending on the type of effect size, a transformation might be
+required so that the assumption of approximately normally distributed effect
+estimates around the unknown effect size $\theta$ (for large enough sample
+sizes) is justified. This could be, for instance, the Fisher $z$-transformation
+for correlations or the log-transformation for odds/hazard ratios \citep[chapter
+11]{Cooper2019}. The associated standard error $\sigma$ represents the
+statistical uncertainty of the estimate. Under the assumption of (asymptotic)
+normality, confidence intervals for $\theta$ and $p$-values for testing the null
+hypothesis $H_{0} \colon \theta = 0$ can be computed as shown in
+Table~\ref{tab:meta}.
 
@@
   respectively, $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$
-  depending on the direction of combined estimate.} Typically, the assumption of
-a common underlying effect size is seen as reasonable so that fixed-effect
-meta-analysis is used for pooling. Random-effects meta-analysis has primarily
-been used if more than one replication study of the same original study are
-conducted since replicators are often interested in understanding
+  depending on the direction of the combined estimate.} Typically, the
+assumption of a common underlying effect size is seen as reasonable so that
+fixed-effect meta-analysis is used for pooling. Random-effects meta-analysis has
+primarily been used if more than one replication study of the same original
+study are conducted since replicators are often interested in understanding
 between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
@@
 
-\subsubsection{Example: Reproducibility Project Cancer Biology}
+\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
 I will now illustrate the assessment of replicability on data from the
@@
 project attempted to replicate 53 landmark studies from the field of cancer
-biology but due to various difficulties (\eg{} missing information from the
-original studies or problems in conducting the experiments) only 23 of the 53
-studies could be repeated. \citet{Errington2021} report that these experiments
-led to data on 158 quantitative effects. However, from the data which they
-provide only 132 quantitative effects are provided with original and replication
-standardized mean difference effect estimates along with standard errors, and
-only they will be used in the subsequent analyses.
+biology \citep[and would perhaps therefore better be named ``Replication
+Project'', see][]{Goodman2016}. In the end, only 23 of the 53 studies could be
+repeated due to various difficulties, such as, missing information from the
+original studies or problems in conducting the experiments.
+\citet{Errington2021} report that these experiments led to data on 158
+quantitative effects. However, from the data which they provide only 132
+quantitative effects are provided with original and replication standardized
+mean difference effect estimates along with standard errors, and only they will
+be used in the subsequent analyses.
 
@@
   $\alpha = \Sexpr{round(100*alpha, 2)}\%$ and a relative effect size threshold
-  of $d_{\text{min}} = \Sexpr{dmin}$ are used.}
+  of $d_{\text{min}} = \Sexpr{dmin}$ are used for replication success (green).}
 \label{fig:upset}
@@
 retested'' in][]{Carey2015}, is a simplification of the matter.
-% that may harm the credibility of science.
 
@@
     meta-analytic \textit{p}-value $p_{m}$, $Q$-test \textit{p}-value $p_{Q}$,
-    and sceptical \textit{p}-value $p_{\mathrm{S}}$. A level $\alpha = 5\%$ is
-    used as threshold for replication success via \textit{p}-values, and a
-    threshold $d_{\text{min}} = 1$ for the relative effect estimate.}
+    and sceptical \textit{p}-value $p_{\mathrm{S}}$. A replication success
+    (green) threshold of $\alpha = 5\%$ is used for the \textit{p}-values and
+    $d_{\text{min}} = 1$ for the relative effect estimate.}
   \label{tab:RPCB}
@@
 parameters conditional on the data, called the \emph{posterior distribution}. It
-can be obtained from Bayes' theorem
+can be obtained from Bayes' theorem,
 \begin{align*}
   f(\theta \given \text{data})
-  = f(\theta) \times \frac{f(\text{data} \given \theta)}{f(\text{data})}
+  = f(\theta) \times \frac{f(\text{data} \given \theta)}{f(\text{data})},
 \end{align*}
@@
 \emph{reverse-Bayes} approach, first proposed by \citet{Good1950}, is one way of
-dealing with this issue. The idea is to reverse Bayes' theorem
+dealing with this issue. The idea is to reverse Bayes' theorem as
 \begin{align*}
@@
 presence of a genuine effect. The ``stubbornness'' of the sceptic is determined
-by how large the variance $\tau^{2}$ is chosen. Combining the sceptical prior
-with the likelihood produces a posterior which is again normal
+by how small the variance $\tau^{2}$ is chosen (the smaller $\tau^{2}$, the more
+scepticism). Combining the sceptical prior with the likelihood produces a
+posterior which is again normal
 $\theta \given \that_{o}, \sigma_{o} \sim \Nor(\mu_{\text{post}}, \sigma^{2}_{\text{post}})$
@@
 $(1 - \alpha)$ credible interval is just fixed to zero. The resulting prior then
-represent the beliefs of a sceptic who is just stubborn enough to not find the
+represents the beliefs of a sceptic who is just stubborn enough to not find the
 original study convincing at level $\alpha$.
@@
     \dfrac{\sigma^{2}_{o}}{\left(z_{o}^{2}/z_{\alpha/2}^{2}\right) - 1}
-    & \text{if} ~ z_{o}^{2} > z_{\alpha/2}^{2} \\
+    & \text{if} ~ z_{o}^{2} > z_{\alpha/2}^{2}, \\
     \text{undefined} & \text{else.}
@@
 $p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
-$p_{\text{Box}} = \Sexpr{pboxFormat[2]}$), while the conflict seems larger for
-the third one (the one with $p_{\text{Box}} = \Sexpr{pboxFormat[3]}$).
+$p_{\text{Box}} = \Sexpr{pboxFormat[2]}$), while the conflict is larger for the
+third one (the one with $p_{\text{Box}} = \Sexpr{pboxFormat[3]}$).
 
@@
 determine the smallest level at which replication success can be established.
-This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and
+This level is called the \emph{sceptical $p$-value} $p_{\text{S}}$, and it is
 available in closed-form
@@
     z^{2}_{\text{H}}/2 & \text{for} ~ c = 1 \\
-    \left\{\surd\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
-          z_{\text{H}}^{2}(c - 1)\right\}\right]
+    \left\{\left[z_{\text{A}}^{2}\left\{z_{\text{A}}^{2} +
+          z_{\text{H}}^{2}(c - 1)\right\}\right]^{1/2}
       - z_{\text{A}}^{2}\right\}/(c - 1)
@@
 have to be dichotomized in this manner, but can also be interpreted as a
-quantitative measure of replication success, the smaller $p_{\text{S}}$ the
+quantitative measure of replication success; the smaller $p_{\text{S}}$, the
 higher the degree of replication success.
 
-The sceptical $p$-value has several interesting properties \citep[section
+The sceptical $p$-value has several interesting properties \citep[Section
 3]{Held2020}: First, it is always larger than the maximum of the original and
@@
 
-This concludes the introduction to replication studies and the summary of the
-reverse-Bayes assessment of replication success. Some additional properties
-(\eg{} the null distribution of the sceptical $p$-value) and extensions (\eg{} a
-one-sided version of the sceptical $p$-value, power and sample size
-calculations) can be found in the original article by \citet{Held2020}.
-Furthermore, the sceptical $p$-value and related methods are implemented in the
-R package \texttt{ReplicationSuccess} available on CRAN
-(\url{https://cran.r-project.org/package=ReplicationSuccess}). However, the
-relevant parts of the procedure have been presented. In the following, I will
-discuss open questions and how they are addressed in this thesis.
+This concludes the introduction to replication studies and reverse-Bayes methods
+for their analysis. Some additional properties (\eg{} the null distribution of
+the sceptical $p$-value) and extensions (\eg{} a one-sided version of the
+sceptical $p$-value, power and sample size calculations) can be found in the
+original article by \citet{Held2020}. Furthermore, the sceptical $p$-value and
+related methods are implemented in the R package \texttt{ReplicationSuccess}
+available on CRAN
+(\url{https://cran.r-project.org/package=ReplicationSuccess}). % However, the
+% relevant parts of the procedure have been presented.
+In the following, I will discuss open questions and how they are addressed in
+this thesis.
 
@@
   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \url{https://doi.org/10.1214/21-AOAS1502}.}
+  \href{https://doi.org/10.1214/21-AOAS1502}{doi:~10.1214/21-AOAS1502}.}
 
@@
     Methodology)}, 2022, 84(3), 879--911.
-  \url{https://doi.org/10.1111/rssb.12491}.}
+  \href{https://doi.org/10.1111/rssb.12491}{doi:~10.1111/rssb.12491}.}
 
@@
   2022. arXiv preprint.
-  \url{https://doi.org/10.48550/arXiv.2211.02552}.}
+  \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:~10.48550/arXiv.2211.02552}.}
 
@@
 parameters. Based on this design prior, predictions about the replication data
-can then be computed, and the replication sample size can be chosen such the
-probability of replication success becomes as high as desired. We illustrate
+can then be computed, and the replication sample size can be chosen such that
+the probability of replication success becomes as high as desired. We illustrate
 Bayesian design of replication studies in the normal-normal hierarchical model
@@
 from a cross-laboratory replication project \citep{Protzko2020} are used for
-illustrating our methods, which are also available in the R package
+illustrating our methods, which are available in the R package
 \texttt{BayesRepDesign} (\url{https://github.com/SamCH93/BayesRepDesign}).
@@
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
-  \url{https://doi.org/10.1002/jrsm.1538}.}
+   \href{https://doi.org/10.1002/jrsm.1538}{doi:~10.1002/jrsm.1538}.}
 
@@
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
-  \url{https://doi.org/10.1186/s12874-022-01635-4}.}
+  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:~10.1186/s12874-022-01635-4}.}
 
@@
 % convincing?''.
-The method is also closely related the Analysis of Credibility by
+The method is also closely related to the Analysis of Credibility by
 \citet{Matthews2018}. We investigate differences and similarities of the two
@@
   2022. arXiv preprint.
-  \url{https://doi.org/10.48550/arXiv.2203.13076}.}
+  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:~10.48550/arXiv.2203.13076}.}
 
@@
 we raise awareness of these issues. We summarize possible questionable research
-practices in simulation studies, and show how easy it is make a method seem
+practices in simulation studies, and show how easy it is to make a method seem
 superior if various questionable research practices are employed. We also give
-recommendations to alleviate these issues. Most importantly we recommend
-researchers write and pre-register simulation protocols.
+recommendations to alleviate these issues. Most importantly, we recommend
+researchers to write and pre-register simulation protocols.
 

### 2022-12-01 thesis.Rnw
added paper 4
improved toc
suggestions from Charlotte
Lisa feedback

@@
 
+\changelocaltocdepth{0}
+
 \addtocontents{toc}{\bigskip}
@@
 
+\addtocontents{toc}{%
+  \protect\vspace{2ex}
+  \textbf{\textsf{Design and analysis of replication studies}}\par}
+\addtocontents{toc}{%
+  \protect\vspace{-2ex}
+  \par\noindent\rule{\textwidth}{0.4pt}\par}
+
 % Paper I
+% ------------------------------------------------------------------------------
+\paperchapter{%
+ The assessment of replication success based on relative effect size
+}{%
+  Leonhard Held, Charlotte Micheloud, Samuel Pawel
+}{%
+   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
+  \href{https://doi.org/10.1214/21-AOAS1502}{doi:~10.1214/21-AOAS1502}}
+\include{paper2}
+
+% Paper II
 % ------------------------------------------------------------------------------
@@
    \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
-   \url{https://doi.org/10.1111/rssb.12491}.
+   \href{https://doi.org/10.1111/rssb.12491}{doi:~10.1111/rssb.12491}
  }
 \include{paper1}
-
-% Paper II
-% ------------------------------------------------------------------------------
-\paperchapter{%
- The assessment of replication success based on relative effect size
-}{%
-  Leonhard Held, Charlotte Micheloud, Samuel Pawel
-}{%
-   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \url{https://doi.org/10.1214/21-AOAS1502}.}
-\include{paper2}
 
@@
   Samuel Pawel, Guido Consonni, Leonhard Held}{%
-  2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2211.02552}.}
+  2022. arXiv preprint. \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:~10.48550/arXiv.2211.02552}
+}
 \include{paper3}
+
+\addtocontents{toc}{\bigskip}
+\addtocontents{toc}{%
+  \protect\vspace{2ex}
+  \textbf{\textsf{Reverse-Bayes methodology}}\par}
+\addtocontents{toc}{%
+  \protect\vspace{-2ex}
+  \par\noindent\rule{\textwidth}{0.4pt}\par}
 
@@
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
-  \url{https://doi.org/10.1186/s12874-022-01635-4}.}
+  \href{https://doi.org/10.1002/jrsm.1538}{doi:~10.1002/jrsm.1538}
+}
+\include{paper4}
+
+\addtocontents{toc}{\protect\newpage}
 
@@
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
-  \url{https://doi.org/10.1002/jrsm.1538}.}
+  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:~10.1186/s12874-022-01635-4}
+}
 \include{paper5}
+
+\addtocontents{toc}{\bigskip}
+\addtocontents{toc}{%
+  \protect\vspace{2ex}
+  \textbf{\textsf{Integrity in methodological research}}\par}
+\addtocontents{toc}{%
+  \protect\vspace{-2ex}
+  \par\noindent\rule{\textwidth}{0.4pt}\par}
 
@@
 \paperchapter{%
- Pitfalls and Potentials in Simulation Studies
-}{%
-  Samuel Pawel, Lucas Kook, Kelly Reeve
-}{%
-  2022. arXiv preprint. \url{https://doi.org/10.48550/arXiv.2203.13076}.}
+  Pitfalls and Potentials in Simulation Studies }{%
+  Samuel Pawel, Lucas Kook, Kelly Reeve }{%
+  2022. arXiv preprint.
+  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:~10.48550/arXiv.2203.13076}
+}
 

### 2022-12-01 abstract.tex
Sandra feedback

@@
 
-The credibility of a scientific finding is based on the fact that it can be
-replicated when the same study is repeated with new subjects. However, various
-failures to replicate major scientific findings in the social and life sciences
-indicate that replicability is often lower than expected. This ``replication
-crisis'' has led to several methodological reforms in the past decade, an
-increased conduct of replication studies being one of them. Yet despite this
-increase in replication studies, there is no consensus on a fundamental
-question: How should replication success be defined statistically?
-% Various methods already exist and various new ones have
-% been proposed in response to the crisis. This thesis centres around a proposal
-% based on the reverse-Bayes approach. The key idea is to reverse the traditional
-% ``forward'' use of Bayes' theorem (``prior + likelihood $\rightarrow$
-% posterior''), starting instead with a pre-specified posterior and deducing the
-% corresponding prior (``posterior + likelihood $\rightarrow$
+% The credibility of a scientific finding is based on the fact that it can be
+% replicated when the same study is repeated with new subjects.
+An important aspect for the credibility of a scientific finding is that the
+finding can be replicated when the same study is repeated with new subjects.
+However, various failures to replicate major scientific findings in the social
+and life sciences indicate that replicability is often lower than expected. This
+``replication crisis'' has led to several methodological reforms in the past
+decade, an increased conduct of replication studies being one of them. Yet
+despite this increase in replication studies, there is no consensus on a
+fundamental question: How should replication success be defined statistically?
+% Various methods already exist and various new ones have been proposed in
+% response to the crisis. This thesis centres around a proposal based on the
+% reverse-Bayes approach. The key idea is to reverse the traditional ``forward''
+% use of Bayes' theorem (``prior + likelihood $\rightarrow$ posterior''),
+% starting instead with a pre-specified posterior and deducing the corresponding
+% prior (``posterior + likelihood $\rightarrow$
 % prior''). % As such, the reverse-Bayes approach naturally fits to the replication
@@
 % longer convincing. This prior then represents the position of a sceptic who
-% remains unconvinced by the original study. Whether or not the sceptics' position
-% is justified can then be assessed in light of the new data from the replication
-% study. The larger the conflict between the replication data and the sceptic, the
-% larger the degree of replication success. This procedure can be summarized in a
-% single quantitative measure of replication success, termed the sceptical
-% $p$-value.
+% remains unconvinced by the original study. Whether or not the sceptics'
+% position is justified can then be assessed in light of the new data from the
+% replication study. The larger the conflict between the replication data and
+% the sceptic, the larger the degree of replication success. This procedure can
+% be summarized in a single quantitative measure of replication success, termed
+% the sceptical $p$-value.
 
@@
 the finding from the study. Replication success is then achieved if there is
-conflict between the sceptical prior and the replication data. The first
-extension recalibrates the method to produce more appropriate inferences in
-terms of effect size. The recalibration is chosen such that for original studies
-which were borderline significant, replication success can only be achieved if
-the effect estimate from the replication study is larger than the estimate from
-the original study. The recalibrated method has good frequentist properties
-comparable to standard methods used in practice. The second extension replaces
-tail probabilities with Bayes factors as measures of evidence.
+conflict between the sceptical prior and the replication data. The procedure can
+be summarized in a single quantitative measure, termed the sceptical $p$-value.
+% extension 1
+The first extension recalibrates the sceptical $p$-value to produce more
+appropriate inferences in terms of effect size. The recalibration is chosen such
+that for original studies which were borderline significant, replication success
+can only be achieved if the effect estimate from the replication study is larger
+than the effect estimate from the original study. We find that the recalibrated
+sceptical $p$-value has good frequentist properties comparable to the standard
+method used in practice.
+% extension 2
+The second extension replaces tail probabilities with Bayes factors as measures
+of evidence. The procedure can again be summarized in a single measure called
+the sceptical Bayes factor.
 % The sceptical prior is now determined such that the original finding is no
@@
 % an effect and ensures that their effect estimates are compatible.
-The extended method has similar properties as the initial method but avoids a
-statistical paradox which the initial method suffers from -- in some situations
-it may flag success replication success even though the effect estimate from the
-replication is arbitrarily smaller than to the original one.
+The sceptical Bayes factor has similar properties as the sceptical $p$-value but
+it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
+some situations the sceptical $p$-value may indicate replication success even
+though the effect estimate from the replication is arbitrarily smaller than
+effect estimate from the original study. % , which cannot happen with the sceptical
+% Bayes factor.
 % Bayes factors have a more
@@
 studies which allows for combining data from the original study with external
-knowledge. External knowledge, such as data from other studies, is ubiquitous in
-the replication setting and taking it into account can lead to potentially more
-efficient designs compared to classical approaches.
+knowledge. This approach can lead to potentially more efficient designs compared
+to classical approaches, and it can be used for replication design based on both
+the sceptical $p$-value and the sceptical Bayes factor.
+% External knowledge, such as data from other studies, is ubiquitous in the
+% replication setting and taking it into account can lead to potentially more
+% efficient designs compared to classical approaches.
 
-The second part of the thesis also deals with reverse-Bayes methods, but with a
-broader scope of applications than replication studies. The reverse-Bayes idea
-was first proposed in the 1950s, but it has mostly been forgotten. To increase
-awareness and show potential use cases, reverse-Bayes history and methods are
-summarized in a comprehensive review. The review includes also some new results
-on connections between revere-Bayes methods and meta-analysis. %  Finally, a
+The second part of this thesis also deals with reverse-Bayes methods, but with a
+broader scope of applications than replication studies as in the first part. The
+reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
+forgotten. To increase awareness and show potential use cases, reverse-Bayes
+history and methods are summarized in a comprehensive review. The review
+includes also some new results on connections between revere-Bayes methods and
+meta-analysis. % Finally, a
 % commentary paper on a recently proposed reverse-Bayes method draws connections
@@
 
-The last part of the thesis revolves around research integrity issues in
+The last part of this thesis revolves around research integrity issues in
 methodological research. Questionable research practices, such as selective

### 2022-12-01 intro.Rnw
Sandra feedback

@@
 
-% \hfill
-% \begin{tabular}{p{0.7\textwidth}}
-%   We can make judgments of initial probabilities and infer
-%   final ones, or we can equally make judgments of final ones and infer
-%   initial ones by \emph{Bayes's theorem in reverse}. \\
-%   \hfill I.J. \citet[p. 29]{Good1983}
-% \end{tabular}
+\hfill
+\begin{tabular}{p{0.7\textwidth}}
+  ``\emph{Confirmation comes from repetition}. Any attempt to avoid this statement leads
+  to failure and more probably to destruction.'' \\
+  \hfill \citet[p. 84]{Tukey1969}
+\end{tabular}
+
+% \begin{center}
+% \begin{minipage}{12cm}
+%   { { { ``We can make judgments of initial probabilities and infer final ones,
+%         or we can equally make judgments of final ones and infer initial ones by
+%         \emph{Bayes's theorem in reverse}.'' }}}
+% \end{minipage}
+% \end{center}
+% \begin{flushright}
+%    \citet[p. 29]{Good1983}
+% \end{flushright}
+
+\section{Replication studies}
 
@@
   \centering
-  \includegraphics[height = 9cm]{images/xkcd.png}
-  \caption*{Replication studies as illustrated by Randall Munroe
-    (\url{https://xkcd.com/242/}).}
+  \includegraphics[height = 7.3cm]{images/xkcd.png}
+  \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
+    \mbox{(\url{https://xkcd.com/242})}.}
 \end{wrapfigure}
 
-\section{Replication studies}
-
-How can we know if a finding from a scientific study is really true? For
-example, how can we know if the protective effect of a vaccine found in a study
-is real? The answer to such questions is of high importance to scientists,
-decision makers, and the general population. However, because any study result
-comes with uncertainty we can never know for sure.
+% How can we know if a finding from a scientific study is really true? For
+% example, how can we know if the protective effect of a vaccine found in a study
+% is real? The answer to such questions is of high importance to scientists,
+% decision makers, and the general population. However, because any study result
+% comes with uncertainty we can never know for sure.
+How can we know whether we can trust a finding from a scientific finding? For
+example, how can we know whether the protective effect of a vaccine found in a
+study is a genuine effect or just a spurious finding? The answer to such
+questions is of high importance to scientists, decision makers, and the general
+population. However, because any study result comes with uncertainty we can
+never know for sure.
 
@@
 acquire by conducting novel research. This is because until relatively recently,
-top journals in many fields refused to publish replication studies as they were
-not considered ``innovative'' enough. To build a successful career, researchers
-thus often had no other choice than to concentrate their efforts on producing
-novel and eye-catching research results \citep{Martin2017}.
+many scientific journals put most emphasis on ``innovation'' thereby lowering
+the chance of publication for replication studies \citep{Makel2012, Martin2017,
+  Coiera2021}. To build a successful career, researchers thus often had no other
+choice than to concentrate their efforts on producing novel and eye-catching
+research results.
 
@@
 results than their original counterparts, and the replicability of research
-findings is surprisingly low on average. This realization led many to declare
-science as being in a ``replication crisis''. Debates arose about whether or not
-the crisis really existed and who or what was to blame \citep{Gilbert2016,
-  Amrhein2019}. Even the popular press became interested
-\citep[\eg{}][]{Carey2015, Kovic2016, Achenbach2017, Devlin2018}, so that also
-in the eyes of the public the credibility of science became seriously
-threatened.
+findings is surprisingly low (whatever replicability means will soon be
+discussed in more detail). This realization led many to declare science as being
+in a ``replication crisis''. Debates arose about whether or not the crisis
+really existed and who or what was to blame \citep{Gilbert2016, Amrhein2019}.
+Even the popular press became interested \citep[\eg{}][]{Carey2015, Kovic2016,
+  Achenbach2017, Devlin2018}, so that also in the eyes of the public the
+credibility of science became seriously threatened.
 
@@
     ## scale_y_log10() +
-    labs(x = "Year", y = paste0('Results for "', searchTerm, '"')) +
+    labs(x = "Year", y = paste0('Number of results \nfor "', searchTerm, '"')) +
     theme_bw() +
@@
 
-In the midst of this doomsday, % , particularly from the hard-hit
+In the midst of this crisis, % , particularly from the hard-hit
 % field of psychology,
-various reforms were implemented to prevent an escalation of the situation and
-save the reputation of science \citep[for an overview see \eg{}][]{Munafo2017}.
-For instance, many journals adopted the ``registered report'' format
-\citep{Chambers2021} in which a study proposal is peer reviewed \emph{before}
-the study is conducted, and which, if accepted, gives provisional publication
-acceptance regardless of the study outcome. Similarly, digital infrastructure
-platforms, such as Zenodo (\url{https://zenodo.org/}) or the Open Science
-Framework (\url{https://osf.io/}), were created to facilitate preregistration,
-preprints, code and data sharing, all of which have substantially increased over
-the last decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of
-conducting replication studies has also gained popularity. Several academic
-journals and funders are now explicitly promoting replication research
-\citep{NWO2016, NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this
-trend via the yearly number of results for the search term
-``\Sexpr{searchTerm}'' on Google Scholar over the last three decades. We see
-that the numbers have been rapidly growing, especially after the mid 2000s, with
-a minor drop in 2021 (perhaps because of research slowing down due to the
-COVID-19 pandemic).
+various reforms were implemented to prevent an escalation of the situation % and
+% save the reputation of science
+\citep[for an overview see \eg{}][]{Munafo2017}. For instance, many journals
+adopted the ``registered report'' format \citep{Chambers2021} in which a study
+proposal is peer reviewed \emph{before} the study is conducted, and which, if
+accepted, gives provisional publication acceptance regardless of the study
+outcome. Similarly, digital infrastructure platforms, such as Zenodo
+(\url{https://zenodo.org}) or the Open Science Framework
+(\url{https://osf.io}), were created to facilitate preregistration, preprints,
+code and data sharing, all of which have substantially increased over the last
+decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of conducting
+replication studies has also gained popularity. Several academic journals and
+funders are now explicitly promoting replication research \citep{NWO2016,
+  NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this trend via the
+yearly number of results for the search term ``\Sexpr{searchTerm}'' on Google
+Scholar over the last three decades. We see that the numbers have been rapidly
+growing, especially after the mid 2000s, with a minor drop in 2021 (perhaps
+because of research slowing down due to the COVID-19 pandemic).
 
@@
 the results from different methods for assessing replication success. For
-example, the \citet{Opensc2015} states ``[t]here is no single standard for
-evaluating replication success. We evaluated [replicability] using significance
-and P values, effect sizes, subjective assessments of replication teams, and
-meta-analyses of effect sizes'' (p. 11). In the following, I will give an
+example, the \citet[p. 11]{Opensc2015} states ``[t]here is no single standard
+for evaluating replication success. We evaluated [replicability] using
+significance and P values, effect sizes, subjective assessments of replication
+teams, and meta-analyses of effect sizes''. In the following, I will give an
 overview about these and other methods which have been used in practice.
@@
 success analysis as the raw data from the original study may not be available to
-the replicators. The most important statistic is the effect estimate $\that$. It
-provides an estimate of the underlying effect size $\theta$ which quantifies the
-true effect or association of an intervention/exposure with an outcome variable.
-Typical effect sizes are mean differences and correlations (for continuous
-outcomes), odds ratios (for binary outcomes), or hazard ratios (for time to
-event outcomes). Depending on the type of effect size, a transformation might be
-required so that the assumption of approximately normally distributed effect
-estimates around the unknown effect size $\theta$ (for large enough sample
-sizes) is justified. This could be, for instance, the Fisher $z$-transformation
-for correlations or the log-transformation for odds/hazard ratios \citep[chapter
-11]{Cooper2019}. The associated standard error $\sigma$ represents the
-statistical uncertainty of the estimate. Under the assumption of (asymptotic)
-normality, confidence intervals for $\theta$ and $p$-values for testing the null
-hypothesis $H_{0} \colon \theta = 0$ can be computed as shown in
-Table~\ref{tab:meta}.
+the researchers conducting the replication study. The most important statistic
+is the effect estimate $\that$. It provides an estimate of the underlying effect
+size $\theta$ which quantifies the true effect or association of an
+intervention/exposure with an outcome variable. Typical effect sizes are mean
+differences and correlations (for continuous outcomes), odds ratios (for binary
+outcomes), or hazard ratios (for time to event outcomes). Depending on the type
+of effect size, a transformation might be required so that the assumption of
+approximately normally distributed effect estimates around the unknown effect
+size $\theta$ (for large enough sample sizes) is justified. This could be, for
+instance, the Fisher $z$-transformation for correlations or the
+log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
+associated standard error $\sigma$ represents the statistical uncertainty of the
+estimate. Under the assumption of (asymptotic) normality, confidence intervals
+for $\theta$ and $p$-values for testing the null hypothesis
+$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
 
@@
 underlying both methods (\eg{} it penalizes shrinkage of the replication effect
-estimate and requires compelling evidence from both studies). However, it is
-also shown that the sceptical $p$-value suffers from a certain type of
-``shrinkage paradox'', which is avoided by the sceptical Bayes factor; when the
-$p$-value from the original study goes to zero, replication success based on the
-sceptical $p$-value can be achieved with any arbitrarily small replication
-effect estimate, whereas replication success based on the sceptical Bayes factor
-poses a finite limit on how much shrinkage is allowed. Technically, the
-procedure is more involved and closed-form solutions for the sceptical Bayes
-factor are only available in special situations. % and in terms of the
+estimate and requires compelling evidence from both studies in terms of
+$p$-values and Bayes factors, respectively). However, it is also shown that the
+sceptical $p$-value suffers from a certain type of ``shrinkage paradox'', which
+is avoided by the sceptical Bayes factor; when the $p$-value from the original
+study goes to zero, replication success based on the sceptical $p$-value can be
+achieved with any arbitrarily small replication effect estimate, whereas
+replication success based on the sceptical Bayes factor poses a finite limit on
+how much shrinkage is allowed. Technically, the procedure is more involved and
+closed-form solutions for the sceptical Bayes factor are only available in
+special situations. % and in terms of the
 % ``Lambert W function'' \citep{Corless1996}.
@@
 improved by expanding it with some logical flaws of the method. The two of us
-iteratively worked on the manuscript, while L. Held gave mostly high-level
-feedback.
+iteratively worked on the manuscript, while L. Held gave high-level feedback.
 
@@
 practices, such as selective reporting \citep{Boulesteix2020}. In this article,
-we raise awareness of these issues. We summarize possible questionable research
+draw attention to these issues. We summarize possible questionable research
 practices in simulation studies, and show how easy it is to make a method seem
@@
 research. I then wrote a first draft of the manuscript and proposed the idea to
-L. Kook and K. Reeve. L. Kook and myself then came up with the method ``AINET''
-and started writing the simulation protocol. L. Kook took lead in developing the
-R package \texttt{ainet} (\url{https://github.com/LucasKook/ainet}) and
-simulation study code. Myself, L. Kook, and K. Reeve then designed the final
-simulation study and wrote the manuscript together. Recently, I was invited to
-present the results from this project at the CEN (Central European Network)
-conference 2023 in Basel.
+L. Kook and K. Reeve. L. Kook and myself then came up with the penalized
+regression method ``AINET'' and started writing the simulation protocol. L. Kook
+took lead in developing the R package \texttt{ainet}
+(\url{https://github.com/LucasKook/ainet}) and simulation study code. Myself, L.
+Kook, and K. Reeve then designed the final simulation study and continued
+working on the manuscript together. Recently, I was invited to present the
+results from this project at the CEN (Central European Network) conference 2023
+in Basel.
 

### 2022-12-01 thesis.Rnw
Sandra feedback

@@
   linkcolor = {black},
+  breaklinks = {true},
   citecolor = {Blue},

### 2022-12-02 intro.Rnw
fixes

@@
 \hfill
-\begin{tabular}{p{0.7\textwidth}}
-  ``\emph{Confirmation comes from repetition}. Any attempt to avoid this statement leads
-  to failure and more probably to destruction.'' \\
+\begin{tabular}{p{0.6\textwidth}}
+  ``\emph{Confirmation comes from repetition}. Any attempt to avoid this statement leads at least to failure and more probably to destruction.'' \\
   \hfill \citet[p. 84]{Tukey1969}
@@
 
-\begin{wrapfigure}{r}{0.34\textwidth}
+\begin{wrapfigure}{r}{0.29\textwidth}
   \centering
-  \includegraphics[height = 7.3cm]{images/xkcd.png}
+  \includegraphics[height = 6.9cm]{images/xkcdCrop.png}
   \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
@@
 % comes with uncertainty we can never know for sure.
-How can we know whether we can trust a finding from a scientific finding? For
+How can we know whether we can trust a finding from a scientific study? For
 example, how can we know whether the protective effect of a vaccine found in a

### 2022-12-02 thesis.Rnw
fixes

@@
    \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \href{https://doi.org/10.1214/21-AOAS1502}{doi:~10.1214/21-AOAS1502}}
+  \href{https://doi.org/10.1214/21-AOAS1502}{doi:10.1214/21-AOAS1502}}
 \include{paper2}
@@
    \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
-   \href{https://doi.org/10.1111/rssb.12491}{doi:~10.1111/rssb.12491}
+   \href{https://doi.org/10.1111/rssb.12491}{doi:10.1111/rssb.12491}
  }
@@
   Samuel Pawel, Guido Consonni, Leonhard Held}{%
-  2022. arXiv preprint. \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:~10.48550/arXiv.2211.02552}
+  2022. arXiv preprint. \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:10.48550/arXiv.2211.02552}
 }
@@
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
-  \href{https://doi.org/10.1002/jrsm.1538}{doi:~10.1002/jrsm.1538}
+  \href{https://doi.org/10.1002/jrsm.1538}{doi:10.1002/jrsm.1538}
 }
@@
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
-  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:~10.1186/s12874-022-01635-4}
+  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:10.1186/s12874-022-01635-4}
 }
@@
   2022. arXiv preprint.
-  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:~10.48550/arXiv.2203.13076}
+  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:10.48550/arXiv.2203.13076}
 }

### 2022-12-02 paper1.tex
change paper order 1 and 2

--- 2022-11-25 paper1.tex
@@
 \section*{Abstract}
-
-Replication studies are increasingly conducted but there is no established
-statistical criterion for replication success. We propose a novel approach
-combining reverse-Bayes analysis with Bayesian hypothesis testing: a sceptical
-prior is determined for the effect size such that the original finding is no
-longer convincing in terms of a Bayes factor. This prior is then contrasted to
-an advocacy prior (the reference posterior of the effect size based on the
-original study), and replication success is declared if the replication data
-favour the advocacy over the sceptical prior at a higher level than the original
-data favoured the sceptical prior over the null hypothesis. The sceptical Bayes
-factor is the highest level where replication success can be declared. A
-comparison to existing methods reveals that the sceptical Bayes factor combines
-several notions of replicability: it ensures that both studies show sufficient
-evidence against the null and penalises incompatibility of their effect
-estimates. Analysis of asymptotic properties and error rates, as well as case
-studies from the Social Sciences Replication Project show the advantages of the
-method for the assessment of replicability.
-
-\textbf{Key words}:
-Bayes factor, Bayesian hypothesis testing, replication studies, reverse-Bayes,
-sceptical $p$-value
+Replication studies are increasingly conducted in order to confirm original
+findings. However, there is no established standard how to assess replication
+success and in practice many different approaches are used. The purpose of this
+paper is to refine and extend a recently proposed reverse-Bayes approach for the
+analysis of replication studies. We show how this method is directly related to
+the relative effect size, the ratio of the replication to the original effect
+estimate. This perspective leads to a new proposal to recalibrate the assessment
+of replication success, the golden level. The recalibration ensures that for
+borderline significant original studies replication success can only be achieved
+if the replication effect estimate is larger than the original one. Conditional
+power for replication success can then take any desired value if the original
+study is significant and the replication sample size is large enough. Compared
+to the standard approach to require statistical significance of both the
+original and replication study, replication success at the golden level offers
+uniform gains in project power and controls the Type-I error rate if the
+replication sample size is not smaller than the original one. An application to
+data from four large replication projects shows that the new approach leads to
+more appropriate inferences, as it penalizes shrinkage of the replication
+estimate compared to the original one, while ensuring that both effect estimates
+are sufficiently convincing on their own.
+
+\textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
+two-trials rule, type-I error rate
 
 \section{Introduction}
-As a consequence of the so-called replication crisis, the scientific community
-increasingly recognises the value of replication studies, and several attempts
-have been made to assess replicability on a large scale \citep{Errington2014,
-  Klein2014, Opensc2015, Camerer2016, Camerer2018, Cova2018}. Despite most
-researchers agreeing on the importance of replication, there is currently no
-agreement on a statistical criterion for replication success. Instead, a variety
-of statistical methods, frequentist \citep{Simonsohn2015, Patil2016, Hedges2019,
-  Mathur2020}, Bayesian \citep{Bayarri2002b, Bayarri2002, Verhagen2014,
-  Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019}, and combinations
-thereof \citep{Held2020, Pawel2020, Held2021} have been proposed to quantify
-replication success.
-
-Due to this lack of an established method, replication projects typically report
-the results of several methods and it is not uncommon for these to contradict
-each other. For example, both studies may find evidence against a null effect,
-but the individual effect estimates may still be incompatible (often the
-replication estimate is much smaller). Conversely, both estimates may be
-compatible, but there may not be enough evidence against a null effect in one of
-the studies.
-
-The objective of this paper is to present a novel Bayesian method for
-quantifying replication success, which builds upon a previously proposed method
-\citep[the \emph{sceptical $p$-value} from][]{Held2020} and unifies several
-notions of replicability. The method combines the natural fit of the
-reverse-Bayes approach to the replication setting with the use of Bayes factors
-for hypothesis testing \citep{Jeffreys1961, Kass1995} and model criticism
-\citep{Box1980}. In a nutshell, replication success is declared if the
-replication data favour an advocacy prior for the effect size, which emerges
-from taking the original result at face value, over a sceptical prior, which
-renders the original result unconvincing.
-
-\citet{Held2020} proposed a reverse-Bayes approach for the assessment of
-replication success: The main idea is to challenge the result from an original
-study by determining a \emph{sceptical prior} for the effect size, sufficiently
-concentrated around the null value such that the resulting posterior is rendered
-unconvincing \citep{Matthews2001b}. An unconvincing posterior at level $\alpha$
-is defined by its $(1 - \alpha)$ credible interval just including the null
-value. Subsequently, the replication data are used in a prior-data conflict
-assessment \citep{Box1980, Evans2006} and replication success is concluded if
-there is sufficient conflict between the sceptical prior and the replication
-data. Specifically, replication success at level $\alpha$ is established if the
-prior predictive tail probability of the replication estimate is smaller than
-$\alpha$. The smallest level $\alpha$ at which replication success can be
-declared corresponds to the sceptical $p$-value.
-
-The method comes with appealing properties: The sceptical $p$-value is never
-smaller than the ordinary $p$-values from both studies, thus ensuring that they
-both provide evidence against the null. At the same time, it also takes into
-account the size of their effect estimates, penalising the case when the
-replication estimate is smaller than the original estimate. \citet{Held2021}
-further refined the method with a recalibration that allows the sceptical
-$p$-value to be interpreted on the same scale as an ordinary $p$-value, as well
-as ensuring appropriate frequentist properties, such as type I error rate
-control if the replication sample size is not smaller than in the original
-study.
-
-Despite the methods' Bayesian nature, it relies on tail probabilities as primary
-inference tool. An alternative is the Bayes factor, the principled Bayesian
-solution to hypothesis testing and model selection \citep{Jeffreys1961,
-Kass1995}. In contrast to tail probabilities, Bayes factors have a more natural
-interpretation and allow for direct quantification of evidence for one
-hypothesis versus another. In this paper we therefore extend the reverse-Bayes
-procedure from \citet{Held2020} to use Bayes factors for the purpose of
-quantifying evidence. This extension was suggested by \citet{Consonni2019} and
-\citet{Pericchi2020} independently. Interestingly, a similar extension of the
-reverse-Bayes method from \citet{Matthews2001b} was already hinted at by
-\citet{Berger2001}, but to date no one has attempted to realise the idea.
-
-The inclusion of Bayes factors leads to a new quantity which we call the
-\emph{sceptical Bayes factor}. Unlike standard forward-Bayes methods, but
-similar to the sceptical $p$-value, the proposed method combines two notions of
-replication success: It requires from both studies to show sufficient evidence
-against the null, while also penalising incompatibility of their effect
-estimates. However, while the sceptical $p$-value quantifies compatibility only
-indirectly through conflict with the sceptical prior, the sceptical Bayes factor
-evaluates directly how likely the replication data are to occur under an
-advocacy prior (the reference posterior of the effect conditional on the
-original study). This direct assessment of compatibility allows for stronger
-statements about the degree of replication success, and it may also lead to
-different conclusions in certain situations.
-
-This paper is structured as follows: Section \ref{sec1:methods} presents the
-derivation of the sceptical Bayes factor. Its asymptotic and finite sample
-properties are then compared with other measures of replication success in
-Section \ref{sec1:comparison}. An extension to non-normal models is presented in
-Section \ref{sec1:tdist}. Section \ref{sec1:applications} illustrates how the
-method works in practice using case studies from the \emph{Social Sciences
-  Replication Project} \citep{Camerer2018}. Section \ref{sec1:discussion}
-provides concluding remarks about strengths, limitations and extensions of the
-method.
-
-\subsection*{Notation and assumptions}
-Denote the Bayes factor comparing the plausibility of hypotheses $H_1$ and $H_2$
-with respect to the observed data $x$ by
-\begin{align*}
-  \BFcol{1}{2}(x) = \frac{f(x \given H_1)}{f(x \given H_2)}
-  = \frac{\int_{\Theta_1} f(x \given \theta_1)f(\theta_1) \, \text{d}\theta_1}{
-  \int_{\Theta_2} f(x \given \theta_2)f(\theta_2) \, \text{d}\theta_2},
-\end{align*}
-where $f(x \given H_i)$ is the marginal likelihood of the data under $H_i$
-obtained by integrating the likelihood $f(x \given \theta_{i})$ with respect to
-the prior distribution $f(\theta_{i})$ of the model parameters
-$\theta_i \in \Theta_i$ with $i = 1, 2$. Sometimes we will also write
-$\BFcol{1}{2}(x ; \phi^\prime)$ to indicate that the Bayes factor is evaluated
-for a specific value $\phi^\prime$ of a hyperparameter $\phi$ of one of the
-model priors. To simplify comparison with $p$-values we will orient Bayes
-factors such that lower values indicate more evidence against a null hypothesis.
-
-Let $\theta$ denote the effect of a treatment on an outcome of interest. Let
-$\that_o$ and $\that_r$ denote its maximum likelihood estimates obtained from an
-original (subscript $o$) and from a replication study (subscript $r$),
-respectively. Let the corresponding standard errors be denoted by $\sigma_o$ and
-$\sigma_r$, the $z$-values by $z_o = \that_o/\sigma_o$ and
-$z_r = \that_r/\sigma_r$, and define the variance ratio as
-$c = \sigma_o^2/\sigma_r^2$ and the relative effect estimate as
-$d = \that_r/\that_o = z_r/(z_o\sqrt{c})$. For many effect size types the
-variances are inversely proportional to the sample size, \ie
-$\sigma^2_{o} = \kappa/n_{o}$ and $\sigma^2_{r} = \kappa/n_{r}$ for some unit
-variance $\kappa$. The variance ratio is then the ratio of the replication to
-the original sample size $c = n_{r}/n_{o}$.
-
-We adopt a meta-analytic framework and consider the effect estimates as the
-data, rather than their underlying samples, and assume that
-$\that_k \given \theta \sim \Nor(\theta, \sigma^2_k)$ for $k \in \{o, r\},$ \ie
-normality of the effect estimates around $\theta$, with known variances equal to
-their squared standard errors. For studies with reasonable sample size, this
-framework usually provides a good approximation for a wide range of (suitably
-transformed) effect size types \citep[Chapter 2.4]{Spiegelhalter2004}. For
-example, means and mean differences (no transformation), odds ratios, hazard
-ratios, risk ratios (logarithmic transformation), or correlation coefficients
-(``Fisher-$z$'' transformation). We refer to the literature of meta-analysis for
-details about transformations of effect sizes \citep[\eg][Chapter
-11.6]{Cooper2019}. The normal model in combination with conjugate priors enables
-derivation of closed-form expressions in many cases, which allows us to easily
-study limiting behaviour and facilitates interpretability. In Section
-\ref{sec1:tdist}, we will present relaxations of the normality assumption, which
-can lead to more accurate inferences when studies have small sample sizes and/or
-show extreme results.
-
-\section{Reverse-Bayes assessment of replication success with Bayes factors}
-\label{sec1:methods}
-% ``judgements are made concerning the values that the final
-% probabilities would have after some imaginary results are obtained; then Bayes'
-% theorem is used backwards to estimate what the consistent initial probabilities
-% must be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain
-% estimates of the final probabilities in the light of the actual observations.
-% This device takes \emph{seriously} the view that a theory of probability or of
-% rationality is no more than a theory of consistency'' (p. 126).
-The idea of reversing Bayes' theorem was first proposed by \citet{Good1950}. He
-acknowledged that in many situations there is no obvious choice for the prior
-distributions involved in Bayesian analyses. On the other hand, we are often
-more certain which posterior inferences would convince us regarding the
-credibility of a hypothesis. For this reason, Good inverted Bayes' theorem and
-derived priors, which combined with the observed data, would lead to posterior
-inferences that were specified beforehand (\eg the data favour one hypothesis
-over another). His reverse-Bayes inference then centred around the question
-whether the resulting prior is plausible, and if so, this would legitimise the
-posterior inference. See Figure~\ref{fig1:RBschmema} for a graphical illustration
-of this process.
-
-\begin{figure}[!htb]
+Replication studies are conducted in order to investigate whether an original
+finding can be confirmed in an independent study. Although replication has long
+been a central part of the scientific method in many fields, the so-called
+replication crisis \citep{Ioannidis2005, Begley2015} has led to increased
+interest in replication over the last decade. These developments eventually
+culminated in large-scale replication projects that were conducted in various
+fields \citep{Errington2014, Klein2014, Opensc2015, Ebersole2016, Camerer2016,
+  Camerer2018, Cova2018, Klein2018}.
+
+Declaring a replication as successful is, however, not a straightforward task,
+and currently used approaches include statistical significance of both the
+original and replication study, compatibility of their effect estimates, and
+meta-analysis of the effect estimates. Many of the replication projects listed
+above also report the relative effect size, the ratio of the replication to the
+original effect estimate. For example, in \citet{Camerer2018} the replication
+effect estimates were only half as large as the original ones on average and
+even smaller in \citet{Opensc2015}. This gives clear evidence of a systematic
+bias of the original studies and strongly suggests that the original and
+replication study should not be treated as exchangeable. However, all the
+approaches mentioned above will give the same results if the order of studies
+would be reversed.
+
+In order to address this problem, a new method has recently been proposed in
+\citet{Held2020}. The approach combines the analysis of credibility
+\citep{Matthews2001a,Matthews2001b} with a prior-data conflict assessment
+\citep{Box1980}. Replication success is declared if the replication study is in
+conflict with a sceptical prior that would make the original study
+non-significant. This approach penalizes small relative effect sizes as we will
+see in more detail in the following.
+
+To introduce some notation, let $z_o = \hat \theta_o/\sigma_o$ and
+$z_r = \hat \theta_r/\sigma_r$ denote the $z$-statistic of the original and
+replication study, respectively. Here $\hat \theta_o$ and $\hat \theta_r$ are
+the corresponding effect estimates (assumed to be normally distributed) of the
+unknown effect $\theta$ with standard errors $\sigma_o$ and $\sigma_r$,
+respectively. The corresponding one-sided $p$-values are denoted by
+$p_o=1-\Phi(z_o)$ and $p_r=1-\Phi(z_r)$, respectively, where $\Phi(\cdot)$
+denotes the standard normal cumulative distribution function. Let
+$c = \sigma_o^2/\sigma_r^2$ denote the variance ratio of the squared standard
+errors of the original and replication effect estimates. The squared standard
+errors are usually inversely proportional to the sample size of each study, \ie{}
+$\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
+variance $\kappa^2$. The variance ratio $c$ can then be identified as the
+relative sample size $c=n_r/n_o$. The relative effect size
+\begin{equation}\label{eq1:d}
+  d = \frac{\hat \theta_r}{\hat \theta_o} = \frac{1}{\sqrt{c}} \frac{z_r}{z_o}
+\end{equation}
+quantifies the size of the replication effect estimate $\hat \theta_r$ relative
+to the original effect estimate $\hat \theta_o$. The corresponding shrinkage of
+the replication effect estimate will be denoted as $s=1-d$.
+
+Suppose the original study achieved statistical significance at one-sided level
+$\alpha$, so $p_o \leq \alpha$. The standard approach to assess replication
+success is based on significance of the replication effect estimate at the same
+level $\alpha$, \ie{} the replication is considered successful if also
+$p_r \leq \alpha$. This approach is known in drug development as the two-trials
+rule \citep{Senn2008}, usually conducted at $\alpha=0.025$. Let
+$z_\alpha = \Phi^{-1}(1-{\alpha})>0$ denote the $z$-value corresponding to the
+level $\alpha$, then significance of the replication study is achieved if
+$z_r \geq z_\alpha$, which is equivalent to the condition
+\begin{equation}\label{eq1:dSig}
+   d \geq \frac{z_\alpha}{z_o  \, \sqrt{c}}
+\end{equation}
+on the relative effect size \eqref{eq1:d}. The right hand-side goes to zero for
+increasing $c$, so if the relative sample size $c$ is large enough, significance
+of the replication study can be achieved with any arbitrarily small (but
+positive) relative effect size $d$. However, declaring replication success when
+there is substantial shrinkage is contrary to common sense, as the replication
+effect estimate may not reflect an effect size of the same practical relevance
+as the original one, despite its statistical significance.
+
+In this paper we first review the \citet{Held2020} approach for the assessment
+of replication success, followed by showing how it relates to the relative
+effect size (Section \ref{sec1:res}). This perspective is used in Section
+\ref{sec1:goldenthresh} and \ref{sec1:recalib} to propose a recalibration of the
+method, the \textit{golden level}, which leads to a more appropriate criterion
+for replication success compared to the two-trials rule (Section \ref{sec1:2TR}).
+In Section \ref{sec1:ER} we study power and Type-I error rates of the proposed
+method and compare it to the two-trials rule. The recalibrated method ensures
+that conditional power can take any desired value if the original study has been
+significant and the replication sample size is large enough (Section
+\ref{sec1:powerrep}), controls the overall Type-I error if the replication sample
+size is not smaller than the original one (Section \ref{sec1:T1E}), and offers
+uniform gains in project power compared to the two-trials rule (Section
+\ref{sec1:PP}). Section \ref{sec1:application} describes an application to data
+from four replication projects and Section \ref{sec1:discussion} closes with some
+discussion.
+
+\section{Replication success}\label{sec1:RS}
+
+\begin{center}
+\begin{figure}[!h]
+\begin{center}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig1-1}
+
+}
+
+\end{knitrout}
+\caption{Example of the assessment of replication success. The original study
+  from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
+  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value $p_o = 0.011$.
+  The left part of the figure illustrates the reverse-Bayes derivation of the
+  sufficiently sceptical prior based on the original study result and the
+  posterior with lower credible limit fixed at zero. The comparison of the
+  sufficiently sceptical prior with the replication study result
+  ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$) in the
+  right part of the figure is used to assess potential prior-data conflict.}
+  \label{fig1:fig1}
+\end{center}
+\end{figure}
+\end{center}
+
+Hereinafter we focus on the one-sided assessment of replication success to
+ensure that replication success can only occur if the original and replication
+effect estimates go in the same direction. Figure \ref{fig1:fig1} illustrates the
+\citet{Held2020} approach based on a replication study from the \textit{Social
+  Sciences Replication Project} \citep{Camerer2018}: the significant original
+finding by \citet{Pyc2010} at one-sided level $\alpha=0.025$ is challenged with
+a sceptical prior, sufficiently concentrated around zero to make the original
+study result no longer convincing \citep{Matthews2001a,Matthews2001b}.
+Replication success is then defined as conflict between the sceptical prior and
+the result from the replication study in order to disprove the sceptic. Conflict
+is quantified by a prior-predictive tail probability $p_{\mbox{\scriptsize
+    Box}}$ \citep{Box1980} where a small value $p_{\mbox{\scriptsize
+    Box}} \leq \alpha$ defines replication success. In Figure \ref{fig1:fig1} the
+original finding is only borderline significant, so the sufficiently sceptical
+prior is fairly wide. Furthermore, there is substantial shrinkage
+($d = 0.15/0.4 = 0.38$) of the replication effect estimate and therefore hardly
+any conflict with the sufficiently sceptical prior (one-sided
+$p_{\mbox{\scriptsize Box}}=0.31$). We are thus not able to declare replication
+success at level $2.5$\%.
+
+The actual value of $p_{\mbox{\scriptsize Box}}$ is difficult to interpret as it
+depends on the level $\alpha$ and does not even exist if the original $p$-value
+$p_o$ exceeds $\alpha$. However, \citet{Held2020} showed that if both
+$\sign(z_o)=\sign(z_r)$ and
+\begin{equation}\label{eq1:extrinsic.p}
+\left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
+- 1 \right) \geq c
+\end{equation}
+hold, replication success at level ${\alpha_S}$ is achieved, where
+$z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$. The requirement
+\eqref{eq1:extrinsic.p} can be assessed for any value of
+${{\alpha_S}} > \max\{p_o, p_r\}$ and of particular interest is the smallest
+possible value of $\alpha_S$ where \eqref{eq1:extrinsic.p} holds, the so-called
+\textit{sceptical $p$-value} $p_S$. We are thus interested in the value $z_S^2$
+that fulfills
+\begin{equation}\label{eq1:extrinsic.p2}
+\left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
+- 1 \right) = c.
+\end{equation}
+There is a unique solution of \eqref{eq1:extrinsic.p2} which defines the
+one-sided {sceptical $p$-value} $p_S= 1-\Phi\left({z_S}\right)$ where
+$z_{S} \coloneqq + \surd z_{S}^2$, provided $\sign(z_o)=\sign(z_r)$ holds.
+Replication success at level $\alpha_S$ is then achieved if $p_S \leq \alpha_S$.
+In the introductory example based on the original study by \citet{Pyc2010}, the
+sceptical $p$-value turns out to be $p_S=0.11$.
+
+The sceptical $p$-value has a number of interesting properties, see
+\citet[Section 3.1]{Held2020} for details. In particular,
+$p_S > \max\{p_o, p_r\}$ always holds with $p_S \downarrow \max\{p_o, p_r\}$ for
+$c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
+sceptical $p$-value $p_S$ increases with decreasing relative effect size $d$.
+The first property ensures that both the original and the replication study have
+to be sufficiently convincing on their own to achieve replication success. The
+second property guarantees that shrinkage of the replication effect estimate is
+penalized.
+
+The level for replication success $\alpha_S$ has to be distinguished from the
+significance level $\alpha$ associated with the ordinary $p$-value.
+\citet{Held2020} has used the \textit{nominal level} for replication success
+($\alpha_S=\alpha$) for convenience, but in the following we will propose a
+recalibration of the procedure along with a new value for $\alpha_S$, the
+\textit{golden level} (Section~\ref{sec1:goldenthresh}). The derivation is based
+on a property of the required relative effect size for replication success, if
+the relative sample size is very large (Section~\ref{sec1:res}). In a nutshell,
+the golden level ensures that for original studies which were only borderline
+significant ($p_o=\alpha$), replication success is only possible if the
+replication
+effect estimate is larger than the original one ($d > 1$).\\
+
+\subsection{Relative effect size}\label{sec1:res}
+Without loss of generality we now assume that $\hat \theta_o > 0$ and that
+$p_o < {\alpha_S}$ has been observed in the original study, otherwise it would
+be impossible to achieve replication success at level $\alpha_S$ because $p_S$
+is always larger than $p_o$. The condition \eqref{eq1:extrinsic.p} for
+replication success can then be re-written as
+\begin{equation}\label{eq1:eq.z}
+  z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
+\end{equation}
+where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of \eqref{eq1:eq.z} is
+the minimum replication $z$-value $\zrmin$ required to achieve replication
+success. Note that $\zrmin$ increases with increasing $c$, so increasing the
+replication sample size leads to a more stringent success requirement $z_r$ and
+the corresponding replication $p$-value $p_r$.
+
+Equation \eqref{eq1:eq.z} can be further transformed to a
+condition on the relative effect size \eqref{eq1:d}:
+\begin{equation}\label{eq1:res}
+  d \geq  \frac{\sqrt{1+c/(K-1)}}{ \sqrt{c K}} \eqqcolon \dmin .
+\end{equation}
+To achieve replication success, the relative effect size must be at least as
+large as the right hand-side of \eqref{eq1:res}, the minimum relative effect size
+$\dmin$, a function of $K$ and the relative sample size $c$. If the relative
+sample size becomes very large, \ie{} $c \rightarrow \infty$, we have
+$\dmin \downarrow \dinfty$ where
+\begin{equation}\label{eq1:smallestpossible}
+  \dinfty = 1/\sqrt{K (K-1)}
+\end{equation}
+is the \textit{limiting relative effect size}. This shows that the minimum
+relative effect size $\dmin$ in \eqref{eq1:res} does not go to zero for
+increasing $c$, so replication success cannot be achieved if the relative effect
+size $d$ is smaller or equal to $\dinfty$, no matter how large the replication
+study is. In contrast, the corresponding criterion \eqref{eq1:dSig} of the
+two-trials rule can be achieved for any positive relative effect size,
+regardless of how small, provided the replication sample size is sufficiently
+large.
+
+\subsection{The golden level}\label{sec1:goldenthresh}
+Significance of both the original and the replication study at level $\alpha$ is
+a necessary but not sufficient requirement for replication success at the
+nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
+stringent. It is more reasonable to calibrate the procedure in such a way that
+to establish replication success, original and replication study do not both
+necessarily need to be significant at level $\alpha$, provided that the
+replication effect estimate does not shrink compared to the original one. We
+therefore choose a level $\alpha_S$ such that a borderline significant original
+study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
+$s > 0$ of the replication effect estimate. Mathematically, this translates to
+setting $\dinfty = 1$ and $K = z_\alpha^2/z_{\alpha_S}^2$
+in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
+with solution $K = \varphi$ where $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
+known as the golden ratio. Solving for $z_{\alpha_S}$ gives
+$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
+  level}
+\begin{eqnarray}\label{eq1:golden}
+\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
+\end{eqnarray}
+for replication success. This is our recommended default choice to assess
+replication success and we will study its properties in the following in more
+detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
+$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig1:fig1},
+the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
+\citet{Pyc2010} study was not successful.
+
+The golden level \eqref{eq1:golden} is derived from~\eqref{eq1:smallestpossible}
+with $\dinfty = 1$. However, we may also use a different value for the limiting
+relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
+only possible for a borderline significant result ($p_o = \alpha$) if there is
+less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication
+effect estimate. This approach is equivalent to a limiting relative effect size
+of 1 if the original $p$-value $p_o$ is equal to a different level $\alpha'$,
+which can be derived as follows: First, solving \eqref{eq1:smallestpossible} for
+$\dinfty > 0$ gives
+$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
+$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
+$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
+\begin{equation}\label{eq1:alphaPrime}
+\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
+\end{equation}
+For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.
+
+\subsection{Recalibration of the sceptical \textit{p}-value}\label{sec1:recalib}
+
+The condition $p_S \leq \alpha_S$ for replication success at the golden level is
+equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
+$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
+recalibrate the sceptical $p$-value $p_{S} = 1 - \Phi(z_S)$ to
+$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
+to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
+be interpreted on the same scale as an ordinary $p$-value. For example, the
+recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
+out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
+level $\alpha<0.061$, including the standard $0.025$ level.
+
+\subsection{Comparison with the two-trials rule}\label{sec1:2TR}
+A useful benchmark for comparison is the two-trials rule in drug development
+\citep[Section 9.4]{Kay2015}, which requires ``at least two adequate and
+well-controlled studies, each convincing on its own, to establish
+effectiveness'' \citep[p.~3]{FDA1998}. This is usually achieved by independently
+replicating the result of a first study in a second study, both significant at
+one-sided level $\alpha=0.025$. {It is worth noting that in practice the two
+  trials are often run in parallel} {\citep{Senn2008}}{, so do not exactly
+  resemble the replication setting.}
+
+The main difference between the replication success and the two-trials
+rule approach concerns how shrinkage of the replication effect
+estimate is handled. Figure~\ref{fig1:fig2} illustrates that
+shrinkage is penalized in the assessment of replication success, \ie{}
+the original $p$-value needs to be quite small to achieve replication
+success for a relative effect size $d<1$. In contrast, significance of
+the replication study can be achieved even if there is substantial
+shrinkage, provided the replication sample size is large enough.
+
+\begin{figure}[!h]
 \centering
-%% first attempt
-\begin{tikzpicture}[node distance = 5em, thick]
-  % nodes %
-  \node[font = \large] (data) {$f(\text{data} \,|\, \theta)$};
-  \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
-  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \text{data})$};
-  \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
-  \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};
-
-  % edges %
-  \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
-  %% other names could be:
-  %% - reverse Bayesian updating vs forward Bayesian updating
-  %% - Bayesian reverting
-  \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
-  \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
-  \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
-\end{tikzpicture}
-\caption{Schematic illustration of reverse-Bayes and forward-Bayes inference
-  for an unknown parameter $\theta$.}
-\label{fig1:RBschmema}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig2-1}
+
+}
+
+\end{knitrout}
+\caption{Comparison of replication success at the golden level
+  ($p_S \leq \alpha_S = 0.062$) and the two-trials rule ($p_o \leq 0.025$ and
+  $p_r \leq 0.025$). The dotted areas indicate that success is impossible for
+  original $p$-value $p_o$ and relative effect size $d$. In the white areas
+  success is possible and depends on the relative sample size $c$ as indicated
+  by the grey lines. The dashed black line in the left plot indicates the
+  limiting relative effect size $\dinfty$. }
+\label{fig1:fig2}
 \end{figure}
 
-Good argued that philosophically there is nothing wrong with inferences
-resulting from backwards use of Bayes' theorem, since the theorem merely
-constrains prior and posterior to be consistent with the laws of probability
-(regardless of their conventional names suggesting a particular temporal
-ordering). Despite his advocacy, the reverse-Bayes idea remained largely
-unexplored until \citet{Matthews2001b} introduced the \emph{Analysis of
-Credibility}, which in turn led to new developments in reverse-Bayes methodology
-(see \citet{Held2021b} for a recent review). Most of these approaches use the
-reversal of Bayes' theorem in order to challenge or substantiate the credibility
-of scientific claims. Usually, a posterior inference corresponding to
-(non-)credibility of a claim is specified, and the associated prior is then
-derived from the data. Inference is subsequently carried out based on this
-reverse-Bayes prior, \eg the interest is often to check whether the prior is
-plausible in light of external evidence, an obvious candidate being data from a
-replication study. This can be done, for example, using methods to assess
-prior-data conflict \citep{Box1980, Evans2006}.
-
-% Good, Good Thinking, P. 126:
-%``In some cases it should be possible to make some progress in the estimation of
-% relative initial probabilities by assuming that the current judgements are correct and
-% by using Bayes's theorem backwards. This idea is closely related to the ``device
-% of imaginary results'' in which judgements are made concerning the values that the
-% final probabilities would have after some imaginary results are obtained; then Bayes'
-% theorem is used backwards to estimate what the consistent initial probabilities must
-% be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain estimates
-% of the final probabilities in the light of the actual observations. This device takes
-% \emph{seriously} the view that a theory of probability or of rationality is no more
-% than a theory of consistency.''
-
-In this paper, we consider a reverse-Bayes procedure consisting of two stages
-that naturally fit the replication setting: We first determine a
-\emph{sufficiently sceptical prior} for the effect $\theta$ such that the
-original result is no longer convincing in terms of a suitable Bayes factor.
-Using another Bayes factor, we then quantify replication success by comparing
-how likely the replication data are predicted by the sufficiently sceptical
-prior relative to an \emph{advocacy prior}, which is the posterior of the effect
-$\theta$ conditional on the original data and an uninformative/reference prior.
-Box \hyperref[box:nutshell]{1} provides a summary of the procedure, the
-following sections will explain it in more detail.
-
-% summarize procedure in box
-\begin{table}[!hbt]
+It is interesting to directly compare the two-trials rule and replication
+success at the golden level in terms of the required relative effect size $d$ to
+fulfill the criteria \eqref{eq1:dSig} and \eqref{eq1:res}, respectively, see
+Figure~\ref{fig1:fig2}. If the original $p$-value is not significant at level
+$\alpha$, only replication success can be achieved, but will require a
+replication effect estimate larger than the original one.
+
+For example, four studies with one-sided $p_o \in (0.025, 0.03)$ have been
+included in the \textit{Reproducibility Project: Psychology} \citep{Opensc2015}
+and one of them achieves replication success (see Section \ref{sec1:application}
+for details). By definition, such non-significant original findings can never
+fulfill the two-trials rule.
+
+If the original $p$-value is smaller than $\alpha$, then the situation depends
+on the relative sample size $c$. For example, when the replication sample size
+is chosen to be the same as in the original study ($c=1$) and $\alpha=0.025$,
+original studies with a $p$-value larger than $0.006$ will require a smaller
+relative effect size $d$ with the two-trials rule, while $p$-values smaller than
+$0.006$ will require a smaller relative effect size $d$ with the replication
+success method. This illustrates that the latter method is less stringent than
+the two-trials rule if the original study is already sufficiently convincing.
+
+\section{Power and Type-I Error Rate}\label{sec1:ER}
+Although Bayesian methods do not rely on the frequentist paradigm of repeated
+testing, it is still useful to investigate their frequentist operating
+characteristics \citep{Dawid1982, Rubin1984, Grieve2016} and this also holds for
+the proposed reverse-Bayes assessment of replication success. We first condition
+on the results from the original study and compare the power to achieve
+replication success with the two-trials rule in Section \ref{sec1:powerrep}. We
+then assume that none of the two studies have been conducted and investigate the
+overall Type-I error rate (Section \ref{sec1:T1E}) and the project power (Section
+\ref{sec1:PP}) \citep{Maca2002} over both studies in combination for fixed
+relative sample size $c$.
+
+\subsection{Conditional power}\label{sec1:powerrep}
+
+\begin{figure}[!ht]
 \begin{center}
-\fbox{
-\begin{minipage}{.95\linewidth}
-  \begin{enumerate}[leftmargin=*]
-
-    \item \textbf{Original study}:
-    For the original effect estimate
-$\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$ consider the point null
-hypothesis $H_0 \colon \theta = 0$ vs. $\HS \colon \theta \neq 0$. Fix a level
-$\gamma \in (0, 1)$ and determine the sufficiently sceptical prior under the
-alternative $\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ such that the
-Bayes factor contrasting $H_0$ to $\HS$
-is $$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma.$$ The prior
-$\theta \given \HS$ represents a \emph{sceptic} who remains unconvinced about
-the presence of an effect at level $\gamma$.
-
-    \item \textbf{Replication study}:
-          For the replication effect estimate
-$\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ compute the Bayes factor
-contrasting the sceptic $\HS \colon \theta \sim \Nor(0, \gy \cdot \sigma^2_o)$
-to an advocate $\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$. Declare
-\emph{replication success} at level $\gamma$ if
-          $$\BFcol{\mathrm{S}}{\mathrm{A}}(\that_r; \gy) \leq \gamma,$$
-          \ie the data favour the advocate over the sceptic at a higher level
-than the sceptic's initial objection.
-
-    \item[$\rightarrow$] The \emph{sceptical Bayes factor} $\BFs$ is the
-smallest level $\gamma$ at which replication success can be declared.
- \end{enumerate}
-\end{minipage}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig3-1}
+
 }
+
+\end{knitrout}
 \end{center}
-\caption*{\textbf{\textrm{Box 1}}: Summary of reverse-Bayes assessment of replication success with
-Bayes factors.}
-\label{box:nutshell}
+\caption{Conditional power as a function of the {one-sided} $p$-value of the
+  original study with relative sample size $c=1$ (left) and $c=5$ (right). Shown
+  is conditional power assuming the unknown parameter is equal to the original
+  effect estimate (solid) and conditional power based on 20\% shrinkage of the
+  original effect estimate (dashed) for the two-trials rule (2TR) at level
+  $\alpha = 0.025$ and for replication success at the corresponding golden and
+  nominal level. Power values of exactly zero are omitted.}
+\label{fig1:fig3}
+\end{figure}
+
+Figure~\ref{fig1:fig3} compares the power for replication success
+\citep[see][Section 4 for details]{Held2020} at the golden and at the nominal
+level with the power of the two-trials rule for relative sample size $c = 1$
+(left) and $c = 5$ (right) as a function of the one-sided $p$-value $p_o$ from
+the original study. Shown is the conditional power assuming the unknown
+parameter $\theta$ is equal to the original effect estimate $\hat \theta_o$.
+Then $\hat \theta_r \given \hat \theta_o \sim \Nor(\hat \theta_o, \kappa^2/n_r)$
+and it follows that $d \given \hat \theta_o \sim \Nor(1, 1/(c z_o^2))$. The
+conditional power for replication success can therefore be calculated as
+\begin{equation}\label{eq1:condPower}
+\P(d \geq \dmin \given \hat \theta_o) = \Phi\left[\sqrt{c} z_o (1-\dmin)\right],
+\end{equation}
+where $\dmin$ is given in \eqref{eq1:res}. Predictive power, which is conditional
+power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution for the
+effect size $\theta$, could also be calculated, then
+\mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}. Conditional and
+predictive power of the two-trials rule also depend on $z_o$, $c$ and $\alpha$
+and are given in \citet{Micheloud2020}.
+
+The two-trials rule requires a significant original study and hence it is
+impossible to power a replication study when $p_o > 0.025$. The same applies for
+replication success at the nominal level, where the power is zero for any
+$p_o > 0.025$, regardless of the replication sample size. This is different for
+the golden level, where the conditional power of an original study with
+$0.025 < p_o < 0.062$ is low, but not zero. However, if the original $p$-value
+$p_o$ is slightly smaller than $0.025$, the two-trials rule has a larger power,
+both for $c=1$ and $c=5$. But if the original $p$-value is sufficiently small
+($p_o < 0.006$ for $c=1$), the power for replication success at the golden level
+is larger than the power of the two-trials rule.
+
+Compared to $c=1$, the conditional power for $c=5$ of both the two-trials rule
+and the replication success approach at the golden level increases if
+$p_o \leq \alpha$. A remarkable feature of the replication success approach at
+the golden level is that conditional power can be pushed towards 100\% for large
+enough $c$ if $p_o<\alpha$, but not otherwise. This can be seen from
+\eqref{eq1:condPower} because $\dmin < 1$ for $p_o<\alpha$ and large enough
+relative sample size $c$. On the other hand, for $p_o > \alpha$ conditional
+power for replication success will tend to 0\% for increasing $c$ because
+$\dmin>1$ for all $c$. Finally, for $p_o = \alpha$ the limit is 50\%. The same
+property can be observed at the nominal level, however at the smaller threshold
+$1-\Phi(z_\alpha \sqrt{\varphi})$ which is $0.006$ for $\alpha=0.025$. Only if
+$p_o < 0.006$ will the conditional power for replication success attain 100\%
+for $c \to \infty$. This further highlights the stringency of the nominal level.
+
+The approach described so far takes the original study at face-value since it
+assumes that $\hat \theta_o$ is equal to the unknown effect size $\theta$. In
+practice, however, there are often good reasons to believe that original effect
+estimates have a tendency to be inflated (\eg{} due to publication bias). One way
+to address this issue is to base power calculations on a shrunken version of the
+original effect estimate, where the amount of shrinkage is guided by domain
+knowledge and a risk of bias assessment of the original study. For illustration,
+Figure~\ref{fig1:fig3} also shows conditional power based on 20\% shrinkage of
+the original effect estimate which reduces the conditional power for all
+methods, especially for a relative sample size $c = 1$. Conditional power for
+replication success at the golden level can now be pushed towards 100\% only for
+$p_o < 0.018$, which can be derived by solving \eqref{eq1:alphaPrime} for
+$\alpha$ with $\alpha'=0.025$ and $\dinfty=0.8$. To be able to push conditional
+power based on 20\% shrinkage towards 100\% for all $p_o < 0.025$, equation
+\eqref{eq1:alphaPrime} would have to be used directly to relax the level from
+$\alpha=0.025$ to $\alpha'=0.033$.
+
+\subsection{Overall Type-I error rate}\label{sec1:T1E}
+The two studies are assumed to be independent with Type-I error rate fixed at
+$\alpha$ for each of them, so the Type-I error rate of the two-trials rule over
+the entire project is simply $\alpha^2$ for any value of the relative effect
+size $c$. In contrast, the Type-I error rate of the proposed replication success
+assessment {depends on} the relative sample size $c$.
+
+For $c=1$, \citet[Section 3]{Held2020} showed that $z_S^2$ in
+\eqref{eq1:extrinsic.p2} simplifies to half the harmonic mean of the squared test
+statistics $z_o^2$ and $z_r^2$. The connection $z_S^2 = z_H^2/4$ to the harmonic
+mean $\chi^2$-test statistic $z_H^2$ \citep{Held2020b}, which has a
+$\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
+compute the Type-I error rate at level $\alpha_S$ for $c = 1$ as
+\begin{eqnarray}\label{eq1:T1E}
+\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
+ \right]\right\}/2.
+\end{eqnarray}
+For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type-I error
+rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type-I error rate
+$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type-I error
+rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
+0.0625\%.
+
+For $c \neq 1$, the Type-I error rate can be calculated through numerical
+integration:
+\begin{equation}\label{eq1:T1E0}
+  \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \phi(z_o) \, dz_o,
+\end{equation}
+where $\phi(\cdot)$ denotes the standard normal density function. The first term
+in the integral of \eqref{eq1:T1E0} is the probability of replication success at
+level $\alpha_S$ conditional on a fixed original test statistic $z_o$ and a
+relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
+this term simplifies to
+$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ where $\zrmin$
+in \eqref{eq1:eq.z} depends on $z_o$, $c$, and $\alpha_S$.
+
+\begin{figure}[!h]
+\centering
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig4-1}
+
+}
+
+\end{knitrout}
+
+\caption{Overall Type-I error rate (left) and project power (right) for fixed
+  relative sample size $c$. Results are given for replication success at the
+  nominal and golden level and compared with the two-trials rule (2TR) at
+  $\alpha = 0.025$. The dashed darkgrey line is the project power at the golden
+  level based on significant original studies ($p_o \leq 0.025$). The power of
+  the original study is 90\%.}
+\label{fig1:fig4}
+\end{figure}
+
+The left plot in Figure \ref{fig1:fig4} displays the Type-I error rate for
+$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
+that the Type-I error of the replication success approach decreases with
+increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
+where $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ decreases
+with increasing $c$, because $\zrmin$ increases with increasing $c$, see
+equation \eqref{eq1:eq.z}.
+
+The Type-I error rate of the nominal level is always below the target
+$0.0625$\%. Although the Type-I error will eventually attain $\alpha^2$ in the
+limit $c \downarrow 0$ \citep[Section 3.4]{Held2020}, the nominal level seems to
+be too stringent for realistic values of $c$. The Type-I error rate of the
+golden level is smaller than $0.0625$\% for $c >0.85$. Appropriate Type-I error
+control is thus ensured even for replication studies where the sample size is
+slightly smaller than in the original study.
+
+\begin{figure}[!ht]
+\begin{center}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig5-1}
+
+}
+
+\end{knitrout}
+
+\end{center}
+\caption{Overall Type-I error rate if the replication sample size equal to the
+  original study ($c=1$). The two-trials rule (2TR) is compared to replication
+  success at the golden and nominal level for different values of $\alpha$.}
+\label{fig1:fig5}
+\end{figure}
+
+Figure \ref{fig1:fig5} compares for $c=1$ the Type-I error rate \eqref{eq1:T1E} of
+replication success at the golden and at the nominal level with the two-trials
+rule for different values of $\alpha$. The Type-I error rate of the two-trials
+rule is $\alpha^2$ and the replication success approach at the nominal level
+always has a much smaller Type-I error rate than $\alpha^2$. At the golden level
+the Type-I error rate of the replication success approach is much closer to
+$\alpha^2$, still slightly smaller if $\alpha < 0.058$. For $\alpha = 0.058$ the
+Type-I error rate is equal to the Type-I error rate $0.058^2 = 0.34\%$ of the
+two-trials rule and for $\alpha > 0.058$ the Type-I error rate is slightly
+larger than $\alpha^2$. The Type-I error rate for replication success decreases
+with increasing $c$, so as long as the replication sample size is not smaller
+than the original sample size, Type-I error control at $\alpha^2$ is guaranteed
+at the golden level for any one-sided level $\alpha < 0.058$.
+
+\subsection{Project power}\label{sec1:PP}
+Under the alternative we have $z_o\sim \Nor(\mu, 1)$ with
+$\mu = z_\alpha + z_\beta$ where $\alpha$ is the assumed significance level and
+$1-\beta = \Phi(\mu - z_\alpha)$ is the power to detect the assumed effect
+$\theta = \mu \sigma_o$ in the original study \citep[Section 3.3]{Matthews2006}.
+In the following $\alpha=0.025$ and $\beta=0.1$ are used. The power of a
+significant replication study with sample size $n_r = c n_o$ is
+\begin{equation*}
+\Phi(\theta/\sigma_r - z_\alpha) =
+\Phi(\sqrt{c} \mu - z_\alpha),
+\end{equation*}
+
+so depends on $\mu$ and the relative sample size $c$. The project power of the
+two-trials rule is therefore $(1-\beta) \, \Phi(\sqrt{c} \mu - z_\alpha)$ and
+increases with increasing $c$.
+
+The project power for replication success is computed as
+\begin{equation*}
+  \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \phi(z_o - \mu) \, dz_o
+\end{equation*}
+and shown in the right plot of Figure \ref{fig1:fig4} as a function of $c$. For
+the golden level, the project power quickly increases to values above 90\%,
+whereas the nominal level only reaches around 80\% project power. The project
+power based on the two-trials rule is shown for comparison, which is always
+smaller than for the golden level and converges to 90\% for large $c$.
+
+The advantage in power stems partly from replication success still being
+possible when the original $p$-value is larger than 0.025, but smaller than
+0.062. If we assume that a replication study is only conducted if the original
+study is significant (with $p_o \leq 0.025$), then the project power based on
+the golden level (the dashed line in Figure \ref{fig1:fig4}) is slightly smaller
+and for $c>1$ barely different than for the two-trials rule. More substantial
+gains are still visible for $c < 1$. However, the restriction to original
+studies with $p_o \leq 0.025$ may not reflect current practice in large-scale
+replication projects. For example, 5 out of 143 replication studies considered
+in Section \ref{sec1:application} do have original $p$-values between 0.025 and
+0.062.
+
+\section{Application}\label{sec1:application}
+In this section, we illustrate the proposed methodology using data from four
+replication projects. All four projects reported effect estimates that were
+transformed to correlation coefficients ($r$). This scale allows for easy
+comparison of effect estimates from studies that investigate different phenomena
+and is bounded to the interval between minus one and one. Moreover, the Fisher
+$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$ can be applied to the
+correlation coefficients, resulting in the transformed estimates being
+asymptotically normal with variance which is only a function of the study sample
+size $n$, \ie{} $\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}.
+
+The first data set comprises the results from the \textit{Reproducibility
+  Project: Psychology} \citep{Opensc2015}, whose aim was to replicate 100
+studies, all of which were published in three major Psychology journals in 2008.
+For our purpose only the 73 study pairs from the ``meta-analytic'' subset are
+considered, since only for these studies the standard error of the Fisher
+$z$-transformed effect estimates can be computed \citep{Johnson2016}. The second
+data set comes from the \textit{Experimental Economics Replication Project}
+\citep{Camerer2016} which attempted to replicate 18 experimental economics
+studies published in two high impact economics journals between 2011 and 2015.
+The third data stem from the \textit{Social Sciences Replication Project}
+\citep{Camerer2018} where 21 replications of studies on the social sciences were
+carried out, all of which were originally published in the journals
+\textit{Nature} and \textit{Science} between 2010 and 2015. The last data set
+originates from the \textit{Experimental Philosophy Replicability Project}
+\citep{Cova2018} which involved 40 replications of studies from the emerging
+field of experimental philosophy. Since only for 31 studies effective sample
+size for original and replication study were available simultaneously, only
+these pairs were included. For more information on the data sets see also
+\citet{Pawel2020}.
+
+\begin{table}[!ht]
+    \centering
+\caption{Results for each replication project:
+Relative effect size $d$ (median with 25\% and 75\% quantiles on Fisher's $z$ scale), proportion of
+successful replications with the two-trials rule (2TR) and the replication success (RS)
+approach (at the golden level), and number of studies where the methods disagree.}
+% \resizebox{\textwidth}{!} {
+% latex table generated in R 4.0.5 by xtable 1.8-4 package
+% Fri Nov 25 12:12:30 2022
+\begin{tabular}{lcccc}
+  \toprule
+Project & relative effect size $d$ & 2TR (\%) & RS (\%) & discrepant \\
+  \midrule
+Psychology & 0.29 [0.03, 0.77] & 28.8 & 30.1 & 3/73 \\
+  Experimental Economics & 0.67 [0.35, 0.92] & 55.6 & 55.6 & 0/18 \\
+  Social Sciences & 0.52 [0.13, 0.65] & 61.9 & 52.4 & 2/21 \\
+  Experimental Philosophy & 0.86 [0.47, 1.12] & 74.2 & 71.0 & 1/31 \\
+   \bottomrule
+\end{tabular}
+
+% }
+\label{tab:marginalres}
 \end{table}
 
-\subsection{Data from the original study}
-For the effect estimate $\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$
-from the original study consider a hypothesis test comparing the null hypothesis
-$H_0\colon$ $\theta = 0$ to the alternative $\HS \colon$ $\theta \neq 0$.
-Specification of a prior distribution for $\theta$ under $\HS$ is now required
-for Bayesian hypothesis testing. A typical choice \citep{Jeffreys1961} is a
-local alternative, a unimodal symmetric prior distribution centred around the
-null value. We consider the sceptical prior
-$\theta \given \HS \sim \Nor(0, \sigma^2_s = g \cdot \sigma^2_o)$ with relative
-sceptical prior variance $g$ for this purpose (relative to the variance from the
-original estimate $g = \sigma^2_s/\sigma^2_o$), resembling the $g$-prior known
-from the regression literature \citep{Zellner1986, Liang2008}. The explicit form
-of the Bayes factor is then given by
-\begin{align}
-  \label{eq1:BFo}
-  \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)
-  = \sqrt{1 + g} \cdot
-  \exp\left\{-\frac{1}{2} \cdot \frac{g}{1 + g} \cdot z^2_o\right\}.
-\end{align}
-
-The Bayes factor from equation ~\eqref{eq1:BFo} is shown in Figure ~\ref{fig1:bfo}
-as a function of $g$ and for different original $z$-values $z_o$. For fixed
-$z_o$, it is well known that this Bayes factor is bounded from below by
-\begin{align}
-  \label{eq1:minBFo}
-  \minBF_{o} =
-  \begin{cases}
-    |z_o| \cdot  \exp(-z_o^2/2) \cdot \sqrt{e} & \text{for} ~ |z_o| > 1 \\
-    1 & \text{for} ~ |z_o| \leq 1
-  \end{cases}
-\end{align}
-which is reached at $\gminBFo = \max\{0, z^2_o - 1\}$ \citep{Edwards1963}.
-Further increasing the relative sceptical prior variance increases
-\eqref{eq1:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \to \infty$ for $g \to \infty$
-\citep[][Section 6.1.4]{Bernardo2000}. Hence, for a relative sceptical prior
-variance $g \in [0, \gminBFo]$, the resulting Bayes factor will be
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \in [\minBF_o, 1]$.
+Table~\ref{tab:marginalres} presents overall results for each of the replication
+projects. While the median relative effect size is below one for all of the four
+projects, there are still large differences. For example, the median relative
+effect size is only $0.29$ in the Psychology project, whereas it is $0.86$ in
+the Philosophy project. The degree of shrinkage is also reflected in the success
+rates (according to the two-trials rule and the replication success approach at
+the golden level), which are around 30\% for the former and more than 70\% for
+the latter. The proportion of successful replications is similar for the
+two-trials rule and the replication success approach. In the Experimental
+Economics project the methods perfectly agree, while in the other three projects
+the methods disagree for a few studies.
+
+\begin{figure}[!h]
+\centering
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig6-1}
+
+}
+
+\end{knitrout}
+\caption{Relative effect size $d$ versus original $p$-value $p_o$. Black
+  indicates that replication success was achieved at the golden level while grey
+  indicates that it was not. The diamonds mark studies where the replication
+  success approach (at the golden level) and the two-trials rule disagree. The
+  dashed black line indicates the limiting relative effect size at the golden
+  level with $\alpha = 0.025$. }
+\label{fig2:fig6}
+\end{figure}
+
+Figure~\ref{fig2:fig6} displays the relative effect size $d$ versus the original
+$p$-value $p_o$ for each study pair and stratified by project. Note that one
+study pair from the Philosophy project is not shown due to extremely small
+original $p$-value and another study pair from the Psychology project is not
+shown due to a very large relative effect size. We can see that for most of the
+study pairs, the replication success approach and the two-trials rule lead to
+the same conclusion, only six replications show conflicting results. They are
+highlighted with diamonds in Figure~\ref{fig2:fig6} and their characteristics are
+summarised in Table~\ref{tbl:discrep}.
+\begin{table}[!ht]
+    \centering
+  \caption{Characteristics of studies for which the replication success approach
+    (at the golden level) and the two-trials rule disagree (at one-sided
+    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
+    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
+    and $\tilde{p}_S$.}
+  \label{tbl:discrep}
+\resizebox{\textwidth}{!} {
+% latex table generated in R 4.0.5 by xtable 1.8-4 package
+% Fri Nov 25 12:12:30 2022
+\begin{tabular}{lllllll}
+  \toprule
+Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
+  \midrule
+\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
+  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
+  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
+  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
+  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
+  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
+   \bottomrule
+\end{tabular}%
+}
+\end{table}
+Two studies from the Psychology project show replication success but fail the
+two-trials rule. These studies show $p$-values that are slightly above the
+significance threshold in either original or replication study, but do not
+exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
+replication $p$-value was $p_r = 0.035$, a little too large to pass the
+two-trials rule. However, as the replication effect estimate shrunk only about
+$30$\% compared to the original one, replication success is still achieved.
+Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
+above the significance level, yet the replication led to a highly significant
+result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
+original counterpart, which therefore also resulted in replication success.
+
+The remaining conflicting studies do not show replication success despite
+passing the two-trials rule. In all cases, there is substantial shrinkage of the
+replication effect estimate compared to the original one. For instance, in the
+replication study of \citet{Pyc2010}, the estimate shrunk by $62$\% and the
+replication $p$-value was only significant because the sample size was increased
+by a factor of $c = 9.2$.
+
+This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
+the golden level as described in Section \ref{sec2:goldenthresh}. We may also
+choose a different value for the limiting relative effect size $\dinfty$ at
+$\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
+$\alpha'$ as given in \eqref{eq2:alphaPrime}. Figure \ref{fig2:fig7} compares the
+proportion of successful replications with the replication success approach for
+$\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
+corresponding levels
+$\alpha' \in (0.06, 0.022)$ for
+all four replication projects. We can see that the two proportions agree fairly
+well for all values of $\alpha'$ considered. The number of discrepant studies in
+each project varies between 0 and 3. Only in the Psychology project there are
+some studies which are successful with the replication success approach but not
+the two-trials rule and some studies successful with the two-trials rule but not
+the replication success approach. The proportion of studies where both methods
+are successful (also shown in Figure \ref{fig2:fig7}) is then smaller than the
+proportion of successful replications with either one of the two methods. The
+three discrepant studies from the Psychology project listed in the top three
+rows of Table~\ref{tbl:discrep} are an example of this particular feature.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/plot-BFo-1.pdf}
+
+{\centering \includegraphics[width=\maxwidth]{images/paper1/fig7-1}
+
+}
+
 \end{knitrout}
-\caption{Bayes factor $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of
-relative sceptical prior variance $g$ for different values of
-$|z_o| = |\that_o|/\sigma_o$. Minimum Bayes factors $\minBF_{o}$ are indicated
-by dots. Dashed vertical lines indicate sufficiently sceptical relative prior
-variance $g_{\scriptscriptstyle \gamma}$ at level $\gamma = 1/10$, if they
-exist.}
-\label{fig1:bfo}
+\caption{Proportion of successful replications as a function of the limiting
+  relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
+  equivalent level $\alpha'$ where the corresponding limiting relative effect
+  size is 1. The replication success (RS) approach is compared with the
+  two-trials rule (2TR).}
+\label{fig2:fig7}
 \end{figure}
 
-We now apply the reverse-Bayes idea and challenge the original finding. To do
-so, we fix a level $\gamma$ above which the original finding is no longer
-convincing to us. For example, this could be $\gamma = 1/10$; the threshold for
-strong evidence against $H_0$ according to the classification from
-\citet{Jeffreys1961}. Suppose now there exists a $\gy \leq \gminBFo$ such that
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma$. It can be shown (Appendix
-\ref{appendix:ssrv}) that $\gy$ can be explicitly computed by
-\begin{align}
-\label{ggamma}
-  \gy &=
-  \begin{cases}
-    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
-    \text{undefined} & ~~ \text{else}
-  \end{cases} \\
-  \text{where} ~ q &= \lw{-1} \left(-\frac{z_o^2}{\gamma^2} \cdot
-  \exp\left\{-z_o^2\right\}\right)
-  \nonumber
-\end{align}
-with $\lw{-1}(\cdot)$ the branch of the Lambert $W$ function \citep{Corless1996}
-that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, see Appendix
-\ref{appendix:lambertW} for details about the Lambert $W$ function. The
-sufficiently sceptical prior is then given by
-$\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ and it can be interpreted
-as the view of a sceptic who argues that given their prior belief about the
-effect $\theta$, the observed effect estimate $\hat{\theta}_o$ cannot convince
-them about the presence of a non-null effect at level $\gamma$. An alternative
-data-based interpretation of sufficiently sceptical priors is to see them as the
-priors obtained by updating an initial uniform prior with the data from an
-imaginary study, which was $1/\gy$ times the size of the original study, and
-which resulted in an effect estimate of exactly zero \citep{Held2021b}.
-
-From Figure \ref{fig1:bfo} we can see that the more compelling the original data
-(\ie the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
-variance $\gy$ needs to be in order to make the result no longer convincing at
-level $\gamma$. In the most extreme case, when $|z_{o}| \to \infty$ and $\gamma$
-remains fixed, the sufficiently sceptical prior variance will converge to
-zero (Appendix \ref{appendix:lambertW}). On the other hand, if $|z_o|$ is not
-sufficiently large, $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ will either be
-always increasing in $g$ (if $|z_o| \leq 1$) or it will reach a minimum above
-the chosen level $\gamma$. In both cases the sufficiently sceptical relative
-prior variance $\gy$ is not defined since there is no need to challenge an
-already unconvincing result.
-
-A side note on the Jeffreys-Lindley paradox is worth being mentioned: If a
-$\gy < \gminBFo$ exists, there exists also a $\gy^\prime > \gminBFo$ as the
-Bayes factor monotonically increases in $g > \gminBFo$ and therefore must
-intersect a second time with $\gamma$, due to the paradox. This means that the
-more compelling the original result, the larger $\gy^\prime$ needs to be chosen,
-such that the result becomes no longer convincing at level $\gamma$. However,
-priors which become increasingly diffuse do not represent increasing scepticism
-but rather increasing ignorance. Using \eqref{ggamma} therefore avoids this
-manifestation of the Jeffreys-Lindley paradox, since it determines sceptical
-priors only from the class of priors that become increasingly concentrated for
-increasing evidence (\ie priors with $\gy \leq \gminBFo$). In principle, the
-solution $\gy^\prime > \gminBFo $ could also be computed by replacing the
-$\lw{-1}$ branch of the Lambert $W$ function in \eqref{ggamma} with the $\lw{0}$
-branch, but this will not be of interest to us.
-
-\subsection{Data from the replication study}
-\label{sec1:bfr}
-In order to assess whether the original finding can be replicated in an
-independent study, a replication study is conducted, leading to a new effect
-estimate $\hat{\theta}_r$. In light of the new data, the sceptic is now
-challenged by an advocate of the original finding. This is formalised with
-another Bayes factor, which compares the plausibility of the replication effect
-estimate $\hat{\theta}_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
-sceptical prior $\HS \colon$ $\theta \sim \Nor(0, g \cdot \sigma^2_o)$ relative
-to the advocacy prior $\HA \colon$ $\theta \sim \Nor(\that_o, \sigma^2_o)$. The
-the view of an advocate is represented by $\HA$ since this is the posterior of
-$\theta$ given the original estimate and a uniform prior (also the reference
-prior for this model). The Bayes factor is given by
-\begin{align}
-  \label{eq1:BFr}
-  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
-%%   &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
-%%   \exp\left\{-\frac{1}{2}\left(\frac{z_r^2}{1/c + g} -
-%%   \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}
-  &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
-  \exp\left\{-\frac{z_o^2}{2}\left(\frac{d^2}{1/c + g} -
-  \frac{\left(d - 1\right)^2}{1/c + 1} \right)\right\}
-\end{align}
-so it depends on the original $z$-statistic $z_o$, the relative sceptical prior
-variance $g$, the relative effect estimate $d = \that_r/\that_o$, and the
-relative variance $c = \sigma^2_o/\sigma^2_r$.
-
-Our goal is now to define a condition for \emph{replication success} in terms of
-\eqref{eq1:BFr}. It is natural to consider a replication successful if the
-replication data favour the advocate over the sceptic to a higher degree than
-the sceptic's initial objection to the original study. More formally, we say
-that if the Bayes factor from \eqref{eq1:BFr} evaluated at the sufficiently
-sceptical relative prior variance $\gy$ is not larger than the corresponding
-level $\gamma$ used to define the sufficiently sceptical prior:
-\begin{align}
-  \label{eq1:success}
-  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
-  \leq \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) =\gamma,
-\end{align}
-we have established \emph{replication success at level $\gamma$}.
-
-For example, if we observe $z_o = 3$ (equivalent to minimum Bayes factor
-$\minBF_{o} = 1/18$) and choose a level $\gamma = 1/10$
-the sufficiently sceptical relative prior variance \eqref{ggamma} is
-$\gy = 1.6$. If a replication is conducted with the
-same precision ($c = 1$) and we observe $z_r = 2.5$ (equivalent to
-minimum Bayes factor $\minBF_{r} = 1/5.5$ and relative effect
-estimate $d = z_{r}/(z_{o}\sqrt{c}) = 0.83$), using equation
-\eqref{eq1:BFr} this would lead to $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r;
-1.6) = 1/3.5$, which means
-that the replication was not successful at level $\gamma = 1/10$.
-However, if we had chosen a less stringent level, \eg$\gamma =
-1/3$, the replication would have been considered successful
-since then $\gy = 0.4$ and
-$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; 0.4)
-= 1/7.4$.
-
-\subsection{The sceptical Bayes factor}
-Apart from specifying a level $\gamma$, the described procedure offers an
-automated way to assess replication success. One way to remove this dependence
-is to find the smallest level $\gamma$ where replication success can be
-established. We thus call this level the \emph{the sceptical Bayes factor}
-\begin{align}
-  \label{eq1:bfs}
-  \BFs
-  =
-  %% \inf_{\gy \in [0, \gminBFo]}
-  \inf
-  \Big\{\gamma :
-  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
-  \leq \gamma\Big\},
-\end{align}
-and replication success at level $\gamma$ is equivalent with $\BFs \leq \gamma$.
-
-Figure \ref{fig1:bfs} shows $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ as a function of $\gy$ for several
-values of $z_o$ and $d$ along with the corresponding $\BFs$. Typically, $\BFs$
-is given by the height of the intersection between
-$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ in $\gy$. It may also happen that
-$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ remains below
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ for all values of $\gy$, in such
-situations $\BFs$ is equal to the original minimum Bayes factor $\minBF_o$.
-Finally, in some pathological cases it may happen that either $z_o$, $d$, or
-both are so small that replication success cannot be established for any level
-$\gamma$ and hence $\BFs$ does not exist. This means that the replication study
-was unsuccessful since it is impossible for the advocate to convince the sceptic
-at any level of evidence.
-
-\begin{figure}[!htb]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/plot-BFs-1}
-\end{knitrout}
-\caption{Bayes factors $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of the sufficiently
-sceptical relative prior variance $\gy$. In all examples
-$c = \sigma^2_o/\sigma^2_r = 1$. Minimum Bayes factors $\minBF_o$ are indicated
-by dots, sceptical Bayes factors $\BFs$ are indicated by crosses where existent.}
-\label{fig1:bfs}
-\end{figure}
-
-In terms of computing the sceptical Bayes factor, it is worth noting that for
-the special case when the replication is conducted with the same precision as
-the original study ($c = 1$) and $\BFs$ is located at the intersection of
-$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
-$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ in $g$, there is an explicit expression
-for $\BFs$
-\begin{align}
-  \label{eq1:BFsc1}
-  \BFs =
-  \sqrt{-\frac{z^2_{o}}{k} \cdot \frac{1 + d^{2}}{2}} \cdot
-  \exp\left\{-\left(\frac{z_o^2}{2} + \frac{k}{1 + d^2}\right)\right\}
-\end{align}
-with
-$$k = \lw{}\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{d^{2} + 1}{2} \cdot \exp\left\{-\frac{z_o^2}{2}
-  \left[1 + \frac{(1 -
-d)^2}{2}\right]\right\}\right),$$ see Appendix \ref{appendix:bfs} for details.
-
-\section{Properties}
-\label{sec1:comparison}
-To study properties of the sceptical Bayes factor and facilitate comparison with
-other methods we will look at the requirements for replication success based on
-the relative effect estimate $d = \that_{r}/\that_{o}$, the variance ratio
-$c = \sigma^{2}_{o}/\sigma^{2}_{r}$ and the original minimum Bayes factor
-$\minBF_{o}$ (respectively the original $z$-value $z_{o}$). This perspective is
-helpful because it disentangles how the method reacts to changes in
-compatibility of the effect estimates ($d$), evidence from the original study
-($\minBF_{o}$), and the change in sample size of the replication compared to the
-original study ($c$).
-
-The condition for replication success at level $\gamma$ from \eqref{eq1:success}
-is equivalent to
-\begin{align}
-  \label{eq1:RSCond-d}
-  \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
-  \frac{z_o^2}{1 + 1/\gy} &\leq z_o^2 \left(\frac{d^2}{1/c +
-    \gy} - \frac{\left(d - 1\right)^2}{1/c + 1} \right).
-\end{align}
-On the right-hand side of~\eqref{eq1:RSCond-d} the $Q$-statistic
-\begin{align}
-  \label{eq1:Qstat}
-  Q
-  = \frac{(\hat{\theta}_o - \hat{\theta}_r)^2}{\sigma^2_o + \sigma^2_r}
-  %% = \frac{(z_r - z_o\sqrt{c})^2}{1 + c}
-  = \frac{z_o^2(d - 1)^2}{1/c + 1}
-\end{align}
-appears. The $Q$-statistic was proposed as a measure of incompatibility among
-original and replication effect estimates since its distribution is known for
-standard meta-analytic models of effect sizes \citep{Hedges2019}. The connection
-to the sceptical Bayes factor is such that $Q$ acts as a penalty term
-in~\eqref{eq1:RSCond-d} and a larger value will lower the degree of replication
-success possible. However, as we will see, the sceptical Bayes factor goes
-beyond assessing effect estimate compatibility as there is also a trade-off with
-the amount of evidence that the replication study provides against the null.
-
-Applying some algebraic manipulations to \eqref{eq1:RSCond-d}, one can show that
-replication success at level $\gamma$ is achieved if and only if the relative
-effect estimate $d$ falls within a success region given by
-\begin{align}
-  \label{eq1:dsuccess}
-  \begin{cases}
-    d \not\in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy < 1 \\
-    d \geq [1 + (1 + 1/c)\{1/2 - \log(2)/z_o^2\}]/2
-    & \text{if} ~ \gy = 1 \\
-   d \in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy > 1\\
-  \end{cases}
-\end{align}
-where
-\begin{align*}
-  M &= \frac{1/c + \gy}{\gy - 1} \\
-  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\}\Bigm/ z_o^2 +
-  \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \\
-  B &= \frac{1 - \gy}{(1/c + \gy)(1/c + 1)}.
-\end{align*}
-
-The top-left plot in Figure~\ref{fig1:dcomparison} shows the conditions on $d$
-from~\eqref{eq1:dsuccess} to achieve replication success at level $\gamma = 1/3$
-as a function of the original minimum Bayes factor $\minBF_{o}$ and for
-different values of the relative variance $c$. It is important to note that
-$\gamma = 1/3$ is an arbitrary choice and in practice one should interpret the
-sceptical Bayes factor as a quantitative measure of replication success. Only
-the success regions for positive $d$ are shown as replication success in the
-opposite direction is usually not of interest (see
-Section~\ref{sec1:replicationParadox} for a discussion of this issue). We see
-that with increased precision of the replication study (larger $c$), the success
-regions shift closer to zero. This means that the method allows for more
-shrinkage of the replication effect estimate when the replication provides more
-evidence against the null (because $\abs{z_{r}} = d \abs{z_{o}} \sqrt{c}$
-increases with increasing $c$). However, the success regions cannot be pushed
-arbitrarily close to zero but are bounded away. So when $c \to \infty$ the
-methods still requires the replication estimate to be sufficiently large,
-despite that the evidence against the null becomes overwhelming (since
-$\abs{z_{r}} \to \infty$ as $c \to \infty$).
-
-\begin{figure}[!htb]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/plot-success-region-comparison-1}
-\end{knitrout}
-\caption{Required relative effect estimate $d = \that_{r}/\that_{o}$ to achieve
-  replication success based on the sceptical Bayes factor
-  ($\BFs \leq 1/3$), the two-trials rule (2TR:
-  $\minBF_{o} \leq 1/3$ and $\minBF_{r} \leq 1/3$),
-  the replication Bayes factor ($\BFr \leq 1/3$), and the
-  recalibrated sceptical $p$-value
-  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$ with
-  $\gamma = 1/3$) as a function of the original minimum
-  Bayes factor $\minBF_{o}$ (respectively the corresponding $z$-value $z_{o}$)
-  for different values of the relative variance
-  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. Shading indicates regions where
-  replication success is possible. Only positive relative effect estimates $d$
-  are shown.}
-\label{fig1:dcomparison}
-\end{figure}
-
-By definition the sceptical Bayes factor can never be smaller than $\minBF_{o}$,
-so replication success at level $\gamma$ is impossible for original studies with
-$\minBF_{o} > \gamma$. This property is visible in the top-left plot in
-Figure~\ref{fig1:dcomparison} by the cut-off at $\minBF_{o} = \gamma = 1/3$. In
-contrast, for more convincing original studies with $\minBF_{o} < 1/3$
-replication success is possible and two cases can be distinguished in terms of
-the success region: When $1/4.5 < \minBF_{o} \leq 1/3$ the
-sufficiently sceptical relative prior variance is $\gy > 1$ and thus by
-condition~\eqref{eq1:dsuccess} the success region consists of an interval
-$(\dmin, \dmax)$. Hence, in this case the method also penalises too large
-replication effect estimates. For original studies with
-$\minBF_{o} < 1/4.5$, the sufficiently sceptical relative prior
-variance is $\gy \leq 1$, so due to~\eqref{eq1:dsuccess} the success region for
-positive $d$ is given by $(\dmin, \dmax = \infty)$. This means that for more
-convincing original studies there are no upper restrictions for the relative
-effect estimate, whereas shrinkage of the replication estimate is still
-penalised.
-
-\subsection{Comparison with other methods}
-Of interest is the relationship between the sceptical Bayes factor and other
-measures of replication success. Here, we review and compare a classical (the
-two-trials rule), a forward-Bayes \citep[the replication Bayes factor
-from][]{Verhagen2014} and a reverse-Bayes method \citep[the sceptical $p$-value
-from][]{Held2020}. These methods provide a useful benchmark as they all are
-based on hypothesis testing, have unique properties, and can be directly
-compared in terms of their replication success regions as shown in
-Figure~\ref{fig1:dcomparison}.
-
-\subsubsection{The two-trials rule}
-Replication success is most commonly declared when both original and replication
-study provide compelling evidence against a null effect. This approach is also
-known as the \emph{two-trials rule} in drug development and usually a
-requirement for drug approval \citep[Section 9.4]{Kay2015}. Most replication
-projects report $p$-values associated with the effect estimates as measures of
-evidence against the null, but also default Bayes factors have been used
-\citep[see \eg the Bayesian supplement of][]{Camerer2018}. To compare the
-two-trials rule with methods based on Bayes factors we will study the two-trials
-rule based on the minimum Bayes factor from~\eqref{eq1:minBFo}, \ie replication
-success at level $\gamma$ is established when both
-$\minBF_{k} % = \abs{z_{k}}\exp(-z_{k}^{2}/2)\sqrt{e}
-\leq \gamma$ for $k \in \{o, r\}$, as well as
-$\sign(\hat{\theta}_o) = \sign(\hat{\theta}_r)$. This approach has a one-to-one
-correspondence to the usual version of two-trials rule as minimum Bayes factors
-and $p$-values both only depend on the $z$-values of original and replication
-study.
-
-The two-trials rule guarantees that both studies provide compelling evidence
-against the null. Similarly, the sceptical Bayes factor requires the original
-study to be compelling on its own since it can never be smaller than
-$\minBF_{o}$. However, one can easily construct examples where the sceptical
-Bayes factor is smaller than the minimum Bayes factor from the replication study
-(\eg when $\minBF_{o} = 1/2$,
-$\minBF_{r} = 1/1.5$, and $c = 1$
-we obtain $\BFs = 1/1.9$). So for the same level of
-replication success $\gamma$ the two-trials may not flag replication success
-whereas the sceptical Bayes factor would.
-
-By definition the two-trials rule can never be fulfilled when the original study
-was uncompelling. Assuming now that $\minBF_{o} < \gamma$, replication success
-with the two-trials rule at level $\gamma$ is achieved if and only if the
-relative effect estimate is
-\begin{align}
-  \label{eq1:2TR}
-  d \geq \frac{z_{\gamma}}{z_{o} \sqrt{c}}
-\end{align}
-with $z_{\gamma} > 1$ corresponding to
-$\minBF = z_{\gamma}\exp(-z_{\gamma}^{2}/2)\sqrt{e} = \gamma$. The success
-region from~\eqref{eq1:2TR} is displayed in the top-right plot of
-Figure~\ref{fig1:dcomparison}. We see that the success regions shift closer to
-zero as the relative variance $c$ increases. Also there is a cut-off at
-$\minBF_{o} = \gamma = 1/3$ similarly as with the sceptical Bayes factor. In
-contrast to the sceptical Bayes factor, however, the two-trials can be fulfilled
-for any arbitrary small (but positive) relative effect estimate $d$, provided
-the relative variance $c$ is large enough. Hence, the two-trials rule may flag
-success even when the replication effect estimate is much smaller than the
-original one.
-
-\subsubsection{The replication Bayes factor}
-\citet{Verhagen2014} proposed the \emph{replication Bayes factor} as a measure
-of replication success. It is defined as the Bayes factor comparing the point
-null hypothesis $H_0 \colon \theta = 0$, to the alternative that the effect is
-distributed according to the posterior distribution of $\theta$ after observing
-the original data. For the normal model considered so far and if an initial
-reference prior was chosen, this alternative is also the advocacy prior
-$\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$ and therefore the replication
-Bayes factor is given by
-\begin{align}
-  \label{eq1:BFrep}
-  \BFr
-  = \BFcol{\mathrm{0}}{\mathrm{A}}(\hat{\theta}_r)
-  %% = \sqrt{1 + c} \cdot
-  %% \exp\left\{-\frac{1}{2} \left(z_r^2 -
-  %% \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}.
-  = \sqrt{1 + c} \cdot
-  \exp\left\{-\frac{z_o^2}{2} \left(d^2 \cdot c -
-  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}.
-\end{align}
-
-Similarly, as with the sceptical Bayes factor, the $Q$-statistic
-from~\eqref{eq1:Qstat} appears in~\eqref{eq1:BFrep} and acts as a penalty term,
-\ie larger values of $Q$ lower the degree of replication success. However, in
-contrast to the sceptical Bayes factor, the replication Bayes factor is not
-limited by the evidence from the original study because $\BFr \downarrow 0$ as
-$c \to \infty$ provided $z_{o} \neq 0$ and $d \neq 0$. Moreover, we have that
-\begin{align*}
-  1 \geq \BFs \geq \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs})
-  = \BFcol{\mathrm{S}}{0}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs}) \cdot \underbrace{\BFcol{0}{\mathrm{A}}(\hat{\theta}_r)}_{= \BFr}.
-\end{align*}
-So the sceptical Bayes factor is larger than the replication Bayes factor if the
-replication data favour the sceptical prior
-$\HS \colon \theta \sim \Nor(0, g_{\scriptscriptstyle \BFs} \cdot \sigma^{2}_{o})$
-over the null hypothesis. They can only coincide when $\BFs = 1$ since then
-$g_{\scriptscriptstyle \BFs} = 0$.
-
-We can also determine conditions on the relative effect estimate in terms of
-replication success based on $\BFr \leq \gamma$. The replication success region
-is given by
-\begin{align}
-  \label{eq1:BFRsuccess}
-  d \not\in [-\sqrt{J} - H, \sqrt{J} - H]
-\end{align}
-with
-\begin{align*}
-  J &= \left\{1 + \frac{\log(1 + c) - 2 \log \gamma}{z_o^2}\right\} \cdot
-  \frac{1/c + 1}{c} \\
-  H &= \frac{1/c + 1}{1 + c}.
-\end{align*}
-The condition \eqref{eq1:BFRsuccess} implies that replication success can also be
-achieved for negative relative effect estimates $d$ (see
-Section~\ref{sec1:replicationParadox} for a discussion of this issue). The
-bottom-left plot in Figure~\ref{fig1:dcomparison} shows the conditions
-from~\eqref{eq1:BFRsuccess} for positive relative effect estimates. As with the
-two-trials rule, the success region of the replication Bayes factor can be
-pushed arbitrarily close to zero by increasing the relative variance $c$. In
-contrast to the two-trials rule, however, replication success can also be
-achieved for original studies with $\minBF_{o} > 1/3$.
-
-\subsubsection{The sceptical \textit{p}-value}
-Of particular interest is the relationship between the sceptical Bayes factor
-and the sceptical $p$-value \citep{Held2020}, as it is the outcome of a similar
-reverse-Bayes procedure. One also considers a sceptical prior for the effect
-size $\theta \sim \Nor(0, \tau^2)$, the sufficiently sceptical prior variance at
-level $\alpha$ is then defined as $\tau^2 = \tau^2_\alpha$ such that the
-$(1 - \alpha)$ credible interval for $\theta$ based on the posterior
-$\theta \given \that_o, \tau^2_\alpha$ does not include zero. Replication
-success is declared if the tail probability of the replication effect estimate
-under its prior predictive distribution
-$\that_r \given \tau^2_\alpha \sim \Nor(0, \tau^2_\alpha + \sigma^2_r)$ is
-smaller than $\alpha$. The smallest level $\alpha$ where replication success can
-be established defines the sceptical $p$-value. In contrast to the sceptical
-Bayes factor, the sceptical $p$-value always exists and there are closed form
-expressions to compute it for all values of $c$, \ie
-$\ps = 1 - \Phi(z_{\mathrm{S}})$ with
-\begin{equation*}
-  z^2_{\mathrm{S}} =
-  \begin{cases}
-    z^2_H/2 & \text{for}~c=1 \\ \frac{1}{c - 1}\left\{\sqrt{z^2_A\left[z^2_A +
-          (c - 1)z^2_H\right]} - z^2_A\right\} & \text{for}~c \neq 1
-  \end{cases}
-  \label{eq1:z2s}
-\end{equation*}
-where $z^2_H = 2/(1/z_o^2 + 1/z_r^2)$ the harmonic mean,
-$z^2_A = (z_o^2 + z_r^2)/2$ the arithmetic mean of the squared $z$-statistics,
-and provided that $\sign(\that_o) = \sign(\that_r)$ (otherwise
-$\ps = \Phi(z_{\mathrm{S}})$).
-
-Similar to the two-trials rule, the sceptical $p$-value requires both studies to
-provide compelling evidence due to the property that
-$\ps \geq \max\{p_o, p_r\}$. The sceptical $p$-value also penalises the case
-when the replication effect estimate shrinks as compared to the original one
-since it monotonically increases with decreasing relative effect estimate $d$
-\citep[Section 3.1]{Held2020}.
-
-\citet{Held2021} showed that replication success based on
-$\ps \leq \alpha_{\mathrm{S}}$ is achieved when
-\begin{align}
-  \label{eq1:psSuccessd}
-  d \geq \sqrt{\frac{1/c + 1/(K - 1)}{K}}
-\end{align}
-with $K = z_{o}^{2}/z_{\alpha_{\mathrm{S}}}^{2}$ where
-$z_{\alpha_{\mathrm{S}}} = \Phi^{-1}(1 - \alpha_{\mathrm{S}})$. Thresholding the
-sceptical $p$-value with the ordinary significance level $\alpha$ for
-traditional $p$-values leads to a very stringent criterion for replication
-success. For example, when $z_{o} = 2$, $\alpha = 0.025$, and
-$c = 2$, the replication effect estimate needs to be
-$d = 4.87$ times larger than the original one. Therefore,
-\citet{Held2021} used~\eqref{eq1:psSuccessd} to determine the \emph{golden level}
-$\alpha_{\mathrm{S}} = 1 - \Phi(z_\alpha/\sqrt{\varphi})$ with
-$\varphi = (1 + \sqrt{5})/2$ the golden ratio. The golden level ensures that
-borderline significant original studies ($\abs{z_{o}} = z_{\alpha}$) can still
-achieve replication success provided the replication effect estimate does not
-shrink compared to the original one ($d \geq 1$). Instead of comparing the
-sceptical $p$-value to the golden level ($\ps < \alpha_{\mathrm{S}}$), one can
-compute a recalibrated sceptical $p$-value
-$\tilde{p}_{\mathrm{S}} = 1 - \Phi(z_{\mathrm{S}} \sqrt{\varphi})$ and compare it to
-the ordinary significance level ($\tilde{p}_{\mathrm{S}} < \alpha$).
-
-The bottom-right plot in Figure~\ref{fig1:dcomparison} shows the success region
-for the recalibrated sceptical $p$-value. We see that increasing the precision
-of the replication study lowers the required minimum relative effect estimate
-$\dmin$ as for all other methods. Similarly, as with the sceptical Bayes factor,
-$\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily close to zero.
-However, its limiting minimum relative effect estimate in $c$
-($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
-factor when $\minBF_{o} < 1/5.6$, while for
-$\minBF_{o} > 1/5.6$ it is the other way around. So for more
-convincing original studies the sceptical $p$-value is less stringent than the
-sceptical Bayes factor. Due to the recalibration, the sceptical $p$-value also
-allows replication success when the $\minBF_{o} > \gamma$. This is visible in
-the bottom-right plot of Figure~\ref{fig1:dcomparison} where the success region
-has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
-the sceptical Bayes factor.
-
-\subsection{Paradoxes in the assessment of replication success}
-The replication setting is different from the classical setting where data from
-only one study are analysed. As a result, several unique paradoxes may occur.
-
-\subsubsection{The replication paradox}
-\label{sec1:replicationParadox}
-The \emph{replication-paradox} \citep{Ly2018} occurs when original and
-replication effect estimates go in opposite directions
-($\sign(\that_{o}) \neq \sign(\that_{r})$) but a method flags replication
-success. This is undesired since effect direction is crucial to most
-scientific theories and research questions.
-
-The two-trials rule and the sceptical $p$-value both avoid the replication
-paradox by using one-sided test-statistics. In contrast, the sceptical Bayes
-factor and the replication Bayes factor may suffer from the paradox as their
-success regions from~\eqref{eq1:dsuccess} and~\eqref{eq1:BFRsuccess},
-respectively, include negative relative effect estimates $d < 0$. This is
-related to the fact that Bayes factors are quantifying relative evidence: When
-the replication estimate goes in the opposite direction, it will be poorly
-predicted by the sceptical prior $\HS$ and the advocacy prior $\HA$, yet when
-$\HS$ is mostly concentrated around zero (or a point-null in case of the
-replication Bayes factor), replication estimates going in the opposite direction
-may still be better predicted by $\HA$.
-
-In practice, the replication paradox is hardly an issue, since replications
-rarely show such contradictory results, \eg to achieve replication success at
-level $\gamma = 1/3$ with
-$\minBF_{o} = 1/10$ and $c = 1$, the
-relative effect estimate needs to be $d < -7.09$ for the
-paradox to appear with the sceptical Bayes factor. The replication Bayes factor
-is more prone to the paradox because its point-null hypothesis fails more
-strongly to predict estimates in opposite direction, \eg for the same numbers as
-before it requires $d < -2.66$.
-
-In both cases the paradox can be overcome by truncating the advocacy prior $\HA$
-such that only effects in the same direction as the original estimate $\that_o$
-have non-zero probability, \ie for positive $\that_{o}$ consider
-$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \, \mathbb{1}_{(0, \infty)}(\theta)$,
-where $\mathbb{1}_{B}(x)$ is the indicator function of the set $B$. The Bayes
-factor contrasting $\HS$ to $\HAp$ turns out to be
-\begin{align}
-  \BFcol{\mathrm{S}}{\mathrm{A}^\prime}(\hat{\theta}_r; g)
-  &= \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
-  \frac{\Phi(\abs{z_o})}{\Phi\left\{\mathrm{sign}(z_o)
-    %     \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}} \right\}}
-    \frac{z_o(1 + dc)}{\sqrt{1 + c}} \right\}}
-   \label{eq1:BFrtrunc}
-\end{align}
-where $\Phi(\cdot)$ is the cumulative distribution function of the standard
-normal distribution (see Appendix \ref{app:BFtrunc}). Hence, \eqref{eq1:BFrtrunc}
-is the Bayes factor under the standard advocacy prior multiplied by a correction
-term. Determining the smallest level of replication success
-with~\eqref{eq1:BFrtrunc} leads to a corrected sceptical Bayes factor, while
-setting $g = 0$ in~\eqref{eq1:BFrtrunc} leads to a corrected replication Bayes
-factor. The correction term goes to one when the replication estimate goes in
-the same direction as the original one and the replication sample size increases
-($d > 0$ and $c \to \infty$), but it penalises when the replication estimate
-goes in the opposite direction ($d < 0$ and $c \to \infty$).
-
-This modification guarantees that the replication paradox is avoided and we
-recommend to compute the sceptical Bayes factor using~\eqref{eq1:BFrtrunc} in
-cases where the replication paradox is likely to appear. However, truncated
-priors are unnatural and hard to interpret. Also the non-truncated advocacy
-prior penalises effect estimate incompatibility and the
-modification~\eqref{eq1:BFrtrunc} will only make a difference in extreme
-situations. Due to its easier mathematical treatment we will focus on the
-standard version of the procedure in the remaining part of the paper.
-
-\subsubsection{The shrinkage paradox}
-The comparison showed that for certain methods replication success is still
-achievable even when the replication estimate is substantially smaller than the
-original one. However, a substantially smaller effect estimate in the
-replication does not reflect an effect size of the same practical importance as
-the original one and a method should thus not flag replication success. The {\em
-shrinkage paradox} occurs if a particular method may flag replication success
-for any arbitrarily small (but positive) relative effect estimate.
-
-Two forms of the shrinkage paradox can formally be distinguished: the
-\emph{shrinkage paradox at replication} appears when, for fixed evidence from
-the original study $\minBF_{o}$ (respectively $z_{o}$), the minimum relative
-effect estimate $\dmin > 0$ required for replication success at a fixed level
-$\gamma$ becomes arbitrarily small as the relative variance $c$ increases:
-\begin{align*}
-  \dmin \downarrow 0 ~\text{as}~ c \to \infty.
-\end{align*}
-\citet{Held2021} found that this form of the paradox occurs for the two-trials
-rule but not for the sceptical $p$-value. Similarly, the minimum relative effect
-estimate $\dmin$ of the sceptical Bayes factor is bounded away from zero, while
-it converges to zero for the replication Bayes factor
-(Appendix~\ref{app:shrinkage}). Hence, among the Bayes factor methods, the
-sceptical Bayes factor avoids the paradox, whereas the replication Bayes factor
-suffers from it.
-
-The shrinkage paradox at replication is a serious issue since it depends on the
-relative variance $c$ which can usually be directly influenced by changing the
-replication sample size. However, there is also a second form of the paradox
-which is affected only by evidence from the original study. The \emph{shrinkage
-paradox at original} appears when, for fixed relative variance $c$, the minimum
-relative effect estimate $\dmin > 0$ required for replication success at a fixed
-level $\gamma$ becomes arbitrarily small as the evidence in the original study
-increases:
-\begin{align*}
-  \dmin \downarrow 0 ~\text{as}~ z_{o}^{2} \to \infty.
-\end{align*}
-
-The replication Bayes factor and the sceptical Bayes factor do not suffer from
-this form of the paradox, while the two-trials rule and the sceptical $p$-value
-do (Appendix~\ref{app:shrinkage}). Hence, with the latter two methods, shrinkage
-of the replication effect estimate is hardly penalised when the original study
-was already very convincing.
-
-\subsection{Frequentist properties}
-Despite the fact that Bayesian methods do not rely on repeated testing, it is
-still often of interest to study their frequentist operating characteristics
-\citep{Dawid1982, Grieve2016}. This is especially important in the replication
-setting where regulators and funders usually require from statistical methods to
-have appropriate error control. We will therefore study and compare type I error
-rate as well as power of the sceptical Bayes factor and other methods.
-
-\subsubsection{Global type I error rate}
-The probability for replication success at level $\gamma$ conditional on the
-original result $z_{o}$ and the relative variance $c$ can be easily computed as
-shown in Appendix~\ref{app:powerBFs}. Under the null hypothesis
-($H_{0}: \theta = 0$) the distribution of the $z$-values is
-$z_{o}, z_{r} \given H_{0} \sim \Nor(0, 1)$ and hence the global type I error
-rate (T1E) based on $\BFs \leq \gamma$ is
-\begin{align*}
-  \text{T1E} = 2 \int_{z_{\gamma}}^{\infty} \P(\BFs \leq \gamma \given z_{o}, c) \phi(z_{o}) \,
-  \text{d}z_{o}
-\end{align*}
-with $\phi(\cdot)$ the standard normal density function. In a similar fashion
-one can compute the type I error rate of the sceptical $p$-value \citep[see
-Section 3 in][]{Held2021}, as well as the replication Bayes factor
-(Appendix~\ref{app:powerBFr}). The type I error rate of the two trials rule is
-simply $\text{T1E} = 2\{1 - \Phi(z_{\gamma})\}^{2}$.
-
-\begin{figure}[!htb]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/T1E-comparison-1}
-\end{knitrout}
-\caption{Type I error rate of the two-trials rule (2TR: $\minBF_{o} \leq \gamma$
-  and $\minBF_{r} \leq \gamma$), the replication Bayes factor
-  ($\BFr \leq \gamma$), the sceptical Bayes factor ($\BFs \leq \gamma$), and the
-  recalibrated sceptical $p$-value
-  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$) as a function of the
-  relative variance $c = \sigma^{2}_{o}/\sigma^{2}_{r}$ for different levels of
-  replication success $\gamma$.}
-\label{fig1:t1ec}
-\end{figure}
-
-Figure~\ref{fig1:t1ec} compares the type I error rates of the four methods for
-different levels $\gamma$. The conventional nominal
-$\text{T1E} = 0.05 \times 0.025$ (two independent experiments with two-sided
-testing in the first and one-sided testing in the second) along with the
-corresponding level ($z_{\gamma} = 1.96$ corresponding to $\gamma = 1/2.1$ and
-$\alpha = 0.025$) is also indicated. In contrast to the other methods, the type
-I error rate of the two trials rule does not depend on the relative variance $c$
-and therefore does not change for the same level $\gamma$. Type I error rates of
-sceptical $p$-value and sceptical Bayes factor are decreasing with increasing
-$c$, the former usually being slightly smaller than the latter. The point at
-which both become smaller than the type I error rate from the two-trials rule
-becomes smaller with more stringent level $\gamma$. Roughly speaking the type I
-error rate of the sceptical Bayes factor is controlled at the conventional level
-when $c$ is slightly larger than one, while for the sceptical $p$-value it is
-controlled when $c$ is slightly below one. Surprisingly, the type I error rate
-of the replication Bayes factor is non-monotone in $c$ and far higher compared
-to the other methods. This suggests that a more stringent level $\gamma$ should
-be used for the replication Bayes factor compared to the other methods to ensure
-appropriate type I error control.
-
-\subsubsection{Power conditional on the original study}
-Another frequentist operating characteristic is the probability to establish
-replication success assuming there is an underlying effect (power). While in
-principle original and replication study could be powered simultaneously, we
-will assume the original study has already been conducted since this is the
-usual situation. The power to establish replication success $\BFs \leq \gamma$
-can be computed using the result from Appendix~\ref{app:powerBFs} and either
-assuming that the underlying true effect corresponds to its estimate from the
-original study (\emph{conditional power}) or using the predictive distribution
-of the replication effect estimate based on the advocacy prior (\emph{predictive
-  power}) \citep{Spiegelhalter1986b, Micheloud2020}. In practice, both forms may
-be too optimistic as original results are often inflated due to publication bias
-and questionable research practices. One solution is to shrink the original
-effect estimate for power calculations \citep{Pawel2020, Held2021}, but we will
-not focus on this aspect here as this would not provide much more insight but
-simply lower the power curves of all methods.
-
-\begin{figure}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/power-plots-1}
-\end{knitrout}
-\caption{Power of the two-trials rule (2TR: $\minBF_{o} \leq
-1/3$ and $\minBF_{r} \leq
-1/3$), the replication Bayes factor ($\BFr
-\leq 1/3$), the sceptical Bayes factor ($\BFs
-\leq
-1/3$), and the recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}
-\leq 1 - \Phi\{z_{\gamma}\}$ with $\gamma =
-1/3$) as a function of the relative variance $c
-= \sigma^2_o/\sigma^2_r$ for different original $z$-values $z_o =
-\that_o/\sigma_o$ (respectively corresponding minimum Bayes factor $\minBF_o$).}
-\label{fig1:condpower}
-\end{figure}
-
-Figure~\ref{fig1:condpower} shows conditional and predictive power as a function
-of the relative variance $c$ and for several values of of the original $z$-value
-$z_o$ (respectively original minimum Bayes factor $\minBF_{o}$). In general,
-uncertainty about replication success is higher for predictive power, leading it
-to be closer to 50\% in all cases. As can also be seen, if the original result
-was not convincing on its own (\eg if $z_o = 1.5$ or $z_{o} = 2$), it is
-impossible to achieve replication success with the two-trials rule, the
-sceptical Bayes factor, and the sceptical $p$-value. This is not the case for
-the replication Bayes factor, for which high power can also be obtained for
-small $z_o$ if $c$ is sufficiently large. However, as shown in the previous
-section, the higher power of the replication Bayes factor comes at the cost of a
-massive type I error inflation. For $z_o = 2.5$, the sceptical Bayes factor
-shows higher power than the two-trials rule when $c = 1$, but the power of the
-two-trials rule increases faster in $c$ and approaches the power curve of the
-replication Bayes factor. The power of the sceptical $p$-value is still a bit
-lower, likely due to the more stringent requirement on the minimum relative
-effect estimate. For $z_{o} = 3$, the power differences between the methods
-mostly disappear.
-
-\subsection{Information consistency}
-\label{sec1:informationcons}
-Bayesian hypothesis testing procedures are desired to fulfil certain asymptotic
-properties \citep{Bayarri2012}. Most notably, they should be \emph{information
-consistent} in the sense that if data provide overwhelming support for a
-particular hypothesis, the procedure should indefinitely favour this hypotheses
-over alternative hypotheses.
-
-There are concerns whether the sceptical Bayes factor is information consistent
-when we look at the asymptotics only in terms of the replication data
-\citep{Consonni2021, Ly2021}. The sceptical Bayes factor can never be smaller
-than the original minimum Bayes factor $\minBF_{o}$. This means that it will be
-bounded away from zero as the replication sample size grows ($c \to \infty$),
-even when the data are generated from the same model in both studies. Similarly,
-the sceptical Bayes factor will be bounded away from zero when the replication
-effect estimate increases indefinitely. If these two cases constitute
-overwhelming evidence for replication success, they could be considered
-instances of the \emph{information paradox} \citep{Liang2008}
-% Similarly, with increasing replication effect estimate
-% ($\that_{r} \to \infty$ implying that also the relative effect estimate
-% $d \to \infty$ when $\that > 0$), replication success can at most be established for a
-% sufficiently sceptical relative prior variance $\gy \leq 1$ due to the
-% success conditions~\eqref{eq1:dsuccess}. This implies that the sceptical Bayes factor
-% $\BFs \to \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g = 1)$, provided $\abs{z_o} \geq
-% \sqrt{2}$ so that $g_{\minBF_{o}} \geq 1$. Hence, the sceptical Bayes factor is
-% also bounded away from zero and this could be considered an
-% instance of the \emph{information paradox} \citep{Liang2008}.
-
-The key to resolving the paradox is to realise that overwhelming evidence for
-replication success needs to be defined through both studies, not only through
-the replication. Assume there is a ``true'' effect size $\theta_{*} \neq 0$
-underlying both effect estimates
-$\that_{i} \sim \Nor(\theta_{*}, \sigma_{i}^{2})$, $i \in \{o, r\}$. Also assume
-the variances $\sigma_{i}^{2} = \kappa/n$ are inversely proportional to the
-sample size $n = n_{o} = n_{r}$ for the same unit variance $\kappa$ in both
-studies. Letting the sample size $n$ go to infinity is then equivalent to
-$\sigma_{o}^{2} \downarrow 0$ and $c = \sigma^{2}_{r}/\sigma^{2}_{o} = 1$. With
-decreasing variances the estimates will
-converge to the true effect size ($\that_{i} \to \theta_{*}$), the relative
-effect estimate will converge to one ($d \to 1$), and the $z$-values will go to
-infinity ($\abs{z_{i}} \to \infty$). Since $c = 1$, the sceptical Bayes factor
-is given by equation~\eqref{eq1:BFsc1}. Moreover, we are allowed to use of the
-approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ as the argument of
-the Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
-350]{Corless1996}. Taken together, we have
-\begin{align}
-  \label{eq1:BFsc1lim2}
-  \BFs =
-  \sqrt{\frac{1 + d^{2}}{1 + (1 - d)^{2}/2 -
-\mathcal{O}\left\{\log(z_{o}^{2})/z_{o}^{2}\right\}}} \cdot
-  \exp\left\{-\frac{z_o^2\left(d^{2} + 2d - 1 \right)}{4(1 + d^{2})}
-- \mathcal{O}\left(\log z_{o}^{2}\right)\right\}
-\end{align}
-Plugging $d = 1$ into~\eqref{eq1:BFsc1lim2}, we see that $\BFs \downarrow 0$ as
-$\abs{z_{o}} \to \infty$, so the sceptical Bayes factor is information
-consistent.
-
-The expression for the sceptical Bayes factor~\eqref{eq1:BFsc1lim2} is also valid
-for other relative effect sizes $d$. Solving for $d$ such that the
-multiplicative term of $z_{o}^{2}$ in the exponent changes the sign, we see that
-the sceptical Bayes factor goes to zero when the underlying true effect size of
-the replication study is at least
-$d > \sqrt{2} - 1 \approx 0.41$ times the size of the
-true effect size from the original study (or
-$d < -\sqrt{2} - 1 \approx -2.41$ due to the
-replication paradox if the advocacy prior is not truncated). This means that
-under the more realistic scenario where the underlying effect sizes from
-original and replication are not exactly the same, the sceptical Bayes factor is
-still consistent when there is not more than 60\% shrinkage of the replication
-effect size.
-
-\section{Extension to non-normal models} \label{sec1:tdist}
-So far, we have always assumed approximate normality of the effect estimates
-$\that_o$ and $\that_r$, as well as known variances $\sigma^2_o$ and
-$\sigma^2_r$. This may be a problem for studies with small sample size and/or
-extreme results (\eg when a study examines a rare disease with death rates close
-to 0\%). One way of dealing with this issue is to consider the exact likelihood
-of the data underlying the effect estimates, and then marginalise over possible
-nuisance parameters \citep[Chapter 8.2.2]{Spiegelhalter2004}. This leads to
-marginal likelihoods which are again only conditional on the effect size
-$\theta$, allowing the procedures to be used analogously as described in the
-proceeding sections. The choice of the likelihood depends on the type of effect
-size $\theta$. We will illustrate the approach for \emph{standardised mean
-differences} (SMD) and \emph{log odds ratios} (logOR), two of the most widely
-used types of effect sizes.
-
-\subsection{Standardised mean difference}
-The SMD quantifies how many standard deviation units $\sigma$, the means $\mu_1$
-and $\mu_2$ of measurements from two groups differ, \ie
-$$\theta = \frac{\mu_1 - \mu_2}{\sigma}.$$
-Assume now that the measurements come from a normal distribution with common
-variance $\sigma^2$. Knowing the test-statistic $t_i$ from the usual two-sample
-$t$-test, as well as the sample sizes in both groups $n_{1i}$ and $n_{2i}$ from
-study $i \in \{o, r\}$ is sufficient to compute the exact likelihood of the
-data. It is given by a non-central $t$-distribution with degrees of freedom
-$\nu_i = n_{1i} + n_{2i} - 2$ and non-centrality parameter $\theta \sqrt{n^*_i}$
-with $n^*_i = (n_{1i}n_{2i})/(n_{1i} + n_{2i})$ \citep{Bayarri2002}
-\begin{align}
-  \label{eq1:nct}
-  T_i \given \theta \sim \text{NCT}_{\nu_i} \left(\theta \sqrt{n^*_i}\right).
-\end{align}
-The same framework is also applicable to test-statistics $t_{i}$ from paired
-$t$-tests based on $n_{i}$ paired measurements. The SMD $\theta$ represents then
-the standardised mean difference score and $\nu_{i} = n_{i} - 1$ and
-$n_{i}^{*} = n_{i}$ need to be used in~\eqref{eq1:nct}.
-
-There is no conjugate prior for the SMD $\theta$ under model~\eqref{eq1:nct}, so
-it is not obvious which prior should be chosen to represent scepticism about it.
-We will use a zero-mean normal prior $\theta \given \HS \sim \Nor(0, \tau^{2})$
-so that the exact procedure is equivalent with the normal approximation as the
-sample size increases. For the advocacy prior we need to know the posterior
-distribution of the SMD $\theta$ conditional on the original study and a flat
-prior on $\theta$. Exploiting the fact that the non-central $t$-distribution can
-be expressed as a location-scale mixture of a normal with an inverse-gamma
-distribution
-%% \ie $\text{NCT}_\nu(t; \theta \sqrt{n^*}) = \int
-%% \Nor(t; \theta \sqrt{n^*\tau^2}, \tau^2) \text{IG}(\tau^2; \nu/2, \nu/2) d\tau^2$
-\citep[Chapter 31]{Johnson1995}, the density of the SMD under the advocacy prior
-is given by
-\begin{align*}
-  f(\theta \given t_o)
-  = \int_0^\infty \Nor\left(\theta; \frac{t_o}{\sqrt{n_o^* \tau^2}},
-  \frac{1}{n_o^*}\right)  \text{IG}\left(\tau^2; \frac{\nu_o + 1}{2},
-  \frac{\nu_o}{2}\right) \, \text{d}\tau^2,
-\end{align*}
-where $\Nor(x; \mu, \phi)$ denotes the density function of the normal
-distribution with mean $\mu$ and variance $\phi$ evaluated at $x$, and similarly
-$\text{IG}(y; a, b)$ denotes the density function of the inverse-gamma
-distribution with shape and rate parameters $a$ and $b$ evaluated at $y$.
-
-Taken together, the SMD version of the method proceeds analogously as in
-Box~\hyperref[box:nutshell]{1} with the two Bayes factors replaced by
-\begin{align*}
-  \BFcol{0}{\mathrm{S}}(t_{o};\tau^{2})
-  &= \frac{\text{NCT}_{\nu_{o}}(t_{o}; 0)}{\int
-  \text{NCT}_{\nu_{o}}(t_{o}; \theta \sqrt{n_{o}^{*}})
-  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
-  \BFcol{\text{S}}{\text{A}}(t_{r};\tau^{2})
-  &= \frac{\int\text{NCT}_{\nu_{r}}(t_{r};\theta
-  \sqrt{n_{r}^{*}})\Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
-  \int\text{NCT}_{\nu_{r}}(t_{r};\theta
-  \sqrt{n_{r}^{*}}) f(\theta \given t_{o}) \, \text{d} \theta}
-\end{align*}
-and using numerical integration as the integrals cannot be evaluated
-analytically.
-
-\subsection{Log odds ratio}
-In the case of binary data, we have two independent binomial samples
-\begin{align*}
-  &X_{1i} \given \pi_1 \sim \Bin(n_{1i}, \pi_1)&
-  &X_{2i} \given \pi_2 \sim \Bin(n_{2i}, \pi_2)&
-\end{align*}
-for each study $i \in \{o, r\}$, and the effect of the treatment in group 1
-relative to the treatment in group 2 is quantified with the logOR
-$$\theta = \log \frac{\pi_1/(1 - \pi_1)}{\pi_2/(1 - \pi_2)}.$$
-To obtain a marginal likelihood that only depends on $\theta$, we need to
-specify a prior for either $\pi_2$ or $\pi_1$ and marginalise over it. A
-principled choice is the translation invariant Jeffreys prior,
-$\pi_1, \pi_2 \sim \Be(1/2, 1/2)$. The exact marginal likelihood for the data
-from study $i$ is then given by
-\begin{align}
-  \label{eq1:binexact}
-  f(x_{1i}, x_{2i} \given \theta)
-  &= \int_0^1 \Bin\left(x_{1i}; n_{1i}, \left\{1 + \exp\left[-\theta - \log
-    \frac{\pi_2}{1 - \pi_2}\right]\right\}^{-1}\right) \Bin(x_{2i}; n_{2i}, \pi_2)
-  \nonumber
-  \\ &\phantom{= \int_0^1}  \times \Be(\pi_2; 1/2, 1/2) \, \text{d} \pi_2
-\end{align}
-where $\Bin(x; n, \pi)$ denotes the probability mass function of the binomial
-distribution with $n$ trials and probability $\pi$ evaluated at $x$, and
-likewise $\Be(y; a, b)$ denotes the density function of the beta distribution
-with parameters $a$ and $b$ evaluated at $y$.
-
-There is no conjugate prior for the logOR under model~\eqref{eq1:binexact}, but a
-pragmatic choice is to specify a zero-mean normal prior
-$\theta \given \HS \sim \Nor(0, \tau^{2})$ for the sceptic, to match with the
-normal approximation as the sample size increases. For the advocacy prior, we
-need to know the posterior distribution of the logOR $\theta$ based on the
-original study.
-Using a result from \citet{Marshall1988} combined with a change-of-variables,
-the exact posterior density of the logOR $\theta$ given the original data and
-Jeffreys priors on $\pi_1$ and $\pi_2$ is
-\begin{align*}
-  f(\theta \given x_{1o}, x_{2o}) &=
-  \begin{cases}
-    % C \, \exp\{(x_{1o} + 1/2) \theta\} \,
-    % F(n_{1o} + 1, x_{1o} + x_{2o} + 1, n_{1o} + n_{2o} + 2, 1 - \exp(\theta))
-    % & \text{for} ~ \theta < 0 \\
-    % C \, \exp\{-(n_{1o} - x_{1o} + 1/2) \theta\} \,
-    % F(n_{1o} + 1, n_{10} - x_{1o} + n_{2o} - x_{2o} + 1, n_{1o} + n_{2o} + 2,
-    % 1 - \exp(-\theta)) & \text{for} ~ \theta > 0 \\
-    C \, \exp\{e \theta\} \,
-    F\left(e + f, e + g, e + f + g + h, 1 - \exp\{\theta\}\right)
-    & \text{for} ~ \theta < 0 \\
-    C \, \exp\{-f \theta\} \,
-    F\left(e + f, f + h, e + f + g + h, 1 - \exp\{-\theta\}\right)
-    & \text{for} ~ \theta > 0 \\
-  \end{cases}
-\end{align*}
-where $F(\cdot)$ is the hypergeometric function, $e = x_{1o} + 1/2$,
-$f = n_{1o} - x_{1o} + 1/2$, $g = x_{2o} + 1/2$, $h = n_{2o} - x_{2o} + 1/2$,
-$C = \text{B}(e + g, f + h)/\{\text{B}(e, f) \text{B}(g, h)\}$, and
-$\text{B}(\cdot, \cdot)$ is the Beta function.
-
-Combining the previous results, we obtain
-\begin{align*}
-  \BFcol{0}{\text{S}}(x_{1o}, x_{2o};\tau^{2})
-  &= \frac{ f(x_{1o}, x_{2o} \given 0)}{\int
-   f(x_{1o}, x_{2o} \given \theta)
-  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
-  \BFcol{\text{S}}{\text{A}}(x_{1r}, x_{2r};\tau^{2})
-  &= \frac{\int f(x_{1r}, x_{2r} \given \theta)
-    \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
-    \int f(x_{1r}, x_{2r} \given \theta)
-    f(\theta \given x_{1o}, x_{2o}) \, \text{d} \theta}
-\end{align*}
-as an exact replacement for the Bayes factors in Box~\hyperref[box:nutshell]{1}.
-Again, there are no closed form expressions for the integrals, but numerical
-integration needs to be used.
-
-\section{Application}
-\label{sec1:applications}
-The following section will illustrate application of the sceptical Bayes factor
-using data from the \emph{Social Sciences Replication Project}
-\citep{Camerer2018}, provided in Table \ref{tab:ssrp}. Effect estimates were
-reported on the correlation scale ($r$), which is why we applied the Fisher
-$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$. This leads to the
-transformed estimates having approximate variance
-$\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}, so the relative variance
-$c$ is roughly the ratio of the replication to the original study sample size
-$c \approx n_{r}/n_{o}$.
-
-For all studies except \citet{Janssen2010} and \citet{Derex2013}, the exact
-approach for either SMD or logOR effect sizes from Section~\ref{sec1:tdist} is
-applicable. In the studies with binary data
-% \citep{Balafoutas2012, Gneezy2014, Hauser2014},
-computing the exact posterior using the hypergeometric function led to numerical
-issues in some cases and numerical integration was used then.
-% Balafoutas and Sutter - integration and hypergeo work
-% Gneezy et al. - only integration works
-% Hauser et al. - only hypergeo works
-In most cases, the normal approximation of the likelihood seems to lead to
-similar numerical results for both $\BFs$ and $\BFr$ as compared to their
-counterparts based on exact likelihoods. Qualitative conclusions are the same
-under both approaches and we will therefore focus on the normal approximation
-due to better comparability with the remaining measures of replication success
-as all of them were computed based on approximate normal likelihoods.
-
-For the study pairs where the sceptical Bayes factor suggests a large degree of
-replication success, all other methods suggest the same in every case. However,
-there are also cases where there appear to be discrepancies among the methods.
-For instance, the two-trials rule and the replication Bayes factor may indicate
-a larger degree of replication success compared to the sceptical $p$-value and
-sceptical Bayes factor. This happens for replications that show a substantial
-increase in sample size but also a much smaller effect estimate compared to the
-original study. For example, in \citet{Balafoutas2012} the sample size was about
-$c = 3.48$ times larger in the replication, whereas the effect estimate was only
-$d = 0.52$ the size of the original one. The replication is successful at
-$\gamma = 1/3$ with the two-trials rule ($\minBF_{o} = 1/4.2$ and
-$\minBF_{r} = 1/3.6$) and the replication Bayes factor ($\BFr = 1/3.9$), but not
-with the sceptical Bayes factor ($\BFr = 1/1.6$) or the sceptical $p$-value
-($\tilde{p}_{\mathrm{S}} = 0.04 > 1 - \Phi(z_\gamma = 2.18) = 0.01$).
-
-\begin{landscape}
-\begin{table}[!htb]
-\centering
-\caption{Results for data from \emph{Social Sciences Replication Project}
-  \citep{Camerer2018}. Shown are relative variances
-  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimates
-  $d = \that_{r}/\that_{o}$ (computed on Fisher $z$-scale), $Q$-statistic
-  $Q = (\that_{o} - \that_{r})^{2}/(\sigma^{2}_{o} + \sigma^{2}_{r})$, minimum
-  Bayes factors of original and replication effect estimate ($\minBF$),
-  recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}$), sceptical Bayes
-  factors ($\BFs$) and replication Bayes factors ($\BFr$), the latter two
-  computed using either a normal approximation or the exact likelihood of the
-  data. }
-% \resizebox{1\textwidth}{!}{%
-
-% latex table generated in R 4.2.2 by xtable 1.8-4 package
-% Thu Nov 24 10:46:19 2022
-{\small
-\begin{tabular}{lrrrlllllll}
-  \toprule
-Original study & $c$ & $d$ & $Q$ & $\minBF_o$ & $\minBF_r$ & $\tilde{p}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ (exact) & $\mathrm{BF}_{\mathrm{R}}$ & $\mathrm{BF}_{\mathrm{R}}$ (exact) \\
-  \midrule
-Hauser et al. (2014) & 0.51 & 1.04 & 0.03 & < 1/1000 & < 1/1000 & < 0.0001 & < 1/1000 & < 1/1000 & < 1/1000 & < 1/1000 \\
-  Aviezer et al. (2012) & 0.92 & 0.60 & 3.49 & < 1/1000 & 1/347 & < 0.0001 & 1/78 & 1/10 & 1/284 & 1/41 \\
-  Wilson et al. (2014) & 1.33 & 0.83 & 0.28 & < 1/1000 & 1/659 & 0.0001 & 1/45 & 1/35 & < 1/1000 & < 1/1000 \\
-  Derex et al. (2013) & 1.29 & 0.65 & 1.14 & 1/520 & 1/17 & 0.002 & 1/8.5 &  & 1/31 &  \\
-  Gneezy et al. (2014) & 2.31 & 0.81 & 0.22 & 1/18 & 1/157 & 0.004 & 1/6.9 & 1/7.5 & 1/474 & 1/551 \\
-  Karpicke and Blunt (2011) & 1.24 & 0.58 & 1.75 & < 1/1000 & 1/9.6 & 0.002 & 1/5.6 & 1/5 & 1/12 & 1/12 \\
-  Morewedge et al. (2010) & 2.97 & 0.76 & 0.30 & 1/7.3 & 1/65 & 0.011 & 1/3.9 & 1/4 & 1/160 & 1/156 \\
-  Kovacs et al. (2010) & 4.38 & 1.38 & 0.59 & 1/3.2 & < 1/1000 & 0.009 & 1/3.2 & 1/3.8 & < 1/1000 & < 1/1000 \\
-  Duncan et al. (2012) & 7.42 & 0.57 & 1.29 & 1/12 & < 1/1000 & 0.011 & 1/3.1 & 1/3.1 & < 1/1000 & < 1/1000 \\
-  Nishi et al. (2015) & 2.42 & 0.57 & 1.05 & 1/12 & 1/6.1 & 0.016 & 1/2.5 & 1/2.2 & 1/8.2 & 1/7.6 \\
-  Janssen et al. (2010) & 0.65 & 0.48 & 3.51 & < 1/1000 & 1/3.3 & 0.003 & 1/1.6 &  & 1/1.6 &  \\
-  Balafoutas and Sutter (2012) & 3.48 & 0.52 & 1.02 & 1/4.2 & 1/3.6 & 0.04 & 1/1.6 & 1/1.6 & 1/3.9 & 1/3.9 \\
-  Pyc and Rawson (2010) & 9.18 & 0.38 & 1.79 & 1/3.5 & 1/7.3 & 0.061 & 1/1.2 & 1/1.2 & 1/4 & 1/4 \\
-  Rand et al. (2012) & 6.27 & 0.18 & 3.96 & 1/7.1 & 1 & 0.13 &  &  & 9.6 & 9.7 \\
-  Ackerman et al. (2010) & 11.69 & 0.23 & 2.15 & 1/2.2 & 1/1.3 & 0.15 &  &  & 3.2 & 3.2 \\
-  Sparrow et al. (2011) & 3.50 & 0.13 & 5.80 & 1/26 & 1 & 0.19 &  &  & 29 & 32 \\
-  Shah et al. (2012) & 11.62 & -0.05 & 4.08 & 1/2.2 & 1 & 0.66 &  &  & 25 & 26 \\
-  Kidd and Castano (2013) & 8.57 & -0.10 & 6.83 & 1/5.7 & 1 & 0.77 &  &  & 72 & 69 \\
-  Gervais and Norenzayan (2012) & 9.78 & -0.12 & 5.44 & 1/3 & 1 & 0.78 &  &  & 36 & 37 \\
-  Lee and Schwarz (2010) & 7.65 & -0.11 & 6.80 & 1/5.4 & 1 & 0.79 &  &  & 65 & 69 \\
-  Ramirez and Beilock (2011) & 4.47 & -0.09 & 19.29 & < 1/1000 & 1 & 0.85 &  &  & > 1000 & > 1000 \\
-   \bottomrule
-\end{tabular}
-}
-% %
-% }
-\label{tab:ssrp}
-\end{table}
-
-\end{landscape}
-
-% % EJ Wagenmakers' analysis
-% % - Ackerman et al. (2010): BFR 3.23  -- our BFR 3.2
-% % -* Aviezer et al. (2012): BFR 1/57 -- our BFR 1/284
-% % - Balafoutas and Sutter (2012): 1/4.27 -- our BFR 1/3.9
-% % -** Derex et al. (2013): 1/3'701 -- our BFR 1/31
-% % - Duncan et al. (2012): 1/2513 -- our BFR 1/3079.4
-% % - Gervais & Norenzayan (2012): 36.5 -- our BFR 36
-% % - Gneezy et al. (2014): 1/485.27 -- our BFR 1/474
-% % -* Hauser et al. (2014): 1/10'211 -- our BFR 1/620'059
-% % -** Janssen et al. (2010): 2'134'835 -- our BFR 1/1.6
-% % - Karpicke & Blunt (2011): 1/11.82 -- our BFR 12
-% % - Kidd & Castano (2013): 71.43 -- our BFR 72
-% % - Kovacs et al. (2010): 1/132'389'305 -- our BFR 1/333'616'129
-% % - Lee & Schwarz (2010): 68 -- our BFR 65
-% % - Morewedge et al. (2010): 1/158 -- our BFR 1/160
-% % - Nishi et al. (2015): 1/7.77 -- our BFR 1/8.2
-% % - Pyc and Rawson (2010): 1/4.04 -- our BFR 1/4
-% % -* Ramirez & Beilock (2011): 12'240 -- our BFR 24'996
-% % - Rand et al. (2012): 9.71 -- our BFR 9.6
-% % - Shah et al. (2012): 26.05 -- our BFR 25
-% % - Sparrow et al. (2011): 31.65 -- our BFR 29
-% % -* Wilson et al. (2014): 1/1871 -- our BFR 1/2533
-
-%% ps does but BFs doesn't flag RS
-Discrepancies between the sceptical $p$-value and the sceptical Bayes factor
-happen in situations where the replication shows an effect estimate that,
-although incompatible with the sceptical prior, is also incompatible with the
-advocacy prior. For example in the \citet{Janssen2010} replication, both effect
-estimates are substantially larger than zero ($\that_o = 0.74$ with
-$\minBF_{o} < 1/1000$ and $\that_r = 0.36$ with $\minBF_{r} = 1/3.3$), yet the
-$Q$-statistic indicates some incompatibility ($Q = 3.51$), which explains why
-$\tilde{p}_{\mathrm{S}} = 0.003$, but $\BFs = 1/1.6$ only.
-
-Discrepancies between the replication Bayes factor and the sceptical Bayes
-factor arise when the replication finding provides overwhelming evidence against
-the null, whereas the original finding was less compelling. The replication of
-\citet{Kovacs2010} illustrates this situation. The original study provided only
-moderate evidence against the null ($\that_o = 0.49$ and $\minBF_o = 1/3.2$),
-whereas the replication finding was more compelling ($\that_r = 0.67$ and
-$\minBF_r < 1/1000$). By construction the sceptical Bayes factor can only be as
-small as the minimum Bayes factor from the original study $\minBF_o$, which is
-actually attained in this case ($\BFs = 1/3.2$). The replication Bayes factor,
-on the other hand, is not limited by the moderate level of evidence from the
-original study and indicates decisive evidence for the advocate
-($\BFr < 1/1000$). This illustrates that in order to achieve a reasonable degree
-of replication success, the sceptical Bayes factor requires the original study
-to be convincing, whereas the replication Bayes factor only requires a
-compelling replication result.
-
-\section{Discussion}
-\label{sec1:discussion}
-We proposed a novel method for the statistical assessment of replicability
-combining reverse-Bayes analysis with Bayesian hypothesis testing. Compared to
-other methods, the sceptical Bayes factor poses more stringent requirements but
-also allows for stronger statements about replication success. It ensures that
-both studies provide sufficient evidence against a null effect, while also
-penalising incompatibility of their effect estimates. If the replication sample
-size is not too small, the sceptical Bayes factor comes with appropriate
-frequentist error rates, which is often a requirement from research funders and
-regulators. Asymptotic analysis of the method showed that it is information
-consistent in the sense that if the sample size in both studies increases, the
-sceptical Bayes factor will indicate overwhelming replication success when the
-underlying effect size of the replication is not much smaller than the
-underlying effect size of the original study. Finally, the sceptical Bayes
-factor is the only method in our comparison which does not suffer from any form
-of the shrinkage paradox, \ie replication success can never be achieved with
-arbitrarily small replication effect estimates, not even when the replication
-sample size becomes very large or the evidence from the original study
-overwhelming.
-
-In extreme scenarios the sceptical Bayes factor can suffer from the replication
-paradox, which means that it may flag success when the replication estimate goes
-in opposite direction of the original one. However, the paradox can be avoided
-by truncating the advocacy prior to the direction of the original estimate. It
-may also happen that the result of the replication is so inconclusive that
-replication success cannot be established at any level, so the sceptical Bayes
-factor does not exist. Other methods, such as the sceptical $p$-value or the
-replication Bayes factor, can be used in this situation.
-
-%% extensions and limitations
-The proposed method could be extended in many ways. First, in many cases not
-just one but several replication studies are conducted for one original study
-\citep[\eg as in][]{Klein2014}. The Bayesian framework allows to easily extend
-the sceptical Bayes factor to the ``many-to-one'' replication setting as the
-likelihoods are also straightforward to compute for a sample of replication
-effect estimates. Second, a multivariate generalisation would allow for effects
-in the form of a vector with approximate multivariate normal likelihood which is
-then combined with a sceptical $g$-prior \citep{Liang2008}. The normal prior
-could also be replaced with other distributions, for example the (multivariate)
-Cauchy distribution which is often the preferred prior choice for default Bayes
-factor hypothesis tests \citep{Jeffreys1961}. The $g$ parameter of the $g$-prior
-or the scale parameter of the Cauchy prior would then take over the role of the
-relative sceptical prior variance. Third, based on the replication result one
-could also compute a posterior distribution for the effect size based on a
-model-average of the advocacy prior and the sceptical prior (using the variance
-at the sceptical Bayes factor). This distribution would provide a formal
-compromise between scepticism and advocacy of the original finding. Fourth,
-while Bayes factors are an important part in Bayesian hypothesis testing, they
-do not take into account the prior probabilities of the hypotheses under
-consideration. It would be interesting to investigate whether the reverse-Bayes
-approach could be used in a framework where priors are assigned jointly to the
-hypothesis and parameter space \citep{Dellaportas2012}. Finally, an important
-aspect is the design of new replication studies. An appropriate sample size is
-of particular importance for a replication to be informative. We will report in
-the future on sample size planning based on the sceptical Bayes factor.
-
-% conclusion
-For a thorough assessment of replication attempts, no single metric seems to be
-able to answer all important questions completely. Instead, we recommend that
-researchers conduct a comprehensive statistical evaluation of replication
-success. Reverse-Bayes methods naturally fit to the replication setting, they
-avoid various paradoxes from which other methods suffers, and they combine
-different notions of replicability. The reverse-Bayes approach therefore leads
-to sensible inferences and decisions, which is why we advocate it as a key part
-in the assessment of replication success.
-
-\section*{Software and data}
-All analyses were performed in the R programming language version
-4.2.2 \citep{R}. The code to
-reproduce this manuscript is available at
-\url{https://gitlab.uzh.ch/samuel.pawel/BFScode}. We used the implementation of
-the Lambert $W$ function from the package \texttt{lamW} \citep{Adler2015},
-graphics were created with the \texttt{ggplot2} package \citep{Wickham2016}, the
-sceptical $p$-value and related calculations were conducted using the package
-\texttt{ReplicationSuccess} available on the Comprehensive R Archive Network
-% \url{https://cran.r-project.org/web/packages/ReplicationSuccess/index.html}
-\citep{Held2020}. All methods are implemented in the R package \texttt{BayesRep}
-which is available at \url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}.
-
-Data on effect estimates from the \emph{Social Sciences Replication Project}
-\citep{Camerer2018} were downloaded from \url{https://osf.io/abu7k/},
-respectively, taken from \url{https://osf.io/nsxgj/} for exact calculations.
-
-\section*{Acknowledgements}
-We thank the anonymous referees for the helpful comments and suggestions that
-have considerably improved the paper. We also thank Guido Consonni, Luca La
-Rocca, Malgorzata Roos, Georgia Salanti, Charlotte Micheloud, and Maria
-Bekker-Nielsen Dunbar for helpful discussion and comments on drafts of the
-manuscript.
-
-\section*{Funding}
-This work was supported by the Swiss National Science Foundation (project number
-189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
-design, data collection and analysis, decision to publish, or preparation of the
-manuscript.
-
-\begin{subappendices}
-  \renewcommand{\thesection}{\Alph{section}}
-
-\section{Sufficiently sceptical relative prior variance}
-\label{appendix:ssrv}
-The sufficiently sceptical relative prior variance at level $\gamma$ is the
-value $\gy \in [0, \gminBFo]$ that fulfils the condition
-\begin{align}
-  \label{sspv}
-  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gy)
-  &= \gamma.
-\end{align}
-Substituting~\eqref{sspv} and rearranging terms, we obtain
-\begin{align}
-  \label{sspv2}
-  \sqrt{1 + \gy} \cdot
-  \exp\left\{-\frac{1}{2} \cdot
-  \frac{\gy}{1 + \gy} \cdot z^2_o\right\}
-  &= \gamma \nonumber \\
-  \iff \frac{1}{\gamma} \cdot \exp\left\{-\frac{z_o^2}{2}\right\}
-  &= \frac{1}{\sqrt{1 + \gy}} \exp\left\{-\frac{1}{2} \cdot
-  \frac{z_o^2}{1 + \gy}\right\}. \nonumber
-  \\
-  \intertext{Squaring both sides and multiplying by $-z_o^2$, this becomes}
-  \iff -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
-  &= -\frac{z_o^2}{1 + \gy}
-  \exp\left\{-\frac{z_o^2}{1 + \gy}\right\}.
-\end{align}
-This is a transcendental equation that cannot be explicitly solved in terms of
-elementary functions. However, if we set $q = -z_o^2/(1 + \gy)$
-then~\eqref{sspv2} becomes
-\begin{align*}
-  -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
-  &= q \cdot \exp\left\{q\right\}.
-\end{align*}
-The solution for $q$ (and consequently for $\gy$) can be explicitly computed
-with
-\begin{align}
-\label{eq1:solutionvss}
-  q &= \lw{-1}\left(-\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}\right)
-  \nonumber \\
-  \gy &=
-  \begin{cases}
-    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
-    \text{undefined} & ~~ \text{else}
-  \end{cases}
-\end{align}
-where $\lw{-1}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
-$W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, ensuring that $\gy \leq \gminBFo$. See
-Appendix~\ref{appendix:lambertW} for details about the Lambert $W$ function. For
-some $z_o$, equation \eqref{sspv2} can also be satisfied for negative $\gy$,
-which is why we need to add the condition $-z_o^2/q \geq 1$ in equation
-\eqref{eq1:solutionvss}, such that $\gy$ is a valid relative variance.
-
-As $z_{o}^{2}$ becomes larger, the argument to the Lambert function
-$x = -z_{o}^{2}\exp(-z_{o}^{2})/\gamma^{2}$ will approach zero, so the
-approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ can be applied
-\citep[p. 350]{Corless1996}. This leads to
-\begin{align*}
-  \gy \approx \frac{z_{o}^{2}}{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2} +
-  \log\{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2}\}} - 1.
-\end{align*}
-We can see that $\gy \downarrow 0$ when $\gamma$ remains fixed and
-$z_{o}^{2} \to \infty$, which means that the sufficiently sceptical relative
-prior variance converges to zero for increasingly compelling evidence from the
-original study.
-
-\section{The Lambert $W$ function}
-\label{appendix:lambertW}
-The Lambert $W$ function \citep{Corless1996} is defined as the function
-$W(\cdot)$ satisfying
-$$W(y) \cdot \exp\{W(y)\} = y$$
-and it is also known as ``product logarithm`` since it returns the number which
-plugged in the exponential function and then multiplied by itself produces $y$.
-For real $y$, $W(y)$ is only defined for $y \geq - e^{-1}$ and for
-$y \in [-e^{-1}, 0)$ the function has two branches that are commonly denoted by
-$\lw{0}(\cdot)$, the branch with $W(y) \geq -1$, and $\lw{-1}(\cdot)$, the
-branch with $W(y) \leq -1$ (see Figure \ref{fig1:lambertW} for an illustration).
-\begin{figure}[!htb]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-\includegraphics[width=\maxwidth]{images/paper1/plot-Lambert-1}
-\end{knitrout}
-\caption{Lambert $W$ function for real argument $y$.}
-\label{fig1:lambertW}
-\end{figure}
-
-\section{Computation of the sceptical Bayes factor}
-\label{appendix:bfs}
-From the definition of the sceptical Bayes factor it is apparent that $\BFs$ is
-either
-\begin{enumerate}
-  \item \label{undef} undefined,
-  if
-  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g) >
-  \BFcol{\text{0}}{\text{S}}(\hat{\theta}_o; g)$ for all $g \in [0,
-    \gminBFo]$
-
-  \item \label{lowbound} $\BFs = \minBF_{o}$, if
-  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq
-  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gminBFo)$
-
-  \item \label{intersection}
-  $\BFs = \inf_{\gy}
-  \left\{\gamma : \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)
-  = \gamma\right\}$,
-  the height of the lowest intersection of
-  $\BFcol{0}{\text{S}}(\hat{\theta}_o; \gy) = \gamma$ and
-  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)$
-  in $\gy$ otherwise
-\end{enumerate}
-Whether $\BFs$ attains the lower bound $\minBF_{o}$ (condition \ref{lowbound})
-can be checked by evaluating if
-$\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq \minBF_{o}$ and setting
-$\BFs = \minBF_{o}$ if it is the case. For condition \ref{intersection}, we know
-that the intersections satisfy
-\begin{align*}
-  \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g_*) &=
-  \BFcol{0}{\text{S}}(\hat{\theta}_o; g_*) \\
-  \sqrt{\frac{1/c + 1}{1/c + g_*}} \cdot
-  \exp\left\{-\frac{z_{o}^{2}}{2}\left(\frac{d^2}{1/c + g_*} -
-  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}
-  &= \sqrt{1 + g_*} \cdot
-  \exp\left\{-\frac{1}{2} \cdot \frac{g_*}{1 + g_*} \cdot z^2_o\right\}
-\end{align*}
-which is equivalent to
-\begin{align}
-  \sqrt{\frac{1}{(1 + g_*)(1/c + g_*)}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
-  \frac{1}{1 + g_*} + \frac{d^{2}}{1/c + g_*}\right)\right\} \nonumber \\
-  = \sqrt{\frac{1}{1/c + 1}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
-  1 + \frac{(1 - d)^{2}}{1/c + 1}\right)\right\}.
-  \label{eq1:bfsroot}
-\end{align}
-This is a transcendental equation that has no closed-form solution for $g_*$ in
-terms of elementary functions, but root-finding algorithms can be used to
-compute it. However, when $c = 1$, equation~\eqref{eq1:bfsroot} simplifies
-\begin{align}
-  \label{eq1:bfsroot2}
-  \frac{1}{1 + g_*}\cdot\exp\left\{-\frac{z_{o}^{2}}{2} \cdot
-  \frac{1 + d^{2}}{1 + g_*}\right\}
-  &= \frac{1}{\sqrt{2}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
-  1 + \frac{(1 - d)^{2}}{2}\right)\right\}.
-\end{align}
-Multiplying~\eqref{eq1:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
-Lambert $W$ function leads to
-\begin{align}
-  \label{eq1:gintersect}
-  % q &= W\left(-\frac{z_A^2}{\sqrt{2}} \cdot
-  % \exp\left\{-\frac{z_o^2}{2} \left(1 + \frac{(1 - d)^2}{2}\right)\right\}\right) \\
-  % g_* &=
-  % \begin{cases}
-  %   \dfrac{-z_A^2}{q} - 1 & ~~ \text{if} ~ \dfrac{-z_A^2}{q} \geq 1 \\
-  %   \text{undefined} & ~~ \text{else},
-  % \end{cases}
-  k &= W\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{1 + d^{2}}{2} \cdot
-      \exp\left\{-\frac{z_o^2}{2} \left[1 + \frac{(1 - d)^2}{2}\right]\right\}\right)
-  \nonumber \\
-  g_* &=
-  \begin{cases}
-    -\dfrac{z_o^2}{k}\cdot \dfrac{1 + d^{2}}{2} - 1 & ~~ \text{if} ~
-    -\dfrac{z_o^2}{k}\cdot\dfrac{1 + d^{2}}{2} \geq 1 \\
-    \text{undefined} & ~~ \text{else},
-  \end{cases}
-\end{align}
-with the condition that $-z_o^2(1 + d^{2})/(2k) \geq 1$ such that $g_*$ is a
-valid relative variance, as the equation may otherwise be satisfied for negative
-$g_*$. Since the argument to $W(\cdot)$ is real and negative (if $z_{o}\neq 0$),
-the branches $\lw{-1}(\cdot)$ and $\lw{0}(\cdot)$ both provide solutions that
-can fulfil the equation (assuming the argument is not smaller than $-e^{-1}$
-which would mean that there are no intersections). It must also hold that
-$g_{*} \leq g_{\minBF_{o}} = \max\{z_{o}^{2} - 1, 0\}$ for $g_{*}$ to be a valid
-sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the $g_{*}$
-from~\eqref{eq1:gintersect} can only be computed with the $\lw{-1}(\cdot)$
-branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$ the solution
-$g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the relative prior
-variance $g_{*}$ from~\eqref{eq1:gintersect} into the Bayes factor
-from~\eqref{eq1:BFo}, we obtain the expression for the sceptical Bayes factor
-in~\eqref{eq1:BFsc1}.
-
-\section{Bayes factor with truncated advocacy prior}
-\label{app:BFtrunc}
-For now assume $\that_o > 0$. The marginal likelihood of the replication effect
-estimate $\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
-truncated advocacy prior
-$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \mathbb{1}_{(0, \infty)}(\theta)$
-is
-\begin{align}
-  f(\that_r \given \HAp)
-  &= \int_{-\infty}^{+\infty} f(\that_r \given \theta) f(\theta \given
-  \HAp) \, \text{d}\theta \nonumber \\
-  &= \int_{-\infty}^{+\infty}
-  \frac{\mathbb{1}_{(0, \infty)}(\theta)}{2\pi\sigma_r\sigma_o\Phi(z_o)}
-  \exp\left\{-\frac{1}{2}\left[\frac{(\that_o - \theta)^2}{\sigma^2_r}
-  + \frac{(\theta - \that_o)^2}{\sigma^2_o}\right]\right\}
-  \, \text{d}\theta \nonumber \\
-  &=
-  \frac{1}{2\pi\sigma_r\sigma_o\Phi(z_o)}
-  \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}\right\}
-   \underbrace{\int_{0}^{+\infty}
-   \exp\left\{-\frac{1}{2}\frac{(\theta - \frac{\that_o/\sigma^2_o +
-       \that_r/\sigma^2_r}{1/\sigma^2_o + 1/\sigma^2_r})^2}{\left(
-     1/\sigma^2_o + 1/\sigma^2_r\right)^{-1}}\right\}
-   \, \text{d}\theta}_{=\sqrt{\frac{2\pi}{1/\sigma^2_o + 1/\sigma^2_r}}
-   % \Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)} \nonumber \\
-  \Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)} \nonumber \\
-   &= \frac{1}{\sqrt{2\pi(\sigma_r^2 + \sigma_o^2)}}
-   \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}
-     % \right\}  \frac{\Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)}{
-     \right\}  \frac{\Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)}{
-     \Phi(z_o)}.
-   \label{eq1:truncmarg}
-\end{align}
-With a similar argument one can show that this result holds for any $\that_o$ if
-the last factor in \eqref{eq1:truncmarg} is changed to
-\begin{align*}
-  % \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}
-  \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o(1 + dc)}{\sqrt{1 + c}}
-  \right\}}{\Phi\left\{\abs{z_o}\right\}}.
-\end{align*}
-By dividing the marginal likelihood of the replication data under the
-sceptical prior by the marginal likelihood under the truncated advocacy prior,
-the Bayes factor in \eqref{eq1:BFrtrunc} is obtained.
-
-\section{The shrinkage paradox}
-\label{app:shrinkage}
-We want to investigate what happens to the replication success regions as the
-relative variance $c$ and the squared original $z$-value $z_{o}^{2}$ (a monotone
-transformation of the original minimum Bayes factor $\minBF_{o}$) become larger.
-Ignoring the success regions on the wrong side of zero (due to the replication
-paradox), the minimum relative effect estimates $\dmin$ as shown in
-Section~\ref{sec1:comparison} are given by
-
-\begin{align*}
-    &\dmin^{\scriptscriptstyle \BFs} =
-      \frac{1/c + \gy}{\gy - 1} +
-      \sqrt{\frac{\log\left[\frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right]/z_{o}^{2}
-      + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\left[(1/c + \gy)(1/c + 1)\right]}}&
-  &\text{(sceptical Bayes factor)} \\
-    &\dmin^{\scriptscriptstyle \text{2TR}} =
-      \frac{z_{\gamma}}{z_{o}\sqrt{c}}&
-  &\text{(two-trials rule)} \\
-    &\dmin^{\scriptscriptstyle \BFr} =
-      \sqrt{\left[1 + \frac{\log(1 + c) - 2\log \gamma}{z_{o}^{2}}\right] \frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c} &
-  &\text{(replication Bayes factor)} \\
-    &\dmin^{\scriptscriptstyle \ps} =
-      \sqrt{\frac{1/c + 1/(z_{o}^{2}/z_{\gamma}^{2} - 1)}{z_{o}^{2}/z_{\gamma}^{2}}}&
-  &\text{(sceptical $p$-value)} \\
-\end{align*}
-where for the sceptical Bayes factor it was assumed that $\gy > 1$ (otherwise
-the plus before the square root term needs to be replaced by a minus).
-
-For the sceptical Bayes factor, we obtain
-\begin{align*}
-  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFs} =
-  \frac{\gy}{\gy - 1} +
-    \sqrt{\frac{\log\left[\frac{1}{\gy(1 + \gy)}\right]/z_{o}^{2}
-    + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\gy}}&
-  &\text{and}&
-  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFs} =
-    \sqrt{\frac{1/c + 1}{c}} - \frac{1}{c}&
-\end{align*}
-where for the second limit we used that $\lim_{z_{o}^{2} \to \infty} \gy = 0$
-for a fixed level $\gamma$ (Appendix~\ref{appendix:ssrv}). So the sceptical
-Bayes factor does not suffer from any form of the shrinkage paradox. The limits
-for the two-trials rule are given by
-\begin{align*}
-  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
-  &\text{and}&
-  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
-\end{align*}
-so the two-trials rule suffers from both forms of the shrinkage paradox. For the
-sceptical $p$-value, we obtain
-\begin{align*}
-  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \ps} =
-    \sqrt{\frac{z_{\gamma}^{2}}{z_{o}^{2}(z_{o}^{2}/z_{\gamma}^{2} - 1)}}&
-  &\text{and}&
-  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \ps} = 0&
-\end{align*}
-thus, the sceptical $p$-value suffers from the shrinkage paradox at original.
-Finally, the limits for the replication Bayes factor are
-\begin{align*}
-  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFr} = 0 &
-  &\text{and}&
-  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFr} =
-    \sqrt{\frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c}&
-\end{align*}
-which means that the replication Bayes factor suffers from the shrinkage paradox
-at replication.
-
-\section{Probability of replication success with the sceptical Bayes factor}
-\label{app:powerBFs}
-Conditional on the original study, the probability for replication success at
-level $\gamma$ is given by the probability of \eqref{eq1:RSCond-d}. This event
-involves $z_r = dz_o \sqrt{c}$ as the only random quantity if the original study
-has been completed. Assuming a normal distribution
-\begin{align*}
-  z_r \given z_o, c \sim \Nor(\mu_{z_r}, \sigma^2_{z_r})
-\end{align*}
-which may depend on $z_o$ and $c$ encompasses the typical scenarios under which
-one would want to compute the probability for replication success. For example,
-under the null hypothesis ($H_{0} \colon \theta = 0$), we have $\mu_{z_r} = 0$
-and $\sigma^2_{z_r} = 1$. For conditional power we assume the underlying effect
-size equals the original effect estimate ($\theta = \that_o$) and therefore
-$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1$. Finally, predictive power
-is obtained by using the predictive distribution based on the advocacy prior
-($\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$) and thus
-$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1 + c$.
-
-Applying some algebraic manipulations to \eqref{eq1:RSCond-d}, the
-probability for replication success at level $\gamma$ can be computed by
-\begin{align}
-  \label{eq1:powerBFs}
-  \Pr\left(\BFs \leq \gamma \given z_o, c\right) =
-  \begin{cases}
-    \Pr(\chi^2_{1,\lambda} \geq  A/[B \sigma^2_{z_r}])
-    & \text{for} ~ \gy < 1 \\
-    \Phi(\text{sign}(z_o) \left\{\mu_{z_r} - D\right\}/\sigma_{z_r})
-    & \text{for} ~ \gy = 1 \\
-    \Pr(\chi^2_{1,\lambda} \leq A/[B \sigma^2_{z_r}])
-    & \text{for} ~ \gy > 1
-  \end{cases}
-\end{align}
-with non-centrality parameter $\lambda = (\mu_{z_r} - M)^2/\sigma^2_{z_r}$
-and
-\begin{align*}
-  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
-  z_o^2 \left\{\frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \right\}, \\
-  B &= \frac{1 - \gy}{(1 + c\gy)(1/c + 1)}, \\
-  D &= \frac{z_o^2 \{1/2 + 1/(1/c + 1)\} - \log 2}{2 z_o \sqrt{c}} (1 + c) \\
-  M &= \frac{z_o(1 + c\gy)}{\sqrt{c}(\gy - 1)}.
-\end{align*}
-The probability is zero, if the original $z$-value $|z_o|$ is not large enough
-such that the sufficiently sceptical relative prior variance $\gy$ can be
-computed for level $\gamma$ with \eqref{ggamma}.
-
-\section{Probability of replication success with the replication Bayes factor}
-\label{app:powerBFr}
-The probability of $\BFr \leq \gamma$ is equivalent to the probability of
-\begin{align}
-  \label{eq1:BFrsuccess}
-  \log(1 + c) - z_{r}^{2} + \frac{(z_{r} - z_{o}\sqrt{c})^{2}}{1 + c}
-  \leq  2 \log \gamma
-\end{align}
-Applying some algebraic manipulations to \eqref{eq1:BFrsuccess} and assuming a
-normal distribution for $z_{r}$ as in Appendix~\ref{app:powerBFs} leads to
-\begin{align*}
-  \Pr\left(\BFr \leq \gamma \given z_o, c\right) =
-  \Pr\left(\chi^2_{1,\lambda} \geq \left\{z_{o}^{2} + \log(1 + c) - \log \gamma^{2}
-  \right\} [1 + 1/c] / \sigma^2_{z_r}\right)
-\end{align*}
-with non-centrality parameter $\lambda = (\mu_{z_r} + z_{o}/\sqrt{c})^2/\sigma^2_{z_r}$.
-
-\end{subappendices}
-
-% Bibliography
+\section{Discussion}\label{sec2:discussion}
+In this paper, we have expanded on the replication success approach introduced
+in \citet{Held2020} and demonstrated its advantages over alternative methods
+such as the two-trials rule. In particular, the method provides an attractive
+compromise between hypothesis testing and estimation,
+as it penalizes
+shrinkage of the replication effect estimate compared to the original one,
+while ensuring that both are statistically significant to some extent.
+%% For instance, the method will indicate only a low degree of replication success when
+%% the replication study shows a much smaller but statistically significant
+%% effect estimate, whereas it can still indicate some degree of
+%% success when either original or replication $p$-value are slightly above the
+%% significance level. %% , provided their effect estimates are compatible.
+
+We further refined the method by proposing the golden level, a new threshold for
+replication success. It guarantees that borderline significant original studies
+can only be replicated successfully if the replication effect estimate is larger
+than the original one. Compared to the two-trials rule, the golden level offers
+uniform gains in project power and controls the Type-I error rate at any
+one-sided level $\alpha < 0.058$ if the replication sample size
+is not smaller than the original one. Empirical evaluation of data from four
+replication projects highlights that in most cases the methods are in agreement,
+however, for the study pairs where the approaches disagree, the replication
+success approach seems to lead to more sensible conclusions. The good
+performance has been recently confirmed by a comparison of different replication
+success metrics through a simulation study in the presence of publication bias
+\citep{Muradchanian2021}.
+
+Despite a lack of agreement as to which statistical method should be used to
+evaluate replication studies, conclusions based on different methods usually
+agree. Nevertheless, in some cases, classical methods such as the two-trials
+rule may produce anomalies. We argue that the replication success approach
+improves upon existing methods leading to more appropriate inferences and
+decisions that better reflect the available evidence. However, in extreme cases
+the performance of the sceptical $p$-value may be considered as strange or even
+counterintuitive. Specifically, if the original study was only borderline
+significant, a highly significant replication study can only lead to success if
+the replication effect estimate is larger than the original one. To understand
+this behaviour it is important to realize that the proposed approach does not
+synthesize the evidence from the two studies (like a standard meta-analysis).
+The sceptical $p$-value is designed to confirm claims of new discoveries through
+replication, but will remain ``stubborn'' \citep{Ly2020} if the original study
+was not particularly convincing, even if the replication study provides
+overwhelming evidence for an effect. It will lead to a different result if the
+order of studies was reversed, as long as original and replication study do not
+have the same sample size ($c \neq 1$). The related harmonic mean $\chi^2$-test
+\citep{Held2020b} for evidence synthesis of two or more studies also requires
+each study to be convincing on its own to a certain degree, but treats them as
+exchangeable.
+
+With this paper we further advanced the reverse-Bayes methodology for the
+analysis and design of replication studies, yet certain limitations and
+opportunities for future research remain: First, assuming normality of the
+effect estimates may be questionable, especially for small sample sizes, and
+more robust distributional assumptions could be considered. Second, in some
+types of analyses (\eg{} regression or ANOVA) the effect estimate is a vector and
+the approach would need suitable adaptations. Third, there is a recent trend to
+not only conduct one but several replications for one original study
+\citep[\eg{}][]{Klein2014, Ebersole2016, Klein2018}. Also for this situation, the
+method would need to be adapted, \eg{} the replication estimates could be first
+synthesized and an analysis of replication success could be performed
+subsequently.
+
+Throughout the paper we have assumed that the relative sample size is fixed in
+advance. In practice the sample size of the replication study is often chosen
+based on the result of the original study \citep{Anderson2017}. Power
+calculations as shown in Figure \ref{fig2:fig3} can then be inverted to determine
+the appropriate sample size of the replication study. We can also invert
+equation \eqref{eq2:res} to obtain the required replication sample size based on
+the specification of the minimum relative effect size $\dmin$ to achieve
+replication success. This novel way of calculating the sample size requires the
+specification of the minimum relative effect size which can still be considered
+as acceptable. Sample size calculations based on the two-trials rule can also be
+formulated in terms of the minimum relative effect size by inverting equation
+\eqref{eq2:dSig}. We will report on a detailed comparison of the different
+approaches in future work.
+
+\section*{Data and Software}
+Code and data to reproduce our analyses are available at
+\url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
+the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
+The data which was used is available in the R package
+\texttt{ReplicationSuccess} (available on CRAN). Further information can be
+found on the corresponding help page (with the command \texttt{?RProjects}).
+
+\section*{Acknowledgments}
+Support by the Swiss National Science Foundation (Project \#~189295) is
+gratefully acknowledged. We acknowledge helpful and constructive comments by the
+editor and a referee on an earlier version of this article.
+
 \bibliographystyle{apalikedoiurl}

### 2022-12-02 paper2.tex
change paper order 1 and 2

--- 2022-11-25 paper2.tex
@@
 \section*{Abstract}
-Replication studies are increasingly conducted in order to confirm original
-findings. However, there is no established standard how to assess replication
-success and in practice many different approaches are used. The purpose of this
-paper is to refine and extend a recently proposed reverse-Bayes approach for the
-analysis of replication studies. We show how this method is directly related to
-the relative effect size, the ratio of the replication to the original effect
-estimate. This perspective leads to a new proposal to recalibrate the assessment
-of replication success, the golden level. The recalibration ensures that for
-borderline significant original studies replication success can only be achieved
-if the replication effect estimate is larger than the original one. Conditional
-power for replication success can then take any desired value if the original
-study is significant and the replication sample size is large enough. Compared
-to the standard approach to require statistical significance of both the
-original and replication study, replication success at the golden level offers
-uniform gains in project power and controls the Type-I error rate if the
-replication sample size is not smaller than the original one. An application to
-data from four large replication projects shows that the new approach leads to
-more appropriate inferences, as it penalizes shrinkage of the replication
-estimate compared to the original one, while ensuring that both effect estimates
-are sufficiently convincing on their own.
-
-\textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
-two-trials rule, type-I error rate
+
+Replication studies are increasingly conducted but there is no established
+statistical criterion for replication success. We propose a novel approach
+combining reverse-Bayes analysis with Bayesian hypothesis testing: a sceptical
+prior is determined for the effect size such that the original finding is no
+longer convincing in terms of a Bayes factor. This prior is then contrasted to
+an advocacy prior (the reference posterior of the effect size based on the
+original study), and replication success is declared if the replication data
+favour the advocacy over the sceptical prior at a higher level than the original
+data favoured the sceptical prior over the null hypothesis. The sceptical Bayes
+factor is the highest level where replication success can be declared. A
+comparison to existing methods reveals that the sceptical Bayes factor combines
+several notions of replicability: it ensures that both studies show sufficient
+evidence against the null and penalises incompatibility of their effect
+estimates. Analysis of asymptotic properties and error rates, as well as case
+studies from the Social Sciences Replication Project show the advantages of the
+method for the assessment of replicability.
+
+\textbf{Key words}:
+Bayes factor, Bayesian hypothesis testing, replication studies, reverse-Bayes,
+sceptical $p$-value
 
 \section{Introduction}
-Replication studies are conducted in order to investigate whether an original
-finding can be confirmed in an independent study. Although replication has long
-been a central part of the scientific method in many fields, the so-called
-replication crisis \citep{Ioannidis2005, Begley2015} has led to increased
-interest in replication over the last decade. These developments eventually
-culminated in large-scale replication projects that were conducted in various
-fields \citep{Errington2014, Klein2014, Opensc2015, Ebersole2016, Camerer2016,
-  Camerer2018, Cova2018, Klein2018}.
-
-Declaring a replication as successful is, however, not a straightforward task,
-and currently used approaches include statistical significance of both the
-original and replication study, compatibility of their effect estimates, and
-meta-analysis of the effect estimates. Many of the replication projects listed
-above also report the relative effect size, the ratio of the replication to the
-original effect estimate. For example, in \citet{Camerer2018} the replication
-effect estimates were only half as large as the original ones on average and
-even smaller in \citet{Opensc2015}. This gives clear evidence of a systematic
-bias of the original studies and strongly suggests that the original and
-replication study should not be treated as exchangeable. However, all the
-approaches mentioned above will give the same results if the order of studies
-would be reversed.
-
-In order to address this problem, a new method has recently been proposed in
-\citet{Held2020}. The approach combines the analysis of credibility
-\citep{Matthews2001a,Matthews2001b} with a prior-data conflict assessment
-\citep{Box1980}. Replication success is declared if the replication study is in
-conflict with a sceptical prior that would make the original study
-non-significant. This approach penalizes small relative effect sizes as we will
-see in more detail in the following.
-
-To introduce some notation, let $z_o = \hat \theta_o/\sigma_o$ and
-$z_r = \hat \theta_r/\sigma_r$ denote the $z$-statistic of the original and
-replication study, respectively. Here $\hat \theta_o$ and $\hat \theta_r$ are
-the corresponding effect estimates (assumed to be normally distributed) of the
-unknown effect $\theta$ with standard errors $\sigma_o$ and $\sigma_r$,
-respectively. The corresponding one-sided $p$-values are denoted by
-$p_o=1-\Phi(z_o)$ and $p_r=1-\Phi(z_r)$, respectively, where $\Phi(\cdot)$
-denotes the standard normal cumulative distribution function. Let
-$c = \sigma_o^2/\sigma_r^2$ denote the variance ratio of the squared standard
-errors of the original and replication effect estimates. The squared standard
-errors are usually inversely proportional to the sample size of each study, \ie
-$\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
-variance $\kappa^2$. The variance ratio $c$ can then be identified as the
-relative sample size $c=n_r/n_o$. The relative effect size
-\begin{equation}\label{eq2:d}
-  d = \frac{\hat \theta_r}{\hat \theta_o} = \frac{1}{\sqrt{c}} \frac{z_r}{z_o}
-\end{equation}
-quantifies the size of the replication effect estimate $\hat \theta_r$ relative
-to the original effect estimate $\hat \theta_o$. The corresponding shrinkage of
-the replication effect estimate will be denoted as $s=1-d$.
-
-Suppose the original study achieved statistical significance at one-sided level
-$\alpha$, so $p_o \leq \alpha$. The standard approach to assess replication
-success is based on significance of the replication effect estimate at the same
-level $\alpha$, \ie the replication is considered successful if also
-$p_r \leq \alpha$. This approach is known in drug development as the two-trials
-rule \citep{Senn2008}, usually conducted at $\alpha=0.025$. Let
-$z_\alpha = \Phi^{-1}(1-{\alpha})>0$ denote the $z$-value corresponding to the
-level $\alpha$, then significance of the replication study is achieved if
-$z_r \geq z_\alpha$, which is equivalent to the condition
-\begin{equation}\label{eq2:dSig}
-   d \geq \frac{z_\alpha}{z_o  \, \sqrt{c}}
-\end{equation}
-on the relative effect size \eqref{eq2:d}. The right hand-side goes to zero for
-increasing $c$, so if the relative sample size $c$ is large enough, significance
-of the replication study can be achieved with any arbitrarily small (but
-positive) relative effect size $d$. However, declaring replication success when
-there is substantial shrinkage is contrary to common sense, as the replication
-effect estimate may not reflect an effect size of the same practical relevance
-as the original one, despite its statistical significance.
-
-In this paper we first review the \citet{Held2020} approach for the assessment
-of replication success, followed by showing how it relates to the relative
-effect size (Section \ref{sec2:res}). This perspective is used in Section
-\ref{sec2:goldenthresh} and \ref{sec2:recalib} to propose a recalibration of the
-method, the \textit{golden level}, which leads to a more appropriate criterion
-for replication success compared to the two-trials rule (Section \ref{sec2:2TR}).
-In Section \ref{sec2:ER} we study power and Type-I error rates of the proposed
-method and compare it to the two-trials rule. The recalibrated method ensures
-that conditional power can take any desired value if the original study has been
-significant and the replication sample size is large enough (Section
-\ref{sec2:powerrep}), controls the overall Type-I error if the replication sample
-size is not smaller than the original one (Section \ref{sec2:T1E}), and offers
-uniform gains in project power compared to the two-trials rule (Section
-\ref{sec2:PP}). Section \ref{sec2:application} describes an application to data
-from four replication projects and Section \ref{sec2:discussion} closes with some
-discussion.
-
-\section{Replication success}\label{sec2:RS}
-
+As a consequence of the so-called replication crisis, the scientific community
+increasingly recognises the value of replication studies, and several attempts
+have been made to assess replicability on a large scale \citep{Errington2014,
+  Klein2014, Opensc2015, Camerer2016, Camerer2018, Cova2018}. Despite most
+researchers agreeing on the importance of replication, there is currently no
+agreement on a statistical criterion for replication success. Instead, a variety
+of statistical methods, frequentist \citep{Simonsohn2015, Patil2016, Hedges2019,
+  Mathur2020}, Bayesian \citep{Bayarri2002b, Bayarri2002, Verhagen2014,
+  Johnson2016, Etz2016, vanAert2017, Ly2018, Harms2019}, and combinations
+thereof \citep{Held2020, Pawel2020, Held2021} have been proposed to quantify
+replication success.
+
+Due to this lack of an established method, replication projects typically report
+the results of several methods and it is not uncommon for these to contradict
+each other. For example, both studies may find evidence against a null effect,
+but the individual effect estimates may still be incompatible (often the
+replication estimate is much smaller). Conversely, both estimates may be
+compatible, but there may not be enough evidence against a null effect in one of
+the studies.
+
+The objective of this paper is to present a novel Bayesian method for
+quantifying replication success, which builds upon a previously proposed method
+\citep[the \emph{sceptical $p$-value} from][]{Held2020} and unifies several
+notions of replicability. The method combines the natural fit of the
+reverse-Bayes approach to the replication setting with the use of Bayes factors
+for hypothesis testing \citep{Jeffreys1961, Kass1995} and model criticism
+\citep{Box1980}. In a nutshell, replication success is declared if the
+replication data favour an advocacy prior for the effect size, which emerges
+from taking the original result at face value, over a sceptical prior, which
+renders the original result unconvincing.
+
+\citet{Held2020} proposed a reverse-Bayes approach for the assessment of
+replication success: The main idea is to challenge the result from an original
+study by determining a \emph{sceptical prior} for the effect size, sufficiently
+concentrated around the null value such that the resulting posterior is rendered
+unconvincing \citep{Matthews2001b}. An unconvincing posterior at level $\alpha$
+is defined by its $(1 - \alpha)$ credible interval just including the null
+value. Subsequently, the replication data are used in a prior-data conflict
+assessment \citep{Box1980, Evans2006} and replication success is concluded if
+there is sufficient conflict between the sceptical prior and the replication
+data. Specifically, replication success at level $\alpha$ is established if the
+prior predictive tail probability of the replication estimate is smaller than
+$\alpha$. The smallest level $\alpha$ at which replication success can be
+declared corresponds to the sceptical $p$-value.
+
+The method comes with appealing properties: The sceptical $p$-value is never
+smaller than the ordinary $p$-values from both studies, thus ensuring that they
+both provide evidence against the null. At the same time, it also takes into
+account the size of their effect estimates, penalising the case when the
+replication estimate is smaller than the original estimate. \citet{Held2021}
+further refined the method with a recalibration that allows the sceptical
+$p$-value to be interpreted on the same scale as an ordinary $p$-value, as well
+as ensuring appropriate frequentist properties, such as type I error rate
+control if the replication sample size is not smaller than in the original
+study.
+
+Despite the methods' Bayesian nature, it relies on tail probabilities as primary
+inference tool. An alternative is the Bayes factor, the principled Bayesian
+solution to hypothesis testing and model selection \citep{Jeffreys1961,
+Kass1995}. In contrast to tail probabilities, Bayes factors have a more natural
+interpretation and allow for direct quantification of evidence for one
+hypothesis versus another. In this paper we therefore extend the reverse-Bayes
+procedure from \citet{Held2020} to use Bayes factors for the purpose of
+quantifying evidence. This extension was suggested by \citet{Consonni2019} and
+\citet{Pericchi2020} independently. Interestingly, a similar extension of the
+reverse-Bayes method from \citet{Matthews2001b} was already hinted at by
+\citet{Berger2001}, but to date no one has attempted to realise the idea.
+
+The inclusion of Bayes factors leads to a new quantity which we call the
+\emph{sceptical Bayes factor}. Unlike standard forward-Bayes methods, but
+similar to the sceptical $p$-value, the proposed method combines two notions of
+replication success: It requires from both studies to show sufficient evidence
+against the null, while also penalising incompatibility of their effect
+estimates. However, while the sceptical $p$-value quantifies compatibility only
+indirectly through conflict with the sceptical prior, the sceptical Bayes factor
+evaluates directly how likely the replication data are to occur under an
+advocacy prior (the reference posterior of the effect conditional on the
+original study). This direct assessment of compatibility allows for stronger
+statements about the degree of replication success, and it may also lead to
+different conclusions in certain situations.
+
+This paper is structured as follows: Section \ref{sec2:methods} presents the
+derivation of the sceptical Bayes factor. Its asymptotic and finite sample
+properties are then compared with other measures of replication success in
+Section \ref{sec2:comparison}. An extension to non-normal models is presented in
+Section \ref{sec2:tdist}. Section \ref{sec2:applications} illustrates how the
+method works in practice using case studies from the \emph{Social Sciences
+  Replication Project} \citep{Camerer2018}. Section \ref{sec2:discussion}
+provides concluding remarks about strengths, limitations and extensions of the
+method.
+
+\subsection*{Notation and assumptions}
+Denote the Bayes factor comparing the plausibility of hypotheses $H_1$ and $H_2$
+with respect to the observed data $x$ by
+\begin{align*}
+  \BFcol{1}{2}(x) = \frac{f(x \given H_1)}{f(x \given H_2)}
+  = \frac{\int_{\Theta_1} f(x \given \theta_1)f(\theta_1) \, \text{d}\theta_1}{
+  \int_{\Theta_2} f(x \given \theta_2)f(\theta_2) \, \text{d}\theta_2},
+\end{align*}
+where $f(x \given H_i)$ is the marginal likelihood of the data under $H_i$
+obtained by integrating the likelihood $f(x \given \theta_{i})$ with respect to
+the prior distribution $f(\theta_{i})$ of the model parameters
+$\theta_i \in \Theta_i$ with $i = 1, 2$. Sometimes we will also write
+$\BFcol{1}{2}(x ; \phi^\prime)$ to indicate that the Bayes factor is evaluated
+for a specific value $\phi^\prime$ of a hyperparameter $\phi$ of one of the
+model priors. To simplify comparison with $p$-values we will orient Bayes
+factors such that lower values indicate more evidence against a null hypothesis.
+
+Let $\theta$ denote the effect of a treatment on an outcome of interest. Let
+$\that_o$ and $\that_r$ denote its maximum likelihood estimates obtained from an
+original (subscript $o$) and from a replication study (subscript $r$),
+respectively. Let the corresponding standard errors be denoted by $\sigma_o$ and
+$\sigma_r$, the $z$-values by $z_o = \that_o/\sigma_o$ and
+$z_r = \that_r/\sigma_r$, and define the variance ratio as
+$c = \sigma_o^2/\sigma_r^2$ and the relative effect estimate as
+$d = \that_r/\that_o = z_r/(z_o\sqrt{c})$. For many effect size types the
+variances are inversely proportional to the sample size, \ie{}
+$\sigma^2_{o} = \kappa/n_{o}$ and $\sigma^2_{r} = \kappa/n_{r}$ for some unit
+variance $\kappa$. The variance ratio is then the ratio of the replication to
+the original sample size $c = n_{r}/n_{o}$.
+
+We adopt a meta-analytic framework and consider the effect estimates as the
+data, rather than their underlying samples, and assume that
+$\that_k \given \theta \sim \Nor(\theta, \sigma^2_k)$ for $k \in \{o, r\},$ \ie{}
+normality of the effect estimates around $\theta$, with known variances equal to
+their squared standard errors. For studies with reasonable sample size, this
+framework usually provides a good approximation for a wide range of (suitably
+transformed) effect size types \citep[Chapter 2.4]{Spiegelhalter2004}. For
+example, means and mean differences (no transformation), odds ratios, hazard
+ratios, risk ratios (logarithmic transformation), or correlation coefficients
+(``Fisher-$z$'' transformation). We refer to the literature of meta-analysis for
+details about transformations of effect sizes \citep[\eg{}][Chapter
+11.6]{Cooper2019}. The normal model in combination with conjugate priors enables
+derivation of closed-form expressions in many cases, which allows us to easily
+study limiting behaviour and facilitates interpretability. In Section
+\ref{sec2:tdist}, we will present relaxations of the normality assumption, which
+can lead to more accurate inferences when studies have small sample sizes and/or
+show extreme results.
+
+\section{Reverse-Bayes assessment of replication success with Bayes factors}
+\label{sec2:methods}
+% ``judgements are made concerning the values that the final
+% probabilities would have after some imaginary results are obtained; then Bayes'
+% theorem is used backwards to estimate what the consistent initial probabilities
+% must be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain
+% estimates of the final probabilities in the light of the actual observations.
+% This device takes \emph{seriously} the view that a theory of probability or of
+% rationality is no more than a theory of consistency'' (p. 126).
+The idea of reversing Bayes' theorem was first proposed by \citet{Good1950}. He
+acknowledged that in many situations there is no obvious choice for the prior
+distributions involved in Bayesian analyses. On the other hand, we are often
+more certain which posterior inferences would convince us regarding the
+credibility of a hypothesis. For this reason, Good inverted Bayes' theorem and
+derived priors, which combined with the observed data, would lead to posterior
+inferences that were specified beforehand (\eg{} the data favour one hypothesis
+over another). His reverse-Bayes inference then centred around the question
+whether the resulting prior is plausible, and if so, this would legitimise the
+posterior inference. See Figure~\ref{fig2:RBschmema} for a graphical illustration
+of this process.
+
+\begin{figure}[!htb]
+  \centering
+%% first attempt
+\begin{tikzpicture}[node distance = 5em, thick]
+  % nodes %
+  \node[font = \large] (data) {$f(\text{data} \,|\, \theta)$};
+  \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
+  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \text{data})$};
+  \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
+  \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};
+
+  % edges %
+  \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
+  %% other names could be:
+  %% - reverse Bayesian updating vs forward Bayesian updating
+  %% - Bayesian reverting
+  \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
+  \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
+  \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
+\end{tikzpicture}
+\caption{Schematic illustration of reverse-Bayes and forward-Bayes inference
+  for an unknown parameter $\theta$.}
+\label{fig2:RBschmema}
+\end{figure}
+
+Good argued that philosophically there is nothing wrong with inferences
+resulting from backwards use of Bayes' theorem, since the theorem merely
+constrains prior and posterior to be consistent with the laws of probability
+(regardless of their conventional names suggesting a particular temporal
+ordering). Despite his advocacy, the reverse-Bayes idea remained largely
+unexplored until \citet{Matthews2001b} introduced the \emph{Analysis of
+Credibility}, which in turn led to new developments in reverse-Bayes methodology
+(see \citet{Held2021b} for a recent review). Most of these approaches use the
+reversal of Bayes' theorem in order to challenge or substantiate the credibility
+of scientific claims. Usually, a posterior inference corresponding to
+(non-)credibility of a claim is specified, and the associated prior is then
+derived from the data. Inference is subsequently carried out based on this
+reverse-Bayes prior, \eg{} the interest is often to check whether the prior is
+plausible in light of external evidence, an obvious candidate being data from a
+replication study. This can be done, for example, using methods to assess
+prior-data conflict \citep{Box1980, Evans2006}.
+
+% Good, Good Thinking, P. 126:
+%``In some cases it should be possible to make some progress in the estimation of
+% relative initial probabilities by assuming that the current judgements are correct and
+% by using Bayes's theorem backwards. This idea is closely related to the ``device
+% of imaginary results'' in which judgements are made concerning the values that the
+% final probabilities would have after some imaginary results are obtained; then Bayes'
+% theorem is used backwards to estimate what the consistent initial probabilities must
+% be assumed to be; and lastly Bayes's theorem is used (forwards) to obtain estimates
+% of the final probabilities in the light of the actual observations. This device takes
+% \emph{seriously} the view that a theory of probability or of rationality is no more
+% than a theory of consistency.''
+
+In this paper, we consider a reverse-Bayes procedure consisting of two stages
+that naturally fit the replication setting: We first determine a
+\emph{sufficiently sceptical prior} for the effect $\theta$ such that the
+original result is no longer convincing in terms of a suitable Bayes factor.
+Using another Bayes factor, we then quantify replication success by comparing
+how likely the replication data are predicted by the sufficiently sceptical
+prior relative to an \emph{advocacy prior}, which is the posterior of the effect
+$\theta$ conditional on the original data and an uninformative/reference prior.
+Box \hyperref[box:nutshell]{1} provides a summary of the procedure, the
+following sections will explain it in more detail.
+
+% summarize procedure in box
+\begin{table}[!hbt]
 \begin{center}
-\begin{figure}[!h]
-\begin{center}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig1-1}
-
+\fbox{
+\begin{minipage}{.95\linewidth}
+  \begin{enumerate}[leftmargin=*]
+
+    \item \textbf{Original study}:
+    For the original effect estimate
+$\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$ consider the point null
+hypothesis $H_0 \colon \theta = 0$ vs. $\HS \colon \theta \neq 0$. Fix a level
+$\gamma \in (0, 1)$ and determine the sufficiently sceptical prior under the
+alternative $\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ such that the
+Bayes factor contrasting $H_0$ to $\HS$
+is $$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma.$$ The prior
+$\theta \given \HS$ represents a \emph{sceptic} who remains unconvinced about
+the presence of an effect at level $\gamma$.
+
+    \item \textbf{Replication study}:
+          For the replication effect estimate
+$\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ compute the Bayes factor
+contrasting the sceptic $\HS \colon \theta \sim \Nor(0, \gy \cdot \sigma^2_o)$
+to an advocate $\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$. Declare
+\emph{replication success} at level $\gamma$ if
+          $$\BFcol{\mathrm{S}}{\mathrm{A}}(\that_r; \gy) \leq \gamma,$$
+          \ie{} the data favour the advocate over the sceptic at a higher level
+than the sceptic's initial objection.
+
+    \item[$\rightarrow$] The \emph{sceptical Bayes factor} $\BFs$ is the
+smallest level $\gamma$ at which replication success can be declared.
+ \end{enumerate}
+\end{minipage}
 }
-
-\end{knitrout}
-\caption{Example of the assessment of replication success. The original study
-  from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
-  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value $p_o = 0.011$.
-  The left part of the figure illustrates the reverse-Bayes derivation of the
-  sufficiently sceptical prior based on the original study result and the
-  posterior with lower credible limit fixed at zero. The comparison of the
-  sufficiently sceptical prior with the replication study result
-  ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$) in the
-  right part of the figure is used to assess potential prior-data conflict.}
-  \label{fig2:fig1}
 \end{center}
-\end{figure}
-\end{center}
-
-Hereinafter we focus on the one-sided assessment of replication success to
-ensure that replication success can only occur if the original and replication
-effect estimates go in the same direction. Figure \ref{fig2:fig1} illustrates the
-\citet{Held2020} approach based on a replication study from the \textit{Social
-  Sciences Replication Project} \citep{Camerer2018}: the significant original
-finding by \citet{Pyc2010} at one-sided level $\alpha=0.025$ is challenged with
-a sceptical prior, sufficiently concentrated around zero to make the original
-study result no longer convincing \citep{Matthews2001a,Matthews2001b}.
-Replication success is then defined as conflict between the sceptical prior and
-the result from the replication study in order to disprove the sceptic. Conflict
-is quantified by a prior-predictive tail probability $p_{\mbox{\scriptsize
-    Box}}$ \citep{Box1980} where a small value $p_{\mbox{\scriptsize
-    Box}} \leq \alpha$ defines replication success. In Figure \ref{fig2:fig1} the
-original finding is only borderline significant, so the sufficiently sceptical
-prior is fairly wide. Furthermore, there is substantial shrinkage
-($d = 0.15/0.4 = 0.38$) of the replication effect estimate and therefore hardly
-any conflict with the sufficiently sceptical prior (one-sided
-$p_{\mbox{\scriptsize Box}}=0.31$). We are thus not able to declare replication
-success at level $2.5$\%.
-
-The actual value of $p_{\mbox{\scriptsize Box}}$ is difficult to interpret as it
-depends on the level $\alpha$ and does not even exist if the original $p$-value
-$p_o$ exceeds $\alpha$. However, \citet{Held2020} showed that if both
-$\sign(z_o)=\sign(z_r)$ and
-\begin{equation}\label{eq2:extrinsic.p}
-\left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
-- 1 \right) \geq c
-\end{equation}
-hold, replication success at level ${\alpha_S}$ is achieved, where
-$z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$. The requirement
-\eqref{eq2:extrinsic.p} can be assessed for any value of
-${{\alpha_S}} > \max\{p_o, p_r\}$ and of particular interest is the smallest
-possible value of $\alpha_S$ where \eqref{eq2:extrinsic.p} holds, the so-called
-\textit{sceptical $p$-value} $p_S$. We are thus interested in the value $z_S^2$
-that fulfills
-\begin{equation}\label{eq2:extrinsic.p2}
-\left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
-- 1 \right) = c.
-\end{equation}
-There is a unique solution of \eqref{eq2:extrinsic.p2} which defines the
-one-sided {sceptical $p$-value} $p_S= 1-\Phi\left({z_S}\right)$ where
-$z_{S} \coloneqq + \surd z_{S}^2$, provided $\sign(z_o)=\sign(z_r)$ holds.
-Replication success at level $\alpha_S$ is then achieved if $p_S \leq \alpha_S$.
-In the introductory example based on the original study by \citet{Pyc2010}, the
-sceptical $p$-value turns out to be $p_S=0.11$.
-
-The sceptical $p$-value has a number of interesting properties, see
-\citet[Section 3.1]{Held2020} for details. In particular,
-$p_S > \max\{p_o, p_r\}$ always holds with $p_S \downarrow \max\{p_o, p_r\}$ for
-$c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
-sceptical $p$-value $p_S$ increases with decreasing relative effect size $d$.
-The first property ensures that both the original and the replication study have
-to be sufficiently convincing on their own to achieve replication success. The
-second property guarantees that shrinkage of the replication effect estimate is
-penalized.
-
-The level for replication success $\alpha_S$ has to be distinguished from the
-significance level $\alpha$ associated with the ordinary $p$-value.
-\citet{Held2020} has used the \textit{nominal level} for replication success
-($\alpha_S=\alpha$) for convenience, but in the following we will propose a
-recalibration of the procedure along with a new value for $\alpha_S$, the
-\textit{golden level} (Section~\ref{sec2:goldenthresh}). The derivation is based
-on a property of the required relative effect size for replication success, if
-the relative sample size is very large (Section~\ref{sec2:res}). In a nutshell,
-the golden level ensures that for original studies which were only borderline
-significant ($p_o=\alpha$), replication success is only possible if the
-replication
-effect estimate is larger than the original one ($d > 1$).\\
-
-\subsection{Relative effect size}\label{sec2:res}
-Without loss of generality we now assume that $\hat \theta_o > 0$ and that
-$p_o < {\alpha_S}$ has been observed in the original study, otherwise it would
-be impossible to achieve replication success at level $\alpha_S$ because $p_S$
-is always larger than $p_o$. The condition \eqref{eq2:extrinsic.p} for
-replication success can then be re-written as
-\begin{equation}\label{eq2:eq.z}
-  z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
-\end{equation}
-where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of \eqref{eq2:eq.z} is
-the minimum replication $z$-value $\zrmin$ required to achieve replication
-success. Note that $\zrmin$ increases with increasing $c$, so increasing the
-replication sample size leads to a more stringent success requirement $z_r$ and
-the corresponding replication $p$-value $p_r$.
-
-Equation \eqref{eq2:eq.z} can be further transformed to a
-condition on the relative effect size \eqref{eq2:d}:
-\begin{equation}\label{eq2:res}
-  d \geq  \frac{\sqrt{1+c/(K-1)}}{ \sqrt{c K}} \eqqcolon \dmin .
-\end{equation}
-To achieve replication success, the relative effect size must be at least as
-large as the right hand-side of \eqref{eq2:res}, the minimum relative effect size
-$\dmin$, a function of $K$ and the relative sample size $c$. If the relative
-sample size becomes very large, \ie $c \rightarrow \infty$, we have
-$\dmin \downarrow \dinfty$ where
-\begin{equation}\label{eq2:smallestpossible}
-  \dinfty = 1/\sqrt{K (K-1)}
-\end{equation}
-is the \textit{limiting relative effect size}. This shows that the minimum
-relative effect size $\dmin$ in \eqref{eq2:res} does not go to zero for
-increasing $c$, so replication success cannot be achieved if the relative effect
-size $d$ is smaller or equal to $\dinfty$, no matter how large the replication
-study is. In contrast, the corresponding criterion \eqref{eq2:dSig} of the
-two-trials rule can be achieved for any positive relative effect size,
-regardless of how small, provided the replication sample size is sufficiently
-large.
-
-\subsection{The golden level}\label{sec2:goldenthresh}
-Significance of both the original and the replication study at level $\alpha$ is
-a necessary but not sufficient requirement for replication success at the
-nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
-stringent. It is more reasonable to calibrate the procedure in such a way that
-to establish replication success, original and replication study do not both
-necessarily need to be significant at level $\alpha$, provided that the
-replication effect estimate does not shrink compared to the original one. We
-therefore choose a level $\alpha_S$ such that a borderline significant original
-study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
-$s > 0$ of the replication effect estimate. Mathematically, this translates to
-setting $\dinfty = 1$ and $K = z_\alpha^2/z_{\alpha_S}^2$
-in~\eqref{eq2:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
-with solution $K = \varphi$ where $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
-known as the golden ratio. Solving for $z_{\alpha_S}$ gives
-$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
-  level}
-\begin{eqnarray}\label{eq2:golden}
-\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
-\end{eqnarray}
-for replication success. This is our recommended default choice to assess
-replication success and we will study its properties in the following in more
-detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
-$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig2:fig1},
-the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
-\citet{Pyc2010} study was not successful.
-
-The golden level \eqref{eq2:golden} is derived from~\eqref{eq2:smallestpossible}
-with $\dinfty = 1$. However, we may also use a different value for the limiting
-relative effect size $\dinfty$, say $\dinfty=0.8$. Then replication success is
-only possible for a borderline significant result ($p_o = \alpha$) if there is
-less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication
-effect estimate. This approach is equivalent to a limiting relative effect size
-of 1 if the original $p$-value $p_o$ is equal to a different level $\alpha'$,
-which can be derived as follows: First, solving \eqref{eq2:smallestpossible} for
-$\dinfty > 0$ gives
-$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
-$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
-$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
-\begin{equation}\label{eq2:alphaPrime}
-\alpha' = 1-\Phi\left(z_{\alpha} \, \sqrt{\varphi / K} \right).
-\end{equation}
-For example, for $\alpha = 0.025$ and $\dinfty = 0.8$ we obtain $\alpha'=0.033$.
-
-\subsection{Recalibration of the sceptical \textit{p}-value}\label{sec2:recalib}
-
-The condition $p_S \leq \alpha_S$ for replication success at the golden level is
-equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie
-$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
-recalibrate the sceptical $p$-value $p_{S} = 1 - \Phi(z_S)$ to
-$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
-to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
-be interpreted on the same scale as an ordinary $p$-value. For example, the
-recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
-out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
-level $\alpha<0.061$, including the standard $0.025$ level.
-
-\subsection{Comparison with the two-trials rule}\label{sec2:2TR}
-A useful benchmark for comparison is the two-trials rule in drug development
-\citep[Section 9.4]{Kay2015}, which requires ``at least two adequate and
-well-controlled studies, each convincing on its own, to establish
-effectiveness'' \citep[p.~3]{FDA1998}. This is usually achieved by independently
-replicating the result of a first study in a second study, both significant at
-one-sided level $\alpha=0.025$. {It is worth noting that in practice the two
-  trials are often run in parallel} {\citep{Senn2008}}{, so do not exactly
-  resemble the replication setting.}
-
-The main difference between the replication success and the two-trials
-rule approach concerns how shrinkage of the replication effect
-estimate is handled. Figure~\ref{fig2:fig2} illustrates that
-shrinkage is penalized in the assessment of replication success, \ie
-the original $p$-value needs to be quite small to achieve replication
-success for a relative effect size $d<1$. In contrast, significance of
-the replication study can be achieved even if there is substantial
-shrinkage, provided the replication sample size is large enough.
-
-\begin{figure}[!h]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig2-1}
-
-}
-
-\end{knitrout}
-\caption{Comparison of replication success at the golden level
-  ($p_S \leq \alpha_S = 0.062$) and the two-trials rule ($p_o \leq 0.025$ and
-  $p_r \leq 0.025$). The dotted areas indicate that success is impossible for
-  original $p$-value $p_o$ and relative effect size $d$. In the white areas
-  success is possible and depends on the relative sample size $c$ as indicated
-  by the grey lines. The dashed black line in the left plot indicates the
-  limiting relative effect size $\dinfty$. }
-\label{fig2:fig2}
-\end{figure}
-
-It is interesting to directly compare the two-trials rule and replication
-success at the golden level in terms of the required relative effect size $d$ to
-fulfill the criteria \eqref{eq2:dSig} and \eqref{eq2:res}, respectively, see
-Figure~\ref{fig2:fig2}. If the original $p$-value is not significant at level
-$\alpha$, only replication success can be achieved, but will require a
-replication effect estimate larger than the original one.
-
-For example, four studies with one-sided $p_o \in (0.025, 0.03)$ have been
-included in the \textit{Reproducibility Project: Psychology} \citep{Opensc2015}
-and one of them achieves replication success (see Section \ref{sec2:application}
-for details). By definition, such non-significant original findings can never
-fulfill the two-trials rule.
-
-If the original $p$-value is smaller than $\alpha$, then the situation depends
-on the relative sample size $c$. For example, when the replication sample size
-is chosen to be the same as in the original study ($c=1$) and $\alpha=0.025$,
-original studies with a $p$-value larger than $0.006$ will require a smaller
-relative effect size $d$ with the two-trials rule, while $p$-values smaller than
-$0.006$ will require a smaller relative effect size $d$ with the replication
-success method. This illustrates that the latter method is less stringent than
-the two-trials rule if the original study is already sufficiently convincing.
-
-\section{Power and Type-I Error Rate}\label{sec2:ER}
-Although Bayesian methods do not rely on the frequentist paradigm of repeated
-testing, it is still useful to investigate their frequentist operating
-characteristics \citep{Dawid1982, Rubin1984, Grieve2016} and this also holds for
-the proposed reverse-Bayes assessment of replication success. We first condition
-on the results from the original study and compare the power to achieve
-replication success with the two-trials rule in Section \ref{sec2:powerrep}. We
-then assume that none of the two studies have been conducted and investigate the
-overall Type-I error rate (Section \ref{sec2:T1E}) and the project power (Section
-\ref{sec2:PP}) \citep{Maca2002} over both studies in combination for fixed
-relative sample size $c$.
-
-\subsection{Conditional power}\label{sec2:powerrep}
-
-\begin{figure}[!ht]
-\begin{center}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig3-1}
-
-}
-
-\end{knitrout}
-\end{center}
-\caption{Conditional power as a function of the {one-sided} $p$-value of the
-  original study with relative sample size $c=1$ (left) and $c=5$ (right). Shown
-  is conditional power assuming the unknown parameter is equal to the original
-  effect estimate (solid) and conditional power based on 20\% shrinkage of the
-  original effect estimate (dashed) for the two-trials rule (2TR) at level
-  $\alpha = 0.025$ and for replication success at the corresponding golden and
-  nominal level. Power values of exactly zero are omitted.}
-\label{fig2:fig3}
-\end{figure}
-
-Figure~\ref{fig2:fig3} compares the power for replication success
-\citep[see][Section 4 for details]{Held2020} at the golden and at the nominal
-level with the power of the two-trials rule for relative sample size $c = 1$
-(left) and $c = 5$ (right) as a function of the one-sided $p$-value $p_o$ from
-the original study. Shown is the conditional power assuming the unknown
-parameter $\theta$ is equal to the original effect estimate $\hat \theta_o$.
-Then $\hat \theta_r \given \hat \theta_o \sim \Nor(\hat \theta_o, \kappa^2/n_r)$
-and it follows that $d \given \hat \theta_o \sim \Nor(1, 1/(c z_o^2))$. The
-conditional power for replication success can therefore be calculated as
-\begin{equation}\label{eq2:condPower}
-\P(d \geq \dmin \given \hat \theta_o) = \Phi\left[\sqrt{c} z_o (1-\dmin)\right],
-\end{equation}
-where $\dmin$ is given in \eqref{eq2:res}. Predictive power, which is conditional
-power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution for the
-effect size $\theta$, could also be calculated, then
-\mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}. Conditional and
-predictive power of the two-trials rule also depend on $z_o$, $c$ and $\alpha$
-and are given in \citet{Micheloud2020}.
-
-The two-trials rule requires a significant original study and hence it is
-impossible to power a replication study when $p_o > 0.025$. The same applies for
-replication success at the nominal level, where the power is zero for any
-$p_o > 0.025$, regardless of the replication sample size. This is different for
-the golden level, where the conditional power of an original study with
-$0.025 < p_o < 0.062$ is low, but not zero. However, if the original $p$-value
-$p_o$ is slightly smaller than $0.025$, the two-trials rule has a larger power,
-both for $c=1$ and $c=5$. But if the original $p$-value is sufficiently small
-($p_o < 0.006$ for $c=1$), the power for replication success at the golden level
-is larger than the power of the two-trials rule.
-
-Compared to $c=1$, the conditional power for $c=5$ of both the two-trials rule
-and the replication success approach at the golden level increases if
-$p_o \leq \alpha$. A remarkable feature of the replication success approach at
-the golden level is that conditional power can be pushed towards 100\% for large
-enough $c$ if $p_o<\alpha$, but not otherwise. This can be seen from
-\eqref{eq2:condPower} because $\dmin < 1$ for $p_o<\alpha$ and large enough
-relative sample size $c$. On the other hand, for $p_o > \alpha$ conditional
-power for replication success will tend to 0\% for increasing $c$ because
-$\dmin>1$ for all $c$. Finally, for $p_o = \alpha$ the limit is 50\%. The same
-property can be observed at the nominal level, however at the smaller threshold
-$1-\Phi(z_\alpha \sqrt{\varphi})$ which is $0.006$ for $\alpha=0.025$. Only if
-$p_o < 0.006$ will the conditional power for replication success attain 100\%
-for $c \to \infty$. This further highlights the stringency of the nominal level.
-
-The approach described so far takes the original study at face-value since it
-assumes that $\hat \theta_o$ is equal to the unknown effect size $\theta$. In
-practice, however, there are often good reasons to believe that original effect
-estimates have a tendency to be inflated (\eg due to publication bias). One way
-to address this issue is to base power calculations on a shrunken version of the
-original effect estimate, where the amount of shrinkage is guided by domain
-knowledge and a risk of bias assessment of the original study. For illustration,
-Figure~\ref{fig2:fig3} also shows conditional power based on 20\% shrinkage of
-the original effect estimate which reduces the conditional power for all
-methods, especially for a relative sample size $c = 1$. Conditional power for
-replication success at the golden level can now be pushed towards 100\% only for
-$p_o < 0.018$, which can be derived by solving \eqref{eq2:alphaPrime} for
-$\alpha$ with $\alpha'=0.025$ and $\dinfty=0.8$. To be able to push conditional
-power based on 20\% shrinkage towards 100\% for all $p_o < 0.025$, equation
-\eqref{eq2:alphaPrime} would have to be used directly to relax the level from
-$\alpha=0.025$ to $\alpha'=0.033$.
-
-\subsection{Overall Type-I error rate}\label{sec2:T1E}
-The two studies are assumed to be independent with Type-I error rate fixed at
-$\alpha$ for each of them, so the Type-I error rate of the two-trials rule over
-the entire project is simply $\alpha^2$ for any value of the relative effect
-size $c$. In contrast, the Type-I error rate of the proposed replication success
-assessment {depends on} the relative sample size $c$.
-
-For $c=1$, \citet[Section 3]{Held2020} showed that $z_S^2$ in
-\eqref{eq2:extrinsic.p2} simplifies to half the harmonic mean of the squared test
-statistics $z_o^2$ and $z_r^2$. The connection $z_S^2 = z_H^2/4$ to the harmonic
-mean $\chi^2$-test statistic $z_H^2$ \citep{Held2020b}, which has a
-$\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
-compute the Type-I error rate at level $\alpha_S$ for $c = 1$ as
-\begin{eqnarray}\label{eq2:T1E}
-\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
- \right]\right\}/2.
-\end{eqnarray}
-For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type-I error
-rate \eqref{eq2:T1E} is $0.0515$\%, slightly less than the Type-I error rate
-$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type-I error
-rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
-0.0625\%.
-
-For $c \neq 1$, the Type-I error rate can be calculated through numerical
-integration:
-\begin{equation}\label{eq2:T1E0}
-  \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
-\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
-  \phi(z_o) \, dz_o,
-\end{equation}
-where $\phi(\cdot)$ denotes the standard normal density function. The first term
-in the integral of \eqref{eq2:T1E0} is the probability of replication success at
-level $\alpha_S$ conditional on a fixed original test statistic $z_o$ and a
-relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
-this term simplifies to
-$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ where $\zrmin$
-in \eqref{eq2:eq.z} depends on $z_o$, $c$, and $\alpha_S$.
-
-\begin{figure}[!h]
-\centering
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig4-1}
-
-}
-
-\end{knitrout}
-
-\caption{Overall Type-I error rate (left) and project power (right) for fixed
-  relative sample size $c$. Results are given for replication success at the
-  nominal and golden level and compared with the two-trials rule (2TR) at
-  $\alpha = 0.025$. The dashed darkgrey line is the project power at the golden
-  level based on significant original studies ($p_o \leq 0.025$). The power of
-  the original study is 90\%.}
-\label{fig2:fig4}
-\end{figure}
-
-The left plot in Figure \ref{fig2:fig4} displays the Type-I error rate for
-$\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
-that the Type-I error of the replication success approach decreases with
-increasing relative sample size $c$. This also follows from \eqref{eq2:T1E0}
-where $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ decreases
-with increasing $c$, because $\zrmin$ increases with increasing $c$, see
-equation \eqref{eq2:eq.z}.
-
-The Type-I error rate of the nominal level is always below the target
-$0.0625$\%. Although the Type-I error will eventually attain $\alpha^2$ in the
-limit $c \downarrow 0$ \citep[Section 3.4]{Held2020}, the nominal level seems to
-be too stringent for realistic values of $c$. The Type-I error rate of the
-golden level is smaller than $0.0625$\% for $c >0.85$. Appropriate Type-I error
-control is thus ensured even for replication studies where the sample size is
-slightly smaller than in the original study.
-
-\begin{figure}[!ht]
-\begin{center}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig5-1}
-
-}
-
-\end{knitrout}
-
-\end{center}
-\caption{Overall Type-I error rate if the replication sample size equal to the
-  original study ($c=1$). The two-trials rule (2TR) is compared to replication
-  success at the golden and nominal level for different values of $\alpha$.}
-\label{fig2:fig5}
-\end{figure}
-
-Figure \ref{fig2:fig5} compares for $c=1$ the Type-I error rate \eqref{eq2:T1E} of
-replication success at the golden and at the nominal level with the two-trials
-rule for different values of $\alpha$. The Type-I error rate of the two-trials
-rule is $\alpha^2$ and the replication success approach at the nominal level
-always has a much smaller Type-I error rate than $\alpha^2$. At the golden level
-the Type-I error rate of the replication success approach is much closer to
-$\alpha^2$, still slightly smaller if $\alpha < 0.058$. For $\alpha = 0.058$ the
-Type-I error rate is equal to the Type-I error rate $0.058^2 = 0.34\%$ of the
-two-trials rule and for $\alpha > 0.058$ the Type-I error rate is slightly
-larger than $\alpha^2$. The Type-I error rate for replication success decreases
-with increasing $c$, so as long as the replication sample size is not smaller
-than the original sample size, Type-I error control at $\alpha^2$ is guaranteed
-at the golden level for any one-sided level $\alpha < 0.058$.
-
-\subsection{Project power}\label{sec2:PP}
-Under the alternative we have $z_o\sim \Nor(\mu, 1)$ with
-$\mu = z_\alpha + z_\beta$ where $\alpha$ is the assumed significance level and
-$1-\beta = \Phi(\mu - z_\alpha)$ is the power to detect the assumed effect
-$\theta = \mu \sigma_o$ in the original study \citep[Section 3.3]{Matthews2006}.
-In the following $\alpha=0.025$ and $\beta=0.1$ are used. The power of a
-significant replication study with sample size $n_r = c n_o$ is
-\begin{equation*}
-\Phi(\theta/\sigma_r - z_\alpha) =
-\Phi(\sqrt{c} \mu - z_\alpha),
-\end{equation*}
-
-so depends on $\mu$ and the relative sample size $c$. The project power of the
-two-trials rule is therefore $(1-\beta) \, \Phi(\sqrt{c} \mu - z_\alpha)$ and
-increases with increasing $c$.
-
-The project power for replication success is computed as
-\begin{equation*}
-  \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
-\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
-  \phi(z_o - \mu) \, dz_o
-\end{equation*}
-and shown in the right plot of Figure \ref{fig2:fig4} as a function of $c$. For
-the golden level, the project power quickly increases to values above 90\%,
-whereas the nominal level only reaches around 80\% project power. The project
-power based on the two-trials rule is shown for comparison, which is always
-smaller than for the golden level and converges to 90\% for large $c$.
-
-The advantage in power stems partly from replication success still being
-possible when the original $p$-value is larger than 0.025, but smaller than
-0.062. If we assume that a replication study is only conducted if the original
-study is significant (with $p_o \leq 0.025$), then the project power based on
-the golden level (the dashed line in Figure \ref{fig2:fig4}) is slightly smaller
-and for $c>1$ barely different than for the two-trials rule. More substantial
-gains are still visible for $c < 1$. However, the restriction to original
-studies with $p_o \leq 0.025$ may not reflect current practice in large-scale
-replication projects. For example, 5 out of 143 replication studies considered
-in Section \ref{sec2:application} do have original $p$-values between 0.025 and
-0.062.
-
-\section{Application}\label{sec2:application}
-In this section, we illustrate the proposed methodology using data from four
-replication projects. All four projects reported effect estimates that were
-transformed to correlation coefficients ($r$). This scale allows for easy
-comparison of effect estimates from studies that investigate different phenomena
-and is bounded to the interval between minus one and one. Moreover, the Fisher
-$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$ can be applied to the
-correlation coefficients, resulting in the transformed estimates being
-asymptotically normal with variance which is only a function of the study sample
-size $n$, \ie $\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}.
-
-The first data set comprises the results from the \textit{Reproducibility
-  Project: Psychology} \citep{Opensc2015}, whose aim was to replicate 100
-studies, all of which were published in three major Psychology journals in 2008.
-For our purpose only the 73 study pairs from the ``meta-analytic'' subset are
-considered, since only for these studies the standard error of the Fisher
-$z$-transformed effect estimates can be computed \citep{Johnson2016}. The second
-data set comes from the \textit{Experimental Economics Replication Project}
-\citep{Camerer2016} which attempted to replicate 18 experimental economics
-studies published in two high impact economics journals between 2011 and 2015.
-The third data stem from the \textit{Social Sciences Replication Project}
-\citep{Camerer2018} where 21 replications of studies on the social sciences were
-carried out, all of which were originally published in the journals
-\textit{Nature} and \textit{Science} between 2010 and 2015. The last data set
-originates from the \textit{Experimental Philosophy Replicability Project}
-\citep{Cova2018} which involved 40 replications of studies from the emerging
-field of experimental philosophy. Since only for 31 studies effective sample
-size for original and replication study were available simultaneously, only
-these pairs were included. For more information on the data sets see also
-\citet{Pawel2020}.
-
-\begin{table}[!ht]
-    \centering
-\caption{Results for each replication project:
-Relative effect size $d$ (median with 25\% and 75\% quantiles on Fisher's $z$ scale), proportion of
-successful replications with the two-trials rule (2TR) and the replication success (RS)
-approach (at the golden level), and number of studies where the methods disagree.}
-% \resizebox{\textwidth}{!} {
-% latex table generated in R 4.0.5 by xtable 1.8-4 package
-% Fri Nov 25 12:12:30 2022
-\begin{tabular}{lcccc}
-  \toprule
-Project & relative effect size $d$ & 2TR (\%) & RS (\%) & discrepant \\
-  \midrule
-Psychology & 0.29 [0.03, 0.77] & 28.8 & 30.1 & 3/73 \\
-  Experimental Economics & 0.67 [0.35, 0.92] & 55.6 & 55.6 & 0/18 \\
-  Social Sciences & 0.52 [0.13, 0.65] & 61.9 & 52.4 & 2/21 \\
-  Experimental Philosophy & 0.86 [0.47, 1.12] & 74.2 & 71.0 & 1/31 \\
-   \bottomrule
-\end{tabular}
-
-% }
-\label{tab:marginalres}
+\caption*{\textbf{\textrm{Box 1}}: Summary of reverse-Bayes assessment of replication success with
+Bayes factors.}
+\label{box:nutshell}
 \end{table}
 
-Table~\ref{tab:marginalres} presents overall results for each of the replication
-projects. While the median relative effect size is below one for all of the four
-projects, there are still large differences. For example, the median relative
-effect size is only $0.29$ in the Psychology project, whereas it is $0.86$ in
-the Philosophy project. The degree of shrinkage is also reflected in the success
-rates (according to the two-trials rule and the replication success approach at
-the golden level), which are around 30\% for the former and more than 70\% for
-the latter. The proportion of successful replications is similar for the
-two-trials rule and the replication success approach. In the Experimental
-Economics project the methods perfectly agree, while in the other three projects
-the methods disagree for a few studies.
-
-\begin{figure}[!h]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig6-1}
-
-}
-
-\end{knitrout}
-\caption{Relative effect size $d$ versus original $p$-value $p_o$. Black
-  indicates that replication success was achieved at the golden level while grey
-  indicates that it was not. The diamonds mark studies where the replication
-  success approach (at the golden level) and the two-trials rule disagree. The
-  dashed black line indicates the limiting relative effect size at the golden
-  level with $\alpha = 0.025$. }
-\label{fig2:fig6}
-\end{figure}
-
-Figure~\ref{fig2:fig6} displays the relative effect size $d$ versus the original
-$p$-value $p_o$ for each study pair and stratified by project. Note that one
-study pair from the Philosophy project is not shown due to extremely small
-original $p$-value and another study pair from the Psychology project is not
-shown due to a very large relative effect size. We can see that for most of the
-study pairs, the replication success approach and the two-trials rule lead to
-the same conclusion, only six replications show conflicting results. They are
-highlighted with diamonds in Figure~\ref{fig2:fig6} and their characteristics are
-summarised in Table~\ref{tbl:discrep}.
-\begin{table}[!ht]
-    \centering
-  \caption{Characteristics of studies for which the replication success approach
-    (at the golden level) and the two-trials rule disagree (at one-sided
-    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
-    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
-    and $\tilde{p}_S$.}
-  \label{tbl:discrep}
-% \resizebox{\textwidth}{!} {
-% latex table generated in R 4.0.5 by xtable 1.8-4 package
-% Fri Nov 25 12:12:30 2022
-\begin{tabular}{lllllll}
-  \toprule
-Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
-  \midrule
-\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
-  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
-  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
-  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
-  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
-  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
-   \bottomrule
-\end{tabular}
-
-% }
-\end{table}
-Two studies from the Psychology project show replication success but fail the
-two-trials rule. These studies show $p$-values that are slightly above the
-significance threshold in either original or replication study, but do not
-exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
-replication $p$-value was $p_r = 0.035$, a little too large to pass the
-two-trials rule. However, as the replication effect estimate shrunk only about
-$30$\% compared to the original one, replication success is still achieved.
-Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
-above the significance level, yet the replication led to a highly significant
-result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
-original counterpart, which therefore also resulted in replication success.
-
-The remaining conflicting studies do not show replication success despite
-passing the two-trials rule. In all cases, there is substantial shrinkage of the
-replication effect estimate compared to the original one. For instance, in the
-replication study of \citet{Pyc2010}, the estimate shrunk by $62$\% and the
-replication $p$-value was only significant because the sample size was increased
-by a factor of $c = 9.2$.
-
-This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
-the golden level as described in Section \ref{sec2:goldenthresh}. We may also
-choose a different value for the limiting relative effect size $\dinfty$ at
-$\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
-$\alpha'$ as given in \eqref{eq2:alphaPrime}. Figure \ref{fig2:fig7} compares the
-proportion of successful replications with the replication success approach for
-$\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
-corresponding levels
-$\alpha' \in (0.06, 0.022)$ for
-all four replication projects. We can see that the two proportions agree fairly
-well for all values of $\alpha'$ considered. The number of discrepant studies in
-each project varies between 0 and 3. Only in the Psychology project there are
-some studies which are successful with the replication success approach but not
-the two-trials rule and some studies successful with the two-trials rule but not
-the replication success approach. The proportion of studies where both methods
-are successful (also shown in Figure \ref{fig2:fig7}) is then smaller than the
-proportion of successful replications with either one of the two methods. The
-three discrepant studies from the Psychology project listed in the top three
-rows of Table~\ref{tbl:discrep} are an example of this particular feature.
+\subsection{Data from the original study}
+For the effect estimate $\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$
+from the original study consider a hypothesis test comparing the null hypothesis
+$H_0\colon$ $\theta = 0$ to the alternative $\HS \colon$ $\theta \neq 0$.
+Specification of a prior distribution for $\theta$ under $\HS$ is now required
+for Bayesian hypothesis testing. A typical choice \citep{Jeffreys1961} is a
+local alternative, a unimodal symmetric prior distribution centred around the
+null value. We consider the sceptical prior
+$\theta \given \HS \sim \Nor(0, \sigma^2_s = g \cdot \sigma^2_o)$ with relative
+sceptical prior variance $g$ for this purpose (relative to the variance from the
+original estimate $g = \sigma^2_s/\sigma^2_o$), resembling the $g$-prior known
+from the regression literature \citep{Zellner1986, Liang2008}. The explicit form
+of the Bayes factor is then given by
+\begin{align}
+  \label{eq2:BFo}
+  \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)
+  = \sqrt{1 + g} \cdot
+  \exp\left\{-\frac{1}{2} \cdot \frac{g}{1 + g} \cdot z^2_o\right\}.
+\end{align}
+
+The Bayes factor from equation ~\eqref{eq2:BFo} is shown in Figure ~\ref{fig2:bfo}
+as a function of $g$ and for different original $z$-values $z_o$. For fixed
+$z_o$, it is well known that this Bayes factor is bounded from below by
+\begin{align}
+  \label{eq2:minBFo}
+  \minBF_{o} =
+  \begin{cases}
+    |z_o| \cdot  \exp(-z_o^2/2) \cdot \sqrt{e} & \text{for} ~ |z_o| > 1 \\
+    1 & \text{for} ~ |z_o| \leq 1
+  \end{cases}
+\end{align}
+which is reached at $\gminBFo = \max\{0, z^2_o - 1\}$ \citep{Edwards1963}.
+Further increasing the relative sceptical prior variance increases
+\eqref{eq2:BFo} indefinitely because of the Jeffreys-Lindley paradox, \ie{}
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \to \infty$ for $g \to \infty$
+\citep[][Section 6.1.4]{Bernardo2000}. Hence, for a relative sceptical prior
+variance $g \in [0, \gminBFo]$, the resulting Bayes factor will be
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g) \in [\minBF_o, 1]$.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{images/paper2/fig7-1}
-
+\includegraphics[width=\maxwidth]{images/paper2/plot-BFo-1.pdf}
+\end{knitrout}
+\caption{Bayes factor $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of
+relative sceptical prior variance $g$ for different values of
+$|z_o| = |\that_o|/\sigma_o$. Minimum Bayes factors $\minBF_{o}$ are indicated
+by dots. Dashed vertical lines indicate sufficiently sceptical relative prior
+variance $g_{\scriptscriptstyle \gamma}$ at level $\gamma = 1/10$, if they
+exist.}
+\label{fig2:bfo}
+\end{figure}
+
+We now apply the reverse-Bayes idea and challenge the original finding. To do
+so, we fix a level $\gamma$ above which the original finding is no longer
+convincing to us. For example, this could be $\gamma = 1/10$; the threshold for
+strong evidence against $H_0$ according to the classification from
+\citet{Jeffreys1961}. Suppose now there exists a $\gy \leq \gminBFo$ such that
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma$. It can be shown (Appendix
+\ref{appendix:ssrv}) that $\gy$ can be explicitly computed by
+\begin{align}
+\label{ggamma}
+  \gy &=
+  \begin{cases}
+    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
+    \text{undefined} & ~~ \text{else}
+  \end{cases} \\
+  \text{where} ~ q &= \lw{-1} \left(-\frac{z_o^2}{\gamma^2} \cdot
+  \exp\left\{-z_o^2\right\}\right)
+  \nonumber
+\end{align}
+with $\lw{-1}(\cdot)$ the branch of the Lambert $W$ function \citep{Corless1996}
+that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, see Appendix
+\ref{appendix:lambertW} for details about the Lambert $W$ function. The
+sufficiently sceptical prior is then given by
+$\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ and it can be interpreted
+as the view of a sceptic who argues that given their prior belief about the
+effect $\theta$, the observed effect estimate $\hat{\theta}_o$ cannot convince
+them about the presence of a non-null effect at level $\gamma$. An alternative
+data-based interpretation of sufficiently sceptical priors is to see them as the
+priors obtained by updating an initial uniform prior with the data from an
+imaginary study, which was $1/\gy$ times the size of the original study, and
+which resulted in an effect estimate of exactly zero \citep{Held2021b}.
+
+From Figure \ref{fig2:bfo} we can see that the more compelling the original data
+(\ie{} the larger $|z_o|$), the smaller the sufficiently sceptical relative prior
+variance $\gy$ needs to be in order to make the result no longer convincing at
+level $\gamma$. In the most extreme case, when $|z_{o}| \to \infty$ and $\gamma$
+remains fixed, the sufficiently sceptical prior variance will converge to
+zero (Appendix \ref{appendix:lambertW}). On the other hand, if $|z_o|$ is not
+sufficiently large, $\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ will either be
+always increasing in $g$ (if $|z_o| \leq 1$) or it will reach a minimum above
+the chosen level $\gamma$. In both cases the sufficiently sceptical relative
+prior variance $\gy$ is not defined since there is no need to challenge an
+already unconvincing result.
+
+A side note on the Jeffreys-Lindley paradox is worth being mentioned: If a
+$\gy < \gminBFo$ exists, there exists also a $\gy^\prime > \gminBFo$ as the
+Bayes factor monotonically increases in $g > \gminBFo$ and therefore must
+intersect a second time with $\gamma$, due to the paradox. This means that the
+more compelling the original result, the larger $\gy^\prime$ needs to be chosen,
+such that the result becomes no longer convincing at level $\gamma$. However,
+priors which become increasingly diffuse do not represent increasing scepticism
+but rather increasing ignorance. Using \eqref{ggamma} therefore avoids this
+manifestation of the Jeffreys-Lindley paradox, since it determines sceptical
+priors only from the class of priors that become increasingly concentrated for
+increasing evidence (\ie{} priors with $\gy \leq \gminBFo$). In principle, the
+solution $\gy^\prime > \gminBFo $ could also be computed by replacing the
+$\lw{-1}$ branch of the Lambert $W$ function in \eqref{ggamma} with the $\lw{0}$
+branch, but this will not be of interest to us.
+
+\subsection{Data from the replication study}
+\label{sec2:bfr}
+In order to assess whether the original finding can be replicated in an
+independent study, a replication study is conducted, leading to a new effect
+estimate $\hat{\theta}_r$. In light of the new data, the sceptic is now
+challenged by an advocate of the original finding. This is formalised with
+another Bayes factor, which compares the plausibility of the replication effect
+estimate $\hat{\theta}_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
+sceptical prior $\HS \colon$ $\theta \sim \Nor(0, g \cdot \sigma^2_o)$ relative
+to the advocacy prior $\HA \colon$ $\theta \sim \Nor(\that_o, \sigma^2_o)$. The
+the view of an advocate is represented by $\HA$ since this is the posterior of
+$\theta$ given the original estimate and a uniform prior (also the reference
+prior for this model). The Bayes factor is given by
+\begin{align}
+  \label{eq2:BFr}
+  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
+%%   &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
+%%   \exp\left\{-\frac{1}{2}\left(\frac{z_r^2}{1/c + g} -
+%%   \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}
+  &= \sqrt{\frac{1/c + 1}{1/c + g}} \cdot
+  \exp\left\{-\frac{z_o^2}{2}\left(\frac{d^2}{1/c + g} -
+  \frac{\left(d - 1\right)^2}{1/c + 1} \right)\right\}
+\end{align}
+so it depends on the original $z$-statistic $z_o$, the relative sceptical prior
+variance $g$, the relative effect estimate $d = \that_r/\that_o$, and the
+relative variance $c = \sigma^2_o/\sigma^2_r$.
+
+Our goal is now to define a condition for \emph{replication success} in terms of
+\eqref{eq2:BFr}. It is natural to consider a replication successful if the
+replication data favour the advocate over the sceptic to a higher degree than
+the sceptic's initial objection to the original study. More formally, we say
+that if the Bayes factor from \eqref{eq2:BFr} evaluated at the sufficiently
+sceptical relative prior variance $\gy$ is not larger than the corresponding
+level $\gamma$ used to define the sufficiently sceptical prior:
+\begin{align}
+  \label{eq2:success}
+  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
+  \leq \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) =\gamma,
+\end{align}
+we have established \emph{replication success at level $\gamma$}.
+
+For example, if we observe $z_o = 3$ (equivalent to minimum Bayes factor
+$\minBF_{o} = 1/18$) and choose a level $\gamma = 1/10$
+the sufficiently sceptical relative prior variance \eqref{ggamma} is
+$\gy = 1.6$. If a replication is conducted with the
+same precision ($c = 1$) and we observe $z_r = 2.5$ (equivalent to
+minimum Bayes factor $\minBF_{r} = 1/5.5$ and relative effect
+estimate $d = z_{r}/(z_{o}\sqrt{c}) = 0.83$), using equation
+\eqref{eq2:BFr} this would lead to $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r;
+1.6) = 1/3.5$, which means
+that the replication was not successful at level $\gamma = 1/10$.
+However, if we had chosen a less stringent level, \eg{}$\gamma =
+1/3$, the replication would have been considered successful
+since then $\gy = 0.4$ and
+$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; 0.4)
+= 1/7.4$.
+
+\subsection{The sceptical Bayes factor}
+Apart from specifying a level $\gamma$, the described procedure offers an
+automated way to assess replication success. One way to remove this dependence
+is to find the smallest level $\gamma$ where replication success can be
+established. We thus call this level the \emph{the sceptical Bayes factor}
+\begin{align}
+  \label{eq2:bfs}
+  \BFs
+  =
+  %% \inf_{\gy \in [0, \gminBFo]}
+  \inf
+  \Big\{\gamma :
+  \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)
+  \leq \gamma\Big\},
+\end{align}
+and replication success at level $\gamma$ is equivalent with $\BFs \leq \gamma$.
+
+Figure \ref{fig2:bfs} shows $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ as a function of $\gy$ for several
+values of $z_o$ and $d$ along with the corresponding $\BFs$. Typically, $\BFs$
+is given by the height of the intersection between
+$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ and
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ in $\gy$. It may also happen that
+$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; \gy)$ remains below
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy)$ for all values of $\gy$, in such
+situations $\BFs$ is equal to the original minimum Bayes factor $\minBF_o$.
+Finally, in some pathological cases it may happen that either $z_o$, $d$, or
+both are so small that replication success cannot be established for any level
+$\gamma$ and hence $\BFs$ does not exist. This means that the replication study
+was unsuccessful since it is impossible for the advocate to convince the sceptic
+at any level of evidence.
+
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper2/plot-BFs-1}
+\end{knitrout}
+\caption{Bayes factors $\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ as a function of the sufficiently
+sceptical relative prior variance $\gy$. In all examples
+$c = \sigma^2_o/\sigma^2_r = 1$. Minimum Bayes factors $\minBF_o$ are indicated
+by dots, sceptical Bayes factors $\BFs$ are indicated by crosses where existent.}
+\label{fig2:bfs}
+\end{figure}
+
+In terms of computing the sceptical Bayes factor, it is worth noting that for
+the special case when the replication is conducted with the same precision as
+the original study ($c = 1$) and $\BFs$ is located at the intersection of
+$\BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)$ and
+$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g)$ in $g$, there is an explicit expression
+for $\BFs$
+\begin{align}
+  \label{eq2:BFsc1}
+  \BFs =
+  \sqrt{-\frac{z^2_{o}}{k} \cdot \frac{1 + d^{2}}{2}} \cdot
+  \exp\left\{-\left(\frac{z_o^2}{2} + \frac{k}{1 + d^2}\right)\right\}
+\end{align}
+with
+$$k = \lw{}\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{d^{2} + 1}{2} \cdot \exp\left\{-\frac{z_o^2}{2}
+  \left[1 + \frac{(1 -
+d)^2}{2}\right]\right\}\right),$$ see Appendix \ref{appendix:bfs} for details.
+
+\section{Properties}
+\label{sec2:comparison}
+To study properties of the sceptical Bayes factor and facilitate comparison with
+other methods we will look at the requirements for replication success based on
+the relative effect estimate $d = \that_{r}/\that_{o}$, the variance ratio
+$c = \sigma^{2}_{o}/\sigma^{2}_{r}$ and the original minimum Bayes factor
+$\minBF_{o}$ (respectively the original $z$-value $z_{o}$). This perspective is
+helpful because it disentangles how the method reacts to changes in
+compatibility of the effect estimates ($d$), evidence from the original study
+($\minBF_{o}$), and the change in sample size of the replication compared to the
+original study ($c$).
+
+The condition for replication success at level $\gamma$ from \eqref{eq2:success}
+is equivalent to
+\begin{align}
+  \label{eq2:RSCond-d}
+  \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
+  \frac{z_o^2}{1 + 1/\gy} &\leq z_o^2 \left(\frac{d^2}{1/c +
+    \gy} - \frac{\left(d - 1\right)^2}{1/c + 1} \right).
+\end{align}
+On the right-hand side of~\eqref{eq2:RSCond-d} the $Q$-statistic
+\begin{align}
+  \label{eq2:Qstat}
+  Q
+  = \frac{(\hat{\theta}_o - \hat{\theta}_r)^2}{\sigma^2_o + \sigma^2_r}
+  %% = \frac{(z_r - z_o\sqrt{c})^2}{1 + c}
+  = \frac{z_o^2(d - 1)^2}{1/c + 1}
+\end{align}
+appears. The $Q$-statistic was proposed as a measure of incompatibility among
+original and replication effect estimates since its distribution is known for
+standard meta-analytic models of effect sizes \citep{Hedges2019}. The connection
+to the sceptical Bayes factor is such that $Q$ acts as a penalty term
+in~\eqref{eq2:RSCond-d} and a larger value will lower the degree of replication
+success possible. However, as we will see, the sceptical Bayes factor goes
+beyond assessing effect estimate compatibility as there is also a trade-off with
+the amount of evidence that the replication study provides against the null.
+
+Applying some algebraic manipulations to \eqref{eq2:RSCond-d}, one can show that
+replication success at level $\gamma$ is achieved if and only if the relative
+effect estimate $d$ falls within a success region given by
+\begin{align}
+  \label{eq2:dsuccess}
+  \begin{cases}
+    d \not\in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy < 1 \\
+    d \geq [1 + (1 + 1/c)\{1/2 - \log(2)/z_o^2\}]/2
+    & \text{if} ~ \gy = 1 \\
+   d \in [M - \sqrt{A/B}, M + \sqrt{A/B}] & \text{if} ~ \gy > 1\\
+  \end{cases}
+\end{align}
+where
+\begin{align*}
+  M &= \frac{1/c + \gy}{\gy - 1} \\
+  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\}\Bigm/ z_o^2 +
+  \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \\
+  B &= \frac{1 - \gy}{(1/c + \gy)(1/c + 1)}.
+\end{align*}
+
+The top-left plot in Figure~\ref{fig2:dcomparison} shows the conditions on $d$
+from~\eqref{eq2:dsuccess} to achieve replication success at level $\gamma = 1/3$
+as a function of the original minimum Bayes factor $\minBF_{o}$ and for
+different values of the relative variance $c$. It is important to note that
+$\gamma = 1/3$ is an arbitrary choice and in practice one should interpret the
+sceptical Bayes factor as a quantitative measure of replication success. Only
+the success regions for positive $d$ are shown as replication success in the
+opposite direction is usually not of interest (see
+Section~\ref{sec2:replicationParadox} for a discussion of this issue). We see
+that with increased precision of the replication study (larger $c$), the success
+regions shift closer to zero. This means that the method allows for more
+shrinkage of the replication effect estimate when the replication provides more
+evidence against the null (because $\abs{z_{r}} = d \abs{z_{o}} \sqrt{c}$
+increases with increasing $c$). However, the success regions cannot be pushed
+arbitrarily close to zero but are bounded away. So when $c \to \infty$ the
+methods still requires the replication estimate to be sufficiently large,
+despite that the evidence against the null becomes overwhelming (since
+$\abs{z_{r}} \to \infty$ as $c \to \infty$).
+
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper2/plot-success-region-comparison-1}
+\end{knitrout}
+\caption{Required relative effect estimate $d = \that_{r}/\that_{o}$ to achieve
+  replication success based on the sceptical Bayes factor
+  ($\BFs \leq 1/3$), the two-trials rule (2TR:
+  $\minBF_{o} \leq 1/3$ and $\minBF_{r} \leq 1/3$),
+  the replication Bayes factor ($\BFr \leq 1/3$), and the
+  recalibrated sceptical $p$-value
+  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$ with
+  $\gamma = 1/3$) as a function of the original minimum
+  Bayes factor $\minBF_{o}$ (respectively the corresponding $z$-value $z_{o}$)
+  for different values of the relative variance
+  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. Shading indicates regions where
+  replication success is possible. Only positive relative effect estimates $d$
+  are shown.}
+\label{fig2:dcomparison}
+\end{figure}
+
+By definition the sceptical Bayes factor can never be smaller than $\minBF_{o}$,
+so replication success at level $\gamma$ is impossible for original studies with
+$\minBF_{o} > \gamma$. This property is visible in the top-left plot in
+Figure~\ref{fig2:dcomparison} by the cut-off at $\minBF_{o} = \gamma = 1/3$. In
+contrast, for more convincing original studies with $\minBF_{o} < 1/3$
+replication success is possible and two cases can be distinguished in terms of
+the success region: When $1/4.5 < \minBF_{o} \leq 1/3$ the
+sufficiently sceptical relative prior variance is $\gy > 1$ and thus by
+condition~\eqref{eq2:dsuccess} the success region consists of an interval
+$(\dmin, \dmax)$. Hence, in this case the method also penalises too large
+replication effect estimates. For original studies with
+$\minBF_{o} < 1/4.5$, the sufficiently sceptical relative prior
+variance is $\gy \leq 1$, so due to~\eqref{eq2:dsuccess} the success region for
+positive $d$ is given by $(\dmin, \dmax = \infty)$. This means that for more
+convincing original studies there are no upper restrictions for the relative
+effect estimate, whereas shrinkage of the replication estimate is still
+penalised.
+
+\subsection{Comparison with other methods}
+Of interest is the relationship between the sceptical Bayes factor and other
+measures of replication success. Here, we review and compare a classical (the
+two-trials rule), a forward-Bayes \citep[the replication Bayes factor
+from][]{Verhagen2014} and a reverse-Bayes method \citep[the sceptical $p$-value
+from][]{Held2020}. These methods provide a useful benchmark as they all are
+based on hypothesis testing, have unique properties, and can be directly
+compared in terms of their replication success regions as shown in
+Figure~\ref{fig2:dcomparison}.
+
+\subsubsection{The two-trials rule}
+Replication success is most commonly declared when both original and replication
+study provide compelling evidence against a null effect. This approach is also
+known as the \emph{two-trials rule} in drug development and usually a
+requirement for drug approval \citep[Section 9.4]{Kay2015}. Most replication
+projects report $p$-values associated with the effect estimates as measures of
+evidence against the null, but also default Bayes factors have been used
+\citep[see \eg{} the Bayesian supplement of][]{Camerer2018}. To compare the
+two-trials rule with methods based on Bayes factors we will study the two-trials
+rule based on the minimum Bayes factor from~\eqref{eq2:minBFo}, \ie{} replication
+success at level $\gamma$ is established when both
+$\minBF_{k} % = \abs{z_{k}}\exp(-z_{k}^{2}/2)\sqrt{e}
+\leq \gamma$ for $k \in \{o, r\}$, as well as
+$\sign(\hat{\theta}_o) = \sign(\hat{\theta}_r)$. This approach has a one-to-one
+correspondence to the usual version of two-trials rule as minimum Bayes factors
+and $p$-values both only depend on the $z$-values of original and replication
+study.
+
+The two-trials rule guarantees that both studies provide compelling evidence
+against the null. Similarly, the sceptical Bayes factor requires the original
+study to be compelling on its own since it can never be smaller than
+$\minBF_{o}$. However, one can easily construct examples where the sceptical
+Bayes factor is smaller than the minimum Bayes factor from the replication study
+(\eg{} when $\minBF_{o} = 1/2$,
+$\minBF_{r} = 1/1.5$, and $c = 1$
+we obtain $\BFs = 1/1.9$). So for the same level of
+replication success $\gamma$ the two-trials may not flag replication success
+whereas the sceptical Bayes factor would.
+
+By definition the two-trials rule can never be fulfilled when the original study
+was uncompelling. Assuming now that $\minBF_{o} < \gamma$, replication success
+with the two-trials rule at level $\gamma$ is achieved if and only if the
+relative effect estimate is
+\begin{align}
+  \label{eq2:2TR}
+  d \geq \frac{z_{\gamma}}{z_{o} \sqrt{c}}
+\end{align}
+with $z_{\gamma} > 1$ corresponding to
+$\minBF = z_{\gamma}\exp(-z_{\gamma}^{2}/2)\sqrt{e} = \gamma$. The success
+region from~\eqref{eq2:2TR} is displayed in the top-right plot of
+Figure~\ref{fig2:dcomparison}. We see that the success regions shift closer to
+zero as the relative variance $c$ increases. Also there is a cut-off at
+$\minBF_{o} = \gamma = 1/3$ similarly as with the sceptical Bayes factor. In
+contrast to the sceptical Bayes factor, however, the two-trials can be fulfilled
+for any arbitrary small (but positive) relative effect estimate $d$, provided
+the relative variance $c$ is large enough. Hence, the two-trials rule may flag
+success even when the replication effect estimate is much smaller than the
+original one.
+
+\subsubsection{The replication Bayes factor}
+\citet{Verhagen2014} proposed the \emph{replication Bayes factor} as a measure
+of replication success. It is defined as the Bayes factor comparing the point
+null hypothesis $H_0 \colon \theta = 0$, to the alternative that the effect is
+distributed according to the posterior distribution of $\theta$ after observing
+the original data. For the normal model considered so far and if an initial
+reference prior was chosen, this alternative is also the advocacy prior
+$\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$ and therefore the replication
+Bayes factor is given by
+\begin{align}
+  \label{eq2:BFrep}
+  \BFr
+  = \BFcol{\mathrm{0}}{\mathrm{A}}(\hat{\theta}_r)
+  %% = \sqrt{1 + c} \cdot
+  %% \exp\left\{-\frac{1}{2} \left(z_r^2 -
+  %% \frac{\left(z_r - z_o \sqrt{c}\right)^2}{1 + c} \right)\right\}.
+  = \sqrt{1 + c} \cdot
+  \exp\left\{-\frac{z_o^2}{2} \left(d^2 \cdot c -
+  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}.
+\end{align}
+
+Similarly, as with the sceptical Bayes factor, the $Q$-statistic
+from~\eqref{eq2:Qstat} appears in~\eqref{eq2:BFrep} and acts as a penalty term,
+\ie{} larger values of $Q$ lower the degree of replication success. However, in
+contrast to the sceptical Bayes factor, the replication Bayes factor is not
+limited by the evidence from the original study because $\BFr \downarrow 0$ as
+$c \to \infty$ provided $z_{o} \neq 0$ and $d \neq 0$. Moreover, we have that
+\begin{align*}
+  1 \geq \BFs \geq \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs})
+  = \BFcol{\mathrm{S}}{0}(\hat{\theta}_r; g_{\scriptscriptstyle \BFs}) \cdot \underbrace{\BFcol{0}{\mathrm{A}}(\hat{\theta}_r)}_{= \BFr}.
+\end{align*}
+So the sceptical Bayes factor is larger than the replication Bayes factor if the
+replication data favour the sceptical prior
+$\HS \colon \theta \sim \Nor(0, g_{\scriptscriptstyle \BFs} \cdot \sigma^{2}_{o})$
+over the null hypothesis. They can only coincide when $\BFs = 1$ since then
+$g_{\scriptscriptstyle \BFs} = 0$.
+
+We can also determine conditions on the relative effect estimate in terms of
+replication success based on $\BFr \leq \gamma$. The replication success region
+is given by
+\begin{align}
+  \label{eq2:BFRsuccess}
+  d \not\in [-\sqrt{J} - H, \sqrt{J} - H]
+\end{align}
+with
+\begin{align*}
+  J &= \left\{1 + \frac{\log(1 + c) - 2 \log \gamma}{z_o^2}\right\} \cdot
+  \frac{1/c + 1}{c} \\
+  H &= \frac{1/c + 1}{1 + c}.
+\end{align*}
+The condition \eqref{eq2:BFRsuccess} implies that replication success can also be
+achieved for negative relative effect estimates $d$ (see
+Section~\ref{sec2:replicationParadox} for a discussion of this issue). The
+bottom-left plot in Figure~\ref{fig2:dcomparison} shows the conditions
+from~\eqref{eq2:BFRsuccess} for positive relative effect estimates. As with the
+two-trials rule, the success region of the replication Bayes factor can be
+pushed arbitrarily close to zero by increasing the relative variance $c$. In
+contrast to the two-trials rule, however, replication success can also be
+achieved for original studies with $\minBF_{o} > 1/3$.
+
+\subsubsection{The sceptical \textit{p}-value}
+Of particular interest is the relationship between the sceptical Bayes factor
+and the sceptical $p$-value \citep{Held2020}, as it is the outcome of a similar
+reverse-Bayes procedure. One also considers a sceptical prior for the effect
+size $\theta \sim \Nor(0, \tau^2)$, the sufficiently sceptical prior variance at
+level $\alpha$ is then defined as $\tau^2 = \tau^2_\alpha$ such that the
+$(1 - \alpha)$ credible interval for $\theta$ based on the posterior
+$\theta \given \that_o, \tau^2_\alpha$ does not include zero. Replication
+success is declared if the tail probability of the replication effect estimate
+under its prior predictive distribution
+$\that_r \given \tau^2_\alpha \sim \Nor(0, \tau^2_\alpha + \sigma^2_r)$ is
+smaller than $\alpha$. The smallest level $\alpha$ where replication success can
+be established defines the sceptical $p$-value. In contrast to the sceptical
+Bayes factor, the sceptical $p$-value always exists and there are closed form
+expressions to compute it for all values of $c$, \ie{}
+$\ps = 1 - \Phi(z_{\mathrm{S}})$ with
+\begin{equation*}
+  z^2_{\mathrm{S}} =
+  \begin{cases}
+    z^2_H/2 & \text{for}~c=1 \\ \frac{1}{c - 1}\left\{\sqrt{z^2_A\left[z^2_A +
+          (c - 1)z^2_H\right]} - z^2_A\right\} & \text{for}~c \neq 1
+  \end{cases}
+  \label{eq2:z2s}
+\end{equation*}
+where $z^2_H = 2/(1/z_o^2 + 1/z_r^2)$ the harmonic mean,
+$z^2_A = (z_o^2 + z_r^2)/2$ the arithmetic mean of the squared $z$-statistics,
+and provided that $\sign(\that_o) = \sign(\that_r)$ (otherwise
+$\ps = \Phi(z_{\mathrm{S}})$).
+
+Similar to the two-trials rule, the sceptical $p$-value requires both studies to
+provide compelling evidence due to the property that
+$\ps \geq \max\{p_o, p_r\}$. The sceptical $p$-value also penalises the case
+when the replication effect estimate shrinks as compared to the original one
+since it monotonically increases with decreasing relative effect estimate $d$
+\citep[Section 3.1]{Held2020}.
+
+\citet{Held2021} showed that replication success based on
+$\ps \leq \alpha_{\mathrm{S}}$ is achieved when
+\begin{align}
+  \label{eq2:psSuccessd}
+  d \geq \sqrt{\frac{1/c + 1/(K - 1)}{K}}
+\end{align}
+with $K = z_{o}^{2}/z_{\alpha_{\mathrm{S}}}^{2}$ where
+$z_{\alpha_{\mathrm{S}}} = \Phi^{-1}(1 - \alpha_{\mathrm{S}})$. Thresholding the
+sceptical $p$-value with the ordinary significance level $\alpha$ for
+traditional $p$-values leads to a very stringent criterion for replication
+success. For example, when $z_{o} = 2$, $\alpha = 0.025$, and
+$c = 2$, the replication effect estimate needs to be
+$d = 4.87$ times larger than the original one. Therefore,
+\citet{Held2021} used~\eqref{eq2:psSuccessd} to determine the \emph{golden level}
+$\alpha_{\mathrm{S}} = 1 - \Phi(z_\alpha/\sqrt{\varphi})$ with
+$\varphi = (1 + \sqrt{5})/2$ the golden ratio. The golden level ensures that
+borderline significant original studies ($\abs{z_{o}} = z_{\alpha}$) can still
+achieve replication success provided the replication effect estimate does not
+shrink compared to the original one ($d \geq 1$). Instead of comparing the
+sceptical $p$-value to the golden level ($\ps < \alpha_{\mathrm{S}}$), one can
+compute a recalibrated sceptical $p$-value
+$\tilde{p}_{\mathrm{S}} = 1 - \Phi(z_{\mathrm{S}} \sqrt{\varphi})$ and compare it to
+the ordinary significance level ($\tilde{p}_{\mathrm{S}} < \alpha$).
+
+The bottom-right plot in Figure~\ref{fig2:dcomparison} shows the success region
+for the recalibrated sceptical $p$-value. We see that increasing the precision
+of the replication study lowers the required minimum relative effect estimate
+$\dmin$ as for all other methods. Similarly, as with the sceptical Bayes factor,
+$\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily close to zero.
+However, its limiting minimum relative effect estimate in $c$
+($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
+factor when $\minBF_{o} < 1/5.6$, while for
+$\minBF_{o} > 1/5.6$ it is the other way around. So for more
+convincing original studies the sceptical $p$-value is less stringent than the
+sceptical Bayes factor. Due to the recalibration, the sceptical $p$-value also
+allows replication success when the $\minBF_{o} > \gamma$. This is visible in
+the bottom-right plot of Figure~\ref{fig2:dcomparison} where the success region
+has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
+the sceptical Bayes factor.
+
+\subsection{Paradoxes in the assessment of replication success}
+The replication setting is different from the classical setting where data from
+only one study are analysed. As a result, several unique paradoxes may occur.
+
+\subsubsection{The replication paradox}
+\label{sec2:replicationParadox}
+The \emph{replication-paradox} \citep{Ly2018} occurs when original and
+replication effect estimates go in opposite directions
+($\sign(\that_{o}) \neq \sign(\that_{r})$) but a method flags replication
+success. This is undesired since effect direction is crucial to most
+scientific theories and research questions.
+
+The two-trials rule and the sceptical $p$-value both avoid the replication
+paradox by using one-sided test-statistics. In contrast, the sceptical Bayes
+factor and the replication Bayes factor may suffer from the paradox as their
+success regions from~\eqref{eq2:dsuccess} and~\eqref{eq2:BFRsuccess},
+respectively, include negative relative effect estimates $d < 0$. This is
+related to the fact that Bayes factors are quantifying relative evidence: When
+the replication estimate goes in the opposite direction, it will be poorly
+predicted by the sceptical prior $\HS$ and the advocacy prior $\HA$, yet when
+$\HS$ is mostly concentrated around zero (or a point-null in case of the
+replication Bayes factor), replication estimates going in the opposite direction
+may still be better predicted by $\HA$.
+
+In practice, the replication paradox is hardly an issue, since replications
+rarely show such contradictory results, \eg{} to achieve replication success at
+level $\gamma = 1/3$ with
+$\minBF_{o} = 1/10$ and $c = 1$, the
+relative effect estimate needs to be $d < -7.09$ for the
+paradox to appear with the sceptical Bayes factor. The replication Bayes factor
+is more prone to the paradox because its point-null hypothesis fails more
+strongly to predict estimates in opposite direction, \eg{} for the same numbers as
+before it requires $d < -2.66$.
+
+In both cases the paradox can be overcome by truncating the advocacy prior $\HA$
+such that only effects in the same direction as the original estimate $\that_o$
+have non-zero probability, \ie{} for positive $\that_{o}$ consider
+$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \, \mathbb{1}_{(0, \infty)}(\theta)$,
+where $\mathbb{1}_{B}(x)$ is the indicator function of the set $B$. The Bayes
+factor contrasting $\HS$ to $\HAp$ turns out to be
+\begin{align}
+  \BFcol{\mathrm{S}}{\mathrm{A}^\prime}(\hat{\theta}_r; g)
+  &= \BFcol{\mathrm{S}}{\mathrm{A}}(\hat{\theta}_r; g)
+  \frac{\Phi(\abs{z_o})}{\Phi\left\{\mathrm{sign}(z_o)
+    %     \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}} \right\}}
+    \frac{z_o(1 + dc)}{\sqrt{1 + c}} \right\}}
+   \label{eq2:BFrtrunc}
+\end{align}
+where $\Phi(\cdot)$ is the cumulative distribution function of the standard
+normal distribution (see Appendix \ref{app:BFtrunc}). Hence, \eqref{eq2:BFrtrunc}
+is the Bayes factor under the standard advocacy prior multiplied by a correction
+term. Determining the smallest level of replication success
+with~\eqref{eq2:BFrtrunc} leads to a corrected sceptical Bayes factor, while
+setting $g = 0$ in~\eqref{eq2:BFrtrunc} leads to a corrected replication Bayes
+factor. The correction term goes to one when the replication estimate goes in
+the same direction as the original one and the replication sample size increases
+($d > 0$ and $c \to \infty$), but it penalises when the replication estimate
+goes in the opposite direction ($d < 0$ and $c \to \infty$).
+
+This modification guarantees that the replication paradox is avoided and we
+recommend to compute the sceptical Bayes factor using~\eqref{eq2:BFrtrunc} in
+cases where the replication paradox is likely to appear. However, truncated
+priors are unnatural and hard to interpret. Also the non-truncated advocacy
+prior penalises effect estimate incompatibility and the
+modification~\eqref{eq2:BFrtrunc} will only make a difference in extreme
+situations. Due to its easier mathematical treatment we will focus on the
+standard version of the procedure in the remaining part of the paper.
+
+\subsubsection{The shrinkage paradox}
+The comparison showed that for certain methods replication success is still
+achievable even when the replication estimate is substantially smaller than the
+original one. However, a substantially smaller effect estimate in the
+replication does not reflect an effect size of the same practical importance as
+the original one and a method should thus not flag replication success. The {\em
+shrinkage paradox} occurs if a particular method may flag replication success
+for any arbitrarily small (but positive) relative effect estimate.
+
+Two forms of the shrinkage paradox can formally be distinguished: the
+\emph{shrinkage paradox at replication} appears when, for fixed evidence from
+the original study $\minBF_{o}$ (respectively $z_{o}$), the minimum relative
+effect estimate $\dmin > 0$ required for replication success at a fixed level
+$\gamma$ becomes arbitrarily small as the relative variance $c$ increases:
+\begin{align*}
+  \dmin \downarrow 0 ~\text{as}~ c \to \infty.
+\end{align*}
+\citet{Held2021} found that this form of the paradox occurs for the two-trials
+rule but not for the sceptical $p$-value. Similarly, the minimum relative effect
+estimate $\dmin$ of the sceptical Bayes factor is bounded away from zero, while
+it converges to zero for the replication Bayes factor
+(Appendix~\ref{app:shrinkage}). Hence, among the Bayes factor methods, the
+sceptical Bayes factor avoids the paradox, whereas the replication Bayes factor
+suffers from it.
+
+The shrinkage paradox at replication is a serious issue since it depends on the
+relative variance $c$ which can usually be directly influenced by changing the
+replication sample size. However, there is also a second form of the paradox
+which is affected only by evidence from the original study. The \emph{shrinkage
+paradox at original} appears when, for fixed relative variance $c$, the minimum
+relative effect estimate $\dmin > 0$ required for replication success at a fixed
+level $\gamma$ becomes arbitrarily small as the evidence in the original study
+increases:
+\begin{align*}
+  \dmin \downarrow 0 ~\text{as}~ z_{o}^{2} \to \infty.
+\end{align*}
+
+The replication Bayes factor and the sceptical Bayes factor do not suffer from
+this form of the paradox, while the two-trials rule and the sceptical $p$-value
+do (Appendix~\ref{app:shrinkage}). Hence, with the latter two methods, shrinkage
+of the replication effect estimate is hardly penalised when the original study
+was already very convincing.
+
+\subsection{Frequentist properties}
+Despite the fact that Bayesian methods do not rely on repeated testing, it is
+still often of interest to study their frequentist operating characteristics
+\citep{Dawid1982, Grieve2016}. This is especially important in the replication
+setting where regulators and funders usually require from statistical methods to
+have appropriate error control. We will therefore study and compare type I error
+rate as well as power of the sceptical Bayes factor and other methods.
+
+\subsubsection{Global type I error rate}
+The probability for replication success at level $\gamma$ conditional on the
+original result $z_{o}$ and the relative variance $c$ can be easily computed as
+shown in Appendix~\ref{app:powerBFs}. Under the null hypothesis
+($H_{0}: \theta = 0$) the distribution of the $z$-values is
+$z_{o}, z_{r} \given H_{0} \sim \Nor(0, 1)$ and hence the global type I error
+rate (T1E) based on $\BFs \leq \gamma$ is
+\begin{align*}
+  \text{T1E} = 2 \int_{z_{\gamma}}^{\infty} \P(\BFs \leq \gamma \given z_{o}, c) \phi(z_{o}) \,
+  \text{d}z_{o}
+\end{align*}
+with $\phi(\cdot)$ the standard normal density function. In a similar fashion
+one can compute the type I error rate of the sceptical $p$-value \citep[see
+Section 3 in][]{Held2021}, as well as the replication Bayes factor
+(Appendix~\ref{app:powerBFr}). The type I error rate of the two trials rule is
+simply $\text{T1E} = 2\{1 - \Phi(z_{\gamma})\}^{2}$.
+
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper2/T1E-comparison-1}
+\end{knitrout}
+\caption{Type I error rate of the two-trials rule (2TR: $\minBF_{o} \leq \gamma$
+  and $\minBF_{r} \leq \gamma$), the replication Bayes factor
+  ($\BFr \leq \gamma$), the sceptical Bayes factor ($\BFs \leq \gamma$), and the
+  recalibrated sceptical $p$-value
+  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$) as a function of the
+  relative variance $c = \sigma^{2}_{o}/\sigma^{2}_{r}$ for different levels of
+  replication success $\gamma$.}
+\label{fig2:t1ec}
+\end{figure}
+
+Figure~\ref{fig2:t1ec} compares the type I error rates of the four methods for
+different levels $\gamma$. The conventional nominal
+$\text{T1E} = 0.05 \times 0.025$ (two independent experiments with two-sided
+testing in the first and one-sided testing in the second) along with the
+corresponding level ($z_{\gamma} = 1.96$ corresponding to $\gamma = 1/2.1$ and
+$\alpha = 0.025$) is also indicated. In contrast to the other methods, the type
+I error rate of the two trials rule does not depend on the relative variance $c$
+and therefore does not change for the same level $\gamma$. Type I error rates of
+sceptical $p$-value and sceptical Bayes factor are decreasing with increasing
+$c$, the former usually being slightly smaller than the latter. The point at
+which both become smaller than the type I error rate from the two-trials rule
+becomes smaller with more stringent level $\gamma$. Roughly speaking the type I
+error rate of the sceptical Bayes factor is controlled at the conventional level
+when $c$ is slightly larger than one, while for the sceptical $p$-value it is
+controlled when $c$ is slightly below one. Surprisingly, the type I error rate
+of the replication Bayes factor is non-monotone in $c$ and far higher compared
+to the other methods. This suggests that a more stringent level $\gamma$ should
+be used for the replication Bayes factor compared to the other methods to ensure
+appropriate type I error control.
+
+\subsubsection{Power conditional on the original study}
+Another frequentist operating characteristic is the probability to establish
+replication success assuming there is an underlying effect (power). While in
+principle original and replication study could be powered simultaneously, we
+will assume the original study has already been conducted since this is the
+usual situation. The power to establish replication success $\BFs \leq \gamma$
+can be computed using the result from Appendix~\ref{app:powerBFs} and either
+assuming that the underlying true effect corresponds to its estimate from the
+original study (\emph{conditional power}) or using the predictive distribution
+of the replication effect estimate based on the advocacy prior (\emph{predictive
+  power}) \citep{Spiegelhalter1986b, Micheloud2020}. In practice, both forms may
+be too optimistic as original results are often inflated due to publication bias
+and questionable research practices. One solution is to shrink the original
+effect estimate for power calculations \citep{Pawel2020, Held2021}, but we will
+not focus on this aspect here as this would not provide much more insight but
+simply lower the power curves of all methods.
+
+\begin{figure}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper2/power-plots-1}
+\end{knitrout}
+\caption{Power of the two-trials rule (2TR: $\minBF_{o} \leq
+1/3$ and $\minBF_{r} \leq
+1/3$), the replication Bayes factor ($\BFr
+\leq 1/3$), the sceptical Bayes factor ($\BFs
+\leq
+1/3$), and the recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}
+\leq 1 - \Phi\{z_{\gamma}\}$ with $\gamma =
+1/3$) as a function of the relative variance $c
+= \sigma^2_o/\sigma^2_r$ for different original $z$-values $z_o =
+\that_o/\sigma_o$ (respectively corresponding minimum Bayes factor $\minBF_o$).}
+\label{fig2:condpower}
+\end{figure}
+
+Figure~\ref{fig2:condpower} shows conditional and predictive power as a function
+of the relative variance $c$ and for several values of of the original $z$-value
+$z_o$ (respectively original minimum Bayes factor $\minBF_{o}$). In general,
+uncertainty about replication success is higher for predictive power, leading it
+to be closer to 50\% in all cases. As can also be seen, if the original result
+was not convincing on its own (\eg{} if $z_o = 1.5$ or $z_{o} = 2$), it is
+impossible to achieve replication success with the two-trials rule, the
+sceptical Bayes factor, and the sceptical $p$-value. This is not the case for
+the replication Bayes factor, for which high power can also be obtained for
+small $z_o$ if $c$ is sufficiently large. However, as shown in the previous
+section, the higher power of the replication Bayes factor comes at the cost of a
+massive type I error inflation. For $z_o = 2.5$, the sceptical Bayes factor
+shows higher power than the two-trials rule when $c = 1$, but the power of the
+two-trials rule increases faster in $c$ and approaches the power curve of the
+replication Bayes factor. The power of the sceptical $p$-value is still a bit
+lower, likely due to the more stringent requirement on the minimum relative
+effect estimate. For $z_{o} = 3$, the power differences between the methods
+mostly disappear.
+
+\subsection{Information consistency}
+\label{sec2:informationcons}
+Bayesian hypothesis testing procedures are desired to fulfil certain asymptotic
+properties \citep{Bayarri2012}. Most notably, they should be \emph{information
+consistent} in the sense that if data provide overwhelming support for a
+particular hypothesis, the procedure should indefinitely favour this hypotheses
+over alternative hypotheses.
+
+There are concerns whether the sceptical Bayes factor is information consistent
+when we look at the asymptotics only in terms of the replication data
+\citep{Consonni2021, Ly2021}. The sceptical Bayes factor can never be smaller
+than the original minimum Bayes factor $\minBF_{o}$. This means that it will be
+bounded away from zero as the replication sample size grows ($c \to \infty$),
+even when the data are generated from the same model in both studies. Similarly,
+the sceptical Bayes factor will be bounded away from zero when the replication
+effect estimate increases indefinitely. If these two cases constitute
+overwhelming evidence for replication success, they could be considered
+instances of the \emph{information paradox} \citep{Liang2008}
+% Similarly, with increasing replication effect estimate
+% ($\that_{r} \to \infty$ implying that also the relative effect estimate
+% $d \to \infty$ when $\that > 0$), replication success can at most be established for a
+% sufficiently sceptical relative prior variance $\gy \leq 1$ due to the
+% success conditions~\eqref{eq2:dsuccess}. This implies that the sceptical Bayes factor
+% $\BFs \to \BFcol{0}{\mathrm{S}}(\hat{\theta}_o; g = 1)$, provided $\abs{z_o} \geq
+% \sqrt{2}$ so that $g_{\minBF_{o}} \geq 1$. Hence, the sceptical Bayes factor is
+% also bounded away from zero and this could be considered an
+% instance of the \emph{information paradox} \citep{Liang2008}.
+
+The key to resolving the paradox is to realise that overwhelming evidence for
+replication success needs to be defined through both studies, not only through
+the replication. Assume there is a ``true'' effect size $\theta_{*} \neq 0$
+underlying both effect estimates
+$\that_{i} \sim \Nor(\theta_{*}, \sigma_{i}^{2})$, $i \in \{o, r\}$. Also assume
+the variances $\sigma_{i}^{2} = \kappa/n$ are inversely proportional to the
+sample size $n = n_{o} = n_{r}$ for the same unit variance $\kappa$ in both
+studies. Letting the sample size $n$ go to infinity is then equivalent to
+$\sigma_{o}^{2} \downarrow 0$ and $c = \sigma^{2}_{r}/\sigma^{2}_{o} = 1$. With
+decreasing variances the estimates will
+converge to the true effect size ($\that_{i} \to \theta_{*}$), the relative
+effect estimate will converge to one ($d \to 1$), and the $z$-values will go to
+infinity ($\abs{z_{i}} \to \infty$). Since $c = 1$, the sceptical Bayes factor
+is given by equation~\eqref{eq2:BFsc1}. Moreover, we are allowed to use of the
+approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ as the argument of
+the Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
+350]{Corless1996}. Taken together, we have
+\begin{align}
+  \label{eq2:BFsc1lim2}
+  \BFs =
+  \sqrt{\frac{1 + d^{2}}{1 + (1 - d)^{2}/2 -
+\mathcal{O}\left\{\log(z_{o}^{2})/z_{o}^{2}\right\}}} \cdot
+  \exp\left\{-\frac{z_o^2\left(d^{2} + 2d - 1 \right)}{4(1 + d^{2})}
+- \mathcal{O}\left(\log z_{o}^{2}\right)\right\}
+\end{align}
+Plugging $d = 1$ into~\eqref{eq2:BFsc1lim2}, we see that $\BFs \downarrow 0$ as
+$\abs{z_{o}} \to \infty$, so the sceptical Bayes factor is information
+consistent.
+
+The expression for the sceptical Bayes factor~\eqref{eq2:BFsc1lim2} is also valid
+for other relative effect sizes $d$. Solving for $d$ such that the
+multiplicative term of $z_{o}^{2}$ in the exponent changes the sign, we see that
+the sceptical Bayes factor goes to zero when the underlying true effect size of
+the replication study is at least
+$d > \sqrt{2} - 1 \approx 0.41$ times the size of the
+true effect size from the original study (or
+$d < -\sqrt{2} - 1 \approx -2.41$ due to the
+replication paradox if the advocacy prior is not truncated). This means that
+under the more realistic scenario where the underlying effect sizes from
+original and replication are not exactly the same, the sceptical Bayes factor is
+still consistent when there is not more than 60\% shrinkage of the replication
+effect size.
+
+\section{Extension to non-normal models} \label{sec2:tdist}
+So far, we have always assumed approximate normality of the effect estimates
+$\that_o$ and $\that_r$, as well as known variances $\sigma^2_o$ and
+$\sigma^2_r$. This may be a problem for studies with small sample size and/or
+extreme results (\eg{} when a study examines a rare disease with death rates close
+to 0\%). One way of dealing with this issue is to consider the exact likelihood
+of the data underlying the effect estimates, and then marginalise over possible
+nuisance parameters \citep[Chapter 8.2.2]{Spiegelhalter2004}. This leads to
+marginal likelihoods which are again only conditional on the effect size
+$\theta$, allowing the procedures to be used analogously as described in the
+proceeding sections. The choice of the likelihood depends on the type of effect
+size $\theta$. We will illustrate the approach for \emph{standardised mean
+differences} (SMD) and \emph{log odds ratios} (logOR), two of the most widely
+used types of effect sizes.
+
+\subsection{Standardised mean difference}
+The SMD quantifies how many standard deviation units $\sigma$, the means $\mu_1$
+and $\mu_2$ of measurements from two groups differ, \ie{}
+$$\theta = \frac{\mu_1 - \mu_2}{\sigma}.$$
+Assume now that the measurements come from a normal distribution with common
+variance $\sigma^2$. Knowing the test-statistic $t_i$ from the usual two-sample
+$t$-test, as well as the sample sizes in both groups $n_{1i}$ and $n_{2i}$ from
+study $i \in \{o, r\}$ is sufficient to compute the exact likelihood of the
+data. It is given by a non-central $t$-distribution with degrees of freedom
+$\nu_i = n_{1i} + n_{2i} - 2$ and non-centrality parameter $\theta \sqrt{n^*_i}$
+with $n^*_i = (n_{1i}n_{2i})/(n_{1i} + n_{2i})$ \citep{Bayarri2002}
+\begin{align}
+  \label{eq2:nct}
+  T_i \given \theta \sim \text{NCT}_{\nu_i} \left(\theta \sqrt{n^*_i}\right).
+\end{align}
+The same framework is also applicable to test-statistics $t_{i}$ from paired
+$t$-tests based on $n_{i}$ paired measurements. The SMD $\theta$ represents then
+the standardised mean difference score and $\nu_{i} = n_{i} - 1$ and
+$n_{i}^{*} = n_{i}$ need to be used in~\eqref{eq2:nct}.
+
+There is no conjugate prior for the SMD $\theta$ under model~\eqref{eq2:nct}, so
+it is not obvious which prior should be chosen to represent scepticism about it.
+We will use a zero-mean normal prior $\theta \given \HS \sim \Nor(0, \tau^{2})$
+so that the exact procedure is equivalent with the normal approximation as the
+sample size increases. For the advocacy prior we need to know the posterior
+distribution of the SMD $\theta$ conditional on the original study and a flat
+prior on $\theta$. Exploiting the fact that the non-central $t$-distribution can
+be expressed as a location-scale mixture of a normal with an inverse-gamma
+distribution
+%% \ie{} $\text{NCT}_\nu(t; \theta \sqrt{n^*}) = \int
+%% \Nor(t; \theta \sqrt{n^*\tau^2}, \tau^2) \text{IG}(\tau^2; \nu/2, \nu/2) d\tau^2$
+\citep[Chapter 31]{Johnson1995}, the density of the SMD under the advocacy prior
+is given by
+\begin{align*}
+  f(\theta \given t_o)
+  = \int_0^\infty \Nor\left(\theta; \frac{t_o}{\sqrt{n_o^* \tau^2}},
+  \frac{1}{n_o^*}\right)  \text{IG}\left(\tau^2; \frac{\nu_o + 1}{2},
+  \frac{\nu_o}{2}\right) \, \text{d}\tau^2,
+\end{align*}
+where $\Nor(x; \mu, \phi)$ denotes the density function of the normal
+distribution with mean $\mu$ and variance $\phi$ evaluated at $x$, and similarly
+$\text{IG}(y; a, b)$ denotes the density function of the inverse-gamma
+distribution with shape and rate parameters $a$ and $b$ evaluated at $y$.
+
+Taken together, the SMD version of the method proceeds analogously as in
+Box~\hyperref[box:nutshell]{1} with the two Bayes factors replaced by
+\begin{align*}
+  \BFcol{0}{\mathrm{S}}(t_{o};\tau^{2})
+  &= \frac{\text{NCT}_{\nu_{o}}(t_{o}; 0)}{\int
+  \text{NCT}_{\nu_{o}}(t_{o}; \theta \sqrt{n_{o}^{*}})
+  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
+  \BFcol{\text{S}}{\text{A}}(t_{r};\tau^{2})
+  &= \frac{\int\text{NCT}_{\nu_{r}}(t_{r};\theta
+  \sqrt{n_{r}^{*}})\Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
+  \int\text{NCT}_{\nu_{r}}(t_{r};\theta
+  \sqrt{n_{r}^{*}}) f(\theta \given t_{o}) \, \text{d} \theta}
+\end{align*}
+and using numerical integration as the integrals cannot be evaluated
+analytically.
+
+\subsection{Log odds ratio}
+In the case of binary data, we have two independent binomial samples
+\begin{align*}
+  &X_{1i} \given \pi_1 \sim \Bin(n_{1i}, \pi_1)&
+  &X_{2i} \given \pi_2 \sim \Bin(n_{2i}, \pi_2)&
+\end{align*}
+for each study $i \in \{o, r\}$, and the effect of the treatment in group 1
+relative to the treatment in group 2 is quantified with the logOR
+$$\theta = \log \frac{\pi_1/(1 - \pi_1)}{\pi_2/(1 - \pi_2)}.$$
+To obtain a marginal likelihood that only depends on $\theta$, we need to
+specify a prior for either $\pi_2$ or $\pi_1$ and marginalise over it. A
+principled choice is the translation invariant Jeffreys prior,
+$\pi_1, \pi_2 \sim \Be(1/2, 1/2)$. The exact marginal likelihood for the data
+from study $i$ is then given by
+\begin{align}
+  \label{eq2:binexact}
+  f(x_{1i}, x_{2i} \given \theta)
+  &= \int_0^1 \Bin\left(x_{1i}; n_{1i}, \left\{1 + \exp\left[-\theta - \log
+    \frac{\pi_2}{1 - \pi_2}\right]\right\}^{-1}\right) \Bin(x_{2i}; n_{2i}, \pi_2)
+  \nonumber
+  \\ &\phantom{= \int_0^1}  \times \Be(\pi_2; 1/2, 1/2) \, \text{d} \pi_2
+\end{align}
+where $\Bin(x; n, \pi)$ denotes the probability mass function of the binomial
+distribution with $n$ trials and probability $\pi$ evaluated at $x$, and
+likewise $\Be(y; a, b)$ denotes the density function of the beta distribution
+with parameters $a$ and $b$ evaluated at $y$.
+
+There is no conjugate prior for the logOR under model~\eqref{eq2:binexact}, but a
+pragmatic choice is to specify a zero-mean normal prior
+$\theta \given \HS \sim \Nor(0, \tau^{2})$ for the sceptic, to match with the
+normal approximation as the sample size increases. For the advocacy prior, we
+need to know the posterior distribution of the logOR $\theta$ based on the
+original study.
+Using a result from \citet{Marshall1988} combined with a change-of-variables,
+the exact posterior density of the logOR $\theta$ given the original data and
+Jeffreys priors on $\pi_1$ and $\pi_2$ is
+\begin{align*}
+  f(\theta \given x_{1o}, x_{2o}) &=
+  \begin{cases}
+    % C \, \exp\{(x_{1o} + 1/2) \theta\} \,
+    % F(n_{1o} + 1, x_{1o} + x_{2o} + 1, n_{1o} + n_{2o} + 2, 1 - \exp(\theta))
+    % & \text{for} ~ \theta < 0 \\
+    % C \, \exp\{-(n_{1o} - x_{1o} + 1/2) \theta\} \,
+    % F(n_{1o} + 1, n_{10} - x_{1o} + n_{2o} - x_{2o} + 1, n_{1o} + n_{2o} + 2,
+    % 1 - \exp(-\theta)) & \text{for} ~ \theta > 0 \\
+    C \, \exp\{e \theta\} \,
+    F\left(e + f, e + g, e + f + g + h, 1 - \exp\{\theta\}\right)
+    & \text{for} ~ \theta < 0 \\
+    C \, \exp\{-f \theta\} \,
+    F\left(e + f, f + h, e + f + g + h, 1 - \exp\{-\theta\}\right)
+    & \text{for} ~ \theta > 0 \\
+  \end{cases}
+\end{align*}
+where $F(\cdot)$ is the hypergeometric function, $e = x_{1o} + 1/2$,
+$f = n_{1o} - x_{1o} + 1/2$, $g = x_{2o} + 1/2$, $h = n_{2o} - x_{2o} + 1/2$,
+$C = \text{B}(e + g, f + h)/\{\text{B}(e, f) \text{B}(g, h)\}$, and
+$\text{B}(\cdot, \cdot)$ is the Beta function.
+
+Combining the previous results, we obtain
+\begin{align*}
+  \BFcol{0}{\text{S}}(x_{1o}, x_{2o};\tau^{2})
+  &= \frac{ f(x_{1o}, x_{2o} \given 0)}{\int
+   f(x_{1o}, x_{2o} \given \theta)
+  \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta} \\
+  \BFcol{\text{S}}{\text{A}}(x_{1r}, x_{2r};\tau^{2})
+  &= \frac{\int f(x_{1r}, x_{2r} \given \theta)
+    \Nor(\theta; 0, \tau^{2}) \, \text{d}\theta}{
+    \int f(x_{1r}, x_{2r} \given \theta)
+    f(\theta \given x_{1o}, x_{2o}) \, \text{d} \theta}
+\end{align*}
+as an exact replacement for the Bayes factors in Box~\hyperref[box:nutshell]{1}.
+Again, there are no closed form expressions for the integrals, but numerical
+integration needs to be used.
+
+\section{Application}
+\label{sec2:applications}
+The following section will illustrate application of the sceptical Bayes factor
+using data from the \emph{Social Sciences Replication Project}
+\citep{Camerer2018}, provided in Table \ref{tab:ssrp}. Effect estimates were
+reported on the correlation scale ($r$), which is why we applied the Fisher
+$z$-transformation $\hat{\theta} = \text{tanh}^{-1}(r)$. This leads to the
+transformed estimates having approximate variance
+$\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}, so the relative variance
+$c$ is roughly the ratio of the replication to the original study sample size
+$c \approx n_{r}/n_{o}$.
+
+For all studies except \citet{Janssen2010} and \citet{Derex2013}, the exact
+approach for either SMD or logOR effect sizes from Section~\ref{sec2:tdist} is
+applicable. In the studies with binary data
+% \citep{Balafoutas2012, Gneezy2014, Hauser2014},
+computing the exact posterior using the hypergeometric function led to numerical
+issues in some cases and numerical integration was used then.
+% Balafoutas and Sutter - integration and hypergeo work
+% Gneezy et al. - only integration works
+% Hauser et al. - only hypergeo works
+In most cases, the normal approximation of the likelihood seems to lead to
+similar numerical results for both $\BFs$ and $\BFr$ as compared to their
+counterparts based on exact likelihoods. Qualitative conclusions are the same
+under both approaches and we will therefore focus on the normal approximation
+due to better comparability with the remaining measures of replication success
+as all of them were computed based on approximate normal likelihoods.
+
+For the study pairs where the sceptical Bayes factor suggests a large degree of
+replication success, all other methods suggest the same in every case. However,
+there are also cases where there appear to be discrepancies among the methods.
+For instance, the two-trials rule and the replication Bayes factor may indicate
+a larger degree of replication success compared to the sceptical $p$-value and
+sceptical Bayes factor. This happens for replications that show a substantial
+increase in sample size but also a much smaller effect estimate compared to the
+original study. For example, in \citet{Balafoutas2012} the sample size was about
+$c = 3.48$ times larger in the replication, whereas the effect estimate was only
+$d = 0.52$ the size of the original one. The replication is successful at
+$\gamma = 1/3$ with the two-trials rule ($\minBF_{o} = 1/4.2$ and
+$\minBF_{r} = 1/3.6$) and the replication Bayes factor ($\BFr = 1/3.9$), but not
+with the sceptical Bayes factor ($\BFr = 1/1.6$) or the sceptical $p$-value
+($\tilde{p}_{\mathrm{S}} = 0.04 > 1 - \Phi(z_\gamma = 2.18) = 0.01$).
+
+\begin{landscape}
+\begin{table}[!htb]
+\centering
+\caption{Results for data from \emph{Social Sciences Replication Project}
+  \citep{Camerer2018}. Shown are relative variances
+  $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimates
+  $d = \that_{r}/\that_{o}$ (computed on Fisher $z$-scale), $Q$-statistic
+  $Q = (\that_{o} - \that_{r})^{2}/(\sigma^{2}_{o} + \sigma^{2}_{r})$, minimum
+  Bayes factors of original and replication effect estimate ($\minBF$),
+  recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}$), sceptical Bayes
+  factors ($\BFs$) and replication Bayes factors ($\BFr$), the latter two
+  computed using either a normal approximation or the exact likelihood of the
+  data. }
+% \resizebox{1\textwidth}{!}{%
+
+% latex table generated in R 4.2.2 by xtable 1.8-4 package
+% Thu Nov 24 10:46:19 2022
+{\small
+\begin{tabular}{lrrrlllllll}
+  \toprule
+Original study & $c$ & $d$ & $Q$ & $\minBF_o$ & $\minBF_r$ & $\tilde{p}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ & $\mathrm{BF}_{\mathrm{S}}$ (exact) & $\mathrm{BF}_{\mathrm{R}}$ & $\mathrm{BF}_{\mathrm{R}}$ (exact) \\
+  \midrule
+Hauser et al. (2014) & 0.51 & 1.04 & 0.03 & < 1/1000 & < 1/1000 & < 0.0001 & < 1/1000 & < 1/1000 & < 1/1000 & < 1/1000 \\
+  Aviezer et al. (2012) & 0.92 & 0.60 & 3.49 & < 1/1000 & 1/347 & < 0.0001 & 1/78 & 1/10 & 1/284 & 1/41 \\
+  Wilson et al. (2014) & 1.33 & 0.83 & 0.28 & < 1/1000 & 1/659 & 0.0001 & 1/45 & 1/35 & < 1/1000 & < 1/1000 \\
+  Derex et al. (2013) & 1.29 & 0.65 & 1.14 & 1/520 & 1/17 & 0.002 & 1/8.5 &  & 1/31 &  \\
+  Gneezy et al. (2014) & 2.31 & 0.81 & 0.22 & 1/18 & 1/157 & 0.004 & 1/6.9 & 1/7.5 & 1/474 & 1/551 \\
+  Karpicke and Blunt (2011) & 1.24 & 0.58 & 1.75 & < 1/1000 & 1/9.6 & 0.002 & 1/5.6 & 1/5 & 1/12 & 1/12 \\
+  Morewedge et al. (2010) & 2.97 & 0.76 & 0.30 & 1/7.3 & 1/65 & 0.011 & 1/3.9 & 1/4 & 1/160 & 1/156 \\
+  Kovacs et al. (2010) & 4.38 & 1.38 & 0.59 & 1/3.2 & < 1/1000 & 0.009 & 1/3.2 & 1/3.8 & < 1/1000 & < 1/1000 \\
+  Duncan et al. (2012) & 7.42 & 0.57 & 1.29 & 1/12 & < 1/1000 & 0.011 & 1/3.1 & 1/3.1 & < 1/1000 & < 1/1000 \\
+  Nishi et al. (2015) & 2.42 & 0.57 & 1.05 & 1/12 & 1/6.1 & 0.016 & 1/2.5 & 1/2.2 & 1/8.2 & 1/7.6 \\
+  Janssen et al. (2010) & 0.65 & 0.48 & 3.51 & < 1/1000 & 1/3.3 & 0.003 & 1/1.6 &  & 1/1.6 &  \\
+  Balafoutas and Sutter (2012) & 3.48 & 0.52 & 1.02 & 1/4.2 & 1/3.6 & 0.04 & 1/1.6 & 1/1.6 & 1/3.9 & 1/3.9 \\
+  Pyc and Rawson (2010) & 9.18 & 0.38 & 1.79 & 1/3.5 & 1/7.3 & 0.061 & 1/1.2 & 1/1.2 & 1/4 & 1/4 \\
+  Rand et al. (2012) & 6.27 & 0.18 & 3.96 & 1/7.1 & 1 & 0.13 &  &  & 9.6 & 9.7 \\
+  Ackerman et al. (2010) & 11.69 & 0.23 & 2.15 & 1/2.2 & 1/1.3 & 0.15 &  &  & 3.2 & 3.2 \\
+  Sparrow et al. (2011) & 3.50 & 0.13 & 5.80 & 1/26 & 1 & 0.19 &  &  & 29 & 32 \\
+  Shah et al. (2012) & 11.62 & -0.05 & 4.08 & 1/2.2 & 1 & 0.66 &  &  & 25 & 26 \\
+  Kidd and Castano (2013) & 8.57 & -0.10 & 6.83 & 1/5.7 & 1 & 0.77 &  &  & 72 & 69 \\
+  Gervais and Norenzayan (2012) & 9.78 & -0.12 & 5.44 & 1/3 & 1 & 0.78 &  &  & 36 & 37 \\
+  Lee and Schwarz (2010) & 7.65 & -0.11 & 6.80 & 1/5.4 & 1 & 0.79 &  &  & 65 & 69 \\
+  Ramirez and Beilock (2011) & 4.47 & -0.09 & 19.29 & < 1/1000 & 1 & 0.85 &  &  & > 1000 & > 1000 \\
+   \bottomrule
+\end{tabular}
 }
-
+% %
+% }
+\label{tab:ssrp}
+\end{table}
+
+\end{landscape}
+
+% % EJ Wagenmakers' analysis
+% % - Ackerman et al. (2010): BFR 3.23  -- our BFR 3.2
+% % -* Aviezer et al. (2012): BFR 1/57 -- our BFR 1/284
+% % - Balafoutas and Sutter (2012): 1/4.27 -- our BFR 1/3.9
+% % -** Derex et al. (2013): 1/3'701 -- our BFR 1/31
+% % - Duncan et al. (2012): 1/2513 -- our BFR 1/3079.4
+% % - Gervais & Norenzayan (2012): 36.5 -- our BFR 36
+% % - Gneezy et al. (2014): 1/485.27 -- our BFR 1/474
+% % -* Hauser et al. (2014): 1/10'211 -- our BFR 1/620'059
+% % -** Janssen et al. (2010): 2'134'835 -- our BFR 1/1.6
+% % - Karpicke & Blunt (2011): 1/11.82 -- our BFR 12
+% % - Kidd & Castano (2013): 71.43 -- our BFR 72
+% % - Kovacs et al. (2010): 1/132'389'305 -- our BFR 1/333'616'129
+% % - Lee & Schwarz (2010): 68 -- our BFR 65
+% % - Morewedge et al. (2010): 1/158 -- our BFR 1/160
+% % - Nishi et al. (2015): 1/7.77 -- our BFR 1/8.2
+% % - Pyc and Rawson (2010): 1/4.04 -- our BFR 1/4
+% % -* Ramirez & Beilock (2011): 12'240 -- our BFR 24'996
+% % - Rand et al. (2012): 9.71 -- our BFR 9.6
+% % - Shah et al. (2012): 26.05 -- our BFR 25
+% % - Sparrow et al. (2011): 31.65 -- our BFR 29
+% % -* Wilson et al. (2014): 1/1871 -- our BFR 1/2533
+
+%% ps does but BFs doesn't flag RS
+Discrepancies between the sceptical $p$-value and the sceptical Bayes factor
+happen in situations where the replication shows an effect estimate that,
+although incompatible with the sceptical prior, is also incompatible with the
+advocacy prior. For example in the \citet{Janssen2010} replication, both effect
+estimates are substantially larger than zero ($\that_o = 0.74$ with
+$\minBF_{o} < 1/1000$ and $\that_r = 0.36$ with $\minBF_{r} = 1/3.3$), yet the
+$Q$-statistic indicates some incompatibility ($Q = 3.51$), which explains why
+$\tilde{p}_{\mathrm{S}} = 0.003$, but $\BFs = 1/1.6$ only.
+
+Discrepancies between the replication Bayes factor and the sceptical Bayes
+factor arise when the replication finding provides overwhelming evidence against
+the null, whereas the original finding was less compelling. The replication of
+\citet{Kovacs2010} illustrates this situation. The original study provided only
+moderate evidence against the null ($\that_o = 0.49$ and $\minBF_o = 1/3.2$),
+whereas the replication finding was more compelling ($\that_r = 0.67$ and
+$\minBF_r < 1/1000$). By construction the sceptical Bayes factor can only be as
+small as the minimum Bayes factor from the original study $\minBF_o$, which is
+actually attained in this case ($\BFs = 1/3.2$). The replication Bayes factor,
+on the other hand, is not limited by the moderate level of evidence from the
+original study and indicates decisive evidence for the advocate
+($\BFr < 1/1000$). This illustrates that in order to achieve a reasonable degree
+of replication success, the sceptical Bayes factor requires the original study
+to be convincing, whereas the replication Bayes factor only requires a
+compelling replication result.
+
+\section{Discussion}
+\label{sec2:discussion}
+We proposed a novel method for the statistical assessment of replicability
+combining reverse-Bayes analysis with Bayesian hypothesis testing. Compared to
+other methods, the sceptical Bayes factor poses more stringent requirements but
+also allows for stronger statements about replication success. It ensures that
+both studies provide sufficient evidence against a null effect, while also
+penalising incompatibility of their effect estimates. If the replication sample
+size is not too small, the sceptical Bayes factor comes with appropriate
+frequentist error rates, which is often a requirement from research funders and
+regulators. Asymptotic analysis of the method showed that it is information
+consistent in the sense that if the sample size in both studies increases, the
+sceptical Bayes factor will indicate overwhelming replication success when the
+underlying effect size of the replication is not much smaller than the
+underlying effect size of the original study. Finally, the sceptical Bayes
+factor is the only method in our comparison which does not suffer from any form
+of the shrinkage paradox, \ie{} replication success can never be achieved with
+arbitrarily small replication effect estimates, not even when the replication
+sample size becomes very large or the evidence from the original study
+overwhelming.
+
+In extreme scenarios the sceptical Bayes factor can suffer from the replication
+paradox, which means that it may flag success when the replication estimate goes
+in opposite direction of the original one. However, the paradox can be avoided
+by truncating the advocacy prior to the direction of the original estimate. It
+may also happen that the result of the replication is so inconclusive that
+replication success cannot be established at any level, so the sceptical Bayes
+factor does not exist. Other methods, such as the sceptical $p$-value or the
+replication Bayes factor, can be used in this situation.
+
+%% extensions and limitations
+The proposed method could be extended in many ways. First, in many cases not
+just one but several replication studies are conducted for one original study
+\citep[\eg{} as in][]{Klein2014}. The Bayesian framework allows to easily extend
+the sceptical Bayes factor to the ``many-to-one'' replication setting as the
+likelihoods are also straightforward to compute for a sample of replication
+effect estimates. Second, a multivariate generalisation would allow for effects
+in the form of a vector with approximate multivariate normal likelihood which is
+then combined with a sceptical $g$-prior \citep{Liang2008}. The normal prior
+could also be replaced with other distributions, for example the (multivariate)
+Cauchy distribution which is often the preferred prior choice for default Bayes
+factor hypothesis tests \citep{Jeffreys1961}. The $g$ parameter of the $g$-prior
+or the scale parameter of the Cauchy prior would then take over the role of the
+relative sceptical prior variance. Third, based on the replication result one
+could also compute a posterior distribution for the effect size based on a
+model-average of the advocacy prior and the sceptical prior (using the variance
+at the sceptical Bayes factor). This distribution would provide a formal
+compromise between scepticism and advocacy of the original finding. Fourth,
+while Bayes factors are an important part in Bayesian hypothesis testing, they
+do not take into account the prior probabilities of the hypotheses under
+consideration. It would be interesting to investigate whether the reverse-Bayes
+approach could be used in a framework where priors are assigned jointly to the
+hypothesis and parameter space \citep{Dellaportas2012}. Finally, an important
+aspect is the design of new replication studies. An appropriate sample size is
+of particular importance for a replication to be informative. We will report in
+the future on sample size planning based on the sceptical Bayes factor.
+
+% conclusion
+For a thorough assessment of replication attempts, no single metric seems to be
+able to answer all important questions completely. Instead, we recommend that
+researchers conduct a comprehensive statistical evaluation of replication
+success. Reverse-Bayes methods naturally fit to the replication setting, they
+avoid various paradoxes from which other methods suffers, and they combine
+different notions of replicability. The reverse-Bayes approach therefore leads
+to sensible inferences and decisions, which is why we advocate it as a key part
+in the assessment of replication success.
+
+\section*{Software and data}
+All analyses were performed in the R programming language version
+4.2.2 \citep{R}. The code to
+reproduce this manuscript is available at
+\url{https://gitlab.uzh.ch/samuel.pawel/BFScode}. We used the implementation of
+the Lambert $W$ function from the package \texttt{lamW} \citep{Adler2015},
+graphics were created with the \texttt{ggplot2} package \citep{Wickham2016}, the
+sceptical $p$-value and related calculations were conducted using the package
+\texttt{ReplicationSuccess} available on the Comprehensive R Archive Network
+% \url{https://cran.r-project.org/web/packages/ReplicationSuccess/index.html}
+\citep{Held2020}. All methods are implemented in the R package \texttt{BayesRep}
+which is available at \url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}.
+
+Data on effect estimates from the \emph{Social Sciences Replication Project}
+\citep{Camerer2018} were downloaded from \url{https://osf.io/abu7k/},
+respectively, taken from \url{https://osf.io/nsxgj/} for exact calculations.
+
+\section*{Acknowledgements}
+We thank the anonymous referees for the helpful comments and suggestions that
+have considerably improved the paper. We also thank Guido Consonni, Luca La
+Rocca, Malgorzata Roos, Georgia Salanti, Charlotte Micheloud, and Maria
+Bekker-Nielsen Dunbar for helpful discussion and comments on drafts of the
+manuscript.
+
+\section*{Funding}
+This work was supported by the Swiss National Science Foundation (project number
+189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
+design, data collection and analysis, decision to publish, or preparation of the
+manuscript.
+
+\begin{subappendices}
+  \renewcommand{\thesection}{\Alph{section}}
+
+\section{Sufficiently sceptical relative prior variance}
+\label{appendix:ssrv}
+The sufficiently sceptical relative prior variance at level $\gamma$ is the
+value $\gy \in [0, \gminBFo]$ that fulfils the condition
+\begin{align}
+  \label{sspv}
+  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gy)
+  &= \gamma.
+\end{align}
+Substituting~\eqref{sspv} and rearranging terms, we obtain
+\begin{align}
+  \label{sspv2}
+  \sqrt{1 + \gy} \cdot
+  \exp\left\{-\frac{1}{2} \cdot
+  \frac{\gy}{1 + \gy} \cdot z^2_o\right\}
+  &= \gamma \nonumber \\
+  \iff \frac{1}{\gamma} \cdot \exp\left\{-\frac{z_o^2}{2}\right\}
+  &= \frac{1}{\sqrt{1 + \gy}} \exp\left\{-\frac{1}{2} \cdot
+  \frac{z_o^2}{1 + \gy}\right\}. \nonumber
+  \\
+  \intertext{Squaring both sides and multiplying by $-z_o^2$, this becomes}
+  \iff -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
+  &= -\frac{z_o^2}{1 + \gy}
+  \exp\left\{-\frac{z_o^2}{1 + \gy}\right\}.
+\end{align}
+This is a transcendental equation that cannot be explicitly solved in terms of
+elementary functions. However, if we set $q = -z_o^2/(1 + \gy)$
+then~\eqref{sspv2} becomes
+\begin{align*}
+  -\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}
+  &= q \cdot \exp\left\{q\right\}.
+\end{align*}
+The solution for $q$ (and consequently for $\gy$) can be explicitly computed
+with
+\begin{align}
+\label{eq2:solutionvss}
+  q &= \lw{-1}\left(-\frac{z_o^2}{\gamma^2} \cdot \exp\left\{-z_o^2\right\}\right)
+  \nonumber \\
+  \gy &=
+  \begin{cases}
+    -\dfrac{z_o^2}{q} - 1 & ~~ \text{if} ~ -\dfrac{z_o^2}{q} \geq 1 \\
+    \text{undefined} & ~~ \text{else}
+  \end{cases}
+\end{align}
+where $\lw{-1}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
+$W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, ensuring that $\gy \leq \gminBFo$. See
+Appendix~\ref{appendix:lambertW} for details about the Lambert $W$ function. For
+some $z_o$, equation \eqref{sspv2} can also be satisfied for negative $\gy$,
+which is why we need to add the condition $-z_o^2/q \geq 1$ in equation
+\eqref{eq2:solutionvss}, such that $\gy$ is a valid relative variance.
+
+As $z_{o}^{2}$ becomes larger, the argument to the Lambert function
+$x = -z_{o}^{2}\exp(-z_{o}^{2})/\gamma^{2}$ will approach zero, so the
+approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ can be applied
+\citep[p. 350]{Corless1996}. This leads to
+\begin{align*}
+  \gy \approx \frac{z_{o}^{2}}{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2} +
+  \log\{z_{o}^{2} + \log \gamma^{2} - \log z_{o}^{2}\}} - 1.
+\end{align*}
+We can see that $\gy \downarrow 0$ when $\gamma$ remains fixed and
+$z_{o}^{2} \to \infty$, which means that the sufficiently sceptical relative
+prior variance converges to zero for increasingly compelling evidence from the
+original study.
+
+\section{The Lambert \textit{W} function}
+\label{appendix:lambertW}
+The Lambert $W$ function \citep{Corless1996} is defined as the function
+$W(\cdot)$ satisfying
+$$W(y) \cdot \exp\{W(y)\} = y$$
+and it is also known as ``product logarithm`` since it returns the number which
+plugged in the exponential function and then multiplied by itself produces $y$.
+For real $y$, $W(y)$ is only defined for $y \geq - e^{-1}$ and for
+$y \in [-e^{-1}, 0)$ the function has two branches that are commonly denoted by
+$\lw{0}(\cdot)$, the branch with $W(y) \geq -1$, and $\lw{-1}(\cdot)$, the
+branch with $W(y) \leq -1$ (see Figure \ref{fig2:lambertW} for an illustration).
+\begin{figure}[!htb]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{images/paper2/plot-Lambert-1}
 \end{knitrout}
-\caption{Proportion of successful replications as a function of the limiting
-  relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
-  equivalent level $\alpha'$ where the corresponding limiting relative effect
-  size is 1. The replication success (RS) approach is compared with the
-  two-trials rule (2TR).}
-\label{fig2:fig7}
+\caption{Lambert $W$ function for real argument $y$.}
+\label{fig2:lambertW}
 \end{figure}
 
-\section{Discussion}\label{sec2:discussion}
-In this paper, we have expanded on the replication success approach introduced
-in \citet{Held2020} and demonstrated its advantages over alternative methods
-such as the two-trials rule. In particular, the method provides an attractive
-compromise between hypothesis testing and estimation,
-as it penalizes
-shrinkage of the replication effect estimate compared to the original one,
-while ensuring that both are statistically significant to some extent.
-%% For instance, the method will indicate only a low degree of replication success when
-%% the replication study shows a much smaller but statistically significant
-%% effect estimate, whereas it can still indicate some degree of
-%% success when either original or replication $p$-value are slightly above the
-%% significance level. %% , provided their effect estimates are compatible.
-
-We further refined the method by proposing the golden level, a new threshold for
-replication success. It guarantees that borderline significant original studies
-can only be replicated successfully if the replication effect estimate is larger
-than the original one. Compared to the two-trials rule, the golden level offers
-uniform gains in project power and controls the Type-I error rate at any
-one-sided level $\alpha < 0.058$ if the replication sample size
-is not smaller than the original one. Empirical evaluation of data from four
-replication projects highlights that in most cases the methods are in agreement,
-however, for the study pairs where the approaches disagree, the replication
-success approach seems to lead to more sensible conclusions. The good
-performance has been recently confirmed by a comparison of different replication
-success metrics through a simulation study in the presence of publication bias
-\citep{Muradchanian2021}.
-
-Despite a lack of agreement as to which statistical method should be used to
-evaluate replication studies, conclusions based on different methods usually
-agree. Nevertheless, in some cases, classical methods such as the two-trials
-rule may produce anomalies. We argue that the replication success approach
-improves upon existing methods leading to more appropriate inferences and
-decisions that better reflect the available evidence. However, in extreme cases
-the performance of the sceptical $p$-value may be considered as strange or even
-counterintuitive. Specifically, if the original study was only borderline
-significant, a highly significant replication study can only lead to success if
-the replication effect estimate is larger than the original one. To understand
-this behaviour it is important to realize that the proposed approach does not
-synthesize the evidence from the two studies (like a standard meta-analysis).
-The sceptical $p$-value is designed to confirm claims of new discoveries through
-replication, but will remain ``stubborn'' \citep{Ly2020} if the original study
-was not particularly convincing, even if the replication study provides
-overwhelming evidence for an effect. It will lead to a different result if the
-order of studies was reversed, as long as original and replication study do not
-have the same sample size ($c \neq 1$). The related harmonic mean $\chi^2$-test
-\citep{Held2020b} for evidence synthesis of two or more studies also requires
-each study to be convincing on its own to a certain degree, but treats them as
-exchangeable.
-
-With this paper we further advanced the reverse-Bayes methodology for the
-analysis and design of replication studies, yet certain limitations and
-opportunities for future research remain: First, assuming normality of the
-effect estimates may be questionable, especially for small sample sizes, and
-more robust distributional assumptions could be considered. Second, in some
-types of analyses (\eg regression or ANOVA) the effect estimate is a vector and
-the approach would need suitable adaptations. Third, there is a recent trend to
-not only conduct one but several replications for one original study
-\citep[\eg][]{Klein2014, Ebersole2016, Klein2018}. Also for this situation, the
-method would need to be adapted, \eg the replication estimates could be first
-synthesized and an analysis of replication success could be performed
-subsequently.
-
-Throughout the paper we have assumed that the relative sample size is fixed in
-advance. In practice the sample size of the replication study is often chosen
-based on the result of the original study \citep{Anderson2017}. Power
-calculations as shown in Figure \ref{fig2:fig3} can then be inverted to determine
-the appropriate sample size of the replication study. We can also invert
-equation \eqref{eq2:res} to obtain the required replication sample size based on
-the specification of the minimum relative effect size $\dmin$ to achieve
-replication success. This novel way of calculating the sample size requires the
-specification of the minimum relative effect size which can still be considered
-as acceptable. Sample size calculations based on the two-trials rule can also be
-formulated in terms of the minimum relative effect size by inverting equation
-\eqref{eq2:dSig}. We will report on a detailed comparison of the different
-approaches in future work.
-
-\section*{Data and Software}
-Code and data to reproduce our analyses are available at
-\url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
-the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
-The data which was used is available in the R package
-\texttt{ReplicationSuccess} (available on CRAN). Further information can be
-found on the corresponding help page (with the command \texttt{?RProjects}).
-
-\section*{Acknowledgments}
-Support by the Swiss National Science Foundation (Project \#~189295) is
-gratefully acknowledged. We acknowledge helpful and constructive comments by the
-editor and a referee on an earlier version of this article.
-
+\section{Computation of the sceptical Bayes factor}
+\label{appendix:bfs}
+From the definition of the sceptical Bayes factor it is apparent that $\BFs$ is
+either
+\begin{enumerate}
+  \item \label{undef} undefined,
+  if
+  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g) >
+  \BFcol{\text{0}}{\text{S}}(\hat{\theta}_o; g)$ for all $g \in [0,
+    \gminBFo]$
+
+  \item \label{lowbound} $\BFs = \minBF_{o}$, if
+  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq
+  \BFcol{0}{\text{S}}(\hat{\theta}_o; \gminBFo)$
+
+  \item \label{intersection}
+  $\BFs = \inf_{\gy}
+  \left\{\gamma : \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)
+  = \gamma\right\}$,
+  the height of the lowest intersection of
+  $\BFcol{0}{\text{S}}(\hat{\theta}_o; \gy) = \gamma$ and
+  $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)$
+  in $\gy$ otherwise
+\end{enumerate}
+Whether $\BFs$ attains the lower bound $\minBF_{o}$ (condition \ref{lowbound})
+can be checked by evaluating if
+$\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gminBFo) \leq \minBF_{o}$ and setting
+$\BFs = \minBF_{o}$ if it is the case. For condition \ref{intersection}, we know
+that the intersections satisfy
+\begin{align*}
+  \BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; g_*) &=
+  \BFcol{0}{\text{S}}(\hat{\theta}_o; g_*) \\
+  \sqrt{\frac{1/c + 1}{1/c + g_*}} \cdot
+  \exp\left\{-\frac{z_{o}^{2}}{2}\left(\frac{d^2}{1/c + g_*} -
+  \frac{\left(1 - d\right)^2}{1/c + 1} \right)\right\}
+  &= \sqrt{1 + g_*} \cdot
+  \exp\left\{-\frac{1}{2} \cdot \frac{g_*}{1 + g_*} \cdot z^2_o\right\}
+\end{align*}
+which is equivalent to
+\begin{align}
+  \sqrt{\frac{1}{(1 + g_*)(1/c + g_*)}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
+  \frac{1}{1 + g_*} + \frac{d^{2}}{1/c + g_*}\right)\right\} \nonumber \\
+  = \sqrt{\frac{1}{1/c + 1}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
+  1 + \frac{(1 - d)^{2}}{1/c + 1}\right)\right\}.
+  \label{eq2:bfsroot}
+\end{align}
+This is a transcendental equation that has no closed-form solution for $g_*$ in
+terms of elementary functions, but root-finding algorithms can be used to
+compute it. However, when $c = 1$, equation~\eqref{eq2:bfsroot} simplifies
+\begin{align}
+  \label{eq2:bfsroot2}
+  \frac{1}{1 + g_*}\cdot\exp\left\{-\frac{z_{o}^{2}}{2} \cdot
+  \frac{1 + d^{2}}{1 + g_*}\right\}
+  &= \frac{1}{\sqrt{2}}\cdot\exp\left\{-\frac{z_{o}^{2}}{2}\left(
+  1 + \frac{(1 - d)^{2}}{2}\right)\right\}.
+\end{align}
+Multiplying~\eqref{eq2:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
+Lambert $W$ function leads to
+\begin{align}
+  \label{eq2:gintersect}
+  % q &= W\left(-\frac{z_A^2}{\sqrt{2}} \cdot
+  % \exp\left\{-\frac{z_o^2}{2} \left(1 + \frac{(1 - d)^2}{2}\right)\right\}\right) \\
+  % g_* &=
+  % \begin{cases}
+  %   \dfrac{-z_A^2}{q} - 1 & ~~ \text{if} ~ \dfrac{-z_A^2}{q} \geq 1 \\
+  %   \text{undefined} & ~~ \text{else},
+  % \end{cases}
+  k &= W\left(-\frac{z_{o}^{2}}{\sqrt{2}} \cdot \frac{1 + d^{2}}{2} \cdot
+      \exp\left\{-\frac{z_o^2}{2} \left[1 + \frac{(1 - d)^2}{2}\right]\right\}\right)
+  \nonumber \\
+  g_* &=
+  \begin{cases}
+    -\dfrac{z_o^2}{k}\cdot \dfrac{1 + d^{2}}{2} - 1 & ~~ \text{if} ~
+    -\dfrac{z_o^2}{k}\cdot\dfrac{1 + d^{2}}{2} \geq 1 \\
+    \text{undefined} & ~~ \text{else},
+  \end{cases}
+\end{align}
+with the condition that $-z_o^2(1 + d^{2})/(2k) \geq 1$ such that $g_*$ is a
+valid relative variance, as the equation may otherwise be satisfied for negative
+$g_*$. Since the argument to $W(\cdot)$ is real and negative (if $z_{o}\neq 0$),
+the branches $\lw{-1}(\cdot)$ and $\lw{0}(\cdot)$ both provide solutions that
+can fulfil the equation (assuming the argument is not smaller than $-e^{-1}$
+which would mean that there are no intersections). It must also hold that
+$g_{*} \leq g_{\minBF_{o}} = \max\{z_{o}^{2} - 1, 0\}$ for $g_{*}$ to be a valid
+sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the $g_{*}$
+from~\eqref{eq2:gintersect} can only be computed with the $\lw{-1}(\cdot)$
+branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$ the solution
+$g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the relative prior
+variance $g_{*}$ from~\eqref{eq2:gintersect} into the Bayes factor
+from~\eqref{eq2:BFo}, we obtain the expression for the sceptical Bayes factor
+in~\eqref{eq2:BFsc1}.
+
+\section{Bayes factor with truncated advocacy prior}
+\label{app:BFtrunc}
+For now assume $\that_o > 0$. The marginal likelihood of the replication effect
+estimate $\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
+truncated advocacy prior
+$\HAp \colon \theta \sim \Nor(\that_o, \sigma^2_o) \mathbb{1}_{(0, \infty)}(\theta)$
+is
+\begin{align}
+  f(\that_r \given \HAp)
+  &= \int_{-\infty}^{+\infty} f(\that_r \given \theta) f(\theta \given
+  \HAp) \, \text{d}\theta \nonumber \\
+  &= \int_{-\infty}^{+\infty}
+  \frac{\mathbb{1}_{(0, \infty)}(\theta)}{2\pi\sigma_r\sigma_o\Phi(z_o)}
+  \exp\left\{-\frac{1}{2}\left[\frac{(\that_o - \theta)^2}{\sigma^2_r}
+  + \frac{(\theta - \that_o)^2}{\sigma^2_o}\right]\right\}
+  \, \text{d}\theta \nonumber \\
+  &=
+  \frac{1}{2\pi\sigma_r\sigma_o\Phi(z_o)}
+  \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}\right\}
+   \underbrace{\int_{0}^{+\infty}
+   \exp\left\{-\frac{1}{2}\frac{(\theta - \frac{\that_o/\sigma^2_o +
+       \that_r/\sigma^2_r}{1/\sigma^2_o + 1/\sigma^2_r})^2}{\left(
+     1/\sigma^2_o + 1/\sigma^2_r\right)^{-1}}\right\}
+   \, \text{d}\theta}_{=\sqrt{\frac{2\pi}{1/\sigma^2_o + 1/\sigma^2_r}}
+   % \Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)} \nonumber \\
+  \Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)} \nonumber \\
+   &= \frac{1}{\sqrt{2\pi(\sigma_r^2 + \sigma_o^2)}}
+   \exp\left\{-\frac{1}{2}\frac{(\that_r - \that_o)^2}{\sigma^2_r + \sigma^2_o}
+     % \right\}  \frac{\Phi\left(\frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}\right)}{
+     \right\}  \frac{\Phi\left(\frac{z_o(1 + dc)}{\sqrt{1 + c}}\right)}{
+     \Phi(z_o)}.
+   \label{eq2:truncmarg}
+\end{align}
+With a similar argument one can show that this result holds for any $\that_o$ if
+the last factor in \eqref{eq2:truncmarg} is changed to
+\begin{align*}
+  % \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o + z_r\sqrt{c}}{\sqrt{1 + c}}
+  \frac{\Phi\left\{\text{sign}(z_o) \frac{z_o(1 + dc)}{\sqrt{1 + c}}
+  \right\}}{\Phi\left\{\abs{z_o}\right\}}.
+\end{align*}
+By dividing the marginal likelihood of the replication data under the
+sceptical prior by the marginal likelihood under the truncated advocacy prior,
+the Bayes factor in \eqref{eq2:BFrtrunc} is obtained.
+
+\section{The shrinkage paradox}
+\label{app:shrinkage}
+We want to investigate what happens to the replication success regions as the
+relative variance $c$ and the squared original $z$-value $z_{o}^{2}$ (a monotone
+transformation of the original minimum Bayes factor $\minBF_{o}$) become larger.
+Ignoring the success regions on the wrong side of zero (due to the replication
+paradox), the minimum relative effect estimates $\dmin$ as shown in
+Section~\ref{sec2:comparison} are given by
+
+\begin{align*}
+    &\dmin^{\scriptscriptstyle \BFs} =
+      \frac{1/c + \gy}{\gy - 1} +
+      \sqrt{\frac{\log\left[\frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right]/z_{o}^{2}
+      + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\left[(1/c + \gy)(1/c + 1)\right]}}&
+  &\text{(sceptical Bayes factor)} \\
+    &\dmin^{\scriptscriptstyle \text{2TR}} =
+      \frac{z_{\gamma}}{z_{o}\sqrt{c}}&
+  &\text{(two-trials rule)} \\
+    &\dmin^{\scriptscriptstyle \BFr} =
+      \sqrt{\left[1 + \frac{\log(1 + c) - 2\log \gamma}{z_{o}^{2}}\right] \frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c} &
+  &\text{(replication Bayes factor)} \\
+    &\dmin^{\scriptscriptstyle \ps} =
+      \sqrt{\frac{1/c + 1/(z_{o}^{2}/z_{\gamma}^{2} - 1)}{z_{o}^{2}/z_{\gamma}^{2}}}&
+  &\text{(sceptical $p$-value)} \\
+\end{align*}
+where for the sceptical Bayes factor it was assumed that $\gy > 1$ (otherwise
+the plus before the square root term needs to be replaced by a minus).
+
+For the sceptical Bayes factor, we obtain
+\begin{align*}
+  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFs} =
+  \frac{\gy}{\gy - 1} +
+    \sqrt{\frac{\log\left[\frac{1}{\gy(1 + \gy)}\right]/z_{o}^{2}
+    + \frac{\gy}{1 + \gy} + \frac{1}{1 - \gy}}{(1 - \gy)/\gy}}&
+  &\text{and}&
+  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFs} =
+    \sqrt{\frac{1/c + 1}{c}} - \frac{1}{c}&
+\end{align*}
+where for the second limit we used that $\lim_{z_{o}^{2} \to \infty} \gy = 0$
+for a fixed level $\gamma$ (Appendix~\ref{appendix:ssrv}). So the sceptical
+Bayes factor does not suffer from any form of the shrinkage paradox. The limits
+for the two-trials rule are given by
+\begin{align*}
+  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
+  &\text{and}&
+  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \text{2TR}} = 0&
+\end{align*}
+so the two-trials rule suffers from both forms of the shrinkage paradox. For the
+sceptical $p$-value, we obtain
+\begin{align*}
+  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \ps} =
+    \sqrt{\frac{z_{\gamma}^{2}}{z_{o}^{2}(z_{o}^{2}/z_{\gamma}^{2} - 1)}}&
+  &\text{and}&
+  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \ps} = 0&
+\end{align*}
+thus, the sceptical $p$-value suffers from the shrinkage paradox at original.
+Finally, the limits for the replication Bayes factor are
+\begin{align*}
+  &\lim_{c \to \infty} \dmin^{\scriptscriptstyle \BFr} = 0 &
+  &\text{and}&
+  &\lim_{z_{o}^{2}\to \infty} \dmin^{\scriptscriptstyle \BFr} =
+    \sqrt{\frac{1/c + 1}{c}} - \frac{1/c + 1}{1 + c}&
+\end{align*}
+which means that the replication Bayes factor suffers from the shrinkage paradox
+at replication.
+
+\section{Probability of replication success with the sceptical Bayes factor}
+\label{app:powerBFs}
+Conditional on the original study, the probability for replication success at
+level $\gamma$ is given by the probability of \eqref{eq2:RSCond-d}. This event
+involves $z_r = dz_o \sqrt{c}$ as the only random quantity if the original study
+has been completed. Assuming a normal distribution
+\begin{align*}
+  z_r \given z_o, c \sim \Nor(\mu_{z_r}, \sigma^2_{z_r})
+\end{align*}
+which may depend on $z_o$ and $c$ encompasses the typical scenarios under which
+one would want to compute the probability for replication success. For example,
+under the null hypothesis ($H_{0} \colon \theta = 0$), we have $\mu_{z_r} = 0$
+and $\sigma^2_{z_r} = 1$. For conditional power we assume the underlying effect
+size equals the original effect estimate ($\theta = \that_o$) and therefore
+$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1$. Finally, predictive power
+is obtained by using the predictive distribution based on the advocacy prior
+($\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$) and thus
+$\mu_{z_r} = z_o \sqrt{c}$ and $\sigma^2_{z_r} = 1 + c$.
+
+Applying some algebraic manipulations to \eqref{eq2:RSCond-d}, the
+probability for replication success at level $\gamma$ can be computed by
+\begin{align}
+  \label{eq2:powerBFs}
+  \Pr\left(\BFs \leq \gamma \given z_o, c\right) =
+  \begin{cases}
+    \Pr(\chi^2_{1,\lambda} \geq  A/[B \sigma^2_{z_r}])
+    & \text{for} ~ \gy < 1 \\
+    \Phi(\text{sign}(z_o) \left\{\mu_{z_r} - D\right\}/\sigma_{z_r})
+    & \text{for} ~ \gy = 1 \\
+    \Pr(\chi^2_{1,\lambda} \leq A/[B \sigma^2_{z_r}])
+    & \text{for} ~ \gy > 1
+  \end{cases}
+\end{align}
+with non-centrality parameter $\lambda = (\mu_{z_r} - M)^2/\sigma^2_{z_r}$
+and
+\begin{align*}
+  A &= \log \left\{ \frac{1/c + 1}{(1/c + \gy)(1 + \gy)}\right\} +
+  z_o^2 \left\{\frac{\gy}{1 + \gy} + \frac{1}{1 - \gy} \right\}, \\
+  B &= \frac{1 - \gy}{(1 + c\gy)(1/c + 1)}, \\
+  D &= \frac{z_o^2 \{1/2 + 1/(1/c + 1)\} - \log 2}{2 z_o \sqrt{c}} (1 + c) \\
+  M &= \frac{z_o(1 + c\gy)}{\sqrt{c}(\gy - 1)}.
+\end{align*}
+The probability is zero, if the original $z$-value $|z_o|$ is not large enough
+such that the sufficiently sceptical relative prior variance $\gy$ can be
+computed for level $\gamma$ with \eqref{ggamma}.
+
+\section{Probability of replication success with the replication Bayes factor}
+\label{app:powerBFr}
+The probability of $\BFr \leq \gamma$ is equivalent to the probability of
+\begin{align}
+  \label{eq2:BFrsuccess}
+  \log(1 + c) - z_{r}^{2} + \frac{(z_{r} - z_{o}\sqrt{c})^{2}}{1 + c}
+  \leq  2 \log \gamma
+\end{align}
+Applying some algebraic manipulations to \eqref{eq2:BFrsuccess} and assuming a
+normal distribution for $z_{r}$ as in Appendix~\ref{app:powerBFs} leads to
+\begin{align*}
+  \Pr\left(\BFr \leq \gamma \given z_o, c\right) =
+  \Pr\left(\chi^2_{1,\lambda} \geq \left\{z_{o}^{2} + \log(1 + c) - \log \gamma^{2}
+  \right\} [1 + 1/c] / \sigma^2_{z_r}\right)
+\end{align*}
+with non-centrality parameter $\lambda = (\mu_{z_r} + z_{o}/\sqrt{c})^2/\sigma^2_{z_r}$.
+
+\end{subappendices}
+
+% Bibliography
 \bibliographystyle{apalikedoiurl}

### 2022-12-05 abstract.tex
table formatting

@@
 
-The first and largest part of this thesis consists of three extensions to a
-recently proposed reverse-Bayes method for quantifying replication success. The
-key idea of the method is to challenge the data from the original study with a
-sceptical prior so that the resulting posterior no longer provides evidence for
-the finding from the study. Replication success is then achieved if there is
-conflict between the sceptical prior and the replication data. The procedure can
-be summarized in a single quantitative measure, termed the sceptical $p$-value.
+Possible answers to this question are given in the first and largest part of
+this thesis. It consists of three extensions to a recently proposed
+reverse-Bayes method for quantifying replication success. The key idea of the
+method is to challenge the data from the original study with a sceptical prior
+so that the resulting posterior distribution is no longer ``significant''. The
+goal of the replication study is then to show that the sceptical prior is
+unrealistic, and replication success is achieved if there is sufficient conflict
+between the prior and the replication data. The procedure can be summarized in a
+single quantitative measure, termed the sceptical $p$-value.
 % extension 1
@@
 some situations the sceptical $p$-value may indicate replication success even
-though the effect estimate from the replication is arbitrarily smaller than
-effect estimate from the original study. % , which cannot happen with the sceptical
+though the effect estimate from the replication is arbitrarily smaller than the
+effect estimate from the original
+study. % , which cannot happen with the sceptical
 % Bayes factor.
@@
 The second part of this thesis also deals with reverse-Bayes methods, but with a
-broader scope of applications than replication studies as in the first part. The
-reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
-forgotten. To increase awareness and show potential use cases, reverse-Bayes
-history and methods are summarized in a comprehensive review. The review
-includes also some new results on connections between revere-Bayes methods and
-meta-analysis. % Finally, a
+broader scope of applications than replication studies. The reverse-Bayes idea
+was first proposed in the 1950s, but it has mostly been forgotten. To increase
+awareness and show potential use cases, reverse-Bayes history and methods are
+summarized in a comprehensive review. The review includes also some new results
+on connections between reverse-Bayes methods and meta-analysis. % Finally, a
 % commentary paper on a recently proposed reverse-Bayes method draws connections
@@
 method can easily be presented as superior over established competitor methods
-if questionable research practices are employed.
+if questionable research practices are employed. Finally, several
+recommendations are given to alleviate these issues, most importantly the need
+for simulation protocols.
 

### 2022-12-05 intro.Rnw
change paper order 1 and 2
table formatting

@@
   ``\emph{Confirmation comes from repetition}. Any attempt to avoid this statement leads at least to failure and more probably to destruction.'' \\
-  \hfill \citet[p. 84]{Tukey1969}
+  \hfill J.W. \citet[p. 84]{Tukey1969}
 \end{tabular}
@@
 questions is of high importance to scientists, decision makers, and the general
-population. However, because any study result comes with uncertainty we can
-never know for sure.
+population. However, because every study result is subject to uncertainty, we
+can never know for sure.
 
@@
 occurred merely by chance. For this reason, ``successful'' replication is often
-a requirement, for example, for acceptance of newly proposed scientific theories
-(\eg{} a new physical model) or the implementation of policies based on
+a requirement, for instance, for acceptance of newly proposed scientific
+theories (\eg{} a new physical model) or the implementation of policies based on
 scientific knowledge (\eg{} market approval of a drug). The results from
@@
 science -- publications, citations, and grant money -- are typically easier to
-acquire by conducting novel research. This is because until relatively recently,
-many scientific journals put most emphasis on ``innovation'' thereby lowering
-the chance of publication for replication studies \citep{Makel2012, Martin2017,
+acquire by conducting novel research. This is because until recently, most
+scientific journals hardly published any replication studies as the emphasis was
+on ``innovation'' rather than on ``repetition'' \citep{Makel2012, Martin2017,
   Coiera2021}. To build a successful career, researchers thus often had no other
 choice than to concentrate their efforts on producing novel and eye-catching
-research results.
+research results \citep{Binswanger2014, Moher2018}.
 
@@
 results than their original counterparts, and the replicability of research
-findings is surprisingly low (whatever replicability means will soon be
-discussed in more detail). This realization led many to declare science as being
-in a ``replication crisis''. Debates arose about whether or not the crisis
+findings is surprisingly low (how precisely replicability is defined will soon
+be discussed in more detail). This realization led many to declare science as
+being in a ``replication crisis''. Debates arose about whether or not the crisis
 really existed and who or what was to blame \citep{Gilbert2016, Amrhein2019}.
@@
 \begin{figure}[!htb]
-<< "google-scholar-graph", fig.height = 2.5 >>=
-## Data gathered on October 18 2022
-searchTerm <- "Replication Study"
-searchDate <- as.Date(x = "2022-10-18", format = "%Y-%m-%d", tz = "GMT")
-searchDateFormat <- format(searchDate, format = "%B %d %Y")
-resultsAnytime <- 114000
-scholarDF <- data.frame(year = seq(2022, 1990, -1),
-                        results = c(4530, 11400, 13600, 12200, 11300, 10700,
-                                    9880, 9220, 8660, 8200, 7500, 6700, 6040,
-                                    5370, 4680, 3890, 3380, 3070, 2790, 2520,
-                                    2310, 2190, 2120, 2020, 1920, 1840, 1730,
-                                    1490, 1270, 1230, 1140, 1070, 970),
-                        study = c(156000, 487000, 1820000, 959000, 2360000,
-                                  675000, 3000000, 688000, 3150000, 512000,
-                                  3630000, 451000, 3650000, 396000, 3680000,
-                                  389000, 3890000, 375000, 3950000, 336000,
-                                  4160000, 364000, 4240000, 385000, 3470000,
-                                  377000, 3120000, 335000, 2620000, 376000,
-                                  2440000, 317000, 2220000))
+<< "google-scholar-graph", fig.height = 3.5 >>=
+## ## Data gathered on October 18 2022
+## searchTerm <- "Replication Study"
+## searchDate <- as.Date(x = "2022-10-18", format = "%Y-%m-%d", tz = "GMT")
+## searchDateFormat <- format(searchDate, format = "%B %d %Y")
+## resultsAnytime <- 114000
+## scholarDF <- data.frame(year = seq(2022, 1990, -1),
+##                         results = c(4530, 11400, 13600, 12200, 11300, 10700,
+##                                     9880, 9220, 8660, 8200, 7500, 6700, 6040,
+##                                     5370, 4680, 3890, 3380, 3070, 2790, 2520,
+##                                     2310, 2190, 2120, 2020, 1920, 1840, 1730,
+##                                     1490, 1270, 1230, 1140, 1070, 970),
+##                         study = c(347000, 459000, 1710000, 938000, 2360000,
+##                                   675000, 3000000, 688000, 3150000, 512000,
+##                                   3630000, 451000, 3650000, 396000, 3680000,
+##                                   389000, 3890000, 375000, 3950000, 336000,
+##                                   4160000, 364000, 4240000, 385000, 3470000,
+##                                   377000, 3120000, 335000, 2620000, 376000,
+##                                   2440000, 317000, 2220000))
+## ## plot data
+## ggplot(data = filter(scholarDF, year < 2022),
+##        aes(x = year, y = results)) +
+##     geom_segment(aes(xend = year, yend = 0), alpha = 0.2, size = 0.4) +
+##     geom_point() +
+##     ## scale_y_continuous(breaks = seq(0, 15000, 2500)) +
+##     scale_x_continuous(breaks = seq(1990, 2020, 5)) +
+##     ## scale_y_log10() +
+##     labs(x = "Year", y = paste0('Number of results \nfor "', searchTerm, '"')) +
+##     theme_bw() +
+##     theme(panel.grid.minor = element_blank(),
+##           panel.grid.major.x = element_blank()## ,
+##           ## panel.grid.major.y = element_line(colour = "grey", linetype = "dashed")
+##           )
+
+WebofScienceDF <- data.frame(year = seq(2022, 1990, -1),
+                             results = c(139, 144, 121, 137, 111, 80,
+                                         89, 63, 68, 92, 63, 60, 39,
+                                         39, 41, 30, 21, 20, 19, 25,
+                                         15, 9, 13, 20, 19, 16, 14,
+                                         8, 17, 13, 21, 5, 12),
+                             study = c(235996, 272173, 245994, 230009, 207625,
+                                       195012, 174800, 164635, 158745,
+                                       184473, 138785, 128779, 116890, 111229,
+                                       102231, 95143, 86691, 83132, 94432,
+                                       79807, 70388, 53983, 54893, 53480,
+                                       51744, 51898, 50070, 46826, 44591,
+                                       43097, 42816, 43277, 43277)) %>%
+    mutate(proportion = results/study,
+           se = sqrt(proportion*(1 - proportion)/study))
 
 ## plot data
-ggplot(data = filter(scholarDF, year < 2022),
-       aes(x = year, y = results)) +
-    geom_segment(aes(xend = year, yend = 0), alpha = 0.2, size = 0.4) +
-    geom_point() +
-    ## scale_y_continuous(breaks = seq(0, 15000, 2500)) +
+plotA <- ggplot(data = WebofScienceDF, aes(x = year, y = results)) +
+    geom_segment(aes(xend = year, yend = 0), alpha = 0.2, linewidth = 0.5) +
+    geom_point(size = 0.7) +
     scale_x_continuous(breaks = seq(1990, 2020, 5)) +
-    ## scale_y_log10() +
-    labs(x = "Year", y = paste0('Number of results \nfor "', searchTerm, '"')) +
+    lims(y = c(0, 160)) +
+    labs(x = "Year", y = 'Number of results for "replication study"') +
     theme_bw() +
     theme(panel.grid.minor = element_blank(),
-          panel.grid.major.x = element_blank()## ,
-          ## panel.grid.major.y = element_line(colour = "grey", linetype = "dashed")
-          )
+          panel.grid.major.x = element_blank())
+plotB <- ggplot(data = WebofScienceDF, aes(x = year, y = proportion)) +
+    geom_segment(aes(y = proportion - 2*se, yend = proportion + 2*se, xend = year),
+                 size = 0.5, alpha = 0.4) +
+    geom_point(size = 0.7) +
+    scale_x_continuous(breaks = seq(1990, 2020, 5), name = "Year") +
+    scale_y_continuous(labels = scales::percent,
+                       name = bquote("Proportion (" %+-% "2SE)")) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank(),
+          panel.grid.major.x = element_blank())
+
+ggarrange(plotA, plotB, ncol = 2)
 @
-\caption{Number of results per year for search term ``\Sexpr{searchTerm}'' on
-  Google Scholar. The search was conducted on 18 October 2022.}
+\caption{Yearly number of results for search term ``replication study'' on Web
+  of Science (left), and number of results normalized by the number of results
+  for the search term ``study'' (right). The search was conducted on 2 December
+  2022.}
 \label{fig:scholar}
@@
 outcome. Similarly, digital infrastructure platforms, such as Zenodo
-(\url{https://zenodo.org}) or the Open Science Framework
-(\url{https://osf.io}), were created to facilitate preregistration, preprints,
-code and data sharing, all of which have substantially increased over the last
-decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of conducting
+(\url{https://zenodo.org}) or the Open Science Framework (\url{https://osf.io}),
+were created to facilitate preregistration, preprints, code and data sharing,
+all of which have substantially increased over the last decade
+\citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of conducting
 replication studies has also gained popularity. Several academic journals and
 funders are now explicitly promoting replication research \citep{NWO2016,
-  NSL2018, Nature2022}. Figure~\ref{fig:scholar} illustrates this trend via the
-yearly number of results for the search term ``\Sexpr{searchTerm}'' on Google
-Scholar over the last three decades. We see that the numbers have been rapidly
-growing, especially after the mid 2000s, with a minor drop in 2021 (perhaps
-because of research slowing down due to the COVID-19 pandemic).
+  NSL2018, Nature2022}. Figure~\ref{fig:scholar} (left) illustrates this trend
+by the yearly number of results for the search term ``replication study''
+obtained from the search engine Web of Science. The numbers have been rapidly
+growing, especially since the mid-2000s. This trend could possibly be explained
+by the fact that more research results are published each year but also when the
+numbers are normalized by the number of results for the search term ``study'',
+the increasing trend is still visible.
 
@@
     $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and
-    \textit{p}-values are based on the normality assumption.}
+    \textit{p}-values are based on the assumption that the effect estimate
+    $\that$ is normally distributed around the unknown effect size $\theta$ with
+    (known) variance equal to the squared standard error $\sigma^{2}$.}
   \label{tab:meta}
@@
 associated standard error $\sigma$ represents the statistical uncertainty of the
-estimate. Under the assumption of (asymptotic) normality, confidence intervals
-for $\theta$ and $p$-values for testing the null hypothesis
-$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
+estimate.\footnote{Typically, the available standard error $\sigma$ is only an
+  estimate of the true standard error. However, in most parts of this thesis it
+  will be assumed that $\sigma$ corresponds to the true standard error. This is
+  the same assumption as in ordinary fixed-effects/random-effects meta-analysis,
+  and reasonable if the sample size of the studies is not too small.} Under the
+assumption of (asymptotic) normality, confidence intervals for $\theta$ and
+$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
+computed as shown in Table~\ref{tab:meta}.
 
@@
                    & \\
-    Prediction interval ($Q$-test) & The replication effect estimate is contained with its
+    Prediction interval ($Q$-test) & The replication effect estimate is contained in its
                                      $(1 - \alpha)$ prediction interval
@@
 not required to show the same direction as this is taken into account by the
-$p$-values. Some replication projects \citep{Opensc2015, Errington2021} also
-defined replication success via simultaneous non-significance of original and
-replication study ($p_{o} > \alpha$ and $p_{r} > \alpha$). However, with this
-definition ``replication success'' can almost always be achieved by conducting
-original and replication study with very few samples so that the $p$-values are
-large. The approach is also logically questionable as it could be seen as an
-instance of the ``absence of evidence fallacy'' \citep{Altman1995} meaning the
-failure to find evidence against the null hypothesis is erroneously interpreted
-as evidence for the null hypothesis. Meta-analytic extensions of the
-significance approach define replication success by significance of a combined
-effect estimate.\footnote{The meta-analytic approach can also be given a
-  Bayesian interpretation: A flat prior distribution for the underlying effect
-  size $\theta$ is updated by the data from original and replication study.
-  Replication success defined by a meta-analytic $p$-value being smaller than
-  $\alpha$ is then equivalent to replication success via a Bayesian posterior
-  probability $\Pr(\theta > 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$,
-  respectively, $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$
-  depending on the direction of the combined estimate.} Typically, the
-assumption of a common underlying effect size is seen as reasonable so that
-fixed-effect meta-analysis is used for pooling. Random-effects meta-analysis has
-primarily been used if more than one replication study of the same original
-study are conducted since replicators are often interested in understanding
-between-replication heterogeneity \citep[\eg{} in][]{Klein2018}.
+one-sided $p$-values. Some replication projects \citep{Opensc2015,
+  Errington2021} also defined replication success via simultaneous
+non-significance of original and replication study ($p_{o} > \alpha$ and
+$p_{r} > \alpha$). However, with this definition ``replication success'' can
+almost always be achieved by conducting original and replication study with very
+few samples so that the $p$-values are large. The approach is also logically
+questionable as it could be seen as an instance of the ``absence of evidence
+fallacy'' \citep{Altman1995} meaning the failure to find evidence against the
+null hypothesis is erroneously interpreted as evidence for the null hypothesis.
+Meta-analytic extensions of the significance approach define replication success
+by significance of a combined effect estimate.\footnote{The meta-analytic
+  approach can also be given a Bayesian interpretation: A flat prior
+  distribution for the underlying effect size $\theta$ is updated by the data
+  from original and replication study. Replication success defined by a
+  meta-analytic $p$-value being smaller than $\alpha$ is then equivalent to
+  replication success via a Bayesian posterior probability
+  $\Pr(\theta > 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$, respectively,
+  $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$, depending on the
+  direction of the combined estimate.} Typically, the assumption of a common
+underlying effect size is seen as reasonable so that fixed-effect meta-analysis
+is used for pooling. Random-effects meta-analysis has primarily been used if
+more than one replication study of the same original study are conducted since
+replicators are often interested in understanding between-replication
+heterogeneity \citep[\eg{} in][]{Klein2018}.
 
@@
 \subsubsection{Example ``Reproducibility Project: Cancer Biology''}
-I will now illustrate the assessment of replicability on data from the
-Reproducibility Project: Cancer Biology \citep{Errington2021}. This large-scale
-project attempted to replicate 53 landmark studies from the field of cancer
-biology \citep[and would perhaps therefore better be named ``Replication
+I will now illustrate the assessment of replication success on data from the
+``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
+large-scale project attempted to replicate 53 landmark studies from the field of
+cancer biology \citep[and would perhaps therefore better be named ``Replication
 Project'', see][]{Goodman2016}. In the end, only 23 of the 53 studies could be
@@
 \begin{figure}[!htb]
-<< "RPCB-graph", fig.height = 3.25 >>=
+<< "RPCB-graph", fig.height = 3.5 >>=
+
+## function to format CI
 ciFormat. <- function(lower, upper) {
-    paste0("[", format(round(lower, 2), nsmall = 2),
-           ", ", format(round(upper, 2), nsmall = 2), "]")
+    paste0("[", format(signif(lower, 2), nsmall = 2),
+           ", ", format(signif(upper, 2), nsmall = 2), "]")
 }
 ciFormat <- Vectorize(FUN = ciFormat.)
-pFormat. <- function(p) {
+
+## function to format p-value
+pFormat. <- function(p, digits = 2, dollar = FALSE, phantom = FALSE) {
     if (is.na(p)) {
-        return(NA)
-    } else if (p > 0.0001) {
-        return(as.character(signif(p, 2)))
+        out <- NA
     } else {
-        return("< 0.0001")
+        if (p > 0.0001) {
+            out <- as.character(signif(p, digits = digits))
+            if (phantom) out <- paste0("\\phantom{<~}", out)
+        } else {
+            out <- "< 0.0001"
+        }
+        if (dollar) {
+            out <- paste0("$", out, "$")
         }
     }
+    return(out)
+}
 pFormat <- Vectorize(FUN = pFormat.)
+
+## function to format (relative) effect estimate
+dFormat. <- function(x, digits = 2, phantom = FALSE, dollar = FALSE) {
+    if (is.na(x)) {
+        out <- NA
+    } else {
+        out <- as.character(signif(x, digits = digits))
+        if (phantom && (x >= 0)) {
+           out <- paste0("\\phantom{-}", out)
+        }
+        if (dollar) out <- paste0("$", out, "$")
+    }
+    return(out)
+}
+dFormat <- Vectorize(FUN = dFormat.)
+
+## function to color code numerical value in LaTeX table based on threshold
+tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "nicegreen",
+                         col2 = "red") {
+    if (is.na(x)) {
+        out <- NA
+    } else {
+        if (x < threshold) col <- col1
+        else col <- col2
+        out <- paste0("\\textcolor{", col, "}{",
+                      outFun(x, dollar = TRUE, phantom = TRUE), "}")
+    }
+    return(out)
+}
+tableFormat <- Vectorize(FUN = tableFormat., vectorize.args = "x")
+
 za <- qnorm(p = 0.975)
@@
            pQ = pchisq(q = Q, df = 1, lower.tail = FALSE),
-           dFormat = ifelse(d > 1,
-                            paste0("\\textcolor{nicegreen}{$", round(d, 2),
-                                   "$}"),
-                            paste0("\\textcolor{red}{$", round(d, 2), "$}")),
+           dFormat = tableFormat(x = d, outFun = dFormat,
+                                 threshold = 1, col1 = "red", col2 = "nicegreen"),
            cioL = smdo - za*so,
@@
            id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
-           po2Format = ifelse(po2 < 0.05,
-                              paste0("\\textcolor{nicegreen}{", pFormat(po2),
-                                     "}"),
-                              paste0("\\textcolor{red}{", pFormat(po2), "}")),
-           pr2Format = ifelse(pr2 < 0.05,
-                              paste0("\\textcolor{nicegreen}{", pFormat(pr2),
-                                     "}"),
-                              paste0("\\textcolor{red}{", pFormat(pr2), "}")),
-           pm2Format = ifelse(pm2 < 0.05,
-                              paste0("\\textcolor{nicegreen}{", pFormat(pm2),
-                                     "}"),
-                              paste0("\\textcolor{red}{", pFormat(pm2), "}")),
-           pQFormat = ifelse(pQ > 0.05, paste0("\\textcolor{nicegreen}{", pFormat(pQ),
-                                               "}"),
-                             paste0("\\textcolor{red}{", pFormat(pQ), "}")),
-           smdoFormat = paste("$", format(round(smdo, 2), nsmall = 2),
+           po2Format = tableFormat(x = po2),
+           pr2Format = tableFormat(x = pr2),
+           pm2Format = tableFormat(x = pm2),
+           pQFormat = tableFormat(x = pQ),
+           smdoFormat = paste("$", dFormat(smdo), "~",
                               ciFormat(lower = cioL, upper = cioU), "$"),
-           smdrFormat = paste("$", format(round(smdr, 2), nsmall = 2),
+           smdrFormat = paste("$", dFormat(smdr), "~",
                               ciFormat(lower = cirL, upper = cirU), "$"),
-           smdmFormat = paste("$", format(round(smdm, 2), nsmall = 2),
+           smdmFormat = paste("$", dFormat(smdm), "~",
                               ciFormat(lower = cimL, upper = cimU), "$"),
@@
 rpcb$ps2Format <- NA
-rpcb$ps2Format[ind] <- ifelse(rpcb$ps2[ind] < 0.05, paste0("\\textcolor{nicegreen}{",
-                                                           pFormat(rpcb$ps2[ind]),
-                                                           "}"),
-                              paste0("\\textcolor{red}{", pFormat(rpcb$ps2[ind]), "}"))
+rpcb$ps2Format <- tableFormat(x = rpcb$ps2)
 
@@
 level. Specifically, from the
-\Sexpr{sum(rpcbWithoutNA$po2 < 0.05)} effects which were significant in the original study only \Sexpr{ sum(rpcbWithoutNA$po2 < 0.05
-  & rpcbWithoutNA$pr2 < 0.05 & rpcbWithoutNA$d > 0)} were also significant in
-the replication study (in the same direction).
+\Sexpr{sum(rpcbWithoutNA$po2 < 0.05)} effects which were significant in the original study only \Sexpr{ sum(rpcbWithoutNA$po2
+  < 0.05 & rpcbWithoutNA$pr2 < 0.05 & rpcbWithoutNA$d > 0)} were also
+significant in the replication study (in the same direction).
 
 \begin{figure}[!htb]
-<< "RPCB-table1", results = "asis", fig.height = 4.8 >>=
+<< "RPCB-table1", results = "asis", fig.height = 5.5 >>=
 ## show number of successes
@@
   $\alpha = \Sexpr{round(100*alpha, 2)}\%$ and a relative effect size threshold
-  of $d_{\text{min}} = \Sexpr{dmin}$ are used for replication success (green).}
+  of $d_{\text{min}} = \Sexpr{dmin}$ are used for replication success.}
 \label{fig:upset}
@@
   \label{tab:RPCB}
-% \resizebox{1\textwidth}{!}{%
+\resizebox{1\linewidth}{!}{%
 << "RPCB-table2", results = "asis" >>=
@@
                           "$\\that_o$ [95\\% CI]",
-                          ## "$\\sigma_o$",
                           "$\\that_r$ [95\\% CI]",
@@
                           "$d$", #"$\\that_r/\\that_o$",
-                          ## "$\\sigma_r$",
                           "$p_o$",
@@
                           )
+colnames(rpcbXtable) <- paste0("\\multicolumn{1}{c}{", colnames(rpcbXtable), "}")
 print(rpcbXtable, booktabs = TRUE, floating = FALSE, include.rownames = TRUE,
-      sanitize.text.function = function(x) {x},
+      sanitize.text.function = function(x){x},
       size = "small")
 @
-% %
-% }
+%
+}
 \end{table}
@@
 observed data. The central quantity for doing so is the distribution of the
-parameters conditional on the data, called the \emph{posterior distribution}. It
-can be obtained from Bayes' theorem,
+parameters conditional on the observed data, called the \emph{posterior
+  distribution}. It can be obtained from Bayes' theorem,
 \begin{align*}
@@
 Figure~\ref{fig:RBillustration} illustrates the derivation of the sufficiently
-sceptical prior variance for an original study included in the Reproducibility
-Project: Cancer Biology with standardized mean difference effect estimate
+sceptical prior variance for an original study included in the ``Reproducibility
+Project: Cancer Biology'' with standardized mean difference effect estimate
 $\that_{o} = \Sexpr{round(to, 2)}$ and standard error
@@
   = \Pr\left\{f(\text{data} \given \text{M}) <
-  f(\text{observed data} \given \text{M})\right\}.
+  f(\text{data} = \text{observed data} \given \text{M}) \given \text{M}\right\}.
   \label{eq:pppval}
@@
   \text{PPR}_{\text{Box}}
-  = \frac{f(\text{observed data} \given \text{M}_{1})}{f(\text{observed data} \given \text{M}_{2})},
+  = \frac{f(\text{data} = \text{observed data} \given \text{M}_{1})}{
+  f(\text{data} = \text{observed data} \given \text{M}_{2})},
 \end{align*}
@@
 % $p_{\text{Box}} = \Sexpr{pboxFormat2[3]}$),
-so that the third replication would be successful (since the prior predictive
+so that the third replication would be successful at the less convincing level
+\mbox{$\alpha = \Sexpr{round(alpha2*100, 2)}\%$} (since the prior predictive
 $p$-value would be
@@
 
-The results from the Reproducibility Project: Cancer Biology in
+The results from the ``Reproducibility Project: Cancer Biology'' in
 Table~\ref{tab:RPCB} illustrate these two properties. The third study fails to
@@
 (\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value
-is therefore only $p_{\text{S}} = 0.25$, indicating hardly any replication
-success.
+is therefore only $p_{\text{S}} = 0.25$, indicating hardly any evidence for
+replication success.
 
@@
 sceptical $p$-value, power and sample size calculations) can be found in the
-original article by \citet{Held2020}. Furthermore, the sceptical $p$-value and
-related methods are implemented in the R package \texttt{ReplicationSuccess}
-available on CRAN
+original article by \citet{Held2020}. The sceptical $p$-value and related
+methods are implemented in the R package \texttt{ReplicationSuccess} available
+on CRAN
 (\url{https://cran.r-project.org/package=ReplicationSuccess}). % However, the
@@
 replication studies. The second part (Paper IV and V) revolves around
-reverse-Bayes methodology in general. % Paper IV is a review paper about
+reverse-Bayes methodology with a broader scope of applications than replication
+studies. % Paper IV is a review paper about
 % reverse-Bayes methodology and Paper V is a short comment on another article
@@
   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \href{https://doi.org/10.1214/21-AOAS1502}{doi:~10.1214/21-AOAS1502}.}
+  doi:\href{https://doi.org/10.1214/21-AOAS1502}{10.1214/21-AOAS1502}.}
 
@@
     Methodology)}, 2022, 84(3), 879--911.
-  \href{https://doi.org/10.1111/rssb.12491}{doi:~10.1111/rssb.12491}.}
+  doi:\href{https://doi.org/10.1111/rssb.12491}{10.1111/rssb.12491}.}
 
@@
 % ``Lambert W function'' \citep{Corless1996}.
-The method is illustrated on data from the Social Sciences Replication Project
-\citep{Camerer2018}, and implemented in the R package \texttt{BayesRep}
-(\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).
+The method is illustrated on data from the ``Social Sciences Replication
+Project'' \citep{Camerer2018}, and implemented in the R package
+\texttt{BayesRep} (\url{https://gitlab.uzh.ch/samuel.pawel/BayesRep}).
 
@@
   2022. arXiv preprint.
-  \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:~10.48550/arXiv.2211.02552}.}
+  doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}.}
 
 An important aspect in the design of replication studies is determining their
-sample size. How exactly the sample size should be determined depends on the
-method used for analyzing the replication data. Various approaches have been
-proposed for doing so which are specifically tailored to certain analysis
+sample size. How exactly the sample size should be determined depends on which
+method is used for the analysis of the replication data. Various approaches have
+been proposed for doing so which are specifically tailored to certain analysis
 methods. In this article, we provide a general Bayesian framework which applies
@@
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
-   \href{https://doi.org/10.1002/jrsm.1538}{doi:~10.1002/jrsm.1538}.}
+   doi:\href{https://doi.org/10.1002/jrsm.1538}{10.1002/jrsm.1538}.}
 
@@
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
-  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:~10.1186/s12874-022-01635-4}.}
+  doi:\href{https://doi.org/10.1186/s12874-022-01635-4}{10.1186/s12874-022-01635-4}.}
 
@@
   2022. arXiv preprint.
-  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:~10.48550/arXiv.2203.13076}.}
+  doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}.}
 
@@
 The first authorship of this manuscript is shared with L. Kook. I had the idea
-to invent a ``mock-method'' and use questionable research practices that make it
+to invent a novel method and use questionable research practices that make it
 seem superior, to draw attention to the low standards in methodological
 research. I then wrote a first draft of the manuscript and proposed the idea to
-L. Kook and K. Reeve. L. Kook and myself then came up with the penalized
-regression method ``AINET'' and started writing the simulation protocol. L. Kook
-took lead in developing the R package \texttt{ainet}
+L. Kook and K. Reeve. L. Kook and myself then came up with the novel regression
+method ``AINET'' and started writing the simulation protocol. L. Kook took lead
+in developing the R package \texttt{ainet}
 (\url{https://github.com/LucasKook/ainet}) and simulation study code. Myself, L.
@@
 \section*{Data and software}
-The CC-By 4.0 licensed data from the Reproducibility Project: Cancer Biology
+The CC-By 4.0 licensed data from the ``Reproducibility Project: Cancer Biology''
 \citep{Errington2021} were downloaded from

### 2022-12-05 paper1.tex
table formatting

@@
   level with $\alpha = 0.025$. }
-\label{fig2:fig6}
+\label{fig1:fig6}
 \end{figure}
 
-Figure~\ref{fig2:fig6} displays the relative effect size $d$ versus the original
+Figure~\ref{fig1:fig6} displays the relative effect size $d$ versus the original
 $p$-value $p_o$ for each study pair and stratified by project. Note that one
@@
 the same conclusion, only six replications show conflicting results. They are
-highlighted with diamonds in Figure~\ref{fig2:fig6} and their characteristics are
+highlighted with diamonds in Figure~\ref{fig1:fig6} and their characteristics are
 summarised in Table~\ref{tbl:discrep}.
@@
 This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
-the golden level as described in Section \ref{sec2:goldenthresh}. We may also
+the golden level as described in Section \ref{sec1:goldenthresh}. We may also
 choose a different value for the limiting relative effect size $\dinfty$ at
 $\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
-$\alpha'$ as given in \eqref{eq2:alphaPrime}. Figure \ref{fig2:fig7} compares the
+$\alpha'$ as given in \eqref{eq1:alphaPrime}. Figure \ref{fig1:fig7} compares the
 proportion of successful replications with the replication success approach for
@@
 the replication success approach. The proportion of studies where both methods
-are successful (also shown in Figure \ref{fig2:fig7}) is then smaller than the
+are successful (also shown in Figure \ref{fig1:fig7}) is then smaller than the
 proportion of successful replications with either one of the two methods. The
@@
   two-trials rule (2TR).}
-\label{fig2:fig7}
+\label{fig1:fig7}
 \end{figure}
 
-\section{Discussion}\label{sec2:discussion}
+\section{Discussion}\label{sec1:discussion}
 In this paper, we have expanded on the replication success approach introduced
@@
 based on the result of the original study \citep{Anderson2017}. Power
-calculations as shown in Figure \ref{fig2:fig3} can then be inverted to determine
+calculations as shown in Figure \ref{fig1:fig3} can then be inverted to determine
 the appropriate sample size of the replication study. We can also invert
-equation \eqref{eq2:res} to obtain the required replication sample size based on
+equation \eqref{eq1:res} to obtain the required replication sample size based on
 the specification of the minimum relative effect size $\dmin$ to achieve
@@
 formulated in terms of the minimum relative effect size by inverting equation
-\eqref{eq2:dSig}. We will report on a detailed comparison of the different
+\eqref{eq1:dSig}. We will report on a detailed comparison of the different
 approaches in future work.

### 2022-12-05 thesis.Rnw
change paper order 1 and 2
table formatting

@@
                message = FALSE,
-               cache = TRUE,
+               cache = FALSE,
                eval = TRUE)
@@
 ## should sessionInfo be printed at the end?
-Reproducibility <- FALSE
+Reproducibility <- TRUE
 
@@
 library(ggplot2) # plotting
+library(ggpubr) # combining ggplots
+library(scales) # scales for plots
 library(xtable) # table
@@
 
+\addtocontents{toc}{\bigskip}
 \addtocontents{toc}{\bigskip}
@@
    \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
-  \href{https://doi.org/10.1214/21-AOAS1502}{doi:10.1214/21-AOAS1502}}
-\include{paper2}
+  doi:\href{https://doi.org/10.1214/21-AOAS1502}{10.1214/21-AOAS1502}}
+\include{paper1}
 
@@
    \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
-   \href{https://doi.org/10.1111/rssb.12491}{doi:10.1111/rssb.12491}
+   doi:\href{https://doi.org/10.1111/rssb.12491}{10.1111/rssb.12491}
  }
-\include{paper1}
+\include{paper2}
 
@@
   Samuel Pawel, Guido Consonni, Leonhard Held}{%
-  2022. arXiv preprint. \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:10.48550/arXiv.2211.02552}
+  2022. arXiv preprint. doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}
 }
@@
   \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
-  \href{https://doi.org/10.1002/jrsm.1538}{doi:10.1002/jrsm.1538}
+  doi:\href{https://doi.org/10.1002/jrsm.1538}{10.1002/jrsm.1538}
 }
@@
   \textit{BMC Medical Research Methodology}, 2022, 22(149).
-  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:10.1186/s12874-022-01635-4}
+  doi:\href{https://doi.org/10.1186/s12874-022-01635-4}{10.1186/s12874-022-01635-4}
 }
@@
   2022. arXiv preprint.
-  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:10.48550/arXiv.2203.13076}
+  doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}
 }

### 2022-12-05 intro.Rnw
packages

@@
 which would make us more confident about the original finding, or may yield
-conflicting results which would lower our confidence. Replication studies are
-thus an essential part of the scientific process as they provide a means for
-substantiating genuine research findings and refuting research findings which
-occurred merely by chance. For this reason, ``successful'' replication is often
-a requirement, for instance, for acceptance of newly proposed scientific
+conflicting results which would lower our confidence. As such, replication
+studies are an essential part of the scientific process as they provide a means
+for substantiating genuine research findings and refuting research findings
+which occurred merely by chance. For this reason, ``successful'' replication is
+often a requirement, for instance, for acceptance of newly proposed scientific
 theories (\eg{} a new physical model) or the implementation of policies based on
@@
 results than their original counterparts, and the replicability of research
-findings is surprisingly low (how precisely replicability is defined will soon
-be discussed in more detail). This realization led many to declare science as
-being in a ``replication crisis''. Debates arose about whether or not the crisis
-really existed and who or what was to blame \citep{Gilbert2016, Amrhein2019}.
-Even the popular press became interested \citep[\eg{}][]{Carey2015, Kovic2016,
-  Achenbach2017, Devlin2018}, so that also in the eyes of the public the
-credibility of science became seriously threatened.
+findings is surprisingly low (how replicability can be defined precisely will
+soon be discussed in more detail). This realization led many to declare science
+as being in a ``replication crisis''. Debates arose about whether or not the
+crisis really existed and who or what was to blame \citep{Gilbert2016,
+  Amrhein2019}. Even the popular press became interested
+\citep[\eg{}][]{Carey2015, Kovic2016, Achenbach2017, Devlin2018}, so that also
+in the eyes of the public the credibility of science became seriously
+threatened.
 
@@
   will be assumed that $\sigma$ corresponds to the true standard error. This is
-  the same assumption as in ordinary fixed-effects/random-effects meta-analysis,
-  and reasonable if the sample size of the studies is not too small.} Under the
-assumption of (asymptotic) normality, confidence intervals for $\theta$ and
-$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
-computed as shown in Table~\ref{tab:meta}.
+  the same assumption as in ordinary fixed-effect/random-effects meta-analysis,
+  and typically reasonable if the sample size of the studies is not too small.}
+Under the assumption of (asymptotic) normality, confidence intervals for
+$\theta$ and $p$-values for testing the null hypothesis
+$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
 
@@
 Some projects also report a confidence interval for $d$ \citep{Camerer2016,
-  Camerer2018}, while others ignore its uncertainty and make a binary cut at
+  Camerer2018}, whereas others ignore its uncertainty and make a binary cut at
 $d_{\text{min}} = 1$ to define replication success \citep{Errington2021}. The
@@
 cancer biology \citep[and would perhaps therefore better be named ``Replication
-Project'', see][]{Goodman2016}. In the end, only 23 of the 53 studies could be
-repeated due to various difficulties, such as, missing information from the
+Project'', see][for the distinction between ``replicabality'' and
+``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
+be repeated due to various difficulties, such as, missing information from the
 original studies or problems in conducting the experiments.
@@
 ## function to color code numerical value in LaTeX table based on threshold
-tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "nicegreen",
-                         col2 = "red") {
+tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "dark2green",
+                         col2 = "dark2orange") {
     if (is.na(x)) {
@@
            dFormat = tableFormat(x = d, outFun = dFormat,
-                                 threshold = 1, col1 = "red", col2 = "nicegreen"),
+                                 threshold = 1, col1 = "dark2orange", col2 = "dark2green"),
            cioL = smdo - za*so,
@@
            pQFormat = tableFormat(x = pQ),
-           smdoFormat = paste("$", dFormat(smdo), "~",
+           smdoFormat = paste("$", dFormat(smdo, phantom = TRUE), "~",
                               ciFormat(lower = cioL, upper = cioU), "$"),
-           smdrFormat = paste("$", dFormat(smdr), "~",
+           smdrFormat = paste("$", dFormat(smdr, phantom = TRUE), "~",
                               ciFormat(lower = cirL, upper = cirU), "$"),
-           smdmFormat = paste("$", dFormat(smdm), "~",
+           smdmFormat = paste("$", dFormat(smdm, phantom = TRUE), "~",
                               ciFormat(lower = cimL, upper = cimU), "$"),
@@
 observed data. The central quantity for doing so is the distribution of the
-parameters conditional on the observed data, called the \emph{posterior
-  distribution}. It can be obtained from Bayes' theorem,
+parameters conditional on the data, called the \emph{posterior distribution}. It
+can be obtained from Bayes' theorem,
 \begin{align*}
@@
 whether the resulting prior is plausible in light of external knowledge, and if
-so, this could be seen as support for the specified posterior.
+so, this indicates support for the specified posterior.
 
@@
   Samuel Pawel, Guido Consonni, Leonhard Held \\
-  2022. arXiv preprint.
+  \textit{arXiv preprint}, 2022.
   doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}.}
@@
   Samuel Pawel, Lucas Kook, Kelly Reeve \\
-  2022. arXiv preprint.
+  \textit{arXiv preprint}, 2022.
   doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}.}
@@
 data to reproduce this thesis are available at
-\url{https://doi.org/10.5281/zenodo.XXXXXXX}.
+\url{https://github.com/SamCH93/thesis}. A snapshot of the git repository is
+archived \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
 

### 2022-12-05 thesis.Rnw
packages

@@
   Samuel Pawel, Guido Consonni, Leonhard Held}{%
-  2022. arXiv preprint. doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}
+  \textit{arXiv preprint}, 2022.
+  doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}
 }
@@
   Samuel Pawel, Lucas Kook, Kelly Reeve }{%
-  2022. arXiv preprint.
+  \textit{arXiv preprint}, 2022.
   doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}

### 2022-12-08 abstract.tex
some suggestions Leo

@@
 some situations the sceptical $p$-value may indicate replication success even
-though the effect estimate from the replication is arbitrarily smaller than the
-effect estimate from the original
-study. % , which cannot happen with the sceptical
+though the effect estimate from the replication is much smaller than the effect
+estimate from the original study. % , which cannot happen with the sceptical
 % Bayes factor.

### 2022-12-08 intro.Rnw
some suggestions Leo

@@
 questions is of high importance to scientists, decision makers, and the general
-population. However, because every study result is subject to uncertainty, we
-can never know for sure.
-
-One way to come a little closer to the truth is to repeat the original study
-with new subjects. Such a \emph{replication study} may yield similar results
-which would make us more confident about the original finding, or may yield
+population, and one way to obtain it is through \emph{replication studies}.
+
+A replication study consists of repeating the original study as close as
+possible but with new subjects. Such a study may yield similar results which
+would make us more confident about the original finding, or may yield
 conflicting results which would lower our confidence. As such, replication
-studies are an essential part of the scientific process as they provide a means
+studies are an essential part of the scientific method as they provide a means
 for substantiating genuine research findings and refuting research findings
@@
 scientific knowledge (\eg{} market approval of a drug). The results from
-replication studies may thus have real world consequences, such as deciding
-whether we receive the recommendation to get vaccinated (a consequence that
-anyone who experienced the COVID-19 pandemic is very aware of).
+replication studies may thus have real world consequences, % , such as deciding
+% whether we receive the recommendation to get vaccinated (a consequence that
+% anyone who experienced the COVID-19 pandemic is very aware of)
+and it is therefore important that methodological aspects of replication
+studies, such as their statistical design and analysis, are well understood.
 
@@
 % save the reputation of science
-\citep[for an overview see \eg{}][]{Munafo2017}. For instance, many journals
+\citep[for an overview see \eg{}][]{Munafo2017}. For instance, some journals
 adopted the ``registered report'' format \citep{Chambers2021} in which a study
@@
     $(1 - \alpha)$ confidence interval &
-    $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
-    $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
-    % $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
-    % $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
+    % $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
+    % $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
+    $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
+    $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
     $z$-value & $z_{o} = \that_{o}/\sigma_{o}$ & $z_{r} = \that_{r}/\sigma_{r}$ \\
@@
 differences and correlations (for continuous outcomes), odds ratios (for binary
-outcomes), or hazard ratios (for time to event outcomes). Depending on the type
+outcomes), or hazard ratios (for time-to-event outcomes). Depending on the type
 of effect size, a transformation might be required so that the assumption of
@@
 associated standard error $\sigma$ represents the statistical uncertainty of the
-estimate.\footnote{Typically, the available standard error $\sigma$ is only an
-  estimate of the true standard error. However, in most parts of this thesis it
-  will be assumed that $\sigma$ corresponds to the true standard error. This is
-  the same assumption as in ordinary fixed-effect/random-effects meta-analysis,
-  and typically reasonable if the sample size of the studies is not too small.}
-Under the assumption of (asymptotic) normality, confidence intervals for
-$\theta$ and $p$-values for testing the null hypothesis
-$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
+estimate. Typically, the available standard error $\sigma$ is only an estimate
+of the true standard error. However, in most parts of this thesis it will be
+assumed that $\sigma$ corresponds to the true standard error. This is the same
+assumption as in ordinary fixed-effect/random-effects meta-analysis, and
+typically reasonable if the sample size of the studies is not too small. Under
+the assumption of (asymptotic) normality, confidence intervals for $\theta$ and
+$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
+computed as shown in Table~\ref{tab:meta}.
 
@@
 one-sided $p$-values, so that the original and replication effect estimate are
-not required to show the same direction as this is taken into account by the
-one-sided $p$-values. Some replication projects \citep{Opensc2015,
-  Errington2021} also defined replication success via simultaneous
-non-significance of original and replication study ($p_{o} > \alpha$ and
-$p_{r} > \alpha$). However, with this definition ``replication success'' can
-almost always be achieved by conducting original and replication study with very
-few samples so that the $p$-values are large. The approach is also logically
-questionable as it could be seen as an instance of the ``absence of evidence
-fallacy'' \citep{Altman1995} meaning the failure to find evidence against the
-null hypothesis is erroneously interpreted as evidence for the null hypothesis.
-Meta-analytic extensions of the significance approach define replication success
-by significance of a combined effect estimate.\footnote{The meta-analytic
-  approach can also be given a Bayesian interpretation: A flat prior
-  distribution for the underlying effect size $\theta$ is updated by the data
-  from original and replication study. Replication success defined by a
-  meta-analytic $p$-value being smaller than $\alpha$ is then equivalent to
-  replication success via a Bayesian posterior probability
-  $\Pr(\theta > 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$, respectively,
-  $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$, depending on the
-  direction of the combined estimate.} Typically, the assumption of a common
-underlying effect size is seen as reasonable so that fixed-effect meta-analysis
-is used for pooling. Random-effects meta-analysis has primarily been used if
-more than one replication study of the same original study are conducted since
-replicators are often interested in understanding between-replication
-heterogeneity \citep[\eg{} in][]{Klein2018}.
+not explicitly required to show the same direction as this is already taken into
+account by the one-sided $p$-values. Some replication projects
+\citep{Opensc2015, Errington2021} also defined replication success via
+simultaneous non-significance of original and replication study
+($p_{o} > \alpha$ and $p_{r} > \alpha$). However, with this definition
+``replication success'' can almost always be achieved by conducting original and
+replication study with very few samples so that the $p$-values are large. The
+approach is also logically questionable as it could be seen as an instance of
+the ``absence of evidence fallacy'' \citep{Altman1995} meaning the failure to
+find evidence against the null hypothesis is erroneously interpreted as evidence
+for the null hypothesis. Meta-analytic extensions of the significance approach
+define replication success by significance of a combined effect
+estimate.
+% \footnote{The meta-analytic approach can also be given a Bayesian
+% interpretation: A flat prior distribution for the underlying effect size
+% $\theta$ is updated by the data from original and replication study.
+% Replication success defined by a meta-analytic $p$-value being smaller than
+% $\alpha$ is then equivalent to replication success via a Bayesian posterior
+% probability $\Pr(\theta > 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$,
+% respectively, $\Pr(\theta < 0 \given \that_{o}, \that_{r}) > 1 - \alpha/2$,
+% depending on the direction of the combined estimate.}
+Typically, the assumption of a common underlying effect size is seen as
+reasonable so that fixed-effect meta-analysis is used for pooling.
+Random-effects meta-analysis has primarily been used if more than one
+replication study of the same original study are conducted since replicators are
+often interested in understanding between-replication heterogeneity \citep[\eg{}
+in][]{Klein2018}.
 
@@
 << "RPCB-graph", fig.height = 3.5 >>=
-
-## function to format CI
-ciFormat. <- function(lower, upper) {
-    paste0("[", format(signif(lower, 2), nsmall = 2),
-           ", ", format(signif(upper, 2), nsmall = 2), "]")
-}
-ciFormat <- Vectorize(FUN = ciFormat.)
-
-## function to format p-value
-pFormat. <- function(p, digits = 2, dollar = FALSE, phantom = FALSE) {
-    if (is.na(p)) {
-        out <- NA
-    } else {
-        if (p > 0.0001) {
-            out <- as.character(signif(p, digits = digits))
-            if (phantom) out <- paste0("\\phantom{<~}", out)
-        } else {
-            out <- "< 0.0001"
-        }
-        if (dollar) {
-            out <- paste0("$", out, "$")
-        }
-    }
-    return(out)
-}
-pFormat <- Vectorize(FUN = pFormat.)
-
-## function to format (relative) effect estimate
-dFormat. <- function(x, digits = 2, phantom = FALSE, dollar = FALSE) {
-    if (is.na(x)) {
-        out <- NA
-    } else {
-        out <- as.character(signif(x, digits = digits))
-        if (phantom && (x >= 0)) {
-           out <- paste0("\\phantom{-}", out)
-        }
-        if (dollar) out <- paste0("$", out, "$")
-    }
-    return(out)
-}
-dFormat <- Vectorize(FUN = dFormat.)
-
-## function to color code numerical value in LaTeX table based on threshold
-tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "dark2green",
-                         col2 = "dark2orange") {
-    if (is.na(x)) {
-        out <- NA
-    } else {
-        if (x < threshold) col <- col1
-        else col <- col2
-        out <- paste0("\\textcolor{", col, "}{",
-                      outFun(x, dollar = TRUE, phantom = TRUE), "}")
-    }
-    return(out)
-}
-tableFormat <- Vectorize(FUN = tableFormat., vectorize.args = "x")
-
 za <- qnorm(p = 0.975)
 rpcb <- read.csv("data/rpcb.csv") |>
-    mutate(zo = smdo/so,
+    mutate(id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
+           zo = smdo/so,
            zr = smdr/sr,
@@
            pQ = pchisq(q = Q, df = 1, lower.tail = FALSE),
-           dFormat = tableFormat(x = d, outFun = dFormat,
-                                 threshold = 1, col1 = "dark2orange", col2 = "dark2green"),
-           cioL = smdo - za*so,
-           cioU = smdo + za*so,
-           cirL = smdr - za*sr,
-           cirU = smdr + za*sr,
-           cimL = smdm - za*sm,
-           cimU = smdm + za*sm,
-           id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
-           po2Format = tableFormat(x = po2),
-           pr2Format = tableFormat(x = pr2),
-           pm2Format = tableFormat(x = pm2),
-           pQFormat = tableFormat(x = pQ),
-           smdoFormat = paste("$", dFormat(smdo, phantom = TRUE), "~",
-                              ciFormat(lower = cioL, upper = cioU), "$"),
-           smdrFormat = paste("$", dFormat(smdr, phantom = TRUE), "~",
-                              ciFormat(lower = cirL, upper = cirU), "$"),
-           smdmFormat = paste("$", dFormat(smdm, phantom = TRUE), "~",
-                              ciFormat(lower = cimL, upper = cimU), "$"),
            rsig = factor(pr2 <= 0.05, levels = c(FALSE, TRUE),
@@
                             alternative = "two.sided", type = "nominal")
-rpcb$ps2Format <- NA
-rpcb$ps2Format <- tableFormat(x = rpcb$ps2)
 
@@
   Cancer Biology \citep{Errington2021} for which effect estimates and standard
-  errors are available on standardized mean difference scale. Shown are the
+  errors are available on the standardized mean difference scale. Shown are the
   number of replication successes according to the different criteria from
@@
 Taken together, this analysis demonstrates that conclusions based on commonly
-used replication success criteria often differ. It is not always clear cut
+used replication success criteria often differ. It is not always clear-cut
 whether or not a replication is successful. Reducing replicability to a single
@@
   \label{tab:RPCB}
-\resizebox{1\linewidth}{!}{%
+\resizebox{1.02\linewidth}{!}{%
 << "RPCB-table2", results = "asis" >>=
-## select a subset with one effect per paper
+## function to format CI
+ciFormat. <- function(lower, upper, dollar = FALSE, digits = 2) {
+    if (dollar) x <- "$" else x <- ""
+    paste0("[", x, format(round(lower, digits), nsmall = digits), x,
+           " to ", x, format(round(upper, digits), nsmall = digits), x, "]")
+}
+ciFormat <- Vectorize(FUN = ciFormat.)
+
+## function to format p-value
+pFormat. <- function(p, digits = 2, dollar = FALSE, phantom = FALSE) {
+    if (is.na(p)) {
+        out <- NA
+    } else {
+        if (p > 0.0001) {
+            if (p < 10^(-digits+1)) {
+                out <- as.character(signif(p, digits = digits))
+            } else {
+                out <- format(round(p, digits), nsmall = digits)
+            }
+            if (phantom) out <- paste0("\\phantom{<~}", out)
+        } else {
+            out <- "< 0.0001"
+        }
+        if (dollar) {
+            out <- paste0("$", out, "$")
+        }
+    }
+    return(out)
+}
+pFormat <- Vectorize(FUN = pFormat.)
+
+## function to format (relative) effect estimate
+dFormat. <- function(x, digits = 2, phantom = FALSE, dollar = FALSE) {
+    if (is.na(x)) {
+        out <- NA
+    } else {
+        out <- as.character(signif(x, digits = digits))
+        if (phantom && (x >= 0)) {
+           out <- paste0("\\phantom{-}", out)
+        }
+        if (dollar) out <- paste0("$", out, "$")
+    }
+    return(out)
+}
+dFormat <- Vectorize(FUN = dFormat.)
+
+## function to color code numerical value in LaTeX table based on threshold
+tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "dark2green",
+                         col2 = "dark2orange") {
+    if (is.na(x)) {
+        out <- NA
+    } else {
+        if (x < threshold) col <- col1
+        else col <- col2
+        out <- paste0("\\textcolor{", col, "}{",
+                      outFun(x, dollar = TRUE, phantom = TRUE), "}")
+    }
+    return(out)
+}
+tableFormat <- Vectorize(FUN = tableFormat., vectorize.args = "x")
+
+## randomly select a subset with one effect per paper
 set.seed(7)
@@
     na.omit() |>
-    ## filter(smdo < 80, smdr < 80) |>
     group_by(paper) |>
@@
     arrange(pr2) |>
+    mutate(smdoFormat = signif(smdo, 3),
+           smdrFormat = signif(smdr, 3),
+           smdmFormat = signif(smdm, 3),
+           dFormat = tableFormat(x = d, outFun = dFormat,
+                                 threshold = 1, col1 = "dark2orange",
+                                 col2 = "dark2green"),
+           cioL = smdo - za*so,
+           cioU = smdo + za*so,
+           cirL = smdr - za*sr,
+           cirU = smdr + za*sr,
+           cimL = smdm - za*sm,
+           cimU = smdm + za*sm,,
+           po2Format = tableFormat(x = po2),
+           pr2Format = tableFormat(x = pr2),
+           pm2Format = tableFormat(x = pm2),
+           ps2Format = tableFormat(x = ps2),
+           pQFormat = tableFormat(x = pQ),
+           cioFormat = ciFormat(lower = cioL, upper = cioU, dollar = TRUE),
+           cirFormat = ciFormat(lower = cirL, upper = cirU, dollar = TRUE),
+           cimFormat = ciFormat(lower = cimL, upper = cimU), dollar = TRUE) |>
     select(id,
-           smdoFormat, ## so,
-           smdrFormat, smdmFormat,
-           c, dFormat, ## sr,
+           smdoFormat, cioFormat,
+           smdrFormat, cirFormat,
+           smdmFormat, cimFormat,
+           c, dFormat,
            po2Format, pr2Format, pm2Format, pQFormat, ps2Format
            )
-
 rpcbXtable <- xtable(rpcbTable)
 colnames(rpcbXtable) <- c("(P, X, E)",
-                          "$\\that_o$ [95\\% CI]",
-                          "$\\that_r$ [95\\% CI]",
-                          "$\\that_m$ [95\\% CI]",
-                          "$c$", #"$\\sigma^2_o/\\sigma^2_r$",
-                          "$d$", #"$\\that_r/\\that_o$",
+                          "$\\that_o$", "[95\\% CI]",
+                          "$\\that_r$", "[95\\% CI]",
+                          "$\\that_m$", "[95\\% CI]",
+                          "$c$",
+                          "$d$",
                           "$p_o$",
@@
                           )
+
 colnames(rpcbXtable) <- paste0("\\multicolumn{1}{c}{", colnames(rpcbXtable), "}")
@@
       sanitize.text.function = function(x){x},
+      math.style.negative = getOption("xtable.math.style.negative", TRUE),
       size = "small")
@@
 \end{align*}
-The associated $(1- \alpha)$ highest posterior density credible interval is
-given by
+The associated $(1- \alpha)$ highest posterior density credible interval has
+limits
 \begin{align}
-  \left[\mu_{\text{post}} \pm z_{\alpha/2} \, \sigma_{\text{post}}\right]
+  \left[\mu_{\text{post}} - z_{\alpha/2} \, \sigma_{\text{post}},
+  \mu_{\text{post}} + z_{\alpha/2} \, \sigma_{\text{post}}\right]
   \label{eq:postCI}
@@
 (depending on the orientation of the effect size) this may be interpreted as
-evidence\footnote{For readers who do not agree with this notion of evidence, do
-  not panic. In this thesis (Paper II and IV) we extend this reverse-Bayes
-  procedure to use alternative measures of evidence, such as Bayes factors.} for
-a genuine effect found in the original study.
+evidence for a genuine effect found in the original study. There exist also
+other definitions of statistical evidence and in latter parts of this thesis
+(Paper\ref{PaperII} and Paper\ref{PaperIV}) we will extend this reverse-Bayes
+procedure to employ alternative measures of evidence, such as Bayes factors.
 
@@
 % only be regarded as adequate if current belief about
-He reasoned that inferences based on the left factor, the posterior distribution
+He argued that inferences based on the left factor, the posterior distribution
 $f(\theta \given \text{data}, \text{M})$, should only be trusted if the right
@@
   p_{\text{Box}}
-  = \Pr\left\{f(\text{data} \given \text{M}) <
-  f(\text{data} = \text{observed data} \given \text{M}) \given \text{M}\right\}.
+  % &= \Pr\left\{f(\text{data} \given \text{M}) <
+  % f(\text{data} = \text{observed data} \given \text{M}) \given \text{M}\right\} \\
+  & = \int_{\mathcal{X}} \,
+    f(\text{data} = x \given \text{M}) \, \text{d}x
   \label{eq:pppval}
 \end{align}
+with $\mathcal{X} = \{x : f(\text{data} = x \given \text{M}) <
+f(\text{data} = \text{observed data} \given \text{M})\}$.
 The $p$-value $p_{\text{Box}}$ is the probability of obtaining data with lower
@@
 approaches based on prior predictive ratios will be used in latter parts of this
-thesis.\footnote{Some readers may have noted that the prior predictive ratio is
-  also the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
-  $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
-  approach is therefore particularly useful in combination with reverse-Bayes
-  procedures based on Bayes factors, as will be demonstrated later (Paper II and
-  IV).}
+thesis (Paper~\ref{PaperII} and Paper~\ref{PaperIV}).
+% \footnote{Some readers may have noted that the prior predictive ratio is also
+% the Bayes factor \citep{Jeffreys1961, Good1958} contrasting model
+% $\text{M}_{1}$ to $\text{M}_{2}$. The prior predictive ratio model criticism
+% approach is therefore particularly useful in combination with reverse-Bayes
+% procedures based on Bayes factors, as will be demonstrated later (Paper~\ref{PaperII} and
+% IV).}
 
@@
 This thesis consists of six papers divided into three parts. The first part
-(Paper I, II, and III) focuses on methodology for design and analysis of
-replication studies. The second part (Paper IV and V) revolves around
-reverse-Bayes methodology with a broader scope of applications than replication
+(Paper~\ref{PaperI}, \ref{PaperII}, and \ref{PaperIII}) focuses on methodology
+for design and analysis of replication studies. The second part
+(Paper~\ref{PaperIV} and \ref{PaperV}) revolves around reverse-Bayes methodology
+with a broader scope of applications than replication
 studies. % Paper IV is a review paper about
@@
 % which proposed a reverse-Bayes method.
-The last part (Paper VI) is about integrity issues in methodological research
-with simulations studies. % The article lists and illustrates questionable
+The last part (Paper~\ref{PaperVI}) is about integrity issues in methodological
+research with simulations
+studies. % The article lists and illustrates questionable
 % research practices in simulation studies, and gives recommendations how to avoid
@@
 L. Held had the idea to apply the sceptical $p$-value method to the data from
-the four replication projects, which I collected for my master thesis. C.
-Micheloud and L. Held came up with the golden level. L. Held wrote an initial
-draft of the manuscript. C. Micheloud, L. Held, and I then iteratively worked on
-the manuscript.
+the four replication projects, which I collected for my master thesis. L. Held
+and C. Micheloud came up with the golden level. L. Held wrote an initial draft
+of the manuscript. L. Held, C. Micheloud, and I then iteratively worked on the
+manuscript.
 
@@
 calculations for the sceptical $p$-value and the sceptical Bayes factor. In
-Paper II, I already derived the power function of the sceptical Bayes factor in
+Paper~\ref{PaperII}, I already derived the power function of the sceptical Bayes factor in
 closed-form for two types of design priors. After its completion, I generalized
@@
 $N$ method \citep{Rosenthal1979,Rosenberg2005}, L. Held suggested that it would
-fit nicely into this manuscript, and that I should start to overhaul it. I
-rewrote and expanded his initial draft, adding also a new section on
-reverse-Bayes approaches with Bayes factors, largely based on the work from
-Paper II. We then managed to recruit R. Matthews to also contribute. From that
-point on the three of us iteratively worked on the manuscript and M. Ott gave
-high-level feedback.
+fit nicely into this manuscript, to add the COVID-19 meta-analysis example, and
+that I should start to overhaul it. I rewrote and expanded his initial draft,
+adding also a new section on reverse-Bayes approaches with Bayes factors,
+largely based on the work from Paper~\ref{PaperII}. We then managed to recruit R. Matthews
+to also contribute. From that point on the three of us iteratively worked on the
+manuscript and M. Ott gave high-level feedback.
 
@@
 
-Shortly after the acceptance of Paper III, the article by \citet{Sondhi2021}
-appeared. It proposed a novel reverse-Bayes method called \emph{Bayesian
-  Additional Evidence}, and we noted some flaws in the article. This prompted us
-to write a commentary. We show that -- contrary to the statement by
-Sondhi et al. -- there is a closed form solution for the key quantity in
-their approach termed ``Bayesian Additional Evidence tipping point''.
+Shortly after the acceptance of Paper~\ref{PaperIII}, the article by
+\citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
+\emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
+This prompted us to write a commentary. We show that -- contrary to the
+statement by Sondhi et al. -- there is a closed form solution for the key
+quantity in their approach termed ``Bayesian Additional Evidence tipping
+point''.
 % The Bayesian Additional Evidence method provides an answer to the question

### 2022-12-09 intro.Rnw
one-sided sceptical p

@@
 \end{tabular}
-
-% \begin{center}
-% \begin{minipage}{12cm}
-%   { { { ``We can make judgments of initial probabilities and infer final ones,
-%         or we can equally make judgments of final ones and infer initial ones by
-%         \emph{Bayes's theorem in reverse}.'' }}}
-% \end{minipage}
-% \end{center}
-% \begin{flushright}
-%    \citet[p. 29]{Good1983}
-% \end{flushright}
 
@@
 study is a genuine effect or just a spurious finding? The answer to such
-questions is of high importance to scientists, decision makers, and the general
+questions is of high importance to researchers, decision makers, and the general
 population, and one way to obtain it is through \emph{replication studies}.
@@
 \begin{figure}[!htb]
-<< "google-scholar-graph", fig.height = 3.5 >>=
+<< "replication-time-graph", fig.height = 3.5 >>=
 ## ## Data gathered on October 18 2022
@@
                           $(1 - \alpha)$ original confidence interval
-                          ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\sigma_{o}]$).
+                          ($\that_{r} \in [\that_{o} - z_{\alpha/2}\sigma_{o},
+                          \that_{o} + z_{\alpha/2}\sigma_{o}]$).
                           Sometimes, also defined as the original effect estimate is
                           contained in the $(1 - \alpha)$ replication confidence interval
-                          ($\that_{o} \in [\that_{r} \pm z_{\alpha/2}\sigma_{r}]$).
+                          ($\that_{o} \in [\that_{r} - z_{\alpha/2}\sigma_{r},
+                          \that_{r} + z_{\alpha/2}\sigma_{r}]$).
                           Usually $\alpha = 5\%$. \\
@@
                                      $(1 - \alpha)$ prediction interval
-                                     ($\that_{r} \in [\that_{o} \pm z_{\alpha/2}\surd(\sigma_{o}^{2}
+                                     ($\that_{r} \in [\that_{o} - z_{\alpha/2}\surd(\sigma_{o}^{2}
+                                     + \sigma_{r}^{2}), \that_{o} + z_{\alpha/2}\surd(\sigma_{o}^{2}
                                      + \sigma_{r}^{2})]$). Usually $\alpha = 5\%$.
@@
 \begin{figure}[!htb]
-<< "RPCB-table1", results = "asis", fig.height = 5.5 >>=
+<< "RPCB-table1", results = "asis", fig.height = 6 >>=
 ## show number of successes
@@
 evidence for a genuine effect found in the original study. There exist also
-other definitions of statistical evidence and in latter parts of this thesis
-(Paper\ref{PaperII} and Paper\ref{PaperIV}) we will extend this reverse-Bayes
-procedure to employ alternative measures of evidence, such as Bayes factors.
+other definitions of statistical evidence and in subsequent chapters of this
+thesis (Paper\ref{PaperII} and Paper\ref{PaperIV}) we will extend this
+reverse-Bayes procedure to employ alternative measures of evidence, such as
+Bayes factors.
 
@@
 the observed data with the model $\text{M}_{1}$. Bayesian model criticism
-approaches based on prior predictive ratios will be used in latter parts of this
-thesis (Paper~\ref{PaperII} and Paper~\ref{PaperIV}).
+approaches based on prior predictive ratios will be used in subsequent chapters
+of this thesis (Paper~\ref{PaperII} and Paper~\ref{PaperIV}).
 % \footnote{Some readers may have noted that the prior predictive ratio is also
@@
 available in closed-form
-\begin{align*}
+\begin{align}
+  \label{eq:ps}
   p_{\text{S}}
@@
   = 2\left\{1 - \Phi(|z_{\text{S}}|)\right\}
-\end{align*}
+\end{align}
 where
@@
 
+<< "paradox-example" >>=
+smdo <- 3
+smdr <- -3
+so <- sr <- 1
+ps2 <- pSceptical(zo = smdo/so, zr = smdr/sr, c = so^2/sr^2,
+                  alternative = "two.sided", type = "nominal")
+@
+
+There is one problem with the (two-sided) sceptical $p$-value as defined
+in~\eqref{eq:ps}; It does not take the direction of the effect estimates into
+account, so replication success may be established even though the effect
+estimate from the replication goes in the opposite direction of the original one
+($\sign(\that_{o}) \neq \sign(\that_{r})$). In fact, the sceptical $p$-value
+will decrease with decreasing negative relative effect estimate
+($\ps \downarrow p_{o}$ as $d \downarrow -\infty$ for fixed $\sigma_{o}$ and
+$\sigma_{r}$) which seems contrary to intuitive understandings of replicability
+as a change in effect direction may diminish the usefulness of a scientific
+finding (\eg{} a negative treatment effect may indicate harm instead of
+benefit).
+% For example, if $\that_{o} = \Sexpr{smdo}$,
+% $\that_{r} = \Sexpr{smdr}$, and $\sigma_{o} = \sigma_{r} = 1$, this would lead
+% to $\ps = \Sexpr{pFormat(ps2)}$, and the sceptical $p$-value continues to
+% decreases with decreasing replication effect estimates.
+This ``replication
+paradox'' \citep{Ly2018} can be avoided by defining a one-sided sceptical
+$p$-value
+\begin{align*}
+  \tilde{p}_{\text{S}} =
+  \begin{cases}
+    \ps/2 & \text{if} ~\sign(\that_{o}) = \sign(\that_{r}) \\
+    1 - \ps/2 & \text{if} ~ \sign(\that_{o}) \neq \sign(\that_{r}) \\
+  \end{cases}
+\end{align*}
+similar to how ordinary one-sided $p$-values are defined. In the subsequent
+chapters only the one-sided version of the sceptical $p$-value will be used.
+
 This concludes the introduction to replication studies and reverse-Bayes methods
 for their analysis. Some additional properties (\eg{} the null distribution of
-the sceptical $p$-value) and extensions (\eg{} a one-sided version of the
-sceptical $p$-value, power and sample size calculations) can be found in the
-original article by \citet{Held2020}. The sceptical $p$-value and related
-methods are implemented in the R package \texttt{ReplicationSuccess} available
-on CRAN
+the sceptical $p$-value) and extensions (\eg{} power and sample size
+calculations) can be found in the original article by \citet{Held2020}. The
+sceptical $p$-value and related methods are implemented in the R package
+\texttt{ReplicationSuccess} available on CRAN
 (\url{https://cran.r-project.org/package=ReplicationSuccess}). % However, the
@@
 % which proposed a reverse-Bayes method.
-The last part (Paper~\ref{PaperVI}) is about integrity issues in methodological
-research with simulations
-studies. % The article lists and illustrates questionable
+The last part (Paper~\ref{PaperVI}) is on meta-scientific perspectives on
+methodological research.
+% The article lists and illustrates questionable
 % research practices in simulation studies, and gives recommendations how to avoid
@@
 It is not clear how to interpret the sceptical $p$-value as it is not an
-ordinary $p$-value (which has a uniform distribution under the corresponding
-null hypothesis). Moreover, when the same level $\alpha$ as for the significance
-criterion is used for dichotomizing the sceptical $p$-value, this leads to a
-much more stringent criterion for replication studies than the significance
-criterion, and many studies which intuitively seem successful will not satisfy
-it.
+ordinary $p$-value (which has a uniform distribution under the null hypothesis
+that the underlying effect size $\theta$ is zero). Moreover, when the same level
+$\alpha$ as for the significance criterion is used for dichotomizing the
+sceptical $p$-value, this leads to a much more stringent criterion for
+replication studies than the significance criterion. Many studies which
+intuitively seem successful will not satisfy it, and frequentist properties such
+as power and type I error rate will be impacted by it (\eg{} power and type I
+error rate will be much lower compared to the significance criterion).
+
+<< "golden-level" >>=
+alpha <- 0.025
+alphaG <- levelSceptical(level = alpha, alternative = "one.sided", type = "golden")
+@
 
@@
 replication effect estimate is at least as large as the original one
-($d \geq 1$). For instance, for the significance level $\alpha = 5\%$, the
-corresponding golden level is $\alpha_{G} = 12.3\%$. The behavior of the golden
-level seems to align with common sense: for original studies which were already
-convincing (in terms of their $p$-value) the effect estimate in the replication
-study is allowed to shrink, to some extent, whereas for less convincing original
-studies (those with $p$-values around the significance level) shrinkage is more
-strongly penalized. We find that for replication studies with equal or larger
-sample size than the original study, replication success based on the golden
-level also has similar or improved frequentist properties (type-I error rate and
-project power) compared to the standard significance criterion. Case studies
-from four large-scale replication projects \citep{Opensc2015, Camerer2016,
-  Camerer2018, Cova2018} illustrate the properties of the method. This extension
-is now implemented as the default option in the R package
-\texttt{ReplicationSuccess}.
+($d \geq 1$). For instance, for the one-sided significance level
+$\alpha = \Sexpr{round(alpha*100, 1)}\%$, the corresponding two-sided golden
+level is $\alpha_{G} = \Sexpr{round(alphaG*100, 1)}\%$. The behavior of the
+golden level seems to align with common sense: for original studies which were
+already convincing (in terms of their $p$-value) the effect estimate in the
+replication study is allowed to shrink, to some extent, whereas for less
+convincing original studies (those with $p$-values around the significance
+level) shrinkage is more strongly penalized. We find that for replication
+studies with equal or larger sample size than the original study, replication
+success based on the golden level controls the type I error rate at the same
+level as the standard significance criterion. Similarly, if the original study
+was adequately powered, replication success based on the golden level has
+comparable or improved ``project power''compared to the significance criterion
+(project power is the probability of replication success conditional on a true
+effect size based on original and replication study). Case studies from four
+large-scale replication projects \citep{Opensc2015, Camerer2016, Camerer2018,
+  Cova2018} illustrate the properties of the golden level. In most cases
+conclusions agree with the significance criterion, but in the differing cases,
+the golden level seems to produce more appropriate inferences as it takes into
+account effect shrinkage. This extension is now implemented as the default
+option in the R package \texttt{ReplicationSuccess}.
 
@@
 details, including closed-form solution for the sceptical Bayes factors,
-asymptotic properties, type-I and type-II error rates, and non-normal
+asymptotic properties, type I and type II error rates, and non-normal
 extensions. I wrote the initial draft of the manuscript and the R package.
@@
 
-\subsection{Integrity in methodological research}
+\subsection{Meta-scientific perspectives on methodological research}
 
@@
 
-Simulation studies are frequently used for evaluating statistical methods.
-However, several studies showed that the reporting standards in simulation
-studies have remained low over the years \citep{Hoaglin1975, Burton2006,
-  Morris2019}. Moreover, some authors have recently argued that methodological
-research is suffering from reproducibility issues, publication bias, and a
-``replication crisis'' due to researchers engaging in questionable research
-practices, such as selective reporting \citep{Boulesteix2020}. In this article,
-draw attention to these issues. We summarize possible questionable research
-practices in simulation studies, and show how easy it is to make a method seem
-superior if various questionable research practices are employed. We also give
-recommendations to alleviate these issues. Most importantly, we recommend
-researchers to write and pre-register simulation protocols.
+In methodological research, simulation studies are frequently used for
+evaluating ``how well'' statistical methods perform. The results of these
+studies therefore often guide the choice in which situation which method should
+be used. However, several literature review articles identified that the design
+and reporting standards of simulation studies have remained low over the years
+\citep{Hoaglin1975, Burton2006, Morris2019}. Moreover, some authors have
+recently argued that methodological research is suffering from reproducibility
+issues, publication bias, and a ``replication crisis'' due to researchers
+engaging in questionable research practices, such as selective reporting
+\citep{Boulesteix2020}. In this article, draw attention to these issues. We
+summarize possible questionable research practices in simulation studies, and
+show how easy it is to make a method seem superior if various questionable
+research practices are employed. We also give recommendations to alleviate these
+issues. Most importantly, we recommend researchers to write and pre-register
+simulation protocols.
 
@@
 research. I then wrote a first draft of the manuscript and proposed the idea to
-L. Kook and K. Reeve. L. Kook and myself then came up with the novel regression
-method ``AINET'' and started writing the simulation protocol. L. Kook took lead
-in developing the R package \texttt{ainet}
+L. Kook and K. Reeve. L. Kook and myself then inented the regression method
+``AINET'' and started writing the simulation protocol. L. Kook took lead in
+developing the R package \texttt{ainet}
 (\url{https://github.com/LucasKook/ainet}) and simulation study code. Myself, L.
@@
 \url{https://github.com/SamCH93/thesis}. A snapshot of the git repository is
-archived \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
+archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
 

### 2022-12-09 paper1.tex
one-sided sceptical p

@@
 original and replication study, replication success at the golden level offers
-uniform gains in project power and controls the Type-I error rate if the
+uniform gains in project power and controls the Type I error rate if the
 replication sample size is not smaller than the original one. An application to
@@
 \textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
-two-trials rule, type-I error rate
+two-trials rule, type I error rate
 
@@
 for replication success compared to the two-trials rule (Section \ref{sec1:2TR}).
-In Section \ref{sec1:ER} we study power and Type-I error rates of the proposed
+In Section \ref{sec1:ER} we study power and Type I error rates of the proposed
 method and compare it to the two-trials rule. The recalibrated method ensures
@@
 significant and the replication sample size is large enough (Section
-\ref{sec1:powerrep}), controls the overall Type-I error if the replication sample
+\ref{sec1:powerrep}), controls the overall Type I error if the replication sample
 size is not smaller than the original one (Section \ref{sec1:T1E}), and offers
@@
 
-\section{Power and Type-I Error Rate}\label{sec1:ER}
+\section{Power and Type I Error Rate}\label{sec1:ER}
 Although Bayesian methods do not rely on the frequentist paradigm of repeated
@@
 then assume that none of the two studies have been conducted and investigate the
-overall Type-I error rate (Section \ref{sec1:T1E}) and the project power (Section
+overall Type I error rate (Section \ref{sec1:T1E}) and the project power (Section
 \ref{sec1:PP}) \citep{Maca2002} over both studies in combination for fixed
@@
 
-\subsection{Overall Type-I error rate}\label{sec1:T1E}
-The two studies are assumed to be independent with Type-I error rate fixed at
-$\alpha$ for each of them, so the Type-I error rate of the two-trials rule over
+\subsection{Overall Type I error rate}\label{sec1:T1E}
+The two studies are assumed to be independent with Type I error rate fixed at
+$\alpha$ for each of them, so the Type I error rate of the two-trials rule over
 the entire project is simply $\alpha^2$ for any value of the relative effect
-size $c$. In contrast, the Type-I error rate of the proposed replication success
+size $c$. In contrast, the Type I error rate of the proposed replication success
 assessment {depends on} the relative sample size $c$.
@@
 $\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
-compute the Type-I error rate at level $\alpha_S$ for $c = 1$ as
+compute the Type I error rate at level $\alpha_S$ for $c = 1$ as
 \begin{eqnarray}\label{eq1:T1E}
@@
 \end{eqnarray}
-For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type-I error
-rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type-I error rate
-$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type-I error
+For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type I error
+rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type I error rate
+$\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type I error
 rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
@@
 
-For $c \neq 1$, the Type-I error rate can be calculated through numerical
+For $c \neq 1$, the Type I error rate can be calculated through numerical
 integration:
@@
 
-\caption{Overall Type-I error rate (left) and project power (right) for fixed
+\caption{Overall Type I error rate (left) and project power (right) for fixed
   relative sample size $c$. Results are given for replication success at the
@@
 
-The left plot in Figure \ref{fig1:fig4} displays the Type-I error rate for
+The left plot in Figure \ref{fig1:fig4} displays the Type I error rate for
 $\alpha=0.025$ as a function of the relative sample size $c$. It can be seen
-that the Type-I error of the replication success approach decreases with
+that the Type I error of the replication success approach decreases with
 increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
@@
 
-The Type-I error rate of the nominal level is always below the target
-$0.0625$\%. Although the Type-I error will eventually attain $\alpha^2$ in the
+The Type I error rate of the nominal level is always below the target
+$0.0625$\%. Although the Type I error will eventually attain $\alpha^2$ in the
 limit $c \downarrow 0$ \citep[Section 3.4]{Held2020}, the nominal level seems to
-be too stringent for realistic values of $c$. The Type-I error rate of the
-golden level is smaller than $0.0625$\% for $c >0.85$. Appropriate Type-I error
+be too stringent for realistic values of $c$. The Type I error rate of the
+golden level is smaller than $0.0625$\% for $c >0.85$. Appropriate Type I error
 control is thus ensured even for replication studies where the sample size is
@@
 \end{center}
-\caption{Overall Type-I error rate if the replication sample size equal to the
+\caption{Overall Type I error rate if the replication sample size equal to the
   original study ($c=1$). The two-trials rule (2TR) is compared to replication
@@
 
-Figure \ref{fig1:fig5} compares for $c=1$ the Type-I error rate \eqref{eq1:T1E} of
+Figure \ref{fig1:fig5} compares for $c=1$ the Type I error rate \eqref{eq1:T1E} of
 replication success at the golden and at the nominal level with the two-trials
-rule for different values of $\alpha$. The Type-I error rate of the two-trials
+rule for different values of $\alpha$. The Type I error rate of the two-trials
 rule is $\alpha^2$ and the replication success approach at the nominal level
-always has a much smaller Type-I error rate than $\alpha^2$. At the golden level
-the Type-I error rate of the replication success approach is much closer to
+always has a much smaller Type I error rate than $\alpha^2$. At the golden level
+the Type I error rate of the replication success approach is much closer to
 $\alpha^2$, still slightly smaller if $\alpha < 0.058$. For $\alpha = 0.058$ the
-Type-I error rate is equal to the Type-I error rate $0.058^2 = 0.34\%$ of the
-two-trials rule and for $\alpha > 0.058$ the Type-I error rate is slightly
-larger than $\alpha^2$. The Type-I error rate for replication success decreases
+Type I error rate is equal to the Type I error rate $0.058^2 = 0.34\%$ of the
+two-trials rule and for $\alpha > 0.058$ the Type I error rate is slightly
+larger than $\alpha^2$. The Type I error rate for replication success decreases
 with increasing $c$, so as long as the replication sample size is not smaller
-than the original sample size, Type-I error control at $\alpha^2$ is guaranteed
+than the original sample size, Type I error control at $\alpha^2$ is guaranteed
 at the golden level for any one-sided level $\alpha < 0.058$.
@@
 than the original one. Compared to the two-trials rule, the golden level offers
-uniform gains in project power and controls the Type-I error rate at any
+uniform gains in project power and controls the Type I error rate at any
 one-sided level $\alpha < 0.058$ if the replication sample size

### 2022-12-09 paper3.tex
one-sided sceptical p

@@
    \multicolumn{1}{c}{\textbf{Constraints}} \\
-   {\scriptsize -- type-I error rate requirements} \\
+   {\scriptsize -- type I error rate requirements} \\
    {\scriptsize -- cost/availability constraints} \\

### 2022-12-09 paper4.tex
one-sided sceptical p

@@
 to achieve that false positive risk. Of specific interest is the value FPR =
-5\%, because many scientists believe that a Type-I error of 5\% is equivalent to
+5\%, because many scientists believe that a Type I error of 5\% is equivalent to
 a FPR of 5\% \citep{Greenland2016}. This is of course not true and we follow

### 2022-12-09 preface.tex
nicer toc
Lisa feedback
one-sided sceptical p

@@
 \section*{Preface}
-\addcontentsline{toc}{chapter}{Preface}
+\addcontentsline{toc}{chapter}{\texorpdfstring{\phantom{IV}Preface}{Preface}}
 
@@
 replication studies'' (project
-\href{https://data.snf.ch/grants/grant/189295}{\#189295}) awarded to Leonard
+\href{https://data.snf.ch/grants/grant/189295}{\#189295}) awarded to Leonhard
 Held.
@@
 alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
-Dafne, Dominik, Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas,
-Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Martin,
-Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala, Torsten, and Ulrike.
-Another thanks goes to my friends from the Department of Psychological Methods
-from the University of Amsterdam (in alphabetical order): Adam, Alexander,
-Alexandra, Alessandra, Alejandro, Angelika, Bruno, Don, František, Frederik,
-Jason, Johnny, Joris, Jill, Julia, Lukas, Maarten, Michelle, Nora, Omid,
-Quentin, René, Serjan, Suzanne, and Ting. I also want to thank my good friends
-from outside of academia (in alphabetical order): Chronis, Dani, Eleftheria,
-Flo, Fabi, Giuachin, Mirela, and Peter. A special thanks goes to Ada. Finally, I
-thank my family: Beni, Christa, Elisabeth, Fabian, Harry, Markus, Maja, and
-Noemi for their support.
+Beate, Beni, Dafne, Dominik, Eveline, Eva, Franscesca, Felix, Julia, Klaus,
+Kelly, Lucas, Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria,
+Marielena, Martin, Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala,
+Torsten, and Ulrike. Another thanks goes to my friends from the Department of
+Psychological Methods from the University of Amsterdam (in alphabetical order):
+Adam, Alexander, Alexandra, Alessandra, Alejandro, Angelika, Bruno, Don,
+František, Frederik, Jason, Johnny, Joris, Jill, Julia, Lukas, Maarten,
+Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also want to
+thank my good friends from outside of academia (in alphabetical order): Chronis,
+Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special thanks goes
+to Ada. Finally, I thank my family: Beni, Christa, Elisabeth, Fabian, Harry,
+Markus, Maja, and Noemi for their support.
 

### 2022-12-09 intro.Rnw
new comments Leo

@@
                                  \mbox{$\sigma_{m} = (1/\sigma^{2}_{o} + 1/\sigma^{2}_{r})^{-1/2}$}.
-                                 Usually $\alpha = 5\%$. \\
+                                 There are no established conventions regarding the level $\alpha$.
+    \\
                    & \\
@@
 often interested in understanding between-replication heterogeneity \citep[\eg{}
-in][]{Klein2018}.
+in][]{Klein2018}. In contrast to the ordinary significance criterion, it is less
+established which level $\alpha$ should be used for thresholding the
+meta-analytic $p$-value. Some replication projects have used the same level as
+for the significance approach \citep{Opensc2015, Camerer2016, Errington2021},
+whereas others have used a smaller level as the pooled estimate is based on both
+data sets \citep[\eg{} $\alpha = 0.5\%$ in][]{Camerer2018}.
 
@@
     if (dollar) x <- "$" else x <- ""
-    paste0("[", x, format(round(lower, digits), nsmall = digits), x,
-           " to ", x, format(round(upper, digits), nsmall = digits), x, "]")
+    paste0("(", x, format(round(lower, digits), nsmall = digits), x,
+           " to ", x, format(round(upper, digits), nsmall = digits), x, ")")
 }
@@
     } else {
-        out <- as.character(signif(x, digits = digits))
+        out <- format(round(x, digits), nsmall = digits)
         if (phantom && (x >= 0)) {
@@
 colnames(rpcbXtable) <- c("(P, X, E)",
-                          "$\\that_o$", "[95\\% CI]",
-                          "$\\that_r$", "[95\\% CI]",
-                          "$\\that_m$", "[95\\% CI]",
+                          "$\\that_o$", "(95\\% CI)",
+                          "$\\that_r$", "(95\\% CI)",
+                          "$\\that_m$", "(95\\% CI)",
                           "$c$",
@@
 \begin{align}
-  \left[\mu_{\text{post}} - z_{\alpha/2} \, \sigma_{\text{post}},
-  \mu_{\text{post}} + z_{\alpha/2} \, \sigma_{\text{post}}\right]
+  \mu_{\text{post}} \pm z_{\alpha/2} \, \sigma_{\text{post}}
   \label{eq:postCI}
@@
 other definitions of statistical evidence and in subsequent chapters of this
-thesis (Paper\ref{PaperII} and Paper\ref{PaperIV}) we will extend this
+thesis (Paper~\ref{PaperII} and Paper~\ref{PaperIV}) we will extend this
 reverse-Bayes procedure to employ alternative measures of evidence, such as
@@
 % which proposed a reverse-Bayes method.
-The last part (Paper~\ref{PaperVI}) is on meta-scientific perspectives on
+The last part (Paper~\ref{PaperVI}) deals with meta-scientific perspectives of
 methodological research.

### 2022-12-12 intro.Rnw
formatting

@@
 scientific knowledge (\eg{} market approval of a drug). The results from
-replication studies may thus have real world consequences, % , such as deciding
+replication studies may hence have real world consequences, % , such as deciding
 % whether we receive the recommendation to get vaccinated (a consequence that
@@
 @
-\caption{Results for 132 effects from the Reproducibility Project: Cancer
-  Biology \citep{Errington2021} for which effect estimates and standard errors
+\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
+  Biology'' \citep{Errington2021} for which effect estimates and standard errors
   are available on standardized mean difference (SMD) scale. The right plot
@@
 @
-\caption{UpSet plot for data on 132 effects from the Reproducibility Project:
-  Cancer Biology \citep{Errington2021} for which effect estimates and standard
+\caption{UpSet plot for data on 132 effects from the ``Reproducibility Project:
+  Cancer Biology'' \citep{Errington2021} for which effect estimates and standard
   errors are available on the standardized mean difference scale. Shown are the
@@
   \centering
-  \caption{Subset of results from the Reproducibility Project: Cancer Biology
-    \citep{Errington2021}. (P, X, E) denotes effect number E from experiment
-    number X, from original paper number P. Shown are original $\that_{o}$,
-    replication $\that_{r}$, and pooled effect estimate $\that_{m}$ with 95\%
-    confidence intervals, variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$,
-    relative effect estimate $d = \that_{r}/\that_{o}$, original
-    \textit{p}-value $p_{o}$, replication \textit{p}-value $p_{r}$,
-    meta-analytic \textit{p}-value $p_{m}$, $Q$-test \textit{p}-value $p_{Q}$,
-    and sceptical \textit{p}-value $p_{\mathrm{S}}$. A replication success
-    (green) threshold of $\alpha = 5\%$ is used for the \textit{p}-values and
-    $d_{\text{min}} = 1$ for the relative effect estimate.}
+  \caption{Subset of results from the ``Reproducibility Project: Cancer
+    Biology'' \citep{Errington2021}. (P, X, E) denotes effect number E from
+    experiment number X, from original paper number P. Shown are original
+    $\that_{o}$, replication $\that_{r}$, and pooled effect estimate $\that_{m}$
+    with 95\% confidence intervals, variance ratio
+    $c = \sigma^{2}_{o}/\sigma^{2}_{r}$, relative effect estimate
+    $d = \that_{r}/\that_{o}$, original \textit{p}-value $p_{o}$, replication
+    \textit{p}-value $p_{r}$, meta-analytic \textit{p}-value $p_{m}$, $Q$-test
+    \textit{p}-value $p_{Q}$, and sceptical \textit{p}-value $p_{\mathrm{S}}$. A
+    replication success (green) threshold of $\alpha = 5\%$ is used for the
+    \textit{p}-values and $d_{\text{min}} = 1$ for the relative effect
+    estimate.}
   \label{tab:RPCB}
@@
   data from the original study (Paper 9, Experiment 2, Effect 5) and its three
-  replication studies from the Reproducibility Project: Cancer Biology
+  replication studies from the ``Reproducibility Project: Cancer Biology''
   \citep{Errington2021}. Shown are effect estimates and prior/posterior means
@@
 from~\eqref{eq:pboxNorm} computed for three example replication studies from the
-Replication Project: Cancer Biology. We see that larger effect estimates show
-smaller prior predictive $p$-values $p_{\text{Box}}$, indicating more prior-data
-conflict. This is because the standard errors from all three replications are
-roughly the same size, so that the distance between zero and the replication
-effect estimate matters most. The $p$-values suggest that there is hardly any
-conflict between the sceptical prior and the first two replications (those with
-$p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
+``Replication Project: Cancer Biology''. We see that larger effect estimates
+show smaller prior predictive $p$-values $p_{\text{Box}}$, indicating more
+prior-data conflict. This is because the standard errors from all three
+replications are roughly the same size, so that the distance between zero and
+the replication effect estimate matters most. The $p$-values suggest that there
+is hardly any conflict between the sceptical prior and the first two
+replications (those with $p_{\text{Box}} = \Sexpr{pboxFormat[1]}$ and
 $p_{\text{Box}} = \Sexpr{pboxFormat[2]}$), while the conflict is larger for the

### 2022-12-12 paper1.tex
formatting

@@
 
+\sloppy
 Figure~\ref{fig1:fig3} compares the power for replication success
@@
 \end{equation}
-where $\dmin$ is given in \eqref{eq1:res}. Predictive power, which is conditional
-power averaged over a $\Nor(\hat \theta_o, \sigma_o^2)$ distribution for the
-effect size $\theta$, could also be calculated, then
+where $\dmin$ is given in \eqref{eq1:res}. Predictive power, which is
+conditional power averaged over a \mbox{$\Nor(\hat \theta_o, \sigma_o^2)$}
+distribution for the effect size $\theta$, could also be calculated, then
 \mbox{$d \given \hat \theta_o \sim \Nor(1, (1+1/c)/z_o^2)$}. Conditional and

### 2022-12-12 paper2.tex
formatting

@@
 
-    \item \textbf{Original study}:
-    For the original effect estimate
-$\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$ consider the point null
-hypothesis $H_0 \colon \theta = 0$ vs. $\HS \colon \theta \neq 0$. Fix a level
-$\gamma \in (0, 1)$ and determine the sufficiently sceptical prior under the
-alternative $\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ such that the
+    \item \textbf{Original study}: For the original effect estimate
+          $\that_o \given \theta \sim \Nor(\theta, \sigma^2_o)$ consider the
+          point null hypothesis $H_0 \colon \theta = 0$ vs.
+          $\HS \colon \theta \neq 0$. Fix a level $\gamma \in (0, 1)$ and
+          determine the sufficiently sceptical prior under the alternative
+          $\theta \given \HS \sim \Nor(0, \gy \cdot \sigma^2_o)$ such that the
           Bayes factor contrasting $H_0$ to $\HS$
           is $$\BFcol{0}{\mathrm{S}}(\hat{\theta}_o; \gy) = \gamma.$$ The prior
-$\theta \given \HS$ represents a \emph{sceptic} who remains unconvinced about
-the presence of an effect at level $\gamma$.
-
-    \item \textbf{Replication study}:
-          For the replication effect estimate
-$\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ compute the Bayes factor
-contrasting the sceptic $\HS \colon \theta \sim \Nor(0, \gy \cdot \sigma^2_o)$
-to an advocate $\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$. Declare
+          $\theta \given \HS$ represents a \emph{sceptic} who remains
+          unconvinced about the presence of an effect at level $\gamma$.
+
+    \item \textbf{Replication study}: For the replication effect estimate
+          $\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ compute the
+          Bayes factor contrasting the sceptic
+          $\HS \colon \theta \sim \Nor(0, \gy \cdot \sigma^2_o)$ to an advocate
+          \mbox{$\HA \colon \theta \sim \Nor(\that_o, \sigma^2_o)$}. Declare
           \emph{replication success} at level $\gamma$ if
@@
 with $\lw{-1}(\cdot)$ the branch of the Lambert $W$ function \citep{Corless1996}
-that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, see Appendix
+that satisfies \mbox{$W(y) \leq -1$} for $y \in [-e^{-1}, 0)$, see Appendix
 \ref{appendix:lambertW} for details about the Lambert $W$ function. The
@@
 the variances $\sigma_{i}^{2} = \kappa/n$ are inversely proportional to the
-sample size $n = n_{o} = n_{r}$ for the same unit variance $\kappa$ in both
-studies. Letting the sample size $n$ go to infinity is then equivalent to
+sample size \mbox{$n = n_{o} = n_{r}$} for the same unit variance $\kappa$ in
+both studies. Letting the sample size $n$ go to infinity is then equivalent to
 $\sigma_{o}^{2} \downarrow 0$ and $c = \sigma^{2}_{r}/\sigma^{2}_{o} = 1$. With
-decreasing variances the estimates will
-converge to the true effect size ($\that_{i} \to \theta_{*}$), the relative
-effect estimate will converge to one ($d \to 1$), and the $z$-values will go to
-infinity ($\abs{z_{i}} \to \infty$). Since $c = 1$, the sceptical Bayes factor
-is given by equation~\eqref{eq2:BFsc1}. Moreover, we are allowed to use of the
-approximation $\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$ as the argument of
-the Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
+decreasing variances the estimates will converge to the true effect size
+($\that_{i} \to \theta_{*}$), the relative effect estimate will converge to one
+($d \to 1$), and the $z$-values will go to infinity ($\abs{z_{i}} \to \infty$).
+Since $c = 1$, the sceptical Bayes factor is given by
+equation~\eqref{eq2:BFsc1}. Moreover, we are allowed to use of the approximation
+\mbox{$\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$} as the argument of the
+Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
 350]{Corless1996}. Taken together, we have
@@
 where $F(\cdot)$ is the hypergeometric function, $e = x_{1o} + 1/2$,
-$f = n_{1o} - x_{1o} + 1/2$, $g = x_{2o} + 1/2$, $h = n_{2o} - x_{2o} + 1/2$,
+$f = n_{1o} - x_{1o} + 1/2$, \mbox{$g = x_{2o} + 1/2$},
+$h = n_{2o} - x_{2o} + 1/2$,
 $C = \text{B}(e + g, f + h)/\{\text{B}(e, f) \text{B}(g, h)\}$, and
@@
 estimates are substantially larger than zero ($\that_o = 0.74$ with
-$\minBF_{o} < 1/1000$ and $\that_r = 0.36$ with $\minBF_{r} = 1/3.3$), yet the
-$Q$-statistic indicates some incompatibility ($Q = 3.51$), which explains why
-$\tilde{p}_{\mathrm{S}} = 0.003$, but $\BFs = 1/1.6$ only.
+\mbox{$\minBF_{o} < 1/1000$} and $\that_r = 0.36$ with $\minBF_{r} = 1/3.3$),
+yet the $Q$-statistic indicates some incompatibility ($Q = 3.51$), which
+explains why $\tilde{p}_{\mathrm{S}} = 0.003$, but $\BFs = 1/1.6$ only.
 
@@
 where $\lw{-1}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
-$W(y) \leq -1$ for $y \in [-e^{-1}, 0)$, ensuring that $\gy \leq \gminBFo$. See
-Appendix~\ref{appendix:lambertW} for details about the Lambert $W$ function. For
-some $z_o$, equation \eqref{sspv2} can also be satisfied for negative $\gy$,
-which is why we need to add the condition $-z_o^2/q \geq 1$ in equation
-\eqref{eq2:solutionvss}, such that $\gy$ is a valid relative variance.
+$W(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$}, ensuring that
+$\gy \leq \gminBFo$. See Appendix~\ref{appendix:lambertW} for details about the
+Lambert $W$ function. For some $z_o$, equation \eqref{sspv2} can also be
+satisfied for negative $\gy$, which is why we need to add the condition
+$-z_o^2/q \geq 1$ in equation \eqref{eq2:solutionvss}, such that $\gy$ is a
+valid relative variance.
 
@@
   the height of the lowest intersection of
-  $\BFcol{0}{\text{S}}(\hat{\theta}_o; \gy) = \gamma$ and
+  \mbox{$\BFcol{0}{\text{S}}(\hat{\theta}_o; \gy) = \gamma$} and
   $\BFcol{\text{S}}{\text{A}}(\hat{\theta}_r; \gy)$
@@
 For now assume $\that_o > 0$. The marginal likelihood of the replication effect
-estimate $\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$ under the
+estimate \mbox{$\that_r \given \theta \sim \Nor(\theta, \sigma^2_r)$} under the
 truncated advocacy prior

### 2022-12-12 paper3.tex
formatting

@@
 self-replication, and with variance
-$\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$
+\mbox{$\sigma^{2}_{o} + \tau^{2} = 0.05^{2} + 0.05^{2} \approx 0.07^{2}$}
 for an external-replication. Figure~\ref{fig3:dpexample} (dark-gray solid lines)
@@
 success and the required sample size are implemented in the R package
-\textbf{BayesRepDesign} (see Appendix) %~\ref{app:package})
-for all analysis methods discussed in the following.
+\texttt{BayesRepDesign} (see Appendix~\ref{app3:package}) for all analysis
+methods discussed in the following.
 
@@
 We now assume that the one-sided original $p$-value was significant at some
-level $\alpha$, \ie{} $p_{o} = 1 - \Phi(\that_{o}/\sigma_{o}) \leq \alpha$.
-Replication success at level $\alpha$ % with the two-trials
-is then achieved if the replication $p$-value is also significant, \ie{}
+level $\alpha$, \ie{}
+\mbox{$p_{o} = 1 - \Phi(\that_{o}/\sigma_{o}) \leq \alpha$}. Replication success
+at level $\alpha$ % with the two-trials
+is then achieved if the replication \mbox{$p$-value} is also significant, \ie{}
 $p_{r} = 1 - \Phi(\that_{r}/\sigma_{r}) \leq \alpha$, which implies a success
@@
 ``conditional'' design prior %from Section~\ref{sec3:designpredictive}
-($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$), we obtain the
+\mbox{($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$)}, we obtain the
 well-known sample size formula \citep[ch. 3.3]{Matthews2006}
@@
 \section{The BayesRepDesign R package}
-\label{app:package}
+\label{app3:package}
 
@@
     \underbrace{\sqrt{\frac{\tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}}{\tau^{2} + \sigma^{2}_{o} +
-    \sigmatheta^{2}}}}_{\to 1} \, \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{
+    \sigmatheta^{2}}}}_{\to 1} \\
+  &\phantom{= \lim_{\sigmatheta^{2} \to \infty}  \int_{0}^{+\infty}} \times \exp\bigg[-\frac{1}{2}\bigg\{\underbrace{
     \frac{(\that_{o} - \mutheta)^{2}}{\tau^{2} + \sigma^{2}_{o} + \sigmatheta^{2}}}_{\downarrow 0} -
@@
 \label{sec3sup:2TR}
+\sloppy
 The two-trials rule is the most common analysis approach for replication
@@
 the original effect estimate was statistically significant at level $\alpha$,
-\ie{} $p_{o} \leq \alpha$. Replication success at level $\alpha$ is then
+\ie{} \mbox{$p_{o} \leq \alpha$}. Replication success at level $\alpha$ is then
 established if the replication effect estimate $\that_{r}$ is also statistically
@@
 with standard error
-$\sigma_{r*} = 1/\surd\{\sum_{i}^{m}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\}$ can be
-computed. If the between-replication heterogeneity variance $\tau^{2}_{r}$ is
-set to zero this corresponds to the fixed effects estimate of $\theta$, while
-estimating $\tau^{2}_{r}$ from the data corresponds to the random effects
-estimate. Replication success at level $\alpha$ is then established if the
-replication $p$-value is smaller than $\alpha$, \ie{}
+\mbox{$\sigma_{r*} = 1/\surd\{\sum_{i}^{m}1/(\sigma^{2}_{ri} + \tau^{2}_{r})\}$}
+can be computed. If the between-replication heterogeneity variance
+$\tau^{2}_{r}$ is set to zero this corresponds to the fixed effects estimate of
+$\theta$, while estimating $\tau^{2}_{r}$ from the data corresponds to the
+random effects estimate. Replication success at level $\alpha$ is then
+established if the replication $p$-value is smaller than $\alpha$, \ie{}
 $p_{r*} = 1 - \Phi(\that_{r*}/\sigma_{r*}) \leq \alpha$. With some algebra one
@@
 quantify the evidence for the null hypothesis $H_{0}\colon \theta = 0$ relative
-to the alternative hypothesis $H_{1} \colon \theta \sim f(\theta \given x_{o})$,
-which postulates that the effect size $\theta$ is distributed according to its
-posterior distribution based on the original data $x_{o}$. Assume again a normal
-model $\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with
-$\that_{i}$ an estimate of the effect size $\theta$ from study $i \in \{o, r\}$
-and $\sigma_{i}$ the corresponding standard error (assumed to be know), and that
-we use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which
-arises from updating an initial flat prior for $\theta$ the original data
+to the alternative hypothesis
+\mbox{$H_{1} \colon \theta \sim f(\theta \given x_{o})$}, which postulates that
+the effect size $\theta$ is distributed according to its posterior distribution
+based on the original data $x_{o}$. Assume again a normal model
+$\that_{i} \given \theta \sim \Nor(\theta, \sigma^{2}_{i})$ with $\that_{i}$ an
+estimate of the effect size $\theta$ from study $i \in \{o, r\}$ and
+$\sigma_{i}$ the corresponding standard error (assumed to be know), and that we
+use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which arises
+from updating an initial flat prior for $\theta$ the original data
 $x_{o} = \{\that_{o}, \sigma_{o}\}$. The replication Bayes factor is then
@@
 to the alternative hypothesis
-$H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$. The marginal density
-of the replication data under the null hypothesis is simply
+\mbox{$H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$}. The marginal
+density of the replication data under the null hypothesis is simply
 $\bthat_{r} \given H_{0} \sim \Nor_{m}\{0 \, \bone_{m}, \diag(\bsigma^{2} + \tau^{2}_{r} \, \bone_{m}\}$,
@@
 \begin{align*}
-        f(\hat{\theta}_{r} \given H_{1})
-        &= \int f(\hat{\theta}_{r} \given \theta) f(\theta \given H_{1})
+        f(\hat{\btheta}_{r} \given H_{1})
+        &= \int f(\hat{\btheta}_{r} \given \theta) f(\theta \given H_{1})
                         \, \text{d}\theta \\
@@
 \begin{align*}
-  \BF_{01}(\hat{\theta}_{r})
-  &= \frac{f(\hat{\theta}_{r} \given H_{0})}{f(\hat{\theta}_{r} \given H_{1})}
+  \BF_{01}(\hat{\btheta}_{r})
+  &= \frac{f(\hat{\btheta}_{r} \given H_{0})}{f(\hat{\btheta}_{r} \given H_{1})}
     = \sqrt{1 + \sigma^{2}_{o}/\sigma^{2}_{r*}}  \exp\left[-\frac{1}{2}\left\{
@@
 %% Bibliography
+\newpage
 \bibliographystyle{apalikedoiurl}

### 2022-12-12 paper4.tex
formatting

@@
 $\sigma_i$. The meta-analytic odds ratio estimate under the fixed-effect model
-(the pre-specified primary analysis) is $\widehat{\text{OR}} = 0.66$ [95\% CI
-$0.53$ to $0.82$], respectively $\hat \theta = -0.42$ [95\% CI $-0.63$ to
-$-0.20$] for the log odds ratio $\theta$, indicating evidence for lower
-mortality of patients treated with corticosteroids compared to patients
+(the pre-specified primary analysis) is \mbox{$\widehat{\text{OR}} = 0.66$ [95\%
+  CI $0.53$ to $0.82$]}, respectively \mbox{$\hat \theta = -0.42$ [95\% CI
+  $-0.63$ to $-0.20$]} for the log odds ratio $\theta$, indicating evidence for
+lower mortality of patients treated with corticosteroids compared to patients
 receiving usual care or placebo. The pooled effect estimate $\hat \theta$
@@
 It is also possible to apply the approach to the meta-analytic log odds ratio
-estimate $\hat \theta = -0.42$ [95\% CI $-0.63$ to $-0.20$] from all 7 studies
-combined. Then $\SL= 0.13$, so the meta-analytic estimate can be considered as
-non-credible if external evidence suggests that mortality reductions are
-unlikely to exceed $1-\exp(-\SL)=1 - 0.88 \approx 12 \%$. This illustrates that
-the meta-analytic estimate has gained credibility compared to the result from
-the RECOVERY study alone, despite the reduction in the effect estimate
-($\widehat{\text{OR}} = \exp(\hat \theta) = 0.66$ vs.~0.59 in the RECOVERY
-study).
+estimate \mbox{$\hat \theta = -0.42$ [95\% CI $-0.63$ to $-0.20$]} from all 7
+studies combined. Then $\SL= 0.13$, so the meta-analytic estimate can be
+considered as non-credible if external evidence suggests that mortality
+reductions are unlikely to exceed $1-\exp(-\SL)=1 - 0.88 \approx 12 \%$. This
+illustrates that the meta-analytic estimate has gained credibility compared to
+the result from the \mbox{RECOVERY} study alone, despite the reduction in the
+effect estimate ($\widehat{\text{OR}} = \exp(\hat \theta) = 0.66$ vs.~0.59 in
+the RECOVERY study).
 
@@
   trial \citep{RECOVERY2020}. The right plot illustrates how an advocacy prior
-  is used to challenge a non-significant finding from the REMAP-CAP trial
+  is used to challenge a non-significant finding from the \mbox{REMAP-CAP} trial
   \citep{REMAPCAP2020}. In both scenarios the posterior is fixed to be just
@@
 estimate showing efficacy, the relatively large uncertainty rendered the overall
-finding non-significant at the 5\% level ($\hat{\theta} = -0.34$ [95\% CI
-$-0.96$ to $0.29$]). Such an outcome is frequently (and wrongly) taken to imply
-no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
-limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{} $0.15$ on the
-odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
-advocates of the effectiveness of corticosteroids can regard the trial as
-providing credible evidence of effectiveness despite its non-significance if
-external evidence supports mortality reductions (in terms of odds) in the range
-0\% to 85\%. So broad an advocacy range reflects the fact that this relatively
-small trial provides only modest evidential weight, and thus little constraint
-on prior beliefs about the effectiveness of corticosteroids.
+finding non-significant at the 5\% level (\mbox{$\hat{\theta} = -0.34$ [95\% CI
+  $-0.96$ to $0.29$]}). Such an outcome is frequently (and wrongly) taken to
+imply no effect. The use of AnCred leads to a more nuanced conclusion. The
+advocacy limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{}
+$0.15$ on the odds ratio scale, see also the right plot in Figure
+\ref{fig4:anCredEx}. Thus advocates of the effectiveness of corticosteroids can
+regard the trial as providing credible evidence of effectiveness despite its
+non-significance if external evidence supports mortality reductions (in terms of
+odds) in the range 0\% to 85\%. So broad an advocacy range reflects the fact
+that this relatively small trial provides only modest evidential weight, and
+thus little constraint on prior beliefs about the effectiveness of
+corticosteroids.
 
@@
 For example, from Figure~\ref{fig4:covid19-meta} the RECOVERY trial has an
-overall mortality rate $R=(95 + 283)/(324 + 683) = 37.54\%$ and $\SL = 0.178$ at
-the $\alpha = 5\%$ level $(z_{\alpha/2} = 1.96)$ corresponds to
+overall mortality rate \mbox{$R=(95 + 283)/(324 + 683) = 37.54\%$} and
+$\SL = 0.178$ at the $\alpha = 5\%$ level $(z_{\alpha/2} = 1.96)$ corresponds to
 $\tau^2=0.091^2$, so $m = 389$ and $n = 648$ (these are integer approximations
@@
 \citet{Matthews2018} described in Section~\ref{sec4:nonSigAnCred} has a mean
-$\mu = \mbox{AL}/2$ and variance $\tau^{2} = \AL^2/(2z_{\alpha/2})^2$. Under the
-large study assumption and equating the latter with \eqref{eq4:SElogOR} as
-before, the corresponding number of events needed to be observed in both arms of
-the hypothetical study is $m = 2/\tau^{2} = 8 \, z_{\alpha/2}^2/\mbox{AL}^2$. To
-incorporate the non-zero mean by which this prior represents advocacy, these $m$
-events are taken to have been observed among participants allocated to the two
-study arms in the ratio $1 \colon K$ where $K = \exp(\mu) = \exp(\AL/2)$, the
-allocation being such that it increases the relative evidential weight for the
-hypothesis ``negated'' by the non-significance.
+\mbox{$\mu = \mbox{AL}/2$} and variance $\tau^{2} = \AL^2/(2z_{\alpha/2})^2$.
+Under the large study assumption and equating the latter with
+\eqref{eq4:SElogOR} as before, the corresponding number of events needed to be
+observed in both arms of the hypothetical study is
+$m = 2/\tau^{2} = 8 \, z_{\alpha/2}^2/\mbox{AL}^2$. To incorporate the non-zero
+mean by which this prior represents advocacy, these $m$ events are taken to have
+been observed among participants allocated to the two study arms in the ratio
+$1 \colon K$ where \mbox{$K = \exp(\mu) = \exp(\AL/2)$}, the allocation being
+such that it increases the relative evidential weight for the hypothesis
+``negated'' by the non-significance.
 
@@
 where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
-$text{W}(y) \leq -1$ for $y \in [-e^{-1}, 0)$ \citep{Corless1996}, see the
+$\text{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see the
 Appendix in \citep{Pawel2020b} for a proof.
@@
   variation from the prior is fixed to
-  $\text{CV} = \tau/\mu = 1/z(\gamma=1/3) = 0.67$, where $z(\gamma)$ is given in
-  \eqref{eq4:zgamma}. The RECOVERY and the CAPE COVID findings are challenged
-  such that $\BF_{01} = 1/3$, for the other trials such a prior does not exist.}
+  \mbox{$\text{CV} = \tau/\mu = 1/z(\gamma=1/3) = 0.67$}, where $z(\gamma)$ is
+  given in \eqref{eq4:zgamma}. The RECOVERY and the CAPE COVID findings are
+  challenged such that $\BF_{01} = 1/3$, for the other trials such a prior does
+  not exist.}
 \label{fig4:bf}
@@
 sufficiently sceptical prior to an optimistic prior, which they defined as
-$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$ the posterior of $\theta$
-based on the data and the reference prior $f(\theta) \propto 1$. The optimistic
-prior therefore represents the position of a proponent who takes the original
-claim at face value. This leads to the second Bayes factor being
+\mbox{$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$} the posterior of
+$\theta$ based on the data and the reference prior $f(\theta) \propto 1$. The
+optimistic prior therefore represents the position of a proponent who takes the
+original claim at face value. This leads to the second Bayes factor being
 \begin{align}
@@
 non-events in the control arm (such that the mortality rate in the control arm
-is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
+is the same as in the CAPE COVID trial). Note that the advocacy prior may not be
 unique, \eg{} for the CAPE COVID finding the prior with relative mean

### 2022-12-12 intro.Rnw
one-sided sceptical p-value

@@
 ind <- !is.na(rpcb$zo) & !is.na(rpcb$zr) & !is.na(rpcb$c)
-rpcb$ps2 <- NA
-rpcb$ps2[ind] <- pSceptical(zo = rpcb$zo[ind], zr = rpcb$zr[ind], c = rpcb$c[ind],
-                            alternative = "two.sided", type = "nominal")
+rpcb$ps1 <- NA
+rpcb$ps1[ind] <- pSceptical(zo = rpcb$zo[ind], zr = rpcb$zr[ind], c = rpcb$c[ind],
+                            alternative = "one.sided", type = "nominal")
 
@@
 Table~\ref{tab:RPCB}. The subset is chosen such that from every original study
-one effect and one replication of that effect is included. For no single study
-pair in the table are all commonly used criteria satisfied simultaneously. For
-instance, the first two replications satisfy the significance criterion
-($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic significance ($p_{m} < 0.05$)
-and the $Q$-test/prediction interval criterion ($p_{Q} > 0.05$), yet the
-replication effect estimate is smaller than the original one ($d < 1$).
-Similarly, there is no single study pair for which all criteria indicate
-replication failure. For example, the last replication (\#20) is a clear failure
-with respect to the relative effect estimate ($d < 1$) and the significance
-criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does not indicate
-evidence for inconsistency of the two effect estimates ($p_{Q} > 0.05$).
+one effect and one replication of that effect is included. For the three
+replications at the bottom of the table (\#18, \#19, and \#20), all criteria
+indicate replication failure. For the remaining majority of the studies, the
+conclusions are more ambiguous; for no single replication study are all criteria
+satisfied simultaneously. For instance, the first three studies satisfy the
+significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic
+significance ($p_{m} < 0.05$) and the $Q$-test/prediction interval criterion
+($p_{Q} > 0.05$), yet the replication effect estimate is smaller than the
+original one ($d < 1$).
+% For example, replication \#17 is a clear
+% failure with respect to the relative effect estimate ($d < 1$) and the
+% significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does
+% not indicate evidence for inconsistency of the two effect estimates
+% ($p_{Q} > 0.05$).
 
@@
     \textit{p}-value $p_{r}$, meta-analytic \textit{p}-value $p_{m}$, $Q$-test
-    \textit{p}-value $p_{Q}$, and sceptical \textit{p}-value $p_{\mathrm{S}}$. A
-    replication success (green) threshold of $\alpha = 5\%$ is used for the
-    \textit{p}-values and $d_{\text{min}} = 1$ for the relative effect
-    estimate.}
+    \textit{p}-value $p_{Q}$, and one-sided sceptical \textit{p}-value
+    $p_{\mathrm{S}}$. A replication success (green) threshold of $\alpha = 5\%$
+    is used for two-sided \textit{p}-values, $\alpha = 2.5\%$ for one-sided
+    $p$-values, and $d_{\text{min}} = 1$ for the relative effect estimate.}
   \label{tab:RPCB}
@@
     ungroup() |>
-    arrange(pr2) |>
+    arrange(ps1) |>
     mutate(smdoFormat = signif(smdo, 3),
@@
            pm2Format = tableFormat(x = pm2),
-           ps2Format = tableFormat(x = ps2),
-           pQFormat = tableFormat(x = pQ),
+           ps1Format = tableFormat(x = ps1, threshold = 0.025),
+           pQFormat = tableFormat(x = pQ, col1 = "dark2orange",
+                                  col2 = "dark2green"),
            cioFormat = ciFormat(lower = cioL, upper = cioU, dollar = TRUE),
@@
            c, dFormat,
-           po2Format, pr2Format, pm2Format, pQFormat, ps2Format
+           po2Format, pr2Format, pm2Format, pQFormat, ps1Format
            )
@@
 
-The sceptical $p$-value has several interesting properties \citep[Section
-3]{Held2020}: First, it is always larger than the maximum of the original and
-replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
-both $p$-values have to be smaller than $\alpha$ such that replication success
-at level $\alpha$ is possible. The sceptical $p$-value hence requires
-\emph{both} studies to be sufficiently convincing on their own (in terms of
-their $p$-values), similar to the significance criterion for replication
-success. Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the
-relative effect estimate $d = \that_{r}/\that_{o}$ decreases, the sceptical
-$p$-value increases, meaning that shrinkage of the replication effect estimate
-is penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$
-and $p_{r}$). The sceptical $p$-value thus takes effect shrinkage into account,
+The sceptical $p$-value has several interesting
+properties \citep[Section 3]{Held2020}: First, it is always larger than the
+maximum of the original and replication $p$-values
+($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that both $p$-values have to be
+smaller than $\alpha$ such that replication success at level $\alpha$ is
+possible. The sceptical $p$-value hence requires \emph{both} studies to be
+sufficiently convincing on their own (in terms of their $p$-values), similar to
+the significance criterion for replication success. Second, if the $p$-values
+$p_{o}$ and $p_{r}$ remain fixed but the relative effect estimate
+$d = \that_{r}/\that_{o}$ decreases towards zero, the sceptical $p$-value
+increases, meaning that shrinkage of the replication effect estimate is
+penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$ and
+$p_{r}$). The sceptical $p$-value thus takes effect shrinkage into account,
 unlike the significance criterion which can be achieved with any non-zero
@@
 anymore, despite its statistical significance.
-
-The results from the ``Reproducibility Project: Cancer Biology'' in
-Table~\ref{tab:RPCB} illustrate these two properties. The third study fails to
-achieve replication success at level $\alpha = 5\%$ with the sceptical
-$p$-value, even though the replication study was highly convincing (the effect
-estimate was almost five times as large as in the original study). Yet, as the
-approach requires both studies to be convincing on their own -- and the original
-study was not significant at the 5\% level -- replication success at this level
-is impossible with the sceptical $p$-value. The second property is illustrated
-by the fifth study. Here the original study was convincing and the replication
-study also achieved significance. However, the effect estimate from the
-replication was roughly 60\% smaller than the one from the original study, and
-significance is merely achieved because the standard error was much smaller
-(\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value
-is therefore only $p_{\text{S}} = 0.25$, indicating hardly any evidence for
-replication success.
-
-<< "paradox-example" >>=
-smdo <- 3
-smdr <- -3
-so <- sr <- 1
-ps2 <- pSceptical(zo = smdo/so, zr = smdr/sr, c = so^2/sr^2,
-                  alternative = "two.sided", type = "nominal")
-@
 
@@
 % $\that_{r} = \Sexpr{smdr}$, and $\sigma_{o} = \sigma_{r} = 1$, this would lead
-% to $\ps = \Sexpr{pFormat(ps2)}$, and the sceptical $p$-value continues to
+% to $\ps = \Sexpr{pFormat(ps1)}$, and the sceptical $p$-value continues to
 % decreases with decreasing replication effect estimates.
@@
 \begin{align*}
-  \tilde{p}_{\text{S}} =
+  p_{\text{S}} =
   \begin{cases}
-    \ps/2 & \text{if} ~\sign(\that_{o}) = \sign(\that_{r}) \\
-    1 - \ps/2 & \text{if} ~ \sign(\that_{o}) \neq \sign(\that_{r}) \\
+   1 - \Phi(|z_{\text{S}}|) & \text{if} ~\sign(\that_{o}) = \sign(\that_{r}) \\
+   \Phi(|z_{\text{S}}|) & \text{if} ~ \sign(\that_{o}) \neq \sign(\that_{r}) \\
   \end{cases}
@@
 chapters only the one-sided version of the sceptical $p$-value will be used.
+
+The results from the ``Reproducibility Project: Cancer Biology'' in
+Table~\ref{tab:RPCB} illustrate the properties of the sceptical $p$-value. For
+example, study \#4 fails to achieve replication success at level
+$\alpha = 2.5\%$ with the one-sided sceptical $p$-value, even though the
+replication study was highly convincing (the effect estimate was almost five
+times as large as in the original study). Yet, as the approach requires both
+studies to be convincing on their own -- and the original study was not
+significant at the 2.5\% level (one-sided) -- replication success at this level
+is impossible with the sceptical $p$-value. The second property is illustrated
+by study \#8. Here the original study was convincing and the replication study
+also achieved significance. However, the effect estimate from the replication
+was roughly 60\% smaller than the one from the original study, and significance
+is merely achieved because the standard error was much smaller (\ie{} around
+$1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value is therefore
+only $p_{\text{S}} = 0.12$, indicating hardly any evidence for replication
+success.
+
+<< "paradox-example" >>=
+smdo <- 3
+smdr <- -3
+so <- sr <- 1
+ps1 <- pSceptical(zo = smdo/so, zr = smdr/sr, c = so^2/sr^2,
+                  alternative = "two.sided", type = "nominal")
+@
 

### 2022-12-14 abstract.tex
one-sided sceptical p
formatting and reproducibility

@@
 method is to challenge the data from the original study with a sceptical prior
-so that the resulting posterior distribution is no longer ``significant''. The
-goal of the replication study is then to show that the sceptical prior is
-unrealistic, and replication success is achieved if there is sufficient conflict
-between the prior and the replication data. The procedure can be summarized in a
-single quantitative measure, termed the sceptical $p$-value.
+distribution so that the resulting posterior distribution is no longer
+``significant''. The goal of the replication study is then to show that the
+sceptical prior is unrealistic, and replication success is achieved if there is
+sufficient conflict between the prior and the replication data. The procedure
+can be summarized in a single quantitative measure, termed the sceptical
+$p$-value.
 % extension 1
@@
 
-The last part of this thesis revolves around research integrity issues in
+The last part of this thesis takes a meta-scientific perspective on
 methodological research. Questionable research practices, such as selective

### 2022-12-14 intro.Rnw
formatting and reproducibility

@@
 example, how can we know whether the protective effect of a vaccine found in a
-study is a genuine effect or just a spurious finding? The answer to such
-questions is of high importance to researchers, decision makers, and the general
-population, and one way to obtain it is through \emph{replication studies}.
-
-A replication study consists of repeating the original study as close as
+study is indeed existent or whether it is just a spurious finding? The answer to
+such questions is of high importance to researchers, decision makers, and the
+general population, and one way to address them scientifically is through
+\emph{replication studies}.
+
+A replication study consists of repeating the original study as closely as
 possible but with new subjects. Such a study may yield similar results which
@@
 All of these are routinely reported in research articles, and if one of them is
-missing they typically can be calculated from the others. Using summary
+missing they can typically be calculated from the others. Using summary
 statistics is also often the only possible way for conducting the replication
@@
 ``replication success'' can almost always be achieved if the sample size of the
-studies is small enough as the prediction interval becomes wider with larger
-standard errors.
+studies is small enough, because the prediction interval becomes wider with
+larger standard errors.
 
@@
 large-scale project attempted to replicate 53 landmark studies from the field of
-cancer biology \citep[and would perhaps therefore better be named ``Replication
-Project'', see][for the distinction between ``replicabality'' and
+cancer biology \citep[and would perhaps better be named ``Replication Project'',
+see][for the distinction between ``replicabality'' and
 ``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
@@
 A detailed view for a subset of the data from the project is given in
-Table~\ref{tab:RPCB}. The subset is chosen such that from every original study
-one effect and one replication of that effect is included. For the three
-replications at the bottom of the table (\#18, \#19, and \#20), all criteria
-indicate replication failure. For the remaining majority of the studies, the
-conclusions are more ambiguous; for no single replication study are all criteria
-satisfied simultaneously. For instance, the first three studies satisfy the
-significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), meta analytic
-significance ($p_{m} < 0.05$) and the $Q$-test/prediction interval criterion
-($p_{Q} > 0.05$), yet the replication effect estimate is smaller than the
-original one ($d < 1$).
+Table~\ref{tab:RPCB}. The subset is randomly chosen such that from every
+original study one effect and one replication of that effect is included. For
+the three replications at the bottom of the table (\#18, \#19, and \#20), all
+criteria indicate replication failure. For the other replications, the
+conclusions are more ambiguous as in no single case are all criteria met
+simultaneously. For instance, the first three replications satisfy the
+significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic
+significance criterion ($p_{m} < 0.05$) and the $Q$-test/prediction interval
+criterion ($p_{Q} > 0.05$), yet the replication effect estimate is smaller than
+the original one so does not satisfy the relative effect size criterion
+($d < 1$). The fourth replication, on the other hand, satisfies the relative
+effect size criterion ($d \geq 1$) but fails to satisfy the significance
+criterion as the original study was not significant ($p_{o} > 0.05$).
 % For example, replication \#17 is a clear
@@
 \emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
-for assessing replication success. In the following, I will summarize its main
-ideas and technical underpinnings.
+for assessing replication success. In the following, I will summarize the
+methods and its technical underpinnings.
 
@@
 
-This shows that the reverse-Bayes approach based on sceptical priors can be used
-to formally challenge the finding of an original study. However, once this
+In this way the reverse-Bayes approach based on sceptical priors can be used to
+formally challenge the finding from an original study. However, once this
 sceptical prior is determined, the question becomes whether it is plausible in
@@
 criticism can be used for doing so.
-
-% \begin{figure}[!htb]
-%   \centering
-%   \begin{tikzpicture}[node distance = 5em, thick]
-%     % nodes %
-%     \node[text width=5em, text centered] (data) {Likelihood $f(\text{data} \,|\, \theta)$};
-%     \node[text width=3em, text centered] (prior) [left=6.5em of data] {Prior $f(\theta)$};
-%     \node[text width=5em, text centered] (post) [right=5em of data] {Posterior $f(\theta \,|\, \text{data})$};
-%     \node[text width=10em, text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
-%     \node[text width=10em, text centered] (FBinference) [below of=post] {Forward-Bayes inference};
-
-%     % edges %
-%     \draw [->, dotted] (prior) to [out=45, in=135, looseness=0.3] node[above]{Bayesian updating} (post);
-%     \draw [->, dashed] (post) to [out=225, in=315, looseness=0.3] node[below]{Bayesian downdating} (prior);
-%     \draw [->, dashed] (prior) to [out=270, in=90, looseness=0] (RBinference);
-%     \draw [->, dotted] (post) to [out=270, in=90, looseness=0] (FBinference);
-%   \end{tikzpicture}
-%   \caption{Schematic illustration of forward-Bayes and reverse-Bayes inference
-%     for an unknown parameter $\theta$.}
-%   \label{fig:illustrationRB}
-% \end{figure}
 
@@
 
-% In general,
-% a distinction can be made between checking for \emph{likelihood-data conflict}
-% and checking for \emph{prior-data conflict}. In the following, we will assume
-% that the likelihood is adequate and focus on the
-
 We now return to the replication setting. Having obtained a sceptical prior
@@
 $p$-value~\eqref{eq:pppval} is
-% the probability of observing replication effects larger in absolute value than
-% the observed one $\that_{r}$ under
 \begin{align}
@@
 \end{align*}
-similar to how ordinary one-sided $p$-values are defined. In the subsequent
-chapters only the one-sided version of the sceptical $p$-value will be used.
-
-The results from the ``Reproducibility Project: Cancer Biology'' in
-Table~\ref{tab:RPCB} illustrate the properties of the sceptical $p$-value. For
-example, study \#4 fails to achieve replication success at level
-$\alpha = 2.5\%$ with the one-sided sceptical $p$-value, even though the
-replication study was highly convincing (the effect estimate was almost five
-times as large as in the original study). Yet, as the approach requires both
-studies to be convincing on their own -- and the original study was not
-significant at the 2.5\% level (one-sided) -- replication success at this level
-is impossible with the sceptical $p$-value. The second property is illustrated
-by study \#8. Here the original study was convincing and the replication study
-also achieved significance. However, the effect estimate from the replication
-was roughly 60\% smaller than the one from the original study, and significance
-is merely achieved because the standard error was much smaller (\ie{} around
-$1/\surd c \approx 1/2.8$ times smaller). The sceptical $p$-value is therefore
-only $p_{\text{S}} = 0.12$, indicating hardly any evidence for replication
-success.
+similar to how ordinary one-sided $p$-values are defined. The one-sided
+sceptical $p$-value has similar properties as the two-sided version -- it is
+always larger than the one-sided $p$-values from original and replication
+studies, and it penalizes shrinkage of the replication effect estimate. In the
+subsequent chapters only the one-sided version of the sceptical $p$-value will
+be used.
+
+The last column of Table~\ref{tab:RPCB} shows the one-sided sceptical $p$-value
+for the subset of replications from the ``Reproducibility Project: Cancer
+Biology''. The results illustrate the previously discussed properties to require
+significance from both studies and to penalize effect shrinkage. For example,
+replication \#4 fails to achieve replication success at level $\alpha = 2.5\%$
+with the one-sided sceptical $p$-value, even though the replication study was
+highly convincing (the effect estimate was almost five times as large as in the
+original study). Yet, as the approach requires both studies to be convincing on
+their own -- and the original study was not significant at the 2.5\% level
+(one-sided) -- replication success at this level is impossible with the
+sceptical $p$-value. The second property is illustrated by replication \#8. Here
+both the original and replication studies were significance. However, the effect
+estimate from the replication was roughly 60\% smaller than the one from the
+original study, and significance is merely achieved because the standard error
+was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The
+sceptical $p$-value is therefore only $p_{\text{S}} = 0.12$, indicating less
+evidence for replication success.
 
@@
 % which proposed a reverse-Bayes method.
-The last part (Paper~\ref{PaperVI}) deals with meta-scientific perspectives of
+The last part (Paper~\ref{PaperVI}) deals with integrity issues in
 methodological research.
@@
 
-L. Held had the idea to apply the sceptical $p$-value method to the data from
-the four replication projects, which I collected for my master thesis. L. Held
-and C. Micheloud came up with the golden level. L. Held wrote an initial draft
-of the manuscript. L. Held, C. Micheloud, and I then iteratively worked on the
+L. Held had the idea to apply the sceptical $p$-value to the data from the four
+replication projects, which I collected for my master thesis. L. Held and C.
+Micheloud came up with the golden level. L. Held wrote an initial draft of the
+manuscript. L. Held, C. Micheloud, and I then iteratively worked on the
 manuscript.
@@
 Similar to the sceptical $p$-value, the procedure leads to a single measure for
-quantifying the degree of replication success, \emph{the sceptical Bayes
-  factor}. Systematic comparisons show that the sceptical Bayes factor has
-similar properties as the sceptical $p$-value due to the reverse-Bayes approach
-underlying both methods (\eg{} it penalizes shrinkage of the replication effect
-estimate and requires compelling evidence from both studies in terms of
-$p$-values and Bayes factors, respectively). However, it is also shown that the
-sceptical $p$-value suffers from a certain type of ``shrinkage paradox'', which
-is avoided by the sceptical Bayes factor; when the $p$-value from the original
-study goes to zero, replication success based on the sceptical $p$-value can be
-achieved with any arbitrarily small replication effect estimate, whereas
-replication success based on the sceptical Bayes factor poses a finite limit on
-how much shrinkage is allowed. Technically, the procedure is more involved and
-closed-form solutions for the sceptical Bayes factor are only available in
-special situations. % and in terms of the
+quantifying replication success, \emph{the sceptical Bayes factor}. Systematic
+comparisons show that the sceptical Bayes factor has similar properties as the
+sceptical $p$-value %due to the reverse-Bayes approach underlying both methods
+(\eg{} it penalizes shrinkage of the replication effect estimate and requires
+compelling evidence from both studies in terms of $p$-values and Bayes factors,
+respectively). However, it is also shown that the sceptical $p$-value suffers
+from a certain type of ``shrinkage paradox'', which is avoided by the sceptical
+Bayes factor; when the $p$-value from the original study goes to zero,
+replication success based on the sceptical $p$-value can be achieved with any
+arbitrarily small replication effect estimate, whereas replication success based
+on the sceptical Bayes factor poses a finite limit on how much shrinkage is
+allowed. Technically, the procedure is more involved and closed-form solutions
+for the sceptical Bayes factor are only available in special
+situations. % and in terms of the
 % ``Lambert W function'' \citep{Corless1996}.
@@
 parameters. Based on this design prior, predictions about the replication data
-can then be computed, and the replication sample size can be chosen such that
-the probability of replication success becomes as high as desired. We illustrate
+can be computed, and the replication sample size can be chosen such that the
+probability of replication success becomes as high as desired. We illustrate
 Bayesian design of replication studies in the normal-normal hierarchical model
@@
 $N$ method \citep{Rosenthal1979,Rosenberg2005}, L. Held suggested that it would
-fit nicely into this manuscript, to add the COVID-19 meta-analysis example, and
-that I should start to overhaul it. I rewrote and expanded his initial draft,
-adding also a new section on reverse-Bayes approaches with Bayes factors,
-largely based on the work from Paper~\ref{PaperII}. We then managed to recruit R. Matthews
-to also contribute. From that point on the three of us iteratively worked on the
-manuscript and M. Ott gave high-level feedback.
+fit nicely into this manuscript and to add the COVID-19 meta-analysis example. I
+rewrote and expanded his initial draft, adding also a new section on
+reverse-Bayes approaches with Bayes factors, largely based on the work from
+Paper~\ref{PaperII}. We then managed to recruit R. Matthews to also contribute.
+From that point on the three of us iteratively worked on the manuscript and M.
+Ott gave high-level feedback.
 
@@
 
-Shortly after the acceptance of Paper~\ref{PaperIII}, the article by
+Shortly after the acceptance of Paper~\ref{PaperIV}, the article by
 \citet{Sondhi2021} appeared. It proposed a novel reverse-Bayes method called
@@
 \citet{Matthews2018}. We investigate differences and similarities of the two
-methods, showing that the priors determined through the Bayesian Additional
-Evidence method are not always helpful.
+methods, concluding that the priors determined through the Bayesian Additional
+Evidence method are of limited use due to their restrictive assumption of having
+equal variance as the data.
 
@@
 and derived a solution. \mbox{L. Held} suggested to write a commentary. I wrote
-an initial draft of the manuscript, which \mbox{R. Matthews} substantially
-improved by expanding it with some logical flaws of the method. The two of us
-iteratively worked on the manuscript, while L. Held gave high-level feedback.
+an initial draft of the manuscript, which \mbox{R. Matthews} improved by
+discussing some logical flaws of the method. The two of us iteratively worked on
+the manuscript, while L. Held gave high-level feedback.
 
@@
 In methodological research, simulation studies are frequently used for
-evaluating ``how well'' statistical methods perform. The results of these
-studies therefore often guide the choice in which situation which method should
+evaluating ``how well'' statistical methods perform. The conclusions from these
+studies are therefore often crucial for recommendations when which method should
 be used. However, several literature review articles identified that the design
@@
 research. I then wrote a first draft of the manuscript and proposed the idea to
-L. Kook and K. Reeve. L. Kook and myself then inented the regression method
+L. Kook and K. Reeve. L. Kook and myself then invented the regression method
 ``AINET'' and started writing the simulation protocol. L. Kook took lead in

### 2022-12-14 paper1.tex
formatting and reproducibility

@@
 $s > 0$ of the replication effect estimate. Mathematically, this translates to
-setting $\dinfty = 1$ and $K = z_\alpha^2/z_{\alpha_S}^2$
+setting $\dinfty = 1$ and \mbox{$K = z_\alpha^2/z_{\alpha_S}^2$}
 in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
-with solution $K = \varphi$ where $\varphi = (\sqrt{5}+1)/2 \approx 1.62$ is
-known as the golden ratio. Solving for $z_{\alpha_S}$ gives
+with solution $K = \varphi$ where \mbox{$\varphi = (\sqrt{5}+1)/2 \approx 1.62$}
+is known as the golden ratio. Solving for $z_{\alpha_S}$ gives
 $z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
@@
 only possible for a borderline significant result ($p_o = \alpha$) if there is
-less than $1-\dinfty$ (20\% for $\dinfty=0.8$) shrinkage of the replication
-effect estimate. This approach is equivalent to a limiting relative effect size
-of 1 if the original $p$-value $p_o$ is equal to a different level $\alpha'$,
-which can be derived as follows: First, solving \eqref{eq1:smallestpossible} for
-$\dinfty > 0$ gives
-$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new level
-$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
+less than $1-\dinfty$ (20\% for \mbox{$\dinfty=0.8$}) shrinkage of the
+replication effect estimate. This approach is equivalent to a limiting relative
+effect size of 1 if the original $p$-value $p_o$ is equal to a different level
+$\alpha'$, which can be derived as follows: First, solving
+\eqref{eq1:smallestpossible} for $\dinfty > 0$ gives
+$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new
+level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
 $z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
@@
 $z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
-recalibrate the sceptical $p$-value $p_{S} = 1 - \Phi(z_S)$ to
+recalibrate the sceptical $p$-value \mbox{$p_{S} = 1 - \Phi(z_S)$} to
 $ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
@@
 increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
-where $\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ decreases
-with increasing $c$, because $\zrmin$ increases with increasing $c$, see
-equation \eqref{eq1:eq.z}.
+where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$}
+decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
+see equation \eqref{eq1:eq.z}.
 
@@
 \section*{Data and Software}
-Code and data to reproduce our analyses are available at
+Code and data to reproduce the analyses are available at
 \url{https://github.com/SamCH93/RSgolden/}. A snapshot of the Git repository at
-the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
-The data which was used is available in the R package
-\texttt{ReplicationSuccess} (available on CRAN). Further information can be
-found on the corresponding help page (with the command \texttt{?RProjects}).
+the time of writing is archived at \url{https://doi.org/10.5281/zenodo.7437689}.
+The data is available in the R package \texttt{ReplicationSuccess} (available on
+CRAN). Further information can be found on the corresponding help page (with the
+command \texttt{?RProjects}).
 
 \section*{Acknowledgments}
-Support by the Swiss National Science Foundation (Project \#~189295) is
-gratefully acknowledged. We acknowledge helpful and constructive comments by the
-editor and a referee on an earlier version of this article.
+We acknowledge helpful and constructive comments by the editor and a referee on
+an earlier version of this article.
 

### 2022-12-14 paper2.tex
formatting and reproducibility

@@
   % nodes %
-  \node[font = \large] (data) {$f(\text{data} \,|\, \theta)$};
-  \node[font = \large] (prior) [left=7em of data] {$f(\theta)$};
-  \node[font = \large] (post) [right=7em of data] {$f(\theta \,|\, \text{data})$};
+    \node[text width=5em, text centered] (data) {Likelihood $f(\text{data} \,|\, \theta)$};
+    \node[text width=3em, text centered] (prior) [left=6.5em of data] {Prior $f(\theta)$};
+    \node[text width=5em, text centered] (post) [right=5em of data] {Posterior $f(\theta \,|\, \text{data})$};
   \node[text width=10em,text centered] (RBinference) [below of=prior] {Reverse-Bayes inference};
@@
 The bottom-right plot in Figure~\ref{fig2:dcomparison} shows the success region
-for the recalibrated sceptical $p$-value. We see that increasing the precision
-of the replication study lowers the required minimum relative effect estimate
-$\dmin$ as for all other methods. Similarly, as with the sceptical Bayes factor,
-$\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily close to zero.
-However, its limiting minimum relative effect estimate in $c$
+for the recalibrated sceptical \mbox{$p$-value}. We see that increasing the
+precision of the replication study lowers the required minimum relative effect
+estimate $\dmin$ as for all other methods. Similarly, as with the sceptical
+Bayes factor, $\dmin$ of the sceptical $p$-value cannot be pushed arbitrarily
+close to zero. However, its limiting minimum relative effect estimate in $c$
 ($\lim_{c \to \infty}\dmin$) is smaller than the one from the sceptical Bayes
-factor when $\minBF_{o} < 1/5.6$, while for
-$\minBF_{o} > 1/5.6$ it is the other way around. So for more
-convincing original studies the sceptical $p$-value is less stringent than the
-sceptical Bayes factor. Due to the recalibration, the sceptical $p$-value also
-allows replication success when the $\minBF_{o} > \gamma$. This is visible in
-the bottom-right plot of Figure~\ref{fig2:dcomparison} where the success region
-has no cut-off at $\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and
-the sceptical Bayes factor.
+factor when $\minBF_{o} < 1/5.6$, while for $\minBF_{o} > 1/5.6$ it is the other
+way around. So for more convincing original studies the sceptical $p$-value is
+less stringent than the sceptical Bayes factor. Due to the recalibration, the
+sceptical $p$-value also allows replication success when the
+$\minBF_{o} > \gamma$. This is visible in the bottom-right plot of
+Figure~\ref{fig2:dcomparison} where the success region has no cut-off at
+$\minBF_{o} = \gamma = 1/3$, unlike the two-trials rule and the sceptical Bayes
+factor.
 
@@
 transformed estimates having approximate variance
-$\Var(\hat{\theta}) = 1/(n - 3)$ \citep{Fisher1921}, so the relative variance
-$c$ is roughly the ratio of the replication to the original study sample size
-$c \approx n_{r}/n_{o}$.
+\mbox{$\Var(\hat{\theta}) = 1/(n - 3)$} \citep{Fisher1921}, so the relative
+variance $c$ is roughly the ratio of the replication to the original study
+sample size $c \approx n_{r}/n_{o}$.
 
@@
 
-\section*{Funding}
-This work was supported by the Swiss National Science Foundation (project number
-189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
-design, data collection and analysis, decision to publish, or preparation of the
-manuscript.
+% \section*{Funding}
+% This work was supported by the Swiss National Science Foundation (project number
+% 189295, \url{http://p3.snf.ch/Project-189295}). The funder had no role in study
+% design, data collection and analysis, decision to publish, or preparation of the
+% manuscript.
 

### 2022-12-14 paper3.tex
formatting and reproducibility

@@
 \section*{Acknowledgments}
-This work was supported by the Swiss National Science Foundation (\#189295). The
-funder had no role in study design, data collection, data analysis, data
-interpretation, decision to publish, or preparation of the manuscript. We thank
-\citet{Protzko2020} for publicly sharing their data. We thank Charlotte
+% This work was supported by the Swiss National Science Foundation (\#189295). The
+% funder had no role in study design, data collection, data analysis, data
+% interpretation, decision to publish, or preparation of the manuscript.
+We thank \citet{Protzko2020} for publicly sharing their data. We thank Charlotte
 Micheloud and Angelika Stefan for helpful comments on drafts of the manuscript.

### 2022-12-14 paper5.tex
formatting
formatting and reproducibility

@@
 then implies a posterior distribution
-$\theta \given \hat{\theta} \sim \Nor(\mu_{p}, \tau^{2}_{p})$ whose mean and
-variance satisfy
+\mbox{$\theta \given \hat{\theta} \sim \Nor(\mu_{p}, \tau^{2}_{p})$} whose mean
+and variance satisfy
 \begin{align*}
@@
 \url{https://github.com/SamCH93/BAEcomment}. A snapshot of the Git repository at
-the time of writing is archived at \url{https://doi.org/10.5281/zenodo.XXXXXX}.
+the time of writing is archived at \url{https://doi.org/10.5281/zenodo.7437722}.
 
@@
 We thank two anonymous referees and the third referee Riko Kelter for their
-helpful suggestions. Financial support from the Swiss National Science
-Foundation (Project \#189295) is gratefully acknowledged. The funder had no role
-in study design, data collection, data analysis, data interpretation, decision
-to publish, or preparation of the manuscript.
+helpful suggestions.%  Financial support from the Swiss National Science
+% Foundation (Project \#189295) is gratefully acknowledged. The funder had no role
+% in study design, data collection, data analysis, data interpretation, decision
+% to publish, or preparation of the manuscript.
 

### 2022-12-14 preface.tex
formatting and reproducibility

@@
 who resurrected the reverse-Bayes approach from the dead almost twenty years
-ago. Furthermore, I want to thank Eric-Jan Wagenmakers for reviewing this thesis
-and for giving me the opportunity to do a very interesting and productive six
-months research stay in Amsterdam.
+ago. Furthermore, I want to thank Eric-Jan Wagenmakers for giving me the
+opportunity to do a very interesting and productive six months research stay in
+Amsterdam.
 
@@
 alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
-Beate, Beni, Dafne, Dominik, Eveline, Eva, Franscesca, Felix, Julia, Klaus,
-Kelly, Lucas, Lisa, Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria,
-Marielena, Martin, Mina, Nadja, Ruedi, Rachel, Sandra, Sona, Steffi, Tala,
-Torsten, and Ulrike. Another thanks goes to my friends from the Department of
-Psychological Methods from the University of Amsterdam (in alphabetical order):
-Adam, Alexander, Alexandra, Alessandra, Alejandro, Angelika, Bruno, Don,
-František, Frederik, Jason, Johnny, Joris, Jill, Julia, Lukas, Maarten,
-Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also want to
-thank my good friends from outside of academia (in alphabetical order): Chronis,
-Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special thanks goes
-to Ada. Finally, I thank my family: Beni, Christa, Elisabeth, Fabian, Harry,
-Markus, Maja, and Noemi for their support.
+Beate, Beni,Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
+Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Nadja, Ruedi,
+Rachel, Sandra, Sona, Steffi, Torsten, and Ulrike. Another thanks goes to my
+friends from the Department of Psychological Methods from the University of
+Amsterdam (in alphabetical order): Adam, Alexander, Alexandra, Alessandra,
+Angelika, Bruno, Don, František, Frederik, Jason, Johnny, Joris, Jill, Lukas,
+Maarten, Michelle, Nora, Omid, Quentin, René, Serjan, Suzanne, and Ting. I also
+want to thank my good friends from outside of academia (in alphabetical order):
+Chronis, Dani, Eleftheria, Flo, Fabi, Giuachin, Mirela, and Peter. A special
+thanks goes to Ada. Finally, I thank my family: Beni, Christa, Elisabeth,
+Fabian, Harry, Markus, Maja, and Noemi for their support.
 

### 2022-12-14 thesis.Rnw
one-sided sceptical p
formatting and reproducibility

@@
   urlcolor = {Blue},
-  pdftitle = {Reverse-Bayes Methods for Replication Studies and Beyond},
+  pdftitle = {Reverse-Bayes Methods for Replication Studies},
   pdfauthor = {Samuel Pawel},
-  pdfsubject = {},
   pdfpagemode = {UseOutlines}
@@
   \protect\vspace{2ex}
-  \textbf{\textsf{Integrity in methodological research}}\par}
+  \textbf{\textsf{Meta-scientific perspectives on methodological research}}\par}
 \addtocontents{toc}{%
@@
 
-% ==============================================================================
-% APPENDIX
-% ==============================================================================
-
-% \appendix
-% \renewcommand{\chaptername}{Appendix}
-% \paperchapter{%
-% Multivariate reverse-Bayes analysis
-% \label{app:multiRB}
-% }{%
-%  Samuel Pawel
-% }{}
-
-% \paperchapter{%
-% Reverse-Bayes asssessment of multiple replications
-% \label{app:multipleRB}
-% }{%
-%  Samuel Pawel
-% }{}
-
 \end{document}

### 2022-12-15 abstract.tex
rewrite intro and abstract a bit

@@
 % replicated when the same study is repeated with new subjects.
-An important aspect for the credibility of a scientific finding is that the
-finding can be replicated when the same study is repeated with new subjects.
-However, various failures to replicate major scientific findings in the social
-and life sciences indicate that replicability is often lower than expected. This
-``replication crisis'' has led to several methodological reforms in the past
-decade, an increased conduct of replication studies being one of them. Yet
-despite this increase in replication studies, there is no consensus on a
-fundamental question: How should replication success be defined statistically?
+% An important aspect of the credibility of a scientific finding is that the
+% finding can be replicated when the same study is repeated with new subjects.
+% An important aspect of the credibility of a scientific finding is its
+% replicability -- the ability to produce similar results when the same study is
+% repeated with new subjects.
+An important aspect of the credibility of a scientific finding is its
+replicability -- the ability that a similar finding can be obtained when the
+same study is repeated with new subjects. However, various failures to replicate
+major scientific findings in the social and life sciences indicate that
+replicability is often lower than expected. This ``replication crisis'' has led
+to several methodological reforms in the past decade, an increased conduct of
+replication studies being one of them. Yet despite this increase in replication
+studies, there is no consensus on a fundamental question: How should replication
+success be defined statistically?
 % Various methods already exist and various new ones have been proposed in

### 2022-12-15 intro.Rnw
rewrite intro and abstract a bit

@@
 
-\begin{wrapfigure}{r}{0.29\textwidth}
+\begin{wrapfigure}{r}{0.27\textwidth}
   \centering
@@
 % comes with uncertainty we can never know for sure.
-How can we know whether we can trust a finding from a scientific study? For
-example, how can we know whether the protective effect of a vaccine found in a
-study is indeed existent or whether it is just a spurious finding? The answer to
-such questions is of high importance to researchers, decision makers, and the
-general population, and one way to address them scientifically is through
-\emph{replication studies}.
-
-A replication study consists of repeating the original study as closely as
-possible but with new subjects. Such a study may yield similar results which
-would make us more confident about the original finding, or may yield
-conflicting results which would lower our confidence. As such, replication
-studies are an essential part of the scientific method as they provide a means
-for substantiating genuine research findings and refuting research findings
-which occurred merely by chance. For this reason, ``successful'' replication is
-often a requirement, for instance, for acceptance of newly proposed scientific
-theories (\eg{} a new physical model) or the implementation of policies based on
-scientific knowledge (\eg{} market approval of a drug). The results from
-replication studies may hence have real world consequences, % , such as deciding
-% whether we receive the recommendation to get vaccinated (a consequence that
-% anyone who experienced the COVID-19 pandemic is very aware of)
-and it is therefore important that methodological aspects of replication
+The ability to trust scientific findings is essential for making evidence-based
+decisions. But how can we know whether a scientific finding is trustworthy? For
+instance, how can we know whether the protective effect of a vaccine found in a
+study is indeed existent, or whether it is just a spurious finding? One way to
+answer this question is through the use of \emph{replication studies}.
+
+A replication study (or, simply, replication) involves repeating the original
+study as closely as possible but with new subjects. If the replication yields
+similar results to the original study, this increases our confidence in the
+original finding. However, if the replication study yields conflicting results,
+this lowers our confidence in the original finding. As such, replication studies
+are an essential part of the scientific method. They provide a means for
+substantiating genuine research findings and refuting findings which occurred
+merely by chance. For this reason, ``successful'' replication is often a
+requirement for acceptance of newly proposed scientific theories (\eg{} a new
+physical model). Yet, replication studies are not only important for
+researchers, but also for decision makers and the general population, as the
+implementation of policies based on scientific findings may also depend on
+whether these findings can be replicated (\eg{} market approval of a drug). The
+results from replication studies may thus also have real-world consequences, and
+it is therefore important that the methodological aspects of replication
 studies, such as their statistical design and analysis, are well understood.
 
-Despite their tremendous importance, the traditional academic system has made it
+Despite their importance, the traditional academic system has made it
 unattractive for researchers to conduct replication studies; the currencies of
@@
 on ``innovation'' rather than on ``repetition'' \citep{Makel2012, Martin2017,
-  Coiera2021}. To build a successful career, researchers thus often had no other
-choice than to concentrate their efforts on producing novel and eye-catching
-research results \citep{Binswanger2014, Moher2018}.
+  Coiera2021}. As a result, researchers often had no other choice than to focus
+their efforts on producing novel and eye-catching research results in order to
+build successful careers \citep{Binswanger2014, Moher2018}.
 

### 2022-12-17 abstract.tex
paper 6

@@
 % repeated with new subjects.
-An important aspect of the credibility of a scientific finding is its
+An important aspect of the credibility of scientific findings is their
 replicability -- the ability that a similar finding can be obtained when the
@@
 to several methodological reforms in the past decade, an increased conduct of
-replication studies being one of them. Yet despite this increase in replication
+replication studies being one of them. Despite this increase in replication
 studies, there is no consensus on a fundamental question: How should replication
@@
 method is to challenge the data from the original study with a sceptical prior
-distribution so that the resulting posterior distribution is no longer
-``significant''. The goal of the replication study is then to show that the
-sceptical prior is unrealistic, and replication success is achieved if there is
-sufficient conflict between the prior and the replication data. The procedure
+distribution so that the resulting posterior distribution no longer indicates
+evidence for an effect. The goal of the replication study is then to show that
+the sceptical prior is unrealistic, and replication success is achieved if there
+is sufficient conflict between the prior and the replication data. The procedure
 can be summarized in a single quantitative measure, termed the sceptical
@@
 % extension 1
-The first extension recalibrates the sceptical $p$-value to produce more
-appropriate inferences in terms of effect size. The recalibration is chosen such
-that for original studies which were borderline significant, replication success
-can only be achieved if the effect estimate from the replication study is larger
-than the effect estimate from the original study. We find that the recalibrated
-sceptical $p$-value has good frequentist properties comparable to the standard
-method used in practice.
+The first extension recalibrates the sceptical $p$-value so that replication
+success takes effect size more appropriately into account. Specifically, the
+recalibration is chosen such that for original studies which were borderline
+significant, replication success can only be achieved if the effect estimate
+from the replication study is larger than the effect estimate from the original
+study. We find that the recalibrated sceptical $p$-value has good frequentist
+properties comparable to the standard method used in practice.
 % extension 2
@@
 if questionable research practices are employed. Finally, several
-recommendations are given to alleviate these issues, most importantly the need
-for simulation protocols.
+recommendations are given to alleviate these issues.
 

### 2022-12-17 intro.Rnw
paper 6

@@
 
+\begin{wrapfigure}{r}{0.29\textwidth}
+  \centering
+  \includegraphics[width = 0.2\textwidth]{images/xkcdCrop.png}
+  \caption*{Replication studies as illustrated by Randall Munroe
+    (\url{https://xkcd.com/242}).}
+\end{wrapfigure}
+
 \section{Replication studies}
-
-\begin{wrapfigure}{r}{0.27\textwidth}
-  \centering
-  \includegraphics[height = 6.9cm]{images/xkcdCrop.png}
-  \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
-    \mbox{(\url{https://xkcd.com/242})}.}
-\end{wrapfigure}
 
@@
 % comes with uncertainty we can never know for sure.
-The ability to trust scientific findings is essential for making evidence-based
+Being able to trust scientific findings is essential for making evidence-based
 decisions. But how can we know whether a scientific finding is trustworthy? For
@@
 original finding. However, if the replication study yields conflicting results,
-this lowers our confidence in the original finding. As such, replication studies
-are an essential part of the scientific method. They provide a means for
-substantiating genuine research findings and refuting findings which occurred
-merely by chance. For this reason, ``successful'' replication is often a
-requirement for acceptance of newly proposed scientific theories (\eg{} a new
-physical model). Yet, replication studies are not only important for
-researchers, but also for decision makers and the general population, as the
-implementation of policies based on scientific findings may also depend on
-whether these findings can be replicated (\eg{} market approval of a drug). The
-results from replication studies may thus also have real-world consequences, and
-it is therefore important that the methodological aspects of replication
-studies, such as their statistical design and analysis, are well understood.
+this lowers our confidence in the original finding. %  As such, replication studies
+% are an essential part of the scientific method. They provide a means for
+% substantiating genuine research findings and refuting findings which occurred
+% merely by chance.
+The concept of replicability has long been a central part of the scientific
+method. For instance, \citet[p. 13]{Fisher1935} noted ``\textit{no isolated
+  experiment, however significant in itself, can suffice for the experimental
+  demonstration of any natural phenomenon}''. For this reason, ``successful''
+replication is typically a requirement for acceptance of newly proposed
+scientific theories (\eg{} a new physical model). Yet, replication studies are
+not only important for researchers, but also for decision makers and the general
+population, as the implementation of policies based on scientific findings may
+also depend on whether these findings can be replicated. For instance, the
+United States food and drug administration requires ``\textit{at least two
+  adequate and well-controlled studies, each convincing on its own, to establish
+  effectiveness}'' \citep[p. 3]{FDA1998} for market approval of a drug. The
+results from replication studies may hence have real-world consequences. It is
+therefore important that the methodological aspects of replication studies, such
+as their statistical design and analysis, are well understood.
 
 Despite their importance, the traditional academic system has made it
-unattractive for researchers to conduct replication studies; the currencies of
-science -- publications, citations, and grant money -- are typically easier to
-acquire by conducting novel research. This is because until recently, most
-scientific journals hardly published any replication studies as the emphasis was
-on ``innovation'' rather than on ``repetition'' \citep{Makel2012, Martin2017,
-  Coiera2021}. As a result, researchers often had no other choice than to focus
-their efforts on producing novel and eye-catching research results in order to
-build successful careers \citep{Binswanger2014, Moher2018}.
+unattractive for researchers to conduct replication studies; publications,
+citations, and grant money are typically easier to acquire by conducting novel
+research. This is because until recently, most scientific journals hardly
+published any replication studies as the emphasis was on ``innovation'' rather
+than on ``repetition'' \citep{Makel2012, Martin2017, Coiera2021}. As a result,
+researchers often had no other choice than to focus their efforts on producing
+novel and eye-catching research results in order to build successful careers
+\citep{Binswanger2014, Moher2018}.
 
@@
     $\Phi^{-1}(1 - \alpha) = \z{\alpha}$. Confidence intervals and
-    \textit{p}-values are based on the assumption that the effect estimate
-    $\that$ is normally distributed around the unknown effect size $\theta$ with
-    (known) variance equal to the squared standard error $\sigma^{2}$.}
+    \textit{p}-values for $H_{0}: \theta = 0$ are based on the assumption that
+    an effect estimate $\that_{k}$ is normally distributed around the unknown
+    effect size $\theta$ with (known) variance equal to the squared standard
+    error $\sigma^{2}_{k}$ for $k \in \{o, r\}$.}
   \label{tab:meta}
@@
     standard error & $\sigma_{o}$ & $\sigma_{r}$ \\
-    $(1 - \alpha)$ confidence interval &
+    $(1 - \alpha)\times100\%$ confidence interval &
     % $[\that_{o} \pm \z{\alpha/2} \sigma_{o}]$ &
     % $[\that_{r} \pm \z{\alpha/2} \sigma_{r}]$ \\
-    $[\that_{o} - \z{\alpha/2} \sigma_{o}, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
-    $[\that_{r} - \z{\alpha/2} \sigma_{r}, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
+    $[\that_{o} - \z{\alpha/2} \sigma_{o}, \, \that_{o} + \z{\alpha/2} \sigma_{o}]$ &
+    $[\that_{r} - \z{\alpha/2} \sigma_{r}, \, \that_{r} + \z{\alpha/2} \sigma_{r}]$ \\
     $z$-value & $z_{o} = \that_{o}/\sigma_{o}$ & $z_{r} = \that_{r}/\sigma_{r}$ \\
@@
 success analysis as the raw data from the original study may not be available to
-the researchers conducting the replication study. The most important statistic
-is the effect estimate $\that$. It provides an estimate of the underlying effect
-size $\theta$ which quantifies the true effect or association of an
-intervention/exposure with an outcome variable. Typical effect sizes are mean
-differences and correlations (for continuous outcomes), odds ratios (for binary
-outcomes), or hazard ratios (for time-to-event outcomes). Depending on the type
-of effect size, a transformation might be required so that the assumption of
-approximately normally distributed effect estimates around the unknown effect
-size $\theta$ (for large enough sample sizes) is justified. This could be, for
-instance, the Fisher $z$-transformation for correlations or the
+the researchers conducting the replication study. The most important statistics
+are the effect estimates $\that_{o}$ and $\that_{r}$. They provide an estimate
+of the underlying effect size $\theta$ which quantifies the true effect or
+association of an intervention/exposure with an outcome variable. Typical effect
+sizes are mean differences and correlations (for continuous outcomes), odds
+ratios (for binary outcomes), or hazard ratios (for time-to-event outcomes).
+Depending on the type of effect size, a transformation might be required so that
+the assumption of approximately normally distributed effect estimates around the
+unknown effect size $\theta$ (for large enough sample sizes) is justified. This
+could be, for instance, the Fisher $z$-transformation for correlations or the
 log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
-associated standard error $\sigma$ represents the statistical uncertainty of the
-estimate. Typically, the available standard error $\sigma$ is only an estimate
-of the true standard error. However, in most parts of this thesis it will be
-assumed that $\sigma$ corresponds to the true standard error. This is the same
-assumption as in ordinary fixed-effect/random-effects meta-analysis, and
-typically reasonable if the sample size of the studies is not too small. Under
-the assumption of (asymptotic) normality, confidence intervals for $\theta$ and
-$p$-values for testing the null hypothesis $H_{0} \colon \theta = 0$ can be
-computed as shown in Table~\ref{tab:meta}.
+associated standard errors $\sigma_{o}$ and $\sigma_{r}$ represent the
+statistical uncertainty of the estimates. Typically, the available standard
+errors are only estimates of the true standard errors. However, in most parts of
+this thesis it will be assumed that $\sigma_{o}$ and $\sigma_{r}$ correspond to
+the true standard errors. This is the same assumption as in ordinary
+fixed-effect/random-effects meta-analysis, and typically reasonable if the
+sample size of the studies is not too small. Under the assumption of
+(asymptotic) normality, confidence intervals for $\theta$ and $p$-values for
+testing the null hypothesis $H_{0} \colon \theta = 0$ can be computed as shown
+in Table~\ref{tab:meta}.
 

### 2022-12-17 paper6.tex
paper 6

\section*{Abstract}
Comparative simulation studies are workhorse tools for benchmarking statistical
methods. As with other empirical studies, the success of simulation studies
hinges on the quality of their design, execution and reporting. If not conducted
carefully and transparently, their conclusions may be misleading. In this paper
we discuss various questionable research practices which may impact the validity
of simulation studies, some of which cannot be detected or prevented by the
current publication process in statistics journals. To illustrate our point, we
invent a novel prediction method with no expected performance gain and benchmark
it in a pre-registered comparative simulation study. We show how easy it is to
make the method appear superior over well-established competitor methods if
questionable research practices are employed. Finally, we provide concrete
suggestions for researchers, reviewers and other academic stakeholders for
improving the methodological quality of comparative simulation studies, such as
pre-registering simulation protocols, incentivizing neutral simulation studies
and code and data sharing.

\textbf{Key words}: Benchmarking studies, Monte Carlo experiments, overoptimism,
reproducibility, replicability, transparency

\section{Introduction}
Simulation studies are to a statistician what experiments are to a scientist
\citep{Hoaglin1975}. They have become a ubiquitous tool for the evaluation of
statistical methods, mainly because simulation can be used for studying the
statistical properties of methods under conditions that would be difficult or
impossible to study theoretically. In this paper we focus on simulation studies
where the objective is to compare the performance of two or more statistical
methods (\emph{comparative simulation studies}). Such studies are needed to
ensure that previously proposed methods work as expected under various
conditions, and to identify conditions under which they fail. Moreover, evidence
from comparative simulation studies is often the only guidance available to data
analysts for choosing from the plethora of available methods
\citep{Boulesteix2013, Boulesteix2017b}. Proper design and execution of
comparative simulation studies is therefore important, and results of
methodologically flawed studies may lead to misinformed decisions in scientific
and medical practice.

Figure~\ref{fig:diagram} shows a schematic illustration of an example
comparative simulation study. We see that, just like non-simulation based
studies, comparative simulation studies require many decisions to be made, for
instance: How will the data be generated? How often will a simulation condition
be repeated? Which statistical methods will be compared and how are their
parameters specified? How will the performance of the methods be evaluated? The
degree of flexibility, however, is much higher for simulation studies than for
non-simulation based studies as they can often be rapidly repeated under
different conditions at practically no additional cost. This is why numerous
recommendations and best practices for design, execution and reporting of
simulation studies have been proposed \citep{Hoaglin1975, Holford2000,
  Burton2006, Smith2010, OKelly2016, Monks2018, Elofsson2019, Morris2019,
  Boulesteix2020B}. We recommend \citet{Morris2019} for an introduction to
state-of-the-art simulation study methodology.

\begin{figure}[!tb]
\centering
{ \small
\begin{tikzpicture}[thick,scale=1, every node/.style={scale=0.99}]

    % nodes
    \node [rectangle, draw, rounded corners = 0.5em, minimum height = 5.5em] (truth)
    {\footnotesize
    \begin{tabular}{l}
    \multicolumn{1}{c}{\small \textbf{Truth}} \\
     Prevalence \\
     Effect type \\
     $\dots$
     \end{tabular}};

   \node [rectangle, draw, rounded corners = 0.5em, minimum height = 5.5em] (simdat) [right = 12em of truth]
   {\footnotesize
   \begin{tabular}{l}
   \multicolumn{1}{c}{\small \textbf{Simulated Data}} \\
      Training data  \\
      Test data  \\
      \phantom{$\dots$}
    \end{tabular}};

  \node [rectangle, draw, rounded corners = 0.5em, minimum height = 5.5em] (output) [right = 10em of simdat]
  {\footnotesize
  \begin{tabular}{c}
  \multicolumn{1}{c}{\small \textbf{Predictions}}
   \end{tabular}};

 % edges
 \draw [->] (truth) -- node [above] (dgp)
 {\small
 \begin{tabular}{c}
 Data Generating \\
 Process
 \end{tabular}}
 (simdat);

 \draw [->] ([yshift = 0.5em] simdat.east) -- node [above] (analysis)
 {\small
 \begin{tabular}{c}
 Model  \\
 Fitting \end{tabular}}
 ([yshift = 0.5em] output.west);

 \draw [->] ([yshift = -0.5em] output.west) to node [below] (performance)
 {\small
 \begin{tabular}{c}
 Performance \\
 Evaluation
 \end{tabular}}
 ([yshift = -0.5em] simdat.east);

  % nodes related to edges
 \node [rectangle, draw, rounded corners = 0.5em] (methods) [above = 2em of analysis]
 {\footnotesize
 \begin{tabular}{l}
 \multicolumn{1}{c}{\small \textbf{Methods}} \\
   Logistic regression \\
   Random forest \\
   $\hdots$
\end{tabular}};

\node [rectangle, draw, rounded corners = 0.5em] (params) [above = 2em of dgp]
   {\footnotesize
   \begin{tabular}{l}
     \multicolumn{1}{c}{\small \textbf{Parameters}} \\
             Sample size \\
             Missingness \\
             $\hdots$
    \end{tabular}};

\node [rectangle, draw, rounded corners = 0.5em] (metrics) [below = 2em of performance]
   {\footnotesize
   \begin{tabular}{l}
   \multicolumn{1}{c}{\small  \textbf{Metrics}} \\
    Brier score \\
    AUC \\
    $\hdots$
    \end{tabular}};

   % QRP nodes
   \node [rectangle, draw, rounded corners = 0.5em, fill = lightg] (tuning) [left = 1.5em of methods]
       {\footnotesize
       \begin{tabular}{l}
       Selective \\
       parameter tuning / \\
       method inclusion
       \end{tabular}};

    \node [rectangle, draw, rounded corners = 0.5em, fill = lightg] (switching) [right = 2em of metrics]
       {\footnotesize \begin{tabular}{l}
       Outcome \\
       switching
       \end{tabular}};

    \node [rectangle, draw, rounded corners = 0.5em, fill = lightg] (selectreport) [above = 3.62em of truth]
       {\footnotesize \begin{tabular}{l}
       Selective \\
       reporting
       \end{tabular}};

    \node [rectangle, draw, rounded corners = 0.5em, fill = lightg] (seed) [below = 3em of dgp]
       {\footnotesize \begin{tabular}{l}
       Seed tuning
       \end{tabular}};

    \node [rectangle, draw, rounded corners = 0.5em, fill = lightg] (inclusion) [left = 2em of metrics]
       {\footnotesize \begin{tabular}{l}
       Selective handling \\
       of missing values
       \end{tabular}};

  \draw [-] (params.south) to (dgp);
  \draw [-] (methods.south) to (analysis);
  \draw [-] (metrics) to (performance);
  \draw [->] (tuning.east) to (methods.west);
  \draw [->] (switching.west) to (metrics.east);
  \draw [->] (selectreport.east) to (params.west);
  \draw [->] (selectreport.south) to (truth.north);
  \draw [->] (seed.north) to ([yshift = -1em] dgp.south);
  \draw [->] (inclusion) to (performance);

\end{tikzpicture}
}
\caption{Schematic illustration of a comparative simulation study for evaluating
  performance of methods for predicting binary outcomes, such as the example
  study in Section~\ref{sec:study}. Questionable research practices (in gray)
  can affect all aspects of the study.}
\label{fig:diagram}
\end{figure}

Despite wide availability of such guidelines, statistics articles often provide
too little detail about the reported simulation studies to enable quality
assessment and replication \citep[see the literature reviews in][]{Burton2006,
  Morris2019}. Journal policies sometimes require the computer code to reproduce
the results, but they rarely require or promote rigorous simulation methodology
(for instance, the preparation of a simulation protocol). This leaves
researchers with considerable flexibility in how they conduct and present
simulations studies. As a consequence, readers of statistics papers can rarely
be sure of the quality of evidence that a simulation study provides.

Unfortunately, there are many questionable research practices (QRPs) which may
undermine the validity of comparative simulations studies and which can easily
go undetected under current publishing standards. Figure~\ref{fig:diagram} shows
several QRPs that may occur in the exemplary simulation study. There is often a
fine line between QRPs and legitimate research practices. For instance, a
researcher may choose to selectively report the most relevant simulation
conditions, methods and outcomes in order to streamline the results for the
reader. These practices only become questionable when they serve to confirm the
hopes and beliefs of researchers regarding a particular method. For instance, if
only conditions and outcomes are reported where the researcher's favored method
appears superior over competitor methods. Consequently, the results and
conclusions of the study will be biased in favor of this method
\citep{Niessl2021}.

The aim of this paper is to raise awareness about the issue of QRPs in
comparative simulation studies, and to highlight the need for the adoption of
higher standards. While researchers may make decisions that can make the
conclusions of simulation studies misleading, we are not accusing them of doing
so intentionally or maliciously. Instead, we highlight how QRPs can occur and
possibly be prevented. External pressures, for example, to publish novel and
superior methods \citep{Boulesteix2015} or to concisely report large amounts of
simulation results, may also lead honest researchers to (unknowingly) employ
QRPs. As we will argue, it is not only up to the researchers but also other
academic stakeholders to improve on these issues.

This article is structured as follows: We first give an illustrative list of
QRPs related to comparative simulation studies (Section \ref{sec:QRP}). With an
exemplary simulation study, we then show h?ow easy it is to present a novel,
made-up method as an improvement over others if QRPs are employed and \emph{a
  priori} simulation plans remain undisclosed (Section \ref{sec:study}). The
main inspiration for this work is drawn from similar illustrative studies which
have been conducted by \citet{Yousefi2009} and \citet{Jelizarow2010} for
benchmarking studies, and by \citet{Simmons2011} in the context of $p$-hacking
in psychological research. Recently, \citet{Niessl2021} and \citet{Ullmann2022}
expanded on QRPs in benchmarking studies with the latter also including
simulation studies. In Section~\ref{sec:recommendations}, we then provide
concrete suggestions for researchers, reviewers, editors and funding bodies to
alleviate the issues of QRPs and improve the methodological quality of
comparative simulation studies. Section~\ref{sec:discussion} closes with
limitations and concluding remarks.

\section{Questionable research practices in comparative simulation studies}
\label{sec:QRP}

There are various QRPs which threaten the validity of comparative simulation
studies (see Table~\ref{table:QRPs} for an overview). QRPs can be categorized
with respect to the stage of research at which they can occur and which other
QRPs they are related to \citep{Wicherts2016}. Typically, QRPs becomes more
problematic if they are combined with related QRPs. For example, adapting the
data-generating process to achieve a desired outcome (E2) is more problematic
when the results based on the adapted process are selectively reported (R2)
compared to reporting the results based on both the original and the adapted
process. In the following, we describe QRPs from all phases of a simulation
study, namely, design, execution and reporting.

\begin{table}[!htb]
  \caption{Types of questionable research practices (QRPs) in comparative
    simulation studies at different stages of the research process. A QRP
    becomes more problematic if combined with a related QRP, especially a
    reporting QRP.}
  \label{table:QRPs}
  \centering
  \begin{tabular}{p{.05\textwidth} p{.11\textwidth} p{.75\textwidth}}
    \toprule
    \textbf{Tag} & \textbf{Related} & \textbf{Type of QRP} \\
    \midrule
    \multicolumn{2}{p{.15\textwidth}}{\textit{Design}} & \\
    D1 & E1, R1 & Not/vaguely defining objectives of simulation study \\
    D2 & E2, R1 & Not/vaguely defining data-generating process \\
    D3 & E3, E4, R1 & Not/vaguely defining which methods will be compared and how their
                      parameters are specified \\
    D4 & E1, E5, R1 & Not/vaguely defining estimands of interest \\
    D5 & E1, E5, R1 & Not/vaguely defining evaluation criteria \\
    D6 & E6, R1 & Not/vaguely defining how to handle missing values
                  (for example, due to non-convergence of methods) \\
    D7 & E7, E8, R3 & Not justifying number of simulations \\[1em]

    \multicolumn{2}{p{.15\textwidth}}{\textit{Execution}} & \\
  	E1 & D1, R2 & Changing objective of the study to achieve desired outcomes \\
    E2 & D2, R2 & Adapting data-generating process to achieve desired outcomes \\
    E3 & D3, R2 & Adding/removing comparison methods to achieve desired outcomes \\
    E4 & D3, R2 & Selective tuning of method hyperparameters to achieve desired outcomes\\
    E5 & D4, D5, R2 & Choosing evaluation criteria to achieve desired outcomes \\
    E6 & D6, R2 & Adapting inclusion/exclusion/imputation rules to achieve desired outcomes \\
    E7 & D7, R3 & Choosing number of simulations to achieve desired outcomes \\
    E8 & D7, R3 & Choosing random number generator seed to achieve desired outcomes \\[1em]

    \multicolumn{2}{p{.15\textwidth}}{\textit{Reporting}} & \\
    R1 & D1--D6 & Justifying design decisions which lead
                  to desired outcomes \emph{post hoc}\\
    R2 & E1--E6 & Selective reporting of results from simulations
                  that lead to desired outcomes \\
    R3 & D7, E7, E8 & Failing to report Monte Carlo uncertainty \\
    R4 & & Failing to assure computational reproducibility
           (for example, not sharing code and sufficient
           details about computing environment) \\
    R5 & & Failing to assure replicability (for example, not sufficiently reporting design and
           execution methodology) \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{QRPs in the design of comparative simulation studies}
The \emph{a priori} specification of research hypotheses, study design and
analytic choices is what separates \emph{confirmatory} from \emph{exploratory}
research. Evidence from confirmatory research is typically considered more
robust because study hypotheses, design, and analysis are independent of the
observed data \citep{Tukey1980}. The line between the two types of research is,
however, blurry in simulation studies since they are often iteratively
conducted, with each iteration including newly simulated data and building on
the results of the previous study. The first simulation study in a sequence of
studies may thus be exploratory whereas the subsequent studies may be
confirmatory. Yet, one may argue that in many cases a single confirmatory
simulation study which is carefully designed and whose design is justified based
on external knowledge provides more relevant evidence than a sequence of
simulation studies which are iteratively tweaked based on previous results.

To allow readers to distinguish between confirmatory and exploratory research,
many non-methodological journals require pre-registration of study design and
analysis protocols. For instance, pre-registration is common practice in
randomized controlled clinical trials \citep{DeAngelis2004}, and increasingly
adopted in experimental psychology \citep{Nosek2018} and epidemiology
\citep{Lawlor2007, Loder2010}. It is also generally recommended to write and
pre-register simulation protocols in simulation studies \citep{Morris2019}.
Well-defined study aims and methodology are arguably at least as important as in
simulation studies compared to non-simulation based studies because the space of
possible design and analysis choices is typically much larger
\citep{Hoffmann2021}. If researchers are vague or fail to define the study goals
(D1), the data-generating process (D2), the methods under investigation (D3),
the estimands of interest (D4), the evaluation metrics (D5), or how missing
values should be handled (D6) \emph{a priori} a high number of \emph{researcher
  degrees of freedom} \citep{Simmons2011} are left open. Researchers can then
generate a multiplicity of possible results which may foster overoptimistic
impressions if they report only the subset of results aligning with their hopes
and beliefs (R2), and for which they can find plausible justifications
\emph{post hoc} (R1).

Another crucial part of rigorous design is simulation size calculation
\citep[see Section~5.3 in][for an overview]{Morris2019}. While an arbitrarily
chosen, often too small, number of simulations can be executed faster, they
yield noisier results. The additional noise is not necessarily problematic if
one is only concerned with estimation. However, if the goal is to establish
method superiority through statistical tests (for instance, through a confidence
interval for the difference in method performance excluding zero), simulation
studies with too few repetitions come with undesirable properties, just as any
other study with an insufficiently large sample size. For instance, ``true''
differences in method performance are more likely to remain undetected
(increased type II errors), detected differences are more likely to be in the
wrong direction \citep[increased ``type S'' errors, see][]{Gelman2000}, and
their magnitude is more likely to be overestimated \citep[increased ``type M''
errors, see][]{Vanzwet2021}. Additionally, a researcher may start with a small
simulation size and continue to add newly simulated data until superiority is
established (\emph{optional stopping}). This is similar to early stopping of a
trial without correction for the interim analysis. Without specialized
corrections, optional stopping leads to biased estimates and increased type I
error rates \citep{Robertson2022}. These biases may also occur when the entire
simulation study is rerun with a larger sample size and the seed of the random
number generator is left unchanged. The simulated data will be the same up to
the additional data (provided the simulation runs deterministically conditional
on a seed). From this perspective, researchers should thus change the seed if
they want rerun the study and increase the simulation size adaptively.

\subsection{QRPs in the execution of comparative simulation studies}
During the execution of a simulation study researchers may (often unknowingly)
engage in various QRPs that can lead to overoptimism. For instance, the
objective of the simulation study may be changed depending on the outcome (E1).
For example, an initial comparison of predictive performance may be changed to
comparing estimation performance if the results suggest that the favored method
performs better at estimation tasks rather than prediction. The data-generating
process may also be adapted until conditions are found in which the favored
method appears superior (E2). For example, the noise levels, the number of
covariates, or the effect sizes could be changed. Competitor methods that are
superior to the proposed method may also be excluded from the comparison
altogether, or methods which perform worse under the (adapted) data-generating
process may be added (E3). The methods under comparison may come with
hyperparameters (for instance, regularization parameters in penalized regression
models). In this case, the hyperparameters of a favored method may be tuned
until the method appears superior, or the hyperparameters of competitor methods
may be tuned selectively, for example, left at their default values (E4).
Finally, the evaluation criteria for comparing the performance of the
investigated methods may also be changed to make a particular method look better
than the others (E5). For example, even though the original aim of the study may
have been to compare predictive performance among methods using the Brier score,
the evaluation criterion of the simulation study may be switched to area under
the curve if the results suggest that the favored method performs better with
respect to the latter metric. This QRP parallels the well-known
\emph{outcome-switching} problem in clinical trials \citep{Altman2017}. It is
usually not difficult to find reasonable justification for such modifications
and then present them as if they were specified during the planning of the study
(R1). As emphasized earlier, iteratively changing simulation goals, conditions,
methods under comparison and evaluation criteria can be part of finding out how
a method works. These practices become mostly problematic if only the
simulations in line with the researchers hopes and beliefs are reported (R2).

There are, however, practices which are considerably more problematic on their
own. For instance, in some simulations a method may fail to converge and thus
produce missing values in the estimates. If it is not pre-specified how these
situations will be handled, different inclusion/exclusion or imputation
strategies may be tried out until a favored method appears superior (E6).
Choosing an inadequate strategy can result in systematic bias and misleading
conclusions. If no \emph{a priori} simulation size calculation was conducted,
the simulation size may also be changed until favorable results are obtained
(E7). If in that case the number of simulations is too small, true performance
differences are more likely to be missed, their estimated direction is more
likely to be incorrect and their magnitude is more likely overestimated, as
explained previously. Finally, if only few simulations are conducted (for
instance, because the methods under investigation are computationally very
expensive), the initializing seed for generating random numbers may have a
substantial impact on the result. A particularly questionable practice in this
situation is to tune the seed until a value is found for which a preferred
method seems superior (E8).

\subsection{QRPs in the reporting of comparative simulation studies}
In the reporting stage, researchers are faced with the challenge of reporting
the design, results, and analyses of their simulation study in a digestible
manner. Various QRPs can occur at this stage. For instance, reporting may focus
on results in which the method of interest performs best (R2). Failing to
mention conditions in which the method was inferior (or at least not superior)
to competitors creates overoptimistic impressions, and may lead readers to think
that the method uniformly outperforms competitors. Similarly, presenting
simulation conditions which were added based on the observed results as
pre-planned and justified (R1) fosters overconfidence in the results.

Another crucial aspect of reporting is to adequately show the uncertainty
related to the simulation results \citep{Hoaglin1975, vanderBles2019}. Failing
to report Monte Carlo uncertainty (R3), such as error bars or confidence
intervals reflecting uncertainty in the simulation, hampers the readers' ability
to assess the accuracy of the results from the simulation study and it allows
one to present random differences in performance as if they were systematic.

Finally, by failing to assure computational reproducibility of the simulation
study (R4), for example, by not sharing code and software versions to run the
simulation, it is more likely that coding errors remain undetected. By not
reporting the design and execution of the study in enough detail (R5), other
researchers are unable to replicate and expand on the simulation study. Unclear
reporting also makes it harder for readers to identify potentially
overoptimistic statements. For instance, if it is reported that all but one
method are left at their default parameters, readers can better contextualize
this method's apparent superior performance.

\section{Empirical study: The Adaptive Importance Elastic Net
  (AINET)} \label{sec:study}

To illustrate the application of QRPs from Table~\ref{table:QRPs} we conducted a
simulation study. The objective of the study was to evaluate the predictive
performance of a made-up regression method termed the \emph{adaptive importance
  elastic net} (\ainet). The main idea of \ainet{} is to use variable importance
measures from a random forest for a weighted penalization of the variables in an
elastic net regression model. The hope is that this \emph{ad hoc} modification
of the elastic net model improves predictive performance in clinical prediction
modeling settings where penalized regression models are frequently used.
Superficially, \ainet{} may seem sensible, however, for the data-generating
process considered in our simulation study no advantage over the classical
elastic net is expected. For more details on the method, we refer the reader to
the simulation protocol (Appendix~\ref{appendix:protocol}). We report the
pre-registered\footnote{We use the term \emph{pre-registered} throughout to
  refer to simulation analyses conducted as pre-specified in the protocol.}
simulation study results in the online supplement. As expected, the performance
of \ainet{} was virtually identical to standard elastic net regression. \ainet{}
also did not yield any improvements over logistic regression for the
data-generating process that we considered sensible \emph{a priori} (that is,
specified based on typical conditions in clinical prediction modeling and
simulation studies from other researchers).

\begin{figure}[!htb]
  \centering
  \includegraphics[width = 0.85\textwidth]{images/paper6/ainet-results.pdf}
  \caption{Differences in Brier score with 95\% adjusted confidence intervals
    between \ainet{} and random forest (RF), logistic regression (GLM), elastic
    net (EN) and adaptive elastic net (AEN) are shown for representative
    simulation conditions (correlated covariates $\rho = 0.95$, prevalence
    $\operatorname{prev} = 0.05$, a range of sample sizes $n$ and events per
    variable (EPV), in each simulation the Brier score is computed for 10'000
    test observations; for details see Appendix~\ref{appendix:protocol}). The
    top row depicts the pre-registered results in which \ainet{} does not
    outperform any competitor uniformly, except AEN. In the second row, we apply
    QRP E2: Altering the data-generating process by adding a non-linear effect
    and sparsity. The gray arrows point from the pre-registered result to the
    results under the tweaked simulation. In the third row, QRP E3 is applied:
    EN is removed as a competitor. In the bottom row, selective reporting R2 is
    applied: Only low EPV settings are reported to give a more favorable
    impression for \ainet{}. Arrows are depicted only for non-overlapping
    confidence intervals. } \label{fig:E1}
\end{figure}

We now show how application of QRPs changes the above pre-registered
conclusions. Figure~\ref{fig:E1} illustrates different types of QRPs
sequentially applied to simulation-based evaluation of \ainet{}. The top row
depicts the pre-registered differences in Brier score (horizontal axis) between
\ainet{} and competitor methods (vertical axis) for a representative subset of
the simulation conditions. A negative difference indicates superior performance
of \ainet{}. In the second row, the arrows depict the change in the
pre-registered results after changing the data-generating process (E2). The
third row shows the result after removal of the elastic net competitor (E3).
Finally, the bottom row shows the end result where selective reporting of
simulation conditions and competitor methods (R2) is applied to give a more
favorable impression of \ainet{}. We will now discuss these QRPs in more detail.

\paragraph{Altering the data-generating process (E2)}
We could not detect a systematic performance benefit of \ainet{} over standard
logistic regression, elastic net regression, or random forest for the scenarios
specified in the protocol. For this reason, we tweaked the data-generating
process by adding different sparsity conditions and a non-linear effect. We then
found that \ainet{} outperforms logistic regression under the following
conditions: Only few variables being associated with the outcome (sparsity), a
non-linear effect and a low number of events per variable (EPV).
Figure~\ref{fig:E1} (second row) shows the changes in Brier score difference
between the pre-registered and the tweaked simulation. As can be seen, the
tweaked data-generating process leads to \ainet{} being superior to competitors
in some conditions, and at least not inferior in others.

\paragraph{Removing competitor methods (E3)}
Despite the adapted data-generating process, we still observed only minor (if
any) improvements of \ainet{} over the elastic net. In order to present \ainet{}
in a better light we could omit the comparisons with the elastic net (E3), as
shown in Figure~\ref{fig:E1} (third row). This could be justified, for example,
by arguing that for neutral comparison it is sufficient to compare a less
flexible method (logistic regression, which has no tuning parameters and
captures linear effects), a more flexible method (random forest, which has
tuning parameters and captures nonlinear relationships), and a comparably
flexible method (adaptive elastic net, which has the same tuning parameters as
AINET, but differs in the way the penalization weights are chosen).

\paragraph{Selective reporting of simulation results (R2)}
After the removal of the competitor elastic net, there are still some simulation
conditions under which \ainet{} is not superior to the remaining competitors. To
make \ainet{} appear more favorable, we thus report only simulation conditions
with low EPV, as shown in Figure~\ref{fig:E1} (fourth row). This could be
justified by the fact that journals require authors to be concise in their
reporting. Otherwise, further conditions with low EPV values could be simulated
to make the results seem more exhaustive. Focusing primarily on low EPV settings
could be justified in hindsight by framing \ainet{} as a method designed for
high-dimensional data (low sample size relative to the number of variables).

\section{Recommendations}
\label{sec:recommendations}

The previous sections painted a rather negative picture of how
undisclosed changes in simulation design, analysis and reporting
may lead to overoptimistic conclusions. In the
following, we summarize what we consider to be practical recommendations for
improving the methodological quality of simulation studies; see
Table~\ref{table:recommendations} for an overview. Our recommendations are
grouped with regards to which stakeholder they concern.

\begin{table}[!htb]
  \caption{Recommendations for improving quality of comparative simulation studies
    and preventing QRPs.}
  \label{table:recommendations}
  \centering
	\begin{tabular}{p{.95\textwidth}}
		\toprule
    \textit{Researchers} \\
    \midrule
    \vspace{-1.5em}
    \begin{itemize}
    \setlength\itemsep{0pt}
    \setlength\itemindent{-12pt}
        \item[--] Write (and possibly pre-register) simulation protocols
    \item[--] Adopt good computational practices (code review, packaging, unit-tests)
    \item[--] Share code and data (possibly in intermediate/summary form to enable
    secondary analysis)
    \item[--] Report the process of the simulation study fully and transparently
    (for instance, time-stamped protocol amendments to disclose pilot studies
    and \emph{post hoc} modifications)
    \item[--] Perform simulation analysis in a blinded manner
    \item[--] Collaborate with other research groups (possibly familiar with ``competing'' methods)
    \item[--] Disclose multiplicity and uncertainty of results (for example, with sensitivity analyses)
    \item[--] Teach simulation study methodology in statistics (post)graduate courses
    \end{itemize}

    \textit{Editors and reviewers} \\
    \midrule
    \vspace{-1.5em}
    \begin{itemize}
    \setlength\itemsep{0pt}
    \setlength\itemindent{-12pt}
    \item[--] Encourage exploration of conditions where methods should
    be inferior or break down
    \item[--] Encourage (pre-registered) simulation protocols
    \item[--] Provide enough space for description of simulation methodology
    \end{itemize}

    \textit{Journals and funding bodies} \\
    \midrule
    \vspace{-1.5em}
    \begin{itemize}
    \setlength\itemsep{0pt}
    \setlength\itemindent{-12pt}
    \item[--] Provide incentives for rigorous simulation methodology (such as badges on papers)
    \item[--] Require code and data
    \item[--] Promote standardized reporting
    \item[--] Adopt reproducibility checks
    \item[--] Promote/fund research and software to improve simulation study methodology
    \item[--] Shift focus away from outperforming state-of-the-art methods
    \end{itemize}\\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Recommendations for researchers}
Adopting pre-registered simulation protocols is an important measure that
researchers can take to prevent themselves from subconsciously engaging in QRPs.
Pre-registration enables readers to distinguish between confirmatory and
exploratory findings, and it lowers the risk of potentially flawed methods being
promoted as an improvement over competitors. While pre-registered simulation
protocols may at first seem disadvantageous due to the additional work and
possibly lower chance of publication, they provide researchers with the means to
differentiate their high-quality simulation studies from the numerous
unregistered and possibly less trustworthy simulation studies in the literature.
Platforms such as GitHub (\url{https://github.com/}), OSF
(\url{https://osf.io/}), or Zenodo (\url{https://zenodo.org/}) can be used for
archiving and time-stamping documents. Moreover, pre-registration can also save
researchers from some work later on. For instance, large parts of the
methodology description can usually be copied from the protocol to the final
manuscript.

When pre-registering and conducting simulation studies, we recommend using a
robust computational workflow. Such a workflow encompasses packaging the
software, writing unit tests and reviewing code \citep[see][]{Schwab2021}. Other
researchers and the authors themselves then benefit from improved computational
reproducibility and less error-prone code. Of course, there are also certain
practical limits to computational reproducibility. For instance, if a simulation
study requires high performance computing and/or several weeks of running time,
the authors should not expect reviewers and journals to replicate their
simulation study from scratch. The authors should nevertheless provide the code
to run the simulation and, if possible, they should also provide intermediate
simulation results (for instance, fitted model objects) so that the simulation
study can at least be partially reproduced. Similarly, authors can share the
simulated data, either in raw and/or some summarized form (for example, sharing
simulated data sets and parameter estimates of fitted models). This allows
interested readers and reviewers to do additional analyses. Unlike experiments
with human subjects, there are no privacy concerns for sharing simulation data.
Furthermore, online tools, such as INTEREST \citep[INteractive Tool for
Exploring REsults from Simulation sTudies,][]{Gasparini2021}, can be used for
interactive exploration of the data set.

While planning a simulation study, it is impossible to think of all potential
weaknesses or problems that may arise when conducting the planned simulations.
In turn, researchers may be reluctant to tie their hands in a pre-registered
protocol. However, a transparently conducted and reported preliminary simulation
can obviate most of these problems. We recommend researchers to disclose
preliminary results and any resulting changes to the protocol, for example, in a
revised and time-stamped version of the protocol. This approach is similar to
conducting a small pilot study, as is often done in non-simulation based
research. Even if researchers realize that further changes are required after
the main simulation study has begun, transparent reporting of when and why
\emph{post hoc} modifications were made allows the reader to better assess the
quality of evidence provided by the study. Researchers designing simulation
studies may draw inspiration from clinical trials by tracking their protocol
modifications and time-stamping versions of their protocol.

A different approach for making \emph{post hoc} changes to the protocol is to
use blinding in the analysis of the simulation results \citep{Dutilh2019}.
Blinded analysis is a standard procedure in particle physics to prevent data
analysts from biasing their result towards their own beliefs \citep{Klein2005},
and it lends legitimacy to \emph{post hoc} modifications of the simulation
study. For instance, researchers might shuffle the method labels and only
unblind themselves after the necessary analysis pipelines are set in place. An
alternative blinding approach is to carry out data generation and analysis by
different researchers. For instance, the study from \citet{Kreutz2020} involved
two independent research groups, one who simulated and one who analyzed the
data. A related way for improving simulation studies is to collaborate with
other researchers, possibly ones familiar with ``competing'' methods. This helps
to design simulation studies which are more objective and whose results are more
useful for making a decision about which method to choose under which
circumstances.

We also recommend researchers to disclose the multiplicity and uncertainty
inherent to the design and analysis of their simulation studies
\citep{Hoffmann2021}. For instance, researchers can report sensitivity analyses
that show how the study results change for different analysis decisions (for
example, Table~4 in \citet{vanSmeden2016} shows how the evaluation metrics for
different estimators change depending on how convergence of a method is
defined). Methods from multivariate statistics can be used for visualizing the
influence of different design choices, such as the multidimensional unfolding
approach in \citet{Niessl2021}.

One reason for the low standards of simulation studies in the statistics
literature may be that rigorous simulation methodology is usually not taught in
graduate or postgraduate courses (with a few exceptions, such as the course
``Using simulation studies to evaluate statistical methods'' from the MRC
Clinical Trials Unit). To improve training of current and future generations of
statisticians, researchers who are involved in teaching should therefore also
include simulation study methodology in their curricula. The standards of
simulation studies in many statistics related fields (for instance, machine
learning, psychometrics, econometrics, or ecology) are arguably not much
different. One possible avenue for future research is thus to also promote
education and adaptation of simulation study methodology for the special needs
in these fields.

\subsection{Recommendations for editors and reviewers}
Peer review is an important tool for identifying QRPs in research results
submitted to methodological journals. For instance, reviewers may demand
researchers to include competitor methods which are not part of their comparison
yet (or which might have been excluded from the comparison). However, reviewers
can only identify a subset of all QRPs since some types are impossible to spot
if no pre-registered simulation protocol is in place (for example, a reviewer
cannot know whether the evaluation criterion was switched). Even QRPs which can
be detected by peer review may be difficult to spot in practice. It is thus
important that reviewers and editors promote that authors make simulation
protocols and computer code available alongside the manuscript. Moreover, by
providing enough space and encouraging authors to provide detailed descriptions
of their simulation studies, replicability of the simulation studies can be
improved. Finally, reviewers should not be satisfied with manuscripts showing
that a method is uniformly superior; they should also encourage authors to
explore conditions in which their method is expected to be inferior to other
methods or to break down entirely.

\subsection{Recommendations for journals and funding bodies}
Journals and funding bodies can improve on the status quo by either actively
requiring or passively incentivizing more rigorous and neutral simulation study
methodology. Actively, journals can make (pre-registered) simulation protocols
mandatory for all articles featuring a simulation study. A more passive and less
extreme measure would be to indicate with a badge whether an article contains a
pre-registered simulation study, or to introduce article types dedicated to
neutral comparison studies. Such an approach rewards researchers who take the
extra effort. Similar initiatives have led to a large increase in the adoption
of pre-registered study protocols in the field of psychology
\citep{Kidwell2016}. Another measure could be to require standardized reporting
of simulation studies, for example, the ``ADEMP'' reporting structure proposed
by \citet{Morris2019}. Journals may also employ reproducibility checks to ensure
computational reproducibility of the published simulation studies. This is
already done, for example, by the Journal of Open Source Software or the Journal
of Statistical Software. Moreover, journals and funding bodies can promote or
fund research and software to improve simulation study methodology. For
instance, a journal might have special calls for papers on simulation
methodology. Similarly, a funding body could have special grants dedicated to
software development that facilitates sound design, execution and reporting of
simulation studies \citep[as][]{White2010, Gasparini2018, Chalmers2020}.
Finally, journals and funding bodies often exert a strong incentive on
researchers to publish novel and superior methods. This may lead to articles
with non-systematic simulation studies that mainly highlight settings beneficial
to the proposed methods. We believe that the above recommendations can shift the
incentive structure towards more transparent and neutral simulation studies, and
away from the ``one method fits all data sets'' philosophy \citep{Strobl2022}.

\section{Conclusions} \label{sec:discussion}

Simulation studies should be viewed and treated analogously to (empirical)
experiments from other fields of science. Transparent reporting of methodology
and results is essential to contextualize the outcome of such a study. As in
other empirical sciences, QRPs in simulation studies can obfuscate the
usefulness of a novel method and lead to misleading and non-replicable results.

By deliberately using several QRPs we were able to present a method with no
expected benefits and little theoretical justification -- invented solely for
this article -- as an improvement over theoretically and empirically
well-established competitors. While such intentional engagement in these
practices is far from the norm, unintentional QRPs may have the same detrimental
effect. We hope that our illustration will increase awareness about the
fragility of findings from simulation studies and the need for higher standards.

While this article focuses on comparative simulation studies, many of the issues
and recommendations also apply to neutral comparison studies with real data sets
as discussed in \citet{Niessl2021}. Some of the noted problems even exist in
theoretical research; due to the incentive to publish positive results,
researchers often selectively study optimality conditions of methods rather than
conditions under which they fail.

Again, it is imperative to note that researchers rarely engage in QRPs with
malicious intent but because humans tend to interpret ambiguous information
self-servingly, and because they are good at finding reasonable justifications
that match their expectations and desires \citep{Simmons2011}. As in other
domains of science, it is easier to publish positive results in methodological
research, that is, novel and superior methods \citep{Boulesteix2015}. Thus,
methodological researchers will typically desire to show the superiority of a
method rather than to neutrally disclose its strengths and weaknesses.

We provide several recommendations involving various stakeholders in the
research community which we believe may help incentivize researchers to perform
well-designed simulation studies. Most importantly, we think that reviewers,
journals and funders should raise the standards for simulation studies by
promoting pre-registered simulation protocols and rewarding researchers who
invest the extra effort. Although there is evidence for the effectiveness of
protocols in preventing QRPs in other fields, it is unclear whether this effect
translates to simulation studies. Indeed, there are many reasons to believe that
simulation studies will not benefit in a similar way as studies with human or
animal subjects, due to the nature of simulations studies. For instance,
requiring pre-registered protocols cannot prevent researchers engaging in QRPs
until they find their desired results and only then writing and registering a
protocol. In addition, there is currently no tradition of pre-registration in
simulation studies, no best-practices guidance and no dedicated platform to
publish protocols. For example, \citet{Kipruto2022} published the
pre-registration of their simulation protocol as a journal article, whereas the
pre-registration of the protocol from our study was uploaded to GitHub. Both
protocols use the ADEMP reporting structure from \citet{Morris2019}, yet the
field could benefit from reporting guidelines developed by a consortium of
simulation experts similar to the guidelines for health research promoted by the
EQUATOR Network \citep{Altman2008}. Similarly, the field could benefit from a
centralized pre-registration platform tailored to simulation studies (similar to
\url{https://clinicaltrials.gov} for clinical trials). Regardless of the
(unknown) effectiveness of pre-registered simulation protocols, we personally
think that they are an important step toward improving simulation studies since
they promote a minimum degree of transparency and credibility. For this reason,
we think that they are especially important for ``late-stage'' methodological
studies \citep{Heinze2022} where the objective is to neutrally compare different
methods and generate robust evidence.

\section*{Software and data}
The simulation study was conducted in the R language for statistical computing
\citep{R} using the version 4.1.1. The method \ainet{} is implemented in the
\texttt{ainet} package and available on GitHub
(\url{https://github.com/LucasKook/ainet}). We provide scripts for reproducing
the different simulation studies on the GitHub repository
(\url{https://github.com/SamCH93/SimPaper}). Due to the computational overhead,
we also provide the resulting data so that the analyses can be conducted without
rerunning the simulations. We used \texttt{pROC} version 1.18.0 to compute the
AUC \citep{Robin2011}. Random forests were fitted using \texttt{ranger} version
0.13.1 \citep{Wright2017}. For penalized likelihood methods, we used
\texttt{glmnet} version 4.1.2 \citep{Friedman2010,Simon2011}. The
\texttt{SimDesign} package version 2.7.1 was used to set up simulation scenarios
\citep{Chalmers2020}.

\section*{Acknowledgements}
We thank Eva Furrer, Malgorzata Roos and Torsten Hothorn for helpful discussion
and comments on the simulation protocol and drafts of the manuscript. We also
thank the anonymous referees and the associate editor for constructive and
valuable comments that improved the manuscript substantially. Our
acknowledgement of these individuals does not imply their endorsement of this
article. The authors declare that they do not have any conflicts of interest.

\begin{subappendices}
\renewcommand{\thesection}{\Alph{section}}

\section{Simulation protocol}
\label{appendix:protocol}

Below, we include an excerpt of the final version of the protocol for the
simulation-based evaluation of \ainet{}. All time-stamped versions of the
protocol are available at \url{https://doi.org/10.5281/zenodo.6364575}.

\subsection{Aims} \label{sec:aims}

The aim of this simulation study is to systematically study the predictive
performance of \ainet{} for a binary prediction task. The simulation conditions
should resemble typical conditions found in the development of prediction models
in biomedical research. In particular we want to evaluate the performance of
\ainet{} conditional on
\begin{itemize}
  \item low- and high-dimensional covariates
  \item (un-)correlated covariates
  \item small and large sample sizes
  \item varying baseline prevalences
\end{itemize}
\ainet{} will be compared to other (penalized) binary regression models
from the literature, namely
\begin{itemize}
  \item Binary logistic regression: the simplest and most popular method for
        binary prediction
  \item Elastic net: a generalization of LASSO and ridge regression, the most
        widely used penalized regression methods
  \item Adaptive elastic net: a generalization of the most popular weighted
  penalized regression method (adaptive LASSO)
  \item Random forest: a popular, more flexible method. This method is related to
        \ainet{}, see Section~\ref{sec:methods}.
\end{itemize}
These cover a wide range of established methods with varying flexibility and
serve as a reasonable benchmark for \ainet. There are many more extensions of
the adaptive elastic net in the literature \citep[see \eg{} the review
by][]{Vidaurre2013}. However, most of these extensions focus on variable
selection and estimation instead of prediction, which is why we restrict our
focus only on the four methods above.

\subsection{Data-generating process} \label{sec:dgp}

In each simulation $b = 1, \dots, B$, we generate a data set consisting of $n$
realizations, \ie $\{(\ry_i, \rx_i)\}_{i=1}^n$. A datum $(\rY, \rX)$ consists of
a binary outcome $\rY \in \{0, 1\}$ and $p$-dimensional covariate vector
$\rX \in \RR^p$. The binary outcomes are generated by
\begin{align*}
  Y \given \rx &\sim \BD\left(\expit\left\{\beta_0 +
	\rx^\top\shiftparm\right\}\right)
\end{align*}
with $\expit(z) = (1 + \exp(-z))^{-1}$ and the covariate vectors are generated
by
\begin{align*}
  \rX &\sim \ND_p\left(0, \Sigma\right)
\end{align*}
with covariance matrix $\Sigma$ that may vary across simulation conditions (see
below). The baseline prevalence is $\prev = \expit(\beta_0)$. The coefficient
vector $\shiftparm$ is generated from
\begin{align*}
  \shiftparm \sim \ND_p(0, \Id)
\end{align*}
once per simulation. Finally, the simulation parameters are varied fully
factorially (except for the removal of some unreasonable conditions) as
described below, leading to a total of 128 scenarios, see below.

\subsection*{Sample size}
The sample size used in the development of predictions models varies widely
\citep{Damen2016}. We will use $n \in \{100, 500, 1000, 5000\}$, which span
typical values occurring in practice. Note that previous simulation studies
usually chose sample size based on the implied number of events together with
the number of covariates in the model for easier interpretation
\citep{vanSmeden2018, Riley2018}. We will use this approach in reverse to
determine the dimensionality of the parameters below.

\subsection*{Dimensionality}
Previous simulation studies showed that events per variable ($\EPV$) rather than
the absolute sample size $n$ and dimensionality $p$ influences the predictive
performance of a method. We will therefore define the dimensionality $p$ via EPV
by $$p = \frac{n \cdot \prev}{\EPV}$$ and $2 \leq p \leq 100.$ If the above
formula gives non-integer values, the next larger integer will be used for $p$.
When the formula gives values above 100 or below 2, this simulation condition
will be removed from the design. This is done because prediction models are in
practice only multivariable models ($p \geq 2$), but at the same time the number
of predictors is rarely larger than $p \geq 100$
\citep{Kreuzberger2020,Seker2020, Wynants2020}. The exception are studies
considering complex data, such as images, omics, or text data which are not the
focus here. The values $\EPV \in \{20, 10, 1, 0.5\}$ are chosen to cover
scenarios with small to large number of covariates \citep[see][]{vanSmeden2018}.

\subsection*{Collinearity in $\rX$}
We distinguish between no, low, medium and high collinearity. The diagonal
elements of $\Sigma$ are given by $\Sigma_{ii} = 1$ and the off-diagonal
elements are set to $\Sigma_{ij} = \rho$, $\rho \in \{0, 0.3, 0.6, 0.95\}$.
These values cover the typical (positive) range of correlations.

\subsection*{Baseline prevalence}
Different baseline prevalences $\expit(\beta_0) \in \{0.01, 0.05, 0.1\}$ are
considered, reflecting a reasonable range of prevalences for rare to common
diseases/adverse events.

\subsection*{Test data}
In order to test the out-of-sample predictive performance, we generate a test
data set of $n_{\text{test}} = 10000$ data points in each simulation $b$.

\subsection{Estimands} \label{sec:estimands}

We will estimate different quantities to evaluate overall predictive
performance, calibration, and discrimination, respectively. All methods will be
evaluated on independently generated test data.

\subsubsection{Primary estimand}

\begin{itemize}
  \item \textbf{Brier score.} We compute the Brier score as
  $$\BS = n_{\text{test}}^{-1} \sum_{i=1}^{n_{\text{test}}} (y_{i} - \hat{y}_{i})^2,$$
        where $\hat{y} = \widehat\Prob(Y = 1 \given \rx)$. Lower values indicate
        better predictive performance in terms of calibration and sharpness. A
        prediction is well-calibrated if the observed proportion of events is
        close to the predicted probabilities. Sharpness refers to how
        concentrated a predictive distribution is (\eg{} how wide/narrow a
        prediction interval is), and the predictive goal is to maximize
        sharpness subject to calibration \citep{Gneiting2008}. The Brier score
        is a proper scoring rule, meaning that it is minimized if a predicted
        distribution is equal to the data-generating distribution
        \citep{Gneiting2007}. Proper scoring rules thus encourage honest
        predictions. The Brier score is therefore a principled choice for our
        primary estimand.
\end{itemize}

\subsubsection{Secondary estimands}
\begin{itemize}
  \item \textbf{Scaled Brier score.} The scaled Brier score (also known as Brier
        skill score) is computed as
  $$\BS^{*} = 1 - \BS/\BS_{0}$$
        with $\BS_{0} = \bar{y}(1 - \bar{y})$ and $\bar{y}$ the observed
        prevalence in the data set. The scaled Brier score takes into account
        that the prevalence varies across simulation conditions. Hence, the
        scaled Brier score can be compared between conditions \citep{Schmid2005,
        Steyerberg2019}.

  \item \textbf{Log-score.} We compute the log-score on independently generated test data,
  $$\LS = - n_{\text{test}}^{-1} \sum_{i=1}^{n_{\text{test}}} \left\{ y_{i} \log(\hat{y}_{i})
        + (1 - y_{i}) \log (1 - \hat{y}_{i})\right\},$$ will be used as a
        secondary measure of overall predictive performance. Lower values
        indicate better predictive performance in terms of calibration and
        sharpness. The log-score is a strictly proper scoring rule, however, it
        is more sensitive to extreme predicted probabilities compared to the
        Brier score \citep{Gneiting2007}.

  \item \textbf{AUC.} The AUC is given by
  $$\text{AUC} = \max\{\text{PI}, 1 - \text{PI}\}$$
        with $$\text{PI} = \widehat\Prob(Y_i \geq Y_j \given \rx_i, \rx_j), \; i,j = 1, \dots, n_{\text{test}},$$
        where $Y_i$ and $Y_j$ denote case and non-case, respectively. The AUC is
        related to the area under the receiver-operating-characteristic (ROC)
        curve \citep{Steyerberg2019}. It will be used as a measure of
        discrimination and values closer to one indicate better discriminative
        ability. Discrimination describes the ability of a prediction model to
        discriminate between cases and non-cases. Other discrimination measures,
        such as accuracy, sensitivity, specificity, etc., are not considered
        because we want to evaluate predictive performance in terms of
        probabilistic predictions instead of point predictions/classification.

  \item \textbf{Calibration slope $\hat b$.} The calibration slope $\hat b$ is
        obtained by regressing the test data outcomes $y_{\text{test}}$ on the
        models' predicted logits $\logit({\hat{y}})$, \ie
  $$\logit\Ex[Y \given \hat\ry] = a + b\logit(\hat\ry).$$
        This measure will be used to assess calibration and deviations of
        $\hat b$ from one indicate miscalibration \citep{Steyerberg2019}.

  \item \textbf{Calibration in the large $\hat a$.} We inspect calibration in the
  large $\hat a$ on independently generated test data, from the model
  $$\logit\Ex[Y \given \hat\ry] = a + \logit(\hat{y}).$$
        This measure will also be used to assess calibration and deviations of
        $\hat a$ from zero indicate miscalibration \citep{Steyerberg2019}.
\end{itemize}

To facilitate comparison between simulation conditions, all estimands will also
be corrected by the oracle version of the estimand, \eg{} the Brier score will
be computed from the ground truth parameters and the simulated data $\rx$,
subsequently the oracle Brier score will be subtracted from the estimated Brier
score.

\subsection{Methods} \label{sec:methods}

\subsubsection{AINET}
We now present the mock-method and give a superficial motivation why it could
lead to improved predictive performance: Choosing the vector of penalization
weights in the adaptive LASSO becomes difficult in high-dimensional settings.
For instance, using absolute LASSO estimates as penalization weights omits the
importance of several predictors by not selecting them, especially in the case
of highly correlated predictors \citep{Algamal2015}. The adaptive importance
elastic net (\ainet{}) circumvents this problem by employing a random forest to
estimate the penalization weights via an \emph{a priori} chosen variable
importance measure. In this way, the importance of all variables enter the
penalization weights simultaneously.

The penalized log-likelihood for \ainet{} for a single observation $(\ry, \rx)$
is defined as
$$\ell_{\text{AINET}}(\beta_0, \shiftparm; \ry, \rx, \alpha, \lambda, \wvec) =
  \ell(\beta_0, \shiftparm; \ry, \rx) + \aipen$$
where
$$\ell(\beta_0, \shiftparm; \ry, \rx) =
\ry \log\left(\expit\left\{\beta_0 + \linpred\right\}\right) + (1 - \ry) \log\left(1 - \expit\left\{\beta_0 + \linpred\right\}\right)$$
denotes the log-likelihood of a binomial GLM and $\wvec$ is derived from a
random forest variable importance measure $\IMP$ as
$$w_j = 1 - \left(\frac{\IMP_j}{\sum_{k=1}^p \IMP_k}\right)^\gamma,$$
where we transform $\IMP$ to be non-negative via
$$\IMP_j = \max\{0, \widetilde\IMP_j\}$$
and $\gamma$ is a hyperparameter for the influence of the weights similar to
$\gamma$ hyperparameter of the adaptive elastic net. \ainet{} is fitted by
maximizing its penalized log-likelihood assuming i.i.d. observations
$\{(\ry_i, \rx_i)\}_{i=1}^n$, \ie
$$\arg\max_{\beta_0, \shiftparm} \sum_{i = 1}^n \ell_{\text{AINET}}(\beta_0,
\shiftparm; \ry_i, \rx_i, \alpha, \lambda, \wvec).$$

Per default, we choose mean decrease in the Gini coefficient for
$\widetilde\IMP$. Hyperparameters of the random forest are not tuned, but kept
at their default values (\eg{} \code{mtry}, \code{ntree}). The hyperparameter
$\gamma = 1$ will stay constant for all simulations.

\ainet{} is supposed to seem like a reasonable method at first glance. However,
\ainet{} cannot be expected to share desirable theoretical properties with the
usual adaptive LASSO, such as oracle estimation \citep{Zou2006}. This is because
the penalization weights $\wvec$ do not meet the required consistency
assumption. Also in terms of prediction performance, \ainet{} is not expected to
outperform methods of comparable complexity.

\subsubsection{Benchmark methods}

\begin{itemize}
  \item \textbf{Binary logistic regression} \citep{Mccullagh2019} with and
        without ridge penalty for high- and low-dimensional settings,
        respectively. In case a ridge penalty is needed, it is tuned via 5-fold
        cross-validation by following the ``one standard error'' rule as
        implemented in \pkg{glmnet} \citep{Friedman2010}.
  \item \textbf{Elastic net} \citep{Zou2005}, for which the penalized
        log-likelihood is given by
    $$\ell_{\text{EN}}(\beta_0, \shiftparm; \ry, \rx, \alpha, \lambda) =
        \ell(\beta_0, \shiftparm; \ry, \rx) + \llpen.$$ Here, $\alpha$ and
        $\lambda$ are tuned via 5-fold cross-validation by following the ``one
        standard error'' rule.
   \item \textbf{Adaptive elastic net} \citep{Zou2006}, with penalized loss function
    $$\ell_{\text{adaptive}}(\beta_0, \shiftparm; \ry, \rx, \alpha, \lambda, \wvec)
        = \ell(\beta_0, \shiftparm; \ry, \rx) + \aipen.$$ Here, the penalty
        weights $\wvec$ are inverse coefficient estimates from a binary logistic
        regression
    $$\hat{w}_j = \lvert\hat\eparm_j\rvert^{-\gamma},$$
        where $\lambda$ and $\alpha$ are tuned via 5-fold cross-validation by
        following the ``one standard error'' rule. The hyperparameter
        $\gamma = 1$ will stay constant for all simulations. In case $p > n$, we
        estimate the penalty weights using a ridge penalty, tuned via an
        additional nested 5-fold cross-validation by following the ``one
        standard error'' rule.
  \item \textbf{Random forests} \citep{Breiman2001} for binary outcomes without
        hyperparameter tuning. The default parameters of \pkg{ranger} will be
        used \citep{Wright2017}.
\end{itemize}

\subsection{Performance measures} \label{sec:performance}

The distribution of all estimands from Section~\ref{sec:estimands} will be
assessed visually with box- and violin-plots that are stratified by method and
simulation conditions. We will also compute mean, median, standard deviation,
interquartile range, and 95\% confidence intervals for each of the estimands.
Moreover, instead of ``eye-balling'' differences in predictive performance
across methods and conditions, we will formally assess them by regressing the
estimands on the method and simulation conditions \citep[see][]{Skrondal2000}.
To do so, we will use a fully interacted model with the interaction between the
methods and the 128 simulations conditions, \ie in R notation: \texttt{estimand
  $\sim$ 0 + method:scenario}. We will rank pairwise comparison between two
methods within a single condition by their $p$-values, to more easily identify
conditions where methods show differences in predictive performance. The choice
of a significance level at which a method is deemed superior will be determined
based on preliminary simulations. We set this level to 5\%, where $p$-values
will be adjusted using the single-step method \citep{Hothorn2008} within a
single simulation condition for comparisons between \ainet{} and any other
method.

\subsection{Determining the number of simulations}

We determine the number of simulation $B$ such that the Monte Carlo standard
error of the primary estimand, the mean Brier score $\BS/B$, is sufficiently
small. The variance of $\BS/B$ is given by
\begin{align*}
  \Var\left(\BS/B\right)
  &= \frac{\Var\left\{(y -
    \hat{y})^{2}\right\}}{B \cdot n_{\text{test}}}
\end{align*}
and $\Var\left\{(y_{ib} - \hat{y}_{ib})^{2}\right\}$ could be decomposed further
\citep{Bradley2008}. However, the resulting expression is difficult to evaluate
for our data-generating process as it depends on several of the simulation
parameters. We therefore follow a similar approach as in \citet{Morris2019} and
estimate $\widehat{\Var}\left\{(y_{ib} - \hat{y}_{ib})^{2}\right\} < V$ from an
initial small simulation run with 100 simulations per condition to get an upper
bound $V$ for worst-case variance across all simulation conditions. Therefore,
the number of simulations is then given by
$$B = \frac{V}{n_{\text{test}} \Var\left(\BS\right)}.$$
Since $\BS \in [0, 1]$ we decide that we require the Monte Carlo standard error
of $\BS$ to be lower than four significant digits, $0.0001$.

The initial simulation run led to an estimated worst case variance of
$\widehat{V} = 0.2$. Therefore, we compute that
$$B = 0.2/(10000 \times 0.0001^{2}) = 2000$$
replications are required to obtain Brier score estimates with the
desired precision.

\subsection{Handling exceptions} \label{sec:exceptions}

It is inevitable that convergence issues and other problems will arise in the
simulation study. We will handle them as follows:
\begin{itemize}
  \item If a method fails to converge, the simulation will be excluded from the
        analysis. The failing simulations will not be replaced with new
        simulations that successfully converge as convergence may be impossible
        for some scenarios.
  \item We will report the proportion of simulations with convergence issues for
        each method and discuss the potential reasons for their emergence.
  \item In case of severe convergence issues or other problems (more than 10\%
        of the simulations failing within a setting), we may adjust the
        simulation parameters post hoc. This will be indicated in the discussion
        of the results.
  \item Convergence may be possible for certain tuning parameters of a method
        (\eg{} cross-validation of LASSO may fail for some values $\lambda$
        while it could work for others). In this case we will choose a parameter
        value where the method still converges, as one would usually do with a
        real data set.
\end{itemize}

\section{Pre-registered simulation results}

Here, we describe the outcomes of the pre-registered simulations. Overall, the
performance of \ainet{} was virtually identical to elastic net regression. The
adaptive penalization weights of \ainet{} do not seem to make a difference for
the data generating mechanism considered in our simulations. Moreover, since the
data were generated under a process equivalent to a logistic regression model,
it is no surprise that for reasonably large sample sizes, logistic regression
also performed the best. The only exception are conditions with small sample
size and low number of events per variable. Here, \ainet{} and elastic net led
to more stable and better calibrated predictions than logistic regression. The
random forest was outperformed by \ainet{} in most simulation conditions, with
exception of very small sample size and prevalence, as well as when a high
correlation between covariates was present. Finally, the performance of the
adaptive elastic net was generally worse compared to \ainet{} and elastic net.
In the following, we summarize the results for each estimand.

\subsection{Brier score (primary estimand)}

Figure~\ref{fig:tiebrier} shows the differences in mean Brier score between
\ainet{} and the other methods stratified by simulation conditions. We see that
there is hardly any difference between \ainet{} and the elastic net (EN) across
all simulation conditions meaning that predictive performance of both methods
seems to be very similar in the investigated scenarios.

% random forest
The random forest (RF) shows better predictive performance than \ainet{} in
conditions with very low sample size ($n = 100$) and prevalence
($\mbox{prev} = 0.01$). For increasing sample size and prevalence, the
performance of \ainet{} seems to become more similar or improve over RF when the
correlation of the covariates is not too large ($\rho \leq 0.6$) especially for
low events per variable ($\mbox{EPV} \leq 1$). For highly correlated covariates
($\rho = 0.95$), the performance of \ainet{} is similar or worse across most
simulation conditions.

% GLM
Logistic regression (GLM) showed better predictive performance compared to
\ainet{} in most simulation conditions. An exception are the conditions with
small sample size ($n = 100$), medium to large prevalence
($\mbox{prev} \geq 0.05$) and low events per variable ($\mbox{EPV} \leq 1$),
where \ainet{} performed better than GLM.

The adaptive elastic net (AEN) method performed worse than \ainet{} in almost
all simulation conditions. Only in conditions with very large sample size
($n = 5000$), very small prevalence ($\mbox{prev} = 0.01$), and high events per
variable ($\mbox{EPV} = 20$), AEN showed predictive performance on par with
\ainet{}.

\subsection{Scaled Brier score (secondary estimand)}

Figure~\ref{fig:tiesbrier} shows the differences in scaled Brier score between
\ainet{} and the other methods stratified by simulation conditions. The scaled
Brier score is useful to compare the actual values of Brier scores across
conditions with different prevalence, but not so much to compare Brier scores of
different methods within a simulation condition with fixed prevalence.

We see that for most conditions the plots look like a flipped version of the
original Brier scores from Figure~\ref{fig:tiebrier}. Therefore, conclusions are
mostly the same. For very small sample sizes coupled with low prevalence and low
events per variable (the topleft plots), the scaled Brier score indicates
superiority of \ainet{} over RF and GLM, which is opposite the conclusion based
on the raw Brier score. We advise to interpret these conditions cautiously since
the prevalence prediction which is used for scaling is based on the much larger
test data set.

\subsection{Log-score (secondary estimand)}

Figure~\ref{fig:tienll} shows the differences in log-score between \ainet{} and
the other methods stratified by simulation conditions. We see that in certain
conditions, the error bars of certain methods are much larger. This is due to
the log-score's sensitivity to extreme predictions, which often happen under the
RF (and sometimes under the GLM). Despite the larger variability of the
log-score, conclusion regarding the comparison between \ainet{} and the other
methods are largely the same as under the Brier score.

\subsection{Area under the curve (secondary estimand)}

Figure~\ref{fig:tienll} shows the differences in area under the curve (AUC)
between \ainet{} and the other methods stratified by simulation conditions. As
with the other estimands, \ainet{} shows virtually identical performance as EN
regression across all simulation conditions. \ainet{} seems to outperform RF
across most simulation conditions, with the exception of a conditions with low
sample size ($n = 100$), medium prevalence ($\mbox{prev} = 0.05$), and low
events per variable ($\mbox{EPV} \leq 1$). GLM, typically outperforms \ainet{}
conditions with small to medium sample size ($n \leq 500$), and also in
conditions with larger sample size when the events per variable is normal to
high ($\mbox{EPV} \geq 10$) and the prevalence is small ($\mbox{prev} = 0.01$).
Finally, the AEN is worse with respect to AUC than \ainet{} across all
simulation conditions.

\subsection{Calibration slope (secondary estimand)}

Figure~\ref{fig:cslope} shows boxplots of calibration slopes stratified by
simulation condition and method. For each condition the percentage of
simulations where no estimate could be obtained is indicated. This usually
happened because of extreme (close to zero or one) predictions, or
non-convergence of the method itself. We caution against interpretation of the
random forest (RF) calibration slopes because this method often resulted in
predicted probabilities of zero or one, so that a calibration slope could not be
fitted.

We see that logistic regression (GLM) shows on average optimal calibration
slopes in most simulation condition. In cases where it is off one, its
calibration slopes are usually too small indicating overoptimistic predictions.
In general, worse calibration slopes are obtained for lower event per variable
(EPV).

The penalized methods (\ainet{}, EN, AEN) show a more stable behavior, and on
average larger calibration slopes than GLM. This is likely confounded by the
simulation conditions in which no GLM calibration slope can be estimated, but
estimation of the penalized methods' calibration slope is still possible. Among
the penalized method's \ainet{} and EN shows relatively similar calibration
slopes whereas the AEN shows worse calibration slopes that are more off the
value of one.

\subsection{Calibration in the large (secondary estimand)}

Figure~\ref{fig:clarge} shows boxplots of calibration in the large estimates
stratified by simulation condition and method. For each condition also the
percentage of simulations where no estimate could be obtained is indicated. This
usually happened because of extreme (close to zero or one) predictions.

We see that the number of simulations with non-estimable calibration is
substantially larger when the sample size is small, whereas it decreases for
larger sample sizes. An exception is the RF where the number of non-estimable
calibrations stays high across most conditions.

While all methods seem to be marginally well calibrated, the penalized methods
(\ainet{}, EN, and AEN) show lower numbers of simulations with non-estimable
calibration compared to GLM, especially for low to medium sample sizes and low
events per variables.

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_brier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in Brier score between any method
  on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted per
  simulation condition using the single-step method. Lower values indicate
  better performance of \ainet{}. } \label{fig:tiebrier}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_scaledBrier_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in scaled Brier score between any
  method on the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted
  per simulation condition using the single-step method. Larger
  values indicate better performance of \ainet{}. } \label{fig:tiesbrier}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_nll_sparsity0.pdf}
\caption{Tie-fighter plot for the difference in log-score between any method on
  the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted per
  simulation condition using the single-step method. Lower values indicate
  better performance of \ainet{}. } \label{fig:tienll}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/calibration-cslope_sparsity0.pdf}
\caption{Boxplots of calibration slopes stratified by method and simulation
  conditions. Mean calibration slope is indicated by a cross. A value of one
  indicates optimal calibration. Percentage of simulations where calibration
  slope could not be estimated (due to extreme predictions or complete
  separation) are also indicated.} \label{fig:cslope}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[!ht]
\center
\includegraphics[width=0.9\linewidth]{images/paper6/calibration-clarge_sparsity0.pdf}
\caption{Boxplots of calibration in the large stratified by method and
  simulation conditions. Mean calibration in the large is indicated by a cross.
  A value of zero indicates optimal calibration in the large. Percentage of
  simulations where calibration in the large could not be estimated (due to
  extreme predictions or complete separation) are also
  indicated.} \label{fig:clarge}
\end{figure}
\end{landscape}

\end{subappendices}

\newpage
\bibliographystyle{apalikedoiurl}
\bibliography{bibliography}

### 2022-12-18 paper6.tex
polish references

@@
 
-Figure~\ref{fig:diagram} shows a schematic illustration of an example
+Figure~\ref{fig6:diagram} shows a schematic illustration of an example
 comparative simulation study. We see that, just like non-simulation based
@@
   performance of methods for predicting binary outcomes, such as the example
-  study in Section~\ref{sec:study}. Questionable research practices (in gray)
+  study in Section~\ref{sec6:study}. Questionable research practices (in gray)
   can affect all aspects of the study.}
-\label{fig:diagram}
+\label{fig6:diagram}
 \end{figure}
@@
 undermine the validity of comparative simulations studies and which can easily
-go undetected under current publishing standards. Figure~\ref{fig:diagram} shows
+go undetected under current publishing standards. Figure~\ref{fig6:diagram} shows
 several QRPs that may occur in the exemplary simulation study. There is often a
@@
 This article is structured as follows: We first give an illustrative list of
-QRPs related to comparative simulation studies (Section \ref{sec:QRP}). With an
+QRPs related to comparative simulation studies (Section \ref{sec6:QRP}). With an
 exemplary simulation study, we then show h?ow easy it is to present a novel,
 made-up method as an improvement over others if QRPs are employed and \emph{a
-  priori} simulation plans remain undisclosed (Section \ref{sec:study}). The
+  priori} simulation plans remain undisclosed (Section \ref{sec6:study}). The
 main inspiration for this work is drawn from similar illustrative studies which
@@
 expanded on QRPs in benchmarking studies with the latter also including
-simulation studies. In Section~\ref{sec:recommendations}, we then provide
+simulation studies. In Section~\ref{sec6:recommendations}, we then provide
 concrete suggestions for researchers, reviewers, editors and funding bodies to
 alleviate the issues of QRPs and improve the methodological quality of
-comparative simulation studies. Section~\ref{sec:discussion} closes with
+comparative simulation studies. Section~\ref{sec6:discussion} closes with
 limitations and concluding remarks.
@@
 \section{Questionable research practices in comparative simulation studies}
-\label{sec:QRP}
+\label{sec6:QRP}
 
 There are various QRPs which threaten the validity of comparative simulation
-studies (see Table~\ref{table:QRPs} for an overview). QRPs can be categorized
+studies (see Table~\ref{table6:QRPs} for an overview). QRPs can be categorized
 with respect to the stage of research at which they can occur and which other
@@
     reporting QRP.}
-  \label{table:QRPs}
+  \label{table6:QRPs}
   \centering
@@
 \section{Empirical study: The Adaptive Importance Elastic Net
-  (AINET)} \label{sec:study}
-
-To illustrate the application of QRPs from Table~\ref{table:QRPs} we conducted a
-simulation study. The objective of the study was to evaluate the predictive
+  (AINET)} \label{sec6:study}
+
+To illustrate the application of QRPs from Table~\ref{table6:QRPs} we conducted
+a simulation study. The objective of the study was to evaluate the predictive
 performance of a made-up regression method termed the \emph{adaptive importance
@@
 elastic net is expected. For more details on the method, we refer the reader to
-the simulation protocol (Appendix~\ref{appendix:protocol}). We report the
-pre-registered\footnote{We use the term \emph{pre-registered} throughout to
-  refer to simulation analyses conducted as pre-specified in the protocol.}
-simulation study results in the online supplement. As expected, the performance
-of \ainet{} was virtually identical to standard elastic net regression. \ainet{}
-also did not yield any improvements over logistic regression for the
-data-generating process that we considered sensible \emph{a priori} (that is,
-specified based on typical conditions in clinical prediction modeling and
-simulation studies from other researchers).
+the simulation protocol (Appendix~\ref{app6:protocol}). We report the
+pre-registered simulation study results in the online supplement (we use the
+term \emph{pre-registered} throughout to refer to simulation analyses conducted
+as pre-specified in the protocol). As expected, the performance of \ainet{} was
+virtually identical to standard elastic net regression. \ainet{} also did not
+yield any improvements over logistic regression for the data-generating process
+that we considered sensible \emph{a priori} (that is, specified based on typical
+conditions in clinical prediction modeling and simulation studies from other
+researchers).
 
@@
     variable (EPV), in each simulation the Brier score is computed for 10'000
-    test observations; for details see Appendix~\ref{appendix:protocol}). The
+    test observations; for details see Appendix~\ref{app6:protocol}). The
     top row depicts the pre-registered results in which \ainet{} does not
@@
     impression for \ainet{}. Arrows are depicted only for non-overlapping
-    confidence intervals. } \label{fig:E1}
+    confidence intervals. } \label{fig6:E1}
 \end{figure}
@@
 We now show how application of QRPs changes the above pre-registered
-conclusions. Figure~\ref{fig:E1} illustrates different types of QRPs
+conclusions. Figure~\ref{fig6:E1} illustrates different types of QRPs
 sequentially applied to simulation-based evaluation of \ainet{}. The top row
@@
 non-linear effect and a low number of events per variable (EPV).
-Figure~\ref{fig:E1} (second row) shows the changes in Brier score difference
+Figure~\ref{fig6:E1} (second row) shows the changes in Brier score difference
 between the pre-registered and the tweaked simulation. As can be seen, the
@@
 in a better light we could omit the comparisons with the elastic net (E3), as
-shown in Figure~\ref{fig:E1} (third row). This could be justified, for example,
+shown in Figure~\ref{fig6:E1} (third row). This could be justified, for example,
 by arguing that for neutral comparison it is sufficient to compare a less
@@
 make \ainet{} appear more favorable, we thus report only simulation conditions
-with low EPV, as shown in Figure~\ref{fig:E1} (fourth row). This could be
+with low EPV, as shown in Figure~\ref{fig6:E1} (fourth row). This could be
 justified by the fact that journals require authors to be concise in their
@@
 \section{Recommendations}
-\label{sec:recommendations}
+\label{sec6:recommendations}
 
@@
 improving the methodological quality of simulation studies; see
-Table~\ref{table:recommendations} for an overview. Our recommendations are
+Table~\ref{table6:recommendations} for an overview. Our recommendations are
 grouped with regards to which stakeholder they concern.
@@
     and preventing QRPs.}
-  \label{table:recommendations}
+  \label{table6:recommendations}
   \centering
@@
 
-\section{Conclusions} \label{sec:discussion}
+\section{Conclusions} \label{sec6:discussion}
 
@@
 \section{Simulation protocol}
-\label{appendix:protocol}
+\label{app6:protocol}
 
@@
 
-\subsection{Aims} \label{sec:aims}
+\subsection{Aims} \label{sec6:aims}
 
@@
   \item Random forest: a popular, more flexible method. This method is related to
-        \ainet{}, see Section~\ref{sec:methods}.
+        \ainet{}, see Section~\ref{sec6:methods}.
 \end{itemize}
@@
 
-\subsection{Data-generating process} \label{sec:dgp}
+\subsection{Data-generating process} \label{sec6:dgp}
 
@@
 In order to test the out-of-sample predictive performance, we generate a test
-data set of $n_{\text{test}} = 10000$ data points in each simulation $b$.
-
-\subsection{Estimands} \label{sec:estimands}
+data set of \mbox{$n_{\text{test}} = 10000$} data points in each simulation $b$.
+
+\subsection{Estimands} \label{sec6:estimands}
 
@@
 
-\subsection{Methods} \label{sec:methods}
+\subsection{Methods} \label{sec6:methods}
 
@@
 
-\subsection{Performance measures} \label{sec:performance}
-
-The distribution of all estimands from Section~\ref{sec:estimands} will be
+\subsection{Performance measures} \label{sec6:performance}
+
+The distribution of all estimands from Section~\ref{sec6:estimands} will be
 assessed visually with box- and violin-plots that are stratified by method and
@@
 
-\subsection{Handling exceptions} \label{sec:exceptions}
+\subsection{Handling exceptions} \label{sec6:exceptions}
 
@@
 
-Figure~\ref{fig:tiebrier} shows the differences in mean Brier score between
+Figure~\ref{fig6:tiebrier} shows the differences in mean Brier score between
 \ainet{} and the other methods stratified by simulation conditions. We see that
@@
 
-Figure~\ref{fig:tiesbrier} shows the differences in scaled Brier score between
+Figure~\ref{fig6:tiesbrier} shows the differences in scaled Brier score between
 \ainet{} and the other methods stratified by simulation conditions. The scaled
@@
 We see that for most conditions the plots look like a flipped version of the
-original Brier scores from Figure~\ref{fig:tiebrier}. Therefore, conclusions are
+original Brier scores from Figure~\ref{fig6:tiebrier}. Therefore, conclusions are
 mostly the same. For very small sample sizes coupled with low prevalence and low
@@
 
-Figure~\ref{fig:tienll} shows the differences in log-score between \ainet{} and
+Figure~\ref{fig6:tienll} shows the differences in log-score between \ainet{} and
 the other methods stratified by simulation conditions. We see that in certain
@@
 
-Figure~\ref{fig:tienll} shows the differences in area under the curve (AUC)
+Figure~\ref{fig6:tienll} shows the differences in area under the curve (AUC)
 between \ainet{} and the other methods stratified by simulation conditions. As
@@
 
-Figure~\ref{fig:cslope} shows boxplots of calibration slopes stratified by
+Figure~\ref{fig6:cslope} shows boxplots of calibration slopes stratified by
 simulation condition and method. For each condition the percentage of
@@
 
-Figure~\ref{fig:clarge} shows boxplots of calibration in the large estimates
+Figure~\ref{fig6:clarge} shows boxplots of calibration in the large estimates
 stratified by simulation condition and method. For each condition also the
@@
   simulation condition using the single-step method. Lower values indicate
-  better performance of \ainet{}. } \label{fig:tiebrier}
+  better performance of \ainet{}. } \label{fig6:tiebrier}
 \end{figure}
@@
   per simulation condition using the single-step method. Larger
-  values indicate better performance of \ainet{}. } \label{fig:tiesbrier}
+  values indicate better performance of \ainet{}. } \label{fig6:tiesbrier}
 \end{figure}
@@
   simulation condition using the single-step method. Lower values indicate
-  better performance of \ainet{}. } \label{fig:tienll}
+  better performance of \ainet{}. } \label{fig6:tienll}
 \end{figure}
@@
   slope could not be estimated (due to extreme predictions or complete
-  separation) are also indicated.} \label{fig:cslope}
+  separation) are also indicated.} \label{fig6:cslope}
 \end{figure}
@@
   extreme predictions or complete separation) are also
-  indicated.} \label{fig:clarge}
+  indicated.} \label{fig6:clarge}
 \end{figure}

### 2022-12-19 intro.Rnw
last polish of intro?

@@
 
-\begin{wrapfigure}{r}{0.29\textwidth}
+\begin{wrapfigure}{r}{0.285\textwidth}
   \centering
@@
 instance, how can we know whether the protective effect of a vaccine found in a
-study is indeed existent, or whether it is just a spurious finding? One way to
-answer this question is through the use of \emph{replication studies}.
-
-A replication study (or, simply, replication) involves repeating the original
+study is indeed existent? One way to answer this question is through the use of
+\emph{replication studies}.
+
+A replication study (or simply replication) involves repeating the original
 study as closely as possible but with new subjects. If the replication yields
@@
 population, as the implementation of policies based on scientific findings may
-also depend on whether these findings can be replicated. For instance, the
-United States food and drug administration requires ``\textit{at least two
-  adequate and well-controlled studies, each convincing on its own, to establish
-  effectiveness}'' \citep[p. 3]{FDA1998} for market approval of a drug. The
-results from replication studies may hence have real-world consequences. It is
-therefore important that the methodological aspects of replication studies, such
-as their statistical design and analysis, are well understood.
+also depend on whether these findings can be replicated. For instance, for a
+drug to be approved to the market, the United States food and drug
+administration requires ``\textit{at least two adequate and well-controlled
+  studies, each convincing on its own, to establish effectiveness}'' \citep[p.
+3]{FDA1998}. The results from replication studies may hence have real-world
+consequences. It is therefore important that the methodological aspects of
+replication studies, such as their statistical design and analysis, are well
+understood.
 
 Despite their importance, the traditional academic system has made it
-unattractive for researchers to conduct replication studies; publications,
+unattractive for researchers to conduct replication studies as publications,
 citations, and grant money are typically easier to acquire by conducting novel
 research. This is because until recently, most scientific journals hardly
-published any replication studies as the emphasis was on ``innovation'' rather
-than on ``repetition'' \citep{Makel2012, Martin2017, Coiera2021}. As a result,
-researchers often had no other choice than to focus their efforts on producing
-novel and eye-catching research results in order to build successful careers
-\citep{Binswanger2014, Moher2018}.
+published any replication studies since the emphasis was on ``innovation''
+rather than on ``repetition'' \citep{Makel2012, Martin2017, Coiera2021}. As a
+result, researchers often had no other choice than to focus their efforts on
+producing novel and eye-catching research results in order to build successful
+careers \citep{Binswanger2014, Moher2018}.
 
@@
 
-In the midst of this crisis, % , particularly from the hard-hit
-% field of psychology,
-various reforms were implemented to prevent an escalation of the situation % and
-% save the reputation of science
-\citep[for an overview see \eg{}][]{Munafo2017}. For instance, some journals
-adopted the ``registered report'' format \citep{Chambers2021} in which a study
-proposal is peer reviewed \emph{before} the study is conducted, and which, if
-accepted, gives provisional publication acceptance regardless of the study
-outcome. Similarly, digital infrastructure platforms, such as Zenodo
-(\url{https://zenodo.org}) or the Open Science Framework (\url{https://osf.io}),
-were created to facilitate preregistration, preprints, code and data sharing,
-all of which have substantially increased over the last decade
-\citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of conducting
-replication studies has also gained popularity. Several academic journals and
-funders are now explicitly promoting replication research \citep{NWO2016,
-  NSL2018, Nature2022}. Figure~\ref{fig:scholar} (left) illustrates this trend
-by the yearly number of results for the search term ``replication study''
-obtained from the search engine Web of Science. The numbers have been rapidly
-growing, especially since the mid-2000s. This trend could possibly be explained
-by the fact that more research results are published each year but also when the
-numbers are normalized by the number of results for the search term ``study'',
-the increasing trend is still visible.
+In the midst of this crisis, various reforms were implemented to prevent an
+escalation of the situation \citep[for an overview see \eg{}][]{Munafo2017}. For
+instance, some journals adopted the ``registered report'' format
+\citep{Chambers2021} in which a study proposal is peer reviewed \emph{before}
+the study is conducted, and which, if accepted, gives provisional publication
+acceptance regardless of the study outcome. Similarly, digital infrastructure
+platforms, such as Zenodo (\url{https://zenodo.org}) or the Open Science
+Framework (\url{https://osf.io}), were created to facilitate pre-registration,
+preprints, code and data sharing, all of which have substantially increased over
+the last decade \citep{Kidwell2016, Nosek2018, Rawlinson2019}. The practice of
+conducting replication studies has also gained popularity. Several academic
+journals and funders are now explicitly promoting replication research
+\citep{NWO2016, NSL2018, Nature2022}. Figure~\ref{fig:scholar} (left)
+illustrates this trend by the yearly number of results for the search term
+``replication study'' obtained from the search engine Web of Science. The
+numbers have been rapidly growing, especially since the mid-2000s. This trend
+could possibly be explained by the fact that more research results are published
+each year but also when the numbers are normalized by the number of results for
+the search term ``study'', the increasing trend is still visible.
 
@@
 Most methods for analyzing replication studies can be formulated in terms of
-study-level summary statistics as shown in Table~\ref{tab:meta}. % Effect
-% estimates, standard error, confidence intervals, and $p$-values
-All of these are routinely reported in research articles, and if one of them is
-missing they can typically be calculated from the others. Using summary
-statistics is also often the only possible way for conducting the replication
-success analysis as the raw data from the original study may not be available to
-the researchers conducting the replication study. The most important statistics
-are the effect estimates $\that_{o}$ and $\that_{r}$. They provide an estimate
-of the underlying effect size $\theta$ which quantifies the true effect or
-association of an intervention/exposure with an outcome variable. Typical effect
-sizes are mean differences and correlations (for continuous outcomes), odds
-ratios (for binary outcomes), or hazard ratios (for time-to-event outcomes).
-Depending on the type of effect size, a transformation might be required so that
-the assumption of approximately normally distributed effect estimates around the
+study-level summary statistics as shown in Table~\ref{tab:meta}. All of these
+are routinely reported in research articles, and if one of them is missing they
+can typically be calculated from the others. Using summary statistics is also
+often the only possible way for conducting the replication success analysis as
+the raw data from the original study may not be available to the researchers
+conducting the replication study. The most important statistics are the effect
+estimates $\that_{o}$ and $\that_{r}$. They provide an estimate of the
+underlying effect size $\theta$ which quantifies the true effect or association
+of an intervention/exposure with an outcome variable. Typical effect sizes are
+mean differences and correlations (for continuous outcomes), odds ratios (for
+binary outcomes), or hazard ratios (for time-to-event outcomes). Depending on
+the type of effect size, a transformation might be required so that the
+assumption of approximately normally distributed effect estimates around the
 unknown effect size $\theta$ (for large enough sample sizes) is justified. This
@@
     \midrule
-    Significance & The original and replication $p$-values are smaller than
+    Significance & \sloppy The original and replication $p$-values are smaller than
                    a threshold $\alpha$ and their effect estimates show
@@
                    & \\
-    Confidence interval & The replication effect estimate is contained in the
-                          $(1 - \alpha)$ original confidence interval
+    Confidence interval & \sloppy The replication effect estimate is contained in the
+                          \mbox{$(1 - \alpha)\times100\%$} original confidence interval
                           ($\that_{r} \in [\that_{o} - z_{\alpha/2}\sigma_{o},
@@
                           Sometimes, also defined as the original effect estimate is
-                          contained in the $(1 - \alpha)$ replication confidence interval
-                          ($\that_{o} \in [\that_{r} - z_{\alpha/2}\sigma_{r},
-                          \that_{r} + z_{\alpha/2}\sigma_{r}]$).
+                          contained in the \mbox{$(1 - \alpha)\times100\%$} replication
+                          confidence interval
+                          (\mbox{$\that_{o} \in [\that_{r} - z_{\alpha/2}\sigma_{r},
+                          \that_{r} + z_{\alpha/2}\sigma_{r}]$}).
                           Usually $\alpha = 5\%$. \\
@@
     Prediction interval ($Q$-test) & The replication effect estimate is contained in its
-                                     $(1 - \alpha)$ prediction interval
-                                     ($\that_{r} \in [\that_{o} - z_{\alpha/2}\surd(\sigma_{o}^{2}
+                                     $(1 - \alpha)\times100\%$ prediction interval
+                                     \mbox{($\that_{r} \in [\that_{o} - z_{\alpha/2}\surd(\sigma_{o}^{2}
                                      + \sigma_{r}^{2}), \that_{o} + z_{\alpha/2}\surd(\sigma_{o}^{2}
-                                     + \sigma_{r}^{2})]$). Usually $\alpha = 5\%$.
+                                     + \sigma_{r}^{2})]$)}. Usually $\alpha = 5\%$.
                                      This criterion is equivalent to $p_{Q} \geq \alpha$ where
@@
 success'' based on the prediction interval may be logically questionable due to
-its connection to the meta-analytic $Q$-test.
-% as it may also be seen as an instance of the ``absence of evidence fallacy''
-% \citep{Altman1995};
-That is, if the $p$-value from the $Q$-test is larger than $\alpha$ this is
-equivalent to the replication effect estimate $\that_{r}$ being contained in its
-$(1- \alpha)$ prediction interval. The null hypothesis of this test is defined
-that the underlying effect sizes of original and replication study are the same
+its connection to the meta-analytic \mbox{$Q$-test}. That is, if the $p$-value
+from the $Q$-test is larger than $\alpha$ this is equivalent to the replication
+effect estimate $\that_{r}$ being contained in its $(1- \alpha)\times 100\%$
+prediction interval. The null hypothesis of this test is defined that the
+underlying effect sizes of original and replication study are the same
 ($H_{0} \colon \theta_{o} = \theta_{r}$), so a rejection of this null hypothesis
@@
 \begin{figure}[!htb]
-<< "RPCB-graph", fig.height = 3.5 >>=
+<< "RPCB-graph", fig.height = 3.75 >>=
 za <- qnorm(p = 0.975)
@@
 rpcbWithoutNA <- na.omit(rpcb)
+cols <- c("#1A1A1A80", "#1B9E77")
+names(cols) <- levels(rpcbWithoutNA$rsig)
 plotA <- ggplot(data = rpcbWithoutNA, aes(x = smdo, y = smdr)) +
@@
     geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
-    geom_point(aes(fill = rsig), shape = 21, alpha = 0.8) +
+    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9) +
     geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
@@
     coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
-    scale_fill_discrete(labels = scales::parse_format()) +
+    scale_fill_manual(values = cols, labels = scales::parse_format()) +
+    scale_color_manual(values = cols) +
     theme_bw() +
@@
     geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
-    geom_point(aes(fill = rsig), shape = 21, alpha = 0.8,
+    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9,
                show.legend = FALSE) +
@@
     coord_fixed(xlim = zoom, ylim = zoom) +
+    scale_fill_manual(values = cols, labels = scales::parse_format()) +
+    scale_color_manual(values = cols) +
     theme_bw() +
@@
 \begin{figure}[!htb]
-<< "RPCB-table1", results = "asis", fig.height = 6 >>=
+<< "RPCB-table1", results = "asis", fig.height = 6.5 >>=
 ## show number of successes
@@
     \textit{p}-value $p_{Q}$, and one-sided sceptical \textit{p}-value
-    $p_{\mathrm{S}}$. A replication success (green) threshold of $\alpha = 5\%$
+    $p_{\mathrm{S}}$. A replication success (green-bold) threshold of $\alpha = 5\%$
     is used for two-sided \textit{p}-values, $\alpha = 2.5\%$ for one-sided
@@
 ## function to format p-value
-pFormat. <- function(p, digits = 2, dollar = FALSE, phantom = FALSE) {
+pFormat. <- function(p, digits = 2, dollar = FALSE, phantom = FALSE, font = "mathrm") {
     if (is.na(p)) {
@@
         if (dollar) {
-            out <- paste0("$", out, "$")
+            out <- paste0("$\\", font, "{", out, "}$")
         }
@@
 ## function to format (relative) effect estimate
-dFormat. <- function(x, digits = 2, phantom = FALSE, dollar = FALSE) {
+dFormat. <- function(x, digits = 2, phantom = FALSE, dollar = FALSE, font = "mathrm") {
     if (is.na(x)) {
@@
         }
-        if (dollar) out <- paste0("$", out, "$")
+        if (dollar) {
+            out <- paste0("$\\", font, "{", out, "}$")
+            }
     }
@@
 tableFormat. <- function(x, outFun = pFormat, threshold = 0.05, col1 = "dark2green",
-                         col2 = "dark2orange") {
+                         col2 = "dark2orange", font1 = "mathbf", font2 = "mathrm") {
     if (is.na(x)) {
@@
     } else {
-        if (x < threshold) col <- col1
-        else col <- col2
+        if (x < threshold) {
+            col <- col1
+            font <- font1
+        } else {
+            col <- col2
+            font <- font2
+        }
         out <- paste0("\\textcolor{", col, "}{",
-                      outFun(x, dollar = TRUE, phantom = TRUE), "}")
+                      outFun(x, dollar = TRUE, phantom = TRUE, font = font),
+                      "}")
     }
@@
            dFormat = tableFormat(x = d, outFun = dFormat,
-                                 threshold = 1, col1 = "dark2orange",
-                                 col2 = "dark2green"),
+                                 threshold = 1, col1 = "dark2orange", font1 = "mathrm",
+                                  col2 = "dark2green", font2 = "mathbf"),
            cioL = smdo - za*so,
@@
            ps1Format = tableFormat(x = ps1, threshold = 0.025),
-           pQFormat = tableFormat(x = pQ, col1 = "dark2orange",
-                                  col2 = "dark2green"),
+           pQFormat = tableFormat(x = pQ, col1 = "dark2orange", font1 = "mathrm",
+                                  col2 = "dark2green", font2 = "mathbf"),
            cioFormat = ciFormat(lower = cioL, upper = cioU, dollar = TRUE),
@@
 \emph{reverse-Bayes inference} and \emph{Bayesian model criticism} in a method
-for assessing replication success. In the following, I will summarize the
-methods and its technical underpinnings.
+for assessing replication success. In the following, I will summarize the method
+and its technical underpinnings.
 
@@
 \end{align*}
-The associated $(1- \alpha)$ highest posterior density credible interval has
-limits
+The associated $(1- \alpha)\times 100\%$ highest posterior density credible
+interval has limits
 \begin{align}
@@
   prior variance} $\tau^{2}_{\alpha}$ so that the appropriate limit of the
-$(1 - \alpha)$ credible interval is just fixed to zero. The resulting prior then
+$(1 - \alpha)\times 100\%$ credible interval is just fixed to zero. The resulting prior then
 represents the beliefs of a sceptic who is just stubborn enough to not find the
@@
 Bayesian model criticism. First, the predictive density of the observed data (or
-the value of a ``checking function'' applied to the observed data) can be
-compared to its reference distribution via a \emph{prior predictive $p$-value}
+the predictive density of a ``checking function'' applied to the observed data)
+can be compared to its reference distribution via a \emph{prior predictive
+  $p$-value}
 \begin{align}
@@
 
-The sceptical $p$-value has several interesting
-properties \citep[Section 3]{Held2020}: First, it is always larger than the
-maximum of the original and replication $p$-values
-($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that both $p$-values have to be
-smaller than $\alpha$ such that replication success at level $\alpha$ is
-possible. The sceptical $p$-value hence requires \emph{both} studies to be
-sufficiently convincing on their own (in terms of their $p$-values), similar to
-the significance criterion for replication success. Second, if the $p$-values
-$p_{o}$ and $p_{r}$ remain fixed but the relative effect estimate
-$d = \that_{r}/\that_{o}$ decreases towards zero, the sceptical $p$-value
-increases, meaning that shrinkage of the replication effect estimate is
-penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed $p_{o}$ and
-$p_{r}$). The sceptical $p$-value thus takes effect shrinkage into account,
-unlike the significance criterion which can be achieved with any non-zero
-replication effect estimate $\that_{r}$ provided the standard error $\sigma_{r}$
-is small enough. This property is desirable in the replication setting as a
-smaller replication effect estimate $\that_{r}$ may not be practically relevant
-anymore, despite its statistical significance.
+The sceptical $p$-value has several interesting properties \citep[Section
+3]{Held2020}: First, it is always larger than the maximum of the original and
+replication $p$-values ($p_{\text{S}} > \max\{p_{o}, p_{r}\}$), meaning that
+both $p$-values have to be smaller than $\alpha$ such that replication success
+at level $\alpha$ is possible. The sceptical $p$-value hence requires
+\emph{both} studies to be sufficiently convincing on their own (in terms of
+their $p$-values), similar to the significance criterion for replication
+success. Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the
+relative effect estimate \mbox{$d = \that_{r}/\that_{o}$} decreases towards
+zero, the sceptical $p$-value increases, meaning that shrinkage of the
+replication effect estimate is penalized ($p_{\text{S}} \uparrow 1$ as
+$d \downarrow 0$ for fixed $p_{o}$ and $p_{r}$). The sceptical $p$-value thus
+takes effect shrinkage into account, unlike the significance criterion which can
+be achieved with any non-zero replication effect estimate $\that_{r}$ provided
+the standard error $\sigma_{r}$ is small enough. This property is desirable in
+the replication setting as a smaller replication effect estimate $\that_{r}$ may
+not be practically relevant anymore, despite its statistical significance.
 
@@
 sceptical $p$-value, this leads to a much more stringent criterion for
-replication studies than the significance criterion. Many studies which
+replication success than the significance criterion. Many studies which
 intuitively seem successful will not satisfy it, and frequentist properties such

### 2022-12-19 preface.tex
last polish of intro?

@@
 alphabetical order): Ainesh, Alexandra, Annina, Charlotte, Babette, Bálint,
-Beate, Beni,Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
+Beate, Beni, Eveline, Eva, Franscesca, Felix, Julia, Klaus, Kelly, Lucas, Lisa,
 Luisa, Goscha, Manuela, Monika, Muriel, Manja, Maria, Marielena, Nadja, Ruedi,
@@
 thanks goes to Ada. Finally, I thank my family: Beni, Christa, Elisabeth,
-Fabian, Harry, Markus, Maja, and Noemi for their support.
+Fabian, Harry, Laurin, Markus, Maja, and Noemi for their support.
 

### 2022-12-19 abstract.tex
last polish of intro?
paper 1 polish

@@
 from the replication study is larger than the effect estimate from the original
-study. We find that the recalibrated sceptical $p$-value has good frequentist
-properties comparable to the standard method used in practice.
+study. We find that the recalibrated sceptical $p$-value also has good
+frequentist properties comparable to the standard method used in practice.
 % extension 2
@@
 some situations the sceptical $p$-value may indicate replication success even
-though the effect estimate from the replication is much smaller than the effect
-estimate from the original study. % , which cannot happen with the sceptical
+though the effect estimate from the replication is arbitrarily smaller than the
+effect estimate from the original study. % , which cannot happen with the sceptical
 % Bayes factor.

### 2022-12-19 intro.Rnw
paper 1 polish

@@
 discussion about the need for better research standards in psychology and the
-social sciences. These discussions eventually culminated in large-scale
-replication projects conducted by huge researcher consortia in fields such as
-psychology \citep{Opensc2015, Klein2014, Klein2018, Protzko2020}, economics
+social sciences. These discussions eventually led to large-scale replication
+projects conducted by huge researcher consortia in fields such as psychology
+\citep{Opensc2015, Klein2014, Klein2018, Protzko2020}, economics
 \citep{Camerer2016}, the social sciences \citep{Camerer2018}, experimental

### 2022-12-19 paper2.tex
polish paper 2

@@
 \end{align}
-with $\lw{-1}(\cdot)$ the branch of the Lambert $W$ function \citep{Corless1996}
-that satisfies \mbox{$W(y) \leq -1$} for $y \in [-e^{-1}, 0)$, see Appendix
-\ref{appendix:lambertW} for details about the Lambert $W$ function. The
+with $\lw{-1}(\cdot)$ the branch of the Lambert W function \citep{Corless1996}
+that satisfies \mbox{$\mathrm{W}(y) \leq -1$} for $y \in [-e^{-1}, 0)$, see
+Appendix \ref{appendix:lambertW} for details about the Lambert W function. The
 sufficiently sceptical prior is then given by
@@
 solution $\gy^\prime > \gminBFo $ could also be computed by replacing the
-$\lw{-1}$ branch of the Lambert $W$ function in \eqref{ggamma} with the $\lw{0}$
+$\lw{-1}$ branch of the Lambert W function in \eqref{ggamma} with the $\lw{0}$
 branch, but this will not be of interest to us.
@@
   recalibrated sceptical $p$-value
-  ($\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$) as a function of the
-  relative variance $c = \sigma^{2}_{o}/\sigma^{2}_{r}$ for different levels of
-  replication success $\gamma$.}
+  (\mbox{$\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$}) as a function of
+  the relative variance $c = \sigma^{2}_{o}/\sigma^{2}_{r}$ for different levels
+  of replication success $\gamma$.}
 \label{fig2:t1ec}
@@
 \end{knitrout}
-\caption{Power of the two-trials rule (2TR: $\minBF_{o} \leq
-1/3$ and $\minBF_{r} \leq
-1/3$), the replication Bayes factor ($\BFr
-\leq 1/3$), the sceptical Bayes factor ($\BFs
-\leq
-1/3$), and the recalibrated sceptical $p$-value ($\tilde{p}_{\mathrm{S}}
-\leq 1 - \Phi\{z_{\gamma}\}$ with $\gamma =
-1/3$) as a function of the relative variance $c
-= \sigma^2_o/\sigma^2_r$ for different original $z$-values $z_o =
-\that_o/\sigma_o$ (respectively corresponding minimum Bayes factor $\minBF_o$).}
+\caption{Power of the two-trials rule (2TR: $\minBF_{o} \leq 1/3$ and
+  $\minBF_{r} \leq 1/3$), the replication Bayes factor ($\BFr \leq 1/3$), the
+  sceptical Bayes factor ($\BFs \leq 1/3$), and the recalibrated sceptical
+  $p$-value (\mbox{$\tilde{p}_{\mathrm{S}} \leq 1 - \Phi\{z_{\gamma}\}$} with
+  $\gamma = 1/3$) as a function of the relative variance
+  $c = \sigma^2_o/\sigma^2_r$ for different original $z$-values
+  $z_o = \that_o/\sigma_o$ (respectively corresponding minimum Bayes factor
+  $\minBF_o$).}
 \label{fig2:condpower}
@@
 \mbox{$\lw{-1}(x) \approx \log(-x) - \log(-\log(-x))$} as the argument of the
-Lambert function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
+Lambert W function is close to zero due to $\abs{z_{o}} \to \infty$ \citep[p.
 350]{Corless1996}. Taken together, we have
@@
 \url{https://gitlab.uzh.ch/samuel.pawel/BFScode}. We used the implementation of
-the Lambert $W$ function from the package \texttt{lamW} \citep{Adler2015},
+the Lambert W function from the package \texttt{lamW} \citep{Adler2015},
 graphics were created with the \texttt{ggplot2} package \citep{Wickham2016}, the
@@
 \end{align}
-where $\lw{-1}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
-$W(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$}, ensuring that
+where $\lw{-1}(\cdot)$ is the branch of the Lambert W function that satisfies
+$\mathrm{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$}, ensuring that
 $\gy \leq \gminBFo$. See Appendix~\ref{appendix:lambertW} for details about the
-Lambert $W$ function. For some $z_o$, equation \eqref{sspv2} can also be
-satisfied for negative $\gy$, which is why we need to add the condition
-$-z_o^2/q \geq 1$ in equation \eqref{eq2:solutionvss}, such that $\gy$ is a
-valid relative variance.
-
-As $z_{o}^{2}$ becomes larger, the argument to the Lambert function
+Lambert W function. For some $z_o$, equation \eqref{sspv2} can also be satisfied
+for negative $\gy$, which is why we need to add the condition $-z_o^2/q \geq 1$
+in equation \eqref{eq2:solutionvss}, such that $\gy$ is a valid relative
+variance.
+
+As $z_{o}^{2}$ becomes larger, the argument to the Lambert W function
 $x = -z_{o}^{2}\exp(-z_{o}^{2})/\gamma^{2}$ will approach zero, so the
@@
 
-\section{The Lambert \textit{W} function}
+\section{The Lambert W function}
 \label{appendix:lambertW}
-The Lambert $W$ function \citep{Corless1996} is defined as the function
-$W(\cdot)$ satisfying
-$$W(y) \cdot \exp\{W(y)\} = y$$
+The Lambert W function \citep{Corless1996} is defined as the function
+$\mathrm{W}(\cdot)$ satisfying
+$$\mathrm{W}(y) \cdot \exp\{\mathrm{W}(y)\} = y$$
 and it is also known as ``product logarithm`` since it returns the number which
 plugged in the exponential function and then multiplied by itself produces $y$.
-For real $y$, $W(y)$ is only defined for $y \geq - e^{-1}$ and for
+For real $y$, $\mathrm{W}(y)$ is only defined for $y \geq - e^{-1}$ and for
 $y \in [-e^{-1}, 0)$ the function has two branches that are commonly denoted by
-$\lw{0}(\cdot)$, the branch with $W(y) \geq -1$, and $\lw{-1}(\cdot)$, the
-branch with $W(y) \leq -1$ (see Figure \ref{fig2:lambertW} for an illustration).
+$\lw{0}(\cdot)$, the branch with $\mathrm{W}(y) \geq -1$, and $\lw{-1}(\cdot)$, the
+branch with $\mathrm{W}(y) \leq -1$ (see Figure \ref{fig2:lambertW} for an illustration).
 \begin{figure}[!htb]
@@
 \end{knitrout}
-\caption{Lambert $W$ function for real argument $y$.}
+\caption{Lambert W function for real argument $y$.}
 \label{fig2:lambertW}
@@
 Multiplying~\eqref{eq2:bfsroot2} by $-z_{o}^{2}(1 + d^{2})/2$ and applying the
-Lambert $W$ function leads to
+Lambert W function leads to
 \begin{align}
@@
 valid relative variance, as the equation may otherwise be satisfied for negative
-$g_*$. Since the argument to $W(\cdot)$ is real and negative (if $z_{o}\neq 0$),
-the branches $\lw{-1}(\cdot)$ and $\lw{0}(\cdot)$ both provide solutions that
-can fulfil the equation (assuming the argument is not smaller than $-e^{-1}$
-which would mean that there are no intersections). It must also hold that
-$g_{*} \leq g_{\minBF_{o}} = \max\{z_{o}^{2} - 1, 0\}$ for $g_{*}$ to be a valid
-sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the $g_{*}$
-from~\eqref{eq2:gintersect} can only be computed with the $\lw{-1}(\cdot)$
-branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$ the solution
-$g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the relative prior
-variance $g_{*}$ from~\eqref{eq2:gintersect} into the Bayes factor
-from~\eqref{eq2:BFo}, we obtain the expression for the sceptical Bayes factor
-in~\eqref{eq2:BFsc1}.
+$g_*$. Since the argument to $\mathrm{W}(\cdot)$ is real and negative (if
+$z_{o}\neq 0$), the branches $\lw{-1}(\cdot)$ and $\lw{0}(\cdot)$ both provide
+solutions that can fulfil the equation (assuming the argument is not smaller
+than $-e^{-1}$ which would mean that there are no intersections). It must also
+hold that $g_{*} \leq g_{\minBF_{o}} = \max\{z_{o}^{2} - 1, 0\}$ for $g_{*}$ to
+be a valid sufficiently sceptical prior variance. Hence, when $|d| \leq 1$, the
+$g_{*}$ from~\eqref{eq2:gintersect} can only be computed with the
+$\lw{-1}(\cdot)$ branch, whereas for $|d| > 1$ and when $-k \geq (1 + d^{2})/2$
+the solution $g_{*}$ is computed from the $\lw{0}(\cdot)$ branch. Plugging the
+relative prior variance $g_{*}$ from~\eqref{eq2:gintersect} into the Bayes
+factor from~\eqref{eq2:BFo}, we obtain the expression for the sceptical Bayes
+factor in~\eqref{eq2:BFsc1}.
 

### 2022-12-19 paper2.tex
paper 3 polish

@@
 framework usually provides a good approximation for a wide range of (suitably
-transformed) effect size types \citep[Chapter 2.4]{Spiegelhalter2004}. For
+transformed) effect size types \citep[chapter 2.4]{Spiegelhalter2004}. For
 example, means and mean differences (no transformation), odds ratios, hazard
@@
 (``Fisher-$z$'' transformation). We refer to the literature of meta-analysis for
-details about transformations of effect sizes \citep[\eg{}][Chapter
+details about transformations of effect sizes \citep[\eg{}][chapter
 11.6]{Cooper2019}. The normal model in combination with conjugate priors enables
@@
 of the data underlying the effect estimates, and then marginalise over possible
-nuisance parameters \citep[Chapter 8.2.2]{Spiegelhalter2004}. This leads to
+nuisance parameters \citep[chapter 8.2.2]{Spiegelhalter2004}. This leads to
 marginal likelihoods which are again only conditional on the effect size
@@
 %% \Nor(t; \theta \sqrt{n^*\tau^2}, \tau^2) \text{IG}(\tau^2; \nu/2, \nu/2) d\tau^2$
-\citep[Chapter 31]{Johnson1995}, the density of the SMD under the advocacy prior
+\citep[chapter 31]{Johnson1995}, the density of the SMD under the advocacy prior
 is given by

### 2022-12-19 intro.Rnw
figure to black white

@@
 rpcbWithoutNA <- na.omit(rpcb)
-cols <- c("#1A1A1A80", "#1B9E77")
+cols <- adjustcolor(col = c("grey70", "grey5"), alpha.f = 0.8)
 names(cols) <- levels(rpcbWithoutNA$rsig)
@@
     geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
-    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9) +
+    geom_point(aes(fill = rsig), shape = 21) +
     geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +
@@
     geom_vline(xintercept = 0, lty = 2, alpha = 0.9, size = 0.4) +
-    geom_point(aes(fill = rsig), shape = 21, alpha = 0.9,
-               show.legend = FALSE) +
+    geom_point(aes(fill = rsig), shape = 21, show.legend = FALSE) +
     geom_rug(aes(color = rsig), size = 0.3, show.legend = FALSE) +

### 2022-12-19 source/paper1.tex
reorganizatin for reproducibility

--- 2022-12-14 paper1.tex
@@
 \textbf{Key words}: Power, replication studies, sceptical $p$-value, shrinkage,
-two-trials rule, type I error rate
+two-trials rule, Type I error rate
 
@@
 errors of the original and replication effect estimates. The squared standard
-errors are usually inversely proportional to the sample size of each study, \ie{}
-$\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
+errors are usually inversely proportional to the sample size of each study,
+\ie{} $\sigma_o^2 = \kappa^2/n_o$ and $\sigma_r^2 = \kappa^2/n_r$ for some unit
 variance $\kappa^2$. The variance ratio $c$ can then be identified as the
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
 {\centering \includegraphics[width=\maxwidth]{images/paper1/fig1-1}
-
 }
-
 \end{knitrout}
@@
   from \citet{Pyc2010} has effect estimate $\hat \theta_o= 0.4$ on Fisher's $z$
-  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value $p_o = 0.011$.
-  The left part of the figure illustrates the reverse-Bayes derivation of the
-  sufficiently sceptical prior based on the original study result and the
-  posterior with lower credible limit fixed at zero. The comparison of the
-  sufficiently sceptical prior with the replication study result
-  ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26, $p_r = 0.004$) in the
-  right part of the figure is used to assess potential prior-data conflict.}
+  scale (95\% CI from $0.05$ to $0.74$) and one-sided $p$-value
+  \mbox{$p_o = 0.011$}. The left part of the figure illustrates the
+  reverse-Bayes derivation of the sufficiently sceptical prior based on the
+  original study result and the posterior with lower credible limit fixed at
+  zero. The comparison of the sufficiently sceptical prior with the replication
+  study result ($\hat \theta_r = 0.15$, 95\% CI from 0.04 to 0.26,
+  $p_r = 0.004$) in the right part of the figure is used to assess potential
+  prior-data conflict.}
   \label{fig1:fig1}
@@
 ensure that replication success can only occur if the original and replication
-effect estimates go in the same direction. Figure \ref{fig1:fig1} illustrates the
-\citet{Held2020} approach based on a replication study from the \textit{Social
-  Sciences Replication Project} \citep{Camerer2018}: the significant original
-finding by \citet{Pyc2010} at one-sided level $\alpha=0.025$ is challenged with
-a sceptical prior, sufficiently concentrated around zero to make the original
-study result no longer convincing \citep{Matthews2001a,Matthews2001b}.
-Replication success is then defined as conflict between the sceptical prior and
-the result from the replication study in order to disprove the sceptic. Conflict
-is quantified by a prior-predictive tail probability $p_{\mbox{\scriptsize
-    Box}}$ \citep{Box1980} where a small value $p_{\mbox{\scriptsize
-    Box}} \leq \alpha$ defines replication success. In Figure \ref{fig1:fig1} the
-original finding is only borderline significant, so the sufficiently sceptical
-prior is fairly wide. Furthermore, there is substantial shrinkage
-($d = 0.15/0.4 = 0.38$) of the replication effect estimate and therefore hardly
-any conflict with the sufficiently sceptical prior (one-sided
-$p_{\mbox{\scriptsize Box}}=0.31$). We are thus not able to declare replication
-success at level $2.5$\%.
+effect estimates go in the same direction. Figure \ref{fig1:fig1} illustrates
+the \citet{Held2020} approach based on a replication study from the
+\textit{Social Sciences Replication Project} \citep{Camerer2018}: the
+significant original finding by \citet{Pyc2010} at one-sided level
+$\alpha=0.025$ is challenged with a sceptical prior, sufficiently concentrated
+around zero to make the original study result no longer convincing
+\citep{Matthews2001a,Matthews2001b}. Replication success is then defined as
+conflict between the sceptical prior and the result from the replication study
+in order to disprove the sceptic. Conflict is quantified by a prior-predictive
+tail probability $p_{\mbox{\scriptsize Box}}$ \citep{Box1980} where a small
+value $p_{\mbox{\scriptsize Box}} \leq \alpha$ defines replication success. In
+Figure \ref{fig1:fig1} the original finding is only borderline significant, so
+the sufficiently sceptical prior is fairly wide. Furthermore, there is
+substantial shrinkage ($d = 0.15/0.4 = 0.38$) of the replication effect estimate
+and therefore hardly any conflict with the sufficiently sceptical prior
+(one-sided $p_{\mbox{\scriptsize Box}}=0.31$). We are thus not able to declare
+replication success at level $2.5$\%.
 
@@
 \begin{equation}\label{eq1:extrinsic.p}
-\left({z_o^2}/{z_{{\alpha_S}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_S}}^2}
+\left({z_o^2}/{z_{{\alpha_{\mathrm{S}}}}^2}-1 \right) \left({z_r^2}/{z_{{\alpha_{\mathrm{S}}}}^2}
 - 1 \right) \geq c
 \end{equation}
-hold, replication success at level ${\alpha_S}$ is achieved, where
-$z_{{\alpha_S}} = \Phi^{-1}(1-{\alpha_S})$. The requirement
-\eqref{eq1:extrinsic.p} can be assessed for any value of
-${{\alpha_S}} > \max\{p_o, p_r\}$ and of particular interest is the smallest
-possible value of $\alpha_S$ where \eqref{eq1:extrinsic.p} holds, the so-called
-\textit{sceptical $p$-value} $p_S$. We are thus interested in the value $z_S^2$
-that fulfills
+hold, replication success at level ${\alpha_{\mathrm{S}}}$ is achieved, where
+$z_{{\alpha_{\mathrm{S}}}} = \Phi^{-1}(1-{\alpha_{\mathrm{S}}})$. The
+requirement \eqref{eq1:extrinsic.p} can be assessed for any value of
+${{\alpha_{\mathrm{S}}}} > \max\{p_o, p_r\}$ and of particular interest is the
+smallest possible value of $\alpha_{\mathrm{S}}$ where \eqref{eq1:extrinsic.p}
+holds, the so-called \textit{sceptical $p$-value} $\ps$. We are thus interested
+in the value $z_{\mathrm{S}}^2$ that fulfills
 \begin{equation}\label{eq1:extrinsic.p2}
-\left({z_o^2}/{z_{S}^2}-1 \right) \left({z_r^2}/{z_{S}^2}
+\left({z_o^2}/{z_{\mathrm{S}}^2}-1 \right) \left({z_r^2}/{z_{\mathrm{S}}^2}
 - 1 \right) = c.
@@
 There is a unique solution of \eqref{eq1:extrinsic.p2} which defines the
-one-sided {sceptical $p$-value} $p_S= 1-\Phi\left({z_S}\right)$ where
-$z_{S} \coloneqq + \surd z_{S}^2$, provided $\sign(z_o)=\sign(z_r)$ holds.
-Replication success at level $\alpha_S$ is then achieved if $p_S \leq \alpha_S$.
-In the introductory example based on the original study by \citet{Pyc2010}, the
-sceptical $p$-value turns out to be $p_S=0.11$.
+one-sided {sceptical $p$-value} $\ps= 1-\Phi\left({z_{\mathrm{S}}}\right)$ where
+$z_{\mathrm{S}} \coloneqq + \surd z_{\mathrm{S}}^2$, provided
+$\sign(z_o)=\sign(z_r)$ holds. Replication success at level
+$\alpha_{\mathrm{S}}$ is then achieved if $\ps \leq \alpha_{\mathrm{S}}$. In the
+introductory example based on the original study by \citet{Pyc2010}, the
+sceptical $p$-value turns out to be $\ps=0.11$.
 
@@
 \citet[Section 3.1]{Held2020} for details. In particular,
-$p_S > \max\{p_o, p_r\}$ always holds with $p_S \downarrow \max\{p_o, p_r\}$ for
+$\ps > \max\{p_o, p_r\}$ always holds with $\ps \downarrow \max\{p_o, p_r\}$ for
 $c \downarrow 0$. Furthermore, if the $p$-values $p_o$ and $p_r$ are fixed, the
-sceptical $p$-value $p_S$ increases with decreasing relative effect size $d$.
+sceptical $p$-value $\ps$ increases with decreasing relative effect size $d$.
 The first property ensures that both the original and the replication study have
@@
 
-The level for replication success $\alpha_S$ has to be distinguished from the
-significance level $\alpha$ associated with the ordinary $p$-value.
+The level for replication success $\alpha_{\mathrm{S}}$ has to be distinguished
+from the significance level $\alpha$ associated with the ordinary $p$-value.
 \citet{Held2020} has used the \textit{nominal level} for replication success
-($\alpha_S=\alpha$) for convenience, but in the following we will propose a
-recalibration of the procedure along with a new value for $\alpha_S$, the
-\textit{golden level} (Section~\ref{sec1:goldenthresh}). The derivation is based
-on a property of the required relative effect size for replication success, if
-the relative sample size is very large (Section~\ref{sec1:res}). In a nutshell,
-the golden level ensures that for original studies which were only borderline
-significant ($p_o=\alpha$), replication success is only possible if the
-replication
+($\alpha_{\mathrm{S}}=\alpha$) for convenience, but in the following we will
+propose a recalibration of the procedure along with a new value for
+$\alpha_{\mathrm{S}}$, the \textit{golden level}
+(Section~\ref{sec1:goldenthresh}). The derivation is based on a property of the
+required relative effect size for replication success, if the relative sample
+size is very large (Section~\ref{sec1:res}). In a nutshell, the golden level
+ensures that for original studies which were only borderline significant
+($p_o=\alpha$), replication success is only possible if the replication
 effect estimate is larger than the original one ($d > 1$).\\
@@
 Without loss of generality we now assume that $\hat \theta_o > 0$ and that
-$p_o < {\alpha_S}$ has been observed in the original study, otherwise it would
-be impossible to achieve replication success at level $\alpha_S$ because $p_S$
-is always larger than $p_o$. The condition \eqref{eq1:extrinsic.p} for
-replication success can then be re-written as
+$p_o < {\alpha_{\mathrm{S}}}$ has been observed in the original study, otherwise
+it would be impossible to achieve replication success at level
+$\alpha_{\mathrm{S}}$ because $\ps$ is always larger than $p_o$. The condition
+\eqref{eq1:extrinsic.p} for replication success can then be re-written as
 \begin{equation}\label{eq1:eq.z}
-  z_r \geq   z_{{\alpha_S}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
+  z_r \geq   z_{{\alpha_{\mathrm{S}}}} \sqrt{1+c/(K-1)} \eqqcolon  \zrmin,
 \end{equation}
-where $K=z_o^2/z_{{\alpha_S}}^2>1$. The right hand-side of \eqref{eq1:eq.z} is
-the minimum replication $z$-value $\zrmin$ required to achieve replication
-success. Note that $\zrmin$ increases with increasing $c$, so increasing the
-replication sample size leads to a more stringent success requirement $z_r$ and
-the corresponding replication $p$-value $p_r$.
+where $K=z_o^2/z_{{\alpha_{\mathrm{S}}}}^2>1$. The right hand-side of
+\eqref{eq1:eq.z} is the minimum replication $z$-value $\zrmin$ required to
+achieve replication success. Note that $\zrmin$ increases with increasing $c$,
+so increasing the replication sample size leads to a more stringent success
+requirement $z_r$ and the corresponding replication $p$-value $p_r$.
 
@@
 To achieve replication success, the relative effect size must be at least as
-large as the right hand-side of \eqref{eq1:res}, the minimum relative effect size
-$\dmin$, a function of $K$ and the relative sample size $c$. If the relative
-sample size becomes very large, \ie{} $c \rightarrow \infty$, we have
+large as the right hand-side of \eqref{eq1:res}, the minimum relative effect
+size $\dmin$, a function of $K$ and the relative sample size $c$. If the
+relative sample size becomes very large, \ie{} $c \rightarrow \infty$, we have
 $\dmin \downarrow \dinfty$ where
@@
 a necessary but not sufficient requirement for replication success at the
-nominal level ($\alpha_S = \alpha$). The nominal level may therefore be too
-stringent. It is more reasonable to calibrate the procedure in such a way that
-to establish replication success, original and replication study do not both
-necessarily need to be significant at level $\alpha$, provided that the
+nominal level ($\alpha_{\mathrm{S}} = \alpha$). The nominal level may therefore
+be too stringent. It is more reasonable to calibrate the procedure in such a way
+that to establish replication success, original and replication study do not
+both necessarily need to be significant at level $\alpha$, provided that the
 replication effect estimate does not shrink compared to the original one. We
-therefore choose a level $\alpha_S$ such that a borderline significant original
-study ($p_o = \alpha$) cannot lead to replication success if there is shrinkage
-$s > 0$ of the replication effect estimate. Mathematically, this translates to
-setting $\dinfty = 1$ and \mbox{$K = z_\alpha^2/z_{\alpha_S}^2$}
+therefore choose a level $\alpha_{\mathrm{S}}$ such that a borderline
+significant original study ($p_o = \alpha$) cannot lead to replication success
+if there is shrinkage $s > 0$ of the replication effect estimate.
+Mathematically, this translates to setting $\dinfty = 1$ and
+\mbox{$K = z_\alpha^2/z_{\alpha_{\mathrm{S}}}^2$}
 in~\eqref{eq1:smallestpossible} and leads to the quadratic equation $K(K-1) = 1$
 with solution $K = \varphi$ where \mbox{$\varphi = (\sqrt{5}+1)/2 \approx 1.62$}
-is known as the golden ratio. Solving for $z_{\alpha_S}$ gives
-$z_{\alpha_S} = z_\alpha / \sqrt{\varphi}$ and the corresponding \textit{golden
-  level}
+is known as the golden ratio. Solving for $z_{\alpha_{\mathrm{S}}}$ gives
+$z_{\alpha_{\mathrm{S}}} = z_\alpha / \sqrt{\varphi}$ and the corresponding
+\textit{golden level}
 \begin{eqnarray}\label{eq1:golden}
-\alpha_S & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
+\alpha_{\mathrm{S}} & = & 1 -  \Phi(z_\alpha / \sqrt{\varphi} )
 \end{eqnarray}
@@
 detail. For $z_\alpha = 1.96$ (one-sided $\alpha = 0.025$), the golden level is
-$\alpha_S =0.062$. In the introductory example shown in Figure \ref{fig1:fig1},
-the sceptical $p$-value is $p_S=0.11 > 0.062$, so the replication of the
-\citet{Pyc2010} study was not successful.
+$\alpha_{\mathrm{S}} =0.062$. In the introductory example shown in Figure
+\ref{fig1:fig1}, the sceptical $p$-value is $\ps=0.11 > 0.062$, so the
+replication of the \citet{Pyc2010} study was not successful.
 
@@
 \eqref{eq1:smallestpossible} for $\dinfty > 0$ gives
-$K = z_\alpha^2/z_{\alpha_S}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The new
-level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_S}^2$, so
-$z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
+$K = z_\alpha^2/z_{\alpha_{\mathrm{S}}}^2 = 1/2+\sqrt{1/4 + 1/\dinfty^2}$. The
+new level~$\alpha'$ fulfills $\varphi=z_{\alpha'}^2/z_{\alpha_{\mathrm{S}}}^2$,
+so $z_\alpha^2/K=z_{\alpha'}^2/\varphi$ and therefore
 \begin{equation}\label{eq1:alphaPrime}
@@
 
-The condition $p_S \leq \alpha_S$ for replication success at the golden level is
-equivalent to $z_S \geq z_\alpha / \sqrt{\varphi}$, \ie{}
-$z_S \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable to
-recalibrate the sceptical $p$-value \mbox{$p_{S} = 1 - \Phi(z_S)$} to
-$ \tilde{p}_S = 1 - \Phi(z_S \sqrt{\varphi})$, which then needs to be compared
-to $\alpha$ (rather than $\alpha_S$) to assess replication success and can thus
-be interpreted on the same scale as an ordinary $p$-value. For example, the
-recalibrated sceptical $p$-value for the replication of \citet{Pyc2010} turns
-out to be $\tilde{p}_S=0.061$ and does not lead to replication success at any
-level $\alpha<0.061$, including the standard $0.025$ level.
+\sloppy The condition $\ps \leq \alpha_{\mathrm{S}}$ for replication success at the
+golden level is equivalent to
+\mbox{$z_{\mathrm{S}} \geq z_\alpha / \sqrt{\varphi}$}, \ie{}
+$z_{\mathrm{S}} \sqrt{\varphi} \geq z_\alpha$. In practice it may be preferable
+to recalibrate the sceptical $p$-value \mbox{$\ps = 1 - \Phi(z_{\mathrm{S}})$}
+to $ \tilde{p}_{\mathrm{S}} = 1 - \Phi(z_{\mathrm{S}} \sqrt{\varphi})$, which
+then needs to be compared to $\alpha$ (rather than $\alpha_{\mathrm{S}}$) to
+assess replication success and can thus be interpreted on the same scale as an
+ordinary $p$-value. For example, the recalibrated sceptical $p$-value for the
+replication of \citet{Pyc2010} turns out to be $\tilde{p}_{\mathrm{S}}=0.061$
+and does not lead to replication success at any level $\alpha<0.061$, including
+the standard $0.025$ level.
 
@@
 
-The main difference between the replication success and the two-trials
-rule approach concerns how shrinkage of the replication effect
-estimate is handled. Figure~\ref{fig1:fig2} illustrates that
-shrinkage is penalized in the assessment of replication success, \ie{}
-the original $p$-value needs to be quite small to achieve replication
-success for a relative effect size $d<1$. In contrast, significance of
-the replication study can be achieved even if there is substantial
-shrinkage, provided the replication sample size is large enough.
+The main difference between the replication success and the two-trials rule
+approach concerns how shrinkage of the replication effect estimate is handled.
+Figure~\ref{fig1:fig2} illustrates that shrinkage is penalized in the assessment
+of replication success, \ie{} the original $p$-value needs to be quite small to
+achieve replication success for a relative effect size $d<1$. In contrast,
+significance of the replication study can be achieved even if there is
+substantial shrinkage, provided the replication sample size is large enough.
 
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
 {\centering \includegraphics[width=\maxwidth]{images/paper1/fig2-1}
-
 }
-
 \end{knitrout}
 \caption{Comparison of replication success at the golden level
-  ($p_S \leq \alpha_S = 0.062$) and the two-trials rule ($p_o \leq 0.025$ and
-  $p_r \leq 0.025$). The dotted areas indicate that success is impossible for
-  original $p$-value $p_o$ and relative effect size $d$. In the white areas
-  success is possible and depends on the relative sample size $c$ as indicated
-  by the grey lines. The dashed black line in the left plot indicates the
-  limiting relative effect size $\dinfty$. }
+  ($\ps \leq \alpha_{\mathrm{S}} = 0.062$) and the two-trials rule
+  (\mbox{$p_o \leq 0.025$} and $p_r \leq 0.025$). The dotted areas indicate that
+  success is impossible for original \mbox{$p$-value $p_o$} and relative effect
+  size $d$. In the white areas success is possible and depends on the relative
+  sample size $c$ as indicated by the grey lines. The dashed black line in the
+  left plot indicates the limiting relative effect size $\dinfty$. }
 \label{fig1:fig2}
@@
 
-For $c=1$, \citet[Section 3]{Held2020} showed that $z_S^2$ in
-\eqref{eq1:extrinsic.p2} simplifies to half the harmonic mean of the squared test
-statistics $z_o^2$ and $z_r^2$. The connection $z_S^2 = z_H^2/4$ to the harmonic
-mean $\chi^2$-test statistic $z_H^2$ \citep{Held2020b}, which has a
+For $c=1$, \citet[Section 3]{Held2020} showed that $z_{\mathrm{S}}^2$ in
+\eqref{eq1:extrinsic.p2} simplifies to half the harmonic mean of the squared
+test statistics $z_o^2$ and $z_r^2$. The connection
+$z_{\mathrm{S}}^2 = z_{\mathrm{H}}^2/4$ to the harmonic mean $\chi^2$-test
+statistic $z_{\mathrm{H}}^2$ \citep{Held2020b}, which has a
 $\chi^2(1)$-distribution under the null hypothesis, makes it straightforward to
-compute the Type I error rate at level $\alpha_S$ for $c = 1$ as
+compute the Type I error rate at level $\alpha_{\mathrm{S}}$ for $c = 1$ as
 \begin{eqnarray}\label{eq1:T1E}
-\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_S \right)
+\mbox{T1E} =   \left\{1-\Phi\left[2 \, \Phi^{-1}\left(1-\alpha_{\mathrm{S}} \right)
  \right]\right\}/2.
 \end{eqnarray}
-For the golden level $\alpha_S =0.062$ at $\alpha = 0.025$, the Type I error
+For the golden level $\alpha_{\mathrm{S}} =0.062$ at $\alpha = 0.025$, the Type I error
 rate \eqref{eq1:T1E} is $0.0515$\%, slightly less than the Type I error rate
 $\alpha^2=0.0625$\% of the two-trials rule. For comparison, the Type I error
-rate at the nominal level $\alpha_S=0.025$ is $0.0022$\%, much smaller than
+rate at the nominal level $\alpha_{\mathrm{S}}=0.025$ is $0.0022$\%, much smaller than
 0.0625\%.
@@
 \begin{equation}\label{eq1:T1E0}
-  \mbox{T1E} = \int_{z_{\alpha_S}}^{\infty}
-\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \mbox{T1E} = \int_{z_{\alpha_{\mathrm{S}}}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) \,
   \phi(z_o) \, dz_o,
@@
 in the integral of \eqref{eq1:T1E0} is the probability of replication success at
-level $\alpha_S$ conditional on a fixed original test statistic $z_o$ and a
+level $\alpha_{\mathrm{S}}$ conditional on a fixed original test statistic $z_o$ and a
 relative sample size $c$. Now $z_r \sim \Nor(0,1)$ under the null hypothesis, so
 this term simplifies to
-$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$ where $\zrmin$
-in \eqref{eq1:eq.z} depends on $z_o$, $c$, and $\alpha_S$.
+$\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) = 1 - \Phi(\zrmin)$ where $\zrmin$
+in \eqref{eq1:eq.z} depends on $z_o$, $c$, and $\alpha_{\mathrm{S}}$.
 
@@
 increasing relative sample size $c$. This also follows from \eqref{eq1:T1E0}
-where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_S) = 1 - \Phi(\zrmin)$}
+where \mbox{$\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) = 1 - \Phi(\zrmin)$}
 decreases with increasing $c$, because $\zrmin$ increases with increasing $c$,
@@
 \begin{equation*}
-  \mbox{PP} = \int_{z_{\alpha_S}}^{\infty}
-\P(z_r \geq \zrmin \given z_o, c, \alpha_S) \,
+  \mbox{PP} = \int_{z_{\alpha_{\mathrm{S}}}}^{\infty}
+\P(z_r \geq \zrmin \given z_o, c, \alpha_{\mathrm{S}}) \,
   \phi(z_o - \mu) \, dz_o
@@
     $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
-    and $\tilde{p}_S$.}
+    and $\tilde{p}_{\mathrm{S}}$.}
   \label{tbl:discrep}
@@
   \toprule
-Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
+Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_{\mathrm{S}}$ \\
   \midrule

### 2022-12-19 source/paper3.tex
reorganizatin for reproducibility

--- 2022-12-14 paper3.tex
@@
 cost-effective replication studies. Our methods can be used through the R
-package BayesRepDesign.
+package \texttt{BayesRepDesign}.
 
@@
    {\begin{tabular}{c} \textbf{Design prior for model parameter} \\
-      {\scriptsize $f(\theta \given x_{o}, \text{external
+      {\scriptsize $f(\theta \given x_{o}, \mathrm{external~
       knowledge})$}\\
@@
   {\begin{tabular}{c} \textbf{Initial prior for model parameter} \\
-     {\scriptsize $f(\theta \given \text{external knowledge})$} \\
+     {\scriptsize $f(\theta \given \mathrm{external~knowledge})$} \\
    \end{tabular}};
@@
  {\begin{tabular}{c} \textbf{Predictive distribution of replication data} \\
-    {\scriptsize $f(x_{r} \given n_{r}, x_{o}, \text{external
+    {\scriptsize $f(x_{r} \given n_{r}, x_{o}, \mathrm{external~
     knowledge})$}
@@
 {\begin{tabular}{c} \textbf{Probability of replication success} \\
-   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \text{external
+   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \mathrm{external
     knowledge})$}
@@
     $f(x_{i} \given \theta)$ for $i \in \{o, r\}$. An initial prior with density
-    function $f(\theta \given \text{external knowledge})$ is assigned to the
+    function $f(\theta \given \mathrm{external~knowledge})$ is assigned to the
     model parameter $\theta$.}
@@
   \label{eq3:dp}
-  f(\theta \given x_o, \text{external knowledge}) =
-  \frac{f(x_o \given \theta) \, f(\theta \given \text{external knowledge})}{f(x_o \given
-  \text{external knowledge})}.
+  f(\theta \given x_o, \mathrm{external~knowledge}) =
+  \frac{f(x_o \given \theta) \, f(\theta \given \mathrm{external~knowledge})}{f(x_o \given
+  \mathrm{external~knowledge})}.
 \end{align}
@@
   \label{eq3:ftr}
-  f(x_r \given n_r, x_o, \text{external knowledge})
+  f(x_r \given n_r, x_o, \mathrm{external~knowledge})
   &= \int%_\Theta
-  % \underbrace{f(x_r \given n_{r}, \theta)}_{\text{likelihood}}
+  % \underbrace{f(x_r \given n_{r}, \theta)}_{\mathrm{likelihood}}
     f(x_r \given n_{r}, \theta)
-    % \, \underbrace{f(\theta \given x_o, \text{external knowledge})}_{\text{design prior}}
-    \, f(\theta \given x_o, \text{external knowledge})
-    \, \text{d}\theta.
+    % \, \underbrace{f(\theta \given x_o, \mathrm{external~knowledge})}_{\mathrm{design prior}}
+    \, f(\theta \given x_o, \mathrm{external~knowledge})
+    \, \mathrm{d}\theta.
 \end{align}
@@
   n_r^* = \inf \left\{n_r : \Pr(X_{r} \in S \given
-  n_r, x_{o}, \text{external knowledge}) \geq 1 - \beta \right\}.
+  n_r, x_{o}, \mathrm{external~knowledge}) \geq 1 - \beta \right\}.
 \end{align}
@@
 $n_{o}$. Depending on the effect size type, this framework might require slight
-modifications \citep[see \eg{}][ch. 2.4]{Spiegelhalter2004}.
+modifications \citep[see \eg{}][chapter 2.4]{Spiegelhalter2004}.
 
@@
 heterogeneous from the original effect size is not relevant to be detected. An
-absolute \citep[ch. 5.7.3]{Spiegelhalter2004} and a relative approach
+absolute \citep[chapter 5.7.3]{Spiegelhalter2004} and a relative approach
 \citep{Held2020c} can be considered. In the absolute approach, a value of
@@
 \begin{align*}
-  S_{\scriptscriptstyle \text{2TR}}
+  S_{\scriptscriptstyle \mathrm{2TR}}
   = \left[\zalpha\, \sigma_{r}, \infty \right),
@@
   \label{eq3:2TRpros}
-  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
+  \Pr(\that_{r} \in S_{\scriptscriptstyle \mathrm{2TR}} \given \that_{o}, \sigma_{o}, \sigma_{r})
   = % \Phi\left(\frac{\muthatr - \zalpha \, \sigma_{r}}{\sqrt{\sigma^{2}_{r} +
@@
   \label{eq3:limP2TR}
-  \text{limPr}_{\scriptscriptstyle \text{2TR}} =
+  \mathrm{limPr}_{\scriptscriptstyle \mathrm{2TR}} =
   \Phi\left(\frac{ \muthatr}{\sqrt{
@@
 probability of replication success
-$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{2TR}}$ can now be obtained
+$1 - \beta < \mathrm{limPr}_{\scriptscriptstyle \mathrm{2TR}}$ can now be obtained
 by equating~\eqref{eq3:2TRpros} to $1 - \beta$ and solving for $\sigma_{r}$. This
@@
 \mbox{($\tau^{2} = 0$, $\mutheta = \that_{o}$, $g \downarrow 0$)}, we obtain the
-well-known sample size formula \citep[ch. 3.3]{Matthews2006}
+well-known sample size formula \citep[chapter 3.3]{Matthews2006}
 \begin{align*}
@@
     \left(\that_{o}/\sigma_{o}^{2} + \that_{r}/\sigma^{2}_{r}\right)\sigma^{2}_{m}&
-&\text{and}&                                                                                       &\sigma_{m} = \left(1/\sigma^{2}_{o} + 1/\sigma^{2}_{r}\right)^{-1/2},&
+&\mathrm{and}&                                                                                       &\sigma_{m} = \left(1/\sigma^{2}_{o} + 1/\sigma^{2}_{r}\right)^{-1/2},&
 \end{align*}
@@
   \label{eq3:SMA}
-  S_{\scriptscriptstyle \text{MA}}
+  S_{\scriptscriptstyle \mathrm{MA}}
   = \left[\sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}} -
@@
   \label{eq3:MApros}
-  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{MA}} \given \that_{o}, \sigma_{o}, \sigma_{r})
+  \Pr(\that_{r} \in S_{\scriptscriptstyle \mathrm{MA}} \given \that_{o}, \sigma_{o}, \sigma_{r})
   = % \Phi\left(\frac{\muthatr - \sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}}
@@
 arbitrarily large by decreasing the standard error $\sigma_{r}$ but is bounded
-from above by $\text{limPr}_{\text{2TR}}$ defined in~\eqref{eq3:limP2TR}.
+from above by $\mathrm{limPr}_{\mathrm{2TR}}$ defined in~\eqref{eq3:limP2TR}.
 % However, as the original data already provide some information, the
@@
 The required standard error $\sigma_{r}^{*}$ to achieve a target probability of
-replication success $1 - \beta < \text{limPr}_{\text{2TR}}$ can be computed
+replication success $1 - \beta < \mathrm{limPr}_{\mathrm{2TR}}$ can be computed
 numerically using root finding algorithms.
@@
   \label{eq3:equivalence}
-  S_{\scriptscriptstyle \text{E}}
+  S_{\scriptscriptstyle \mathrm{E}}
   = \left[\that_{o} - \Delta + \zalphatwo \sqrt{\sigma^{2}_{o} +
@@
   \label{eq3:porsEqu}
-  \Pr(\that_{r} \in S_{\scriptscriptstyle \text{E}} \given \that_{o}, \sigma_{o}, \sigma_{r})
+  \Pr(\that_{r} \in S_{\scriptscriptstyle \mathrm{E}} \given \that_{o}, \sigma_{o}, \sigma_{r})
   &= % \Phi\left(\frac{\that_{o} + \Delta - \zalphatwo
@@
 \begin{align*}
-  \text{limPr}_{\scriptscriptstyle \text{E}} =
+  \mathrm{limPr}_{\scriptscriptstyle \mathrm{E}} =
   \Phi\left(\frac{\that_{o} + \Delta - \zalphatwo\sigma_{o}
@@
 probability of replication success
-$1 - \beta < \text{limPr}_{\scriptscriptstyle \text{E}}$ can again be computed
+$1 - \beta < \mathrm{limPr}_{\scriptscriptstyle \mathrm{E}}$ can again be computed
 numerically.
@@
 probability~\eqref{eq3:BFrpros} is bounded from above by a constant
-$\text{limPr}_{\scriptscriptstyle \BFr} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})$,
+$\mathrm{limPr}_{\scriptscriptstyle \BFr} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \BFr} \given \that_{o}, \sigma_{o}, \sigma_{r})$,
 and root finding algorithms can be used to numerically determine the required
 standard error $\sigma^{*}_{r}$ for achieving a target probability of
-replication success $1 - \beta < \text{limPr}_{\scriptscriptstyle \BFr}$.
+replication success $1 - \beta < \mathrm{limPr}_{\scriptscriptstyle \BFr}$.
 
@@
 and also bounded from above by a constant
-$\text{limPr}_{\scriptscriptstyle \ps} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})$.
+$\mathrm{limPr}_{\scriptscriptstyle \ps} = \lim_{\sigma_{r} \downarrow 0} \Pr(\that_r \in S_{\scriptscriptstyle \ps} \given \that_{o}, \sigma_{o}, \sigma_{r})$.
 As for the two-trials rule, the required standard error $\sigma_{r}^{*}$ to
 achieve a probability of replication success
-$1 - \beta < \text{limPr}_{\scriptscriptstyle \ps}$ can be computed analytically
+$1 - \beta < \mathrm{limPr}_{\scriptscriptstyle \ps}$ can be computed analytically
 for $\alpha < \beta$:
@@
 \caption{Probability of replication success as a function of relative sample
-  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original
-  effect estimate $\hat{\theta}_{o} = 0.205$ and
-  standard error $\sigma_{o} = 0.051$ for
+  size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original effect estimate
+  $\hat{\theta}_{o} = 0.205$ and standard error $\sigma_{o} = 0.051$ for
   different initial prior parameters ($\tau, \mutheta, \sigmatheta^{2}$). The
   probability of replication success with the design prior
-  $\tau = 0, \mutheta = 0$, and $\sigmatheta^{2} = 0$ (right plot) corresponds
-  to the type I error rate under the fixed effects null hypothesis
+  \mbox{$\tau = 0, \mutheta = 0$, and $\sigmatheta^{2} = 0$} (right plot)
+  corresponds to the type I error rate under the fixed effects null hypothesis
   ($H_{0}\colon \theta = 0, \tau^{2} = 0$). Replication success is defined by
-  the two-trials rule at level $\alpha = 0.025$, the replication
-  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
-  analysis at level $\alpha = 0.025^{2}$, effect size
-  equivalence based on $90\%$ confidence interval and with
-  margin $\Delta = 0.2$, sceptical $p$-value at level
-  $\alpha = 0.062$, and sceptical Bayes factor at level
-  $\gamma = 1/10$.}
+  the two-trials rule at level $\alpha = 0.025$, the replication Bayes factor at
+  level $\gamma = 1/10$, fixed effects-meta analysis at level
+  $\alpha = 0.025^{2}$, effect size equivalence based on $90\%$ confidence
+  interval and with margin $\Delta = 0.2$, sceptical $p$-value at level
+  $\alpha = 0.062$, and sceptical Bayes factor at level $\gamma = 1/10$.}
 \label{fig3:example}
@@
 \begin{align}
-  \bthat_r \given \mspace{-1mu} \btheta_r &\sim \Nor_{m}\left\{\btheta_r, \text{diag}\left(\bsigma_r^2\right)\right\}
+  \bthat_r \given \mspace{-1mu} \btheta_r &\sim \Nor_{m}\left\{\btheta_r, \mathrm{diag}\left(\bsigma_r^2\right)\right\}
   \label{eq3:hat_theta_k22} \\
   \btheta_r \given \theta \,\,  &\sim \Nor_{m}\left\{\theta \, \bone_{m},
-  \tau^2 \text{diag}(\bone_{m})\right\}, \label{eq3:theta_k2}
+  \tau^2 \mathrm{diag}(\bone_{m})\right\}, \label{eq3:theta_k2}
 \end{align}
@@
   \bthat_r \given \theta \sim \Nor_{m}\left\{\theta \, \bone_{m},
-\text{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right)\right\},
+\mathrm{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right)\right\},
   \label{eq3:margimulti}
@@
   \sim \Nor_{m}\left\{\muthatr \bone_{m},
-  \text{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right) +
+  \mathrm{diag}\left(\bsigma_r^2 + \tau^2 \bone_{m}\right) +
   \left(\frac{\tau^{2} + \sigma^{2}_{o}}{1 + 1/g}\right)
@@
 in SSD for cluster randomized trials and we can adapt the common solution based
-on cost functions \citep{Raudenbush1997}. %\citep[ch. 9.6]{Cochran1977}.
+on cost functions \citep{Raudenbush1997}. %\citep[chapter 9.6]{Cochran1977}.
 That is, the optimal configuration is determined so that the probability of
@@
     \tau^{2}) \,
-    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}.
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \mathrm{d}\tau^{2}.
 \end{align*}
@@
   f(\tau^{2} \given \that_{o}, \sigma_{o})
-  &= \int_{-\infty}^{+\infty} f(\theta, \tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\theta \\
+  &= \int_{-\infty}^{+\infty} f(\theta, \tau^{2} \given \that_{o}, \sigma_{o}) \, \mathrm{d}\theta \\
   &= \frac{\int_{-\infty}^{+\infty} f(\that_{o} \given \theta, \tau^{2}, \sigma^{2}_{o}) \,
-    f(\theta \given \tau^{2}) \, f(\tau^{2}) \, \text{d}\theta}{\int_{0}^{+\infty}
+    f(\theta \given \tau^{2}) \, f(\tau^{2}) \, \mathrm{d}\theta}{\int_{0}^{+\infty}
     \int_{-\infty}^{+\infty} f(\that_{o} \given \theta_{*}, \tau^{2}_{*}, \sigma^{2}_{o}) \,
-    f(\theta_{*} \given \tau^{2}_{*}) \, f(\tau^{2}_{*}) \, \text{d}\theta_{*} \,
-    \text{d}\tau^{2}_{*}} \\
+    f(\theta_{*} \given \tau^{2}_{*}) \, f(\tau^{2}_{*}) \, \mathrm{d}\theta_{*} \,
+    \mathrm{d}\tau^{2}_{*}} \\
   &= \frac{f(\tau^{2}) \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta, \tau^{2}
-    + \sigma^{2}_{o}) \, \Nor(\theta \given \mutheta, \sigmatheta^{2}) \,\text{d}\theta
+    + \sigma^{2}_{o}) \, \Nor(\theta \given \mutheta, \sigmatheta^{2}) \,\mathrm{d}\theta
     }{\int_{0}^{+\infty} f(\tau^{2}_{*})
     \int_{-\infty}^{+\infty} \Nor(\that_{o} \given \theta_{*}, \tau^{2}_{*} + \sigma^{2}_{o}) \,
-    \Nor(\theta_{*} \given \mutheta, \sigmatheta^{2}) \, \text{d}\theta_{*} \,
-    \text{d}\tau^{2}_{*}} \\
+    \Nor(\theta_{*} \given \mutheta, \sigmatheta^{2}) \, \mathrm{d}\theta_{*} \,
+    \mathrm{d}\tau^{2}_{*}} \\
   &= \frac{f(\tau^{2}) \, \Nor(\that_{o} \given \mutheta, \tau^{2}
@@
     \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
-    \text{d}\tau^{2}_{*}}.
+    \mathrm{d}\tau^{2}_{*}}.
 \end{align*}
@@
     \Nor(\that_{o} \given \mutheta, \tau^{2}_{*} + \sigma^{2}_{o} + \sigmatheta^{2}) \,
-    \text{d}\tau^{2}_{*}} \\
+    \mathrm{d}\tau^{2}_{*}} \\
   &= \lim_{\sigmatheta^{2} \to \infty}  \int_{0}^{+\infty} \frac{f(\tau^{2})}{f(\tau^{2}_{*})} \,
@@
     \underbrace{\frac{(\that_{o} - \mutheta)^{2}}{\tau^{2}_{*} + \sigma^{2}_{o} +
-    \sigmatheta^{2}}}_{\downarrow 0} \bigg\}\bigg] \, \text{d}\tau^{2}_{*} \\
+    \sigmatheta^{2}}}_{\downarrow 0} \bigg\}\bigg] \, \mathrm{d}\tau^{2}_{*} \\
   &= f(\tau^{2}),
@@
   &= \int_{S}\int_{0}^{+\infty} f(\that_{r} \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
-    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\that_{r} \,\text{d}\tau^{2} \\
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \mathrm{d}\that_{r} \,\mathrm{d}\tau^{2} \\
   &= \int_{0}^{+\infty} \Pr(\that_{r} \in S \given \that_{o}, \sigma_{o}, \sigma_{r}, \tau^{2}) \,
-    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \text{d}\tau^{2}. \\
+    f(\tau^{2} \given \that_{o}, \sigma_{o}) \, \mathrm{d}\tau^{2}. \\
 \end{align*}
@@
   size $c = n_{r}/n_{o}$ for experiment ``Labels'' with original effect estimate
-  $\hat{\theta}_{o} = 0.205$ and standard error
-  $\sigma_{o} = 0.051$ for uniform initial prior for effect size
-  $\theta$ and either fixed $\tau = 0.05$ (as in main
-  manuscript) or half normal prior with standard deviation
-  $0.04$ assigned to $\tau$. Replication success is defined
-  by the two-trials rule at level $\alpha = 0.025$, the replication
-  Bayes factor at level $\gamma = 1/10$, fixed effects-meta
-  analysis at level $\alpha = 0.025^{2}$, effect size
-  equivalence based on $90\%$ confidence interval and with
-  margin $\Delta = 0.2$, sceptical $p$-value at level
-  $\alpha = 0.062$, and sceptical Bayes factor at level
-  $\gamma = 1/10$.}
+  $\hat{\theta}_{o} = 0.205$ and standard error $\sigma_{o} = 0.051$ for uniform
+  initial prior for effect size $\theta$ and either fixed $\tau = 0.05$ (as in
+  main manuscript) or half normal prior with standard deviation $0.04$ assigned
+  to $\tau$. Replication success is defined by the two-trials rule at level
+  $\alpha = 0.025$, the replication Bayes factor at level $\gamma = 1/10$, fixed
+  effects-meta analysis at level \mbox{$\alpha = 0.025^{2}$}, effect size
+  equivalence based on $90\%$ confidence interval and with margin
+  $\Delta = 0.2$, sceptical $p$-value at level $\alpha = 0.062$, and sceptical
+  Bayes factor at level $\gamma = 1/10$.}
 \label{fig3sup:exampletaurandom}
@@
 \begin{align*}
-  S_{\text{2TR}} =
+  S_{\mathrm{2TR}} =
   \begin{cases}
-    \left[\zalpha \, \sigma_{r}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
-    \left[-\infty, -\zalpha \, \sigma_{r} \right) & \text{for} ~ \that_{o} < 0.
+    \left[\zalpha \, \sigma_{r}, \infty \right) & \mathrm{for} ~ \that_{o} > 0 \\
+    \left[-\infty, -\zalpha \, \sigma_{r} \right) & \mathrm{for} ~ \that_{o} < 0.
   \end{cases}
@@
 \begin{align*}
-  S_{\text{2TR}} =
+  S_{\mathrm{2TR}} =
   \begin{cases}
-    \left[\zalpha \, \sigma_{r*}, \infty \right) & \text{for} ~ \that_{o} > 0 \\
-    \left[-\infty, -\zalpha \, \sigma_{r*} \right) & \text{for} ~ \that_{o} < 0.
+    \left[\zalpha \, \sigma_{r*}, \infty \right) & \mathrm{for} ~ \that_{o} > 0 \\
+    \left[-\infty, -\zalpha \, \sigma_{r*} \right) & \mathrm{for} ~ \that_{o} < 0.
   \end{cases}
@@
 With some algebraic manipulations one can show that this criterion implies a
-success region $S_{\text{MA}}$ for the replication effect estimate $\that_{r}$
+success region $S_{\mathrm{MA}}$ for the replication effect estimate $\that_{r}$
 given by
@@
       (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o},   \infty )
-    & \text{for} ~ \that_{o} > 0 \\
+    & \mathrm{for} ~ \that_{o} > 0 \\
     (-\infty, -\sigma_{r} \zalpha\sqrt{1 + \sigma^{2}_{r}/\sigma^{2}_{o}} -
       (\that_{o} \sigma^{2}_{r})/\sigma^{2}_{o}]
-    & \text{for} ~ \that_{o} < 0.
+    & \mathrm{for} ~ \that_{o} < 0.
 \end{cases}
@@
 $\sigma_{i}$ the corresponding standard error (assumed to be know), and that we
-use the alternative $H_{1} \colon \Nor(\that_{o}, \sigma^{2}_{o})$ which arises
-from updating an initial flat prior for $\theta$ the original data
+use the alternative $H_{1} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$
+which arises from updating an initial flat prior for $\theta$ the original data
 $x_{o} = \{\that_{o}, \sigma_{o}\}$. The replication Bayes factor is then
@@
         &= \int f(\hat{\btheta}_{r} \given \theta) f(\theta \given H_{1})
-                        \, \text{d}\theta \\
+                        \, \mathrm{d}\theta \\
               &= \int \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \theta)^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}} +
@@
                                     \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
-    \, \text{d}\theta \\
+    \, \mathrm{d}\theta \\
   &= \int \frac{
@@
     \left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
-    \, \text{d}\theta \\
+    \, \mathrm{d}\theta \\
   &= \frac{\exp\left[-\frac{1}{2} \left\{\sum_{i=1}^{n} \frac{(\hat{\theta}_{ri} - \hat{\theta}_{r*})^{2}}{\sigma^{2}_{ri} + \tau^{2}_{r}}\right\} \right]}{\left\{2\pi \sigma^{2}_{o} \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{1/2}}
     \underbrace{\int \exp\left[-\frac{1}{2} \left\{\frac{(\hat{\theta}_{r*} - \theta)^{2}}{\sigma^{2}_{r*}} +
-    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right] \text{d}\theta}_{= \Nor(\hat{\theta}_{r*}; m, \sigma^{2}_{o} + \sigma^{2}_{r*}) 2\pi \sigma_{o} \sigma_{r*}} \\
+    \frac{(\theta - \that_{o})^{2}}{\sigma^{2}_{o}}\right\} \right] \mathrm{d}\theta}_{= \Nor(\hat{\theta}_{r*}; m, \sigma^{2}_{o} + \sigma^{2}_{r*}) 2\pi \sigma_{o} \sigma_{r*}} \\
   &= \left\{(1 + \sigma^{2}_{o}/\sigma^{2}_{r*}) \prod_{i = 1}^{n} 2\pi \left(\sigma^{2}_{ri} + \tau^{2}_{r}\right)\right\}^{-1/2} \exp\left[-\frac{1}{2}\left\{
@@
 $i \in \{o, r\}$, along with a zero-mean ``sceptical'' prior
-$\theta \sim \Nor(0, \sigma^{2}_{s})$ for the effect size. In a first step, a
+$\theta \sim \Nor(0, \sigma^2_{\mathrm{S}})$ for the effect size. In a first step, a
 level $\alpha \geq p_{o} = 1 - \Phi(|\that_{o}|/\sigma_{o})$ is fixed and the
-``sufficiently sceptical'' prior variance $\sigma^{2}_{s}$ is computed
-\begin{align*}
-  \sigma^{2}_{s} = \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}
+``sufficiently sceptical'' prior variance $\sigma^2_{\mathrm{S}}$ is computed
+\begin{align*}
+  \sigma^2_{\mathrm{S}} = \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}
 \end{align*}
 where $z_{o} = \that_{o}/\sigma_{o}$. The sufficiently sceptical prior variance
-$\sigma^{2}_{s}$ has the property that it renders the resulting posterior of
+$\sigma^2_{\mathrm{S}}$ has the property that it renders the resulting posterior of
 $\theta$ no longer ``credible'' at level $\alpha$, that is, the posterior tail
 probability is fixed to
-$\Pr(\theta \geq 0 \given \that_{o}, \sigma_{o}, \sigma_{s}) = 1 - \alpha$ for
+$\Pr(\theta \geq 0 \given \that_{o}, \sigma_{o}, \sigma_{\mathrm{S}}) = 1 - \alpha$ for
 positive estimates and
-$\Pr(\theta \leq 0 \given \that_{o}, \sigma_{o}, \sigma_{s}) = 1 - \alpha$ for
+$\Pr(\theta \leq 0 \given \that_{o}, \sigma_{o}, \sigma_{\mathrm{S}}) = 1 - \alpha$ for
 negative estimates. In a second step, the conflict between the sceptical prior
@@
 \begin{align*}
-  p_{\text{Box}} =
+  p_{\mathrm{Box}} =
   \begin{cases}
-    1 - \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^{2}_{s})\right\}
-    & \text{if} ~ \that_{o} > 0 \\
-   \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^{2}_{s})\right\}
-    & \text{if} ~ \that_{o} < 0 \\
+    1 - \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^2_{\mathrm{S}})\right\}
+    & \mathrm{if} ~ \that_{o} > 0 \\
+   \Phi\left\{\that_{r}/(\sigma^{2}_{r} + \sigma^2_{\mathrm{S}})\right\}
+    & \mathrm{if} ~ \that_{o} < 0 \\
     \end{cases}
@@
 is computed and replication success at level $\alpha$ is declared if
-$p_{\text{Box}} \leq \alpha$. The smallest level $\alpha$ at which replication
+$p_{\mathrm{Box}} \leq \alpha$. The smallest level $\alpha$ at which replication
 success is achieved is called the \emph{the sceptical $p$-value} $\ps$ and
@@
 \citep[see][for more details on $\ps$]{Held2020, Held2021}. By applying some
-algebraic manipulations to the condition $p_{\text{Box}} \leq \alpha$, one can
+algebraic manipulations to the condition $p_{\mathrm{Box}} \leq \alpha$, one can
 show that it is equivalent to the replication effect estimate $\that_{r}$
@@
   \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}\}, \infty)
-    & \text{if} ~ \that_{o} > 0 \\
+    & \mathrm{if} ~ \that_{o} > 0 \\
    (-\infty, -\zalpha \surd\{\sigma^{2}_{r} +
   \frac{\sigma^{2}_{o}}{(z_{o}^{2}/\zalpha^{2}) - 1}\}]
-    & \text{if} ~ \that_{o} < 0. \\
+    & \mathrm{if} ~ \that_{o} < 0. \\
     \end{cases}
@@
 evidence for the point null hypothesis $H_{0} \colon \theta = 0$ relative to the
-``sceptical'' alternative $H_{S} \colon \theta \sim \Nor(0, \sigma^{2}_{s})$
+``sceptical'' alternative $H_{\mathrm{S}} \colon \theta \sim \Nor(0, \sigma^2_{\mathrm{S}})$
 with the Bayes factor
 \begin{align*}
-  \BF_{0S}
-  = \frac{f(\that_{o} \given H_{0})}{f(\that_{o} \given H_{S})}
-  = \sqrt{1 + \sigma^{2}_{s}/\sigma^{2}_{o}} \, \exp\left\{-
-  \, \frac{z_{o}^{2}}{2(1 + \sigma^{2}_{o}/\sigma^{2}_{s})}\right\}.
+  \BF_{\mathrm{0S}}
+  = \frac{f(\that_{o} \given H_{0})}{f(\that_{o} \given H_{\mathrm{S}})}
+  = \sqrt{1 + \sigma^2_{\mathrm{S}}/\sigma^{2}_{o}} \, \exp\left\{-
+  \, \frac{z_{o}^{2}}{2(1 + \sigma^{2}_{o}/\sigma^2_{\mathrm{S}})}\right\}.
 \end{align*}
 where $z_{o} = \that/\sigma^{2}_{o}$. One then determines the sufficiently
-sceptical prior variance $\sigma^{2}_{s}$ so that the Bayes factor is fixed to a
+sceptical prior variance $\sigma^2_{\mathrm{S}}$ so that the Bayes factor is fixed to a
 level $\gamma \in (0, 1)$ meaning that there is no longer evidence against the
@@
   \label{eq3sup:ssv}
-  \sigma^{2}_{s} &=
+  \sigma^2_{\mathrm{S}} &=
   \begin{cases}
-    -\dfrac{\that_{o}^2}{q} - \sigma^{2}_{o} & ~~ \text{if} ~ -\dfrac{\that_o^2}{q} \geq \sigma^{2}_{o} \\
-    \text{undefined} & ~~ \text{else}
+    -\dfrac{\that_{o}^2}{q} - \sigma^{2}_{o} & ~~ \mathrm{if} ~ -\dfrac{\that_o^2}{q} \geq \sigma^{2}_{o} \\
+    \mathrm{undefined} & ~~ \mathrm{else}
   \end{cases} \\
-  \text{where} ~ q &= \lw{-1} \left\{-\frac{z_o^2}{\gamma^2} \,
+  \mathrm{where} ~ q &= \lw{-1} \left\{-\frac{z_o^2}{\gamma^2} \,
   \exp\left(-z_o^2\right)\right\}
@@
 with $\lw{-1}(\cdot)$ the branch of the
-Lambert W function with $\text{W}(y) \leq -1$ for $y \in [-1/e, 0)$.
+Lambert W function with $\mathrm{W}(y) \leq -1$ for $y \in [-1/e, 0)$.
 
@@
 data is quantified. To do so, the sceptic is contrasted to the ``advocacy''
-alternative $H_{A} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$ which
+alternative $H_{\mathrm{A}} \colon \theta \sim \Nor(\that_{o}, \sigma^{2}_{o})$ which
 represents the position of an advocate as the prior corresponds to the posterior
@@
 \begin{align*}
-  \BF_{SA}
-  = \frac{f(\that_{r} \given H_{S})}{f(\that_{r} \given H_{A})}
-  = \sqrt{\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^{2}_{s} + \sigma^{2}_{r}}}
-  \, \exp\left[-\frac{1}{2}\left\{\frac{\that_{r}^{2}}{\sigma^{2}_{s} +
+  \BF_{\mathrm{SA}}
+  = \frac{f(\that_{r} \given H_{\mathrm{S}})}{f(\that_{r} \given H_{\mathrm{A}})}
+  = \sqrt{\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^2_{\mathrm{S}} + \sigma^{2}_{r}}}
+  \, \exp\left[-\frac{1}{2}\left\{\frac{\that_{r}^{2}}{\sigma^2_{\mathrm{S}} +
   \sigma^{2}_{r}} - \frac{(\that_{r} - \that_{o}^{2})}{\sigma^{2}_{o} +
@@
 \end{align*}
-and replication success at level $\gamma$ is defined by $\BF_{SA} \leq \gamma$
+and replication success at level $\gamma$ is defined by $\BF_{\mathrm{SA}} \leq \gamma$
 as the data favor the advocate over the sceptic at a higher level than the
@@
 $\BFs$]{Pawel2022b}. To derive the success region of the sceptical Bayes factor
-one can apply algebraic manipulations to $\BF_{SA} \leq \gamma$, the condition
+one can apply algebraic manipulations to $\BF_{\mathrm{SA}} \leq \gamma$, the condition
 for replication success at level $\gamma$, which leads to
@@
   = \begin{cases}
-    (-\infty, -\sqrt{B} - M] \bigcup [\sqrt{B} - M, \infty) & \text{for} ~ \sigma^{2}_{s} < \sigma^{2}_{o} \\
+    (-\infty, -\sqrt{B} - M] \bigcup [\sqrt{B} - M, \infty) & \mathrm{for} ~ \sigma^2_{\mathrm{S}} < \sigma^{2}_{o} \\
     [\that_{o} -\{(\sigma^{2}_{o} + \sigma^{2}_{r})\log\gamma\}/\that_{o}, \infty)
-    & \text{for} ~ \sigma^{2}_{s} = \sigma^{2}_{o}  \\
-    [-\sqrt{B} - M, \sqrt{B} - M] & \text{for} ~ \sigma^{2}_{s} > \sigma^{2}_{o}
+    & \mathrm{for} ~ \sigma^2_{\mathrm{S}} = \sigma^{2}_{o}  \\
+    [-\sqrt{B} - M, \sqrt{B} - M] & \mathrm{for} ~ \sigma^2_{\mathrm{S}} > \sigma^{2}_{o}
     \end{cases}
@@
 \begin{align*}
-  B &= \left\{\frac{\that_{o}^{2}}{\sigma^{2}_{o} - \sigma^{2}_{s}} +
-      2\log\left(\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^{2}_{s} + \sigma^{2}_{r}}\right)
+  B &= \left\{\frac{\that_{o}^{2}}{\sigma^{2}_{o} - \sigma^2_{\mathrm{S}}} +
+      2\log\left(\frac{\sigma^{2}_{o} + \sigma^{2}_{r}}{\sigma^2_{\mathrm{S}} + \sigma^{2}_{r}}\right)
       - 2\log \gamma \right\}
-      \frac{(\sigma^{2}_{s} + \sigma^{2}_{r})(\sigma^{2}_{o} + \sigma^{2}_{r})}{\sigma^{2}_{o}
-       - \sigma^{2}_{s}} \\
-  M &= \frac{\that_{o} (\sigma^{2}_{s} + \sigma^{2}_{r})}{\sigma^{2}_{o} - \sigma^{2}_{s}}
-\end{align*}
-and the sufficiently sceptical prior variance $\sigma^{2}_{s}$ computed
+      \frac{(\sigma^2_{\mathrm{S}} + \sigma^{2}_{r})(\sigma^{2}_{o} + \sigma^{2}_{r})}{\sigma^{2}_{o}
+       - \sigma^2_{\mathrm{S}}} \\
+  M &= \frac{\that_{o} (\sigma^2_{\mathrm{S}} + \sigma^{2}_{r})}{\sigma^{2}_{o} - \sigma^2_{\mathrm{S}}}
+\end{align*}
+and the sufficiently sceptical prior variance $\sigma^2_{\mathrm{S}}$ computed
 by~\eqref{eq3sup:ssv}.

### 2022-12-19 source/paper4.tex
reorganizatin for reproducibility

--- 2022-12-12 paper4.tex
@@
   deaths among total number of patients for treatment/control group, log odds
-  ratio effect estimates with 95\% confidence interval, two-sided $p$-values
-  $p$, and prior-predictive tail probabilities $p_{\text{Box}}$ with a
-  meta-analytic estimate based on the remaining studies serving as the prior.}
+  ratio effect estimates with 95\% confidence interval, two-sided
+  \textit{p}-values $p$, and prior-predictive tail probabilities
+  $p_{\text{Box}}$ with a meta-analytic estimate based on the remaining studies
+  serving as the prior.}
 \label{fig4:covid19-meta}
@@
 statistically significant and non-significant findings have been termed the
-Analysis of Credibility \citep{Matthews2018} (or AnCred), whose principles and
-practice we now briefly review.
+Analysis of Credibility, or in short AnCred \citep{Matthews2018}, whose
+principles and practice we now briefly review.
 
@@
 information content of the prior is equivalent to that provided by a single
-subject or event (\emph{unit-information prior}) \citep{Kass1995b}. The other
+subject or event \citep[\emph{unit-information prior},][]{Kass1995b}. The other
 component is an informative prior based on the (significant) results from the
@@
 $\alpha=0.05$, providing another principled argument for the recent proposition
-to lower the $p$-value threshold for the claims of new discoveries to 0.005
-\citep{Benjamin2017}. A simple check for intrinsic credibility is based on the
-\emph{credibility ratio}, the ratio of the upper to the lower limit (or vice
+to lower the \mbox{$p$-value} threshold for the claims of new discoveries to
+0.005 \citep{Benjamin2017}. A simple check for intrinsic credibility is based on
+the \emph{credibility ratio}, the ratio of the upper to the lower limit (or vice
 versa) of a confidence interval for a significant effect size estimate. If the
@@
   \text{where} ~ q &=
-  \text{W} \left(-\frac{z^2}{\gamma^2} \cdot
+  \mathrm{W} \left(-\frac{z^2}{\gamma^2} \cdot
   \exp\left\{-z^2\right\}\right)
@@
 \end{align}
-where $\text{W}(\cdot)$ is the branch of the Lambert $W$ function that satisfies
-$\text{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see the
-Appendix in \citep{Pawel2020b} for a proof.
+where $\mathrm{W}(\cdot)$ is the branch of the Lambert W function that satisfies
+$\mathrm{W}(y) \leq -1$ for \mbox{$y \in [-e^{-1}, 0)$} \citep{Corless1996}, see
+the Appendix in \citep{Pawel2020b} for a proof.
 
@@
 \end{align}
-with $k = W(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $W(\cdot)$ the branch of the
-Lambert $W$ function that satisfies $W(y) \leq -1$ for $y \in [-e^{-1}, 0).$ If
+with $k = \mathrm{W}(-z^{2} \exp\{-z^{2}/2\}/\sqrt{2})$ and $\mathrm{W}(\cdot)$
+the branch of the Lambert W function that satisfies $\mathrm{W}(y) \leq -1$ for
+$y \in [-e^{-1}, 0).$ If
 $\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at

### 2022-12-19 source/data/extract.R

@@ -1,0 +1,11 @@
+library(dplyr)
+# download from https://osf.io/39s7j
+dat <- read.csv("RP_CB Final Analysis - Effect level data.csv")
+datClean <- dat |>
+    select(paper = Paper.., experiment = Experiment.., effect = Effect..,
+           internalReplication = Internal.replication..,
+           smdo = Original.effect.size..SMD.,
+           so = Original.standard.error..SMD., no = Original.sample.size,
+           smdr = Replication.effect.size..SMD.,
+           sr = Replication.standard.error..SMD. , nr = Replication.sample.size)
+write.csv(x = datClean, file = "rpcb.csv", row.names = FALSE)

### 2022-12-20 source/intro.Rnw
docker support

--- 2022-12-19 intro.Rnw
@@
 << "sessionInfo2", echo = Reproducibility, results = Reproducibility >>=
+cat(paste(Sys.time(), Sys.timezone(), "\n"))
 sessionInfo()

### 2022-12-20 source/abstract.tex
R packages

--- 2022-12-19 abstract.tex
@@
 some situations the sceptical $p$-value may indicate replication success even
-though the effect estimate from the replication is arbitrarily smaller than the
-effect estimate from the original study. % , which cannot happen with the sceptical
+though the effect estimate from the replication is substantially smaller than
+the effect estimate from the original study. % , which cannot happen with the sceptical
 % Bayes factor.

### 2022-12-20 source/intro.Rnw
R packages

@@
 % merely by chance.
-The concept of replicability has long been a central part of the scientific
+The concept of replicability has long been a cornerstone of the scientific
 method. For instance, \citet[p. 13]{Fisher1935} noted ``\textit{no isolated
@@
 
-ggarrange(plotA, plotB, ncol = 2)
+grid.arrange(plotA, plotB, ncol = 2)
 @
@@
     theme(panel.grid = element_blank())
-ggpubr::ggarrange(plotA, plotB, ncol = 2, align = "v")
+grid.arrange(plotA, plotB, ncol = 2)
 @
@@
 investigation. Reverse-Bayes inference then revolves around the question of
-whether the resulting prior is plausible in light of external knowledge, and if
-so, this indicates support for the specified posterior.
+whether the resulting prior is plausible in light of external data/knowledge,
+and if so, this indicates support for the specified posterior.
 
@@
 mean $z_{\text{H}}^{2} = 2/(1/z^{2}_{o} + 1/z^{2}_{r})$ of the squared
-$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$.
-Replication success at level $\alpha$ is then equivalent to
-$p_{\text{S}} \leq \alpha$. For instance, the sceptical $p$-values of the three
+$z$-statistics, and variance ratio $c = \sigma^{2}_{o}/\sigma^{2}_{r}$. A
+sceptical $p$-value $\ps \leq \alpha$ is then equivalent to replication success
+at level $\alpha$. For instance, the sceptical $p$-values of the three
 replication studies in Figure~\ref{fig:RBillustration} are
@@
 at level $\alpha$ is possible. The sceptical $p$-value hence requires
-\emph{both} studies to be sufficiently convincing on their own (in terms of
-their $p$-values), similar to the significance criterion for replication
-success. Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the
-relative effect estimate \mbox{$d = \that_{r}/\that_{o}$} decreases towards
-zero, the sceptical $p$-value increases, meaning that shrinkage of the
-replication effect estimate is penalized ($p_{\text{S}} \uparrow 1$ as
-$d \downarrow 0$ for fixed $p_{o}$ and $p_{r}$). The sceptical $p$-value thus
-takes effect shrinkage into account, unlike the significance criterion which can
-be achieved with any non-zero replication effect estimate $\that_{r}$ provided
-the standard error $\sigma_{r}$ is small enough. This property is desirable in
-the replication setting as a smaller replication effect estimate $\that_{r}$ may
-not be practically relevant anymore, despite its statistical significance.
+\emph{both} studies to be sufficiently convincing (in terms of their
+$p$-values), similar to the significance criterion for replication success.
+Second, if the $p$-values $p_{o}$ and $p_{r}$ remain fixed but the relative
+effect estimate \mbox{$d = \that_{r}/\that_{o}$} decreases towards zero, the
+sceptical $p$-value increases, meaning that shrinkage of the replication effect
+estimate is penalized ($p_{\text{S}} \uparrow 1$ as $d \downarrow 0$ for fixed
+$p_{o}$ and $p_{r}$). The sceptical $p$-value thus takes effect shrinkage into
+account, unlike the significance criterion which can be achieved with any
+non-zero replication effect estimate $\that_{r}$ provided the standard error
+$\sigma_{r}$ is small enough. This property is desirable in the replication
+setting as a smaller replication effect estimate $\that_{r}$ may not be
+practically relevant anymore, despite its statistical significance.
 
@@
 success based on $p_{\text{S}} \leq \alpha_{G}$ is only possible if the
-replication effect estimate is at least as large as the original one
+replication effect estimate does not shrink compared to the original one
 ($d \geq 1$). For instance, for the one-sided significance level
@@
 assessment of replication studies to use Bayes factors \citep{Good1958,
-  Jeffreys1961} for quantifying evidence and prior-data
-conflict. % Bayes factors are also
-% used for prior-data conflict assessment as suggested by \citep{Box1980}.
-Similar to the sceptical $p$-value, the procedure leads to a single measure for
-quantifying replication success, \emph{the sceptical Bayes factor}. Systematic
-comparisons show that the sceptical Bayes factor has similar properties as the
-sceptical $p$-value %due to the reverse-Bayes approach underlying both methods
-(\eg{} it penalizes shrinkage of the replication effect estimate and requires
-compelling evidence from both studies in terms of $p$-values and Bayes factors,
-respectively). However, it is also shown that the sceptical $p$-value suffers
-from a certain type of ``shrinkage paradox'', which is avoided by the sceptical
-Bayes factor; when the $p$-value from the original study goes to zero,
-replication success based on the sceptical $p$-value can be achieved with any
-arbitrarily small replication effect estimate, whereas replication success based
-on the sceptical Bayes factor poses a finite limit on how much shrinkage is
-allowed. Technically, the procedure is more involved and closed-form solutions
-for the sceptical Bayes factor are only available in special
-situations. % and in terms of the
+  Jeffreys1961} for quantifying evidence and prior-data conflict. Similar to the
+sceptical $p$-value, the procedure leads to a single measure for quantifying
+replication success, \emph{the sceptical Bayes factor}. Systematic comparisons
+show that the sceptical Bayes factor has similar properties as the sceptical
+$p$-value -- it penalizes shrinkage of the replication effect estimate and
+requires compelling evidence from both studies (in terms Bayes factors).
+However, it is also shown that the sceptical $p$-value suffers from a certain
+type of ``shrinkage paradox'', which is avoided by the sceptical Bayes factor;
+when the $p$-value from the original study goes to zero, replication success
+based on the sceptical $p$-value can be achieved with any arbitrarily small
+replication effect estimate, whereas replication success based on the sceptical
+Bayes factor poses a finite limit on how much shrinkage is allowed. Technically,
+the procedure is more involved and closed-form solutions for the sceptical Bayes
+factor are only available in special situations. % and in terms of the
 % ``Lambert W function'' \citep{Corless1996}.
@@
 \emph{Bayesian Additional Evidence}, and we noted some flaws in the article.
-This prompted us to write a commentary. We show that -- contrary to the
-statement by Sondhi et al. -- there is a closed form solution for the key
-quantity in their approach termed ``Bayesian Additional Evidence tipping
-point''.
+This prompted us to write a commentary. We show that -- contrary to the claim by
+Sondhi et al. -- there is a closed form solution for the key quantity in their
+approach termed ``Bayesian Additional Evidence tipping point''.
 % The Bayesian Additional Evidence method provides an answer to the question
@@
   ".")} \citep{R}. The packages \texttt{dplyr} \citep{Wickham2022},
-\texttt{ggplot2} \citep{Wickham2016}, \texttt{knitr} \citep{Xie2022},
-\texttt{ReplicationSuccess} \citep{Held2020}, \texttt{UpSetR}
-\citep{Gehlenborg2019}, and \texttt{xtable} \citep{Dahl2019} were used. Code and
-data to reproduce this thesis are available at
-\url{https://github.com/SamCH93/thesis}. A snapshot of the git repository is
-archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
+\texttt{ggplot2} \citep{Wickham2016}, \texttt{gridExtra} \citep{Auguie2017},
+\texttt{knitr} \citep{Xie2022}, \texttt{ReplicationSuccess} \citep{Held2020},
+\texttt{scales} \citep{Wickham2022b}, \texttt{UpSetR} \citep{Gehlenborg2019},
+and \texttt{xtable} \citep{Dahl2019} were used. Code and data to reproduce this
+thesis are available at \url{https://github.com/SamCH93/thesis}. A snapshot of
+the git repository is archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
 

### 2022-12-20 source/thesis.Rnw
R packages

--- 2022-12-14 thesis.Rnw
@@
 library(ggplot2) # plotting
-library(ggpubr) # combining ggplots
+library(gridExtra) # combining ggplots
 library(scales) # scales for plots
@@
 }
+\include{paper6}
 

### 2022-12-20 source/abstract.tex
polish

@@
 % % verständliche kurze Zusammenfassung voranzustellen."
-
-% \cleardoublepage
-% \pdfbookmark{Zusammenfassung}{abstract_DE}
-
-% { % need this extra grouping to avoid carry-over effects
-% \begin{otherlanguage}{ngerman}
-% \enlargethispage{4\baselineskip}
-% \begin{center}\abstractnamefont
-%   Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor
-%   incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis
-%   nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-%   Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore
-%   eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt
-%   in culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor
-%   sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut
-%   labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud
-%   exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis
-%   aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu
-%   fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
-%   culpa qui officia deserunt mollit anim id est laborum. Lorem ipsum dolor sit
-%   amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore
-%   et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation
-%   ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
-%   in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla
-%   pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui
-%   officia deserunt mollit anim id est laborum.
-
-% \end{center}
-% \end{otherlanguage}
-% }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% The credibility of a scientific finding is based on the fact that it can be
-% replicated when the same study is repeated with new subjects.
-% An important aspect of the credibility of a scientific finding is that the
-% finding can be replicated when the same study is repeated with new subjects.
-% An important aspect of the credibility of a scientific finding is its
-% replicability -- the ability to produce similar results when the same study is
-% repeated with new subjects.
 An important aspect of the credibility of scientific findings is their
-replicability -- the ability that a similar finding can be obtained when the
-same study is repeated with new subjects. However, various failures to replicate
-major scientific findings in the social and life sciences indicate that
-replicability is often lower than expected. This ``replication crisis'' has led
-to several methodological reforms in the past decade, an increased conduct of
-replication studies being one of them. Despite this increase in replication
-studies, there is no consensus on a fundamental question: How should replication
-success be defined statistically?
-% Various methods already exist and various new ones have been proposed in
-% response to the crisis. This thesis centres around a proposal based on the
-% reverse-Bayes approach. The key idea is to reverse the traditional ``forward''
-% use of Bayes' theorem (``prior + likelihood $\rightarrow$ posterior''),
-% starting instead with a pre-specified posterior and deducing the corresponding
-% prior (``posterior + likelihood $\rightarrow$
-% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
-% % setting as it enables the mathematical formalization of scepticism regarding the
-% % finding from the original study.
-% This allows us to challenge the original finding by determining a sceptical
-% prior for the underlying effect size such that the resulting posterior is no
-% longer convincing. This prior then represents the position of a sceptic who
-% remains unconvinced by the original study. Whether or not the sceptics'
-% position is justified can then be assessed in light of the new data from the
-% replication study. The larger the conflict between the replication data and
-% the sceptic, the larger the degree of replication success. This procedure can
-% be summarized in a single quantitative measure of replication success, termed
-% the sceptical $p$-value.
+replicability -- the ability that a similar finding can be obtained when a study
+is repeated with new subjects. However, various failures to replicate major
+scientific findings in the social and life sciences indicate that replicability
+is often lower than expected. This ``replication crisis'' has led to several
+methodological reforms in the past decade, an increased conduct of replication
+studies being one of them. Despite this increase in replication studies, there
+is no consensus on a fundamental question: How should replication success be
+defined statistically?
 
@@
 this thesis. It consists of three extensions to a recently proposed
-reverse-Bayes method for quantifying replication success. The key idea of the
-method is to challenge the data from the original study with a sceptical prior
-distribution so that the resulting posterior distribution no longer indicates
-evidence for an effect. The goal of the replication study is then to show that
-the sceptical prior is unrealistic, and replication success is achieved if there
-is sufficient conflict between the prior and the replication data. The procedure
-can be summarized in a single quantitative measure, termed the sceptical
-$p$-value.
+reverse-Bayes method for quantifying replication success. The methods' key idea
+is to challenge the data from the original study with a sceptical prior
+distribution for the effect size so that the resulting posterior distribution no
+longer indicates evidence for an effect. The goal of the replication study is
+then to show that the sceptical prior is unrealistic, and replication success is
+achieved if there is sufficient conflict between the prior and the replication
+data. The procedure can be summarized in a single quantitative measure, termed
+the sceptical $p$-value.
 % extension 1
@@
 of evidence. The procedure can again be summarized in a single measure called
-the sceptical Bayes factor.
-% The sceptical prior is now determined such that the original finding is no
-% longer convincing in terms of a Bayes factor. In contrast to tail
-% probabilities,
-% We find that the extended method combines two notions of replicability: It
-% requires that original and replication study independently provide evidence for
-% an effect and ensures that their effect estimates are compatible.
-The sceptical Bayes factor has similar properties as the sceptical $p$-value but
-it avoids a statistical paradox which the sceptical $p$-value suffers from -- in
-some situations the sceptical $p$-value may indicate replication success even
-though the effect estimate from the replication is substantially smaller than
-the effect estimate from the original study. % , which cannot happen with the sceptical
-% Bayes factor.
-% Bayes factors have a more
-% natural interpretation and allow for direct quantification of evidence for one
-% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
-% to a single measure quantifying the degree of replication success called the
-% sceptical Bayes factor.
+the sceptical Bayes factor. The sceptical Bayes factor has similar properties as
+the sceptical $p$-value but it avoids a statistical paradox which the sceptical
+$p$-value suffers from -- in some situations the sceptical $p$-value may
+indicate replication success even though the effect estimate from the
+replication is substantially smaller than the effect estimate from the original
+study.
+% extension 3
 The third extension provides a framework for Bayesian design of replication
@@
 the sceptical $p$-value and the sceptical Bayes factor.
-% External knowledge, such as data from other studies, is ubiquitous in the
-% replication setting and taking it into account can lead to potentially more
-% efficient designs compared to classical approaches.
 

### 2022-12-20 source/intro.Rnw
polish

@@
 Despite their importance, the traditional academic system has made it
-unattractive for researchers to conduct replication studies as publications,
-citations, and grant money are typically easier to acquire by conducting novel
-research. This is because until recently, most scientific journals hardly
-published any replication studies since the emphasis was on ``innovation''
-rather than on ``repetition'' \citep{Makel2012, Martin2017, Coiera2021}. As a
-result, researchers often had no other choice than to focus their efforts on
-producing novel and eye-catching research results in order to build successful
-careers \citep{Binswanger2014, Moher2018}.
+unattractive for researchers to conduct replication studies. This is because
+until recently, most scientific journals hardly published any replication
+studies as the emphasis was on ``innovation'' rather than on ``repetition''
+\citep{Makel2012, Martin2017, Coiera2021}. As a result, researchers often had no
+other choice than to focus their efforts on producing novel and eye-catching
+research results in order to build successful careers \citep{Binswanger2014,
+  Moher2018}.
 
@@
 the raw data from the original study may not be available to the researchers
-conducting the replication study. The most important statistics are the effect
-estimates $\that_{o}$ and $\that_{r}$. They provide an estimate of the
-underlying effect size $\theta$ which quantifies the true effect or association
-of an intervention/exposure with an outcome variable. Typical effect sizes are
-mean differences and correlations (for continuous outcomes), odds ratios (for
-binary outcomes), or hazard ratios (for time-to-event outcomes). Depending on
-the type of effect size, a transformation might be required so that the
-assumption of approximately normally distributed effect estimates around the
-unknown effect size $\theta$ (for large enough sample sizes) is justified. This
-could be, for instance, the Fisher $z$-transformation for correlations or the
-log-transformation for odds/hazard ratios \citep[chapter 11]{Cooper2019}. The
-associated standard errors $\sigma_{o}$ and $\sigma_{r}$ represent the
-statistical uncertainty of the estimates. Typically, the available standard
-errors are only estimates of the true standard errors. However, in most parts of
-this thesis it will be assumed that $\sigma_{o}$ and $\sigma_{r}$ correspond to
-the true standard errors. This is the same assumption as in ordinary
-fixed-effect/random-effects meta-analysis, and typically reasonable if the
-sample size of the studies is not too small. Under the assumption of
-(asymptotic) normality, confidence intervals for $\theta$ and $p$-values for
-testing the null hypothesis $H_{0} \colon \theta = 0$ can be computed as shown
-in Table~\ref{tab:meta}.
+conducting the replication study. The effect estimates $\that_{o}$ and
+$\that_{r}$ provide an estimate of the underlying effect size $\theta$ which
+quantifies the true effect or association of an intervention/exposure with an
+outcome variable. Typical effect sizes are mean differences and correlations
+(for continuous outcomes), odds ratios (for binary outcomes), or hazard ratios
+(for time-to-event outcomes). Depending on the type of effect size, a
+transformation might be required so that the assumption of approximately
+normally distributed effect estimates around the unknown effect size $\theta$
+(for large enough sample sizes) is justified. This could be, for instance, the
+Fisher $z$-transformation for correlations or the log-transformation for
+odds/hazard ratios \citep[chapter 11]{Cooper2019}. The associated standard
+errors $\sigma_{o}$ and $\sigma_{r}$ represent the statistical uncertainty of
+the estimates. Typically, the available standard errors are only estimates of
+the true standard errors. However, in most parts of this thesis it will be
+assumed that $\sigma_{o}$ and $\sigma_{r}$ correspond to the true standard
+errors. This is the same assumption as in ordinary fixed-effect/random-effects
+meta-analysis, and typically reasonable if the sample size of the studies is not
+too small. Under the assumption of (asymptotic) normality, confidence intervals
+for $\theta$ and $p$-values for testing the null hypothesis
+$H_{0} \colon \theta = 0$ can be computed as shown in Table~\ref{tab:meta}.
 
@@
 find evidence against the null hypothesis is erroneously interpreted as evidence
-for the null hypothesis. Meta-analytic extensions of the significance approach
-define replication success by significance of a combined effect
-estimate.
+for the null hypothesis.
+
+Meta-analytic extensions of the significance approach define replication success
+by significance of a combined effect estimate.
 % \footnote{The meta-analytic approach can also be given a Bayesian

### 2023-02-14 source/intro.Rnw
paper VI revision and proofs

@@
   Samuel Pawel, Lucas Kook, Kelly Reeve \\
-  \textit{arXiv preprint}, 2022.
-  doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}.}
+  \textit{Biometrical Journal}, 2023.
+  doi:\href{https://doi.org/10.1002/bimj.202200091}{10.1002/bimj.202200091}.}
 
@@
 thesis are available at \url{https://github.com/SamCH93/thesis}. A snapshot of
-the git repository is archived at \url{https://doi.org/10.5281/zenodo.XXXXXXX}.
+the git repository is archived at \url{https://doi.org/10.5281/zenodo.7464296}.
 

### 2023-02-14 source/paper6.tex
reorganizatin for reproducibility
paper VI revision and proofs

--- 2022-12-18 paper6.tex
@@
 QRPs related to comparative simulation studies (Section \ref{sec6:QRP}). With an
-exemplary simulation study, we then show h?ow easy it is to present a novel,
+exemplary simulation study, we then show how easy it is to present a novel,
 made-up method as an improvement over others if QRPs are employed and \emph{a
@@
   \centering
-  \begin{tabular}{p{.05\textwidth} p{.11\textwidth} p{.75\textwidth}}
+  \begin{tabular}{p{.05\textwidth} p{.115\textwidth} p{.75\textwidth}}
     \toprule
@@
 acknowledgement of these individuals does not imply their endorsement of this
-article. The authors declare that they do not have any conflicts of interest.
+article.
 
@@
 
-  \item \textbf{AUC.} The AUC is given by
-  $$\text{AUC} = \max\{\text{PI}, 1 - \text{PI}\}$$
-        with $$\text{PI} = \widehat\Prob(Y_i \geq Y_j \given \rx_i, \rx_j), \; i,j = 1, \dots, n_{\text{test}},$$
-        where $Y_i$ and $Y_j$ denote case and non-case, respectively. The AUC is
-        related to the area under the receiver-operating-characteristic (ROC)
-        curve \citep{Steyerberg2019}. It will be used as a measure of
-        discrimination and values closer to one indicate better discriminative
-        ability. Discrimination describes the ability of a prediction model to
-        discriminate between cases and non-cases. Other discrimination measures,
-        such as accuracy, sensitivity, specificity, etc., are not considered
-        because we want to evaluate predictive performance in terms of
-        probabilistic predictions instead of point predictions/classification.
+  \item \textbf{AUC.} The AUC is the area under the
+        receiver-operating-characteristic (ROC) curve \citep{Steyerberg2019}. It
+        will be used as a measure of discrimination and values closer to one
+        indicate better discriminative ability. Discrimination describes the
+        ability of a prediction model to discriminate between cases and
+        non-cases. Other discrimination measures, such as accuracy, sensitivity,
+        specificity, etc., are not considered because we want to evaluate
+        predictive performance in terms of probabilistic predictions instead of
+        point predictions/classification.
 
@@
 denotes the log-likelihood of a binomial GLM and $\wvec$ is derived from a
-random forest variable importance measure $\IMP$ as
+random forest variable importance measure $\widetile{IMP}$ as
 $$w_j = 1 - \left(\frac{\IMP_j}{\sum_{k=1}^p \IMP_k}\right)^\gamma,$$
@@
 
-Figure~\ref{fig6:tienll} shows the differences in area under the curve (AUC)
+Figure~\ref{fig6:tieAUC} shows the differences in area under the curve (AUC)
 between \ainet{} and the other methods stratified by simulation conditions. As
@@
 \center
-\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_brier_sparsity0.pdf}
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS1.pdf}
 \caption{Tie-fighter plot for the difference in Brier score between any method
@@
 \center
-\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_scaledBrier_sparsity0.pdf}
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS2.pdf}
 \caption{Tie-fighter plot for the difference in scaled Brier score between any
@@
 \center
-\includegraphics[width=0.9\linewidth]{images/paper6/tie-fighter_nll_sparsity0.pdf}
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS3.pdf}
 \caption{Tie-fighter plot for the difference in log-score between any method on
@@
 \center
-\includegraphics[width=0.9\linewidth]{images/paper6/calibration-cslope_sparsity0.pdf}
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS4.pdf}
+\caption{Tie-fighter plot for the difference in AUC between any method on
+  the $y$-axis and \ainet{}. The 95\% confidence intervals are adjusted per
+  simulation condition using the single-step method. Larger values indicate
+  better performance of \ainet{}. } \label{fig6:tieAUC}
+\end{figure}
+\end{landscape}
+
+\begin{landscape}
+\begin{figure}[!ht]
+\center
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS5.pdf}
 \caption{Boxplots of calibration slopes stratified by method and simulation
@@
 \center
-\includegraphics[width=0.9\linewidth]{images/paper6/calibration-clarge_sparsity0.pdf}
+\includegraphics[width=0.9\linewidth]{images/paper6/figureS6.pdf}
 \caption{Boxplots of calibration in the large stratified by method and

### 2023-02-17 source/paper3.tex
typos

@@
 {\begin{tabular}{c} \textbf{Probability of replication success} \\
-   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \mathrm{external
+   {\scriptsize $\Pr(X_r \in S \given n_{r}, x_{o}, \mathrm{external~
     knowledge})$}
@@
 research is needed for investigating how systematic study deviations and
-external knowledge can be incorporated. Furthermore, as is standard in
+external knowledge can be incorporated. Furthermore, as in standard in
 meta-analysis we assumed that the variances of the effect estimates are known,

### 2023-02-17 source/paper4.tex
polish
typos

@@
 \begin{equation*}
-  \Pr(\data \given H_{i}) = \int \Pr(\data \given \theta, H_{i}) \p(\theta \given H_{i}) d
-  \theta
+  \Pr(\data \given H_{i}) = \int \Pr(\data \given \theta, H_{i})\,
+  \p(\theta \given H_{i}) \,\mathrm{d} \theta
 \end{equation*}
@@
     \sqrt{-z^{2}/k}\cdot \exp\left\{-(z^{2} + k)/2\right\}
-    & \text{if} \abs{z} \geq \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\}\\
+    & \text{if} \abs{z} \geq \surd\big\{-2 \mathrm{W}\big(-e^{-1}/\sqrt2\big)\big\}\\
     \mbox{minBF}_{01} \
-    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 W\big(-e^{-1}/\sqrt2\big)\big\} \\
+    & \text{if} ~ \sqrt{\log 2} \leq \abs{z} < \surd\big\{-2 \mathrm{W}\big(-e^{-1}/\sqrt2\big)\big\} \\
     \text{undefined}
@@
 $y \in [-e^{-1}, 0).$ If
-$\abs{z} \geq \sqrt{-2 W(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is located at
-the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative prior
-variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
+$\abs{z} \geq \sqrt{-2 \mathrm{W}(-e^{-1}/\sqrt2)} \approx 2.04$, $\BFIC$ is
+located at the intersection between $\BF_{12}$ and $\BF_{01}$ in the relative
+prior variance $g$, so equation (7) from \citet{Pawel2020b} can be used. For
 $\abs{z} \geq \sqrt{\log 2} \approx 0.83$, $\BF_{12}$ remains below $\BF_{01}$

### 2023-02-17 source/paper6.tex
typos

@@
 denotes the log-likelihood of a binomial GLM and $\wvec$ is derived from a
-random forest variable importance measure $\widetile{IMP}$ as
+random forest variable importance measure $\widetilde{\IMP}$ as
 $$w_j = 1 - \left(\frac{\IMP_j}{\sum_{k=1}^p \IMP_k}\right)^\gamma,$$

### 2023-03-29 source/intro.Rnw
typos and new references
fix data issue

@@
 
-\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
-I will now illustrate the assessment of replication success on data from the
-``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
-large-scale project attempted to replicate 53 landmark studies from the field of
-cancer biology \citep[and would perhaps better be named ``Replication Project'',
-see][for the distinction between ``replicabality'' and
-``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
-be repeated due to various difficulties, such as, missing information from the
-original studies or problems in conducting the experiments.
-\citet{Errington2021} report that these experiments led to data on 158
-quantitative effects. However, from the data which they provide only 132
-quantitative effects are provided with original and replication standardized
-mean difference effect estimates along with standard errors, and only they will
-be used in the subsequent analyses.
-
-\begin{figure}[!htb]
-<< "RPCB-graph", fig.height = 3.75 >>=
-za <- qnorm(p = 0.975)
-rpcb <- read.csv("data/rpcb.csv") |>
+<< "RPCB-data" >>=
+rpcb <- read.csv("data/rpcb-outcome-level.csv") |>
     mutate(id = paste0("(", paper, ", ", experiment, ", ", effect, ")"),
@@
                          labels = c("italic(p[r]) > 0.05",
-                                    "italic(p[r]) <= 0.05")))
+                                    "italic(p[r]) <= 0.05"))## ,
+           ## rsig = factor(pr <= 0.05, levels = c(FALSE, TRUE),
+           ##               labels = c("italic(p[r]) > 0.05",
+           ##                          "italic(p[r]) <= 0.05"))
+           ## ## uncomment for the same significance assessment as in RPCB paper
+           ## ## (differs in some cases due to normal approximation)
+           )
 ## compute sceptical p-value (TODO fix problems with NA)
@@
                             alternative = "one.sided", type = "nominal")
-
-zoom <- c(-2, 12)
+rpcbWithoutNA <- na.omit(rpcb)
+@
+
+\subsubsection{Example ``Reproducibility Project: Cancer Biology''}
+I will now illustrate the assessment of replication success on data from the
+``Reproducibility Project: Cancer Biology'' \citep{Errington2021}. This
+large-scale project attempted to replicate 53 landmark studies from the field of
+cancer biology \citep[and would perhaps better be named ``Replication Project'',
+see][for the distinction between ``replicability'' and
+``reproducibility'']{Goodman2016}. In the end, only 23 of the 53 studies could
+be repeated due to various difficulties, such as, missing information from the
+original studies or problems in conducting the experiments.
+\citet{Errington2021} report that these experiments led to data on 158
+quantitative effects. However, from the data which they provide only
+\Sexpr{nrow(rpcb)} quantitative effects are provided with original and
+replication standardized mean difference effect estimates along with standard
+errors, and only they will be used in the subsequent analyses.
+
+\begin{figure}[!htb]
+<< "RPCB-graph", fig.height = 3.75 >>=
+za <- qnorm(p = 0.975)
+zoom <- c(-2, 12) # c(-2.5, 5) # in original plot
 alphazoom <- 0.6
 ltyzoom <- 3
-rpcbWithoutNA <- na.omit(rpcb)
 cols <- adjustcolor(col = c("grey70", "grey5"), alpha.f = 0.8)
@@
     coord_fixed(xlim = c(-5, 30), ylim = c(-5, 30)) +
-    scale_fill_manual(values = cols, labels = scales::parse_format()) +
-    scale_color_manual(values = cols) +
+    scale_fill_discrete(labels = scales::parse_format()) +
+    ## scale_fill_manual(values = cols, labels = scales::parse_format()) +
+    ## scale_color_manual(values = cols) +
     theme_bw() +
@@
     coord_fixed(xlim = zoom, ylim = zoom) +
-    scale_fill_manual(values = cols, labels = scales::parse_format()) +
-    scale_color_manual(values = cols) +
+    ## scale_fill_manual(values = cols, labels = scales::parse_format()) +
+    ## scale_color_manual(values = cols) +
     theme_bw() +
@@
 grid.arrange(plotA, plotB, ncol = 2)
+## cf Figure 2—figure supplement 1
+## https://iiif.elifesciences.org/lax/71601%2Felife-71601-fig2-figsupp1-v3.tif/full/1500,/0/default.jpg
 @
-\caption{Results for 132 effects from the ``Reproducibility Project: Cancer
-  Biology'' \citep{Errington2021} for which effect estimates and standard errors
-  are available on standardized mean difference (SMD) scale. The right plot
-  shows a zoomed-in view of the dotted area in the left plot. The
-  \textit{p}-values are recomputed using a normal approximation. Two study pairs
-  with original effect estimate larger than 80 are not shown.}
+\caption{Results from \Sexpr{nrow(rpcb)} replication studies from the
+  ``Reproducibility Project: Cancer Biology'' \citep{Errington2021} for which
+  effect estimates and standard errors are available on standardized mean
+  difference (SMD) scale. The right plot shows a zoomed-in view of the dotted
+  area in the left plot. The \textit{p}-values are recomputed using a normal
+  approximation. Two study pairs with original effect estimate larger than 80
+  are not shown.}
 \label{fig:rpcb}
@@
 level. Specifically, from the
-\Sexpr{sum(rpcbWithoutNA$po2 < 0.05)} effects which were significant in the original study only \Sexpr{ sum(rpcbWithoutNA$po2
+\Sexpr{sum(rpcbWithoutNA$po2 < 0.05)} effects which were significant in the
+original study only \Sexpr{ sum(rpcbWithoutNA$po2
   < 0.05 & rpcbWithoutNA$pr2 < 0.05 & rpcbWithoutNA$d > 0)} were also
@@
 interval criteria since they do not take into account the uncertainty from both
-studies). For the total 132 replications, most successes occur for the
-meta-analytic significance (\Sexpr{nma}) and the prediction interval criteria
-(\Sexpr{npi}), followed by significance (\Sexpr{nsig}), and relative effect size
-(\Sexpr{nres}). However, looking at the combinations of the criteria, only in
-two replications are all criteria satisfied simultaneously (green).
-
-A detailed view for a subset of the data from the project is given in
-Table~\ref{tab:RPCB}. The subset is randomly chosen such that from every
-original study one effect and one replication of that effect is included. For
-the three replications at the bottom of the table (\#18, \#19, and \#20), all
-criteria indicate replication failure. For the other replications, the
-conclusions are more ambiguous as in no single case are all criteria met
-simultaneously. For instance, the first three replications satisfy the
-significance criterion ($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic
-significance criterion ($p_{m} < 0.05$) and the $Q$-test/prediction interval
-criterion ($p_{Q} > 0.05$), yet the replication effect estimate is smaller than
-the original one so does not satisfy the relative effect size criterion
-($d < 1$). The fourth replication, on the other hand, satisfies the relative
-effect size criterion ($d \geq 1$) but fails to satisfy the significance
-criterion as the original study was not significant ($p_{o} > 0.05$).
-% For example, replication \#17 is a clear
-% failure with respect to the relative effect estimate ($d < 1$) and the
-% significance criteria ($p_{o} > 0.05$ and $p_{r} > 0.05$), yet the $Q$-test does
-% not indicate evidence for inconsistency of the two effect estimates
-% ($p_{Q} > 0.05$).
+studies). For the total \Sexpr{nrow(rpcb)} replications, most successes occur
+for the meta-analytic significance (\Sexpr{nma}) and the prediction interval
+criteria (\Sexpr{npi}), followed by significance (\Sexpr{nsig}), and relative
+effect size (\Sexpr{nres}). However, looking at the combinations of the
+criteria, only in two replications are all criteria satisfied simultaneously
+(green).
+
+A detailed view for an illustrative subset of the data from the project is given
+in Table~\ref{tab:RPCB}. The subset is chosen such that from every original
+study one effect and one replication of that effect is included. For two
+replications at the bottom of the table (\#18 and \#20), all criteria indicate
+replication failure. For the other replications, the conclusions are more
+ambiguous as in no single case are all criteria met simultaneously. For
+instance, the first three replications satisfy the significance criterion
+($p_{o} < 0.05$ and $p_{r} < 0.05$), the meta analytic significance criterion
+($p_{m} < 0.05$) and the $Q$-test/prediction interval criterion
+($p_{Q} > 0.05$), yet the replication effect estimate is smaller than the
+original one so does not satisfy the relative effect size criterion ($d < 1$).
+The fourth replication, on the other hand, satisfies the relative effect size
+criterion ($d \geq 1$) but fails to satisfy the significance criterion for the
+original study ($p_{o} > 0.05$) and the $Q$-test/prediction interval criterion
+($p_{Q} \leq 5\%$).
 
@@
 set.seed(7)
-rpcbTable <- rpcb |>
+rpcbTable1 <- rpcb |>
     na.omit() |>
@@
            cirFormat = ciFormat(lower = cirL, upper = cirU, dollar = TRUE),
-           cimFormat = ciFormat(lower = cimL, upper = cimU), dollar = TRUE) |>
+           cimFormat = ciFormat(lower = cimL, upper = cimU), dollar = TRUE)
+rpcbTable <- rpcbTable1 |>
     select(id,
@@
   \citep{Errington2021}. Shown are effect estimates and prior/posterior means
-  with \Sexpr{100*(1-alpha)}\% confidence/credible interval. The original finding is
-  challenged with a sceptical prior, sufficiently concentrated around zero so
-  that the resulting posterior is no longer convincing at level
-  $\alpha = \Sexpr{100*(alpha)}\%$. Prior predictive \textit{p}-values $p_{\text{Box}}$ are
-  computed for quantifying prior-data conflict.}
+  with \Sexpr{100*(1-alpha)}\% confidence/credible interval. The original
+  finding is challenged with a sceptical prior, sufficiently concentrated around
+  zero so that the resulting posterior is no longer convincing at level
+  $\alpha = \Sexpr{100*(alpha)}\%$. Prior predictive \textit{p}-values
+  $p_{\text{Box}}$ are computed for quantifying prior-data conflict.}
 \label{fig:RBillustration}
@@
 @
+
 \subsubsection{The sceptical \textit{p}-value}
@@
 
+<< "examples-sceptical-p" >>=
+ex2 <- rpcbTable1[5,]
+@
+
 The last column of Table~\ref{tab:RPCB} shows the one-sided sceptical $p$-value
@@
 (one-sided) -- replication success at this level is impossible with the
-sceptical $p$-value. The second property is illustrated by replication \#8. Here
+sceptical $p$-value. The second property is illustrated by replication \#5. Here
 both the original and replication studies were significance. However, the effect
-estimate from the replication was roughly 60\% smaller than the one from the
+estimate from the replication was roughly \Sexpr{round(100*(1 - ex2$d), 0)}\%
+smaller than the one from the
 original study, and significance is merely achieved because the standard error
-was much smaller (\ie{} around $1/\surd c \approx 1/2.8$ times smaller). The
-sceptical $p$-value is therefore only $p_{\text{S}} = 0.12$, indicating less
-evidence for replication success.
+was much smaller (\ie{} around
+$1/\surd c \approx 1/\Sexpr{round(sqrt(ex2$c), 2)}$ times smaller). The
+sceptical $p$-value is therefore only
+$p_{\text{S}} = \Sexpr{pFormat(ex2[,"ps1"])}$, indicating less evidence for
+replication success.
 
@@
   Samuel Pawel, Lucas Kook, Kelly Reeve \\
-  \textit{Biometrical Journal}, 2023.
+  \textit{Biometrical Journal}, 2023, e2200091.
   doi:\href{https://doi.org/10.1002/bimj.202200091}{10.1002/bimj.202200091}.}
@@
 \citep{Errington2021} were downloaded from
-\url{https://doi.org/10.17605/osf.io/e5nvr}. The relevant variables were then
-extracted from the file ``\texttt{RP\_CB Final Analysis - Effect level
-  data.csv}''. All analyses from this chapter were conducted in the R
+\url{https://github.com/mayamathur/rpcb} (commit a1e0c63). The R script
+\texttt{preprocess-rpcb-data.R} available on the git repository accompanying
+this thesis shows all preproccessing steps that were performed for extracting
+the relevant variables. All analyses from this chapter were conducted in the R
 programming language version \Sexpr{paste(version$major, version$minor, sep =

### 2023-03-29 source/data/extract.R

@@ -1,11 +1,0 @@
-library(dplyr)
-# download from https://osf.io/39s7j
-dat <- read.csv("RP_CB Final Analysis - Effect level data.csv")
-datClean <- dat |>
-    select(paper = Paper.., experiment = Experiment.., effect = Effect..,
-           internalReplication = Internal.replication..,
-           smdo = Original.effect.size..SMD.,
-           so = Original.standard.error..SMD., no = Original.sample.size,
-           smdr = Replication.effect.size..SMD.,
-           sr = Replication.standard.error..SMD. , nr = Replication.sample.size)
-write.csv(x = datClean, file = "rpcb.csv", row.names = FALSE)

### 2023-03-29 source/data/preprocess-rpcb-data.R

@@ -1,0 +1,141 @@
+## libraries
+library(dplyr) # for data wrangling
+library(ggplot2) # to reproduce plots from publication
+
+## RPCB data with SMD transformed effect sizes but before aggregating internal replications
+## https://github.com/mayamathur/rpcb/tree/master/Prepped%20data/Intermediate%20work
+dat <- read.csv(file = "intermediate_dataset_step3.csv")
+dat2 <- dat %>%
+    filter(!is.na(origDirection),
+           quantPair == TRUE)
+
+## organize data set for reanalysis
+datClean <- dat2 %>%
+    mutate(
+        ## define identifier for paper, experiment, effect, internal replication
+        id = paste0("(", pID, ", ", eID, ", ", oID, ", ", internalID, ")")
+    ) %>%
+    select(
+        osf = OSF.project.link,
+        id,
+        paper = pID,
+        experiment = eID,
+        effect = oID,
+        internalReplication = internalID,
+        resulto = origDirection,
+        resultr = repDirection,
+        ## effect sizes and standard errors on SMD scale
+        smdo = origES3,
+        so = origSE3,
+        smdr = repES3,
+        sr = repSE3,
+        ## effect sizes, standard errors, p-values, confidence intervals on original scale
+        effectType = Effect.size.type,
+        ESo = Original.effect.size,
+        seESo = Original.standard.error,
+        lowerESo = Original.lower.CI,
+        upperESo = Original.upper.CI,
+        po = origPval,
+        ESr = Replication.effect.size,
+        seESr = Replication.standard.error,
+        lowerESr = Replication.lower.CI,
+        upperESr = Replication.upper.CI,
+        pr = repPval,
+        ## original and replication sample size
+        ## (not clear whether group or full sample size)
+        no = origN,
+        nr = repN
+    )
+
+
+## should give 20 original null effects and 10 "successful" null replications
+## (see null results in Table 1)
+datClean %>%
+    summarise(nulls = sum(resulto == "Null"),
+              successes = sum(resulto == "Null" &
+                              resultr %in% c("Null-positive", "Null-negative",
+                                             "Null")))
+
+## should give 112 original positive effects and 44 successful replications
+datClean %>%
[…]
